### 2019-01-04 algorithm chapter.Rmd
Moved from masters repo

---
title: "An algorithm for a spatial mapping using a hexagon tilegram, with application to Australia disease maps"
author: "Stephanie"
date: "6 December 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Abstract

<!--
problem has been studied
what is the goal of the thesis/paper
brief statement on existing solutions and their drawbacks
major  contributions  of  the  thesis
State  briefly  assumptions  and  limitations. 
The  abstract  should  also  include  major idea(s)
the type (e.g. performance, complexity) and result of analysis done
-->

KEYWORDS:

# Introduction

Representing the globe in 2D space has presented issues for many years. Methods have been established to visualise geographical space.
We present a solution for alternate visualisations when the intention is to represent the spatial distribution.

## Motivation
<!--
Problem   statement   (precise   definition   and   importance);   
avoid   very   technical definitions  and  statements, give  good  intuition for your involved definitions or facts. 
-->

- Spatial distributions are not well presented when areas differ in size.
- We want to understand the distribution among population
- We can benefit from making the focus the distribution, not the geography

<!--
Existing  solutions  and  their  criticism  (limit  only  to  those  directly  relevant  to  the  contribution of the thesis; give a motivation for doing research on the topic); 
-->

- Presenting spatial distributions
- Extremely small areas are lost not easily compared at a high level
- Choropleths; unequal space on the display, difficult to represent Australia
- Cartograms; strong distortions misrepresent Australia

<!--
With different characteristics or properties:

-->

- Unusual population settlement and dispersion over the geographical space: Australia
Dense south east, sparse central and west

- Applying alternative maps that allow for dense population areas when cities that are population dense are close together

## Background
<!--
basic facts needed to tune the reader to the thesis or paper
-->

- Choropleth methods are accurate geographically.
- Cartogram alternative map has been used historically.
- Spatial relationships are preserved.

<!--
all  known  results  relevant  to  the  problem  stated,  
whether  or  not  they  are  used  in  proposed  contributions
-->

<!--
Discuss  advantages  and  drawbacks  of  known  solutions  that  are  relevant  to  your  problem, 
discuss  the  relevance of each reviewed item to your topic and your solutions. 
-->

<!--
For  every  discussed  reference,  it  is  very  important  to  relate  them  to  your  problem  and  contribution  in  one  of  several  ways:  
it  does  not  exactly  solve  the  same  problem,
it  solves  the  same  problem  but  makes  different  assumptions  about  the  system, 
it  has  some  limitations  that you  do  not  have, 
it  makes  the  same  assumptions  but  does  not  work  well  under  certain  
conditions  and  scenarios  for  which  you  have  better  solutions,  or, 
if  none  of  these  is  true,  you are   considering   it   as   valid   competitor,   and   will   try   to   defeat   it   in   your   analytical   or

experimental  comparisons.  
-->
## Proposed Solution

<!--
Contributions (proposed solutions; why they are expected to be better; essence of the idea(s) used in proposed solutions); 
What the algorithm is trying to do:
-->

- Like Dorling, same shape will be used.
Like tilegram, tesselation using equally sized shapes.

- Allocate each geographic area to a map space of consistent tesselated shape

which is different from existing algorithms:
- contiguous, keeps exact neightbours, no recognisable shape
- non contiguous, keeps shape, can lose neighbours

<!--
Why the reader should believe that it is correct or reasonable.
-->
- Clear to see spatial distribution, 
_ Should keep neighbours relationships intact as geographic neighbours will have similar values

<!--
If it is supposed to be “better”, what is meant by better.
-->
Easier to read distribution at a distance, see a much larger area, general relationship at a glance

<!--
Conditions, assumptions and limitations of the research done; 
-->
Works well for America, states are almost homogeneous 
Works well for England, London is the biggest issue, pushing out rural areas does not disturb population dense areas.

<!--
Analysis  (theoretical,  experimental,  simulations,  implementations, done  in  thesis;  under what conditions and scenarios is your solution best?  
-->

Our solution considers multiple population dense areas.

Allows dispersion to be increased when needed, and distance from origin to be considered

The Dorling maps in [@TVSSS] give examples of displacing central geographically small, population dense areas.
This inspired the concept of this algorithm.

# Algorithm

The algorithm operates on a set of polygons.
There are parameters considered that may be provided, or will be automatically derived.
All necessary functions are exported, with a main function `create_hexmap` used to step through automatically.

When utilising individual functions, we recommend the following approach:

## Polygon Information

The collection of polygons should be considered first.
There are several ways of providing the set of polygons.
The following methods are available via the `read_shape` function.

To utilise a shape file from a directory on your device, provide the file path for .shp file.
The `st_read` function is applied internally to create the sf object.
If the shape file is an .Rda file, it is loaded into the current environment.
Empty geometries are removed from the sf object, and the remaining polygons are projected to the Australian standard.

```{r}

```

The geometry column now contains projected polygons,
the projected centroids are derived for all polygons remaining in the set.

## Hexgon grid
Create a grid of hexagon centroids using the `create_grid` function.

The following parameter values are necessary for this step, and will be automatically derived in the `create_hexmap` function if not provided:

- buffer distance: *the distance, in degrees, to extend the hexagon grid beyond the polygon centroids provided*
- size of the hexagons: *a float value in degrees for the width of the hexagons to be placed on the map space*
- filter distance: *the amount of hexagons around each centroid to consider for allocation, by default this is 10 hexagons*

The grid creation takes several steps:

```{r}
# create grid calls these functions
# call create grid here, or call these parts individually, may be a lot of code
```

### Step 1: Expand the grid
Two sequences are used, one for longitude and another for latitude.
The sequences begin at the minimum longitude or latitude, minus the buffer distance.
Equally spaced intervals, the size of the hexagons, are created up to the maximum longitude or latitude, plus the buffer distance.

An individual point is created from all combinations of longitude and latitude sequences.

This grid is square, which will not facilitate tesselated hexagons. 
Every second latitude (row) of points will be shifted right by half of the hexagon size.

There are more points than necessary on this grid.
To filter the grid for appropriate hexagons for allocation,
the `create_buffer` function is used.

### Step 2: Rolling windows
The longitude columns and latitude rows are given integer id values.
The rows and columns are then divided into 20 groups, 
recording the amount of rows in each latitude group and the amount of columns in each longitude group.

The amount of rows and columns are then used to make manual rolling windows.

The first rolling window function finds the minimum and maximum centroid values for the longitude columns and latitude rows.

The second rolling window function finds the average of the rolling minimum and rolling maximum centroid values, for the longitude columns and latitude rows.

<!--
Figure of rolling window construction
-->

### Step 3: Filtering the grid
Only the grid points between the rolling average of the minimum and maximum centroid valuesare kept, for each row and column of the grid.

<!--
Grid point figure
-->

## Centroid to focal point distance

```{r}
#map closest focal point function
```

For each polygon centroid in the set. Find the distance to each of the focal points provided. The closest focal point name, the distance to the polygon centroid, and the angle from focal point to polygon centroid will be returned and added to the polygon data set in the polygon centroid row.

The distance between the polygon centroid and it's closest focal point data set is used to arrange the data set for allocation. The points are arranged in ascending order, from the centroid closest to any of the focal points, to the furthest.

## Allocation of centroids

```{r}
#loop of centroid allocation
```

Allocation of all centroids can now take place using the set of polygon centroids and the hexagon map grid. 
For each polygon centroid, only the hexagon grid points that have not yet been used can be considered.
The filter distance parameter is used to subset possible grid points to only those surrounding the polygon centroid within the filter distance.
Using the angle between each polygon centroid, and it's the closest focal point, the subset of points is filtered again.
Of these possible points, only those within a specific amount of degrees plus and minus a specific angle range are kept. This angle begins at 30 degrees by default, and may increase if necessary.

<!--
figure of angle growing to show allocation of hexagons
-->

If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded, only when a maximum distance is reached will the angle expand to accomodate more possible grid points.

The allocation is returned and combined with the data relating to each polygon.

<!--
Prosecode:  Number each step, never break a loop over steps,
use subnumbering for parts of each step, and
include explanatory text.
Literate code:  The algorithm is introduced gradually,
intermingled with discussion of underlying ideas.
-->

## Applications of algorithm

<!--
Is  your  solution  always  working?  
Can  you  prove it? 
How does it work? 
-->

Examples of Melbourne, Victoria, Australia
At different levels, distance from original centroids, change in area

LGA of all australia
sa2 for queensland

<!--
Is your analysis about worst case or average case? 
What kind of theoretical and analytical support can you give for your proposed scheme/solution? 
-->

# Evaluation

<!--
The  performance  of  your  solution  can  be  compared  with  existing  solutions,  if  any  exists 
under  same  or  similar  assumptions,  analytically  and/or  by  doing  a  simulation.

Find examples of measures of cartogram effectiveness

-->

Measure changes to areas:
Each hexagon area in the set of $npolys$ is standardised to 1 unit.
Where 1 unit is the area of a hexagon of the designated size.

$area_{h_i} = 1$

$area_h = 1 * npolys$

$y_i$ denotes the statistic of interest for polygon i, where i = 1,...,npolygs
$x_i$ denotes the spatial area for polygon i, where i = 1,...,npolys

Areal Statistic Distortion is the change in the areal distribution of the set of polygons.
Difference between space taken by polygons and space taken by hexagons, with respect to the desired statistic. Setting the desired statistic to area givesthe change in map space used to represent the polygons.

The average when considering area used to display:

$A = \sum_{i=1}^{npolys}y_ix_i/ \sum_{i=1}^{npolys}x_i$

$H = \sum_{i=1}^{npolys}y_i/npolys$

Using $w_i = x_i/\sum_{i=1}^{npolys}x_i$

$\sqrt{ 1/npolys\sum_{i=1}^{npolys}(y_i - \bar y)^2 w_i }$

Considering only a local area distortion: 
Where the subset used contains only neighbours within a certain distance of the polygon centroid

Where $\bar y_d$ is the average of the polygon statistics considering only the polygons where the distance between polygon centroid x_i and polygon centroid x_p is less than d:

$d(x_ix_p) < d$

$\sqrt{ 1/npolys\sum_{i=1}^{npolys}(y_i - \bar y_d)^2 w_i }$

<!--
Apply methods of evaluation used elsewhere
Nusrat, Alam and Kobourov:
- Statistical accuracy: how well do the modified areas
represent the corresponding statistic shown (e.g.,
population or GDP). This is measured in terms of
“cartographic error.”
- Geographical accuracy: how much do the modified
shapes resemble the original geographic shapes and
how well preserved are their relative positions.
- Topological accuracy: how well does the topology (as
measured by adjacent regions) of the cartogram
match that of the original map.
-->

# Summary

<!--
What did you achieve with this research? 
What are the drawbacks of your solution(s)? 
What kind  of  future  work  can  be  done? 
Do  you  have  some  ideas  that  you  intend  to  study  further? 
The  ownership  of  some  other  possible  solutions,  not  fully  explored,  or  subject  of  your  
forthcoming  different  article,  can  be  protected  by  outlining  them  briefly  in  the  conclusion  
section, sometimes with reference to upcoming article. 
-->

# Discussion

\pagebreak

# Reference List

<div id="refs"></div>

### 2019-01-04 algorithm_radix.Rmd
Radix format

--- 2019-01-04 algorithm chapter.Rmd
@@
 title: "An algorithm for a spatial mapping using a hexagon tilegram, with application to Australia disease maps"
-author: "Stephanie"
-date: "6 December 2018"
-output:
-  pdf_document: default
-  html_document: default
+
+author:
+  - name: Stephanie Kobakian
+    url: https://github.com/srkobakian
+    affiliation: Queensland University of Technology
+date: "`r Sys.Date()`"
+output: radix::radix_article
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE)
 ```
+
 # Abstract

### 2019-01-07 algorithm_radix.Rmd
Parameters section

@@
 - Like Dorling, same shape will be used.
-Like tilegram, tesselation using equally sized shapes.
+Like tilegram, tessellation using equally sized shapes.
 
-- Allocate each geographic area to a map space of consistent tesselated shape
+- Allocate each geographic area to a map space of consistent tessellated shape
 
 which is different from existing algorithms:
-- contiguous, keeps exact neightbours, no recognisable shape
+- contiguous, keeps exact neighbours, no recognisable shape
 - non contiguous, keeps shape, can lose neighbours
@@
 
+## Parameters
+
+The `create_hexmap` functions requires several parameters. If not provided the information may be derived from the polygon set used.
+
+**The following must be provided to `create_hexmap`:**
+
+The set of polygons to be made into a hexagon map:
+`shp: a shape file`
+
+The location of a set of polygons to be made into a hexagon map:
+`shp_path: character string location of shape file`
+
+A column of unique names or id values for each area
+`sf_id: name of a unique column that distinguishes areas`
+
+A data frame of reference points to determine the order of allocation
+`focal_points a data frame of reference locations when allocating hexagons, capital cities of Australia are provided as capital_cities`
+
+```{r}
+library(tidyverse)
+library(sugaRbag)
+
+shp_path <- "data/lga_2011.rda"
+sf_id <- "LGA_CODE11"
+focal_points <- sugaRbag::capital_cities
+```
+
+**The following will be determined within `create_hexmap` if not provided, but must be created for the following example:**
+
+- `projstring	a string to indicate the projection and epsg`
+- `epsg	the four character string to indicate the CRS`
+- `buffer_dist: a float value for distance in degrees to extend beyond the - geometry provided`
+- `hex_size	a float value in degrees for the diameter of the hexagons`
+- `filter_dist amount of hexagons around centroid to consider for allocation`
+- `width the angle used to filter the grid points around a centroid`
+
+These parameters will be created when they are needed in the example:
+
+```{r}
+width <- 30 # arbitrary angle width
+```
+
+<!--
+needed later:
+
+- filter distance: *the amount of hexagons around each centroid to consider for allocation, by default this is 10 hexagons*
+-->
+
 When utilising individual functions, we recommend the following approach:
@@
 
-To utilise a shape file from a directory on your device, provide the file path for .shp file.
-The `st_read` function is applied internally to create the sf object.
-If the shape file is an .Rda file, it is loaded into the current environment.
+- To utilise a shape file from a directory on your device, provide the file path for .shp file.
+- The `st_read` function is applied internally to create the sf object.
+- If the shape file is an .Rda file, it is loaded into the current environment.
+
 Empty geometries are removed from the sf object, and the remaining polygons are projected to the Australian standard.
 
+We will use the Local Government Areas of Hobart as an example:
+
 ```{r}
+# Read in shape information
+tas_shp <- read_shape(shp_path = shp_path)
 
+# Convert to a simple features object
+tas_lga <- sf::st_as_sf(tas_shp)
+
+# Select only desired LGA areas, those from Tasmania.
+tas_lga <- tas_shp %>% filter(STE_NAME11 == "Tasmania")
+tas_lga[[sf_id]] <- droplevels(as.factor(tas_lga[[sf_id]]))
+
+## Not necessary within `create_hexmap`:
+## Derive projection information
+crs_info <- sf::st_crs(tas_lga)
+proj4string <- crs_info$proj4string
+epsg <- crs_info$epsg
+
+## For UTM as per shape file
+projstring <- paste0("+init=epsg:", epsg, " ", proj4string, collapse = "")
+## if long lat is preferred to UTM, and not in proj4string:
+projstring <- "+init=epsg:3112 +proj=longlat +lat_1=-18 +lat_2=-36 +lat_0=0 +lon_0=134 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +no_defs"
+
+## Use the create_centroids function to find polygon centroids:
+centroids <- create_centroids(shp_sf = tas_lga, sf_id = sf_id, projstring = projstring, verbose = FALSE)
 ```
 
-The geometry column now contains projected polygons,
-the projected centroids are derived for all polygons remaining in the set.
-
-## Hexgon grid
+## Hexagon grid
 Create a grid of hexagon centroids using the `create_grid` function.
 
-The following parameter values are necessary for this step, and will be automatically derived in the `create_hexmap` function if not provided:
-
-- buffer distance: *the distance, in degrees, to extend the hexagon grid beyond the polygon centroids provided*
-- size of the hexagons: *a float value in degrees for the width of the hexagons to be placed on the map space*
-- filter distance: *the amount of hexagons around each centroid to consider for allocation, by default this is 10 hexagons*
-
-The grid creation takes several steps:
+The grid creation takes several steps. It requires the centroids, the bounding box, the hexagon size and the buffer distance.
 
 ```{r}
-# create grid calls these functions
-# call create grid here, or call these parts individually, may be a lot of code
+## Not necessary within `create_hexmap`:
+## create the bounding box from the set of polygon centroids:
+bbox <- tibble::tibble(min = c(min(centroids$longitude), min(centroids$latitude)),
+        max = c(max(centroids$longitude), max(centroids$latitude)))
+
+hex_size <- (bbox$max[1] - bbox$min[1])/(bbox$max[2] - bbox$min[2]) / 10
+
+buffer_dist <- max((bbox$max[1] - bbox$min[1]), (bbox$max[2] - bbox$min[2]))*0.3
 ```
@@
 
-This grid is square, which will not facilitate tesselated hexagons. 
+```{r}
+grid <- tibble::as.tibble(expand.grid(hex_long = seq(bbox$min[1] - buffer_dist,
+    bbox$max[1] + buffer_dist,
+    hex_size),
+    hex_lat = seq(bbox$min[2] - buffer_dist,
+        bbox$max[2] + buffer_dist,
+        hex_size)))
+```
+
+This grid is square, which will not facilitate tessellated hexagons. 
 Every second latitude (row) of points will be shifted right by half of the hexagon size.
+
+```{r}
+# Find every second latitude
+shift_lat <- grid %>% dplyr::select(hex_lat) %>%
+    dplyr::distinct() %>%
+    dplyr::filter(dplyr::row_number() %% 2 == 1) %>% unlist()
+
+# Shift the longitude of every second latitude to the right to make hex structure
+grid <- grid %>%
+    dplyr::mutate(hex_long = ifelse(hex_lat %in% shift_lat, hex_long,
+        hex_long + (hex_size / 2))) %>%
+    dplyr::mutate(id=1:NROW(.)) %>%
+    dplyr::mutate(assigned=FALSE)
+```
+
+Each row and column is given an ID
+
+```{r}
+grid <- grid %>%
+    mutate(hex_long_int = dense_rank(hex_long)-1,
+        hex_lat_int = dense_rank(hex_lat)-1)
+```
 
@@
 
+```{r}
+return_grid <- create_buffer(centroids, grid, hex_size, buffer_dist)
+```
+
 ### Step 2: Rolling windows
-The longitude columns and latitude rows are given integer id values.
-The rows and columns are then divided into 20 groups, 
-recording the amount of rows in each latitude group and the amount of columns in each longitude group.
+The rows and columns are divided into 20 groups. The amount of rows in each latitude group and the amount of columns in each longitude group are then used as the width of manual rolling windows.
 
-The amount of rows and columns are then used to make manual rolling windows.
-
-The first rolling window function finds the minimum and maximum centroid values for the longitude columns and latitude rows.
+The first rolling window function finds the minimum and maximum centroid values for the groups of longitude columns and the groups of latitude rows.
 
@@
 ### Step 3: Filtering the grid
-Only the grid points between the rolling average of the minimum and maximum centroid valuesare kept, for each row and column of the grid.
+Only the grid points between the rolling average of the minimum and maximum centroid values are kept, for each row and column of the grid.
 
@@
 
-If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded, only when a maximum distance is reached will the angle expand to accomodate more possible grid points.
+If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded, only when a maximum distance is reached will the angle expand to accommodate more possible grid points.
 
@@
 <!--
-Prosecode:  Number each step, never break a loop over steps,
-use subnumbering for parts of each step, and
+Prose code:  Number each step, never break a loop over steps,
+use sub numbering for parts of each step, and
 include explanatory text.
@@
 
-Examples of Melbourne, Victoria, Australia
+Examples of Melbourne, Tasmania, Australia
 At different levels, distance from original centroids, change in area
 
-LGA of all australia
-sa2 for queensland
+LGA of all Australia
+SA2 for Queensland
 
@@
 Difference between space taken by polygons and space taken by hexagons, with respect to the desired statistic.
-Setting the desired statistic to area givesthe change in map space used to represent the polygons.
+Setting the desired statistic to area gives the change in map space used to represent the polygons.
 
@@
 
+Old neighbours over new neighbours?
 <!--

### 2019-01-08 algorithm_radix.Rmd
fixing toy example tasmania

@@
 
+tas_lga <- tas_lga %>%
+    sf::st_transform(., crs = projstring)
+
 ## Use the create_centroids function to find polygon centroids:
@@
 
+```{r, fig.cap="Tasmanian Local Government Areas and derived centroids."}
+fort_tas <- fortify_sfc(tas_lga, projstring = projstring)
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "green") + geom_point(aes(x=longitude, y = latitude),data= centroids)
+```
+
 ## Hexagon grid
+
 Create a grid of hexagon centroids using the `create_grid` function.
@@
 ```{r}
-grid <- grid %>%
+full_grid <- grid %>%
     mutate(hex_long_int = dense_rank(hex_long)-1,
@@
 There are more points than necessary on this grid.
+
+### Step 2: Rolling windows
+
 To filter the grid for appropriate hexagons for allocation,
@@
 ```{r}
-return_grid <- create_buffer(centroids, grid, hex_size, buffer_dist)
+grid <- create_buffer(centroids, full_grid, hex_size, buffer_dist)
 ```
 
-### Step 2: Rolling windows
 The rows and columns are divided into 20 groups. The amount of rows in each latitude group and the amount of columns in each longitude group are then used as the width of manual rolling windows.
@@
 
+```{r}
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "green") + geom_point(aes(x=longitude, y = latitude), colour = "red", data= centroids) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "black", data = full_grid, size = 0.5) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "grey", data = grid, size = 0.75)
+```
+
 <!--
@@
 ```{r}
-#map closest focal point function
+# Split the centroid data set
+centroids <- centroids %>% 
+  nest(longitude, latitude) %>% 
+  mutate(closest = map(data, closest_focal_point, focal_points = focal_points)) %>% 
+  unnest(data, closest) %>% 
+  arrange(focal_distance)
 ```
@@
 
+Define a distance around a centroid to consider for possible hexagon location.
+
 ```{r}
-#loop of centroid allocation
+## Not necessary within `create_hexmap`:
+## Consider hexagon points up to a certain distance from centroid
+
+filter_dist <- (hex_size)*10
+```
+
+Allocate each centroid, beginning with the closest to a focal point, extending to the furthest. Will preserve spatial relationship.
+
+```{r}
+hexmap_allocation <- allocate(centroids = centroids,
+        hex_grid = grid,
+        hex_size = hex_size,
+        filter_dist = filter_dist,
+        width = width,
+        focal_points = focal_points,
+        verbose = TRUE,
+        id = sf_id)
 ```

### 2019-01-10 algorithm_radix.Rmd
more steps in filtering the grid

@@
 The algorithm operates on a set of polygons.
-There are parameters considered that may be provided, or will be automatically derived.
+There are parameters needed that may be provided, or will be automatically derived.
 All necessary functions are exported, with a main function `create_hexmap` used to step through automatically.
@@
 
-```{r}
+```{r, eval = FALSE}
 hexmap_allocation <- allocate(centroids = centroids,
@@
 For each polygon centroid, only the hexagon grid points that have not yet been used can be considered.
+
+```{r}
+s_centroids <- centroids %>% arrange(focal_distance)
+
+s_centroids <- split(s_centroids, s_centroids[["focal_distance"]])
+
+# Set up allocation data frame
+centroid_allocation <- NULL
+```
+
 The filter distance parameter is used to subset possible grid points to only those surrounding the polygon centroid within the filter distance.
+
+```{r}
+# keep value to reset expanded distances
+expand_dist <- filter_dist
+```
+
+The following example considers one of the Local Government Areas. 
+These steps are repeated for each polygon.
+
+### Step 1: Filter the grid for unassigned hexagon points
+
+```{r}
+# filter for only the available hex grid points
+hex_grid <- grid %>% filter(!assigned)
+```
+
+### Step 2: Filter the grid points for those closest to the centroid
+```{r}
+
+# filter grid for avaiable points
+centroid1 <- centroids %>% head(1)
+
+flong <- centroid1$longitude
+flat <- centroid1$latitude
+
+hex_grid <- hex_grid %>% ungroup() %>%
+        filter(flat - filter_dist < hex_lat & hex_lat < flat + filter_dist) %>%
+        filter(flong - filter_dist < hex_long & hex_long < flong + filter_dist)
+
+```
+
+Create a box filter
+```{r, echo = FALSE}
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "green") + geom_point(aes(x=longitude, y = latitude), colour = "red", data= centroids[1,]) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "grey", data = hex_grid, size = 0.75) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "orange", data = hex_grid, size = 0.75)
+```
+
+```{r}
+    grid <- grid %>%
+        rowwise %>%
+        mutate(
+        hex_lat_c = hex_lat - flat,
+        hex_long_c = hex_long - flong) %>%
+        mutate(hyp = ((hex_lat_c^2) + (hex_long_c^2))^(1/2))
+
+```
+
+Create circle filter
+
+```{r, echo = FALSE}
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "green") + geom_point(aes(x=longitude, y = latitude), colour = "red", data= centroids[1,]) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "grey", data = hex_grid, size = 0.75) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "orange", data = hex_grid, size = 0.75)
+```
+
+```{r}
+
+    # Filter for angle within circle
+    if ("focal_distance" %in% colnames(centroid1)) {
+
+        f_angle <- centroid1 %>%
+            mutate(atan = atan2(latitude-latitude1,longitude-longitude1),
+                angle = (atan*180/pi),
+                pangle = ifelse(angle<0, angle +360, angle)) %>% pull()
+
+        grid <- grid %>%
+            # create circle of radius: filter_dist
+            filter(hyp < filter_dist) %>%
+            mutate(
+                # geosphere takes a long time
+                angle = f_angle,
+                angle_plus = (angle + angle_width)%%360,
+                angle_minus = (angle - angle_width)%%360,
+                atan = atan2(hex_lat_c, hex_long_c),
+                hex_angle = (atan*180/pi),
+                hex_angle = ifelse(hex_angle<0, hex_angle +360, hex_angle))
+
+        if (grid$angle_minus[1] < grid$angle_plus[1]) {
+            grid <- grid %>%
+                # create slice of 60 degrees from centroid
+                filter(angle_minus < hex_angle & hex_angle < angle_plus)
+        }
+        else {
+            grid <- grid %>%
+                # create slice of 60 degrees from centroid
+                filter(hex_angle < angle_plus | angle_minus > hex_angle)
+        }
+
+    }
+
+```
+
+```{r}
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "green") + geom_point(aes(x=longitude, y = latitude), colour = "red", data= centroids[1,]) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "grey", data = hex_grid, size = 0.75) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "orange", data = hex_grid, size = 0.75)
+```
+
+```{r}
+
+# Choose first available point
+        cent <- centroid1 %>% dplyr::rename(focal_point = points, focal_dist = focal_distance, focal_angle = angle)
+
+        # Filter should give one hex point
+        hex <- hex_grid %>% 
+          ungroup %>% 
+          filter(hyp == min(hyp)) %>%
+          select(hex_long, hex_lat, hex_id = id)
+
+        #update grid to show this centroid as assigned
+        hex_grid[which(hex_grid$id == hex$hex_id),]$assigned <- TRUE
+
+        centroid_allocation <- bind_rows(centroid_allocation, dplyr::bind_cols(cent, hex)) %>% as.tibble()
+
+```
+
 Using the angle between each polygon centroid, and it's the closest focal point, the subset of points is filtered again.

### 2019-01-17 algorithm_radix.Rmd
Plot explanations of algorithm

--- 2019-01-08 algorithm_radix.Rmd
@@
 title: "An algorithm for a spatial mapping using a hexagon tilegram, with application to Australia disease maps"
-
 author:
@@
 fort_tas <- fortify_sfc(tas_lga, projstring = projstring)
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "green") + geom_point(aes(x=longitude, y = latitude),data= centroids)
+ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal()
 ```
@@
 hex_size <- (bbox$max[1] - bbox$min[1])/(bbox$max[2] - bbox$min[2]) / 10
+hex_size <- 0.2
 
@@
 ```{r}
-grid <- tibble::as.tibble(expand.grid(hex_long = seq(bbox$min[1] - buffer_dist,
+grid <- tibble::as_tibble(expand.grid(hex_long = seq(bbox$min[1] - buffer_dist,
     bbox$max[1] + buffer_dist,
@@
         hex_size)))
+```
+
+```{r, fig}
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
 ```
@@
     dplyr::mutate(assigned=FALSE)
+```
+
+```{r}
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
 ```
@@
 ```{r}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "green") + geom_point(aes(x=longitude, y = latitude), colour = "red", data= centroids) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "black", data = full_grid, size = 0.5) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "grey", data = grid, size = 0.75)
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = full_grid, size = 0.25) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75)
 ```
-
-<!--
-Grid point figure
--->
 
@@
 For each polygon centroid, only the hexagon grid points that have not yet been used can be considered.
+
+```{r}
+s_centroids <- centroids %>% arrange(focal_distance)
+
+s_centroids <- split(s_centroids, s_centroids[["focal_distance"]])
+
+# Set up allocation data frame
+centroid_allocation <- NULL
+```
+
 The filter distance parameter is used to subset possible grid points to only those surrounding the polygon centroid within the filter distance.
+
+```{r}
+# keep value to reset expanded distances
+expand_dist <- filter_dist
+```
+
+The following example considers one of the Local Government Areas. 
+These steps are repeated for each polygon.
+
+### Step 1: Filter the grid for unassigned hexagon points
+
+```{r}
+# filter for only the available hex grid points
+hex_grid <- grid %>% filter(!assigned)
+```
+
+### Step 2: Filter the grid points for those closest to the centroid
+```{r}
+# filter grid for avaiable points
+centroid1 <- centroids %>% head(1)
+
+flong <- centroid1$longitude
+flat <- centroid1$latitude
+
+hex_grid <- hex_grid %>% ungroup() %>%
+        filter(flat - filter_dist < hex_lat & hex_lat < flat + filter_dist) %>%
+        filter(flong - filter_dist < hex_long & hex_long < flong + filter_dist)
+
+```
+
+Create a box filter
+```{r, echo = FALSE}
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75)
+
+```
+
+Create circle filter
+```{r}
+    hex_grid <- hex_grid %>%
+        rowwise %>%
+        mutate(
+        hex_lat_c = hex_lat - flat,
+        hex_long_c = hex_long - flong) %>%
+        mutate(hyp = ((hex_lat_c^2) + (hex_long_c^2))^(1/2))
+
+        f_angle <- centroid1 %>%
+            mutate(atan = atan2(latitude-latitude1,longitude-longitude1),
+                angle = (atan*180/pi),
+                pangle = ifelse(angle<0, angle +360, angle)) %>% pull()
+
+        hex_grid <- hex_grid %>%
+            # create circle of radius: filter_dist
+            filter(hyp < filter_dist) %>%
+            mutate(
+                # geosphere takes a long time
+                angle = f_angle,
+                angle_plus = (angle + width)%%360,
+                angle_minus = (angle - width)%%360,
+                atan = atan2(hex_lat_c, hex_long_c),
+                hex_angle = (atan*180/pi),
+                hex_angle = ifelse(hex_angle<0, hex_angle +360, hex_angle))
+
+```
+
+```{r, echo = FALSE}
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75)
+```
+
+Filter for angle within circle, relates hexagon location to focal point, Hobart.
+
+```{r}
+# Filter for angle within circle
+
+        if (hex_grid$angle_minus[1] < hex_grid$angle_plus[1]) {
+            hex_grid <- hex_grid %>%
+                # create slice of 60 degrees from centroid
+                filter(angle_minus < hex_angle & hex_angle < angle_plus)
+        } else {
+            hex_grid <- hex_grid %>%
+                # create slice of 60 degrees from centroid
+                filter(hex_angle < angle_plus | angle_minus > hex_angle)
+        }
+
+```
+
+```{r}
+
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75)
+
+```
+
+```{r}
+
+# Choose first available point
+        cent <- centroid1 %>% dplyr::rename(focal_point = points, focal_dist = focal_distance, focal_angle = angle)
+
+        # Filter should give one hex point
+        hex <- hex_grid %>% 
+          ungroup %>% 
+          filter(hyp == min(hyp)) %>%
+          select(hex_long, hex_lat, hex_id = id)
+
+        #update grid to show this centroid as assigned
+        hex_grid[which(hex_grid$id == hex$hex_id),]$assigned <- TRUE
+
+        centroid_allocation <- bind_rows(centroid_allocation, dplyr::bind_cols(cent, hex)) %>% as_tibble()
+
+```
+
 Using the angle between each polygon centroid, and it's the closest focal point, the subset of points is filtered again.
 Of these possible points, only those within a specific amount of degrees plus and minus a specific angle range are kept. This angle begins at 30 degrees by default, and may increase if necessary.
-
-<!--
-figure of angle growing to show allocation of hexagons
--->
 
@@
 The allocation is returned and combined with the data relating to each polygon.
+```{r}
+hex_points_df <- centroid_allocation %>% 
+  group_by(LGA_CODE11) %>%
+  nest() %>%
+  mutate(hex_points = 
+      map(.x = data,.f = function(a) { 
+        fortify_hexagon(data = a, hex_size = hex_size)})) %>%
+  unnest(data) %>%
+  unnest(hex_points)
+```
 
-<!--
-Prose code:  Number each step, never break a loop over steps,
-use sub numbering for parts of each step, and
-include explanatory text.
-Literate code:  The algorithm is introduced gradually,
-intermingled with discussion of underlying ideas.
--->
+```{r}
+ggplot(hex_points_df) + 
+  geom_polygon(aes(x = hexv_long, y = hexv_lat, group = LGA_CODE11)) +
+  coord_equal() +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75)
+```
+
+```{r}
+allocation <- centroid_allocation
+hexmap_lga <- left_join(tas_lga, allocation)
+ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") +
+  theme_void() + coord_equal() +
+    geom_hex(aes(x = hex_long, y = hex_lat, fill = AREA_SQKM), data = hexmap_lga, 
+      position = "identity", stat = "identity")
+```
+
+```{r, eval = FALSE}
+hexmap_lga <- left_join(tas_lga, 
+  create_hexmap(shp = tas_lga, sf_id = "LGA_CODE11", buffer_dist = NULL, filter_dist = 10, hex_size = 0.2, export_shp = FALSE, focal_points = sugaRbag::capital_citie, verbose = TRUE)
+)
+```
 

### 2019-01-17 sandbox_animation.Rmd
Plot explanations of algorithm

---
title: "Untitled"
author: "Stephanie"
date: "15/01/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}

library(tidyverse)
library(sugaRbag)
```

```{r}

hexmap_allocation <- allocate(centroids = centroids,
  hex_grid = grid,
  hex_size = hex_size,
  filter_dist = filter_dist,
  width = width,
  focal_points = sugaRbag::capital_cities,
  verbose = TRUE,
  id = sf_id)

hex_points_df <- hexmap_allocation %>% 
  group_by(LGA_CODE11) %>%
  nest() %>%
  mutate(hex_points = 
      map(.x = data,.f = function(a) {
        fortify_hexagon(data = a, hex_size = hex_size)})) %>%
  unnest(data) %>%
  unnest(hex_points)

# hexagon data
hex_cents <- hex_points_df %>% dplyr::select(LGA_CODE11, starts_with("hex_"), hexv_id, hex_id) %>%
  gather(key = "hex", value = "location", starts_with("hex_"), -hexv_id, -hex_id, -LGA_CODE11) %>%
  separate(hex, into = c("point_type", "axis")) %>%
  spread(axis, location)

# variable data
areasq <- bind_cols(LGA_CODE11 = tas_lga$LGA_CODE11, 
  area = tas_lga$AREA_SQKM)

hex_verts <-  hex_points_df %>% dplyr::select(LGA_CODE11, starts_with("hexv_"), hexv_id, hex_id) %>%
  gather(key = "hexv", value = "location", starts_with("hexv_"), -hexv_id, -hexv_id, -LGA_CODE11) %>%
  separate(hexv, into = c("point_type", "axis")) %>%
  spread(axis, location) %>%
  mutate(group = LGA_CODE11,
    order = hexv_id) %>%
  left_join(areasq)

geo_verts <- fort_tas %>% dplyr::select(LGA_CODE11, long, lat, group, order, area = AREA_SQKM) %>% mutate(point_type = "polygon") %>% left_join(
  hex_verts %>% 
    dplyr::select(LGA_CODE11, hex_id))

hex_animate <- bind_rows(hex_verts, geo_verts)

library(ggplot2)
library(gganimate)

# Create static plot
ggplot(hex_animate) + 
  geom_polygon(aes(x = long, y = lat, group = LGA_CODE11))

# Create animated plot
hex <- ggplot(hex_animate) + 
  geom_polygon(aes(x = long, y = lat, group = group, fill = area, order = order)) + coord_equal() + 
  transition_states(states = point_type, transition_length = 1, state_length = 2) +
  ease_aes('quadratic-in')

animate(hex)

```

### SF ALTERNATIVE
```{r}

hex_points_polys <- sf::st_as_sf(hex_points_df, coords = c("hexv_long", "hexv_lat")) %>% 
  group_by(hex_id) %>% 
  summarize(do_union=FALSE) %>%
  sf::st_cast("POLYGON") %>%
  left_join(hex_points_df %>% group_by(LGA_CODE11) %>% top_n(1) %>%
      select(LGA_CODE11, hex_id, focal_dist)) %>% mutate(point_type = "hexagon")

# colnames(hex_points_polys)
#"hex_id"     "LGA_CODE11" "focal_dist" "point_type" "geometry"

sf_animate <- bind_rows(hex_points_polys, tas_lga %>% mutate(point_type = "geography"))

```

# Create animated plot sf_anim
```{r}
ggplot() +
  geom_sf(data = tas_lga) 
```

+
  transition_states(states = point_type, 
    transition_length = 1, state_length = 2) +
  ease_aes('quadratic-in')

animate(sf_anim)

### 2019-01-17 algorithm_radix.Rmd
Introduction draft

@@
     url: https://github.com/srkobakian
-    affiliation: Queensland University of Technology
+    affiliation: nswmania University of Technology
 date: "`r Sys.Date()`"
@@
 
-Representing the globe in 2D space has presented issues for many years. Methods have been established to visualise geographical space.
-We present a solution for alternate visualisations when the intention is to represent the spatial distribution.
+Spatial distrbutions have utilised alternative representations of geography for many years.
+In modern times with the ease of interactivity and animation, alternative representations have been popularised by online news sites.
+Applications are iincreasingly widespread, especially in the area of disease mapping.
 
@@
 
-- Spatial distributions are not well presented when areas differ in size.
-- We want to understand the distribution among population
-- We can benefit from making the focus the distribution, not the geography
+Spatial distributions of people and human related statistics are not well presented in geographic maps.
+Populations congregate around major cities and the lack of land available encourages vertical living.
+Government bodies define localities, attempting to evenly distribute the population into measureable areas.
+As the rural areas of Australia are often sparsely populated in comparison to their urban centres the square meterage of the geographic areas may vastly differ in size.
+
+Alternative mapping methods allow increased understanding of the spatial distribution of a variable amongst the population.
+Allowing the focus to be placed on the distribution of the statistics between the groups of areas, not the geography.
 
@@
 
-- Presenting spatial distributions
-- Extremely small areas are lost not easily compared at a high level
-- Choropleths; unequal space on the display, difficult to represent Australia
-- Cartograms; strong distortions misrepresent Australia
+Extremely small geographic areas are lost on large geographic maps, areas in Sydney or Melbourne are not easily compared at a high level.
+Cartograms allow an alternative view.
+Placingimportance on the statistic of interest, allowing unequal map space on the display to represent differences in the statistic.
+These maps rely on the statistic of interest to determine the layout, and often fail to preserve a recognisable view of Australia.
+Tile grams allow a better preservation of relationships.
+Decrease the emphasis on the amount of geograhic area considered to be interesting.
+Focus on the relationship between neighbours, in considering aggregated statistics of heterogeneous regions.
 
@@
 
-- Unusual population settlement and dispersion over the geographical space: Australia
-Dense south east, sparse central and west
+Australia and Canada present an application that contains an unusual population settlement and dispersion over the geographical space: 
+- Australia: Dense south east, sparse central and west
 
-- Applying alternative maps that allow for dense population areas when cities that are population dense are close together
+This provides an opportunity for a new class of
 
@@
 The algorithm operates on a set of polygons.
-There are parameters needed that may be provided, or will be automatically derived.
+There are parameters used in the process that may be provided, or will be automatically derived.
 All necessary functions are exported, with a main function `create_hexmap` used to step through automatically.
@@
 
-The `create_hexmap` functions requires several parameters. If not provided the information may be derived from the polygon set used.
+As the `create_hexmap` function requires several parameters, if they are not provided, the information will be derived from the polygon set used.
 
 **The following must be provided to `create_hexmap`:**
+```{r table_necessary}
+knitr::kable(tibble::tibble(parameter = c('shp', 
+  'shp_path',
+  'sf_id',
+  'focal_points'),
+  description = c('a shape file', 'character string location of shape file', 'name of a unique column that distinguishes areas',
+    'a data frame of reference locations when allocating hexagons, capital cities of Australia are provided as capital_cities'
+    )))
 
-The set of polygons to be made into a hexagon map:
-`shp: a shape file`
+```
 
-The location of a set of polygons to be made into a hexagon map:
-`shp_path: character string location of shape file`
-
-A column of unique names or id values for each area
-`sf_id: name of a unique column that distinguishes areas`
-
-A data frame of reference points to determine the order of allocation
-`focal_points a data frame of reference locations when allocating hexagons, capital cities of Australia are provided as capital_cities`
-
-```{r}
+```{r data}
 library(tidyverse)
@@
 
-**The following will be determined within `create_hexmap` if not provided, but must be created for the following example:**
+**The following will be determined within `create_hexmap` if not provided. They are created throughout the following example:**
 
-- `projstring	a string to indicate the projection and epsg`
-- `epsg	the four character string to indicate the CRS`
-- `buffer_dist: a float value for distance in degrees to extend beyond the - geometry provided`
-- `hex_size	a float value in degrees for the diameter of the hexagons`
-- `filter_dist amount of hexagons around centroid to consider for allocation`
-- `width the angle used to filter the grid points around a centroid`
-
-These parameters will be created when they are needed in the example:
+```{r}
+knitr::kable(tibble(parameter = c('projstring', 
+  'epsg', 'buffer_dist', 'hex_size',  'filter_dist', 'width'),
+  description = c('a string to indicate the projection and epsg', 'the four character string to indicate the CRS', 
+    'a float value for distance in degrees to extend beyond the - geometry provided',
+    'a float value in degrees for the diameter of the hexagons', 'amount of hexagons around centroid to consider for allocation',
+    'the angle used to filter the grid points around a centroid')))
+```
 
@@
 
-<!--
-needed later:
-
-- filter distance: *the amount of hexagons around each centroid to consider for allocation, by default this is 10 hexagons*
--->
-
-When utilising individual functions, we recommend the following approach:
+When utilising individual `sugaRbag` functions, we recommend the following approach:
 
@@
 
-The collection of polygons should be considered first.
+Begin with a set of polygons.
 There are several ways of providing the set of polygons.
-The following methods are available via the `read_shape` function.
+The following methods are available via the `read_shape` function. It utilises the `st_read` function is to create the sf object.
 
 - To utilise a shape file from a directory on your device, provide the file path for .shp file.
-- The `st_read` function is applied internally to create the sf object.
 - If the shape file is an .Rda file, it is loaded into the current environment.
 
-Empty geometries are removed from the sf object, and the remaining polygons are projected to the Australian standard.
+Empty geometries are removed from the sf object, and the remaining polygons are projected to the Australian standard using `projstring`.
 
@@
 # Read in shape information
-tas_shp <- read_shape(shp_path = shp_path)
+nsw_shp <- read_shape(shp_path = shp_path)
 
 # Convert to a simple features object
-tas_lga <- sf::st_as_sf(tas_shp)
+nsw_lga <- sf::st_as_sf(nsw_shp)
 
-# Select only desired LGA areas, those from Tasmania.
-tas_lga <- tas_shp %>% filter(STE_NAME11 == "Tasmania")
-tas_lga[[sf_id]] <- droplevels(as.factor(tas_lga[[sf_id]]))
+# Select only desired LGA areas, those from nswmania.
+nsw_lga <- nsw_shp %>% filter(STE_NAME11 == "New South Wales")
+nsw_lga[[sf_id]] <- droplevels(as.factor(nsw_lga[[sf_id]]))
 
-## Not necessary within `create_hexmap`:
+## Not necessary when using `create_hexmap`:
 ## Derive projection information
-crs_info <- sf::st_crs(tas_lga)
+crs_info <- sf::st_crs(nsw_lga)
 proj4string <- crs_info$proj4string
@@
 
-tas_lga <- tas_lga %>%
+nsw_lga <- nsw_lga %>%
     sf::st_transform(., crs = projstring)
@@
 ## Use the create_centroids function to find polygon centroids:
-centroids <- create_centroids(shp_sf = tas_lga, sf_id = sf_id, projstring = projstring, verbose = FALSE)
+centroids <- create_centroids(shp_sf = nsw_lga, sf_id = sf_id, projstring = projstring, verbose = FALSE)
 ```
 
-```{r, fig.cap="Tasmanian Local Government Areas and derived centroids."}
-fort_tas <- fortify_sfc(tas_lga, projstring = projstring)
+```{r, fig.cap="nswmania Local Government Areas and derived centroids."}
+fort_nsw <- fortify_sfc(nsw_lga, projstring = projstring)
 ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal()
+  geom_polygon(aes(x = long, y = lat, group = group), data = fort_nsw, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal()
 ```
@@
 ```{r}
-## Not necessary within `create_hexmap`:
+## Not necessary when using `create_hexmap`:
 ## create the bounding box from the set of polygon centroids:
@@
 
-hex_size <- (bbox$max[1] - bbox$min[1])/(bbox$max[2] - bbox$min[2]) / 10
-hex_size <- 0.2
+hex_size <- (bbox$max[1] - bbox$min[1])/(bbox$max[2] - bbox$min[2]) / 5
 
@@
 
-```{r, fig}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
+```{r}
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_nsw, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
@@
 ```{r}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_nsw, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
@@
 ```{r}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_nsw, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = full_grid, size = 0.25) +
@@
 ```{r}
-## Not necessary within `create_hexmap`:
+## Not necessary when using `create_hexmap`:
 ## Consider hexagon points up to a certain distance from centroid
@@
 ```{r, echo = FALSE}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_nsw, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
@@
 
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_nsw, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
@@
 
+```{r fullhexmap}
+lga_map <- create_hexmap(shp = nsw_lga, sf_id = "LGA_CODE11", buffer_dist = NULL, filter_dist = 10, export_shp = FALSE, focal_points = sugaRbag::capital_cities, projstring = projstring, verbose = TRUE)
+
+hexmap_lga <- left_join(nsw_lga, 
+  lga_map)
+
+```
+
 ```{r}
-allocation <- centroid_allocation
-hexmap_lga <- left_join(tas_lga, allocation)
 ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") +
+  geom_polygon(aes(x = long, y = lat, group = group), data = fort_nsw, fill = "grey", colour = "white") +
   theme_void() + coord_equal() +
@@
       position = "identity", stat = "identity")
-```
-
-```{r, eval = FALSE}
-hexmap_lga <- left_join(tas_lga, 
-  create_hexmap(shp = tas_lga, sf_id = "LGA_CODE11", buffer_dist = NULL, filter_dist = 10, hex_size = 0.2, export_shp = FALSE, focal_points = sugaRbag::capital_citie, verbose = TRUE)
-)
 ```
@@
 
-Examples of Melbourne, Tasmania, Australia
+Examples of Melbourne, nswmania, Australia
 At different levels, distance from original centroids, change in area
@@
 LGA of all Australia
-SA2 for Queensland
+SA2 for nswmania
 

### 2019-01-18 sandbox_animation_aus.Rmd
Australia and Tasmania Animations

---
title: "Australia"
author: "Stephanie"
date: "15/01/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r packages}
library(tidyverse)
library(sugaRbag)
```

```{r data}
shp_path <- "data/lga_2011.rda"
sf_id <- "LGA_CODE11"
focal_points <- sugaRbag::capital_cities

# Select only desired LGA areas, those from ausmania.
lga_2011[[sf_id]] <- droplevels(as.factor(lga_2011[[sf_id]]))

## Not necessary when using `create_hexmap`:
## Derive projection information
crs_info <- sf::st_crs(lga_2011)
proj4string <- crs_info$proj4string
epsg <- crs_info$epsg

## For UTM as per shape file
projstring <- paste0("+init=epsg:", epsg, " ", proj4string, collapse = "")
## if long lat is preferred to UTM, and not in proj4string:
projstring <- "+init=epsg:3112 +proj=longlat +lat_1=-18 +lat_2=-36 +lat_0=0 +lon_0=134 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +no_defs"

lga_2011 <- lga_2011 %>%
    sf::st_transform(., crs = projstring)

```

```{r}
# Change this for a more detailed map
fort_aus <- fortify_sfc(lga_2011, projstring = projstring, simplify = 0.2)
```

```{r}
hex_size <- 0.2

lga_map <- create_hexmap(shp = lga_2011, sf_id = "LGA_CODE11", buffer_dist = NULL, filter_dist = 10, hex_size = hex_size, export_shp = FALSE, focal_points = sugaRbag::capital_cities, projstring = projstring, verbose = TRUE)

hexmap_lga <- left_join(lga_2011, 
  lga_map)
```

```{r}

hex_points_df <- lga_map %>% 
  group_by(LGA_CODE11) %>%
  nest() %>%
  mutate(hex_points = 
      map(.x = data,.f = function(a) {
        fortify_hexagon(data = a, hex_size = hex_size)})) %>%
  unnest(data) %>% 
  unnest(hex_points) %>%
  dplyr::rename(long = hexv_long,
    lat = hexv_lat)

# variable data
areasq <- bind_cols(LGA_CODE11 = lga_2011$LGA_CODE11, 
  area = lga_2011$AREA_SQKM)

hex_verts <-  hex_points_df %>%
  left_join(areasq) %>% 
  mutate(point_type = "hex") %>% 
  left_join(fort_aus %>% 
      dplyr::select(LGA_CODE11, group) %>%
      mutate(group = group))

geo_verts <- fort_aus %>% dplyr::select(LGA_CODE11, long, lat, group, order, area = AREA_SQKM) %>% 
  mutate(point_type = "polygon") %>%
  left_join(hex_verts %>% 
    dplyr::select(LGA_CODE11, hex_id) %>% distinct())

hex_animate <- full_join(hex_verts, geo_verts)
```

```{r}
library(ggplot2)
library(gganimate)

# Create static plot
ggplot(hex_animate) + 
  geom_polygon(aes(x = long, y = lat, group = group)) + facet_wrap(~point_type) + coord_equal()
ggplot() +geom_sf(data = lga_2011)
```

```{r}
# Create animated plot
hex <- ggplot(hex_animate, aes(group = LGA_CODE11)) + 
  geom_polygon(aes(x = long, y = lat, group = group, fill = area)) + theme_void() + coord_equal() + 
  transition_states(states = point_type, 
    transition_length = 1, state_length = 2) +
  ease_aes('quadratic-in')

anim <- animate(hex)
anim
```

### 2019-01-18 sandbox_animation_tas.Rmd
Australia and Tasmania Animations

--- 2019-01-18 sandbox_animation_aus.Rmd
@@
 ---
-title: "Australia"
+title: "Untitled"
 author: "Stephanie"
@@
 
-# Select only desired LGA areas, those from ausmania.
-lga_2011[[sf_id]] <- droplevels(as.factor(lga_2011[[sf_id]]))
+# Select only desired LGA areas, those from tasmania.
+tas_lga <- lga_2011 %>% filter(STE_NAME11 == "Tasmania")
+tas_lga[[sf_id]] <- droplevels(as.factor(tas_lga[[sf_id]]))
 
@@
 ## Derive projection information
-crs_info <- sf::st_crs(lga_2011)
+crs_info <- sf::st_crs(tas_lga)
 proj4string <- crs_info$proj4string
@@
 
-lga_2011 <- lga_2011 %>%
+tas_lga <- tas_lga %>%
     sf::st_transform(., crs = projstring)
 
-```
+## Use the create_centroids function to find polygon centroids:
+#centroids <- create_centroids(shp_sf = tas_lga, sf_id = sf_id, projstring = projstring, verbose = FALSE)
 
-```{r}
 # Change this for a more detailed map
-fort_aus <- fortify_sfc(lga_2011, projstring = projstring, simplify = 0.2)
+fort_tas <- fortify_sfc(tas_lga, projstring = projstring, simplify = 1)
 ```
@@
 
-lga_map <- create_hexmap(shp = lga_2011, sf_id = "LGA_CODE11", buffer_dist = NULL, filter_dist = 10, hex_size = hex_size, export_shp = FALSE, focal_points = sugaRbag::capital_cities, projstring = projstring, verbose = TRUE)
+lga_map <- create_hexmap(shp = tas_lga, sf_id = "LGA_CODE11", buffer_dist = NULL, filter_dist = 10, hex_size = hex_size, export_shp = FALSE, focal_points = sugaRbag::capital_cities, projstring = projstring, verbose = TRUE)
 
-hexmap_lga <- left_join(lga_2011, 
+hexmap_lga <- left_join(tas_lga, 
   lga_map)
@@
 # variable data
-areasq <- bind_cols(LGA_CODE11 = lga_2011$LGA_CODE11, 
-  area = lga_2011$AREA_SQKM)
+areasq <- bind_cols(LGA_CODE11 = tas_lga$LGA_CODE11, 
+  area = tas_lga$AREA_SQKM)
 
@@
   mutate(point_type = "hex") %>% 
-  left_join(fort_aus %>% 
+  left_join(fort_tas %>% 
       dplyr::select(LGA_CODE11, group) %>%
@@
 
-geo_verts <- fort_aus %>% dplyr::select(LGA_CODE11, long, lat, group, order, area = AREA_SQKM) %>% 
+geo_verts <- fort_tas %>% dplyr::select(LGA_CODE11, long, lat, group, order, area = AREA_SQKM) %>% 
   mutate(point_type = "polygon") %>%
@@
   geom_polygon(aes(x = long, y = lat, group = group)) + facet_wrap(~point_type) + coord_equal()
-ggplot() +geom_sf(data = lga_2011)
+ggplot() +geom_sf(data = tas_lga)
 ```

### 2019-01-18 algorithm_radix.Rmd
Expanded introduction

@@
     url: https://github.com/srkobakian
-    affiliation: nswmania University of Technology
+    affiliation: Queensland University of Technology
 date: "`r Sys.Date()`"
@@
 Spatial distrbutions have utilised alternative representations of geography for many years.
-In modern times with the ease of interactivity and animation, alternative representations have been popularised by online news sites.
-Applications are iincreasingly widespread, especially in the area of disease mapping.
+In modern times with the ease of interactivity and animation, alternative representations have been popularised by online news sites, with a focus on public consumption.
+Applications are increasingly widespread, especially in the area of disease mapping, election results and .
 
@@
 - Australia: Dense south east, sparse central and west
-
-This provides an opportunity for a new class of
 
@@
 ```{r}
-width <- 30 # arbitrary angle width
+width <- 15 # arbitrary angle width
 ```
@@
 centroids <- create_centroids(shp_sf = nsw_lga, sf_id = sf_id, projstring = projstring, verbose = FALSE)
+
+fort_nsw <- fortify_sfc(nsw_lga, projstring = projstring)
 ```

### 2019-01-18 sandbox_animation_aus.Rmd
level 5

@@
 # Change this for a more detailed map
-fort_aus <- fortify_sfc(lga_2011, projstring = projstring, simplify = 0.2)
+fort_aus <- fortify_sfc(lga_2011, projstring = projstring, simplify = 0.6)
 ```
@@
 ```{r}
-hex_size <- 0.2
+hex_size <- 0.5
 
 lga_map <- create_hexmap(shp = lga_2011, sf_id = "LGA_CODE11", buffer_dist = NULL, filter_dist = 10, hex_size = hex_size, export_shp = FALSE, focal_points = sugaRbag::capital_cities, projstring = projstring, verbose = TRUE)
+
+lga_map5 <- lga_map
+save(lga_map5, file = "lga_map3")
 
@@
 anim
+anim_save(filename = paste0("hex_aus_anim", hex_size, ".gif"))
 ```

### 2019-01-30 algorithm_radix.Rmd
Don't evaluate read_shape function call

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE, cache = FALSE)
 ```
@@
   'focal_points'),
-  description = c('a shape file', 'character string location of shape file', 'name of a unique column that distinguishes areas',
+  description = c('an Rdata object containing the polygon information', 'character string location of the shape file that contains the polygon information', 'name of a unique column that distinguishes areas',
     'a data frame of reference locations when allocating hexagons, capital cities of Australia are provided as capital_cities'
@@
 
+```{r libraries}
+library(tidyverse)
+# To install:
+# devtools::install_github("srkobakian/sugaRbag")
+library(sugaRbag)
+```
+
+The polygon set of Local Government Areas in Australia in 2011 is stored in the sugaRbag package as `lga_2011`.
+
 ```{r data}
-library(tidyverse)
-library(sugaRbag)
-
-shp_path <- "data/lga_2011.rda"
 sf_id <- "LGA_CODE11"
@@
 
-```{r}
-width <- 15 # arbitrary angle width
-```
-
 When utilising individual `sugaRbag` functions, we recommend the following approach:
@@
 
-- To utilise a shape file from a directory on your device, provide the file path for .shp file.
 - If the shape file is an .Rda file, it is loaded into the current environment.
+- To utilise a custom shape file from a directory on your device, provide the file path for .shp file.
+
+```{r, eval = FALSE}
+# Read in shape information
+shp <- read_shape(shp_path = shp_path)
+
+# Convert to a simple features object
+shp_sf <- sf::st_as_sf(shp)
+```
 
@@
 
-We will use the Local Government Areas of Hobart as an example:
+We will use the Local Government Areas of Australia in the `lga_2011` data set, and take only those from New South Wales as an example:
 
 ```{r}
-# Read in shape information
-nsw_shp <- read_shape(shp_path = shp_path)
+shp_sf <- sugaRbag::lga_2011
 
-# Convert to a simple features object
-nsw_lga <- sf::st_as_sf(nsw_shp)
+nsw_lga <- shp_sf %>% dplyr::filter(STE_NAME11 == "New South Wales")
+# Select only desired LGA areas, those from nsw.
+nsw_lga[[sf_id]] <- droplevels(as.factor(nsw_lga[[sf_id]]))
+```
 
-# Select only desired LGA areas, those from nswmania.
-nsw_lga <- nsw_shp %>% filter(STE_NAME11 == "New South Wales")
-nsw_lga[[sf_id]] <- droplevels(as.factor(nsw_lga[[sf_id]]))
-
+```{r project}
 ## Not necessary when using `create_hexmap`:
@@
 
-nsw_lga <- nsw_lga %>%
-    sf::st_transform(., crs = projstring)
+nsw_lga <- sf::st_transform(nsw_lga, crs = projstring)
+```
 
+```{r area_variable}
+nsw_lga <- nsw_lga %>% mutate(logarea = log(AREA_SQKM))
+```
+
+```{r centroids}
 ## Use the create_centroids function to find polygon centroids:
 centroids <- create_centroids(shp_sf = nsw_lga, sf_id = sf_id, projstring = projstring, verbose = FALSE)
+
+centroids$logarea <- nsw_lga$logarea
 
@@
 
-```{r, fig.cap="nswmania Local Government Areas and derived centroids."}
+```{r, fig.cap="NSW Local Government Areas and derived centroids."}
 fort_nsw <- fortify_sfc(nsw_lga, projstring = projstring)
-ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = group), data = fort_nsw, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal()
+
+end_cents <- ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = group), data = fort_nsw, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude, colour = logarea), data= centroids) + theme_void() + coord_equal()
+end_cents
 ```
@@
 
-```{r}
+```{r bbox}
 ## Not necessary when using `create_hexmap`:
@@
 
-```{r}
+```{r grid}
 grid <- tibble::as_tibble(expand.grid(hex_long = seq(bbox$min[1] - buffer_dist,
@@
 
-```{r}
+```{r plot_grid}
 ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_nsw, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
@@
 
-```{r}
+```{r shift}
 # Find every second latitude
@@
 
-```{r}
+```{r plot_shift}
 ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_nsw, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a") + theme_void() + coord_equal() +
@@
 
-```{r}
+```{r grid_id}
 full_grid <- grid %>%
@@
 
-```{r}
+```{r buffer}
 grid <- create_buffer(centroids, full_grid, hex_size, buffer_dist)
@@
 ### Step 3: Filtering the grid
+
 Only the grid points between the rolling average of the minimum and maximum centroid values are kept, for each row and column of the grid.
 
-```{r}
+```{r plot_buffer}
 ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_nsw, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
@@
 
-```{r}
+```{r split_centroids}
 # Split the centroid data set
@@
 
-```{r}
+```{r f_dist}
 ## Not necessary when using `create_hexmap`:
@@
         filter_dist = filter_dist,
-        width = width,
+        width = 15,
         focal_points = focal_points,
@@
 
-```{r}
+```{r arrange}
 s_centroids <- centroids %>% arrange(focal_distance)
@@
 
-```{r}
+```{r orig_dist}
 # keep value to reset expanded distances
@@
 
-```{r}
+Keep only the available hexagon points, this will prevent multiple areas being allocated to the same hexagon.
+
+```{r available_points}
 # filter for only the available hex grid points
@@
 ### Step 2: Filter the grid points for those closest to the centroid
-```{r}
+
+This will allow only the closest points, that are not assigned, to be considered.
+
+```{r close_points}
 # filter grid for avaiable points
@@
 Create a box filter
+
 ```{r, echo = FALSE}
@@
 Create circle filter
+
 ```{r}
@@
 
-Filter for angle within circle, relates hexagon location to focal point, Hobart.
+Filter for angle within circle, relates hexagon location to focal point, Sydney.
 
@@
 The allocation is returned and combined with the data relating to each polygon.
+
 ```{r}
@@
 ```{r}
-ggplot() + 
+end_hex <- ggplot() + 
   geom_polygon(aes(x = long, y = lat, group = group), data = fort_nsw, fill = "grey", colour = "white") +
@@
       position = "identity", stat = "identity")
+
+gridExtra::grid.arrange(end_hex, end_cents)
 ```
@@
 
-Examples of Melbourne, nswmania, Australia
+Examples of Melbourne, nsw, Australia
 At different levels, distance from original centroids, change in area
@@
 LGA of all Australia
-SA2 for nswmania
+SA2 for nsw
 

### 2019-02-21 algorithm_radix.Rmd
included buffer code

@@
 library(tidyverse)
-# To install:
+# To install sugaRbag:
 # devtools::install_github("srkobakian/sugaRbag")
@@
 
-The polygon set of Local Government Areas in Australia in 2011 is stored in the sugaRbag package as `lga_2011`.
+The polygon set of Local Government Areas in Australia in 2011 is stored in the sugaRbag package data as `tas_sa2`. To create this object:
+
+```
+# Download resource 
+# link to folder containing .shp file on sugaRbag site.
+
+aus_sa2 <- read_shape("file location")
+
+filter for Tasmanian areas
+
+tas_sa2 <- filter(aus_sa2, aus_sa2$STE_NAME11 == "Tasmania)
+```
+
+A column of the data set must be used as a unique identifier of areas.
 
 ```{r data}
-sf_id <- "LGA_CODE11"
+sf_id <- "SA2_5DIG16"
 focal_points <- sugaRbag::capital_cities
@@
 
-```{r, eval = FALSE}
+<!--
+```
 # Read in shape information
 shp <- read_shape(shp_path = shp_path)
-
-# Convert to a simple features object
-shp_sf <- sf::st_as_sf(shp)
 ```
+-->
 
@@
 
-We will use the Local Government Areas of Australia in the `lga_2011` data set, and take only those from New South Wales as an example:
+We will use the Statical Areas (Level 2) of Australia, provided by Australian Bureau of Statistics. With only those from Tasmania as an example:
 
 ```{r}
-shp_sf <- sugaRbag::lga_2011
+# Convert to a simple features object
+tas_sa2 <- sf::st_as_sf(tas_sa2)
 
-nsw_lga <- shp_sf %>% dplyr::filter(STE_NAME11 == "New South Wales")
-# Select only desired LGA areas, those from nsw.
-nsw_lga[[sf_id]] <- droplevels(as.factor(nsw_lga[[sf_id]]))
+# Select only desired LGA areas, those from tas.
+tas_sa2[[sf_id]] <- droplevels(as.factor(tas_sa2[[sf_id]]))
+
+fort_tas <- fortify_sfc(tas_sa2)
 ```
 
-```{r project}
-## Not necessary when using `create_hexmap`:
-## Derive projection information
-crs_info <- sf::st_crs(nsw_lga)
-proj4string <- crs_info$proj4string
-epsg <- crs_info$epsg
-
-## For UTM as per shape file
-projstring <- paste0("+init=epsg:", epsg, " ", proj4string, collapse = "")
-## if long lat is preferred to UTM, and not in proj4string:
-projstring <- "+init=epsg:3112 +proj=longlat +lat_1=-18 +lat_2=-36 +lat_0=0 +lon_0=134 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +no_defs"
-
-nsw_lga <- sf::st_transform(nsw_lga, crs = projstring)
-```
-
-```{r area_variable}
-nsw_lga <- nsw_lga %>% mutate(logarea = log(AREA_SQKM))
+```{r}
+# Include area variable
+area_var <- fort_tas %>% 
+  distinct(SA2_5DIG16, .keep_all = TRUE) %>% 
+  select(SA2_5DIG16, AREASQKM16)
 ```
@@
 ## Use the create_centroids function to find polygon centroids:
-centroids <- create_centroids(shp_sf = nsw_lga, sf_id = sf_id, projstring = projstring, verbose = FALSE)
-
-centroids$logarea <- nsw_lga$logarea
-
-fort_nsw <- fortify_sfc(nsw_lga, projstring = projstring)
+centroids <- create_centroids(shp_sf = tas_sa2, sf_id = sf_id) %>%
+  left_join(., select(area_var, SA2_5DIG16, AREASQKM16), by = "SA2_5DIG16")
 ```
 
-```{r, fig.cap="NSW Local Government Areas and derived centroids."}
-fort_nsw <- fortify_sfc(nsw_lga, projstring = projstring)
+```{r, fig.cap="tas Local Government Areas and derived centroids."}
+end_cents <- ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude, colour = log(AREASQKM16)), data= centroids) + theme_void() + coord_equal()
+end_cents
 
-end_cents <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = group), data = fort_nsw, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude, colour = logarea), data= centroids) + theme_void() + coord_equal()
-end_cents
+#ggplot() + geom_histogram(aes(x = log(AREASQKM16), fill = log(AREASQKM16)), data= centroids, bins = 20) 
 ```
@@
 ```{r plot_grid}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_nsw, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
@@
 ```{r plot_shift}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_nsw, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
@@
 ```{r grid_id}
-full_grid <- grid %>%
+full_grid <- grid <- grid %>%
     mutate(hex_long_int = dense_rank(hex_long)-1,
@@
 To filter the grid for appropriate hexagons for allocation,
-the `create_buffer` function is used.
+the `create_buffer` function is called from `create_grid`.
 
-```{r buffer}
-grid <- create_buffer(centroids, full_grid, hex_size, buffer_dist)
+It finds the amount of columns and rows needed to capture the set of centroids.
+
+```{r}
+nlong <- length(unique(grid$hex_long))
+nlat <- length(unique(grid$hex_lat))
+
+centroids <- centroids %>%
+  mutate(long_int = round((longitude-min(grid$hex_long))/(max(grid$hex_long)-min(grid$hex_long))*nlong, 0),
+          lat_int = round((latitude-min(grid$hex_lat))/(max(grid$hex_lat)-min(grid$hex_lat))*nlat, 0))
 ```
@@
 
+```{r echo = FALSE}
+# Amount of lats and longs in each group
+lat_size = round(nlat/20,0)
+long_size = round(nlong/20,0)
+```
+
 The first rolling window function finds the minimum and maximum centroid values for the groups of longitude columns and the groups of latitude rows.
+The specific rows and columns in the rolling windows are defined.
+
+```{r echo = FALSE}
+ # make a list of groups, manual sliding windows
+    nlat_list <- purrr::map2(seq(1:nlat), lat_size + seq(1:nlat), c)
+    nlong_list <- purrr::map2(seq(1:nlong), long_size + seq(1:nlong), c)
+
+    lat_window <- function(x, cents = centroids, maximum = nlat){
+        max_int = min(x[2],maximum)
+
+        cents_in <- filter(cents, between(lat_int, x[1], max_int))
+        return(cents_in)
+    }
+
+    long_window <- function(x, cents = centroids, maximum = nlong){
+        max_int = x[2]
+        while (max_int > maximum){
+            max_int = max_int - 1
+        }
+
+        cents_in <- filter(cents, between(long_int, x[1], max_int))
+        return(cents_in)
+    }
+
+    # LATITUDE ROWS FILTER
+    # amount of latitude in sliding window
+    lat_windows <- purrr::map(.x = nlat_list, .f = lat_window)
+
+    # find the min and max longitude for each latitude
+    range_rows <- purrr::map_dfr(.x = lat_windows,
+        .f = function(x) {x %>%
+                dplyr::summarise(
+                    long_min = ifelse(purrr::is_empty(long_int), NA, min(x$long_int)),
+                    long_max = ifelse(purrr::is_empty(long_int), NA, max(x$long_int))
+                )}
+    )
+```
 
 The second rolling window function finds the average of the rolling minimum and rolling maximum centroid values, for the longitude columns and latitude rows.
+
+```{r echo = FALSE}
+ # smooth the minimums
+    av_range_rows <- purrr::map_dfr(.x = nlat_list, .f = function(x, rows = range_rows) {
+        rows[x[1]:min(x[2], NROW(rows)),] %>%
+            dplyr::summarise(mean_long_min = mean(long_min, na.rm=T), mean_long_max = mean(long_max, na.rm=T))
+    }) %>%
+        bind_cols(lat_id = c(seq(1:nlat) +lat_size), .)
+
+    # LONGITUDE COLS FILTER
+    long_windows <- purrr::map(.x = nlong_list, .f = long_window, centroids, nlong)
+
+    # find the min and max longitude for each latitude
+    range_cols <- purrr::map_dfr(.x = long_windows, .f = function(x) { x %>%
+            dplyr::summarise(
+                lat_min = ifelse(purrr::is_empty(lat_int), NA, min(x$lat_int)),
+                lat_max = ifelse(purrr::is_empty(lat_int), NA, max(x$lat_int))
+            )}
+    )
+
+    # smooth the minimums
+    av_range_cols <- purrr::map_dfr(.x = nlong_list, .f = function(x, cols = range_cols) {
+        cols[x[1]:min(x[2], NROW(cols)),] %>%
+            dplyr::summarise(mean_lat_min = mean(lat_min, na.rm=T), mean_lat_max = mean(lat_max, na.rm=T))
+    }) %>%
+        bind_cols(long_id = c(seq(1:nlong) + round(long_size/2)), .)
+
+```
 
@@
 
+```{r echo = FALSE}
+    # APPLY A BUFFER
+    # change buffer to amount of hexagons (ints) either side
+    hex_buffer <- floor(buffer_dist/hex_size)
+
+    grid <- grid %>%
+        left_join(., av_range_rows, by = c("hex_lat_int" = "lat_id")) %>%
+        left_join(., av_range_cols, by = c("hex_long_int" = "long_id")) %>%
+        rowwise() %>%
+        mutate(long_buffer = ifelse(between(hex_long_int,mean_long_min - hex_buffer,
+            mean_long_max + hex_buffer), "in", "out")) %>%
+        mutate(lat_buffer = ifelse(between(hex_lat_int,mean_lat_min - hex_buffer,
+            mean_lat_max + hex_buffer), "in", "out")) %>%
+        filter(lat_buffer =="in" | long_buffer == "in")
+
+```
+
 ```{r plot_buffer}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_nsw, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = full_grid, size = 0.25) +
@@
 
+```{r}
+width = 15
+```
+
 ```{r, eval = FALSE}
@@
         filter_dist = filter_dist,
-        width = 15,
+        width = width,
         focal_points = focal_points,
@@
 ```{r, echo = FALSE}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_nsw, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
@@
 
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_nsw, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
@@
 hex_points_df <- centroid_allocation %>% 
-  group_by(LGA_CODE11) %>%
+  group_by(SA2_CODE11) %>%
   nest() %>%
@@
 ggplot(hex_points_df) + 
-  geom_polygon(aes(x = hexv_long, y = hexv_lat, group = LGA_CODE11)) +
+  geom_polygon(aes(x = hexv_long, y = hexv_lat, group = SA2_CODE11)) +
   coord_equal() +
@@
 ```{r fullhexmap}
-lga_map <- create_hexmap(shp = nsw_lga, sf_id = "LGA_CODE11", buffer_dist = NULL, filter_dist = 10, export_shp = FALSE, focal_points = sugaRbag::capital_cities, projstring = projstring, verbose = TRUE)
+lga_map <- create_hexmap(shp = tas_sa2, sf_id = "SA2_CODE11", buffer_dist = NULL, filter_dist = 10, export_shp = FALSE, focal_points = sugaRbag::capital_cities, projstring = projstring, verbose = TRUE)
 
-hexmap_lga <- left_join(nsw_lga, 
+hexmap_lga <- left_join(tas_sa2, 
   lga_map)
@@
 end_hex <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = group), data = fort_nsw, fill = "grey", colour = "white") +
+  geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") +
   theme_void() + coord_equal() +
@@
 
-Examples of Melbourne, nsw, Australia
+Examples of Melbourne, tas, Australia
 At different levels, distance from original centroids, change in area
@@
 LGA of all Australia
-SA2 for nsw
+SA2 for tas
 

### 2019-02-21 algorithm_radix.Rmd
included buffer code
Replace column name for 2016 data

@@
 hex_points_df <- centroid_allocation %>% 
-  group_by(SA2_CODE11) %>%
+  group_by(SA2_5DIG16) %>%
   nest() %>%
@@
 ggplot(hex_points_df) + 
-  geom_polygon(aes(x = hexv_long, y = hexv_lat, group = SA2_CODE11)) +
+  geom_polygon(aes(x = hexv_long, y = hexv_lat, group = SA2_5DIG16)) +
   coord_equal() +
@@
 ```{r fullhexmap}
-lga_map <- create_hexmap(shp = tas_sa2, sf_id = "SA2_CODE11", buffer_dist = NULL, filter_dist = 10, export_shp = FALSE, focal_points = sugaRbag::capital_cities, projstring = projstring, verbose = TRUE)
+lga_map <- create_hexmap(shp = tas_sa2, sf_id = "SA2_5DIG16", buffer_dist = NULL, filter_dist = 10, export_shp = FALSE, focal_points = sugaRbag::capital_cities, projstring = projstring, verbose = TRUE)
 

### 2019-02-21 algorithm_radix.Rmd
Need to include data in centroids for plotting end_cents

@@
 
-# Select only desired LGA areas, those from tas.
+# Select only desired SA2 areas, those from tas.
 tas_sa2[[sf_id]] <- droplevels(as.factor(tas_sa2[[sf_id]]))
@@
 end_cents <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude, colour = log(AREASQKM16)), data= centroids) + theme_void() + coord_equal()
+  geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids) + theme_void() + coord_equal()
 end_cents
@@
 hex_points_df <- centroid_allocation %>% 
-  group_by(SA2_5DIG16) %>%
-  nest() %>%
+  group_nest(SA2_5DIG16) %>%
   mutate(hex_points = 
@@
 ```{r fullhexmap}
-lga_map <- create_hexmap(shp = tas_sa2, sf_id = "SA2_5DIG16", buffer_dist = NULL, filter_dist = 10, export_shp = FALSE, focal_points = sugaRbag::capital_cities, projstring = projstring, verbose = TRUE)
-
-hexmap_lga <- left_join(tas_sa2, 
-  lga_map)
-
+# Create centroids set
+centroids <- create_centroids(tas_sa2, "SA2_5DIG16")
+# Create hexagon location grid
+grid <- create_grid(centroids = centroids, hex_size = 0.1, buffer_dist = 0.1)
+# Allocate polygon centroids to hexagon grid points
+hex_allocated <- allocate(centroids = centroids,
+hex_grid = grid,
+hex_size = 0.1, # same size used in create_grid
+filter_dist = 0.25,
+focal_points = sugaRbag::capital_cities,
+width = 30,
+id = "SA2_5DIG16", verbose = TRUE) # same column used in create_centroids
 ```
@@
 ```{r}
-end_hex <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") +
-  theme_void() + coord_equal() +
-    geom_hex(aes(x = hex_long, y = hex_lat, fill = AREA_SQKM), data = hexmap_lga, 
-      position = "identity", stat = "identity")
+h1 <- hex_allocated %>%
+  dplyr::group_nest(SA2_5DIG16) %>%
+                mutate(hex = purrr::map(data, fortify_hexagon, hex_size = 0.1)) %>%
+                unnest(data) %>% 
+  unnest(hex) %>% left_join(., tas_sa2)
+
+p1 <- fortify_sfc(tas_sa2)
+
+ggplot(mapping = aes(fill = SA4_NAME16)) +
+  geom_polygon(data = p1, aes(x=long, lat, group = group), alpha = 0.1) +
+  geom_polygon(data = h1, aes(x=hexv_long, hexv_lat, group = SA2_5DIG16))
 

### 2019-03-04 algorithm_radix.Rmd
tas lga data set to play

--- 2019-02-21 algorithm_radix.Rmd
@@
   'sf_id',
-  'focal_points'),
+  'capital_cities'),
   description = c('an Rdata object containing the polygon information', 'character string location of the shape file that contains the polygon information', 'name of a unique column that distinguishes areas',
@@
 library(tidyverse)
-# To install sugaRbag:
-# devtools::install_github("srkobakian/sugaRbag")
-library(sugaRbag)
+# To install sugarbag:
+# devtools::install_github("srkobakian/sugarbag")
+library(sugarbag)
 ```
 
-The polygon set of Local Government Areas in Australia in 2011 is stored in the sugaRbag package data as `tas_sa2`. To create this object:
+The polygon set of Local Government Areas in Australia in 2016 is stored in the sugarbag package data as `tas_lga`. To create this object:
 
@@
 # Download resource 
-# link to folder containing .shp file on sugaRbag site.
+# link to folder containing .shp file on sugarbag site.
 
@@
 
-filter for Tasmanian areas
-
-tas_sa2 <- filter(aus_sa2, aus_sa2$STE_NAME11 == "Tasmania)
 ```
@@
 ```{r data}
-sf_id <- "SA2_5DIG16"
-focal_points <- sugaRbag::capital_cities
+sf_id <- "LGA_CODE16"
+data(capital_cities)
 ```
@@
 knitr::kable(tibble(parameter = c('projstring', 
-  'epsg', 'buffer_dist', 'hex_size',  'filter_dist', 'width'),
+  'epsg', 'buffer_dist', 'hex_size',  'hex_filter', 'width'),
   description = c('a string to indicate the projection and epsg', 'the four character string to indicate the CRS', 
@@
 
-When utilising individual `sugaRbag` functions, we recommend the following approach:
+When utilising individual `sugarbag` functions, we recommend the following approach:
 
@@
 
-We will use the Statical Areas (Level 2) of Australia, provided by Australian Bureau of Statistics. With only those from Tasmania as an example:
+We will use the Statical Areas (Level 2) of Australia, provided by Australian Bureau of Statistics.
 
 ```{r}
+load("data/tas_lga.rda")
+
 # Convert to a simple features object
-tas_sa2 <- sf::st_as_sf(tas_sa2)
+tas_lga <- sf::st_as_sf(tas_lga)
 
-# Select only desired LGA areas, those from tas.
-tas_sa2[[sf_id]] <- droplevels(as.factor(tas_sa2[[sf_id]]))
+# Select only desired LGA areas.
+tas_lga[[sf_id]] <- droplevels(as.factor(tas_lga[[sf_id]]))
 
-fort_tas <- fortify_sfc(tas_sa2)
+fort_lga <- fortify_sfc(tas_lga)
 ```
@@
 # Include area variable
-area_var <- fort_tas %>% 
-  distinct(SA2_5DIG16, .keep_all = TRUE) %>% 
-  select(SA2_5DIG16, AREASQKM16)
+area_var <- fort_lga %>% 
+  distinct(LGA_CODE16, .keep_all = TRUE) %>% 
+  select(LGA_CODE16, AREASQKM16)
 ```
@@
 ## Use the create_centroids function to find polygon centroids:
-centroids <- create_centroids(shp_sf = tas_sa2, sf_id = sf_id) %>%
-  left_join(., select(area_var, SA2_5DIG16, AREASQKM16), by = "SA2_5DIG16")
+centroids <- create_centroids(shp_sf = tas_lga, sf_id = sf_id) %>%
+  left_join(., select(area_var, LGA_CODE16, AREASQKM16), by = "LGA_CODE16")
 ```
 
-```{r, fig.cap="tas Local Government Areas and derived centroids."}
+```{r, fig.cap="lga Local Government Areas and derived centroids."}
 end_cents <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude, colour = log(AREASQKM16)), data= centroids) + theme_void() + coord_equal()
+  geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids) + theme_void() + coord_equal()
 end_cents
@@
 ```{r plot_grid}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
@@
 ```{r plot_shift}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
@@
 ```{r plot_buffer}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = full_grid, size = 0.25) +
@@
   nest(longitude, latitude) %>% 
-  mutate(closest = map(data, closest_focal_point, focal_points = focal_points)) %>% 
+  mutate(closest = map(data, closest_focal_point, focal_points = capital_cities)) %>% 
   unnest(data, closest) %>% 
@@
 
-filter_dist <- (hex_size)*10
+hex_filter <- (hex_size)*10
 ```
@@
         hex_size = hex_size,
-        filter_dist = filter_dist,
+        hex_filter = hex_filter,
         width = width,
-        focal_points = focal_points,
+        capital_cities = capital_cities,
         verbose = TRUE,
@@
 # keep value to reset expanded distances
-expand_dist <- filter_dist
+expand_dist <- hex_filter
 ```
@@
 hex_grid <- hex_grid %>% ungroup() %>%
-        filter(flat - filter_dist < hex_lat & hex_lat < flat + filter_dist) %>%
-        filter(flong - filter_dist < hex_long & hex_long < flong + filter_dist)
+        filter(flat - hex_filter < hex_lat & hex_lat < flat + hex_filter) %>%
+        filter(flong - hex_filter < hex_long & hex_long < flong + hex_filter)
 
@@
 ```{r, echo = FALSE}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
@@
         hex_grid <- hex_grid %>%
-            # create circle of radius: filter_dist
-            filter(hyp < filter_dist) %>%
+            # create circle of radius: hex_filter
+            filter(hyp < hex_filter) %>%
             mutate(
@@
 
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
@@
 hex_points_df <- centroid_allocation %>% 
-  group_by(SA2_5DIG16) %>%
-  nest() %>%
+  group_nest(LGA_CODE16) %>%
   mutate(hex_points = 
@@
 ggplot(hex_points_df) + 
-  geom_polygon(aes(x = hexv_long, y = hexv_lat, group = SA2_5DIG16)) +
+  geom_polygon(aes(x = hexv_long, y = hexv_lat, group = LGA_CODE16)) +
   coord_equal() +
@@
 ```{r fullhexmap}
-lga_map <- create_hexmap(shp = tas_sa2, sf_id = "SA2_5DIG16", buffer_dist = NULL, filter_dist = 10, export_shp = FALSE, focal_points = sugaRbag::capital_cities, projstring = projstring, verbose = TRUE)
-
-hexmap_lga <- left_join(tas_sa2, 
-  lga_map)
-
+# Create centroids set
+centroids <- create_centroids(tas_lga, "LGA_CODE16")
+# Create hexagon location grid
+grid <- create_grid(centroids = centroids, hex_size = 0.1, buffer_dist = 0.1)
+# Allocate polygon centroids to hexagon grid points
+hex_allocated <- allocate(centroids = centroids,
+hex_grid = grid,
+sf_id = "LGA_CODE16",
+hex_size = 0.1, # same size used in create_grid
+hex_filter = 1.2,
+focal_points = capital_cities,
+width = 30,
+ verbose = TRUE) # same column used in create_centroids
 ```
@@
 ```{r}
+h1 <- hex_allocated %>%
+  dplyr::group_nest(LGA_CODE16) %>%
+                mutate(hex = purrr::map(data, fortify_hexagon, hex_size = 0.1)) %>%
+                unnest(data) %>% 
+  unnest(hex) %>% left_join(., tas_lga)
+
+p1 <- fortify_sfc(tas_lga)
+
 end_hex <- ggplot() +
-  geom_polygon(aes(x = long, y = lat, group = group), data = fort_tas, fill = "grey", colour = "white") +
-  theme_void() + coord_equal() +
-    geom_hex(aes(x = hex_long, y = hex_lat, fill = AREA_SQKM), data = hexmap_lga, 
-      position = "identity", stat = "identity")
+  geom_polygon(data = p1, aes(x=long, lat, group = group), alpha = 0.1) +
+  geom_polygon(data = h1, aes(x=hexv_long, hexv_lat, group = LGA_CODE16)) + theme_void() + coord_equal()
 
@@
 
-Examples of Melbourne, tas, Australia
+Examples of Melbourne, lga, Australia
 At different levels, distance from original centroids, change in area
@@
 LGA of all Australia
-SA2 for tas
+SA2 for lga
 

### 2019-03-27 algorithmRjournal/algorithmRjournal.Rmd
R journal template draft

--- 2019-03-04 algorithm_radix.Rmd
@@
 ---
-title: "An algorithm for a spatial mapping using a hexagon tilegram, with application to Australia disease maps"
+title: An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With Application to Australian Maps
 author:
   - name: Stephanie Kobakian
-    url: https://github.com/srkobakian
-    affiliation: Queensland University of Technology
-date: "`r Sys.Date()`"
-output: radix::radix_article
+    affiliation: Queensland Univeristy of Technology
+    email:  stephanie.kobakian@monash.edu
+  - name: Dianne Cook
+    affiliation: Monash University
+    email:  dicook@monash.edu
+abstract: >
+  This algorithm creates a hexagon to represent each of the spatial polygons provided.
+It allocates these hexagon in a manner that preserves the spatial relationship of the areas.
+It showcases spatial distributions, by emphasising the small geograhical regions that are often diffcult to locate on large geographic maps.
+output:
+  rticles::rjournal_article:
+    includes:
+      in_header: preamble.tex
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, cache = FALSE)
+knitr::opts_chunk$set(echo = FALSE,
+  cache = FALSE,
+  message = FALSE,
+  warning = FALSE,
+  fig.height = 3, fig.width = 3)
 ```
 
-# Abstract
-
-<!--
-problem has been studied
-what is the goal of the thesis/paper
-brief statement on existing solutions and their drawbacks
-major  contributions  of  the  thesis
-State  briefly  assumptions  and  limitations. 
-The  abstract  should  also  include  major idea(s)
-the type (e.g. performance, complexity) and result of analysis done
--->
-
-KEYWORDS:
-
-# Introduction
+## Introduction
 
 Spatial distrbutions have utilised alternative representations of geography for many years.
-In modern times with the ease of interactivity and animation, alternative representations have been popularised by online news sites, with a focus on public consumption.
-Applications are increasingly widespread, especially in the area of disease mapping, election results and .
+In modern times interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, with a focus on public consumption.
+Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
 
 ## Motivation
-<!--
-Problem   statement   (precise   definition   and   importance);   
-avoid   very   technical definitions  and  statements, give  good  intuition for your involved definitions or facts. 
--->
 
-Spatial distributions of people and human related statistics are not well presented in geographic maps.
-Populations congregate around major cities and the lack of land available encourages vertical living.
-Government bodies define localities, attempting to evenly distribute the population into measureable areas.
-As the rural areas of Australia are often sparsely populated in comparison to their urban centres the square meterage of the geographic areas may vastly differ in size.
+Spatial distributions of people and human related statistics can be misrepresented in geographic maps.
+Populations congregate around major cities and vertical living is increasingly common.
+Population statistics often requires dividing people into smaller, measureable areas.
+Government bodies such as the Australian Bureau of Statistics, or intentionally segregated organisations, like the Australian Electoral Comission hold the responsibility of the division.
+Australia is an example of strong urbanisation, the rural areas are often sparsely populated in comparison to the urban centres.
+To divide the population equally, the square meterage of the geographic areas differ dramatically in size.
 
-Alternative mapping methods allow increased understanding of the spatial distribution of a variable amongst the population.
-Allowing the focus to be placed on the distribution of the statistics between the groups of areas, not the geography.
+Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population.
+Alternative maps allow the focus to be placed on the distribution of the statistics between the groups of areas.
 
-<!--
-Existing  solutions  and  their  criticism  (limit  only  to  those  directly  relevant  to  the  contribution of the thesis; give a motivation for doing research on the topic); 
--->
+Extremely small geographic areas are lost on large geographic maps, small inner areas of Sydney or Melbourne are not easily compared at a high level.
+Cartograms place importance on the statistic of interest, allowing distorted map space on the display to represent differences in the statistic.
+These maps rely on the statistic of interest to determine the layout, and for Australia, often fail to preserve a recognisable view.
+Tilegrams allow preservation of spatial relationships as they decrease the emphasis on the amount of geograhic area considered to be interesting.
+These maps focus on the relationship between neighbours, in considering aggregated statistics of heterogeneous regions.
 
-Extremely small geographic areas are lost on large geographic maps, areas in Sydney or Melbourne are not easily compared at a high level.
-Cartograms allow an alternative view.
-Placingimportance on the statistic of interest, allowing unequal map space on the display to represent differences in the statistic.
-These maps rely on the statistic of interest to determine the layout, and often fail to preserve a recognisable view of Australia.
-Tile grams allow a better preservation of relationships.
-Decrease the emphasis on the amount of geograhic area considered to be interesting.
-Focus on the relationship between neighbours, in considering aggregated statistics of heterogeneous regions.
-
-<!--
-With different characteristics or properties:
-
--->
-
-Australia and Canada present an application that contains an unusual population settlement and dispersion over the geographical space: 
-- Australia: Dense south east, sparse central and west
-
-## Background
-<!--
-basic facts needed to tune the reader to the thesis or paper
--->
-
-- Choropleth methods are accurate geographically.
-- Cartogram alternative map has been used historically.
-- Spatial relationships are preserved.
-
-<!--
-all  known  results  relevant  to  the  problem  stated,  
-whether  or  not  they  are  used  in  proposed  contributions
--->
-
-<!--
-Discuss  advantages  and  drawbacks  of  known  solutions  that  are  relevant  to  your  problem, 
-discuss  the  relevance of each reviewed item to your topic and your solutions. 
--->
-
-<!--
-For  every  discussed  reference,  it  is  very  important  to  relate  them  to  your  problem  and  contribution  in  one  of  several  ways:  
-it  does  not  exactly  solve  the  same  problem,
-it  solves  the  same  problem  but  makes  different  assumptions  about  the  system, 
-it  has  some  limitations  that you  do  not  have, 
-it  makes  the  same  assumptions  but  does  not  work  well  under  certain  
-conditions  and  scenarios  for  which  you  have  better  solutions,  or, 
-if  none  of  these  is  true,  you are   considering   it   as   valid   competitor,   and   will   try   to   defeat   it   in   your   analytical   or
-
-experimental  comparisons.  
--->
-## Proposed Solution
-
-<!--
-Contributions (proposed solutions; why they are expected to be better; essence of the idea(s) used in proposed solutions); 
-What the algorithm is trying to do:
--->
-
-- Like Dorling, same shape will be used.
-Like tilegram, tessellation using equally sized shapes.
-
-- Allocate each geographic area to a map space of consistent tessellated shape
-
-which is different from existing algorithms:
-- contiguous, keeps exact neighbours, no recognisable shape
-- non contiguous, keeps shape, can lose neighbours
-
-<!--
-Why the reader should believe that it is correct or reasonable.
--->
-- Clear to see spatial distribution, 
-_ Should keep neighbours relationships intact as geographic neighbours will have similar values
-
-<!--
-If it is supposed to be “better”, what is meant by better.
--->
-Easier to read distribution at a distance, see a much larger area, general relationship at a glance
-
-<!--
-Conditions, assumptions and limitations of the research done; 
--->
-Works well for America, states are almost homogeneous 
-Works well for England, London is the biggest issue, pushing out rural areas does not disturb population dense areas.
-
-<!--
-Analysis  (theoretical,  experimental,  simulations,  implementations, done  in  thesis;  under what conditions and scenarios is your solution best?  
--->
-
-Our solution considers multiple population dense areas.
-
-Allows dispersion to be increased when needed, and distance from origin to be considered
-
-The Dorling maps in [@TVSSS] give examples of displacing central geographically small, population dense areas.
-This inspired the concept of this algorithm.
+Our case is an extension of these concepts.
+Extending the tilegram to Australian applications required preserving the spatial relationships.
+It emphasises the capital cities as population hubs, and recognises the populations distributed across the large rural areas.
 
@@
 
-The algorithm operates on a set of polygons.
+Our solution operates on a set of polygons.
 There are parameters used in the process that may be provided, or will be automatically derived.
-All necessary functions are exported, with a main function `create_hexmap` used to step through automatically.
+All necessary functions are exported, with a main function `create_hexmap` used to step through these automatically.
 
@@
 
-As the `create_hexmap` function requires several parameters, if they are not provided, the information will be derived from the polygon set used.
+The `create_hexmap` function requires several parameters, if they are not provided, the information will be derived from the polygon set used.
 
@@
   description = c('an Rdata object containing the polygon information', 'character string location of the shape file that contains the polygon information', 'name of a unique column that distinguishes areas',
-    'a data frame of reference locations when allocating hexagons, capital cities of Australia are provided as capital_cities'
-    )))
+    'a data frame of reference locations used to allocate hexagons'
+    )), format = "latex")
 
@@
 
-The polygon set of Local Government Areas in Australia in 2016 is stored in the sugarbag package data as `tas_lga`. To create this object:
+The polygon set of Local Government Areas in Tasmania in 2016 is stored in the sugarbag package data as `tas_lga`. 
+A single column of the data set must be used as a unique identifier of areas. In this case, the unique LGA codes associated with each LGA have been used, their names could have also been used.
 
-```
-# Download resource 
-# link to folder containing .shp file on sugarbag site.
-
-aus_sa2 <- read_shape("file location")
-
+```{r id}
+sf_id <- "LGA_CODE16"
 ```
 
-A column of the data set must be used as a unique identifier of areas.
+The centre of the population hubs are used to distribute areas around the closest captial city.
 
 ```{r data}
-sf_id <- "LGA_CODE16"
 data(capital_cities)
@@
 
-**The following will be determined within `create_hexmap` if not provided. They are created throughout the following example:**
+**The following parameters will be determined within `create_hexmap` if not provided. They are created throughout the following example:**
 
 ```{r}
-knitr::kable(tibble(parameter = c('projstring', 
-  'epsg', 'buffer_dist', 'hex_size',  'hex_filter', 'width'),
-  description = c('a string to indicate the projection and epsg', 'the four character string to indicate the CRS', 
-    'a float value for distance in degrees to extend beyond the - geometry provided',
+knitr::kable(tibble(parameter = c('buffer_dist', 'hex_size',  'hex_filter', 'width'),
+  description = c('a float value for distance in degrees to extend beyond the - geometry provided',
     'a float value in degrees for the diameter of the hexagons', 'amount of hexagons around centroid to consider for allocation',
-    'the angle used to filter the grid points around a centroid')))
+    'the angle used to filter the grid points around a centroid')), format = "latex")
 ```
@@
 Begin with a set of polygons.
-There are several ways of providing the set of polygons.
-The following methods are available via the `read_shape` function. It utilises the `st_read` function is to create the sf object.
-
-- If the shape file is an .Rda file, it is loaded into the current environment.
-- To utilise a custom shape file from a directory on your device, provide the file path for .shp file.
-
-<!--
-```
-# Read in shape information
-shp <- read_shape(shp_path = shp_path)
-```
--->
-
-Empty geometries are removed from the sf object, and the remaining polygons are projected to the Australian standard using `projstring`.
-
-We will use the Statical Areas (Level 2) of Australia, provided by Australian Bureau of Statistics.
+The set should be provided as an `sf` object, this is a data frame containing a `geometry` column.
+The `read_shape` function can assist in creating this object.
+We will use the Loca Goverment Areas of Tasmania, sourced from the Australian Bureau of Statistics.
 
 ```{r}
-load("data/tas_lga.rda")
+# Create a suitable data set for plotting
+fort_lga <- fortify_sfc(tas_lga)
 
-# Convert to a simple features object
-tas_lga <- sf::st_as_sf(tas_lga)
-
-# Select only desired LGA areas.
-tas_lga[[sf_id]] <- droplevels(as.factor(tas_lga[[sf_id]]))
-
-fort_lga <- fortify_sfc(tas_lga)
-```
-
-```{r}
 # Include area variable
@@
 
-Create a grid of hexagon centroids using the `create_grid` function.
-
-The grid creation takes several steps. It requires the centroids, the bounding box, the hexagon size and the buffer distance.
+Each new hexagon will need to tesselate, a grid is created to ensure a close point is found, that will allow all areas to tesselate, this is inspired by tilegrams.
+The grid of possible hexagon centroids can be made using the `create_grid` function.
+The grid creation takes several steps.
+It requires the centroids, the hexagon size and the buffer distance.
 
 ```{r bbox}
-## Not necessary when using `create_hexmap`:
 ## create the bounding box from the set of polygon centroids:
-bbox <- tibble::tibble(min = c(min(centroids$longitude), min(centroids$latitude)),
-        max = c(max(centroids$longitude), max(centroids$latitude)))
+bbox <- tibble::tibble(min = c(min(centroids$longitude, na.rm = TRUE), min(centroids$latitude, na.rm = TRUE)),
+        max = c(max(centroids$longitude, na.rm = TRUE), max(centroids$latitude, na.rm = TRUE)))
 
-hex_size <- (bbox$max[1] - bbox$min[1])/(bbox$max[2] - bbox$min[2]) / 5
+hex_size <- 0.2
+
+# default size calculation:
+#(bbox$max[1] - bbox$min[1])/(bbox$max[2] - bbox$min[2]) / 5
 
@@
 ### Step 1: Expand the grid
-Two sequences are used, one for longitude and another for latitude.
+
+One sequence is created for longitude columns, and another for latitude rows.
+
 The sequences begin at the minimum longitude or latitude, minus the buffer distance.
-Equally spaced intervals, the size of the hexagons, are created up to the maximum longitude or latitude, plus the buffer distance.
+Equally spaced intervals the size of the hexagons are created up to the maximum longitude or latitude, plus the buffer distance.
 
-An individual point is created from all combinations of longitude and latitude sequences.
+An individual point is created from all intersections of the longitude columns and latitude row sequences.
 
 ```{r grid}
-grid <- tibble::as_tibble(expand.grid(hex_long = seq(bbox$min[1] - buffer_dist,
-    bbox$max[1] + buffer_dist,
-    hex_size),
-    hex_lat = seq(bbox$min[2] - buffer_dist,
-        bbox$max[2] + buffer_dist,
-        hex_size)))
+grid <- tibble::as_tibble(
+  expand.grid(
+    hex_long = seq(bbox$min[1] - buffer_dist, # minimum
+      bbox$max[1] + buffer_dist, # maximum
+      hex_size), # distance between hexagons
+    hex_lat = seq(bbox$min[2] - buffer_dist, # minimum
+      bbox$max[2] + buffer_dist, # maximum
+      hex_size))) # distance between hexagons
 ```
@@
 
-This grid is square, which will not facilitate tessellated hexagons. 
-Every second latitude (row) of points will be shifted right by half of the hexagon size.
+A square grid will not facilitate tessellated hexagons. Every second latitude row of points will be shifted right by half of the hexagon size.
 
@@
 
-Each row and column is given an ID
+Each point is now given an ID.
 
@@
 
-There are more points than necessary on this grid.
-
 ### Step 2: Rolling windows
 
-To filter the grid for appropriate hexagons for allocation,
+Not all of the grid points will be used, especially if islands impact the overall space covered.
+To filter the grid for appropriate points for allocation,
 the `create_buffer` function is called from `create_grid`.
-
-It finds the amount of columns and rows needed to capture the set of centroids.
+It finds the amount of columns and rows needed to best capture the set of centroids.
 
@@
 
-The rows and columns are divided into 20 groups. The amount of rows in each latitude group and the amount of columns in each longitude group are then used as the width of manual rolling windows.
+The rows and columns are divided into 20 groups.
+The amount of rows in each latitude group and the amount of columns in each longitude group are then used as the width of manual rolling windows.
+This will tailor the available points to the areas most likely to be used.
+It helps reduce amount of time taken.
 
@@
 
-The first rolling window function finds the minimum and maximum centroid values for the groups of longitude columns and the groups of latitude rows.
-The specific rows and columns in the rolling windows are defined.
+The specific rows and columns in the rolling windows are defined.The first rolling window function finds the minimum and maximum centroid values for the sliding groups of longitude columns and the groups of latitude rows.
 
@@
   nest(longitude, latitude) %>% 
-  mutate(closest = map(data, closest_focal_point, focal_points = capital_cities)) %>% 
+  mutate(closest = map(data, closest_focal_point, focal_points = capital_cities %>% filter(points == "Hobart"))) %>% 
   unnest(data, closest) %>% 
@@
 
-For each polygon centroid in the set.
-Find the distance to each of the focal points provided.
-The closest focal point name, the distance to the polygon centroid, and the angle from focal point to polygon centroid will be returned and added to the polygon data set in the polygon centroid row.
+For each polygon centroid in the set, the distance to each of the focal points provided is recorded.
+The closest focal point name, the distance to the polygon centroid, and the angle from focal point to polygon centroid will be added to the polygon's row, in the polygon data set.
+To minimise time taken for this step, only Tasmania's capital city Hobart has been provided.
 
-The distance between the polygon centroid and it's closest focal point data set is used to arrange the data set for allocation.
+The distance between the polygon centroid and it's closest focal point data set is used to order the data set for allocation.
 The points are arranged in ascending order, from the centroid closest to any of the focal points, to the furthest.
@@
 
-Define a distance around a centroid to consider for possible hexagon location.
+The distance around a centroid to consider for possible hexagon locations is determined by the hex_filter.
+It multiplies the amount given by hex_filter, by the size of the hexagons to find the distance.
 
-```{r f_dist}
-## Not necessary when using `create_hexmap`:
+```{r}
 ## Consider hexagon points up to a certain distance from centroid
-
-hex_filter <- (hex_size)*10
+hex_filter <- 10
 ```
-
-Allocate each centroid, beginning with the closest to a focal point, extending to the furthest. Will preserve spatial relationship.
 
@@
         width = width,
-        capital_cities = capital_cities,
+        focal_points = capital_cities,
         verbose = TRUE,
@@
 For each polygon centroid, only the hexagon grid points that have not yet been used can be considered.
+Allocate each centroid, beginning with the closest centroid to a focal point.
+This will preserve spatial relationship with the capital, as the inner areas will be allowed closest to the captial, and the areas that are further will be accomodated after.
 
@@
 
-The filter distance parameter is used to subset possible grid points to only those surrounding the polygon centroid within the filter distance.
+The filter parameter is used to subset possible grid points to only those surrounding the polygon centroid within the filter distance, smaller distance will increase speed, but can decrease accuracy.
 
@@
 hex_grid <- hex_grid %>% ungroup() %>%
-        filter(flat - hex_filter < hex_lat & hex_lat < flat + hex_filter) %>%
-        filter(flong - hex_filter < hex_long & hex_long < flong + hex_filter)
+        filter(flat - buffer_dist < hex_lat & hex_lat < flat + buffer_dist) %>%
+        filter(flong - buffer_dist < hex_long & hex_long < flong + buffer_dist)
 
@@
 hex_points_df <- centroid_allocation %>% 
-  group_nest(LGA_CODE16) %>%
-  mutate(hex_points = 
-      map(.x = data,.f = function(a) { 
-        fortify_hexagon(data = a, hex_size = hex_size)})) %>%
-  unnest(data) %>%
-  unnest(hex_points)
+  fortify_hexagon(hex_size = hex_size)
 ```
@@
 ggplot(hex_points_df) + 
-  geom_polygon(aes(x = hexv_long, y = hexv_lat, group = LGA_CODE16)) +
+  geom_polygon(aes(x = long, y = lat, group = LGA_CODE16)) +
   coord_equal() +
@@
 # Create hexagon location grid
-grid <- create_grid(centroids = centroids, hex_size = 0.1, buffer_dist = 0.1)
+grid <- create_grid(centroids = centroids, hex_size = 0.25, buffer_dist = 1.2)
 # Allocate polygon centroids to hexagon grid points
@@
 sf_id = "LGA_CODE16",
-hex_size = 0.1, # same size used in create_grid
-hex_filter = 1.2,
+hex_size = 0.25, # same size used in create_grid
+hex_filter = 10,
 focal_points = capital_cities,
-width = 30,
- verbose = TRUE) # same column used in create_centroids
+width = 30, verbose = FALSE) # same column used in create_centroids
 ```
@@
 h1 <- hex_allocated %>%
-  dplyr::group_nest(LGA_CODE16) %>%
-                mutate(hex = purrr::map(data, fortify_hexagon, hex_size = 0.1)) %>%
-                unnest(data) %>% 
-  unnest(hex) %>% left_join(., tas_lga)
+  fortify_hexagon(hex_size = 0.25) %>% 
+  left_join(., tas_lga)
 
@@
   geom_polygon(data = p1, aes(x=long, lat, group = group), alpha = 0.1) +
-  geom_polygon(data = h1, aes(x=hexv_long, hexv_lat, group = LGA_CODE16)) + theme_void() + coord_equal()
+  geom_polygon(data = h1, aes(x=long, lat, group = LGA_CODE16)) + theme_void() + coord_equal()
 
@@
 
-# Evaluation
-
-<!--
-The  performance  of  your  solution  can  be  compared  with  existing  solutions,  if  any  exists 
-under  same  or  similar  assumptions,  analytically  and/or  by  doing  a  simulation.
-
-Find examples of measures of cartogram effectiveness
-
--->
-
-Measure changes to areas:
-Each hexagon area in the set of $npolys$ is standardised to 1 unit.
-Where 1 unit is the area of a hexagon of the designated size.
-
-$area_{h_i} = 1$
-
-$area_h = 1 * npolys$
-
-$y_i$ denotes the statistic of interest for polygon i, where i = 1,...,npolygs
-$x_i$ denotes the spatial area for polygon i, where i = 1,...,npolys
-
-Areal Statistic Distortion is the change in the areal distribution of the set of polygons.
-Difference between space taken by polygons and space taken by hexagons, with respect to the desired statistic.
-Setting the desired statistic to area gives the change in map space used to represent the polygons.
-
-The average when considering area used to display:
-
-$A = \sum_{i=1}^{npolys}y_ix_i/ \sum_{i=1}^{npolys}x_i$
-
-$H = \sum_{i=1}^{npolys}y_i/npolys$
-
-Using $w_i = x_i/\sum_{i=1}^{npolys}x_i$
-
-$\sqrt{ 1/npolys\sum_{i=1}^{npolys}(y_i - \bar y)^2 w_i }$
-
-Considering only a local area distortion: 
-Where the subset used contains only neighbours within a certain distance of the polygon centroid
-
-Where $\bar y_d$ is the average of the polygon statistics considering only the polygons where the distance between polygon centroid x_i and polygon centroid x_p is less than d:
-
-$d(x_ix_p) < d$
-
-$\sqrt{ 1/npolys\sum_{i=1}^{npolys}(y_i - \bar y_d)^2 w_i }$
-
-Old neighbours over new neighbours?
-<!--
-Apply methods of evaluation used elsewhere
-Nusrat, Alam and Kobourov:
-- Statistical accuracy: how well do the modified areas
-represent the corresponding statistic shown (e.g.,
-population or GDP). This is measured in terms of
-“cartographic error.”
-- Geographical accuracy: how much do the modified
-shapes resemble the original geographic shapes and
-how well preserved are their relative positions.
-- Topological accuracy: how well does the topology (as
-measured by adjacent regions) of the cartogram
-match that of the original map.
--->
-
-# Summary
-
-<!--
-What did you achieve with this research? 
-What are the drawbacks of your solution(s)? 
-What kind  of  future  work  can  be  done? 
-Do  you  have  some  ideas  that  you  intend  to  study  further? 
-The  ownership  of  some  other  possible  solutions,  not  fully  explored,  or  subject  of  your  
-forthcoming  different  article,  can  be  protected  by  outlining  them  briefly  in  the  conclusion  
-section, sometimes with reference to upcoming article. 
--->
-
-# Discussion
-
-\pagebreak
-
-# Reference List
-
-<div id="refs"></div>
+\bibliography{algorithmbib}

### 2019-03-27 algorithmRjournal/algorithmRjournal.tex
R journal template draft

--- 2019-03-27 algorithmRjournal/algorithmRjournal.Rmd
@@
----
-title: An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With Application to Australian Maps
-author:
-  - name: Stephanie Kobakian
-    affiliation: Queensland Univeristy of Technology
-    email:  stephanie.kobakian@monash.edu
-  - name: Dianne Cook
-    affiliation: Monash University
-    email:  dicook@monash.edu
-abstract: >
-  This algorithm creates a hexagon to represent each of the spatial polygons provided.
-It allocates these hexagon in a manner that preserves the spatial relationship of the areas.
-It showcases spatial distributions, by emphasising the small geograhical regions that are often diffcult to locate on large geographic maps.
-output:
-  rticles::rjournal_article:
-    includes:
-      in_header: preamble.tex
----
+% !TeX root = RJwrapper.tex
+\title{An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With
+Application to Australian Maps}
+\author{by Stephanie Kobakian, Dianne Cook}
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE,
-  cache = FALSE,
-  message = FALSE,
-  warning = FALSE,
-  fig.height = 3, fig.width = 3)
-```
+\maketitle
 
-## Introduction
+\abstract{%
+This algorithm creates a hexagon to represent each of the spatial
+polygons provided. It allocates these hexagon in a manner that preserves
+the spatial relationship of the areas. It showcases spatial
+distributions, by emphasising the small geograhical regions that are
+often diffcult to locate on large geographic maps.
+}
 
-Spatial distrbutions have utilised alternative representations of geography for many years.
-In modern times interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, with a focus on public consumption.
-Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
+% Any extra LaTeX you need in the preamble
 
-## Motivation
+\hypertarget{introduction}{%
+\subsection{Introduction}\label{introduction}}
 
-Spatial distributions of people and human related statistics can be misrepresented in geographic maps.
-Populations congregate around major cities and vertical living is increasingly common.
-Population statistics often requires dividing people into smaller, measureable areas.
-Government bodies such as the Australian Bureau of Statistics, or intentionally segregated organisations, like the Australian Electoral Comission hold the responsibility of the division.
-Australia is an example of strong urbanisation, the rural areas are often sparsely populated in comparison to the urban centres.
-To divide the population equally, the square meterage of the geographic areas differ dramatically in size.
+Spatial distrbutions have utilised alternative representations of
+geography for many years. In modern times interactivity and animation
+have begun to play a larger role, as alternative representations have
+been popularised by online news sites, with a focus on public
+consumption. Applications are increasingly widespread, especially in the
+areas of disease mapping, and election results.
 
-Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population.
-Alternative maps allow the focus to be placed on the distribution of the statistics between the groups of areas.
+\hypertarget{motivation}{%
+\subsection{Motivation}\label{motivation}}
 
-Extremely small geographic areas are lost on large geographic maps, small inner areas of Sydney or Melbourne are not easily compared at a high level.
-Cartograms place importance on the statistic of interest, allowing distorted map space on the display to represent differences in the statistic.
-These maps rely on the statistic of interest to determine the layout, and for Australia, often fail to preserve a recognisable view.
-Tilegrams allow preservation of spatial relationships as they decrease the emphasis on the amount of geograhic area considered to be interesting.
-These maps focus on the relationship between neighbours, in considering aggregated statistics of heterogeneous regions.
+Spatial distributions of people and human related statistics can be
+misrepresented in geographic maps. Populations congregate around major
+cities and vertical living is increasingly common. Population statistics
+often requires dividing people into smaller, measureable areas.
+Government bodies such as the Australian Bureau of Statistics, or
+intentionally segregated organisations, like the Australian Electoral
+Comission hold the responsibility of the division. Australia is an
+example of strong urbanisation, the rural areas are often sparsely
+populated in comparison to the urban centres. To divide the population
+equally, the square meterage of the geographic areas differ dramatically
+in size.
 
-Our case is an extension of these concepts.
-Extending the tilegram to Australian applications required preserving the spatial relationships.
-It emphasises the capital cities as population hubs, and recognises the populations distributed across the large rural areas.
+Alternative mapping methods allow increased understanding of the spatial
+distribution of a variable across the population. Alternative maps allow
+the focus to be placed on the distribution of the statistics between the
+groups of areas.
 
-# Algorithm
+Extremely small geographic areas are lost on large geographic maps,
+small inner areas of Sydney or Melbourne are not easily compared at a
+high level. Cartograms place importance on the statistic of interest,
+allowing distorted map space on the display to represent differences in
+the statistic. These maps rely on the statistic of interest to determine
+the layout, and for Australia, often fail to preserve a recognisable
+view. Tilegrams allow preservation of spatial relationships as they
+decrease the emphasis on the amount of geograhic area considered to be
+interesting. These maps focus on the relationship between neighbours, in
+considering aggregated statistics of heterogeneous regions.
 
-Our solution operates on a set of polygons.
-There are parameters used in the process that may be provided, or will be automatically derived.
-All necessary functions are exported, with a main function `create_hexmap` used to step through these automatically.
+Our case is an extension of these concepts. Extending the tilegram to
+Australian applications required preserving the spatial relationships.
+It emphasises the capital cities as population hubs, and recognises the
+populations distributed across the large rural areas.
 
-## Parameters
+\hypertarget{algorithm}{%
+\section{Algorithm}\label{algorithm}}
 
-The `create_hexmap` function requires several parameters, if they are not provided, the information will be derived from the polygon set used.
+Our solution operates on a set of polygons. There are parameters used in
+the process that may be provided, or will be automatically derived. All
+necessary functions are exported, with a main function
+\texttt{create\_hexmap} used to step through these automatically.
 
-**The following must be provided to `create_hexmap`:**
-```{r table_necessary}
-knitr::kable(tibble::tibble(parameter = c('shp', 
-  'shp_path',
-  'sf_id',
-  'capital_cities'),
-  description = c('an Rdata object containing the polygon information', 'character string location of the shape file that contains the polygon information', 'name of a unique column that distinguishes areas',
-    'a data frame of reference locations used to allocate hexagons'
-    )), format = "latex")
+\hypertarget{parameters}{%
+\subsection{Parameters}\label{parameters}}
 
-```
+The \texttt{create\_hexmap} function requires several parameters, if
+they are not provided, the information will be derived from the polygon
+set used.
 
-```{r libraries}
-library(tidyverse)
-# To install sugarbag:
-# devtools::install_github("srkobakian/sugarbag")
-library(sugarbag)
-```
+\textbf{The following must be provided to \texttt{create\_hexmap}:}
 
-The polygon set of Local Government Areas in Tasmania in 2016 is stored in the sugarbag package data as `tas_lga`. 
-A single column of the data set must be used as a unique identifier of areas. In this case, the unique LGA codes associated with each LGA have been used, their names could have also been used.
+\begin{Schunk}
 
-```{r id}
-sf_id <- "LGA_CODE16"
-```
+\begin{tabular}{l|l}
+\hline
+parameter & description\\
+\hline
+shp & an Rdata object containing the polygon information\\
+\hline
+shp\_path & character string location of the shape file that contains the polygon information\\
+\hline
+sf\_id & name of a unique column that distinguishes areas\\
+\hline
+capital\_cities & a data frame of reference locations used to allocate hexagons\\
+\hline
+\end{tabular}
 
-The centre of the population hubs are used to distribute areas around the closest captial city.
+\end{Schunk}
 
-```{r data}
-data(capital_cities)
-```
+The polygon set of Local Government Areas in Tasmania in 2016 is stored
+in the sugarbag package data as \texttt{tas\_lga}. A single column of
+the data set must be used as a unique identifier of areas. In this case,
+the unique LGA codes associated with each LGA have been used, their
+names could have also been used.
 
-**The following parameters will be determined within `create_hexmap` if not provided. They are created throughout the following example:**
+The centre of the population hubs are used to distribute areas around
+the closest captial city.
 
-```{r}
-knitr::kable(tibble(parameter = c('buffer_dist', 'hex_size',  'hex_filter', 'width'),
-  description = c('a float value for distance in degrees to extend beyond the - geometry provided',
-    'a float value in degrees for the diameter of the hexagons', 'amount of hexagons around centroid to consider for allocation',
-    'the angle used to filter the grid points around a centroid')), format = "latex")
-```
+\textbf{The following parameters will be determined within
+\texttt{create\_hexmap} if not provided. They are created throughout the
+following example:}
 
-When utilising individual `sugarbag` functions, we recommend the following approach:
+\begin{Schunk}
 
-## Polygon Information
+\begin{tabular}{l|l}
+\hline
+parameter & description\\
+\hline
+buffer\_dist & a float value for distance in degrees to extend beyond the - geometry provided\\
+\hline
+hex\_size & a float value in degrees for the diameter of the hexagons\\
+\hline
+hex\_filter & amount of hexagons around centroid to consider for allocation\\
+\hline
+width & the angle used to filter the grid points around a centroid\\
+\hline
+\end{tabular}
 
-Begin with a set of polygons.
-The set should be provided as an `sf` object, this is a data frame containing a `geometry` column.
-The `read_shape` function can assist in creating this object.
-We will use the Loca Goverment Areas of Tasmania, sourced from the Australian Bureau of Statistics.
+\end{Schunk}
 
-```{r}
-# Create a suitable data set for plotting
-fort_lga <- fortify_sfc(tas_lga)
+When utilising individual \texttt{sugarbag} functions, we recommend the
+following approach:
 
-# Include area variable
-area_var <- fort_lga %>% 
-  distinct(LGA_CODE16, .keep_all = TRUE) %>% 
-  select(LGA_CODE16, AREASQKM16)
-```
+\hypertarget{polygon-information}{%
+\subsection{Polygon Information}\label{polygon-information}}
 
-```{r centroids}
-## Use the create_centroids function to find polygon centroids:
-centroids <- create_centroids(shp_sf = tas_lga, sf_id = sf_id) %>%
-  left_join(., select(area_var, LGA_CODE16, AREASQKM16), by = "LGA_CODE16")
-```
+Begin with a set of polygons. The set should be provided as an
+\texttt{sf} object, this is a data frame containing a \texttt{geometry}
+column. The \texttt{read\_shape} function can assist in creating this
+object. We will use the Loca Goverment Areas of Tasmania, sourced from
+the Australian Bureau of Statistics.
 
-```{r, fig.cap="lga Local Government Areas and derived centroids."}
-end_cents <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids) + theme_void() + coord_equal()
-end_cents
+\begin{Schunk}
+\begin{figure}
+\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-3-1} \caption[lga Local Government Areas and derived centroids]{lga Local Government Areas and derived centroids.}\label{fig:unnamed-chunk-3}
+\end{figure}
+\end{Schunk}
 
-#ggplot() + geom_histogram(aes(x = log(AREASQKM16), fill = log(AREASQKM16)), data= centroids, bins = 20) 
-```
+\hypertarget{hexagon-grid}{%
+\subsection{Hexagon grid}\label{hexagon-grid}}
 
-## Hexagon grid
+Each new hexagon will need to tesselate, a grid is created to ensure a
+close point is found, that will allow all areas to tesselate, this is
+inspired by tilegrams. The grid of possible hexagon centroids can be
+made using the \texttt{create\_grid} function. The grid creation takes
+several steps. It requires the centroids, the hexagon size and the
+buffer distance.
 
-Each new hexagon will need to tesselate, a grid is created to ensure a close point is found, that will allow all areas to tesselate, this is inspired by tilegrams.
-The grid of possible hexagon centroids can be made using the `create_grid` function.
-The grid creation takes several steps.
-It requires the centroids, the hexagon size and the buffer distance.
+\hypertarget{step-1-expand-the-grid}{%
+\subsubsection{Step 1: Expand the grid}\label{step-1-expand-the-grid}}
 
-```{r bbox}
-## create the bounding box from the set of polygon centroids:
-bbox <- tibble::tibble(min = c(min(centroids$longitude, na.rm = TRUE), min(centroids$latitude, na.rm = TRUE)),
-        max = c(max(centroids$longitude, na.rm = TRUE), max(centroids$latitude, na.rm = TRUE)))
+One sequence is created for longitude columns, and another for latitude
+rows.
 
-hex_size <- 0.2
+The sequences begin at the minimum longitude or latitude, minus the
+buffer distance. Equally spaced intervals the size of the hexagons are
+created up to the maximum longitude or latitude, plus the buffer
+distance.
 
-# default size calculation:
-#(bbox$max[1] - bbox$min[1])/(bbox$max[2] - bbox$min[2]) / 5
+An individual point is created from all intersections of the longitude
+columns and latitude row sequences.
 
-buffer_dist <- max((bbox$max[1] - bbox$min[1]), (bbox$max[2] - bbox$min[2]))*0.3
-```
+\begin{Schunk}
 
-### Step 1: Expand the grid
+\includegraphics{algorithmRjournal_files/figure-latex/plot_grid-1} \end{Schunk}
 
-One sequence is created for longitude columns, and another for latitude rows.
+A square grid will not facilitate tessellated hexagons. Every second
+latitude row of points will be shifted right by half of the hexagon
+size.
 
-The sequences begin at the minimum longitude or latitude, minus the buffer distance.
-Equally spaced intervals the size of the hexagons are created up to the maximum longitude or latitude, plus the buffer distance.
+\begin{Schunk}
 
-An individual point is created from all intersections of the longitude columns and latitude row sequences.
-
-```{r grid}
-grid <- tibble::as_tibble(
-  expand.grid(
-    hex_long = seq(bbox$min[1] - buffer_dist, # minimum
-      bbox$max[1] + buffer_dist, # maximum
-      hex_size), # distance between hexagons
-    hex_lat = seq(bbox$min[2] - buffer_dist, # minimum
-      bbox$max[2] + buffer_dist, # maximum
-      hex_size))) # distance between hexagons
-```
-
-```{r plot_grid}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
-```
-
-A square grid will not facilitate tessellated hexagons. Every second latitude row of points will be shifted right by half of the hexagon size.
-
-```{r shift}
-# Find every second latitude
-shift_lat <- grid %>% dplyr::select(hex_lat) %>%
-    dplyr::distinct() %>%
-    dplyr::filter(dplyr::row_number() %% 2 == 1) %>% unlist()
-
-# Shift the longitude of every second latitude to the right to make hex structure
-grid <- grid %>%
-    dplyr::mutate(hex_long = ifelse(hex_lat %in% shift_lat, hex_long,
-        hex_long + (hex_size / 2))) %>%
-    dplyr::mutate(id=1:NROW(.)) %>%
-    dplyr::mutate(assigned=FALSE)
-```
-
-```{r plot_shift}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a") + theme_void() + coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
-```
+\includegraphics{algorithmRjournal_files/figure-latex/plot_shift-1} \end{Schunk}
 
@@
 
-```{r grid_id}
-full_grid <- grid <- grid %>%
-    mutate(hex_long_int = dense_rank(hex_long)-1,
-        hex_lat_int = dense_rank(hex_lat)-1)
-```
+\hypertarget{step-2-rolling-windows}{%
+\subsubsection{Step 2: Rolling windows}\label{step-2-rolling-windows}}
 
-### Step 2: Rolling windows
+Not all of the grid points will be used, especially if islands impact
+the overall space covered. To filter the grid for appropriate points for
+allocation, the \texttt{create\_buffer} function is called from
+\texttt{create\_grid}. It finds the amount of columns and rows needed to
+best capture the set of centroids.
 
-Not all of the grid points will be used, especially if islands impact the overall space covered.
-To filter the grid for appropriate points for allocation,
-the `create_buffer` function is called from `create_grid`.
-It finds the amount of columns and rows needed to best capture the set of centroids.
+The rows and columns are divided into 20 groups. The amount of rows in
+each latitude group and the amount of columns in each longitude group
+are then used as the width of manual rolling windows. This will tailor
+the available points to the areas most likely to be used. It helps
+reduce amount of time taken.
 
-```{r}
-nlong <- length(unique(grid$hex_long))
-nlat <- length(unique(grid$hex_lat))
+The specific rows and columns in the rolling windows are defined.The
+first rolling window function finds the minimum and maximum centroid
+values for the sliding groups of longitude columns and the groups of
+latitude rows.
 
-centroids <- centroids %>%
-  mutate(long_int = round((longitude-min(grid$hex_long))/(max(grid$hex_long)-min(grid$hex_long))*nlong, 0),
-          lat_int = round((latitude-min(grid$hex_lat))/(max(grid$hex_lat)-min(grid$hex_lat))*nlat, 0))
-```
+The second rolling window function finds the average of the rolling
+minimum and rolling maximum centroid values, for the longitude columns
+and latitude rows.
 
-The rows and columns are divided into 20 groups.
-The amount of rows in each latitude group and the amount of columns in each longitude group are then used as the width of manual rolling windows.
-This will tailor the available points to the areas most likely to be used.
-It helps reduce amount of time taken.
+\hypertarget{step-3-filtering-the-grid}{%
+\subsubsection{Step 3: Filtering the
+grid}\label{step-3-filtering-the-grid}}
 
-```{r echo = FALSE}
-# Amount of lats and longs in each group
-lat_size = round(nlat/20,0)
-long_size = round(nlong/20,0)
-```
+Only the grid points between the rolling average of the minimum and
+maximum centroid values are kept, for each row and column of the grid.
 
-The specific rows and columns in the rolling windows are defined.The first rolling window function finds the minimum and maximum centroid values for the sliding groups of longitude columns and the groups of latitude rows.
+\begin{Schunk}
 
-```{r echo = FALSE}
- # make a list of groups, manual sliding windows
-    nlat_list <- purrr::map2(seq(1:nlat), lat_size + seq(1:nlat), c)
-    nlong_list <- purrr::map2(seq(1:nlong), long_size + seq(1:nlong), c)
+\includegraphics{algorithmRjournal_files/figure-latex/plot_buffer-1} \end{Schunk}
 
-    lat_window <- function(x, cents = centroids, maximum = nlat){
-        max_int = min(x[2],maximum)
+\hypertarget{centroid-to-focal-point-distance}{%
+\subsection{Centroid to focal point
+distance}\label{centroid-to-focal-point-distance}}
 
-        cents_in <- filter(cents, between(lat_int, x[1], max_int))
-        return(cents_in)
-    }
+For each polygon centroid in the set, the distance to each of the focal
+points provided is recorded. The closest focal point name, the distance
+to the polygon centroid, and the angle from focal point to polygon
+centroid will be added to the polygon's row, in the polygon data set. To
+minimise time taken for this step, only Tasmania's capital city Hobart
+has been provided.
 
-    long_window <- function(x, cents = centroids, maximum = nlong){
-        max_int = x[2]
-        while (max_int > maximum){
-            max_int = max_int - 1
-        }
+The distance between the polygon centroid and it's closest focal point
+data set is used to order the data set for allocation. The points are
+arranged in ascending order, from the centroid closest to any of the
+focal points, to the furthest.
 
-        cents_in <- filter(cents, between(long_int, x[1], max_int))
-        return(cents_in)
-    }
+\hypertarget{allocation-of-centroids}{%
+\subsection{Allocation of centroids}\label{allocation-of-centroids}}
 
-    # LATITUDE ROWS FILTER
-    # amount of latitude in sliding window
-    lat_windows <- purrr::map(.x = nlat_list, .f = lat_window)
+The distance around a centroid to consider for possible hexagon
+locations is determined by the hex\_filter. It multiplies the amount
+given by hex\_filter, by the size of the hexagons to find the distance.
 
-    # find the min and max longitude for each latitude
-    range_rows <- purrr::map_dfr(.x = lat_windows,
-        .f = function(x) {x %>%
-                dplyr::summarise(
-                    long_min = ifelse(purrr::is_empty(long_int), NA, min(x$long_int)),
-                    long_max = ifelse(purrr::is_empty(long_int), NA, max(x$long_int))
-                )}
-    )
-```
+Allocation of all centroids can now take place using the set of polygon
+centroids and the hexagon map grid. For each polygon centroid, only the
+hexagon grid points that have not yet been used can be considered.
+Allocate each centroid, beginning with the closest centroid to a focal
+point. This will preserve spatial relationship with the capital, as the
+inner areas will be allowed closest to the captial, and the areas that
+are further will be accomodated after.
 
-The second rolling window function finds the average of the rolling minimum and rolling maximum centroid values, for the longitude columns and latitude rows.
+The filter parameter is used to subset possible grid points to only
+those surrounding the polygon centroid within the filter distance,
+smaller distance will increase speed, but can decrease accuracy.
 
-```{r echo = FALSE}
- # smooth the minimums
-    av_range_rows <- purrr::map_dfr(.x = nlat_list, .f = function(x, rows = range_rows) {
-        rows[x[1]:min(x[2], NROW(rows)),] %>%
-            dplyr::summarise(mean_long_min = mean(long_min, na.rm=T), mean_long_max = mean(long_max, na.rm=T))
-    }) %>%
-        bind_cols(lat_id = c(seq(1:nlat) +lat_size), .)
+The following example considers one of the Local Government Areas. These
+steps are repeated for each polygon.
 
-    # LONGITUDE COLS FILTER
-    long_windows <- purrr::map(.x = nlong_list, .f = long_window, centroids, nlong)
+\hypertarget{step-1-filter-the-grid-for-unassigned-hexagon-points}{%
+\subsubsection{Step 1: Filter the grid for unassigned hexagon
+points}\label{step-1-filter-the-grid-for-unassigned-hexagon-points}}
 
-    # find the min and max longitude for each latitude
-    range_cols <- purrr::map_dfr(.x = long_windows, .f = function(x) { x %>%
-            dplyr::summarise(
-                lat_min = ifelse(purrr::is_empty(lat_int), NA, min(x$lat_int)),
-                lat_max = ifelse(purrr::is_empty(lat_int), NA, max(x$lat_int))
-            )}
-    )
+Keep only the available hexagon points, this will prevent multiple areas
+being allocated to the same hexagon.
 
-    # smooth the minimums
-    av_range_cols <- purrr::map_dfr(.x = nlong_list, .f = function(x, cols = range_cols) {
-        cols[x[1]:min(x[2], NROW(cols)),] %>%
-            dplyr::summarise(mean_lat_min = mean(lat_min, na.rm=T), mean_lat_max = mean(lat_max, na.rm=T))
-    }) %>%
-        bind_cols(long_id = c(seq(1:nlong) + round(long_size/2)), .)
+\hypertarget{step-2-filter-the-grid-points-for-those-closest-to-the-centroid}{%
+\subsubsection{Step 2: Filter the grid points for those closest to the
+centroid}\label{step-2-filter-the-grid-points-for-those-closest-to-the-centroid}}
 
-```
-
-<!--
-Figure of rolling window construction
--->
-
-### Step 3: Filtering the grid
-
-Only the grid points between the rolling average of the minimum and maximum centroid values are kept, for each row and column of the grid.
-
-```{r echo = FALSE}
-    # APPLY A BUFFER
-    # change buffer to amount of hexagons (ints) either side
-    hex_buffer <- floor(buffer_dist/hex_size)
-
-    grid <- grid %>%
-        left_join(., av_range_rows, by = c("hex_lat_int" = "lat_id")) %>%
-        left_join(., av_range_cols, by = c("hex_long_int" = "long_id")) %>%
-        rowwise() %>%
-        mutate(long_buffer = ifelse(between(hex_long_int,mean_long_min - hex_buffer,
-            mean_long_max + hex_buffer), "in", "out")) %>%
-        mutate(lat_buffer = ifelse(between(hex_lat_int,mean_lat_min - hex_buffer,
-            mean_lat_max + hex_buffer), "in", "out")) %>%
-        filter(lat_buffer =="in" | long_buffer == "in")
-
-```
-
-```{r plot_buffer}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = full_grid, size = 0.25) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75)
-```
-
-## Centroid to focal point distance
-
-```{r split_centroids}
-# Split the centroid data set
-centroids <- centroids %>% 
-  nest(longitude, latitude) %>% 
-  mutate(closest = map(data, closest_focal_point, focal_points = capital_cities %>% filter(points == "Hobart"))) %>% 
-  unnest(data, closest) %>% 
-  arrange(focal_distance)
-```
-
-For each polygon centroid in the set, the distance to each of the focal points provided is recorded.
-The closest focal point name, the distance to the polygon centroid, and the angle from focal point to polygon centroid will be added to the polygon's row, in the polygon data set.
-To minimise time taken for this step, only Tasmania's capital city Hobart has been provided.
-
-The distance between the polygon centroid and it's closest focal point data set is used to order the data set for allocation.
-The points are arranged in ascending order, from the centroid closest to any of the focal points, to the furthest.
-
-## Allocation of centroids
-
-The distance around a centroid to consider for possible hexagon locations is determined by the hex_filter.
-It multiplies the amount given by hex_filter, by the size of the hexagons to find the distance.
-
-```{r}
-## Consider hexagon points up to a certain distance from centroid
-hex_filter <- 10
-```
-
-```{r}
-width = 15
-```
-
-```{r, eval = FALSE}
-hexmap_allocation <- allocate(centroids = centroids,
-        hex_grid = grid,
-        hex_size = hex_size,
-        hex_filter = hex_filter,
-        width = width,
-        focal_points = capital_cities,
-        verbose = TRUE,
-        id = sf_id)
-```
-
-Allocation of all centroids can now take place using the set of polygon centroids and the hexagon map grid. 
-For each polygon centroid, only the hexagon grid points that have not yet been used can be considered.
-Allocate each centroid, beginning with the closest centroid to a focal point.
-This will preserve spatial relationship with the capital, as the inner areas will be allowed closest to the captial, and the areas that are further will be accomodated after.
-
-```{r arrange}
-s_centroids <- centroids %>% arrange(focal_distance)
-
-s_centroids <- split(s_centroids, s_centroids[["focal_distance"]])
-
-# Set up allocation data frame
-centroid_allocation <- NULL
-```
-
-The filter parameter is used to subset possible grid points to only those surrounding the polygon centroid within the filter distance, smaller distance will increase speed, but can decrease accuracy.
-
-```{r orig_dist}
-# keep value to reset expanded distances
-expand_dist <- hex_filter
-```
-
-The following example considers one of the Local Government Areas. 
-These steps are repeated for each polygon.
-
-### Step 1: Filter the grid for unassigned hexagon points
-
-Keep only the available hexagon points, this will prevent multiple areas being allocated to the same hexagon.
-
-```{r available_points}
-# filter for only the available hex grid points
-hex_grid <- grid %>% filter(!assigned)
-```
-
-### Step 2: Filter the grid points for those closest to the centroid
-
-This will allow only the closest points, that are not assigned, to be considered.
-
-```{r close_points}
-# filter grid for avaiable points
-centroid1 <- centroids %>% head(1)
-
-flong <- centroid1$longitude
-flat <- centroid1$latitude
-
-hex_grid <- hex_grid %>% ungroup() %>%
-        filter(flat - buffer_dist < hex_lat & hex_lat < flat + buffer_dist) %>%
-        filter(flong - buffer_dist < hex_long & hex_long < flong + buffer_dist)
-
-```
+This will allow only the closest points, that are not assigned, to be
+considered.
 
@@
 
-```{r, echo = FALSE}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75)
+\begin{Schunk}
 
-```
+\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-12-1} \end{Schunk}
 
@@
 
-```{r}
-    hex_grid <- hex_grid %>%
-        rowwise %>%
-        mutate(
-        hex_lat_c = hex_lat - flat,
-        hex_long_c = hex_long - flong) %>%
-        mutate(hyp = ((hex_lat_c^2) + (hex_long_c^2))^(1/2))
+\begin{Schunk}
 
-        f_angle <- centroid1 %>%
-            mutate(atan = atan2(latitude-latitude1,longitude-longitude1),
-                angle = (atan*180/pi),
-                pangle = ifelse(angle<0, angle +360, angle)) %>% pull()
+\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-14-1} \end{Schunk}
 
-        hex_grid <- hex_grid %>%
-            # create circle of radius: hex_filter
-            filter(hyp < hex_filter) %>%
-            mutate(
-                # geosphere takes a long time
-                angle = f_angle,
-                angle_plus = (angle + width)%%360,
-                angle_minus = (angle - width)%%360,
-                atan = atan2(hex_lat_c, hex_long_c),
-                hex_angle = (atan*180/pi),
-                hex_angle = ifelse(hex_angle<0, hex_angle +360, hex_angle))
+Filter for angle within circle, relates hexagon location to focal point,
+Sydney.
 
-```
+\begin{Schunk}
 
-```{r, echo = FALSE}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75)
-```
+\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-16-1} \end{Schunk}
 
-Filter for angle within circle, relates hexagon location to focal point, Sydney.
+Using the angle between each polygon centroid, and it's the closest
+focal point, the subset of points is filtered again. Of these possible
+points, only those within a specific amount of degrees plus and minus a
+specific angle range are kept. This angle begins at 30 degrees by
+default, and may increase if necessary.
 
-```{r}
-# Filter for angle within circle
+If no available hexagon grid point is found within the original filter
+distance and angle, the distance is expanded, only when a maximum
+distance is reached will the angle expand to accommodate more possible
+grid points.
 
-        if (hex_grid$angle_minus[1] < hex_grid$angle_plus[1]) {
-            hex_grid <- hex_grid %>%
-                # create slice of 60 degrees from centroid
-                filter(angle_minus < hex_angle & hex_angle < angle_plus)
-        } else {
-            hex_grid <- hex_grid %>%
-                # create slice of 60 degrees from centroid
-                filter(hex_angle < angle_plus | angle_minus > hex_angle)
-        }
+The allocation is returned and combined with the data relating to each
+polygon.
 
-```
+\begin{Schunk}
 
-```{r}
+\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-19-1} \end{Schunk}
 
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75)
+\begin{Schunk}
 
-```
+\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-20-1} \end{Schunk}
 
-```{r}
+\hypertarget{applications-of-algorithm}{%
+\subsection{Applications of algorithm}\label{applications-of-algorithm}}
 
-# Choose first available point
-        cent <- centroid1 %>% dplyr::rename(focal_point = points, focal_dist = focal_distance, focal_angle = angle)
+Examples of Melbourne, lga, Australia At different levels, distance from
+original centroids, change in area
 
-        # Filter should give one hex point
-        hex <- hex_grid %>% 
-          ungroup %>% 
-          filter(hyp == min(hyp)) %>%
-          select(hex_long, hex_lat, hex_id = id)
-
-        #update grid to show this centroid as assigned
-        hex_grid[which(hex_grid$id == hex$hex_id),]$assigned <- TRUE
-
-        centroid_allocation <- bind_rows(centroid_allocation, dplyr::bind_cols(cent, hex)) %>% as_tibble()
-
-```
-
-Using the angle between each polygon centroid, and it's the closest focal point, the subset of points is filtered again.
-Of these possible points, only those within a specific amount of degrees plus and minus a specific angle range are kept. This angle begins at 30 degrees by default, and may increase if necessary.
-
-If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded, only when a maximum distance is reached will the angle expand to accommodate more possible grid points.
-
-The allocation is returned and combined with the data relating to each polygon.
-
-```{r}
-hex_points_df <- centroid_allocation %>% 
-  fortify_hexagon(hex_size = hex_size)
-```
-
-```{r}
-ggplot(hex_points_df) + 
-  geom_polygon(aes(x = long, y = lat, group = LGA_CODE16)) +
-  coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75)
-```
-
-```{r fullhexmap}
-# Create centroids set
-centroids <- create_centroids(tas_lga, "LGA_CODE16")
-# Create hexagon location grid
-grid <- create_grid(centroids = centroids, hex_size = 0.25, buffer_dist = 1.2)
-# Allocate polygon centroids to hexagon grid points
-hex_allocated <- allocate(centroids = centroids,
-hex_grid = grid,
-sf_id = "LGA_CODE16",
-hex_size = 0.25, # same size used in create_grid
-hex_filter = 10,
-focal_points = capital_cities,
-width = 30, verbose = FALSE) # same column used in create_centroids
-```
-
-```{r}
-h1 <- hex_allocated %>%
-  fortify_hexagon(hex_size = 0.25) %>% 
-  left_join(., tas_lga)
-
-p1 <- fortify_sfc(tas_lga)
-
-end_hex <- ggplot() +
-  geom_polygon(data = p1, aes(x=long, lat, group = group), alpha = 0.1) +
-  geom_polygon(data = h1, aes(x=long, lat, group = LGA_CODE16)) + theme_void() + coord_equal()
-
-gridExtra::grid.arrange(end_hex, end_cents)
-```
-
-## Applications of algorithm
-
-<!--
-Is  your  solution  always  working?  
-Can  you  prove it? 
-How does it work? 
--->
-
-Examples of Melbourne, lga, Australia
-At different levels, distance from original centroids, change in area
-
-LGA of all Australia
-SA2 for lga
-
-<!--
-Is your analysis about worst case or average case? 
-What kind of theoretical and analytical support can you give for your proposed scheme/solution? 
--->
+LGA of all Australia SA2 for lga
 
 \bibliography{algorithmbib}
+
+\address{%
+Stephanie Kobakian\\
+Queensland Univeristy of Technology\\
+\\
+}
+\href{mailto:stephanie.kobakian@monash.edu}{\nolinkurl{stephanie.kobakian@monash.edu}}
+
+\address{%
+Dianne Cook\\
+Monash University\\
+\\
+}
+\href{mailto:dicook@monash.edu}{\nolinkurl{dicook@monash.edu}}

### 2019-03-27 AusCancerAtlas.R
Australian Cancer Atlas maps data files

@@ -1,0 +1,37 @@
+library(sugarbag)
+library(absmapsdata)
+library(tidyverse)
+
+
+# Create centroids set
+centroids <- create_centroids(sa22011, "sa2_5dig_2011")
+# save(centroids, file = "data/sa22011/centroids.rda")
+
+# Create hexagon location grid
+grid <- create_grid(centroids = centroids, hex_size = 0.2, buffer_dist = 5)
+# save(grid, file = "data/sa22011/grid.rda")
+
+# Allocate polygon centroids to hexagon grid points
+allocated <- allocate(centroids = centroids,
+  hex_grid = grid,
+  sf_id = "sa2_5dig_2011",
+  hex_size = 0.2, # same size used in create_grid
+  hex_filter = 15,
+  width = 30,
+  focal_points = capital_cities,
+  verbose = TRUE) 
+
+#save(allocated, file = "data/sa22011/allocated.rda")
+
+hex_allocated <- create_hexmap(sa22011, sf_id = "sa2_5dig_2011",
+  focal_points = capital_cities,
+  verbose = TRUE)
+
+#save(hex_allocated, file = "data/sa22011/hex_allocated.rda")
+
+
+# same column used in create_centroids
+hexagons <- fortify_hexagon(data = allocated, sf_id = "sa2_5dig_2011", hex_size = 0.2)
+polygons <- fortify_sfc(sa22011, keep = 0.1)
+
+ggplot(hexagons) + geom_polygon(aes(x=long, y = lat, group = sa2_5dig_2011))

### 2019-03-27 algorithmRjournal/algorithmRjournal.Rmd
use filter dist for individual centroids

@@
 ```{r close_points}
+filter_dist <- hex_filter*hex_size
+
 # filter grid for avaiable points
@@
 hex_grid <- hex_grid %>% ungroup() %>%
-        filter(flat - buffer_dist < hex_lat & hex_lat < flat + buffer_dist) %>%
-        filter(flong - buffer_dist < hex_long & hex_long < flong + buffer_dist)
+        filter(flat - filter_dist < hex_lat & hex_lat < flat + filter_dist) %>%
+        filter(flong - filter_dist < hex_long & hex_long < flong + filter_dist)
 
@@
             # create circle of radius: hex_filter
-            filter(hyp < hex_filter) %>%
+            filter(hyp < filter_dist) %>%
             mutate(

### 2019-03-27 algorithmRjournal/algorithmRjournal.Rmd
Make plots more readable, need to add captions and figure numbers

@@
 end_cents <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids) + theme_void() + coord_equal()
+  geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids) + theme_void() + coord_equal()
 end_cents
@@
 
-hex_size <- 0.2
+hex_size <- 0.25
 
@@
 ```{r plot_grid}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
@@
 ```{r plot_shift}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
@@
 ```{r plot_buffer}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroids, fill = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = full_grid, size = 0.25) +
@@
 
-Create a box filter
+Create a box of possible hexagon locations areoung the centroid. The bottom of the box will not be square as the buffer has already removed unnecessary points from over the ocean.
 
 ```{r, echo = FALSE}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroid1, fill = "red") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
@@
 
-Create circle filter
+The algorithm removes the outer corners of the square, creating a cricle of points, by only keeping points within a certain radius around the original centroid location.
 
@@
 ```{r, echo = FALSE}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "#b2df8a") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
@@
 
-Filter for angle within circle, relates hexagon location to focal point, Sydney.
+The width parameter is now used.
+Of the remaining points, a slice is taken.
+This uses the angle from the closest capital city, to the current centroid.
+If it is not the closest to the capital there may have been points available that were taken by closer centroids.
+This allows the spatial relationship to be preserved, even when it gets allocated to a hexagon that is further from the city centre.
+This angle begins at 30 degrees by default, and may increase if necessary.
+
+If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded, only when a maximum distance is reached will the angle expand to accommodate more possible grid points.
+
+The allocation is returned and combined with the data relating to each polygon.
 
@@
         }
-
 ```
@@
 ```{r}
-
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", colour = "white") + geom_point(aes(x=longitude, y = latitude),data= centroid1, fill = "red") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75)
-
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75) + 
+  geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "#b2df8a", size = 0.8) 
 ```
 
+This area was the very closest to the Hobart central point ( coloured pink) provided in the capital cities data set, it gets a hexagon point (coloured blue) extremely close to it's centroid (coloured green).
+
 ```{r}
-
 # Choose first available point
@@
 
-        #update grid to show this centroid as assigned
+# Update grid to show this centroid as assigned
 hex_grid[which(hex_grid$id == hex$hex_id),]$assigned <- TRUE
 
+# Add to table of allocated centroids
 centroid_allocation <- bind_rows(centroid_allocation, dplyr::bind_cols(cent, hex)) %>% as_tibble()
@@
 ```
-
-Using the angle between each polygon centroid, and it's the closest focal point, the subset of points is filtered again.
-Of these possible points, only those within a specific amount of degrees plus and minus a specific angle range are kept. This angle begins at 30 degrees by default, and may increase if necessary.
-
-If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded, only when a maximum distance is reached will the angle expand to accommodate more possible grid points.
-
-The allocation is returned and combined with the data relating to each polygon.
 
@@
 ```{r}
-ggplot(hex_points_df) + 
-  geom_polygon(aes(x = long, y = lat, group = LGA_CODE16)) +
-  coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75)
+ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga %>% filter(LGA_CODE16=="62810"), fill = "grey", size = 0.3, colour = "lightgrey") +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75) + 
+  geom_point(aes(x=longitude1, y = latitude1), data = centroid1, colour = "#fb9a99", size = 1) + 
+  geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "#b2df8a", size = 0.8) + 
+  theme_void() +
+  coord_equal()
 ```
 
-```{r fullhexmap}
+The following code creates a map for all the Local Government Areas in Tasmania:
+
+```{r fullhexmapcode, echo = TRUE}
 # Create centroids set
@@
 # Create hexagon location grid
-grid <- create_grid(centroids = centroids, hex_size = 0.25, buffer_dist = 1.2)
+grid <- create_grid(centroids = centroids,
+    hex_size = 0.25,
+    buffer_dist = 1.2)
 # Allocate polygon centroids to hexagon grid points
-hex_allocated <- allocate(centroids = centroids,
+hex_allocated <- allocate(
+  centroids = centroids,
   hex_grid = grid,
   sf_id = "LGA_CODE16",
-hex_size = 0.25, # same size used in create_grid
+  # same column used in create_centroids
+  hex_size = 0.25,
+  # same size used in create_grid
   hex_filter = 10,
-focal_points = capital_cities,
-width = 30, verbose = FALSE) # same column used in create_centroids
+  focal_points = capital_cities %>% filter(points == "Hobart"),
+  width = 30,
+  verbose = FALSE
+)
 ```
 
-```{r}
+```{r, fig.height=2.5, fig.width = 5}
 h1 <- hex_allocated %>%
@@
 end_hex <- ggplot() +
-  geom_polygon(data = p1, aes(x=long, lat, group = group), alpha = 0.1) +
+  geom_polygon(data = p1, aes(x=long, lat, group = group), fill = "grey", size = 0.3, colour = "lightgrey") +
   geom_polygon(data = h1, aes(x=long, lat, group = LGA_CODE16)) + theme_void() + coord_equal()
 
-gridExtra::grid.arrange(end_hex, end_cents)
+gridExtra::grid.arrange(end_cents, end_hex, nrow = 1)
 ```
 
-## Applications of algorithm
+## Summary
 
-<!--
-Is  your  solution  always  working?  
-Can  you  prove it? 
-How does it work? 
--->
+It is possible to use alternative maps to communicate spatial distributions.
+Current methods do not always work for Australia due to the large gaps between denseley populated capital cities.
 
-Examples of Melbourne, lga, Australia
-At different levels, distance from original centroids, change in area
+## Code
 
-LGA of all Australia
-SA2 for lga
-
-<!--
-Is your analysis about worst case or average case? 
-What kind of theoretical and analytical support can you give for your proposed scheme/solution? 
--->
+This map algorithm is found in the `sugarbag` package, currently available on github: https://github.com/srkobakian/sugarbag
 

### 2019-03-27 algorithmRjournal/algorithmRjournal.tex
Make plots more readable, need to add captions and figure numbers

@@
 
-Create a box filter
+Create a box of possible hexagon locations areoung the centroid. The
+bottom of the box will not be square as the buffer has already removed
+unnecessary points from over the ocean.
 
@@
 
-Create circle filter
+The algorithm removes the outer corners of the square, creating a cricle
+of points, by only keeping points within a certain radius around the
+original centroid location.
 
@@
 
-Filter for angle within circle, relates hexagon location to focal point,
-Sydney.
-
-\begin{Schunk}
-
-\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-16-1} \end{Schunk}
-
-Using the angle between each polygon centroid, and it's the closest
-focal point, the subset of points is filtered again. Of these possible
-points, only those within a specific amount of degrees plus and minus a
-specific angle range are kept. This angle begins at 30 degrees by
-default, and may increase if necessary.
+The width parameter is now used. Of the remaining points, a slice is
+taken. This uses the angle from the closest capital city, to the current
+centroid. If it is not the closest to the capital there may have been
+points available that were taken by closer centroids. This allows the
+spatial relationship to be preserved, even when it gets allocated to a
+hexagon that is further from the city centre. This angle begins at 30
+degrees by default, and may increase if necessary.
 
@@
 
+\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-16-1} \end{Schunk}
+
+This area was the very closest to the Hobart central point ( coloured
+pink) provided in the capital cities data set, it gets a hexagon point
+(coloured blue) extremely close to it's centroid (coloured green).
+
+\begin{Schunk}
+
 \includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-19-1} \end{Schunk}
+
+The following code creates a map for all the Local Government Areas in
+Tasmania:
+
+\begin{Schunk}
+\begin{Sinput}
+# Create centroids set
+centroids <- create_centroids(tas_lga, "LGA_CODE16")
+# Create hexagon location grid
+grid <- create_grid(centroids = centroids,
+    hex_size = 0.25,
+    buffer_dist = 1.2)
+# Allocate polygon centroids to hexagon grid points
+hex_allocated <- allocate(
+  centroids = centroids,
+  hex_grid = grid,
+  sf_id = "LGA_CODE16",
+  # same column used in create_centroids
+  hex_size = 0.25,
+  # same size used in create_grid
+  hex_filter = 10,
+  focal_points = capital_cities %>% filter(points == "Hobart"),
+  width = 30,
+  verbose = FALSE
+)
+\end{Sinput}
+\end{Schunk}
 
@@
 
-\hypertarget{applications-of-algorithm}{%
-\subsection{Applications of algorithm}\label{applications-of-algorithm}}
+\hypertarget{summary}{%
+\subsection{Summary}\label{summary}}
 
-Examples of Melbourne, lga, Australia At different levels, distance from
-original centroids, change in area
+It is possible to use alternative maps to communicate spatial
+distributions. Current methods do not always work for Australia due to
+the large gaps between denseley populated capital cities.
 
-LGA of all Australia SA2 for lga
+\hypertarget{code}{%
+\subsection{Code}\label{code}}
+
+This map algorithm is found in the \texttt{sugarbag} package, currently
+available on github: \url{https://github.com/srkobakian/sugarbag}
 

### 2019-03-27 algorithmRjournal/algorithmRjournal.Rmd
Spell check

@@
 It allocates these hexagon in a manner that preserves the spatial relationship of the areas.
-It showcases spatial distributions, by emphasising the small geograhical regions that are often diffcult to locate on large geographic maps.
+It showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on large geographic maps.
 output:
@@
 
-Spatial distrbutions have utilised alternative representations of geography for many years.
+Spatial distributions have utilised alternative representations of geography for many years.
 In modern times interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, with a focus on public consumption.
@@
 Populations congregate around major cities and vertical living is increasingly common.
-Population statistics often requires dividing people into smaller, measureable areas.
-Government bodies such as the Australian Bureau of Statistics, or intentionally segregated organisations, like the Australian Electoral Comission hold the responsibility of the division.
+Population statistics often requires dividing people into smaller, measurable areas.
+Government bodies such as the Australian Bureau of Statistics, or intentionally segregated organisations, like the Australian Electoral Commission hold the responsibility of the division.
 Australia is an example of strong urbanisation, the rural areas are often sparsely populated in comparison to the urban centres.
-To divide the population equally, the square meterage of the geographic areas differ dramatically in size.
+To divide the population equally, the square meters of the geographic areas differ dramatically in size.
 
@@
 These maps rely on the statistic of interest to determine the layout, and for Australia, often fail to preserve a recognisable view.
-Tilegrams allow preservation of spatial relationships as they decrease the emphasis on the amount of geograhic area considered to be interesting.
+Tilegrams allow preservation of spatial relationships as they decrease the emphasis on the amount of geographic area considered to be interesting.
 These maps focus on the relationship between neighbours, in considering aggregated statistics of heterogeneous regions.
@@
 
-The centre of the population hubs are used to distribute areas around the closest captial city.
+The centre of the population hubs are used to distribute areas around the closest capital city.
 
@@
 The `read_shape` function can assist in creating this object.
-We will use the Loca Goverment Areas of Tasmania, sourced from the Australian Bureau of Statistics.
+We will use the Local Government Areas of Tasmania, sourced from the Australian Bureau of Statistics.
 
@@
 
-Each new hexagon will need to tesselate, a grid is created to ensure a close point is found, that will allow all areas to tesselate, this is inspired by tilegrams.
+Each new hexagon will need to tessellate, a grid is created to ensure a close point is found, that will allow all areas to tessellate, this is inspired by tilegrams.
 The grid of possible hexagon centroids can be made using the `create_grid` function.
@@
 Allocate each centroid, beginning with the closest centroid to a focal point.
-This will preserve spatial relationship with the capital, as the inner areas will be allowed closest to the captial, and the areas that are further will be accomodated after.
+This will preserve spatial relationship with the capital, as the inner areas will be allowed closest to the capital, and the areas that are further will be accommodated after.
 
@@
 
-Create a box of possible hexagon locations areoung the centroid. The bottom of the box will not be square as the buffer has already removed unnecessary points from over the ocean.
+Create a box of possible hexagon locations around the centroid. The bottom of the box will not be square as the buffer has already removed unnecessary points from over the ocean.
 
@@
 
-The algorithm removes the outer corners of the square, creating a cricle of points, by only keeping points within a certain radius around the original centroid location.
+The algorithm removes the outer corners of the square, creating a circle of points, by only keeping points within a certain radius around the original centroid location.
 
@@
 It is possible to use alternative maps to communicate spatial distributions.
-Current methods do not always work for Australia due to the large gaps between denseley populated capital cities.
+Current methods do not always work for Australia due to the large gaps between densely populated capital cities.
 

### 2019-03-27 algorithmRjournal/algorithmRjournal.tex
Spell check

@@
 the spatial relationship of the areas. It showcases spatial
-distributions, by emphasising the small geograhical regions that are
-often diffcult to locate on large geographic maps.
+distributions, by emphasising the small geographical regions that are
+often difficult to locate on large geographic maps.
 }
@@
 
-Spatial distrbutions have utilised alternative representations of
+Spatial distributions have utilised alternative representations of
 geography for many years. In modern times interactivity and animation
@@
 cities and vertical living is increasingly common. Population statistics
-often requires dividing people into smaller, measureable areas.
+often requires dividing people into smaller, measurable areas.
 Government bodies such as the Australian Bureau of Statistics, or
 intentionally segregated organisations, like the Australian Electoral
-Comission hold the responsibility of the division. Australia is an
+Commission hold the responsibility of the division. Australia is an
 example of strong urbanisation, the rural areas are often sparsely
 populated in comparison to the urban centres. To divide the population
-equally, the square meterage of the geographic areas differ dramatically
+equally, the square meters of the geographic areas differ dramatically
 in size.
@@
 view. Tilegrams allow preservation of spatial relationships as they
-decrease the emphasis on the amount of geograhic area considered to be
+decrease the emphasis on the amount of geographic area considered to be
 interesting. These maps focus on the relationship between neighbours, in
@@
 The centre of the population hubs are used to distribute areas around
-the closest captial city.
+the closest capital city.
 
@@
 column. The \texttt{read\_shape} function can assist in creating this
-object. We will use the Loca Goverment Areas of Tasmania, sourced from
+object. We will use the Local Government Areas of Tasmania, sourced from
 the Australian Bureau of Statistics.
@@
 
-Each new hexagon will need to tesselate, a grid is created to ensure a
-close point is found, that will allow all areas to tesselate, this is
+Each new hexagon will need to tessellate, a grid is created to ensure a
+close point is found, that will allow all areas to tessellate, this is
 inspired by tilegrams. The grid of possible hexagon centroids can be
@@
 point. This will preserve spatial relationship with the capital, as the
-inner areas will be allowed closest to the captial, and the areas that
-are further will be accomodated after.
+inner areas will be allowed closest to the capital, and the areas that
+are further will be accommodated after.
 
@@
 
-Create a box of possible hexagon locations areoung the centroid. The
+Create a box of possible hexagon locations around the centroid. The
 bottom of the box will not be square as the buffer has already removed
@@
 
-The algorithm removes the outer corners of the square, creating a cricle
+The algorithm removes the outer corners of the square, creating a circle
 of points, by only keeping points within a certain radius around the
@@
 distributions. Current methods do not always work for Australia due to
-the large gaps between denseley populated capital cities.
+the large gaps between densely populated capital cities.
 

### 2019-07-29 algorithmRjournal/algorithmRjournal.Rmd
Tasmania

@@
   - name: Stephanie Kobakian
-    affiliation: Queensland Univeristy of Technology
+    affiliation: Queensland University of Technology
     email:  stephanie.kobakian@monash.edu
@@
 Spatial distributions have utilised alternative representations of geography for many years.
-In modern times interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, with a focus on public consumption.
+In modern times, interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption.
 Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
 
-## Motivation
+<!-- Motivation to map -->
 
-Spatial distributions of people and human related statistics can be misrepresented in geographic maps.
-Populations congregate around major cities and vertical living is increasingly common.
-Population statistics often requires dividing people into smaller, measurable areas.
-Government bodies such as the Australian Bureau of Statistics, or intentionally segregated organisations, like the Australian Electoral Commission hold the responsibility of the division.
-Australia is an example of strong urbanisation, the rural areas are often sparsely populated in comparison to the urban centres.
-To divide the population equally, the square meters of the geographic areas differ dramatically in size.
+Choropleths are the current best practice approach for presenting geographical data as
+maps highlight the geographic patterns in geospatially related statistics [@SAMGIS].
+The land on the map space is divided to separate each area, these boundaries are usually administrative. The areas are filled with colour to represent the value of the statistic for the area [@EI].
 
-Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population.
-Alternative maps allow the focus to be placed on the distribution of the statistics between the groups of areas.
+<!-- urbanisation -->
+In Australia, government bodies such as the Australian Bureau of Statistics, or the Australian Electoral Commission hold the responsibility for the division of areas.
+These boundaries are often adjusted as the population in areas increase.
+Australian people are increasingly congregating around major cities, the rural areas are often sparsely populated in comparison to the urban centres.
+The division of the population into equal population areas results in dramatically different square meterage of the geographic areas. 
+This results in an unequal presentation of the statistic in each area, this can misrepresent the spatial distributions of the human related statistics in geographic maps.
 
-Extremely small geographic areas are lost on large geographic maps, small inner areas of Sydney or Melbourne are not easily compared at a high level.
-Cartograms place importance on the statistic of interest, allowing distorted map space on the display to represent differences in the statistic.
-These maps rely on the statistic of interest to determine the layout, and for Australia, often fail to preserve a recognisable view.
-Tilegrams allow preservation of spatial relationships as they decrease the emphasis on the amount of geographic area considered to be interesting.
-These maps focus on the relationship between neighbours, in considering aggregated statistics of heterogeneous regions.
+<!-- solutions -->
+Beginning with the geography, cartograms apply a transformation to place importance on the statistic of interest.
+They result in a distortion of the map space to represent differences in the statistic.
+These displays rely on the statistic of interest to determine the layout, however for Australia, many cartograms fail to preserve a recognisable display.
+Contiguous cartograms change the shape of an area, preserving neighbouring relationships. Non-contiguous cartograms maintain the shape of each area, but lose the connection to neighbours.
 
-Our case is an extension of these concepts.
+Alternative maps shift the focus from land area, to the value of the statistics in a group of areas.
+Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing each administrative area.
+
+Tilegrams are an extension of Dorling cartograms, using one simple shape to represnt each area.
+This allows preservation of spatial relationships and decreases the emphasis from the amount of geographic area.
+These maps focus on the relationship between neighbours attempting to preserve connections, and disregard the unique shapes of the administrative boundaries.
+
+The sugarbag package provides a new method to implement hexagon tilegrams. 
 Extending the tilegram to Australian applications required preserving the spatial relationships.
-It emphasises the capital cities as population hubs, and recognises the populations distributed across the large rural areas.
+It emphasises the capital cities as population hubs, and recognises the distances between locations of populations distributed across the large rural areas.
 
@@
 
-Our solution operates on a set of polygons.
+This solution operates on a set of `sf` [@sf] polygons.
+
+There are four necessary tasks to create a hexagon tilegram.
+These steps can be executed by the main function, `create_hexmap`, or can be applied separately for more flexibility.
+
+They perform the following tasks:
+ - Create the set of centroids to allocate
+ - Create the set of hexagons to use
+ - Allocate each centroid to an available hexagon
+ - Transform the data for plotting
+
+```{r, eval = FALSE}
+tibble::tibble(
+  Step = c("1", "2", "3", "4"),
+  Task = c("Create the set of centroids to allocate",
+    "Create the set of hexagons to use", 
+    "Allocate each centroid to an available hexagon",
+    "Transform the data for plotting"),
+  #Function = c("create_centroids", "create_grid", "allocate", "fortify_hexagon"),
+  Input = 
+    c("1", "2", "3",
+    "Allocated hexagons, identifying column, size of hexagons"),
+  Output = c("1", "2", "3", "Fortified data frame")
+  )
+```
+
 There are parameters used in the process that may be provided, or will be automatically derived.
-All necessary functions are exported, with a main function `create_hexmap` used to step through these automatically.
 
-## Parameters
+### Use the sugarbag package
+
+```{r libraries}
+# To install sugarbag:
+# devtools::install_github("srkobakian/sugarbag")
+library(sugarbag)
+
+library(tidyverse)
+```
+
+### Parameters
 
 The `create_hexmap` function requires several parameters, if they are not provided, the information will be derived from the polygon set used.
+If users already have a grid and set of centroids they may choose to only use the `allocate` function.
 
@@
 knitr::kable(tibble::tibble(parameter = c('shp', 
-  'shp_path',
   'sf_id',
-  'capital_cities'),
-  description = c('an Rdata object containing the polygon information', 'character string location of the shape file that contains the polygon information', 'name of a unique column that distinguishes areas',
+  'focal_points'),
+  description = c(
+    'an sf object containing the polygon information', 
+    'name of a column that distinguishes unique areas',
     'a data frame of reference locations used to allocate hexagons'
     )), format = "latex")
-
 ```
 
-```{r libraries}
-library(tidyverse)
-# To install sugarbag:
-# devtools::install_github("srkobakian/sugarbag")
-library(sugarbag)
-```
+### Example data
 
-The polygon set of Local Government Areas in Tasmania in 2016 is stored in the sugarbag package data as `tas_lga`. 
-A single column of the data set must be used as a unique identifier of areas. In this case, the unique LGA codes associated with each LGA have been used, their names could have also been used.
+The polygon set of Local Government Areas of Tasmania in 2016 is provided with the sugarbag package as `tas_lga`. 
+A single column of the data set must be used as a unique identifier of areas. In this case, the unique LGA codes associated with each LGA have been used.
 
-```{r id}
-sf_id <- "LGA_CODE16"
-```
+The longitude and latitude centre of the capital cities of Australia are used to  allocate areas around the closest capital city.
 
-The centre of the population hubs are used to distribute areas around the closest capital city.
-
-```{r data}
+```{r capital_cities}
 data(capital_cities)
@@
 knitr::kable(tibble(parameter = c('buffer_dist', 'hex_size',  'hex_filter', 'width'),
-  description = c('a float value for distance in degrees to extend beyond the - geometry provided',
+  description = c('a float value for distance in degrees to extend beyond the geometry provided',
     'a float value in degrees for the diameter of the hexagons', 'amount of hexagons around centroid to consider for allocation',
@@
 
+## Create the set of centroid points
+
 When utilising individual `sugarbag` functions, we recommend the following approach:
-
-## Polygon Information
-
 Begin with a set of polygons.
 The set should be provided as an `sf` object, this is a data frame containing a `geometry` column.
-The `read_shape` function can assist in creating this object.
-We will use the Local Government Areas of Tasmania, sourced from the Australian Bureau of Statistics.
+^[The `read_shape` function can assist in creating this object.] We will use the Local Government Areas of Tasmania, downloaded from the Australian Bureau of Statistics.
 
-```{r}
-# Create a suitable data set for plotting
-fort_lga <- fortify_sfc(tas_lga)
-
-# Include area variable
-area_var <- fort_lga %>% 
-  distinct(LGA_CODE16, .keep_all = TRUE) %>% 
-  select(LGA_CODE16, AREASQKM16)
-```
+The centroids can be derived from the set of polygons:
 
@@
 ## Use the create_centroids function to find polygon centroids:
-centroids <- create_centroids(shp_sf = tas_lga, sf_id = sf_id) %>%
-  left_join(., select(area_var, LGA_CODE16, AREASQKM16), by = "LGA_CODE16")
+centroids <- create_centroids(shp_sf = tas_lga, sf_id = "LGA_CODE16")
+## Join to data for each area
+centroids <- left_join(centroids, as_tibble(tas_lga), by = "LGA_CODE16")
+
 ```
 
-```{r, fig.cap="lga Local Government Areas and derived centroids."}
-end_cents <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids) + theme_void() + coord_equal()
-end_cents
+```{r end_cents, fig.cap="Local Government Areas and derived centroids.", fig.height = 3.5, fig.width = 7}
+fort_lga <- fortify_sfc(tas_lga)
+polys <- ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") +theme_void() + coord_equal()
 
-#ggplot() + geom_histogram(aes(x = log(AREASQKM16), fill = log(AREASQKM16)), data= centroids, bins = 20) 
+cents <- ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids) + theme_void() + coord_equal()
+
+gridExtra::grid.arrange(polys, cents, nrow = 1)
 ```
@@
 
-Each new hexagon will need to tessellate, a grid is created to ensure a close point is found, that will allow all areas to tessellate, this is inspired by tilegrams.
+A tilegram allows areas to be allocated to a tellesated set of tiles.
+The grid is created to ensure a close point is found, that ensures tessellation with other previously allocated points.
+
 The grid of possible hexagon centroids can be made using the `create_grid` function.
-The grid creation takes several steps.
-It requires the centroids, the hexagon size and the buffer distance.
+The grid creation requires several steps.
+It uses the centroids, the hexagon size and the buffer distance.
 
@@
 
-hex_size <- 0.25
+hex_size = 0.3
 
@@
 
-One sequence is created for longitude columns, and another for latitude rows.
+A sequence is created for longitude columns, and another for latitude rows.
 
-The sequences begin at the minimum longitude or latitude, minus the buffer distance.
-Equally spaced intervals the size of the hexagons are created up to the maximum longitude or latitude, plus the buffer distance.
+The sequences begin at the minimum longitude (latitude), minus the buffer distance.
+Equally spaced intervals the size of the hexagons are created up to the maximum longitude (latitude), plus the buffer distance.
 
@@
 ```{r plot_grid}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
+grid1 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
@@
 ```{r plot_shift}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
+grid2 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
@@
 
+```{r, fig.cap="Grid points to create a tilegram.", fig.height = 3.5, fig.width = 7}
+gridExtra::grid.arrange(grid1, grid2, nrow = 1)
+```
+
 ### Step 2: Rolling windows
 
-Not all of the grid points will be used, especially if islands impact the overall space covered.
+Not all of the grid points will be used, especially if islands result in a large grid space.
 To filter the grid for appropriate points for allocation,
 the `create_buffer` function is called from `create_grid`.
-It finds the amount of columns and rows needed to best capture the set of centroids.
+It finds the grid points needed to best capture the set of centroids.
 
@@
 The rows and columns are divided into 20 groups.
-The amount of rows in each latitude group and the amount of columns in each longitude group are then used as the width of manual rolling windows.
-This will tailor the available points to the areas most likely to be used.
-It helps reduce amount of time taken.
+The amount of rows in each latitude group and the amount of columns in each longitude group are then used as the width of rolling windows.
+This will tailor the available grid points to the most likely to be used point.
+It also helps reduce amount of time taken, as it decreases the amount of points considered.
 
@@
 
-The specific rows and columns in the rolling windows are defined.The first rolling window function finds the minimum and maximum centroid values for the sliding groups of longitude columns and the groups of latitude rows.
+The first rolling window function finds the minimum and maximum centroid values for the sliding groups of longitude columns and the groups of latitude rows.
 
@@
     lat_windows <- purrr::map(.x = nlat_list, .f = lat_window)
+    # LONGITUDE COLS FILTER
+    long_windows <- purrr::map(.x = nlong_list, .f = long_window)
 
@@
     )
-```
-
-The second rolling window function finds the average of the rolling minimum and rolling maximum centroid values, for the longitude columns and latitude rows.
-
-```{r echo = FALSE}
- # smooth the minimums
-    av_range_rows <- purrr::map_dfr(.x = nlat_list, .f = function(x, rows = range_rows) {
-        rows[x[1]:min(x[2], NROW(rows)),] %>%
-            dplyr::summarise(mean_long_min = mean(long_min, na.rm=T), mean_long_max = mean(long_max, na.rm=T))
-    }) %>%
-        bind_cols(lat_id = c(seq(1:nlat) +lat_size), .)
-
-    # LONGITUDE COLS FILTER
-    long_windows <- purrr::map(.x = nlong_list, .f = long_window, centroids, nlong)
 
@@
     )
+```
+
+The second rolling window function finds the average of the rolling centroid values minimum and maximum, for the longitude columns and latitude rows.
+
+```{r echo = FALSE}
+ # smooth the minimums
+    av_range_rows <- purrr::map_dfr(.x = nlat_list, .f = function(x, rows = range_rows) {
+        rows[x[1]:min(x[2], NROW(rows)),] %>%
+            dplyr::summarise(mean_long_min = mean(long_min, na.rm=T), mean_long_max = mean(long_max, na.rm=T))
+    }) %>%
+        bind_cols(lat_id = c(seq(1:nlat) + lat_size), .)
 
@@
     }) %>%
-        bind_cols(long_id = c(seq(1:nlong) + round(long_size/2)), .)
+        bind_cols(long_id = c(seq(1:nlong) + long_size + round(long_size/2)), .)
 
@@
 ```{r plot_buffer}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = full_grid, size = 0.25) +
@@
 centroids <- centroids %>% 
+  select(-geometry) %>% 
   nest(longitude, latitude) %>% 
@@
 
-```{r}
-## Consider hexagon points up to a certain distance from centroid
-hex_filter <- 10
-```
-
-```{r}
-width = 15
-```
-
 ```{r, eval = FALSE}
-hexmap_allocation <- allocate(centroids = centroids,
+hexmap_allocation <- allocate(
+  centroids = centroids,
+  sf_id = "LGA_CODE16",
   hex_grid = grid,
-        hex_size = hex_size,
-        hex_filter = hex_filter,
-        width = width,
+  hex_size = 0.2, # same size used in create_grid
+  hex_filter = 10,
+  width = 35,
   focal_points = capital_cities,
-        verbose = TRUE,
-        id = sf_id)
+  verbose = TRUE
+)
 ```
@@
 ```{r orig_dist}
+hex_filter = 10
+width = 35
 # keep value to reset expanded distances
@@
 ```{r, echo = FALSE}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroid1, fill = "red") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroid1, fill = "red") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
@@
 ```{r, echo = FALSE}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "#b2df8a") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "#b2df8a") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
@@
 ```{r}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + theme_void() + coord_equal() +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
@@
 hex_points_df <- centroid_allocation %>% 
-  fortify_hexagon(hex_size = hex_size)
+  fortify_hexagon(hex_size = hex_size,
+  sf_id = "LGA_CODE16")
 ```
@@
 ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = group), data = fort_lga %>% filter(LGA_CODE16=="62810"), fill = "grey", size = 0.3, colour = "lightgrey") +
+  geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga %>% filter(LGA_CODE16=="62810"), fill = "grey", size = 0.3, colour = "lightgrey") +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75) + 
@@
 grid <- create_grid(centroids = centroids,
-    hex_size = 0.25,
+    hex_size = 0.3,
     buffer_dist = 1.2)
@@
   # same column used in create_centroids
-  hex_size = 0.25,
+  hex_size = 0.3,
   # same size used in create_grid
@@
   focal_points = capital_cities %>% filter(points == "Hobart"),
-  width = 30,
+  width = 35,
   verbose = FALSE
@@
 h1 <- hex_allocated %>%
-  fortify_hexagon(hex_size = 0.25) %>% 
+  fortify_hexagon(hex_size = 0.3, 
+  sf_id = "LGA_CODE16") %>% 
   left_join(., tas_lga)
@@
 p1 <- fortify_sfc(tas_lga)
-
 end_hex <- ggplot() +
-  geom_polygon(data = p1, aes(x=long, lat, group = group), fill = "grey", size = 0.3, colour = "lightgrey") +
+  geom_polygon(data = p1, aes(x=long, lat, group = interaction(LGA_NAME16, polygon)), fill = "grey", size = 0.3, colour = "lightgrey") +
   geom_polygon(data = h1, aes(x=long, lat, group = LGA_CODE16)) + theme_void() + coord_equal()
 
-gridExtra::grid.arrange(end_cents, end_hex, nrow = 1)
+gridExtra::grid.arrange(cents, end_hex, nrow = 1)
 ```

### 2019-07-29 algorithmRjournal/algorithmRjournal.tex
Tasmania

@@
 Spatial distributions have utilised alternative representations of
-geography for many years. In modern times interactivity and animation
+geography for many years. In modern times, interactivity and animation
 have begun to play a larger role, as alternative representations have
-been popularised by online news sites, with a focus on public
-consumption. Applications are increasingly widespread, especially in the
-areas of disease mapping, and election results.
+been popularised by online news sites, and atlas websites with a focus
+on public consumption. Applications are increasingly widespread,
+especially in the areas of disease mapping, and election results.
 
-\hypertarget{motivation}{%
-\subsection{Motivation}\label{motivation}}
+Choropleths are the current best practice approach for presenting
+geographical data as maps highlight the geographic patterns in
+geospatially related statistics {[}@SAMGIS{]}. The land on the map space
+is divided to separate each area, these boundaries are usually
+administrative. The areas are filled with colour to represent the value
+of the statistic for the area {[}@EI{]}.
 
-Spatial distributions of people and human related statistics can be
-misrepresented in geographic maps. Populations congregate around major
-cities and vertical living is increasingly common. Population statistics
-often requires dividing people into smaller, measurable areas.
-Government bodies such as the Australian Bureau of Statistics, or
-intentionally segregated organisations, like the Australian Electoral
-Commission hold the responsibility of the division. Australia is an
-example of strong urbanisation, the rural areas are often sparsely
-populated in comparison to the urban centres. To divide the population
-equally, the square meters of the geographic areas differ dramatically
-in size.
+In Australia, government bodies such as the Australian Bureau of
+Statistics, or the Australian Electoral Commission hold the
+responsibility for the division of areas. These boundaries are often
+adjusted as the population in areas increase. Australian people are
+increasingly congregating around major cities, the rural areas are often
+sparsely populated in comparison to the urban centres. The division of
+the population into equal population areas results in dramatically
+different square meterage of the geographic areas. This results in an
+unequal presentation of the statistic in each area, this can
+misrepresent the spatial distributions of the human related statistics
+in geographic maps.
 
-Alternative mapping methods allow increased understanding of the spatial
-distribution of a variable across the population. Alternative maps allow
-the focus to be placed on the distribution of the statistics between the
-groups of areas.
+Beginning with the geography, cartograms apply a transformation to place
+importance on the statistic of interest. They result in a distortion of
+the map space to represent differences in the statistic. These displays
+rely on the statistic of interest to determine the layout, however for
+Australia, many cartograms fail to preserve a recognisable display.
+Contiguous cartograms change the shape of an area, preserving
+neighbouring relationships. Non-contiguous cartograms maintain the shape
+of each area, but lose the connection to neighbours.
 
-Extremely small geographic areas are lost on large geographic maps,
-small inner areas of Sydney or Melbourne are not easily compared at a
-high level. Cartograms place importance on the statistic of interest,
-allowing distorted map space on the display to represent differences in
-the statistic. These maps rely on the statistic of interest to determine
-the layout, and for Australia, often fail to preserve a recognisable
-view. Tilegrams allow preservation of spatial relationships as they
-decrease the emphasis on the amount of geographic area considered to be
-interesting. These maps focus on the relationship between neighbours, in
-considering aggregated statistics of heterogeneous regions.
+Alternative maps shift the focus from land area, to the value of the
+statistics in a group of areas. Alternative mapping methods allow
+increased understanding of the spatial distribution of a variable across
+the population, by fairly representing each administrative area.
 
-Our case is an extension of these concepts. Extending the tilegram to
-Australian applications required preserving the spatial relationships.
-It emphasises the capital cities as population hubs, and recognises the
+Tilegrams are an extension of Dorling cartograms, using one simple shape
+to represnt each area. This allows preservation of spatial relationships
+and decreases the emphasis from the amount of geographic area. These
+maps focus on the relationship between neighbours attempting to preserve
+connections, and disregard the unique shapes of the administrative
+boundaries.
+
+The sugarbag package provides a new method to implement hexagon
+tilegrams. Extending the tilegram to Australian applications required
+preserving the spatial relationships. It emphasises the capital cities
+as population hubs, and recognises the distances between locations of
 populations distributed across the large rural areas.
@@
 
-Our solution operates on a set of polygons. There are parameters used in
-the process that may be provided, or will be automatically derived. All
-necessary functions are exported, with a main function
-\texttt{create\_hexmap} used to step through these automatically.
+This solution operates on a set of \texttt{sf} {[}@sf{]} polygons.
+
+There are four necessary tasks to create a hexagon tilegram. These steps
+can be executed by the main function, \texttt{create\_hexmap}, or can be
+applied separately for more flexibility.
+
+They perform the following tasks: - Create the set of centroids to
+allocate - Create the set of hexagons to use - Allocate each centroid to
+an available hexagon - Transform the data for plotting
+
+There are parameters used in the process that may be provided, or will
+be automatically derived.
+
+\hypertarget{use-the-sugarbag-package}{%
+\subsubsection{Use the sugarbag
+package}\label{use-the-sugarbag-package}}
 
 \hypertarget{parameters}{%
-\subsection{Parameters}\label{parameters}}
+\subsubsection{Parameters}\label{parameters}}
 
@@
 they are not provided, the information will be derived from the polygon
-set used.
+set used. If users already have a grid and set of centroids they may
+choose to only use the \texttt{allocate} function.
 
@@
 \hline
-shp & an Rdata object containing the polygon information\\
+shp & an sf object containing the polygon information\\
 \hline
-shp\_path & character string location of the shape file that contains the polygon information\\
+sf\_id & name of a column that distinguishes unique areas\\
 \hline
-sf\_id & name of a unique column that distinguishes areas\\
-\hline
-capital\_cities & a data frame of reference locations used to allocate hexagons\\
+focal\_points & a data frame of reference locations used to allocate hexagons\\
 \hline
@@
 
-The polygon set of Local Government Areas in Tasmania in 2016 is stored
-in the sugarbag package data as \texttt{tas\_lga}. A single column of
-the data set must be used as a unique identifier of areas. In this case,
-the unique LGA codes associated with each LGA have been used, their
-names could have also been used.
+\hypertarget{example-data}{%
+\subsubsection{Example data}\label{example-data}}
 
-The centre of the population hubs are used to distribute areas around
-the closest capital city.
+The polygon set of Local Government Areas of Tasmania in 2016 is
+provided with the sugarbag package as \texttt{tas\_lga}. A single column
+of the data set must be used as a unique identifier of areas. In this
+case, the unique LGA codes associated with each LGA have been used.
+
+The longitude and latitude centre of the capital cities of Australia are
+used to allocate areas around the closest capital city.
 
@@
 \hline
-buffer\_dist & a float value for distance in degrees to extend beyond the - geometry provided\\
+buffer\_dist & a float value for distance in degrees to extend beyond the geometry provided\\
 \hline
@@
 
+\hypertarget{create-the-set-of-centroid-points}{%
+\subsection{Create the set of centroid
+points}\label{create-the-set-of-centroid-points}}
+
 When utilising individual \texttt{sugarbag} functions, we recommend the
-following approach:
+following approach: Begin with a set of polygons. The set should be
+provided as an \texttt{sf} object, this is a data frame containing a
+\texttt{geometry} column. \footnote{The \texttt{read\_shape} function
+  can assist in creating this object.} We will use the Local Government
+Areas of Tasmania, downloaded from the Australian Bureau of Statistics.
 
-\hypertarget{polygon-information}{%
-\subsection{Polygon Information}\label{polygon-information}}
-
-Begin with a set of polygons. The set should be provided as an
-\texttt{sf} object, this is a data frame containing a \texttt{geometry}
-column. The \texttt{read\_shape} function can assist in creating this
-object. We will use the Local Government Areas of Tasmania, sourced from
-the Australian Bureau of Statistics.
+The centroids can be derived from the set of polygons:
 
@@
 \begin{figure}
-\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-3-1} \caption[lga Local Government Areas and derived centroids]{lga Local Government Areas and derived centroids.}\label{fig:unnamed-chunk-3}
+\includegraphics{algorithmRjournal_files/figure-latex/end_cents-1} \caption[Local Government Areas and derived centroids]{Local Government Areas and derived centroids.}\label{fig:end_cents}
 \end{figure}
@@
 
-Each new hexagon will need to tessellate, a grid is created to ensure a
-close point is found, that will allow all areas to tessellate, this is
-inspired by tilegrams. The grid of possible hexagon centroids can be
-made using the \texttt{create\_grid} function. The grid creation takes
-several steps. It requires the centroids, the hexagon size and the
-buffer distance.
+A tilegram allows areas to be allocated to a tellesated set of tiles.
+The grid is created to ensure a close point is found, that ensures
+tessellation with other previously allocated points.
+
+The grid of possible hexagon centroids can be made using the
+\texttt{create\_grid} function. The grid creation requires several
+steps. It uses the centroids, the hexagon size and the buffer distance.
 
@@
 
-One sequence is created for longitude columns, and another for latitude
+A sequence is created for longitude columns, and another for latitude
 rows.
 
-The sequences begin at the minimum longitude or latitude, minus the
+The sequences begin at the minimum longitude (latitude), minus the
 buffer distance. Equally spaced intervals the size of the hexagons are
-created up to the maximum longitude or latitude, plus the buffer
+created up to the maximum longitude (latitude), plus the buffer
 distance.
@@
 
-\begin{Schunk}
-
-\includegraphics{algorithmRjournal_files/figure-latex/plot_grid-1} \end{Schunk}
-
 A square grid will not facilitate tessellated hexagons. Every second
@@
 
+Each point is now given an ID.
+
 \begin{Schunk}
-
-\includegraphics{algorithmRjournal_files/figure-latex/plot_shift-1} \end{Schunk}
-
-Each point is now given an ID.
+\begin{figure}
+\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-3-1} \caption[Grid points to create a tilegram]{Grid points to create a tilegram.}\label{fig:unnamed-chunk-3}
+\end{figure}
+\end{Schunk}
 
@@
 
-Not all of the grid points will be used, especially if islands impact
-the overall space covered. To filter the grid for appropriate points for
+Not all of the grid points will be used, especially if islands result in
+a large grid space. To filter the grid for appropriate points for
 allocation, the \texttt{create\_buffer} function is called from
-\texttt{create\_grid}. It finds the amount of columns and rows needed to
-best capture the set of centroids.
+\texttt{create\_grid}. It finds the grid points needed to best capture
+the set of centroids.
 
@@
 each latitude group and the amount of columns in each longitude group
-are then used as the width of manual rolling windows. This will tailor
-the available points to the areas most likely to be used. It helps
-reduce amount of time taken.
+are then used as the width of rolling windows. This will tailor the
+available grid points to the most likely to be used point. It also helps
+reduce amount of time taken, as it decreases the amount of points
+considered.
 
-The specific rows and columns in the rolling windows are defined.The
-first rolling window function finds the minimum and maximum centroid
+The first rolling window function finds the minimum and maximum centroid
 values for the sliding groups of longitude columns and the groups of
@@
 The second rolling window function finds the average of the rolling
-minimum and rolling maximum centroid values, for the longitude columns
-and latitude rows.
+centroid values minimum and maximum, for the longitude columns and
+latitude rows.
 
@@
 
-\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-12-1} \end{Schunk}
+\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-10-1} \end{Schunk}
 
@@
 
-\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-14-1} \end{Schunk}
+\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-12-1} \end{Schunk}
 
@@
 
-\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-16-1} \end{Schunk}
+\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-14-1} \end{Schunk}
 
@@
 
-\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-19-1} \end{Schunk}
+\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-17-1} \end{Schunk}
 
@@
 
-\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-20-1} \end{Schunk}
+\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-18-1} \end{Schunk}
 
@@
 Stephanie Kobakian\\
-Queensland Univeristy of Technology\\
+Queensland University of Technology\\
 \\

### 2019-07-30 algorithmRjournal/algorithmRjournal.Rmd
join figures

@@
     email:  dicook@monash.edu
+bibliography: RJreferences.bib
+link-citations: true
+fig_caption: yes
 abstract: >
@@
 It showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on large geographic maps.
+Spatial distributions have been presented on alternative representations of geography for many years.
+In modern times, interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption.
+Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
 output:
@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE,
-  cache = FALSE,
-  message = FALSE,
-  warning = FALSE,
-  fig.height = 3, fig.width = 3)
+```{r cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+library(knitcitations)
+library(RefManageR)
+knitr::opts_chunk$set(echo=FALSE, 
+                      message=FALSE, 
+                      warning=FALSE, 
+                      kfigr.link=TRUE, 
+                      kfigr.prefix=TRUE, 
+                      cache=TRUE, 
+                      fig.cap=TRUE)
+
+options("citation_format" = "pandoc")
+BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')
 ```
@@
 ## Introduction
-
-Spatial distributions have utilised alternative representations of geography for many years.
-In modern times, interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption.
-Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
 
@@
 
-This solution operates on a set of `sf` [@sf] polygons.
+This solution operates on a set of \CRANpkg{sf} [@sf] polygons.
 
@@
 
-```{r, eval = FALSE}
+```{r tasks, eval = FALSE}
 tibble::tibble(
@@
 
-The polygon set of Local Government Areas of Tasmania in 2016 is provided with the sugarbag package as `tas_lga`. 
+The polygon set of Local Government Areas of Tasmania in 2016 is provided with the \CRANpkg{sugarbag} package as `tas_lga`. 
 A single column of the data set must be used as a unique identifier of areas. In this case, the unique LGA codes associated with each LGA have been used.
@@
 
-```{r}
+```{r parameters}
 knitr::kable(tibble(parameter = c('buffer_dist', 'hex_size',  'hex_filter', 'width'),
@@
 
-```{r centroids}
+```{r derive_centroids}
 ## Use the create_centroids function to find polygon centroids:
@@
 ## Join to data for each area
-centroids <- left_join(centroids, as_tibble(tas_lga), by = "LGA_CODE16")
-
+centroids <- left_join(centroids,
+  sf::st_drop_geometry(tas_lga), by = "LGA_CODE16")
 ```
 
-```{r end_cents, fig.cap="Local Government Areas and derived centroids.", fig.height = 3.5, fig.width = 7}
+```{r end_cents, fig.cap="Local Government Areas and derived centroids.", fig.height=2.5, fig.width = 5}
 fort_lga <- fortify_sfc(tas_lga)
@@
 
-```{r, fig.cap="Grid points to create a tilegram.", fig.height = 3.5, fig.width = 7}
+```{r, fig.cap="Grid points to create a tilegram.", fig.height=2.5, fig.width = 5}
 gridExtra::grid.arrange(grid1, grid2, nrow = 1)
@@
 
-```{r}
+```{r windows}
 nlong <- length(unique(grid$hex_long))
@@
 
-```{r echo = FALSE}
+```{r sizes, echo = FALSE}
 # Amount of lats and longs in each group
@@
 
-```{r echo = FALSE}
+```{r rolling_windows, echo = FALSE}
  # make a list of groups, manual sliding windows
@@
 
-```{r echo = FALSE}
+```{r rolling_ave, echo = FALSE}
  # smooth the minimums
@@
 
-```{r echo = FALSE}
+```{r filter_grid, echo = FALSE}
     # APPLY A BUFFER
@@
 
-```
-
-```{r plot_buffer}
 ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
@@
 centroids <- centroids %>% 
-  select(-geometry) %>% 
   nest(longitude, latitude) %>% 
@@
 
-```{r, eval = FALSE}
+```{r centroids, eval = FALSE}
 hexmap_allocation <- allocate(
@@
 
-```{r, echo = FALSE}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroid1, fill = "red") + theme_void() + coord_equal() +
+```{r plot_buffer, echo = FALSE}
+buff1 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroid1, fill = "red") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75)
-
 ```
@@
 
-```{r}
+```{r buffer_circle}
     hex_grid <- hex_grid %>%
@@
 
-```{r, echo = FALSE}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "#b2df8a") + theme_void() + coord_equal() +
+```{r plot_circle, echo = FALSE}
+buff2 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "#b2df8a") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75)
+```
+
+```{r buffers, fig.height=2.5, fig.width = 5}
+gridExtra::grid.arrange(buff1, buff2, nrow=1)
 ```
@@
 
-```{r}
+```{r buffer_slice}
 # Filter for angle within circle
@@
 
-```{r}
+```{r plot_slice}
 ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + theme_void() + coord_equal() +
@@
 
-```{r}
+```{r choose_point}
 # Choose first available point
@@
 
-```{r}
+```{r allocated}
 hex_points_df <- centroid_allocation %>% 
@@
 
-```{r}
+```{r plot_allocated}
 ggplot() + 
@@
 
-```{r fullhexmapcode, echo = TRUE}
+```{r full_hexmapcode, echo = TRUE}
 # Create centroids set
@@
 
-```{r, fig.height=2.5, fig.width = 5}
+```{r plot_final, fig.height=2.5, fig.width = 5}
 h1 <- hex_allocated %>%
@@
 
+@R
+
 \bibliography{algorithmbib}

### 2019-07-30 algorithmRjournal/algorithmRjournal.tex
join figures

@@
 distributions, by emphasising the small geographical regions that are
-often difficult to locate on large geographic maps.
+often difficult to locate on large geographic maps. Spatial
+distributions have been presented on alternative representations of
+geography for many years. In modern times, interactivity and animation
+have begun to play a larger role, as alternative representations have
+been popularised by online news sites, and atlas websites with a focus
+on public consumption. Applications are increasingly widespread,
+especially in the areas of disease mapping, and election results.
 }
@@
 
-Spatial distributions have utilised alternative representations of
-geography for many years. In modern times, interactivity and animation
-have begun to play a larger role, as alternative representations have
-been popularised by online news sites, and atlas websites with a focus
-on public consumption. Applications are increasingly widespread,
-especially in the areas of disease mapping, and election results.
-
 Choropleths are the current best practice approach for presenting
 geographical data as maps highlight the geographic patterns in
-geospatially related statistics {[}@SAMGIS{]}. The land on the map space
-is divided to separate each area, these boundaries are usually
+geospatially related statistics (Moore and Carpenter
+\protect\hyperlink{ref-SAMGIS}{1999}). The land on the map space is
+divided to separate each area, these boundaries are usually
 administrative. The areas are filled with colour to represent the value
-of the statistic for the area {[}@EI{]}.
+of the statistic for the area (Tufte \protect\hyperlink{ref-EI}{1990}).
 
@@
 
-This solution operates on a set of \texttt{sf} {[}@sf{]} polygons.
+This solution operates on a set of \CRANpkg{sf} (Pebesma
+\protect\hyperlink{ref-sf}{2019}) polygons.
 
@@
 
+\begin{Schunk}
+\begin{Sinput}
+tibble::tibble(
+  Step = c("1", "2", "3", "4"),
+  Task = c("Create the set of centroids to allocate",
+    "Create the set of hexagons to use", 
+    "Allocate each centroid to an available hexagon",
+    "Transform the data for plotting"),
+  #Function = c("create_centroids", "create_grid", "allocate", "fortify_hexagon"),
+  Input = 
+    c("1", "2", "3",
+    "Allocated hexagons, identifying column, size of hexagons"),
+  Output = c("1", "2", "3", "Fortified data frame")
+  )
+\end{Sinput}
+\end{Schunk}
+
 There are parameters used in the process that may be provided, or will
@@
 package}\label{use-the-sugarbag-package}}
+
+\begin{Schunk}
+\begin{Sinput}
+# To install sugarbag:
+# devtools::install_github("srkobakian/sugarbag")
+library(sugarbag)
+
+library(tidyverse)
+\end{Sinput}
+\begin{Soutput}
+#> Registered S3 methods overwritten by 'ggplot2':
+#>   method         from 
+#>   [.quosures     rlang
+#>   c.quosures     rlang
+#>   print.quosures rlang
+\end{Soutput}
+\begin{Soutput}
+#> Registered S3 method overwritten by 'rvest':
+#>   method            from
+#>   read_xml.response xml2
+\end{Soutput}
+\begin{Soutput}
+#> -- Attaching packages --------------------------------------------------- tidyverse 1.2.1 --
+\end{Soutput}
+\begin{Soutput}
+#> v ggplot2 3.1.1       v purrr   0.3.2  
+#> v tibble  2.1.1       v dplyr   0.8.0.1
+#> v tidyr   0.8.3       v stringr 1.4.0  
+#> v readr   1.3.1       v forcats 0.4.0
+\end{Soutput}
+\begin{Soutput}
+#> -- Conflicts ------------------------------------------------------ tidyverse_conflicts() --
+#> x dplyr::filter() masks stats::filter()
+#> x dplyr::lag()    masks stats::lag()
+\end{Soutput}
+\end{Schunk}
 
@@
 \begin{Schunk}
+\begin{Sinput}
+knitr::kable(tibble::tibble(parameter = c('shp', 
+  'sf_id',
+  'focal_points'),
+  description = c(
+    'an sf object containing the polygon information', 
+    'name of a column that distinguishes unique areas',
+    'a data frame of reference locations used to allocate hexagons'
+    )), format = "latex")
+\end{Sinput}
 
@@
 The polygon set of Local Government Areas of Tasmania in 2016 is
-provided with the sugarbag package as \texttt{tas\_lga}. A single column
-of the data set must be used as a unique identifier of areas. In this
-case, the unique LGA codes associated with each LGA have been used.
+provided with the \CRANpkg{sugarbag} package as \texttt{tas\_lga}. A
+single column of the data set must be used as a unique identifier of
+areas. In this case, the unique LGA codes associated with each LGA have
+been used.
 
@@
 used to allocate areas around the closest capital city.
+
+\begin{Schunk}
+\begin{Sinput}
+data(capital_cities)
+\end{Sinput}
+\end{Schunk}
 
@@
 \begin{Schunk}
+\begin{Sinput}
+knitr::kable(tibble(parameter = c('buffer_dist', 'hex_size',  'hex_filter', 'width'),
+  description = c('a float value for distance in degrees to extend beyond the geometry provided',
+    'a float value in degrees for the diameter of the hexagons', 'amount of hexagons around centroid to consider for allocation',
+    'the angle used to filter the grid points around a centroid')), format = "latex")
+\end{Sinput}
 
@@
 provided as an \texttt{sf} object, this is a data frame containing a
-\texttt{geometry} column. \footnote{The \texttt{read\_shape} function
-  can assist in creating this object.} We will use the Local Government
+\texttt{geometry} column.\footnote{The \texttt{read\_shape} function can
+  assist in creating this object.} We will use the Local Government
 Areas of Tasmania, downloaded from the Australian Bureau of Statistics.
@@
 \begin{Schunk}
+\begin{Sinput}
+## Use the create_centroids function to find polygon centroids:
+centroids <- create_centroids(shp_sf = tas_lga, sf_id = "LGA_CODE16")
+\end{Sinput}
+\begin{Soutput}
+#> Warning in st_centroid.sf(.): st_centroid assumes attributes are constant
+#> over geometries of x
+\end{Soutput}
+\begin{Soutput}
+#> Warning in st_centroid.sfc(st_geometry(x), of_largest_polygon =
+#> of_largest_polygon): st_centroid does not give correct centroids for
+#> longitude/latitude data
+\end{Soutput}
+\begin{Sinput}
+## Join to data for each area
+centroids <- left_join(centroids,
+  sf::st_drop_geometry(tas_lga), by = "LGA_CODE16")
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+fort_lga <- fortify_sfc(tas_lga)
+polys <- ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") +theme_void() + coord_equal()
+
+cents <- ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids) + theme_void() + coord_equal()
+
+gridExtra::grid.arrange(polys, cents, nrow = 1)
+\end{Sinput}
 \begin{figure}
@@
 
+\begin{Schunk}
+\begin{Sinput}
+## create the bounding box from the set of polygon centroids:
+bbox <- tibble::tibble(min = c(min(centroids$longitude, na.rm = TRUE), min(centroids$latitude, na.rm = TRUE)),
+        max = c(max(centroids$longitude, na.rm = TRUE), max(centroids$latitude, na.rm = TRUE)))
+
+hex_size = 0.3
+
+# default size calculation:
+#(bbox$max[1] - bbox$min[1])/(bbox$max[2] - bbox$min[2]) / 5
+
+buffer_dist <- max((bbox$max[1] - bbox$min[1]), (bbox$max[2] - bbox$min[2]))*0.3
+\end{Sinput}
+\end{Schunk}
+
 \hypertarget{step-1-expand-the-grid}{%
@@
 
+\begin{Schunk}
+\begin{Sinput}
+grid <- tibble::as_tibble(
+  expand.grid(
+    hex_long = seq(bbox$min[1] - buffer_dist, # minimum
+      bbox$max[1] + buffer_dist, # maximum
+      hex_size), # distance between hexagons
+    hex_lat = seq(bbox$min[2] - buffer_dist, # minimum
+      bbox$max[2] + buffer_dist, # maximum
+      hex_size))) # distance between hexagons
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+grid1 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
+\end{Sinput}
+\end{Schunk}
+
 A square grid will not facilitate tessellated hexagons. Every second
@@
 
+\begin{Schunk}
+\begin{Sinput}
+# Find every second latitude
+shift_lat <- grid %>% dplyr::select(hex_lat) %>%
+    dplyr::distinct() %>%
+    dplyr::filter(dplyr::row_number() %% 2 == 1) %>% unlist()
+
+# Shift the longitude of every second latitude to the right to make hex structure
+grid <- grid %>%
+    dplyr::mutate(hex_long = ifelse(hex_lat %in% shift_lat, hex_long,
+        hex_long + (hex_size / 2))) %>%
+    dplyr::mutate(id=1:NROW(.)) %>%
+    dplyr::mutate(assigned=FALSE)
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+grid2 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
+\end{Sinput}
+\end{Schunk}
+
 Each point is now given an ID.
@@
 \begin{Schunk}
+\begin{Sinput}
+full_grid <- grid <- grid %>%
+    mutate(hex_long_int = dense_rank(hex_long)-1,
+        hex_lat_int = dense_rank(hex_lat)-1)
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+gridExtra::grid.arrange(grid1, grid2, nrow = 1)
+\end{Sinput}
 \begin{figure}
-\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-3-1} \caption[Grid points to create a tilegram]{Grid points to create a tilegram.}\label{fig:unnamed-chunk-3}
+\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-2-1} \caption[Grid points to create a tilegram]{Grid points to create a tilegram.}\label{fig:unnamed-chunk-2}
 \end{figure}
@@
 the set of centroids.
+
+\begin{Schunk}
+\begin{Sinput}
+nlong <- length(unique(grid$hex_long))
+nlat <- length(unique(grid$hex_lat))
+
+centroids <- centroids %>%
+  mutate(long_int = round((longitude-min(grid$hex_long))/(max(grid$hex_long)-min(grid$hex_long))*nlong, 0),
+          lat_int = round((latitude-min(grid$hex_lat))/(max(grid$hex_lat)-min(grid$hex_lat))*nlat, 0))
+\end{Sinput}
+\end{Schunk}
 
@@
 
-\includegraphics{algorithmRjournal_files/figure-latex/plot_buffer-1} \end{Schunk}
+\includegraphics{algorithmRjournal_files/figure-latex/filter_grid-1} \end{Schunk}
 
@@
 distance}\label{centroid-to-focal-point-distance}}
+
+\begin{Schunk}
+\begin{Sinput}
+# Split the centroid data set
+centroids <- centroids %>% 
+  nest(longitude, latitude) %>% 
+  mutate(closest = map(data, closest_focal_point, focal_points = capital_cities %>% filter(points == "Hobart"))) %>% 
+  unnest(data, closest) %>% 
+  arrange(focal_distance)
+\end{Sinput}
+\end{Schunk}
 
@@
 
+\begin{Schunk}
+\begin{Sinput}
+hexmap_allocation <- allocate(
+  centroids = centroids,
+  sf_id = "LGA_CODE16",
+  hex_grid = grid,
+  hex_size = 0.2, # same size used in create_grid
+  hex_filter = 10,
+  width = 35,
+  focal_points = capital_cities,
+  verbose = TRUE
+)
+\end{Sinput}
+\end{Schunk}
+
 Allocation of all centroids can now take place using the set of polygon
@@
 
+\begin{Schunk}
+\begin{Sinput}
+s_centroids <- centroids %>% arrange(focal_distance)
+
+s_centroids <- split(s_centroids, s_centroids[["focal_distance"]])
+
+# Set up allocation data frame
+centroid_allocation <- NULL
+\end{Sinput}
+\end{Schunk}
+
 The filter parameter is used to subset possible grid points to only
@@
 smaller distance will increase speed, but can decrease accuracy.
+
+\begin{Schunk}
+\begin{Sinput}
+hex_filter = 10
+width = 35
+# keep value to reset expanded distances
+expand_dist <- hex_filter
+\end{Sinput}
+\end{Schunk}
 
@@
 
+\begin{Schunk}
+\begin{Sinput}
+# filter for only the available hex grid points
+hex_grid <- grid %>% filter(!assigned)
+\end{Sinput}
+\end{Schunk}
+
 \hypertarget{step-2-filter-the-grid-points-for-those-closest-to-the-centroid}{%
@@
 
+\begin{Schunk}
+\begin{Sinput}
+filter_dist <- hex_filter*hex_size
+
+# filter grid for avaiable points
+centroid1 <- centroids %>% head(1)
+
+flong <- centroid1$longitude
+flat <- centroid1$latitude
+
+hex_grid <- hex_grid %>% ungroup() %>%
+        filter(flat - filter_dist < hex_lat & hex_lat < flat + filter_dist) %>%
+        filter(flong - filter_dist < hex_long & hex_long < flong + filter_dist)
+\end{Sinput}
+\end{Schunk}
+
 Create a box of possible hexagon locations around the centroid. The
@@
 unnecessary points from over the ocean.
-
-\begin{Schunk}
-
-\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-10-1} \end{Schunk}
 
@@
 \begin{Schunk}
+\begin{Sinput}
+    hex_grid <- hex_grid %>%
+        rowwise %>%
+        mutate(
+        hex_lat_c = hex_lat - flat,
+        hex_long_c = hex_long - flong) %>%
+        mutate(hyp = ((hex_lat_c^2) + (hex_long_c^2))^(1/2))
 
-\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-12-1} \end{Schunk}
+        f_angle <- centroid1 %>%
+            mutate(atan = atan2(latitude-latitude1,longitude-longitude1),
+                angle = (atan*180/pi),
+                pangle = ifelse(angle<0, angle +360, angle)) %>% pull()
+
+        hex_grid <- hex_grid %>%
+            # create circle of radius: hex_filter
+            filter(hyp < filter_dist) %>%
+            mutate(
+                # geosphere takes a long time
+                angle = f_angle,
+                angle_plus = (angle + width)%%360,
+                angle_minus = (angle - width)%%360,
+                atan = atan2(hex_lat_c, hex_long_c),
+                hex_angle = (atan*180/pi),
+                hex_angle = ifelse(hex_angle<0, hex_angle +360, hex_angle))
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+gridExtra::grid.arrange(buff1, buff2, nrow=1)
+\end{Sinput}
+
+\includegraphics{algorithmRjournal_files/figure-latex/buffers-1} \end{Schunk}
 
@@
 \begin{Schunk}
+\begin{Sinput}
+# Filter for angle within circle
 
-\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-14-1} \end{Schunk}
+        if (hex_grid$angle_minus[1] < hex_grid$angle_plus[1]) {
+            hex_grid <- hex_grid %>%
+                # create slice of 60 degrees from centroid
+                filter(angle_minus < hex_angle & hex_angle < angle_plus)
+        } else {
+            hex_grid <- hex_grid %>%
+                # create slice of 60 degrees from centroid
+                filter(hex_angle < angle_plus | angle_minus > hex_angle)
+        }
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + theme_void() + coord_equal() +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75) + 
+  geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "#b2df8a", size = 0.8) 
+\end{Sinput}
+
+\includegraphics{algorithmRjournal_files/figure-latex/plot_slice-1} \end{Schunk}
 
@@
 \begin{Schunk}
+\begin{Sinput}
+# Choose first available point
+cent <- centroid1 %>% dplyr::rename(focal_point = points, focal_dist = focal_distance, focal_angle = angle)
 
-\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-17-1} \end{Schunk}
+# Filter should give one hex point
+hex <- hex_grid %>% 
+  ungroup %>% 
+  filter(hyp == min(hyp)) %>%
+  select(hex_long, hex_lat, hex_id = id)
+
+# Update grid to show this centroid as assigned
+hex_grid[which(hex_grid$id == hex$hex_id),]$assigned <- TRUE
+
+# Add to table of allocated centroids
+centroid_allocation <- bind_rows(centroid_allocation, dplyr::bind_cols(cent, hex)) %>% as_tibble()
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+hex_points_df <- centroid_allocation %>% 
+  fortify_hexagon(hex_size = hex_size,
+  sf_id = "LGA_CODE16")
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga %>% filter(LGA_CODE16=="62810"), fill = "grey", size = 0.3, colour = "lightgrey") +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75) + 
+  geom_point(aes(x=longitude1, y = latitude1), data = centroid1, colour = "#fb9a99", size = 1) + 
+  geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "#b2df8a", size = 0.8) + 
+  theme_void() +
+  coord_equal()
+\end{Sinput}
+
+\includegraphics{algorithmRjournal_files/figure-latex/plot_allocated-1} \end{Schunk}
 
@@
 centroids <- create_centroids(tas_lga, "LGA_CODE16")
+\end{Sinput}
+\begin{Soutput}
+#> Warning in st_centroid.sf(.): st_centroid assumes attributes are constant
+#> over geometries of x
+\end{Soutput}
+\begin{Soutput}
+#> Warning in st_centroid.sfc(st_geometry(x), of_largest_polygon =
+#> of_largest_polygon): st_centroid does not give correct centroids for
+#> longitude/latitude data
+\end{Soutput}
+\begin{Sinput}
 # Create hexagon location grid
@@
 \end{Sinput}
+\begin{Soutput}
+#> Allocating centroids, in order of distance to closest focal point.
+\end{Soutput}
 \end{Schunk}
@@
 \begin{Schunk}
+\begin{Sinput}
+h1 <- hex_allocated %>%
+  fortify_hexagon(hex_size = 0.3, 
+  sf_id = "LGA_CODE16") %>% 
+  left_join(., tas_lga)
+\end{Sinput}
+\begin{Soutput}
+#> Joining, by = "LGA_CODE16"
+\end{Soutput}
+\begin{Soutput}
+#> Warning: Column `LGA_CODE16` joining character vector and factor, coercing
+#> into character vector
+\end{Soutput}
+\begin{Sinput}
+p1 <- fortify_sfc(tas_lga)
+end_hex <- ggplot() +
+  geom_polygon(data = p1, aes(x=long, lat, group = interaction(LGA_NAME16, polygon)), fill = "grey", size = 0.3, colour = "lightgrey") +
+  geom_polygon(data = h1, aes(x=long, lat, group = LGA_CODE16)) + theme_void() + coord_equal()
 
-\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-18-1} \end{Schunk}
+gridExtra::grid.arrange(cents, end_hex, nrow = 1)
+\end{Sinput}
+
+\includegraphics{algorithmRjournal_files/figure-latex/plot_final-1} \end{Schunk}
 
@@
 
+R Core Team (\protect\hyperlink{ref-R}{2012})
+
 \bibliography{algorithmbib}
+
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-SAMGIS}{}%
+Moore, Dale A., and Tim E. Carpenter. 1999. ``Spatial Analytical Methods
+and Geographic Information Systems: Use in Health Research and
+Epidemiology.'' \emph{Epidemiologic Reviews} 21 (2): 143--61.
+\url{https://doi.org/10.1093/oxfordjournals.epirev.a017993}.
+
+\leavevmode\hypertarget{ref-sf}{}%
+Pebesma, Edzer. 2019. \emph{Sf: Simple Features for R}.
+\url{https://CRAN.R-project.org/package=sf}.
+
+\leavevmode\hypertarget{ref-R}{}%
+R Core Team. 2012. \emph{R: A Language and Environment for Statistical
+Computing}. Vienna, Austria: R Foundation for Statistical Computing.
+\url{http://www.R-project.org/}.
+
+\leavevmode\hypertarget{ref-EI}{}%
+Tufte, Edward R. 1990. \emph{Envisioning Information}. Graphics Press.
+
+\bibliography{RJreferences.bib}
 

### 2019-07-30 algorithmRjournal/algorithmRjournal.Rmd
Four tasks

@@
 
-The sugarbag package provides a new method to implement hexagon tilegrams. 
+The \CRANpkg{sugarbag} package provides a new method to implement hexagon tilegrams. 
 Extending the tilegram to Australian applications required preserving the spatial relationships.
@@
 
-There are four necessary tasks to create a hexagon tilegram.
+There are four tasks to create a hexagon tilegram.
 These steps can be executed by the main function, `create_hexmap`, or can be applied separately for more flexibility.
 
-They perform the following tasks:
- - Create the set of centroids to allocate
- - Create the set of hexagons to use
- - Allocate each centroid to an available hexagon
- - Transform the data for plotting
+ 1. Create the set of centroids to allocate
+ 2. Create the set of hexagons to use
+ 3. Allocate each centroid to an available hexagon
+ 4. Transform the data for plotting
 
-```{r tasks, eval = FALSE}
-tibble::tibble(
-  Step = c("1", "2", "3", "4"),
-  Task = c("Create the set of centroids to allocate",
-    "Create the set of hexagons to use", 
-    "Allocate each centroid to an available hexagon",
-    "Transform the data for plotting"),
-  #Function = c("create_centroids", "create_grid", "allocate", "fortify_hexagon"),
-  Input = 
-    c("1", "2", "3",
-    "Allocated hexagons, identifying column, size of hexagons"),
-  Output = c("1", "2", "3", "Fortified data frame")
-  )
-```
+There are parameters used in the process that can be provided, if they are not, they will be automatically derived.
 
-There are parameters used in the process that may be provided, or will be automatically derived.
-
-### Use the sugarbag package
+### Install sugarbag package
 
@@
 
-### Example data
+### Tasmania example
 
-The polygon set of Local Government Areas of Tasmania in 2016 is provided with the \CRANpkg{sugarbag} package as `tas_lga`. 
-A single column of the data set must be used as a unique identifier of areas. In this case, the unique LGA codes associated with each LGA have been used.
+The polygon set of Local Government Areas (LGA) of Tasmania in 2016 is provided with the \CRANpkg{sugarbag} package as `tas_lga`. 
+A single column of the data set must be used to identify the unique areas. 
+In this case, the unique LGA codes associated with each LGA have been used.
 
-The longitude and latitude centre of the capital cities of Australia are used to  allocate areas around the closest capital city.
+The longitude and latitude centre of the capital cities of Australia are used to  allocate areas around the closest capital city, as this example uses only the areas in the state of Tasmania, Hobart will be the common focal point.
 
@@
 
-**The following parameters will be determined within `create_hexmap` if not provided. They are created throughout the following example:**
+**The following parameters will be determined within `create_hexmap` if they are not provided. They are created throughout the following example:**
 
@@
 
-## Hexagon grid
+## Create the hexagon grid points
 
@@
 
-## Allocation of centroids
+## Allocate each centroids to a hexagon grid point
 

### 2019-07-30 algorithmRjournal/algorithmRjournal.tex
Four tasks

@@
 
-The sugarbag package provides a new method to implement hexagon
-tilegrams. Extending the tilegram to Australian applications required
-preserving the spatial relationships. It emphasises the capital cities
-as population hubs, and recognises the distances between locations of
-populations distributed across the large rural areas.
+The \CRANpkg{sugarbag} package provides a new method to implement
+hexagon tilegrams. Extending the tilegram to Australian applications
+required preserving the spatial relationships. It emphasises the capital
+cities as population hubs, and recognises the distances between
+locations of populations distributed across the large rural areas.
 
@@
 
-There are four necessary tasks to create a hexagon tilegram. These steps
-can be executed by the main function, \texttt{create\_hexmap}, or can be
+There are four tasks to create a hexagon tilegram. These steps can be
+executed by the main function, \texttt{create\_hexmap}, or can be
 applied separately for more flexibility.
 
-They perform the following tasks: - Create the set of centroids to
-allocate - Create the set of hexagons to use - Allocate each centroid to
-an available hexagon - Transform the data for plotting
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Create the set of centroids to allocate
+\item
+  Create the set of hexagons to use
+\item
+  Allocate each centroid to an available hexagon
+\item
+  Transform the data for plotting
+\end{enumerate}
 
-\begin{Schunk}
-\begin{Sinput}
-tibble::tibble(
-  Step = c("1", "2", "3", "4"),
-  Task = c("Create the set of centroids to allocate",
-    "Create the set of hexagons to use", 
-    "Allocate each centroid to an available hexagon",
-    "Transform the data for plotting"),
-  #Function = c("create_centroids", "create_grid", "allocate", "fortify_hexagon"),
-  Input = 
-    c("1", "2", "3",
-    "Allocated hexagons, identifying column, size of hexagons"),
-  Output = c("1", "2", "3", "Fortified data frame")
-  )
-\end{Sinput}
-\end{Schunk}
+There are parameters used in the process that can be provided, if they
+are not, they will be automatically derived.
 
-There are parameters used in the process that may be provided, or will
-be automatically derived.
-
-\hypertarget{use-the-sugarbag-package}{%
-\subsubsection{Use the sugarbag
-package}\label{use-the-sugarbag-package}}
+\hypertarget{install-sugarbag-package}{%
+\subsubsection{Install sugarbag
+package}\label{install-sugarbag-package}}
 
@@
 
-\hypertarget{example-data}{%
-\subsubsection{Example data}\label{example-data}}
+\hypertarget{tasmania-example}{%
+\subsubsection{Tasmania example}\label{tasmania-example}}
 
-The polygon set of Local Government Areas of Tasmania in 2016 is
+The polygon set of Local Government Areas (LGA) of Tasmania in 2016 is
 provided with the \CRANpkg{sugarbag} package as \texttt{tas\_lga}. A
-single column of the data set must be used as a unique identifier of
-areas. In this case, the unique LGA codes associated with each LGA have
-been used.
+single column of the data set must be used to identify the unique areas.
+In this case, the unique LGA codes associated with each LGA have been
+used.
 
 The longitude and latitude centre of the capital cities of Australia are
-used to allocate areas around the closest capital city.
+used to allocate areas around the closest capital city, as this example
+uses only the areas in the state of Tasmania, Hobart will be the common
+focal point.
 

### 2019-07-30 algorithmRjournal/algorithmRjournal.Rmd
Hide table code

@@
 **The following must be provided to `create_hexmap`:**
-```{r table_necessary}
+```{r table_necessary, echo = FALSE}
 knitr::kable(tibble::tibble(parameter = c('shp', 
@@
 
-```{r parameters}
+```{r parameters, echo = FALSE}
 knitr::kable(tibble(parameter = c('buffer_dist', 'hex_size',  'hex_filter', 'width'),

### 2019-07-30 algorithmRjournal/algorithmRjournal.tex
Hide table code

@@
 \begin{Schunk}
-\begin{Sinput}
-knitr::kable(tibble::tibble(parameter = c('shp', 
-  'sf_id',
-  'focal_points'),
-  description = c(
-    'an sf object containing the polygon information', 
-    'name of a column that distinguishes unique areas',
-    'a data frame of reference locations used to allocate hexagons'
-    )), format = "latex")
-\end{Sinput}
 
@@
 \textbf{The following parameters will be determined within
-\texttt{create\_hexmap} if not provided. They are created throughout the
-following example:}
+\texttt{create\_hexmap} if they are not provided. They are created
+throughout the following example:}
 
 \begin{Schunk}
-\begin{Sinput}
-knitr::kable(tibble(parameter = c('buffer_dist', 'hex_size',  'hex_filter', 'width'),
-  description = c('a float value for distance in degrees to extend beyond the geometry provided',
-    'a float value in degrees for the diameter of the hexagons', 'amount of hexagons around centroid to consider for allocation',
-    'the angle used to filter the grid points around a centroid')), format = "latex")
-\end{Sinput}
 
@@
 
-\hypertarget{hexagon-grid}{%
-\subsection{Hexagon grid}\label{hexagon-grid}}
+\hypertarget{create-the-hexagon-grid-points}{%
+\subsection{Create the hexagon grid
+points}\label{create-the-hexagon-grid-points}}
 
@@
 
-\hypertarget{allocation-of-centroids}{%
-\subsection{Allocation of centroids}\label{allocation-of-centroids}}
+\hypertarget{allocate-each-centroids-to-a-hexagon-grid-point}{%
+\subsection{Allocate each centroids to a hexagon grid
+point}\label{allocate-each-centroids-to-a-hexagon-grid-point}}
 

### 2019-07-30 algorithmRjournal/algorithmRjournal.Rmd
remove cache folder

@@
 
-```{r cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
+```{r cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, comment = FALSE}
 library(knitcitations)
@@
                       cache=TRUE, 
-                      fig.cap=TRUE)
+                      fig.cap=TRUE, comment = FALSE)
 

### 2019-07-30 algorithmRjournal/algorithmRjournal.Rmd
Cleaned file

@@
 There are four tasks to create a hexagon tilegram.
-These steps can be executed by the main function, `create_hexmap`, or can be applied separately for more flexibility.
+These steps can be executed by the main function, `create_hexmap`, or can be implemented separately for more flexibility.
 
@@
 
-```{r libraries}
+```{r libraries, message=FALSE, warning=FALSE, comment = FALSE}
 # To install sugarbag:
@@
 library(sugarbag)
-
 library(tidyverse)
@@
 
-The `create_hexmap` function requires several parameters, if they are not provided, the information will be derived from the polygon set used.
+The `create_hexmap` function requires several parameters, if they are not provided, the information will be derived from the \CRANpkg{sf} set of shapes used.
 If users already have a grid and set of centroids they may choose to only use the `allocate` function.
 
-**The following must be provided to `create_hexmap`:**
+*The following must be provided to `create_hexmap`:*
 ```{r table_necessary, echo = FALSE}
@@
 The centroids can be derived from the set of polygons:
-
-```{r derive_centroids}
+```{r cents, message=FALSE, warning=FALSE, comment = FALSE}
+centroids <- create_centroids(shp_sf = tas_lga, sf_id = "LGA_CODE16")
+```
+```{r derive_centroids, echo = FALSE}
 ## Use the create_centroids function to find polygon centroids:
-centroids <- create_centroids(shp_sf = tas_lga, sf_id = "LGA_CODE16")
 ## Join to data for each area
@@
 
-```{r end_cents, fig.cap="Local Government Areas and derived centroids.", fig.height=2.5, fig.width = 5}
+```{r end_cents, fig.cap="Local Government Areas and derived centroids.", fig.height=2.5, fig.width = 5, echo = FALSE}
 fort_lga <- fortify_sfc(tas_lga)
@@
 
-```{r bbox}
+```{r}
+grid <- create_grid(centroids = centroids, hex_size = 0.2, buffer_dist = 1.2)
+```
+
+```{r bbox, echo = FALSE}
 ## create the bounding box from the set of polygon centroids:
@@
 A sequence is created for longitude columns, and another for latitude rows.
-
 The sequences begin at the minimum longitude (latitude), minus the buffer distance.
 Equally spaced intervals the size of the hexagons are created up to the maximum longitude (latitude), plus the buffer distance.
-
 An individual point is created from all intersections of the longitude columns and latitude row sequences.
-
-```{r grid}
+```{r grid, echo = FALSE}
 grid <- tibble::as_tibble(
@@
       hex_size))) # distance between hexagons
-```
 
-```{r plot_grid}
 grid1 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
@@
 ```
-
 A square grid will not facilitate tessellated hexagons. Every second latitude row of points will be shifted right by half of the hexagon size.
-
-```{r shift}
+```{r shift, echo = FALSE}
 # Find every second latitude
@@
     dplyr::mutate(assigned=FALSE)
-```
 
-```{r plot_shift}
 grid2 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75)
-```
 
-Each point is now given an ID.
-
-```{r grid_id}
 full_grid <- grid <- grid %>%
@@
 
-```{r, fig.cap="Grid points to create a tilegram.", fig.height=2.5, fig.width = 5}
+```{r, fig.cap="Grid points to create a tilegram.", fig.height=2.5, fig.width = 5, echo = FALSE}
 gridExtra::grid.arrange(grid1, grid2, nrow = 1)
@@
 
-```{r windows}
+```{r windows, echo = FALSE}
 nlong <- length(unique(grid$hex_long))
@@
 ```
-
 <!--
@@
 -->
-
 ### Step 3: Filtering the grid
@@
 
-```{r filter_grid, echo = FALSE}
+```{r filter_grid, echo = FALSE, fig.height = 2.5, fig.width = 2.5}
     # APPLY A BUFFER
@@
 
-```{r split_centroids}
+```{r split_centroids, echo = FALSE}
 # Split the centroid data set
@@
 
-## Allocate each centroids to a hexagon grid point
+## Allocate each centroid to a hexagon grid point
 
@@
 
-```{r centroids, eval = FALSE}
+```{r centroids, eval = FALSE, fig.height = 2.5, fig.width = 2.5}
 hexmap_allocation <- allocate(
@@
 
-```{r arrange}
+```{r arrange, echo = FALSE}
 s_centroids <- centroids %>% arrange(focal_distance)
@@
 
-```{r orig_dist}
+```{r orig_dist, echo = FALSE}
 hex_filter = 10
@@
 
-```{r available_points}
+```{r available_points, echo = FALSE}
 # filter for only the available hex grid points
@@
 
-```{r close_points}
+```{r close_points, echo = FALSE}
 filter_dist <- hex_filter*hex_size
@@
 
-```{r buffer_circle}
+```{r buffer_circle, echo = FALSE}
     hex_grid <- hex_grid %>%
@@
 
-```{r buffers, fig.height=2.5, fig.width = 5}
+```{r buffers, echo = FALSE, fig.height=2.5, fig.width = 5}
 gridExtra::grid.arrange(buff1, buff2, nrow=1)
@@
 
-```{r buffer_slice}
+```{r buffer_slice, echo = FALSE}
 # Filter for angle within circle
@@
         }
-```
 
-```{r plot_slice}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + theme_void() + coord_equal() +
+buff3 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
@@
 
-```{r choose_point}
+```{r choose_point, echo = FALSE}
 # Choose first available point
@@
 
-```{r allocated}
+```{r allocated, echo = FALSE}
 hex_points_df <- centroid_allocation %>% 
@@
   sf_id = "LGA_CODE16")
-```
 
-```{r plot_allocated}
-ggplot() + 
+buff4 <- ggplot() + 
   geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga %>% filter(LGA_CODE16=="62810"), fill = "grey", size = 0.3, colour = "lightgrey") +
@@
 
+```{r buffs, fig.height = 2.5, fig.width = 5, echo = FALSE}
+gridExtra::grid.arrange(buff3, buff4 , nrow=1)
+```
+
 The following code creates a map for all the Local Government Areas in Tasmania:
 
-```{r full_hexmapcode, echo = TRUE}
+```{r full_hexmapcode, echo = TRUE, warning = FALSE}
 # Create centroids set
@@
 
-```{r plot_final, fig.height=2.5, fig.width = 5}
+# Transform the data for plotting
+
+To plot polygons using \CRANpkg{ggplot} the \CRANpkg{sf} object can be transformed to a set of indidivual points that can be joined as a polygon.
+
+```{r create_plot_final, fig.height=2.5, fig.width = 5, message = FALSE, warning = FALSE}
 h1 <- hex_allocated %>%
@@
   left_join(., tas_lga)
+```
 
+```{r plot_final, echo = FALSE, fig.height=2.5, fig.width = 5, message = FALSE, warning = FALSE}
 p1 <- fortify_sfc(tas_lga)

### 2019-07-30 algorithmRjournal/algorithmRjournal.tex
Cleaned file

@@
 executed by the main function, \texttt{create\_hexmap}, or can be
-applied separately for more flexibility.
+implemented separately for more flexibility.
 
@@
 library(sugarbag)
-
 library(tidyverse)
 \end{Sinput}
-\begin{Soutput}
-#> Registered S3 methods overwritten by 'ggplot2':
-#>   method         from 
-#>   [.quosures     rlang
-#>   c.quosures     rlang
-#>   print.quosures rlang
-\end{Soutput}
-\begin{Soutput}
-#> Registered S3 method overwritten by 'rvest':
-#>   method            from
-#>   read_xml.response xml2
-\end{Soutput}
-\begin{Soutput}
-#> -- Attaching packages --------------------------------------------------- tidyverse 1.2.1 --
-\end{Soutput}
-\begin{Soutput}
-#> v ggplot2 3.1.1       v purrr   0.3.2  
-#> v tibble  2.1.1       v dplyr   0.8.0.1
-#> v tidyr   0.8.3       v stringr 1.4.0  
-#> v readr   1.3.1       v forcats 0.4.0
-\end{Soutput}
-\begin{Soutput}
-#> -- Conflicts ------------------------------------------------------ tidyverse_conflicts() --
-#> x dplyr::filter() masks stats::filter()
-#> x dplyr::lag()    masks stats::lag()
-\end{Soutput}
 \end{Schunk}
@@
 The \texttt{create\_hexmap} function requires several parameters, if
-they are not provided, the information will be derived from the polygon
-set used. If users already have a grid and set of centroids they may
-choose to only use the \texttt{allocate} function.
+they are not provided, the information will be derived from the
+\CRANpkg{sf} set of shapes used. If users already have a grid and set of
+centroids they may choose to only use the \texttt{allocate} function.
 
-\textbf{The following must be provided to \texttt{create\_hexmap}:}
+\emph{The following must be provided to \texttt{create\_hexmap}:}
 
@@
 \begin{Sinput}
-## Use the create_centroids function to find polygon centroids:
 centroids <- create_centroids(shp_sf = tas_lga, sf_id = "LGA_CODE16")
-\end{Sinput}
-\begin{Soutput}
-#> Warning in st_centroid.sf(.): st_centroid assumes attributes are constant
-#> over geometries of x
-\end{Soutput}
-\begin{Soutput}
-#> Warning in st_centroid.sfc(st_geometry(x), of_largest_polygon =
-#> of_largest_polygon): st_centroid does not give correct centroids for
-#> longitude/latitude data
-\end{Soutput}
-\begin{Sinput}
-## Join to data for each area
-centroids <- left_join(centroids,
-  sf::st_drop_geometry(tas_lga), by = "LGA_CODE16")
 \end{Sinput}
@@
 \begin{Schunk}
-\begin{Sinput}
-fort_lga <- fortify_sfc(tas_lga)
-polys <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") +theme_void() + coord_equal()
-
-cents <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids) + theme_void() + coord_equal()
-
-gridExtra::grid.arrange(polys, cents, nrow = 1)
-\end{Sinput}
 \begin{figure}
@@
 \begin{Sinput}
-## create the bounding box from the set of polygon centroids:
-bbox <- tibble::tibble(min = c(min(centroids$longitude, na.rm = TRUE), min(centroids$latitude, na.rm = TRUE)),
-        max = c(max(centroids$longitude, na.rm = TRUE), max(centroids$latitude, na.rm = TRUE)))
-
-hex_size = 0.3
-
-# default size calculation:
-#(bbox$max[1] - bbox$min[1])/(bbox$max[2] - bbox$min[2]) / 5
-
-buffer_dist <- max((bbox$max[1] - bbox$min[1]), (bbox$max[2] - bbox$min[2]))*0.3
+grid <- create_grid(centroids = centroids, hex_size = 0.2, buffer_dist = 1.2)
 \end{Sinput}
@@
 A sequence is created for longitude columns, and another for latitude
-rows.
-
-The sequences begin at the minimum longitude (latitude), minus the
+rows. The sequences begin at the minimum longitude (latitude), minus the
 buffer distance. Equally spaced intervals the size of the hexagons are
 created up to the maximum longitude (latitude), plus the buffer
-distance.
-
-An individual point is created from all intersections of the longitude
-columns and latitude row sequences.
-
-\begin{Schunk}
-\begin{Sinput}
-grid <- tibble::as_tibble(
-  expand.grid(
-    hex_long = seq(bbox$min[1] - buffer_dist, # minimum
-      bbox$max[1] + buffer_dist, # maximum
-      hex_size), # distance between hexagons
-    hex_lat = seq(bbox$min[2] - buffer_dist, # minimum
-      bbox$max[2] + buffer_dist, # maximum
-      hex_size))) # distance between hexagons
-\end{Sinput}
-\end{Schunk}
-
-\begin{Schunk}
-\begin{Sinput}
-grid1 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
-\end{Sinput}
-\end{Schunk}
+distance. An individual point is created from all intersections of the
+longitude columns and latitude row sequences.
 
@@
 \begin{Schunk}
-\begin{Sinput}
-# Find every second latitude
-shift_lat <- grid %>% dplyr::select(hex_lat) %>%
-    dplyr::distinct() %>%
-    dplyr::filter(dplyr::row_number() %% 2 == 1) %>% unlist()
-
-# Shift the longitude of every second latitude to the right to make hex structure
-grid <- grid %>%
-    dplyr::mutate(hex_long = ifelse(hex_lat %in% shift_lat, hex_long,
-        hex_long + (hex_size / 2))) %>%
-    dplyr::mutate(id=1:NROW(.)) %>%
-    dplyr::mutate(assigned=FALSE)
-\end{Sinput}
-\end{Schunk}
-
-\begin{Schunk}
-\begin{Sinput}
-grid2 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
-\end{Sinput}
-\end{Schunk}
-
-Each point is now given an ID.
-
-\begin{Schunk}
-\begin{Sinput}
-full_grid <- grid <- grid %>%
-    mutate(hex_long_int = dense_rank(hex_long)-1,
-        hex_lat_int = dense_rank(hex_lat)-1)
-\end{Sinput}
-\end{Schunk}
-
-\begin{Schunk}
-\begin{Sinput}
-gridExtra::grid.arrange(grid1, grid2, nrow = 1)
-\end{Sinput}
 \begin{figure}
-\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-2-1} \caption[Grid points to create a tilegram]{Grid points to create a tilegram.}\label{fig:unnamed-chunk-2}
+\includegraphics{algorithmRjournal_files/figure-latex/unnamed-chunk-3-1} \caption[Grid points to create a tilegram]{Grid points to create a tilegram.}\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 the set of centroids.
-
-\begin{Schunk}
-\begin{Sinput}
-nlong <- length(unique(grid$hex_long))
-nlat <- length(unique(grid$hex_lat))
-
-centroids <- centroids %>%
-  mutate(long_int = round((longitude-min(grid$hex_long))/(max(grid$hex_long)-min(grid$hex_long))*nlong, 0),
-          lat_int = round((latitude-min(grid$hex_lat))/(max(grid$hex_lat)-min(grid$hex_lat))*nlat, 0))
-\end{Sinput}
-\end{Schunk}
 
@@
 
-\begin{Schunk}
-\begin{Sinput}
-# Split the centroid data set
-centroids <- centroids %>% 
-  nest(longitude, latitude) %>% 
-  mutate(closest = map(data, closest_focal_point, focal_points = capital_cities %>% filter(points == "Hobart"))) %>% 
-  unnest(data, closest) %>% 
-  arrange(focal_distance)
-\end{Sinput}
-\end{Schunk}
-
 For each polygon centroid in the set, the distance to each of the focal
@@
 
-\hypertarget{allocate-each-centroids-to-a-hexagon-grid-point}{%
-\subsection{Allocate each centroids to a hexagon grid
-point}\label{allocate-each-centroids-to-a-hexagon-grid-point}}
+\hypertarget{allocate-each-centroid-to-a-hexagon-grid-point}{%
+\subsection{Allocate each centroid to a hexagon grid
+point}\label{allocate-each-centroid-to-a-hexagon-grid-point}}
 
@@
 
-\begin{Schunk}
-\begin{Sinput}
-s_centroids <- centroids %>% arrange(focal_distance)
-
-s_centroids <- split(s_centroids, s_centroids[["focal_distance"]])
-
-# Set up allocation data frame
-centroid_allocation <- NULL
-\end{Sinput}
-\end{Schunk}
-
 The filter parameter is used to subset possible grid points to only
@@
 smaller distance will increase speed, but can decrease accuracy.
-
-\begin{Schunk}
-\begin{Sinput}
-hex_filter = 10
-width = 35
-# keep value to reset expanded distances
-expand_dist <- hex_filter
-\end{Sinput}
-\end{Schunk}
 
@@
 
-\begin{Schunk}
-\begin{Sinput}
-# filter for only the available hex grid points
-hex_grid <- grid %>% filter(!assigned)
-\end{Sinput}
-\end{Schunk}
-
 \hypertarget{step-2-filter-the-grid-points-for-those-closest-to-the-centroid}{%
@@
 considered.
-
-\begin{Schunk}
-\begin{Sinput}
-filter_dist <- hex_filter*hex_size
-
-# filter grid for avaiable points
-centroid1 <- centroids %>% head(1)
-
-flong <- centroid1$longitude
-flat <- centroid1$latitude
-
-hex_grid <- hex_grid %>% ungroup() %>%
-        filter(flat - filter_dist < hex_lat & hex_lat < flat + filter_dist) %>%
-        filter(flong - filter_dist < hex_long & hex_long < flong + filter_dist)
-\end{Sinput}
-\end{Schunk}
 
@@
 \begin{Schunk}
-\begin{Sinput}
-    hex_grid <- hex_grid %>%
-        rowwise %>%
-        mutate(
-        hex_lat_c = hex_lat - flat,
-        hex_long_c = hex_long - flong) %>%
-        mutate(hyp = ((hex_lat_c^2) + (hex_long_c^2))^(1/2))
-
-        f_angle <- centroid1 %>%
-            mutate(atan = atan2(latitude-latitude1,longitude-longitude1),
-                angle = (atan*180/pi),
-                pangle = ifelse(angle<0, angle +360, angle)) %>% pull()
-
-        hex_grid <- hex_grid %>%
-            # create circle of radius: hex_filter
-            filter(hyp < filter_dist) %>%
-            mutate(
-                # geosphere takes a long time
-                angle = f_angle,
-                angle_plus = (angle + width)%%360,
-                angle_minus = (angle - width)%%360,
-                atan = atan2(hex_lat_c, hex_long_c),
-                hex_angle = (atan*180/pi),
-                hex_angle = ifelse(hex_angle<0, hex_angle +360, hex_angle))
-\end{Sinput}
-\end{Schunk}
-
-\begin{Schunk}
-\begin{Sinput}
-gridExtra::grid.arrange(buff1, buff2, nrow=1)
-\end{Sinput}
 
@@
 
-\begin{Schunk}
-\begin{Sinput}
-# Filter for angle within circle
-
-        if (hex_grid$angle_minus[1] < hex_grid$angle_plus[1]) {
-            hex_grid <- hex_grid %>%
-                # create slice of 60 degrees from centroid
-                filter(angle_minus < hex_angle & hex_angle < angle_plus)
-        } else {
-            hex_grid <- hex_grid %>%
-                # create slice of 60 degrees from centroid
-                filter(hex_angle < angle_plus | angle_minus > hex_angle)
-        }
-\end{Sinput}
-\end{Schunk}
-
-\begin{Schunk}
-\begin{Sinput}
-ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + theme_void() + coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75) + 
-  geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "#b2df8a", size = 0.8) 
-\end{Sinput}
-
-\includegraphics{algorithmRjournal_files/figure-latex/plot_slice-1} \end{Schunk}
-
 This area was the very closest to the Hobart central point ( coloured
@@
 \begin{Schunk}
-\begin{Sinput}
-# Choose first available point
-cent <- centroid1 %>% dplyr::rename(focal_point = points, focal_dist = focal_distance, focal_angle = angle)
 
-# Filter should give one hex point
-hex <- hex_grid %>% 
-  ungroup %>% 
-  filter(hyp == min(hyp)) %>%
-  select(hex_long, hex_lat, hex_id = id)
-
-# Update grid to show this centroid as assigned
-hex_grid[which(hex_grid$id == hex$hex_id),]$assigned <- TRUE
-
-# Add to table of allocated centroids
-centroid_allocation <- bind_rows(centroid_allocation, dplyr::bind_cols(cent, hex)) %>% as_tibble()
-\end{Sinput}
-\end{Schunk}
-
-\begin{Schunk}
-\begin{Sinput}
-hex_points_df <- centroid_allocation %>% 
-  fortify_hexagon(hex_size = hex_size,
-  sf_id = "LGA_CODE16")
-\end{Sinput}
-\end{Schunk}
-
-\begin{Schunk}
-\begin{Sinput}
-ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga %>% filter(LGA_CODE16=="62810"), fill = "grey", size = 0.3, colour = "lightgrey") +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75) + 
-  geom_point(aes(x=longitude1, y = latitude1), data = centroid1, colour = "#fb9a99", size = 1) + 
-  geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "#b2df8a", size = 0.8) + 
-  theme_void() +
-  coord_equal()
-\end{Sinput}
-
-\includegraphics{algorithmRjournal_files/figure-latex/plot_allocated-1} \end{Schunk}
+\includegraphics{algorithmRjournal_files/figure-latex/buffs-1} \end{Schunk}
 
@@
 centroids <- create_centroids(tas_lga, "LGA_CODE16")
-\end{Sinput}
-\begin{Soutput}
-#> Warning in st_centroid.sf(.): st_centroid assumes attributes are constant
-#> over geometries of x
-\end{Soutput}
-\begin{Soutput}
-#> Warning in st_centroid.sfc(st_geometry(x), of_largest_polygon =
-#> of_largest_polygon): st_centroid does not give correct centroids for
-#> longitude/latitude data
-\end{Soutput}
-\begin{Sinput}
 # Create hexagon location grid
@@
 
+\hypertarget{transform-the-data-for-plotting}{%
+\section{Transform the data for
+plotting}\label{transform-the-data-for-plotting}}
+
+To plot polygons using \CRANpkg{ggplot} the \CRANpkg{sf} object can be
+transformed to a set of indidivual points that can be joined as a
+polygon.
+
 \begin{Schunk}
@@
 \end{Sinput}
-\begin{Soutput}
-#> Joining, by = "LGA_CODE16"
-\end{Soutput}
-\begin{Soutput}
-#> Warning: Column `LGA_CODE16` joining character vector and factor, coercing
-#> into character vector
-\end{Soutput}
-\begin{Sinput}
-p1 <- fortify_sfc(tas_lga)
-end_hex <- ggplot() +
-  geom_polygon(data = p1, aes(x=long, lat, group = interaction(LGA_NAME16, polygon)), fill = "grey", size = 0.3, colour = "lightgrey") +
-  geom_polygon(data = h1, aes(x=long, lat, group = LGA_CODE16)) + theme_void() + coord_equal()
+\end{Schunk}
 
-gridExtra::grid.arrange(cents, end_hex, nrow = 1)
-\end{Sinput}
+\begin{Schunk}
 

### 2019-10-31 algorithmRjournal/kobakian_sugarbag.Rmd
New name

--- 2019-07-30 algorithmRjournal/algorithmRjournal.Rmd
@@
       in_header: preamble.tex
+editor_options: 
+  chunk_output_type: console
 ---
@@
 
-Choropleths are the current best practice approach for presenting geographical data as
-maps highlight the geographic patterns in geospatially related statistics [@SAMGIS].
-The land on the map space is divided to separate each area, these boundaries are usually administrative. The areas are filled with colour to represent the value of the statistic for the area [@EI].
+Choropleths are current practice for presenting geographical data on a map, as they highlight the geographic patterns in geospatially related statistics [@SAMGIS].
+The land on the map space is divided into separate areas, these boundaries are usually administrative, such as states or counties.
+The areas are filled with colour to represent the value of the statistic for the area [@EI].
 
 <!-- urbanisation -->
-In Australia, government bodies such as the Australian Bureau of Statistics, or the Australian Electoral Commission hold the responsibility for the division of areas.
-These boundaries are often adjusted as the population in areas increase.
-Australian people are increasingly congregating around major cities, the rural areas are often sparsely populated in comparison to the urban centres.
-The division of the population into equal population areas results in dramatically different square meterage of the geographic areas. 
-This results in an unequal presentation of the statistic in each area, this can misrepresent the spatial distributions of the human related statistics in geographic maps.
+Australian residents are increasingly congregating around major cities, the vast rural areas are often sparsely populated in comparison to the urban centres. 
+In Australia, government bodies such as the Australian Bureau of Statistics, and the Australian Electoral Commission hold the responsibility for the division of areas.
+These boundaries are adjusted as the population increases. 
+The division of the population into approximately equal population areas results in dramatically different square meterage of the geographic areas. 
+This results in an unequal visualisation of the statistic in each area, this can allow misrepresentation of the spatial distributions of human related statistics in geographic maps.
 
 <!-- solutions -->
-Beginning with the geography, cartograms apply a transformation to place importance on the statistic of interest.
-They result in a distortion of the map space to represent differences in the statistic.
-These displays rely on the statistic of interest to determine the layout, however for Australia, many cartograms fail to preserve a recognisable display.
-Contiguous cartograms change the shape of an area, preserving neighbouring relationships. Non-contiguous cartograms maintain the shape of each area, but lose the connection to neighbours.
+A solution to this visualisation problem begins with the geography.
+Cartograms apply a transformation to the geographic boundaries based on the value of the statistic of interest.
+These displays result in a distortion of the map space to represent differences in the statistic across the areas [@ACCAC].
+These displays rely on the statistic of interest to determine the layout.
+Australian population statistics often result in a cartogram that fails to preserve a recognisable display due to the difference in size of metropolitan and rural areas, a common feature of British Colonies [@ACTUC].
+Contiguous cartograms change the shape of an area, preserving neighbouring relationships. Non-contiguous cartograms maintain the geographic shape of each area, but lose the connection to neighbours.
+Population cartograms use either of these methods with population as the statistic of interest [@GOINO].
 
-Alternative maps shift the focus from land area, to the value of the statistics in a group of areas.
+Alternative maps shift the focus from land area and shape, to the value of the statistics in a group of areas.
 Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing each administrative area.
+This acknowledges that the amount of residents can be different despite best efforts to normalise the areas using boundary shifts, but recognises that each area is equally important.
 
-Tilegrams are an extension of Dorling cartograms, using one simple shape to represnt each area.
+Tilegrams are an extension of Rectangular cartograms [@ORC] and Dorling cartograms [@ACTUC], using one simple shape to represnt each area.
 This allows preservation of spatial relationships and decreases the emphasis from the amount of geographic area.
@@
  1. Create the set of centroids to allocate
- 2. Create the set of hexagons to use
+ 2. Create the grid of hexagons to use
  3. Allocate each centroid to an available hexagon
@@
 
-The `create_hexmap` function requires several parameters, if they are not provided, the information will be derived from the \CRANpkg{sf} set of shapes used.
+The `create_hexmap` function requires several parameters, if they are not provided, the information will be derived from the simple features (\CRANpkg{sf}) set of shapes used.
 If users already have a grid and set of centroids they may choose to only use the `allocate` function.
@@
 
-The polygon set of Local Government Areas (LGA) of Tasmania in 2016 is provided with the \CRANpkg{sugarbag} package as `tas_lga`. 
+The polygon set of Local Government Areas (sa2) of Tasmania in 2016 is provided with the \CRANpkg{sugarbag} package as `tas_sa2`. 
 A single column of the data set must be used to identify the unique areas. 
-In this case, the unique LGA codes associated with each LGA have been used.
+In this case, the unique sa2 codes associated with each sa2 have been used.
 
@@
 The set should be provided as an `sf` object, this is a data frame containing a `geometry` column.
-^[The `read_shape` function can assist in creating this object.] We will use the Local Government Areas of Tasmania, downloaded from the Australian Bureau of Statistics.
+^[The `read_shape` function can assist in creating this object.] We will use the Statistical Areas of Tasmania, at Level 2, downloaded from the Australian Bureau of Statistics.
 
@@
 ```{r cents, message=FALSE, warning=FALSE, comment = FALSE}
-centroids <- create_centroids(shp_sf = tas_lga, sf_id = "LGA_CODE16")
+centroids <- create_centroids(shp_sf = tas_sa2, sf_id = "SA2_NAME16")
 ```
+
 ```{r derive_centroids, echo = FALSE}
@@
 centroids <- left_join(centroids,
-  sf::st_drop_geometry(tas_lga), by = "LGA_CODE16")
+  sf::st_drop_geometry(tas_sa2), by = "SA2_NAME16")
 ```
@@
 ```{r end_cents, fig.cap="Local Government Areas and derived centroids.", fig.height=2.5, fig.width = 5, echo = FALSE}
-fort_lga <- fortify_sfc(tas_lga)
+fort_sa2 <- fortify_sfc(tas_sa2)
+
 polys <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") +theme_void() + coord_equal()
+  geom_polygon(aes(x = long, y = lat, group = interaction(SA2_NAME16, polygon)), data = fort_sa2, fill = "grey", size = 0.2, colour = "lightgrey") +theme_void() + coord_equal()
 
 cents <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids) + theme_void() + coord_equal()
+  geom_polygon(aes(x = long, y = lat, group = interaction(SA2_NAME16, polygon)), data = fort_sa2, fill = "grey", size = 0.2, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids) + theme_void() + coord_equal()
 
@@
 
-A tilegram allows areas to be allocated to a tellesated set of tiles.
-The grid is created to ensure a close point is found, that ensures tessellation with other previously allocated points.
+A tilegram allocates areas to a tellesated set of tiles.
+The grid is created to ensure tessellation with other previously allocated points.
 
@@
 
-hex_size = 0.3
+hex_size = 0.2
 
@@
 
-### Step 1: Expand the grid
+### Step 1: Inital grid
 
-A sequence is created for longitude columns, and another for latitude rows.
-The sequences begin at the minimum longitude (latitude), minus the buffer distance.
-Equally spaced intervals the size of the hexagons are created up to the maximum longitude (latitude), plus the buffer distance.
-An individual point is created from all intersections of the longitude columns and latitude row sequences.
+Creating the grid involves using the centroids provided to find the minimum and maximum, longitude and latitude centroid values.
+The buffer distance is used to extend the equally spaced rows and columns from the minimum longitude (latitude) minus the buffer distance, up to the maximum longitude (latitude) plus the buffer distance.
+The set of longitude columns, and latitude rows  are created to define hexagons which are the size specified by `hex_size`.
+An individual hexagon location is created from all intersections of the longitude columns and latitude rows.
+
 ```{r grid, echo = FALSE}
@@
 
-grid1 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
+grid1 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(SA2_NAME16, polygon)), data = fort_sa2, fill = "grey", size = 0.2, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data= centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75) 
 ```
-A square grid will not facilitate tessellated hexagons. Every second latitude row of points will be shifted right by half of the hexagon size.
+
+A square grid will not facilitate tessellated hexagons. Every second latitude row of points must be shifted right by half of the hexagon size.
+
 ```{r shift, echo = FALSE}
@@
 
-grid2 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
+grid2 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(SA2_NAME16, polygon)), data = fort_sa2, fill = "grey", size = 0.2, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75)
@@
 It finds the grid points needed to best capture the set of centroids.
+
+```{r fort_grid, echo = FALSE}
+fort_grid <- fortify_hexagon(data = grid, sf_id = "id", hex_size = 0.2)
+
+```
 
@@
 
-ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = full_grid, size = 0.25) +
+ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(SA2_NAME16, polygon)), data = fort_sa2, fill = "grey", size = 0.2, colour = "lightgrey")  +
+  geom_polygon(aes(x = long, y = lat, group = id), data = fort_grid, fill = NA, colour = "#a6cee3") +
+  geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a", fill = "red") + theme_void() + coord_equal() +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = grid, size = 0.75)
@@
 centroids <- centroids %>% 
-  nest(longitude, latitude) %>% 
+  nest(data = c(longitude, latitude)) %>% 
   mutate(closest = map(data, closest_focal_point, focal_points = capital_cities %>% filter(points == "Hobart"))) %>% 
-  unnest(data, closest) %>% 
+  unnest(c(data, closest)) %>% 
   arrange(focal_distance)
@@
 hexmap_allocation <- allocate(
-  centroids = centroids,
-  sf_id = "LGA_CODE16",
+  centroids = centroids %>% select(SA2_NAME16, longitude, latitude),
+  sf_id = "SA2_NAME16",
   hex_grid = grid,
@@
 ```{r plot_buffer, echo = FALSE}
-buff1 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroid1, fill = "red") + theme_void() + coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75)
+buff1 <- ggplot()+
+   geom_polygon(aes(x = long, y = lat, group = interaction(SA2_NAME16, polygon)), data = fort_sa2, fill = "grey", size = 0.2, colour = "lightgrey") + 
+  geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a", fill = "red")  + 
+  geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "orange") + theme_void() +
+    geom_polygon(aes(x = long, y = lat, group = id), data = fort_grid, fill = NA, colour = "#a6cee3") +  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 1) +
+  theme_void() + coord_equal() 
 ```
@@
         f_angle <- centroid1 %>%
-            mutate(atan = atan2(latitude-latitude1,longitude-longitude1),
+            mutate(atan = atan2(latitude-focal_latitude,longitude-focal_longitude),
                 angle = (atan*180/pi),
@@
 ```{r plot_circle, echo = FALSE}
-buff2 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "#b2df8a") + theme_void() + coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75)
+buff2 <- ggplot() + 
+   geom_polygon(aes(x = long, y = lat, group = interaction(SA2_NAME16, polygon)), data = fort_sa2, fill = "grey", size = 0.2, colour = "lightgrey") + 
+  geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a", fill = "red")  + 
+  geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "orange") + theme_void() +
+    geom_polygon(aes(x = long, y = lat, group = id), data = fort_grid, fill = NA, colour = "#a6cee3") +  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 1) +
+  theme_void() + coord_equal()
+
 ```
@@
 ```{r buffer_slice, echo = FALSE}
+
 # Filter for angle within circle
-
   if (hex_grid$angle_minus[1] < hex_grid$angle_plus[1]) {
@@
 
-buff3 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga, fill = "grey", size = 0.3, colour = "lightgrey") + theme_void() + coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#a6cee3", data = grid, size = 0.25) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75) + 
-  geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "#b2df8a", size = 0.8) 
+buff3 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(SA2_NAME16, polygon)), data = fort_sa2, fill = "grey", size = 0.2, colour = "lightgrey") +  
+   geom_polygon(aes(x = long, y = lat, group = interaction(SA2_NAME16, polygon)), data = fort_sa2, fill = "grey", size = 0.2, colour = "lightgrey") + 
+  geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a", fill = "red")  + 
+  geom_point(aes(x=focal_longitude, y = focal_latitude), data = centroid1, colour = "red") +
+  geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "orange") +
+    geom_polygon(aes(x = long, y = lat, group = id), data = fort_grid, fill = NA, colour = "#a6cee3") + 
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 1) +
+  theme_void() + coord_equal()
+
 ```
@@
   fortify_hexagon(hex_size = hex_size,
-  sf_id = "LGA_CODE16")
+  sf_id = "SA2_NAME16")
 
-buff4 <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = interaction(LGA_NAME16, polygon)), data = fort_lga %>% filter(LGA_CODE16=="62810"), fill = "grey", size = 0.3, colour = "lightgrey") +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 0.75) + 
-  geom_point(aes(x=longitude1, y = latitude1), data = centroid1, colour = "#fb9a99", size = 1) + 
-  geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "#b2df8a", size = 0.8) + 
-  theme_void() +
-  coord_equal()
+buff4 <- ggplot() + geom_polygon(aes(x = long, y = lat, group = interaction(SA2_NAME16, polygon)), data = fort_sa2, fill = "grey", size = 0.2, colour = "lightgrey") +  
+    geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#b2df8a", fill = "red")  + 
+  geom_point(aes(x=focal_longitude, y = focal_latitude), data = centroid1, colour = "red") +
+  geom_point(aes(x=longitude, y = latitude), data = centroid1, colour = "orange") +
+    geom_polygon(aes(x = long, y = lat, group = id), data = fort_grid, fill = NA, colour = "#a6cee3") + 
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#1f78b4", data = hex_grid, size = 1) +
+  theme_void() + coord_equal() 
 ```
@@
 # Create centroids set
-centroids <- create_centroids(tas_lga, "LGA_CODE16")
+centroids <- create_centroids(tas_sa2, "SA2_NAME16")
 # Create hexagon location grid
 grid <- create_grid(centroids = centroids,
-    hex_size = 0.3,
+    hex_size = 0.2,
     buffer_dist = 1.2)
@@
   hex_grid = grid,
-  sf_id = "LGA_CODE16",
+  sf_id = "SA2_NAME16",
   # same column used in create_centroids
-  hex_size = 0.3,
+  hex_size = 0.2,
   # same size used in create_grid
@@
 h1 <- hex_allocated %>%
-  fortify_hexagon(hex_size = 0.3, 
-  sf_id = "LGA_CODE16") %>% 
-  left_join(., tas_lga)
+  fortify_hexagon(hex_size = 0.2, 
+  sf_id = "SA2_NAME16") %>% 
+  left_join(., tas_sa2)
 ```
@@
 ```{r plot_final, echo = FALSE, fig.height=2.5, fig.width = 5, message = FALSE, warning = FALSE}
-p1 <- fortify_sfc(tas_lga)
+p1 <- fortify_sfc(tas_sa2)
 end_hex <- ggplot() +
-  geom_polygon(data = p1, aes(x=long, lat, group = interaction(LGA_NAME16, polygon)), fill = "grey", size = 0.3, colour = "lightgrey") +
-  geom_polygon(data = h1, aes(x=long, lat, group = LGA_CODE16)) + theme_void() + coord_equal()
+  geom_polygon(data = p1, aes(x=long, lat, group = interaction(SA2_NAME16, polygon)), fill = "grey", size = 0.2, colour = "lightgrey") +
+  geom_polygon(aes(x=long, y = lat, group = SA2_NAME16), data = h1, colour = "white", fill = "#b2df8a") + theme_void() + coord_equal()
 

### 2020-01-10 AusCancerAtlas.R
remove from master branch

@@ -1,37 +1,0 @@
-library(sugarbag)
-library(absmapsdata)
-library(tidyverse)
-
-
-# Create centroids set
-centroids <- create_centroids(sa22011, "sa2_5dig_2011")
-# save(centroids, file = "data/sa22011/centroids.rda")
-
-# Create hexagon location grid
-grid <- create_grid(centroids = centroids, hex_size = 0.2, buffer_dist = 5)
-# save(grid, file = "data/sa22011/grid.rda")
-
-# Allocate polygon centroids to hexagon grid points
-allocated <- allocate(centroids = centroids,
-  hex_grid = grid,
-  sf_id = "sa2_5dig_2011",
-  hex_size = 0.2, # same size used in create_grid
-  hex_filter = 15,
-  width = 30,
-  focal_points = capital_cities,
-  verbose = TRUE) 
-
-#save(allocated, file = "data/sa22011/allocated.rda")
-
-hex_allocated <- create_hexmap(sa22011, sf_id = "sa2_5dig_2011",
-  focal_points = capital_cities,
-  verbose = TRUE)
-
-#save(hex_allocated, file = "data/sa22011/hex_allocated.rda")
-
-
-# same column used in create_centroids
-hexagons <- fortify_hexagon(data = allocated, sf_id = "sa2_5dig_2011", hex_size = 0.2)
-polygons <- fortify_sfc(sa22011, keep = 0.1)
-
-ggplot(hexagons) + geom_polygon(aes(x=long, y = lat, group = sa2_5dig_2011))

### 2020-01-10 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
JSS version of algorithm paper

---
documentclass: jss
author:
  - name: Stephanie Kobakian
    affiliation: Queensland University of Technology
    address: >
      School of Mthematical Sciences,
      Science and Engineering Faculty,
      Brisbane, QLD, Australia
    email: \email{stephanie.kobakian@qut.edu.au}
    url: http://rstudio.com
title:
  plain: An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With Application to Australian Maps   
abstract: >
  This algorithm creates a tesselated hexagon display to represent each of the spatial polygons. It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units. It showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps. Spatial distributions have been presented on alternative representations of geography for many years. In modern times, interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption. Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
keywords:
  # at least one keyword must be supplied
  formatted: [spatial, statistics, cartogram]
preamble: >
  \usepackage{amsmath}
biblio-style: jss
output:
  rticles::jss_article:
    fig_caption: true
    citation_package: natbib
bibliography: sugarbag.bib
link-citations: true
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE, comment = FALSE}
library(knitcitations)
library(RefManageR)
library(sf)

knitr::opts_chunk$set(warning = FALSE, message = FALSE)
options("citation_format" = "pandoc")
BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')
```

# Introduction

<!-- Motivation to map -->

The current practice for presenting geogspatial data involves a choropleth map display. These maps highlight the geographic patterns in geospatially related statistics \citep{SAMGIS}.
The land on the map space is divided into geographic units, these boundaries are usually administrative, such as states or counties. The units are filled with colour to represent the value of the statistic \citep{EI}.

<!-- urbanisation -->
Australian residents are increasingly congregating around major cities, the vast rural areas are often sparsely populated in comparison to the urban centres. 
In Australia, government bodies such as the Australian Bureau of Statistics, and the Australian Electoral Commission hold the responsibility for the division of geographic units. These boundaries are adjusted as the population increases. The division of the population into approximately equal population areas results in dramatically different square meterage of the geographic areas. This results in an unequal attention given to the statistic of each area, this can allow misrepresentation of the spatial distributions of human related statistics in geographic maps.

<!-- solutions -->
The solution to this visualisation problem begins with the geography. Cartograms apply a transformation to the geographic boundaries based on the value of the statistic of interest. These displays result in a distortion of the map space to represent differences in the statistic across the areas \citep{ACCAC}. 
The statistic of interest is used to determine the layout. When using the
Australian population, the result is a population cartogram that fails to preserve a recognisable display due to the difference in size of metropolitan and rural areas \citep{ACTUC}, \citep{GOINO}.
Contiguous cartograms change the shape of an area, preserving boundary relationships of neighbours. Non-contiguous cartograms maintain the geographic shape of each area, but lose the connection to neighbours as each areas shrinks or grows.

Alternative maps shift the focus from land area and shape, to the value of the statistics in a group of areas.
Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing each administrative area. This acknowledges that the amount of residents can be different but recognises that each area, or person is equally important.

Tilegrams, Rectangular cartograms \citep{ORC} and Dorling cartograms \citep{ACTUC}, all use one simple shape to represent each area. This allows preservation of spatial relationships and decreases the emphasis from the amount of geographic area. These maps focus on the relationship between neighbours attempting to preserve connections, and disregard the unique shapes of the administrative boundaries.

The \pkg{sugarbag} package provides a new method to create tesselated hexagon tilegrams. 
Extending the tilegram to Australian applications required preserving the spatial relationships. It emphasises the capital cities as population hubs, and emphasises the distances rather than size of large, rural geographic units.

# Algorithm

This solution operates on a set of \pkg{sf} \citep{sf} polygons.

There are four steps to create a tesselated hexagon tilegram.
These steps can be executed by the main function, \code{create_hexmap}, or can be implemented separately for more flexibility. There are parameters used in the process that can be provided, if they are not, they will be automatically derived.

 1. Create the set of centroids to allocate
 2. Create the grid of hexagons locations to use
 3. Allocate each centroid to an available hexagon
 4. Transform the data for plotting

## Parameters

The \code{create_hexmap} function requires several parameters, if they are not provided, the information will be derived from the simple features (\pkg{sf}) set of shapes used. Users may choose to only use the \code{allocate} function when they wish to use a set of centroids, rather than \pkg{sf} polygons.

The following must be provided to \code{create_hexmap}:
```{r table_necessary, echo = FALSE, fig.cap = "This table details the parameters that must be provided to create a hexagon tile map using sugarbag."}
library(sugarbag)
library(tidyverse)

knitr::kable(tibble::tibble(parameter = c('shp', 
  'sf_id',
  'focal_points'),
  description = c(
    'an sf object containing the polygon information', 
    'name of a column that distinguishes unique areas',
    'a data frame of reference locations used to allocate hexagons'
    )), format = "latex")
```

## Tasmania

The polygon set of Statistical Areas at Level 2 (SA2) \citep{abs2016} of Tasmania in 2016 is provided with the \pkg{sugarbag} package as \code{tas_sa2}. 
A single column of the data set must be used to identify the unique areas. 
In this case, the unique SA2 names for each SA2 have been used.

The longitude and latitude centre of the capital cities of Australia are used to allocate areas around the closest capital city. Hobart will be the common focal point, as this example uses only the areas in the state of Tasmania.

```{r capital_cities}
data(capital_cities)
```

The following parameters will be determined within \code{create_hexmap} if they are not provided. They are created throughout the following example:

```{r parameters, echo = FALSE, fig.cap = "This table details the additional parameters that are used to create a hexagon tile map using sugarbag."}
knitr::kable(tibble(parameter = c('buffer_dist', 'hex_size',  'hex_filter', 'width'),
  description = c('a float value for distance in degrees to extend beyond the geometry provided',
    'a float value in degrees for the diameter of the hexagons', 'amount of hexagons around centroid to consider for allocation',
    'the angle used to filter the grid points around a centroid')), format = "latex")
```

## Create the set of centroid points

Individual \pkg{sugarbag} functions can be used outside of the main function.
The set of polygons should be provided as an \pkg{sf} object, this is a data frame containing a \code{geometry} column. The \code{read_shape} function can assist in creating this object.

The centroids can be derived from the set of polygons using the \code{create_centroids} function:
```{r cents}
centroids <- create_centroids(shp_sf = tas_sa2, sf_id = "SA2_NAME16")
```

```{r centroids_plot, out.width = "100%", echo = FALSE, eval = FALSE, fig.cap="The geographic shapes of the Statistical Areas of Tasmania at Level 2. The points show the locations of the centroids of the SA2 areas."}
knitr::include_graphics(path = "figures/1centroids.png")
```

## Create the hexagon grid points

A tilegram presents areas on a tellesated set of tiles.
The grid is created to ensure tessellation between the hexagons.

The grid of possible hexagon centroids is made using the \code{create_grid} function.
The grid creation requires several steps.
It uses the centroids, the hexagon size and the buffer distance.

```{r grid}
grid <- create_grid(centroids = centroids, hex_size = 0.2, buffer_dist = 1.2)
```

### Step 1: Creating a tesselated grid

A set of longitude columns, and latitude rows are created to define the locations of the hexagons. The distance between each row and column is defined by the size specified as \code{hex_size}.
The minimum and maximum, longitude and latitude values of the centroid locations are found. Equally spaced columns are created from the minimum longitude minus the buffer distance, up to the maximum longitude plus the buffer distance. The rows are then created from the latitude values and the buffer distance.
An individual hexagon location is created from all intersections of the longitude columns and latitude rows.

A square grid could be used for sqaure tiles, but it will not facilitate tessellated hexagons. Figure \ref{fig:grid2} allows for hexagons, as every second latitude row on the grid is shifted right, by half of the hexagon size.

```{r grid2, fig.cap="Grid points to create a tilegram.", out.width = "100%", echo = FALSE}
knitr::include_graphics(path = "figures/2grid.png")
```

### Step 2: Rolling windows

Not all of the grid points will be used, especially if islands result in a large grid space.
To filter the grid for appropriate points for allocation,
the \code{create_buffer} function is called within \code{create_grid}.
It finds the grid points needed to best capture the set of centroids on a hexagon tile map.

For each centroid location, the closest latitude row and longitude column are found. Then rows and columns of centroids are divided into 20 groups.
The amount of rows in each latitude group and the amount of columns in each longitude group are used as the width of rolling windows. The rolling windows can be seen on the This will tailor the available grid points to those most likely to be used.
It also helps reduce the amount of time taken, as it decreases the amount of points considered for each centroid allocation.

The first rolling window function finds the minimum and maximum centroid values for the sliding window groups of longitude columns and the groups of latitude rows.

The second rolling window function finds the average of the rolling minimum and maximum centroid values, for the longitude columns and latitude rows.

### Step 3: Filtering the grid

Only the grid points between the rolling average of the minimum and maximum centroid values are kept, for each row and column of the grid.

```{r filter_grid, fig.cap = "All possible hexagon locations from the initial grid are shown with blue outlines. The blue dots shown the grid points left as to choose from after the buffer step. The rolling windows to the right show the rows used to filter the hexagon locations.", echo = FALSE, out.width = "100%"}
knitr::include_graphics(path = "figures/3grid.png", dpi = 300)
```

## Centroid to focal point distance

The distance between each centroid in the set, and each of the focal points provided is calculated. The name of the closest focal point, and the distance and angle from focal point to polygon centroid is joined to polygon data set. To minimise time taken for this step, only Tasmania's capital city Hobart is provided.
The order for allocation is determined by the distance between the polygon centroid and it's closest focal point. The points are arranged from the centroid closest to the focal points, to the furthest.

## Allocate each centroid to a hexagon grid point

Allocation of all centroids takes place using the set of polygon centroids and the hexagon map grid. 
Centroid allocation begins with the closest centroid to a focal point.
This will preserve spatial relationships with the focal point, as the inner city areas are allocated first, they will be placed closest to the capital, and the areas that are further will then be accommodated.
Only the hexagon grid points that have not yet been allocated are considered.

The possible hexagon locations consider for a centroid location are determined by the \code{hex_filter}. This is the maximum amount of hexagons between the centroid and the furthest considered hexagon. It is used to subset possible grid points to only those surrounding the polygon centroid within an appropriate range. A smaller distance will increase speed, but can decrease accuracy if the angle width increases.

```{r centroids, eval = FALSE}
hexmap_allocation <- allocate(
  centroids = centroids %>% select(SA2_NAME16, longitude, latitude),
  sf_id = "SA2_NAME16",
  hex_grid = grid,
  hex_size = 0.2, # same size used in create_grid
  hex_filter = 10,
  width = 35,
  focal_points = capital_cities,
  verbose = TRUE)
```

The following example considers one of the Statistical Areas at Level 2. 
Within the algorithm, these steps are repeated for each polygon.

### Step 1: Filter the grid for unassigned hexagon points

Keep only the available hexagon points, this will prevent multiple areas being allocated to the same hexagon.

### Step 2: Filter the grid points for those closest to the centroid

This will allow only the closest points that are not yet assigned, to be considered.

A box of possible hexagon locations around the centroid. The corners of the box may not look square as the buffer has already removed unnecessary points from over the ocean.

The algorithm then removes the outer corners of the square, creating a circle of points, by only keeping points within a certain radial distance around the original centroid location.

```{r buffers, echo = FALSE, out.width = "100%"}
knitr::include_graphics(path = "figures/4grid.png")
```

The \code{width} parameter is used to take a slice of the remaining points. This uses the angle from the closest capital city, to the current centroid. This allows the spatial relationship to be preserved, even when it is allocated to a hexagon that is further from the focal point then the original centroid location.

If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded, only when a maximum distance is reached will the angle expand to accommodate more possible grid points.  
The angle begins at 30 degrees by default, and will increase if no points can be found within the \code{hex_filter} distance.
The allocation is returned and combined with the data relating to each polygon.

```{r buffs, out.width = "100%", echo = FALSE}
knitr::include_graphics(path = "figures/6allocate.png")
```

The following code creates a map for all the Statistical Areas at Level 2 in Tasmania:

# Using sugarbag

```{r full_hexmapcode, echo = TRUE, warning = FALSE, message = FALSE}

# install.packages("sugarbag")
library(sugarbag)

# Create centroids set
centroids <- create_centroids(tas_sa2, "SA2_NAME16")

# Create hexagon location grid
grid <- create_grid(centroids = centroids,
    hex_size = 0.2,
    buffer_dist = 1.2)

# Allocate polygon centroids to hexagon grid points
hex_allocated <- allocate(
  centroids = centroids,
  hex_grid = grid,
  sf_id = "SA2_NAME16",
  # same column used in create_centroids
  hex_size = 0.2,
  # same size used in create_grid
  hex_filter = 10,
  use_neighbours = tas_sa2,
  focal_points = capital_cities %>% filter(points == "Hobart"),
  width = 35,
  verbose = FALSE)
```

## Neighbour relationships

It is possible to encourage the use of neighbourhood relationshipd, for stronger preservation of neighbour relations.

An additional step may be included to allow the neighbours that have alredy been allocated to influence the placement of the current centroid. 
This requires respecifying the \code{sf} object as the argument for the \code{use_neighbours} parameter. This calculates neighbours using intersections of their polygons. This occurs for all areas before any allocations begin.

For the current centroid, the list of neighbours is consulted. If any neighbour was already allocated, the surrounding hexagons on the grid are prioritised. For multiple neighbours, the neighbouring hexagon grid points are aggregated and considered in order of distance from the original centroid.

# Australian Cancer Atlas

The hexagon tile map visualisation method can be applied to the Australian Cancer Atlas data. A small example of Lung Cancer Standardised Incidence Rates (SIRs) allows two views of the same data produced by the Australian Cancer Atlas. This small example in Figure  \ref{fig:sir} shows the group of blue areas in the Hobart CBD more prominently in the hexagon tile map (b).
The small red areas visible in the choropleth map (a) along the north coast are much larger in the hexagon tile maps. The hexagon tile map shows less yellow, this no longer overwhelms the map space with the information regarding the more rural areas.

```{r sir, out.width = "100%", echo = FALSE, fig.cap = "The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2. A choropleth map (a) of Standardised Incidence Rates (SIRs) is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented."}
knitr::include_graphics(path = "figures/7SIR.png")
```

# Conclusion

It is possible to use alternative maps to communicate spatial distributions.While a choropleth map display is the current practice spatial visualisation of geographical data. Current methods do not always work for Australia due to the large gaps between densely populated capital cities. The administrative boundaries may distract from the statistics, communicated using colour.

Alternative maps highlight the value of the statistics across the geographic units. Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing each administrative area. This acknowledges that the amount of residents can be different but recognises that each population area is equally important. The solution to this visualisation problem has equally sized areas, with neighbourhood boundary connections. This map algorithm is implemented in the @sugarbag package written for @R.
The \pkg{sugarbag} package creates tesselated hexagon tilegrams. The Australian application preserves the spatial relationships, emphasising capital cities. The hexagon tile map is a visualisation solution that highlights spatial distributions.

### 2020-01-10 kobakian_sugarbag_jss/kobakian_sugarbag_jss.tex
JSS version of algorithm paper

--- 2020-01-10 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
@@
----
-documentclass: jss
-author:
-  - name: Stephanie Kobakian
-    affiliation: Queensland University of Technology
-    address: >
-      School of Mthematical Sciences,
-      Science and Engineering Faculty,
-      Brisbane, QLD, Australia
-    email: \email{stephanie.kobakian@qut.edu.au}
-    url: http://rstudio.com
-title:
-  plain: An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With Application to Australian Maps   
-abstract: >
-  This algorithm creates a tesselated hexagon display to represent each of the spatial polygons.
-It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units.
-It showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps.
-Spatial distributions have been presented on alternative representations of geography for many years.
-In modern times, interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption.
-Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
-keywords:
-  # at least one keyword must be supplied
-  formatted: [spatial, statistics, cartogram]
-preamble: >
+\documentclass[
+]{jss}
+
+\usepackage[utf8]{inputenc}
+
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+\author{
+Stephanie Kobakian\\Queensland University of Technology
+}
+\title{}
+
+\Plainauthor{Stephanie Kobakian}
+\Plaintitle{An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With
+Application to Australian Maps}
+
+\Abstract{
+This algorithm creates a tesselated hexagon display to represent each of
+the spatial polygons. It allocates these hexagon in a manner that
+preserves the spatial relationship of the geographic units. It showcases
+spatial distributions, by emphasising the small geographical regions
+that are often difficult to locate on geographic maps. Spatial
+distributions have been presented on alternative representations of
+geography for many years. In modern times, interactivity and animation
+have begun to play a larger role, as alternative representations have
+been popularised by online news sites, and atlas websites with a focus
+on public consumption. Applications are increasingly widespread,
+especially in the areas of disease mapping, and election results.
+}
+
+\Keywords{spatial, statistics, cartogram}
+
+%% publication information
+%% \Volume{50}
+%% \Issue{9}
+%% \Month{June}
+%% \Year{2012}
+%% \Submitdate{}
+%% \Acceptdate{2012-06-04}
+
+\Address{
+    Stephanie Kobakian\\
+  Queensland University of Technology\\
+  School of Mthematical Sciences, Science and Engineering Faculty,
+  Brisbane, QLD, Australia\\
+  E-mail: \email{stephanie.kobakian@qut.edu.au}\\
+  URL: \url{http://rstudio.com}\\~\\
+  }
+
+% Pandoc header
+
 \usepackage{amsmath}
-biblio-style: jss
-output:
-  rticles::jss_article:
-    fig_caption: true
-    citation_package: natbib
-bibliography: sugarbag.bib
-link-citations: true
----
 
-```{r setup, echo=FALSE, message=FALSE, warning=FALSE, comment = FALSE}
-library(knitcitations)
-library(RefManageR)
-library(sf)
+\begin{document}
 
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-options("citation_format" = "pandoc")
-BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')
-```
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-# Introduction
+The current practice for presenting geogspatial data involves a
+choropleth map display. These maps highlight the geographic patterns in
+geospatially related statistics \citep{SAMGIS}. The land on the map
+space is divided into geographic units, these boundaries are usually
+administrative, such as states or counties. The units are filled with
+colour to represent the value of the statistic \citep{EI}.
 
-<!-- Motivation to map -->
+Australian residents are increasingly congregating around major cities,
+the vast rural areas are often sparsely populated in comparison to the
+urban centres. In Australia, government bodies such as the Australian
+Bureau of Statistics, and the Australian Electoral Commission hold the
+responsibility for the division of geographic units. These boundaries
+are adjusted as the population increases. The division of the population
+into approximately equal population areas results in dramatically
+different square meterage of the geographic areas. This results in an
+unequal attention given to the statistic of each area, this can allow
+misrepresentation of the spatial distributions of human related
+statistics in geographic maps.
 
-The current practice for presenting geogspatial data involves a choropleth map display. These maps highlight the geographic patterns in geospatially related statistics \citep{SAMGIS}.
-The land on the map space is divided into geographic units, these boundaries are usually administrative, such as states or counties.
-The units are filled with colour to represent the value of the statistic \citep{EI}.
+The solution to this visualisation problem begins with the geography.
+Cartograms apply a transformation to the geographic boundaries based on
+the value of the statistic of interest. These displays result in a
+distortion of the map space to represent differences in the statistic
+across the areas \citep{ACCAC}. The statistic of interest is used to
+determine the layout. When using the Australian population, the result
+is a population cartogram that fails to preserve a recognisable display
+due to the difference in size of metropolitan and rural areas
+\citep{ACTUC}, \citep{GOINO}. Contiguous cartograms change the shape of
+an area, preserving boundary relationships of neighbours. Non-contiguous
+cartograms maintain the geographic shape of each area, but lose the
+connection to neighbours as each areas shrinks or grows.
 
-<!-- urbanisation -->
-Australian residents are increasingly congregating around major cities, the vast rural areas are often sparsely populated in comparison to the urban centres. 
-In Australia, government bodies such as the Australian Bureau of Statistics, and the Australian Electoral Commission hold the responsibility for the division of geographic units.
-These boundaries are adjusted as the population increases.
-The division of the population into approximately equal population areas results in dramatically different square meterage of the geographic areas.
-This results in an unequal attention given to the statistic of each area, this can allow misrepresentation of the spatial distributions of human related statistics in geographic maps.
+Alternative maps shift the focus from land area and shape, to the value
+of the statistics in a group of areas. Alternative mapping methods allow
+increased understanding of the spatial distribution of a variable across
+the population, by fairly representing each administrative area. This
+acknowledges that the amount of residents can be different but
+recognises that each area, or person is equally important.
 
-<!-- solutions -->
-The solution to this visualisation problem begins with the geography.
-Cartograms apply a transformation to the geographic boundaries based on the value of the statistic of interest.
-These displays result in a distortion of the map space to represent differences in the statistic across the areas \citep{ACCAC}.
-The statistic of interest is used to determine the layout. When using the
-Australian population, the result is a population cartogram that fails to preserve a recognisable display due to the difference in size of metropolitan and rural areas \citep{ACTUC}, \citep{GOINO}.
-Contiguous cartograms change the shape of an area, preserving boundary relationships of neighbours.
-Non-contiguous cartograms maintain the geographic shape of each area, but lose the connection to neighbours as each areas shrinks or grows.
+Tilegrams, Rectangular cartograms \citep{ORC} and Dorling cartograms
+\citep{ACTUC}, all use one simple shape to represent each area. This
+allows preservation of spatial relationships and decreases the emphasis
+from the amount of geographic area. These maps focus on the relationship
+between neighbours attempting to preserve connections, and disregard the
+unique shapes of the administrative boundaries.
 
-Alternative maps shift the focus from land area and shape, to the value of the statistics in a group of areas.
-Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing each administrative area.
-This acknowledges that the amount of residents can be different but recognises that each area, or person is equally important.
+The \pkg{sugarbag} package provides a new method to create tesselated
+hexagon tilegrams. Extending the tilegram to Australian applications
+required preserving the spatial relationships. It emphasises the capital
+cities as population hubs, and emphasises the distances rather than size
+of large, rural geographic units.
 
-Tilegrams, Rectangular cartograms \citep{ORC} and Dorling cartograms \citep{ACTUC}, all use one simple shape to represent each area.
-This allows preservation of spatial relationships and decreases the emphasis from the amount of geographic area.
-These maps focus on the relationship between neighbours attempting to preserve connections, and disregard the unique shapes of the administrative boundaries.
-
-The \pkg{sugarbag} package provides a new method to create tesselated hexagon tilegrams. 
-Extending the tilegram to Australian applications required preserving the spatial relationships.
-It emphasises the capital cities as population hubs, and emphasises the distances rather than size of large, rural geographic units.
-
-# Algorithm
+\hypertarget{algorithm}{%
+\section{Algorithm}\label{algorithm}}
 
@@
 
-There are four steps to create a tesselated hexagon tilegram.
-These steps can be executed by the main function, \code{create_hexmap}, or can be implemented separately for more flexibility.
-There are parameters used in the process that can be provided, if they are not, they will be automatically derived.
+There are four steps to create a tesselated hexagon tilegram. These
+steps can be executed by the main function, \code{create_hexmap}, or can
+be implemented separately for more flexibility. There are parameters
+used in the process that can be provided, if they are not, they will be
+automatically derived.
 
- 1. Create the set of centroids to allocate
- 2. Create the grid of hexagons locations to use
- 3. Allocate each centroid to an available hexagon
- 4. Transform the data for plotting
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Create the set of centroids to allocate
+\item
+  Create the grid of hexagons locations to use
+\item
+  Allocate each centroid to an available hexagon
+\item
+  Transform the data for plotting
+\end{enumerate}
 
-## Parameters
+\hypertarget{parameters}{%
+\subsection{Parameters}\label{parameters}}
 
-The \code{create_hexmap} function requires several parameters, if they are not provided, the information will be derived from the simple features (\pkg{sf}) set of shapes used.
-Users may choose to only use the \code{allocate} function when they wish to use a set of centroids, rather than \pkg{sf} polygons.
+The \code{create_hexmap} function requires several parameters, if they
+are not provided, the information will be derived from the simple
+features (\pkg{sf}) set of shapes used. Users may choose to only use the
+\code{allocate} function when they wish to use a set of centroids,
+rather than \pkg{sf} polygons.
 
 The following must be provided to \code{create_hexmap}:
-```{r table_necessary, echo = FALSE, fig.cap = "This table details the parameters that must be provided to create a hexagon tile map using sugarbag."}
-library(sugarbag)
-library(tidyverse)
 
-knitr::kable(tibble::tibble(parameter = c('shp', 
-  'sf_id',
-  'focal_points'),
-  description = c(
-    'an sf object containing the polygon information', 
-    'name of a column that distinguishes unique areas',
-    'a data frame of reference locations used to allocate hexagons'
-    )), format = "latex")
-```
+\begin{CodeChunk}
 
-## Tasmania
+\begin{tabular}{l|l}
+\hline
+parameter & description\\
+\hline
+shp & an sf object containing the polygon information\\
+\hline
+sf\_id & name of a column that distinguishes unique areas\\
+\hline
+focal\_points & a data frame of reference locations used to allocate hexagons\\
+\hline
+\end{tabular}
 
-The polygon set of Statistical Areas at Level 2 (SA2) \citep{abs2016} of Tasmania in 2016 is provided with the \pkg{sugarbag} package as \code{tas_sa2}. 
-A single column of the data set must be used to identify the unique areas. 
-In this case, the unique SA2 names for each SA2 have been used.
+\end{CodeChunk}
 
-The longitude and latitude centre of the capital cities of Australia are used to allocate areas around the closest capital city.
-Hobart will be the common focal point, as this example uses only the areas in the state of Tasmania.
+\hypertarget{tasmania}{%
+\subsection{Tasmania}\label{tasmania}}
 
-```{r capital_cities}
-data(capital_cities)
-```
+The polygon set of Statistical Areas at Level 2 (SA2) \citep{abs2016} of
+Tasmania in 2016 is provided with the \pkg{sugarbag} package as
+\code{tas_sa2}. A single column of the data set must be used to identify
+the unique areas. In this case, the unique SA2 names for each SA2 have
+been used.
 
-The following parameters will be determined within \code{create_hexmap} if they are not provided. They are created throughout the following example:
+The longitude and latitude centre of the capital cities of Australia are
+used to allocate areas around the closest capital city. Hobart will be
+the common focal point, as this example uses only the areas in the state
+of Tasmania.
 
-```{r parameters, echo = FALSE, fig.cap = "This table details the additional parameters that are used to create a hexagon tile map using sugarbag."}
-knitr::kable(tibble(parameter = c('buffer_dist', 'hex_size',  'hex_filter', 'width'),
-  description = c('a float value for distance in degrees to extend beyond the geometry provided',
-    'a float value in degrees for the diameter of the hexagons', 'amount of hexagons around centroid to consider for allocation',
-    'the angle used to filter the grid points around a centroid')), format = "latex")
-```
+\begin{CodeChunk}
 
-## Create the set of centroid points
+\begin{CodeInput}
+R> data(capital_cities)
+\end{CodeInput}
+\end{CodeChunk}
 
-Individual \pkg{sugarbag} functions can be used outside of the main function.
-The set of polygons should be provided as an \pkg{sf} object, this is a data frame containing a \code{geometry} column. The \code{read_shape} function can assist in creating this object.
+The following parameters will be determined within \code{create_hexmap}
+if they are not provided. They are created throughout the following
+example:
 
-The centroids can be derived from the set of polygons using the \code{create_centroids} function:
-```{r cents}
-centroids <- create_centroids(shp_sf = tas_sa2, sf_id = "SA2_NAME16")
-```
+\begin{CodeChunk}
 
-```{r centroids_plot, out.width = "100%", echo = FALSE, eval = FALSE, fig.cap="The geographic shapes of the Statistical Areas of Tasmania at Level 2.
-The points show the locations of the centroids of the SA2 areas."}
-knitr::include_graphics(path = "figures/1centroids.png")
-```
+\begin{tabular}{l|l}
+\hline
+parameter & description\\
+\hline
+buffer\_dist & a float value for distance in degrees to extend beyond the geometry provided\\
+\hline
+hex\_size & a float value in degrees for the diameter of the hexagons\\
+\hline
+hex\_filter & amount of hexagons around centroid to consider for allocation\\
+\hline
+width & the angle used to filter the grid points around a centroid\\
+\hline
+\end{tabular}
 
-## Create the hexagon grid points
+\end{CodeChunk}
 
-A tilegram presents areas on a tellesated set of tiles.
-The grid is created to ensure tessellation between the hexagons.
+\hypertarget{create-the-set-of-centroid-points}{%
+\subsection{Create the set of centroid
+points}\label{create-the-set-of-centroid-points}}
 
-The grid of possible hexagon centroids is made using the \code{create_grid} function.
-The grid creation requires several steps.
+Individual \pkg{sugarbag} functions can be used outside of the main
+function. The set of polygons should be provided as an \pkg{sf} object,
+this is a data frame containing a \code{geometry} column. The
+\code{read_shape} function can assist in creating this object.
+
+The centroids can be derived from the set of polygons using the
+\code{create_centroids} function:
+
+\begin{CodeChunk}
+
+\begin{CodeInput}
+R> centroids <- create_centroids(shp_sf = tas_sa2, sf_id = "SA2_NAME16")
+\end{CodeInput}
+\end{CodeChunk}
+
+\hypertarget{create-the-hexagon-grid-points}{%
+\subsection{Create the hexagon grid
+points}\label{create-the-hexagon-grid-points}}
+
+A tilegram presents areas on a tellesated set of tiles. The grid is
+created to ensure tessellation between the hexagons.
+
+The grid of possible hexagon centroids is made using the
+\code{create_grid} function. The grid creation requires several steps.
 It uses the centroids, the hexagon size and the buffer distance.
 
-```{r grid}
-grid <- create_grid(centroids = centroids, hex_size = 0.2, buffer_dist = 1.2)
-```
+\begin{CodeChunk}
 
-### Step 1: Creating a tesselated grid
+\begin{CodeInput}
+R> grid <- create_grid(centroids = centroids, hex_size = 0.2, buffer_dist = 1.2)
+\end{CodeInput}
+\end{CodeChunk}
 
-A set of longitude columns, and latitude rows are created to define the locations of the hexagons. The distance between each row and column is defined by the size specified as \code{hex_size}.
-The minimum and maximum, longitude and latitude values of the centroid locations are found.
-Equally spaced columns are created from the minimum longitude minus the buffer distance, up to the maximum longitude plus the buffer distance.
-The rows are then created from the latitude values and the buffer distance.
-An individual hexagon location is created from all intersections of the longitude columns and latitude rows.
+\hypertarget{step-1-creating-a-tesselated-grid}{%
+\subsubsection{Step 1: Creating a tesselated
+grid}\label{step-1-creating-a-tesselated-grid}}
 
-A square grid could be used for sqaure tiles, but it will not facilitate tessellated hexagons.
-Figure \ref{fig:grid2} allows for hexagons, as every second latitude row on the grid is shifted right, by half of the hexagon size.
+A set of longitude columns, and latitude rows are created to define the
+locations of the hexagons. The distance between each row and column is
+defined by the size specified as \code{hex_size}. The minimum and
+maximum, longitude and latitude values of the centroid locations are
+found. Equally spaced columns are created from the minimum longitude
+minus the buffer distance, up to the maximum longitude plus the buffer
+distance. The rows are then created from the latitude values and the
+buffer distance. An individual hexagon location is created from all
+intersections of the longitude columns and latitude rows.
 
-```{r grid2, fig.cap="Grid points to create a tilegram.", out.width = "100%", echo = FALSE}
-knitr::include_graphics(path = "figures/2grid.png")
-```
+A square grid could be used for sqaure tiles, but it will not facilitate
+tessellated hexagons. Figure \ref{fig:grid2} allows for hexagons, as
+every second latitude row on the grid is shifted right, by half of the
+hexagon size.
 
-### Step 2: Rolling windows
+\begin{CodeChunk}
+\begin{figure}
 
-Not all of the grid points will be used, especially if islands result in a large grid space.
-To filter the grid for appropriate points for allocation,
-the \code{create_buffer} function is called within \code{create_grid}.
-It finds the grid points needed to best capture the set of centroids on a hexagon tile map.
+{\centering \includegraphics[width=1\linewidth]{figures/2grid}
 
-For each centroid location, the closest latitude row and longitude column are found. Then rows and columns of centroids are divided into 20 groups.
-The amount of rows in each latitude group and the amount of columns in each longitude group are used as the width of rolling windows.
-The rolling windows can be seen on the This will tailor the available grid points to those most likely to be used.
-It also helps reduce the amount of time taken, as it decreases the amount of points considered for each centroid allocation.
+}
 
-The first rolling window function finds the minimum and maximum centroid values for the sliding window groups of longitude columns and the groups of latitude rows.
+\caption[Grid points to create a tilegram]{Grid points to create a tilegram.}\label{fig:grid2}
+\end{figure}
+\end{CodeChunk}
 
-The second rolling window function finds the average of the rolling minimum and maximum centroid values, for the longitude columns and latitude rows.
+\hypertarget{step-2-rolling-windows}{%
+\subsubsection{Step 2: Rolling windows}\label{step-2-rolling-windows}}
 
-### Step 3: Filtering the grid
+Not all of the grid points will be used, especially if islands result in
+a large grid space. To filter the grid for appropriate points for
+allocation, the \code{create_buffer} function is called within
+\code{create_grid}. It finds the grid points needed to best capture the
+set of centroids on a hexagon tile map.
 
-Only the grid points between the rolling average of the minimum and maximum centroid values are kept, for each row and column of the grid.
+For each centroid location, the closest latitude row and longitude
+column are found. Then rows and columns of centroids are divided into 20
+groups. The amount of rows in each latitude group and the amount of
+columns in each longitude group are used as the width of rolling
+windows. The rolling windows can be seen on the This will tailor the
+available grid points to those most likely to be used. It also helps
+reduce the amount of time taken, as it decreases the amount of points
+considered for each centroid allocation.
 
-```{r filter_grid, fig.cap = "All possible hexagon locations from the initial grid are shown with blue outlines.
+The first rolling window function finds the minimum and maximum centroid
+values for the sliding window groups of longitude columns and the groups
+of latitude rows.
+
+The second rolling window function finds the average of the rolling
+minimum and maximum centroid values, for the longitude columns and
+latitude rows.
+
+\hypertarget{step-3-filtering-the-grid}{%
+\subsubsection{Step 3: Filtering the
+grid}\label{step-3-filtering-the-grid}}
+
+Only the grid points between the rolling average of the minimum and
+maximum centroid values are kept, for each row and column of the grid.
+
+\begin{CodeChunk}
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{figures/3grid}
+
+}
+
+\caption[All possible hexagon locations from the initial grid are shown with blue outlines]{All possible hexagon locations from the initial grid are shown with blue outlines.
 The blue dots shown the grid points left as to choose from after the buffer step.
-The rolling windows to the right show the rows used to filter the hexagon locations.", echo = FALSE, out.width = "100%"}
-knitr::include_graphics(path = "figures/3grid.png", dpi = 300)
-```
+The rolling windows to the right show the rows used to filter the hexagon locations.}\label{fig:filter_grid}
+\end{figure}
+\end{CodeChunk}
 
-## Centroid to focal point distance
+\hypertarget{centroid-to-focal-point-distance}{%
+\subsection{Centroid to focal point
+distance}\label{centroid-to-focal-point-distance}}
 
-The distance between each centroid in the set, and each of the focal points provided is calculated.
-The name of the closest focal point, and the distance and angle from focal point to polygon centroid is joined to polygon data set.
-To minimise time taken for this step, only Tasmania's capital city Hobart is provided.
-The order for allocation is determined by the distance between the polygon centroid and it's closest focal point.
-The points are arranged from the centroid closest to the focal points, to the furthest.
+The distance between each centroid in the set, and each of the focal
+points provided is calculated. The name of the closest focal point, and
+the distance and angle from focal point to polygon centroid is joined to
+polygon data set. To minimise time taken for this step, only Tasmania's
+capital city Hobart is provided. The order for allocation is determined
+by the distance between the polygon centroid and it's closest focal
+point. The points are arranged from the centroid closest to the focal
+points, to the furthest.
 
-## Allocate each centroid to a hexagon grid point
+\hypertarget{allocate-each-centroid-to-a-hexagon-grid-point}{%
+\subsection{Allocate each centroid to a hexagon grid
+point}\label{allocate-each-centroid-to-a-hexagon-grid-point}}
 
-Allocation of all centroids takes place using the set of polygon centroids and the hexagon map grid. 
-Centroid allocation begins with the closest centroid to a focal point.
-This will preserve spatial relationships with the focal point, as the inner city areas are allocated first, they will be placed closest to the capital, and the areas that are further will then be accommodated.
-Only the hexagon grid points that have not yet been allocated are considered.
+Allocation of all centroids takes place using the set of polygon
+centroids and the hexagon map grid. Centroid allocation begins with the
+closest centroid to a focal point. This will preserve spatial
+relationships with the focal point, as the inner city areas are
+allocated first, they will be placed closest to the capital, and the
+areas that are further will then be accommodated. Only the hexagon grid
+points that have not yet been allocated are considered.
 
-The possible hexagon locations consider for a centroid location are determined by the \code{hex_filter}.
-This is the maximum amount of hexagons between the centroid and the furthest considered hexagon.
-It is used to subset possible grid points to only those surrounding the polygon centroid within an appropriate range.
-A smaller distance will increase speed, but can decrease accuracy if the angle width increases.
+The possible hexagon locations consider for a centroid location are
+determined by the \code{hex_filter}. This is the maximum amount of
+hexagons between the centroid and the furthest considered hexagon. It is
+used to subset possible grid points to only those surrounding the
+polygon centroid within an appropriate range. A smaller distance will
+increase speed, but can decrease accuracy if the angle width increases.
 
-```{r centroids, eval = FALSE}
-hexmap_allocation <- allocate(
-  centroids = centroids %>% select(SA2_NAME16, longitude, latitude),
-  sf_id = "SA2_NAME16",
-  hex_grid = grid,
-  hex_size = 0.2, # same size used in create_grid
-  hex_filter = 10,
-  width = 35,
-  focal_points = capital_cities,
-  verbose = TRUE)
-```
+\begin{CodeChunk}
+
+\begin{CodeInput}
+R> hexmap_allocation <- allocate(
+R>   centroids = centroids %>% select(SA2_NAME16, longitude, latitude),
+R>   sf_id = "SA2_NAME16",
+R>   hex_grid = grid,
+R>   hex_size = 0.2, # same size used in create_grid
+R>   hex_filter = 10,
+R>   width = 35,
+R>   focal_points = capital_cities,
+R>   verbose = TRUE)
+\end{CodeInput}
+\end{CodeChunk}
 
@@
 
-### Step 1: Filter the grid for unassigned hexagon points
+\hypertarget{step-1-filter-the-grid-for-unassigned-hexagon-points}{%
+\subsubsection{Step 1: Filter the grid for unassigned hexagon
+points}\label{step-1-filter-the-grid-for-unassigned-hexagon-points}}
 
-Keep only the available hexagon points, this will prevent multiple areas being allocated to the same hexagon.
+Keep only the available hexagon points, this will prevent multiple areas
+being allocated to the same hexagon.
 
-### Step 2: Filter the grid points for those closest to the centroid
+\hypertarget{step-2-filter-the-grid-points-for-those-closest-to-the-centroid}{%
+\subsubsection{Step 2: Filter the grid points for those closest to the
+centroid}\label{step-2-filter-the-grid-points-for-those-closest-to-the-centroid}}
 
-This will allow only the closest points that are not yet assigned, to be considered.
+This will allow only the closest points that are not yet assigned, to be
+considered.
 
-A box of possible hexagon locations around the centroid. The corners of the box may not look square as the buffer has already removed unnecessary points from over the ocean.
+A box of possible hexagon locations around the centroid. The corners of
+the box may not look square as the buffer has already removed
+unnecessary points from over the ocean.
 
-The algorithm then removes the outer corners of the square, creating a circle of points, by only keeping points within a certain radial distance around the original centroid location.
+The algorithm then removes the outer corners of the square, creating a
+circle of points, by only keeping points within a certain radial
+distance around the original centroid location.
 
-```{r buffers, echo = FALSE, out.width = "100%"}
-knitr::include_graphics(path = "figures/4grid.png")
-```
+\begin{CodeChunk}
 
-The \code{width} parameter is used to take a slice of the remaining points.
-This uses the angle from the closest capital city, to the current centroid.
-This allows the spatial relationship to be preserved, even when it is allocated to a hexagon that is further from the focal point then the original centroid location.
+\begin{center}\includegraphics[width=1\linewidth]{figures/4grid} \end{center}
 
-If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded, only when a maximum distance is reached will the angle expand to accommodate more possible grid points.
-The angle begins at 30 degrees by default, and will increase if no points can be found within the \code{hex_filter} distance.
-The allocation is returned and combined with the data relating to each polygon.
+\end{CodeChunk}
 
-```{r buffs, out.width = "100%", echo = FALSE}
-knitr::include_graphics(path = "figures/6allocate.png")
-```
+The \code{width} parameter is used to take a slice of the remaining
+points. This uses the angle from the closest capital city, to the
+current centroid. This allows the spatial relationship to be preserved,
+even when it is allocated to a hexagon that is further from the focal
+point then the original centroid location.
 
-The following code creates a map for all the Statistical Areas at Level 2 in Tasmania:
+If no available hexagon grid point is found within the original filter
+distance and angle, the distance is expanded, only when a maximum
+distance is reached will the angle expand to accommodate more possible
+grid points.\\
+The angle begins at 30 degrees by default, and will increase if no
+points can be found within the \code{hex_filter} distance. The
+allocation is returned and combined with the data relating to each
+polygon.
 
-# Using sugarbag
+\begin{CodeChunk}
 
-```{r full_hexmapcode, echo = TRUE, warning = FALSE, message = FALSE}
+\begin{center}\includegraphics[width=1\linewidth]{figures/6allocate} \end{center}
 
-# install.packages("sugarbag")
-library(sugarbag)
+\end{CodeChunk}
 
-# Create centroids set
-centroids <- create_centroids(tas_sa2, "SA2_NAME16")
+The following code creates a map for all the Statistical Areas at Level
+2 in Tasmania:
 
-# Create hexagon location grid
-grid <- create_grid(centroids = centroids,
-    hex_size = 0.2,
-    buffer_dist = 1.2)
+\hypertarget{using-sugarbag}{%
+\section{Using sugarbag}\label{using-sugarbag}}
 
-# Allocate polygon centroids to hexagon grid points
-hex_allocated <- allocate(
-  centroids = centroids,
-  hex_grid = grid,
-  sf_id = "SA2_NAME16",
-  # same column used in create_centroids
-  hex_size = 0.2,
-  # same size used in create_grid
-  hex_filter = 10,
-  use_neighbours = tas_sa2,
-  focal_points = capital_cities %>% filter(points == "Hobart"),
-  width = 35,
-  verbose = FALSE)
-```
+\begin{CodeChunk}
 
-## Neighbour relationships
+\begin{CodeInput}
+R> # install.packages("sugarbag")
+R> library(sugarbag)
+R> 
+R> # Create centroids set
+R> centroids <- create_centroids(tas_sa2, "SA2_NAME16")
+R> 
+R> # Create hexagon location grid
+R> grid <- create_grid(centroids = centroids,
+R+     hex_size = 0.2,
+R+     buffer_dist = 1.2)
+R> 
+R> # Allocate polygon centroids to hexagon grid points
+R> hex_allocated <- allocate(
+R+   centroids = centroids,
+R+   hex_grid = grid,
+R+   sf_id = "SA2_NAME16",
+R+   # same column used in create_centroids
+R+   hex_size = 0.2,
+R+   # same size used in create_grid
+R+   hex_filter = 10,
+R+   use_neighbours = tas_sa2,
+R+   focal_points = capital_cities %>% filter(points == "Hobart"),
+R+   width = 35,
+R+   verbose = FALSE)
+\end{CodeInput}
+\end{CodeChunk}
 
-It is possible to encourage the use of neighbourhood relationshipd, for stronger preservation of neighbour relations.
+\hypertarget{neighbour-relationships}{%
+\subsection{Neighbour relationships}\label{neighbour-relationships}}
 
-An additional step may be included to allow the neighbours that have alredy been allocated to influence the placement of the current centroid. 
-This requires respecifying the \code{sf} object as the argument for the \code{use_neighbours} parameter.
-This calculates neighbours using intersections of their polygons.
-This occurs for all areas before any allocations begin.
+It is possible to encourage the use of neighbourhood relationshipd, for
+stronger preservation of neighbour relations.
 
-For the current centroid, the list of neighbours is consulted.
-If any neighbour was already allocated, the surrounding hexagons on the grid are prioritised.
-For multiple neighbours, the neighbouring hexagon grid points are aggregated and considered in order of distance from the original centroid.
+An additional step may be included to allow the neighbours that have
+alredy been allocated to influence the placement of the current
+centroid. This requires respecifying the \code{sf} object as the
+argument for the \code{use_neighbours} parameter. This calculates
+neighbours using intersections of their polygons. This occurs for all
+areas before any allocations begin.
 
-# Australian Cancer Atlas
+For the current centroid, the list of neighbours is consulted. If any
+neighbour was already allocated, the surrounding hexagons on the grid
+are prioritised. For multiple neighbours, the neighbouring hexagon grid
+points are aggregated and considered in order of distance from the
+original centroid.
 
-The hexagon tile map visualisation method can be applied to the Australian Cancer Atlas data.
-A small example of Lung Cancer Standardised Incidence Rates (SIRs) allows two views of the same data produced by the Australian Cancer Atlas.
-This small example in Figure  \ref{fig:sir} shows the group of blue areas in the Hobart CBD more prominently in the hexagon tile map (b).
-The small red areas visible in the choropleth map (a) along the north coast are much larger in the hexagon tile maps.
-The hexagon tile map shows less yellow, this no longer overwhelms the map space with the information regarding the more rural areas.
+\hypertarget{australian-cancer-atlas}{%
+\section{Australian Cancer Atlas}\label{australian-cancer-atlas}}
 
-```{r sir, out.width = "100%", echo = FALSE, fig.cap = "The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2.
-A choropleth map (a) of Standardised Incidence Rates (SIRs) is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented."}
-knitr::include_graphics(path = "figures/7SIR.png")
-```
+The hexagon tile map visualisation method can be applied to the
+Australian Cancer Atlas data. A small example of Lung Cancer
+Standardised Incidence Rates (SIRs) allows two views of the same data
+produced by the Australian Cancer Atlas. This small example in Figure
+\ref{fig:sir} shows the group of blue areas in the Hobart CBD more
+prominently in the hexagon tile map (b). The small red areas visible in
+the choropleth map (a) along the north coast are much larger in the
+hexagon tile maps. The hexagon tile map shows less yellow, this no
+longer overwhelms the map space with the information regarding the more
+rural areas.
 
-# Conclusion
+\begin{CodeChunk}
+\begin{figure}
 
-It is possible to use alternative maps to communicate spatial distributions.While a choropleth map display is the current practice spatial visualisation of geographical data.
-Current methods do not always work for Australia due to the large gaps between densely populated capital cities.
-The administrative boundaries may distract from the statistics, communicated using colour.
+{\centering \includegraphics[width=1\linewidth]{figures/7SIR}
 
-Alternative maps highlight the value of the statistics across the geographic units.
-Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing each administrative area.
-This acknowledges that the amount of residents can be different but recognises that each population area is equally important.
-The solution to this visualisation problem has equally sized areas, with neighbourhood boundary connections.
-This map algorithm is implemented in the @sugarbag package written for @R.
-The \pkg{sugarbag} package creates tesselated hexagon tilegrams.
-The Australian application preserves the spatial relationships, emphasising capital cities.
-The hexagon tile map is a visualisation solution that highlights spatial distributions.
+}
+
+\caption[The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2]{The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2.
+A choropleth map (a) of Standardised Incidence Rates (SIRs) is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented.}\label{fig:sir}
+\end{figure}
+\end{CodeChunk}
+
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
+
+It is possible to use alternative maps to communicate spatial
+distributions.While a choropleth map display is the current practice
+spatial visualisation of geographical data. Current methods do not
+always work for Australia due to the large gaps between densely
+populated capital cities. The administrative boundaries may distract
+from the statistics, communicated using colour.
+
+Alternative maps highlight the value of the statistics across the
+geographic units. Alternative mapping methods allow increased
+understanding of the spatial distribution of a variable across the
+population, by fairly representing each administrative area. This
+acknowledges that the amount of residents can be different but
+recognises that each population area is equally important. The solution
+to this visualisation problem has equally sized areas, with
+neighbourhood boundary connections. This map algorithm is implemented in
+the \citet{sugarbag} package written for \citet{R}. The \pkg{sugarbag}
+package creates tesselated hexagon tilegrams. The Australian application
+preserves the spatial relationships, emphasising capital cities. The
+hexagon tile map is a visualisation solution that highlights spatial
+distributions.
+
+\bibliography{sugarbag.bib}
+
+\end{document}

### 2020-01-10 kobakian_sugarbag_jss/kobakian_sugarbag_jss.R

@@ -1,0 +1,485 @@
+
+###########################################################
+## LIBRARIES
+## sugarbag to create tesellated hexagon map
+## tidyverse for tidy data manipulation, not necessary
+
+library(sugarbag)
+library(dplyr)
+library(ggplot2)
+library(gridExtra)
+library(purrr)
+library(sf)
+
+
+###########################################################
+## DATA
+## load data files from sugarbag
+data(capital_cities)
+
+sa2 <- absmapsdata::sa22011  %>% 
+  filter(state_name_2011 == "Tasmania")
+
+# Join with cancer data from Australian Cancer Atlas
+aus_colours <- function(sir_p50){
+  value <- case_when(
+    sir_p50 < 0.5 ~ "#33809d",
+    sir_p50 >= 0.5 & sir_p50 < 0.75 ~ "#aec6c7",
+    sir_p50 >= 0.75 & sir_p50 < 1.5 ~ "#fff4bc",
+    sir_p50 >= 1.25 & sir_p50 < 1.5 ~ "#ff9a64",
+    sir_p50 >= 1.5 ~ "#ff3500",
+    TRUE ~ "#FFFFFF")
+  return(value)
+}
+
+SIR <- read_csv("kobakian_sugarbag_jss/data/SIR Downloadable Data.csv") %>% 
+  dplyr::select(Cancer_name, SA2_name, Sex_name, p50) %>% 
+  filter(Cancer_name == "Lung", Sex_name == "Males") %>% 
+  filter(SA2_name %in% sa2$sa2_name_2011) %>% 
+  mutate(SIR = map_chr(p50, aus_colours)) 
+
+# No data for "Mount Wellington", "Wilderness - East", "Wilderness - West" 
+###########################################################
+## CENTROIDS
+## Use the create_centroids function to find polygon centroids:
+centroids <- create_centroids(shp_sf = sa2, sf_id = "sa2_name_2011")
+
+## Join the data from the original data set to the set of centroids by sf_id
+centroids <- left_join(centroids,
+  sf::st_drop_geometry(sa2), by = "sa2_name_2011")
+
+###########################################################
+## CENTROID PLOTS
+## Fortify the underlying geographical areas for plotting
+fort_sa2 <- fortify_sfc(sa2)
+
+cents <- ggplot() + 
[…]

### 2020-01-10 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
fixed author info

@@
     address: >
-      School of Mthematical Sciences,
+      School of Mathematical Sciences,
       Science and Engineering Faculty,
@@
     email: \email{stephanie.kobakian@qut.edu.au}
-    url: http://rstudio.com
+  - name: Dianne Cook
+    affiliation: Monash University
+    address: >
+      Department of Econometrics and Business Statistics,
+      Melbourne, VIC, Australia
+    email: \email{dicook@monash.edu}
 title:
@@
 
-## Tasmania
+## Polygon set
 

### 2020-01-10 kobakian_sugarbag_jss/kobakian_sugarbag_jss.tex
fixed author info

@@
 \author{
-Stephanie Kobakian\\Queensland University of Technology
+Stephanie Kobakian\\Queensland University of Technology \And Dianne Cook\\Monash University
 }
@@
 
-\Plainauthor{Stephanie Kobakian}
+\Plainauthor{Stephanie Kobakian, Dianne Cook}
 \Plaintitle{An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With
@@
   Queensland University of Technology\\
-  School of Mthematical Sciences, Science and Engineering Faculty,
+  School of Mathematical Sciences, Science and Engineering Faculty,
   Brisbane, QLD, Australia\\
   E-mail: \email{stephanie.kobakian@qut.edu.au}\\
-  URL: \url{http://rstudio.com}\\~\\
+
+      Dianne Cook\\
+  Monash University\\
+  Department of Econometrics and Business Statistics, Melbourne, VIC,
+  Australia\\
+  E-mail: \email{dicook@monash.edu}\\
+
   }

### 2020-01-12 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
suggestions on paper to finish it, see XXX

@@
 
-The current practice for presenting geogspatial data involves a choropleth map display. These maps highlight the geographic patterns in geospatially related statistics \citep{SAMGIS}.
+The current practice for presenting geospatial data involves a choropleth map display. These maps highlight the geographic patterns in geospatially related statistics \citep{SAMGIS}.
 The land on the map space is divided into geographic units, these boundaries are usually administrative, such as states or counties.
@@
 
-The following code creates a map for all the Statistical Areas at Level 2 in Tasmania:
+## Neighbour relationships
+
+It is possible to encourage the use of neighbourhood relationshipd, for stronger preservation of neighbour relations.
+
+An additional step may be included to allow the neighbours that have alredy been allocated to influence the placement of the current centroid. 
+This requires respecifying the \code{sf} object as the argument for the \code{use_neighbours} parameter.
+This calculates neighbours using intersections of their polygons.
+This occurs for all areas before any allocations begin.
+
+For the current centroid, the list of neighbours is consulted.
+If any neighbour was already allocated, the surrounding hexagons on the grid are prioritised.
+For multiple neighbours, the neighbouring hexagon grid points are aggregated and considered in order of distance from the original centroid.
 
@@
 
-```{r full_hexmapcode, echo = TRUE, warning = FALSE, message = FALSE}
+## Installation
 
-# install.packages("sugarbag")
+The package can be installed from CRAN:
+
+```{r eval=FALSE}
+install.packages("sugarbag")
+```
+
+and the development version can be install from the GitHub repository:
+
+```{r eval=FALSE}
+devtools::install_github("srkobakian","sugarbag")
+```
+
+Load the library into your R session with:
+
+```{r eval=FALSE}
 library(sugarbag)
+```
+
+## Creating a hexagon tile map
+
+The following code creates the hexagon tile map for all the Statistical Areas at Level 2 in Tasmania.
+
+```{r full_hexmapcode, echo = TRUE, warning = FALSE, message = FALSE, eval=FALSE}
+# Load data
+data(tas_sa2)
 
@@
 
-# Create hexagon location grid
+# Create hexagon grid
 grid <- create_grid(centroids = centroids,
@@
   verbose = FALSE)
+
+# Prepare to plot
+fort_hex <- fortify_hexagon(data = hex_allocated, sf_id = "SA2_NAME16", hex_size = 0.2)
+
+# Make a plot
+library(ggplot2)
+ggplot(fort_hex) + 
+  geom_polygon(aes(x=long, y=lat, group=hex_id, fill = lat)) +
+  scale_fill_distiller("", palette="PRGn")
 ```
 
-## Neighbour relationships
+# Applications
 
-It is possible to encourage the use of neighbourhood relationshipd, for stronger preservation of neighbour relations.
+## Australian Cancer Atlas
 
-An additional step may be included to allow the neighbours that have alredy been allocated to influence the placement of the current centroid. 
-This requires respecifying the \code{sf} object as the argument for the \code{use_neighbours} parameter.
-This calculates neighbours using intersections of their polygons.
-This occurs for all areas before any allocations begin.
-
-For the current centroid, the list of neighbours is consulted.
-If any neighbour was already allocated, the surrounding hexagons on the grid are prioritised.
-For multiple neighbours, the neighbouring hexagon grid points are aggregated and considered in order of distance from the original centroid.
-
-# Australian Cancer Atlas
+XXX Show whole Australia male liver cancer with choropleth and hexagon tile map, and discuss the pros/cons of the result, for understanding the incidence.
 
@@
 
+XXX Move this image (ref: sir) to the end of the algorithm section to illustrate the final result for Tassie
+
 ```{r sir, out.width = "100%", echo = FALSE, fig.cap = "The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2.
@@
 
+## Election results
+
+XXX Code from web site, and a couple of paragraphs of explanation
+
+# Animation
+
+XXX show how to make an animation, and make a link to a web page where the animation can be viewed
+
 # Conclusion
+
+Structure of conclusions: (1) summarise paper, discuss limitations, suggest future directions
 
@@
 The hexagon tile map is a visualisation solution that highlights spatial distributions.
+
+# Acknowledgements
+
+The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations.
+They would also like to thank Professor Kerrie Mengersen and Dr Earl Duncan for suggestions and comments.
+Mitch O'Hara-Wild provided assistance with some parts of the algorithm and code.
+Sayani Gupta provided helpful advice on parts of this paper.
+
+The code for sugarbag can be found at XXX, along with details on installation and usage.

### 2020-01-12 kobakian_sugarbag_jss/kobakian_sugarbag_jss.tex
suggestions on paper to finish it, see XXX

@@
 
-The current practice for presenting geogspatial data involves a
+The current practice for presenting geospatial data involves a
 choropleth map display. These maps highlight the geographic patterns in
@@
 
-\hypertarget{tasmania}{%
-\subsection{Tasmania}\label{tasmania}}
+\hypertarget{polygon-set}{%
+\subsection{Polygon set}\label{polygon-set}}
 
@@
 
-The following code creates a map for all the Statistical Areas at Level
-2 in Tasmania:
-
-\hypertarget{using-sugarbag}{%
-\section{Using sugarbag}\label{using-sugarbag}}
-
-\begin{CodeChunk}
-
-\begin{CodeInput}
-R> # install.packages("sugarbag")
-R> library(sugarbag)
-R> 
-R> # Create centroids set
-R> centroids <- create_centroids(tas_sa2, "SA2_NAME16")
-R> 
-R> # Create hexagon location grid
-R> grid <- create_grid(centroids = centroids,
-R+     hex_size = 0.2,
-R+     buffer_dist = 1.2)
-R> 
-R> # Allocate polygon centroids to hexagon grid points
-R> hex_allocated <- allocate(
-R+   centroids = centroids,
-R+   hex_grid = grid,
-R+   sf_id = "SA2_NAME16",
-R+   # same column used in create_centroids
-R+   hex_size = 0.2,
-R+   # same size used in create_grid
-R+   hex_filter = 10,
-R+   use_neighbours = tas_sa2,
-R+   focal_points = capital_cities %>% filter(points == "Hobart"),
-R+   width = 35,
-R+   verbose = FALSE)
-\end{CodeInput}
-\end{CodeChunk}
-
 \hypertarget{neighbour-relationships}{%
@@
 
+\hypertarget{using-sugarbag}{%
+\section{Using sugarbag}\label{using-sugarbag}}
+
+\hypertarget{installation}{%
+\subsection{Installation}\label{installation}}
+
+The package can be installed from CRAN:
+
+\begin{CodeChunk}
+
+\begin{CodeInput}
+R> install.packages("sugarbag")
+\end{CodeInput}
+\end{CodeChunk}
+
+and the development version can be install from the GitHub repository:
+
+\begin{CodeChunk}
+
+\begin{CodeInput}
+R> devtools::install_github("srkobakian","sugarbag")
+\end{CodeInput}
+\end{CodeChunk}
+
+Load the library into your R session with:
+
+\begin{CodeChunk}
+
+\begin{CodeInput}
+R> library(sugarbag)
+\end{CodeInput}
+\end{CodeChunk}
+
+\hypertarget{creating-a-hexagon-tile-map}{%
+\subsection{Creating a hexagon tile
+map}\label{creating-a-hexagon-tile-map}}
+
+The following code creates the hexagon tile map for all the Statistical
+Areas at Level 2 in Tasmania.
+
+\begin{CodeChunk}
+
+\begin{CodeInput}
+R> # Load data
+R> data(tas_sa2)
+R> 
+R> # Create centroids set
+R> centroids <- create_centroids(tas_sa2, "SA2_NAME16")
+R> 
+R> # Create hexagon grid
+R> grid <- create_grid(centroids = centroids,
+R>     hex_size = 0.2,
+R>     buffer_dist = 1.2)
+R> 
+R> # Allocate polygon centroids to hexagon grid points
+R> hex_allocated <- allocate(
+R>   centroids = centroids,
+R>   hex_grid = grid,
+R>   sf_id = "SA2_NAME16",
+R>   # same column used in create_centroids
+R>   hex_size = 0.2,
+R>   # same size used in create_grid
+R>   hex_filter = 10,
+R>   use_neighbours = tas_sa2,
+R>   focal_points = capital_cities %>% filter(points == "Hobart"),
+R>   width = 35,
+R>   verbose = FALSE)
+R> 
+R> # Prepare to plot
+R> fort_hex <- fortify_hexagon(data = hex_allocated, sf_id = "SA2_NAME16", hex_size = 0.2)
+R> 
+R> # Make a plot
+R> library(ggplot2)
+R> ggplot(fort_hex) + 
+R>   geom_polygon(aes(x=long, y=lat, group=hex_id, fill = lat)) +
+R>   scale_fill_distiller("", palette="PRGn")
+\end{CodeInput}
+\end{CodeChunk}
+
+\hypertarget{applications}{%
+\section{Applications}\label{applications}}
+
 \hypertarget{australian-cancer-atlas}{%
-\section{Australian Cancer Atlas}\label{australian-cancer-atlas}}
+\subsection{Australian Cancer Atlas}\label{australian-cancer-atlas}}
+
+XXX Show whole Australia male liver cancer with choropleth and hexagon
+tile map, and discuss the pros/cons of the result, for understanding the
+incidence.
 
@@
 rural areas.
+
+XXX Move this image (ref: sir) to the end of the algorithm section to
+illustrate the final result for Tassie
 
@@
 
+\hypertarget{election-results}{%
+\subsection{Election results}\label{election-results}}
+
+XXX Code from web site, and a couple of paragraphs of explanation
+
+\hypertarget{animation}{%
+\section{Animation}\label{animation}}
+
+XXX show how to make an animation, and make a link to a web page where
+the animation can be viewed
+
 \hypertarget{conclusion}{%
 \section{Conclusion}\label{conclusion}}
+
+Structure of conclusions: (1) summarise paper, discuss limitations,
+suggest future directions
 
@@
 
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
+
+The authors would like to thank the Australian Cancer Atlas team for
+discussions regarding alternative spatial visualizations. They would
+also like to thank Professor Kerrie Mengersen and Dr Earl Duncan for
+suggestions and comments. Mitch O'Hara-Wild provided assistance with
+some parts of the algorithm and code. Sayani Gupta provided helpful
+advice on parts of this paper.
+
+The code for sugarbag can be found at XXX, along with details on
+installation and usage.
+
 \bibliography{sugarbag.bib}

### 2020-01-13 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
Show title

@@
 title: 
-  plain: An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With Application to Australian Maps   
+  formatted: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With Application to Australian Maps"
+  plain: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map,\nWith Application to Australian Maps"  
 abstract: >
@@
 
+A complete hexagon tile map of Tasmania is created by applying the algorithm steps to each centroid.
+The hexagon tile map visualisation is used below to visualise the Australian Cancer Atlas data.
+Two views of the same data are produced by filling according to the Lung Cancer Standardised Incidence Rates (SIRs) downloaded from the Australian Cancer Atlas site.
+This small example in Figure  \ref{fig:sir} shows the group of blue areas in the Hobart CBD more prominently in the hexagon tile map (b).
+The small red areas visible in the choropleth map (a) along the north coast are much larger in the hexagon tile maps.
+The hexagon tile map shows less yellow, this no longer overwhelms the map space with the information regarding the more rural areas.
+
+```{r sir, out.width = "100%", echo = FALSE, fig.cap = "The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2.
+A choropleth map (a) of Standardised Incidence Rates (SIRs) is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented."}
+knitr::include_graphics(path = "figures/7SIR.png")
+```
+
 ## Neighbour relationships
@@
 
-The hexagon tile map visualisation method can be applied to the Australian Cancer Atlas data.
-A small example of Lung Cancer Standardised Incidence Rates (SIRs) allows two views of the same data produced by the Australian Cancer Atlas.
-This small example in Figure  \ref{fig:sir} shows the group of blue areas in the Hobart CBD more prominently in the hexagon tile map (b).
-The small red areas visible in the choropleth map (a) along the north coast are much larger in the hexagon tile maps.
-The hexagon tile map shows less yellow, this no longer overwhelms the map space with the information regarding the more rural areas.
+```{r liver-geo}
+knitr::include_graphics("figures/aus_liver_m.png")
+```
 
-XXX Move this image (ref: sir) to the end of the algorithm section to illustrate the final result for Tassie
-
-```{r sir, out.width = "100%", echo = FALSE, fig.cap = "The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2.
-A choropleth map (a) of Standardised Incidence Rates (SIRs) is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented."}
-knitr::include_graphics(path = "figures/7SIR.png")
+```{r liver-hex}
+knitr::include_graphics("figures/aus_liver_m_hex.png")
 ```
@@
 
-The code for sugarbag can be found at XXX, along with details on installation and usage.
+The code for sugarbag [@sugarbag] can be found on [CRAN](https://cran.r-project.org/web/packages/sugarbag/index.html), along with vignettes on installation and usage.

### 2020-01-13 kobakian_sugarbag_jss/kobakian_sugarbag_jss.tex
Show title

@@
 }
-\title{}
+\title{An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With
+Application to Australian Maps}
 
 \Plainauthor{Stephanie Kobakian, Dianne Cook}
-\Plaintitle{An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With
+\Plaintitle{An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With
 Application to Australian Maps}
@@
 
+A complete hexagon tile map of Tasmania is created by applying the
+algorithm steps to each centroid. The hexagon tile map visualisation is
+used below to visualise the Australian Cancer Atlas data. Two views of
+the same data are produced by filling according to the Lung Cancer
+Standardised Incidence Rates (SIRs) downloaded from the Australian
+Cancer Atlas site. This small example in Figure \ref{fig:sir} shows the
+group of blue areas in the Hobart CBD more prominently in the hexagon
+tile map (b). The small red areas visible in the choropleth map (a)
+along the north coast are much larger in the hexagon tile maps. The
+hexagon tile map shows less yellow, this no longer overwhelms the map
+space with the information regarding the more rural areas.
+
+\begin{CodeChunk}
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{figures/7SIR}
+
+}
+
+\caption[The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2]{The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2.
+A choropleth map (a) of Standardised Incidence Rates (SIRs) is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented.}\label{fig:sir}
+\end{figure}
+\end{CodeChunk}
+
 \hypertarget{neighbour-relationships}{%
@@
 
-The hexagon tile map visualisation method can be applied to the
-Australian Cancer Atlas data. A small example of Lung Cancer
-Standardised Incidence Rates (SIRs) allows two views of the same data
-produced by the Australian Cancer Atlas. This small example in Figure
-\ref{fig:sir} shows the group of blue areas in the Hobart CBD more
-prominently in the hexagon tile map (b). The small red areas visible in
-the choropleth map (a) along the north coast are much larger in the
-hexagon tile maps. The hexagon tile map shows less yellow, this no
-longer overwhelms the map space with the information regarding the more
-rural areas.
+\begin{CodeChunk}
 
-XXX Move this image (ref: sir) to the end of the algorithm section to
-illustrate the final result for Tassie
+\begin{CodeInput}
+R> knitr::include_graphics("figures/aus_liver_m.png")
+\end{CodeInput}
+
+\begin{center}\includegraphics[width=41.67in]{figures/aus_liver_m} \end{center}
+
+\end{CodeChunk}
 
 \begin{CodeChunk}
-\begin{figure}
 
-{\centering \includegraphics[width=1\linewidth]{figures/7SIR}
+\begin{CodeInput}
+R> knitr::include_graphics("figures/aus_liver_m_hex.png")
+\end{CodeInput}
 
-}
+\begin{center}\includegraphics[width=41.67in]{figures/aus_liver_m_hex} \end{center}
 
-\caption[The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2]{The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2.
-A choropleth map (a) of Standardised Incidence Rates (SIRs) is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented.}\label{fig:sir}
-\end{figure}
 \end{CodeChunk}
@@
 
-The code for sugarbag can be found at XXX, along with details on
-installation and usage.
+The code for sugarbag \citep{sugarbag} can be found on
+\href{https://cran.r-project.org/web/packages/sugarbag/index.html}{CRAN},
+along with vignettes on installation and usage.
 

### 2020-01-13 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
Explain Aus example

@@
 
-XXX Show whole Australia male liver cancer with choropleth and hexagon tile map, and discuss the pros/cons of the result, for understanding the incidence.
+Estimates derived from the models of Standardised Incidence Rates and excess deaths can be downloaded from Australian Cancer Atlas [@atlas]. 
+The estimates are communicated as a selection of points on the posterior probability curve for each Statistical Area at Level 2 (SA2).
+Figure \ref{fig:liver-geo} is a choropleth map that uses colour to display the median (0.5) of the posterior probabilities of the estimated Standardised Incidence Rate for each SA2.
+
+The Australian choropleth map display draws attention to the expanse of light blue areas  across the rural communities in all states.
+The SA2s in the north of the country stand out as more orange and red.
+Comparatively, hexagon tile map display in Figure \ref{fig:liver-geo} draws attention to the capital cities of Sydney and Melbourne.
+In both of these capital cities, the hexagons that represent the SA2 areas in the outer regions of Melbourne have average or lower than average Incidence Rates, but the inner-city areas have groups of orange SA2 areas that have above average rates.
+
+With careful consideratin of the choropleth map these very small areas may have been noticed by viewers, but the hexagon tile map display emphasises them.
+The communities in northern Queensland and the Northern territory do not draw attention because of their size, but their colour is still noticably above average when contrasted with the heaxgons further south.
 
@@
 ## Election results
+
+The concept of tile mapping with both hexagons and squares is not unfamiliar in practice.
+In fact there are many prominent news sites that utilise these techniques, these include [@NPR], [@FiveThirtyEight], [@WSJ], [@WP].
+A common applicate of the hexagon tile map is election mapping for United States of America.
 

### 2020-01-13 kobakian_sugarbag_jss/kobakian_sugarbag_jss.tex
Explain Aus example

@@
 
-XXX Show whole Australia male liver cancer with choropleth and hexagon
-tile map, and discuss the pros/cons of the result, for understanding the
-incidence.
+Estimates derived from the models of Standardised Incidence Rates and
+excess deaths can be downloaded from Australian Cancer Atlas
+\citep{atlas}. The estimates are communicated as a selection of points
+on the posterior probability curve for each Statistical Area at Level 2
+(SA2). Figure \ref{fig:liver-geo} is a choropleth map that uses colour
+to display the median (0.5) of the posterior probabilities of the
+estimated Standardised Incidence Rate for each SA2.
+
+The Australian choropleth map display draws attention to the expanse of
+light blue areas across the rural communities in all states. The SA2s in
+the north of the country stand out as more orange and red.
+Comparatively, hexagon tile map display in Figure \ref{fig:liver-geo}
+draws attention to the capital cities of Sydney and Melbourne. In both
+of these capital cities, the hexagons that represent the SA2 areas in
+the outer regions of Melbourne have average or lower than average
+Incidence Rates, but the inner-city areas have groups of orange SA2
+areas that have above average rates.
+
+With careful consideratin of the choropleth map these very small areas
+may have been noticed by viewers, but the hexagon tile map display
+emphasises them. The communities in northern Queensland and the Northern
+territory do not draw attention because of their size, but their colour
+is still noticably above average when contrasted with the heaxgons
+further south.
 
@@
 \subsection{Election results}\label{election-results}}
+
+The concept of tile mapping with both hexagons and squares is not
+unfamiliar in practice. In fact there are many prominent news sites that
+utilise these techniques, these include \citep{NPR},
+\citep{FiveThirtyEight}, \citep{WSJ}, \citep{WP}. A common applicate of
+the hexagon tile map is election mapping for United States of America.
 

### 2020-01-14 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
election example, not happy with it

@@
 
-```{r liver-geo}
+```{r liver-geo, fig.cap = "A choropleth map of the Statistical Areas of Australia at Level 2.
+The colours communicate the value of the estimated Standardised Incidence Rate, they range from much lower than average (blue) to much higher than average (red)", results = "asis", echo = FALSE, out.width = "60%"                             }
 knitr::include_graphics("figures/aus_liver_m.png")
@@
 
-```{r liver-hex}
+```{r liver-hex, fig.cap = "A hexagon tile map of the Statistical Areas of Australia at Level 2.
+The colours communicate the value of the estimated Standardised Incidence Rate, they range from much lower than average (blue) to much higher than average (red)", results = "asis", echo = FALSE, out.width = "60%"}
 knitr::include_graphics("figures/aus_liver_m_hex.png")
@@
 The concept of tile mapping with both hexagons and squares is not unfamiliar in practice.
-In fact there are many prominent news sites that utilise these techniques, these include [@NPR], [@FiveThirtyEight], [@WSJ], [@WP].
-A common applicate of the hexagon tile map is election mapping for United States of America.
+A common application of the hexagon tile map is election mapping for United States of America, there are many prominent news sites that utilise these techniques [@NPR], [@FiveThirtyEight], [@WSJ], [@WP].
+To apply hexagon tile mapping to election mapping Australia using \code{R}, the \pkg{sugarbag} package provides Australian election data and the Australian Electoral Commission provides electoral boundaries for 2019 [@AEC19].
 
-XXX Code from web site, and a couple of paragraphs of explanation
+```{r aec-packages}
+library(sugarbag)
+library(eechidna)
+
+# First Preference votes in 2019
+data(sugarbag::fp19)
+# Electoral Boundaries
+nat_data19 <- nat_data_download(2019)
+```
+
+The centroids are derived from the National Electoral data for 2019 provided in the \{eechidna} package.
+
+```{r aec-centroids}
+centroids <- nat_data19 %>%
+  select(Elect_div = elect_div, longitude = long_c, latitude = lat_c)
+```
+
+The hexagon grid for allocation is created using the set of electorate centroids.
+
+```{r aec-grid}
+# Create a grid of hexagons to allocate centroids
+grid <- create_grid(centroids = centroids, hex_size = 0.9, buffer_dist = 10)
+```
+
+The centroids and the grid can be passed to the \code{allocate} function.
+
+```{r allocate}
+# Allocate the centroids to the hexagon grid
+# We have the same amount of rows, as individual regions
+hex_allocated <- allocate(centroids = centroids,
+  sf_id = "Elect_div",
+  hex_grid = grid,
+  hex_size = 0.9, # same size used in create_grid
+  hex_filter = 10,
+  use_neighbours = ELB,
+  focal_points = capital_cities,
+  width = 30, verbose = TRUE) # same column used in create_centroids
+```
+
+To display hexagons on a map, \code{fortify_hexagon} takes the center of the hexagon and finds the 6 points needed to create a hexagon shape.
+
+For animations to move between geography and hexagons the \code{sf_id} must match, there also needs to be an identifier to separate the states to animate between for \code{gganimate}.
+
+```{r data}
+# When plotting, the polygons are needed, rather than single centroid points.
+# We can find 6 points, and then convert them into an sf geometry object
+hex <- hex_allocated %>%
+  fortify_hexagon(hex_size = 0.9, sf_id = "Elect_div") %>%
+  select(Elect_div, long, lat) %>% 
+  sf::st_as_sf(coords = c("long", "lat"), crs = 4283) %>%
+  group_by(Elect_div) %>% 
+  summarise(do_union = FALSE) %>%
+  st_cast("POLYGON") %>%
+  st_cast("MULTIPOLYGON") %>% 
+  left_join(st_drop_geometry(nat_data19), ., by = "Elect_div")
+
+anim_aus <- bind_rows("Hex." = hex, "Choro." = ELB19, .id = "polygon_type") %>% st_as_sf()
+
+# Join election data from 2016
+fp_maps <- fp19 %>% 
+  filter(Elected == "Y") %>% 
+  select(Elect_div = DivisionNm, PartyAb, PartyNm, TotalVotes) %>% 
+  left_join(anim_aus, by = "Elect_div")
+
+```
+
+Here we show the two sets of areas they can be plotted separately using `geom_facet`.
+
+```{r plot_facet, dpi = 300}
+auscolours <- c(
+  "ALP" = "#DE3533",
+  "LNP" = "#080CAB",
+  "KAP" = "#b50204",
+  "GRN" = "#10C25B",
+  "XEN" = "#ff6300",
+  "LNP" = "#0047AB",
+  "LP" = "#0047AB",
+  "NP" = "#006644",
+  "IND" = "#307560")
+
+ggplot(fp_maps %>% filter(polygon_type == "Hex."), 
+  aes(geometry = geometry, fill = PartyAb)) +
+  scale_fill_manual(values = auscolours) +
+  geom_sf(fill = "white", data = absmapsdata::state2016) +
+  geom_sf() +
+  theme_void()
+
+ggplot(fp_maps %>% filter(polygon_type == "Choro."), 
+  aes(geometry = geometry, fill = PartyAb)) +
+  scale_fill_manual(values = auscolours) +
+  geom_sf(fill = "white", data = absmapsdata::state2016) +
+  geom_sf() +
+  theme_void()
+```
+
+We can move between the two plots using the \code{transition_states} function from the \code{gganimate} package.
 
@@
 XXX show how to make an animation, and make a link to a web page where the animation can be viewed
+
+```{r}
+anim <- anim_aus %>% 
+  ggplot(aes(x=long, y=lat, group = interaction(elect_div))) +
+  geom_polygon(aes(x=long, y=lat, group = group),fill = "grey", alpha = 0.3, data= nat_map16) +
+  geom_polygon(aes(fill = PartyAb)) + 
+  coord_equal() + 
+  theme_void() +
+  scale_fill_manual(values = auscolours) +
+  guides(fill = guide_legend(title = NULL)) + 
+  theme(legend.position = "bottom") +
+  transition_states(poly_type)
+animate(anim, duration = 6, nframes = 60)
+```
 
@@
 The solution to this visualisation problem has equally sized areas, with neighbourhood boundary connections.
-This map algorithm is implemented in the @sugarbag package written for @R.
+This map algorithm is implemented in the \pkg{sugarbag} @sugarbag package written for \code{R} @R.
 The \pkg{sugarbag} package creates tesselated hexagon tilegrams.
@@
 
-The code for sugarbag [@sugarbag] can be found on [CRAN](https://cran.r-project.org/web/packages/sugarbag/index.html), along with vignettes on installation and usage.
+The code for \pkg{sugarbag} [@sugarbag] can be found on [CRAN](https://cran.r-project.org/web/packages/sugarbag/index.html), along with vignettes on installation and usage.
+
+Australian Electoral Data can be found in the \pkg{eechidna} package for R.

### 2020-01-14 kobakian_sugarbag_jss/kobakian_sugarbag_jss.tex
election example, not happy with it

@@
 
-\begin{CodeChunk}
+\begin{figure}
 
-\begin{CodeInput}
-R> knitr::include_graphics("figures/aus_liver_m.png")
-\end{CodeInput}
+{\centering \includegraphics[width=0.6\linewidth]{figures/aus_liver_m}
 
-\begin{center}\includegraphics[width=41.67in]{figures/aus_liver_m} \end{center}
+}
 
-\end{CodeChunk}
+\caption[A choropleth map of the Statistical Areas of Australia at Level 2]{A choropleth map of the Statistical Areas of Australia at Level 2.
+The colours communicate the value of the estimated Standardised Incidence Rate, they range from much lower than average (blue) to much higher than average (red)}\label{fig:liver-geo}
+\end{figure}
 
-\begin{CodeChunk}
+\begin{figure}
 
-\begin{CodeInput}
-R> knitr::include_graphics("figures/aus_liver_m_hex.png")
-\end{CodeInput}
+{\centering \includegraphics[width=0.6\linewidth]{figures/aus_liver_m_hex}
 
-\begin{center}\includegraphics[width=41.67in]{figures/aus_liver_m_hex} \end{center}
+}
 
-\end{CodeChunk}
+\caption[A hexagon tile map of the Statistical Areas of Australia at Level 2]{A hexagon tile map of the Statistical Areas of Australia at Level 2.
+The colours communicate the value of the estimated Standardised Incidence Rate, they range from much lower than average (blue) to much higher than average (red)}\label{fig:liver-hex}
+\end{figure}
 
@@
 neighbourhood boundary connections. This map algorithm is implemented in
-the \citet{sugarbag} package written for \citet{R}. The \pkg{sugarbag}
-package creates tesselated hexagon tilegrams. The Australian application
-preserves the spatial relationships, emphasising capital cities. The
-hexagon tile map is a visualisation solution that highlights spatial
-distributions.
+the \pkg{sugarbag} \citet{sugarbag} package written for \code{R}
+\citet{R}. The \pkg{sugarbag} package creates tesselated hexagon
+tilegrams. The Australian application preserves the spatial
+relationships, emphasising capital cities. The hexagon tile map is a
+visualisation solution that highlights spatial distributions.
 
@@
 
-The code for sugarbag \citep{sugarbag} can be found on
+The code for \pkg{sugarbag} \citep{sugarbag} can be found on
 \href{https://cran.r-project.org/web/packages/sugarbag/index.html}{CRAN},

### 2020-01-14 Index.Rmd
Melanoma map

---
title: "Australian Cancer Atlas"
author: "Stephanie Kobakian"
date: "14/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# The Australian Cancer Atlas

```{r fig.cap = "A choropleth map of the distribution of Standardised Incidence Rates of melanoma cancer for Australians."}
knitr::include_graphics("kobakian_sugarbag_jss/figures/aus_melanoma_p.png")
```

```{r fig.cap = "A hexagon tile map distribution of Standardised Incidence Rates of melanoma cancer for Australians."}
knitr::include_graphics("kobakian_sugarbag_jss/figures/aus_melanoma_p_hex.png")
```

This is an animation that changes from a choropleth map to a hexagon tile map of Australian Statistical Areas at Level 2 using Standardised Incidence Ratios taken from the Australian Cancer Atlas website.

```{r}
knitr::include_graphics("melanoma_animation.gif")
```

### 2020-01-14 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
Melanoma map

--- 2020-01-13 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
@@
 
-XXX Show whole Australia male liver cancer with choropleth and hexagon tile map, and discuss the pros/cons of the result, for understanding the incidence.
+The Australian Cancer Atlas [@atlas] allows estimates derived from the models of Standardised Incidence Rates and excess deaths to be downloaded. 
+Figure \ref{fig:melanoma-geo} is a choropleth map that uses colour to display the estimated Standardised Incidence Rate of melanoma cancer for all persons for each SA2.
+The Australian choropleth map display draws attention to the expanse of light blue areas across the rural communities in all states.
+The SA2s around Brisbane stand out as more orange and red.
+Comparatively, the hexagon tile map display in Figure \ref{fig:melanoma-hex} draws attention to contrast of the blue areas in Sydney and Melbourne and the capital city of Brisbane.
+In both Sydney and Melbourne, the hexagons that represent the SA2 areas in the inner-city areas have lower than average Incidence Rates.
 
-```{r liver-geo}
-knitr::include_graphics("figures/aus_liver_m.png")
+With careful consideration of the choropleth map, the small geographic inner city areas may have been noticed by viewers, but the hexagon tile map display emphasises them.
+The communities in northern Queensland and the Northern territory do not draw attention because of their size as in the choropleth, but their colour is still noticably below average when contrasted with the heaxgons further south.
+
+To create this choropleth map the SA2 polygons for 2011 from the Australian Bureau of Statistics. The Standardised Incidence Ratios for each geographic unit are joined to the appropriate polygons.
+
+```{r melanoma-geo, fig.cap = "A choropleth map of the Statistical Areas of Australia at Level 2.
+The colours communicate the value of the estimated Standardised Incidence Rate of Melanoma for all persons, they range from much lower than average (blue) to much higher than average (red)", results = "asis", echo = FALSE, out.width = "60%"                             }
+knitr::include_graphics("figures/aus_melanoma_p.png")
 ```
 
-```{r liver-hex}
-knitr::include_graphics("figures/aus_liver_m_hex.png")
+To create the hexagon tile map display, the same steps are followed as outlined above:
+
+ - Create the set of centroid points
+ - Create the hexagon grid points
+ - Allocate each centroid to a hexagon grid point
+
+```{r melanoma-hex, fig.cap = "A hexagon tile map of the Statistical Areas of Australia at Level 2.
+The colours communicate the value of the estimated Standardised Incidence Rate, they range from much lower than average (blue) to much higher than average (red)", results = "asis", echo = FALSE, out.width = "60%"}
+knitr::include_graphics("figures/aus_melanoma_p_hex.png")
 ```
-
-## Election results
-
-XXX Code from web site, and a couple of paragraphs of explanation
 
@@
 
-XXX show how to make an animation, and make a link to a web page where the animation can be viewed
+The \pkg{gganimate} package can be used to make an animation.
+It requires connecting the two displays, which can be done using the \code{sf_id} such as the SA2 name.
+The animation^[This animation can be viewed at: ] connecting these two displays will highlight the rapid growth of the inner-city areas, and will decrease the large rural areas.
 
@@
 The hexagon tile map is a visualisation solution that highlights spatial distributions.
+
+These hexagons equally represent each area. However, the tesselation does not allow the size of the hexagons to represent another variable.
 

### 2020-01-14 Index.Rmd
rearrange site

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE, out.width = "100%")
 ```
@@
 # The Australian Cancer Atlas
+
+```{r fig.cap = "This is an animation that changes from a choropleth map to a hexagon tile map of Australian Statistical Areas at Level 2 using Standardised Incidence Ratios taken from the Australian Cancer Atlas website."}
+knitr::include_graphics("melanoma_animation.gif")
+```
 
@@
 ```
-
-This is an animation that changes from a choropleth map to a hexagon tile map of Australian Statistical Areas at Level 2 using Standardised Incidence Ratios taken from the Australian Cancer Atlas website.
-
-```{r}
-knitr::include_graphics("melanoma_animation.gif")
-```

### 2020-01-14 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
future work

@@
 
-The Australian Cancer Atlas [@atlas] allows estimates derived from the models of Standardised Incidence Rates and excess deaths to be downloaded. 
+The Australian Cancer Atlas [@TACA] allows estimates derived from the models of Standardised Incidence Rates and excess deaths to be downloaded. 
 Figure \ref{fig:melanoma-geo} is a choropleth map that uses colour to display the estimated Standardised Incidence Rate of melanoma cancer for all persons for each SA2.
@@
 ```{r melanoma-geo, fig.cap = "A choropleth map of the Statistical Areas of Australia at Level 2.
-The colours communicate the value of the estimated Standardised Incidence Rate of Melanoma for all persons, they range from much lower than average (blue) to much higher than average (red)", results = "asis", echo = FALSE, out.width = "60%"                             }
+The colours communicate the value of the estimated Standardised Incidence Rate of Melanoma for all persons, they range from much lower than average (blue) to much higher than average (red)", results = "asis", echo = FALSE, out.width = "60%"}
 knitr::include_graphics("figures/aus_melanoma_p.png")
@@
 The \pkg{gganimate} package can be used to make an animation.
-It requires connecting the two displays, which can be done using the \code{sf_id} such as the SA2 name.
-The animation^[This animation can be viewed at: ] connecting these two displays will highlight the rapid growth of the inner-city areas, and will decrease the large rural areas.
+It requires connecting the polygons for each area in two displays two displays, which can be done using the \code{sf_id} variable, such as the SA2 name.
+The animation^[This animation can be viewed at: https://sugarbagjss.netlify.com/] connecting these two displays will highlight the rapid growth of the inner-city areas, and will decrease the large rural areas.
+The hexagons that move the furthest will move rapidly in the animation.
 
 # Conclusion
-
-Structure of conclusions: (1) summarise paper, discuss limitations, suggest future directions
 
@@
 
-These hexagons equally represent each area. However, the tesselation does not allow the size of the hexagons to represent another variable.
+These hexagons equally represent each area. However, the tesselation does not allow the size of the hexagons to represent another variable, similar to the choropleth maps.
+The algorithm is heavily dependent on the focal points used, as this determines the order of allocation.
+It works on the assumption that viewers can use directional assumptions to identify their neighbourhoods, this can be aided by the animation.
+
+<!-- future -->
+Future work will include refining the algorithm.
+It would be possible to take a logarithmic function rather than a direct angle to help choose a closer hexagon to the original centroid location, before increasing the width of the angle used to filter the hexagons.
+
+This algorithm has only been tested using single countries, and does not consider definite borders of countries.
+While the buffer allows extention beyond the furthest centroids, there is no mechanism to protect the borders and ensure centroids are placed within the geographic borders of a country.
+
+This algorithm is an effective start to creating hexagon tile maps for many geographic units.
 

### 2020-01-14 kobakian_sugarbag_jss/kobakian_sugarbag_jss.tex
future work

--- 2020-01-13 kobakian_sugarbag_jss/kobakian_sugarbag_jss.tex
@@
 
-XXX Show whole Australia male liver cancer with choropleth and hexagon
-tile map, and discuss the pros/cons of the result, for understanding the
-incidence.
+The Australian Cancer Atlas \citep{TACA} allows estimates derived from
+the models of Standardised Incidence Rates and excess deaths to be
+downloaded. Figure \ref{fig:melanoma-geo} is a choropleth map that uses
+colour to display the estimated Standardised Incidence Rate of melanoma
+cancer for all persons for each SA2. The Australian choropleth map
+display draws attention to the expanse of light blue areas across the
+rural communities in all states. The SA2s around Brisbane stand out as
+more orange and red. Comparatively, the hexagon tile map display in
+Figure \ref{fig:melanoma-hex} draws attention to contrast of the blue
+areas in Sydney and Melbourne and the capital city of Brisbane. In both
+Sydney and Melbourne, the hexagons that represent the SA2 areas in the
+inner-city areas have lower than average Incidence Rates.
 
-\begin{CodeChunk}
+With careful consideration of the choropleth map, the small geographic
+inner city areas may have been noticed by viewers, but the hexagon tile
+map display emphasises them. The communities in northern Queensland and
+the Northern territory do not draw attention because of their size as in
+the choropleth, but their colour is still noticably below average when
+contrasted with the heaxgons further south.
 
-\begin{CodeInput}
-R> knitr::include_graphics("figures/aus_liver_m.png")
-\end{CodeInput}
+To create this choropleth map the SA2 polygons for 2011 from the
+Australian Bureau of Statistics. The Standardised Incidence Ratios for
+each geographic unit are joined to the appropriate polygons.
 
-\begin{center}\includegraphics[width=41.67in]{figures/aus_liver_m} \end{center}
+\begin{figure}
 
-\end{CodeChunk}
+{\centering \includegraphics[width=0.6\linewidth]{figures/aus_melanoma_p}
 
-\begin{CodeChunk}
+}
 
-\begin{CodeInput}
-R> knitr::include_graphics("figures/aus_liver_m_hex.png")
-\end{CodeInput}
+\caption[A choropleth map of the Statistical Areas of Australia at Level 2]{A choropleth map of the Statistical Areas of Australia at Level 2.
+The colours communicate the value of the estimated Standardised Incidence Rate of Melanoma for all persons, they range from much lower than average (blue) to much higher than average (red)}\label{fig:melanoma-geo}
+\end{figure}
 
-\begin{center}\includegraphics[width=41.67in]{figures/aus_liver_m_hex} \end{center}
+To create the hexagon tile map display, the same steps are followed as
+outlined above:
 
-\end{CodeChunk}
+\begin{itemize}
+\tightlist
+\item
+  Create the set of centroid points
+\item
+  Create the hexagon grid points
+\item
+  Allocate each centroid to a hexagon grid point
+\end{itemize}
 
-\hypertarget{election-results}{%
-\subsection{Election results}\label{election-results}}
+\begin{figure}
 
-XXX Code from web site, and a couple of paragraphs of explanation
+{\centering \includegraphics[width=0.6\linewidth]{figures/aus_melanoma_p_hex}
+
+}
+
+\caption[A hexagon tile map of the Statistical Areas of Australia at Level 2]{A hexagon tile map of the Statistical Areas of Australia at Level 2.
+The colours communicate the value of the estimated Standardised Incidence Rate, they range from much lower than average (blue) to much higher than average (red)}\label{fig:melanoma-hex}
+\end{figure}
 
@@
 
-XXX show how to make an animation, and make a link to a web page where
-the animation can be viewed
+The \pkg{gganimate} package can be used to make an animation. It
+requires connecting the polygons for each area in two displays two
+displays, which can be done using the \code{sf_id} variable, such as the
+SA2 name. The animation\footnote{This animation can be viewed at:
+  \url{https://sugarbagjss.netlify.com/}} connecting these two displays
+will highlight the rapid growth of the inner-city areas, and will
+decrease the large rural areas. The hexagons that move the furthest will
+move rapidly in the animation.
 
@@
 \section{Conclusion}\label{conclusion}}
-
-Structure of conclusions: (1) summarise paper, discuss limitations,
-suggest future directions
 
@@
 neighbourhood boundary connections. This map algorithm is implemented in
-the \citet{sugarbag} package written for \citet{R}. The \pkg{sugarbag}
-package creates tesselated hexagon tilegrams. The Australian application
-preserves the spatial relationships, emphasising capital cities. The
-hexagon tile map is a visualisation solution that highlights spatial
-distributions.
+the \pkg{sugarbag} \citet{sugarbag} package written for \code{R}
+\citet{R}. The \pkg{sugarbag} package creates tesselated hexagon
+tilegrams. The Australian application preserves the spatial
+relationships, emphasising capital cities. The hexagon tile map is a
+visualisation solution that highlights spatial distributions.
+
+These hexagons equally represent each area. However, the tesselation
+does not allow the size of the hexagons to represent another variable,
+similar to the choropleth maps. The algorithm is heavily dependent on
+the focal points used, as this determines the order of allocation. It
+works on the assumption that viewers can use directional assumptions to
+identify their neighbourhoods, this can be aided by the animation.
+
+Future work will include refining the algorithm. It would be possible to
+take a logarithmic function rather than a direct angle to help choose a
+closer hexagon to the original centroid location, before increasing the
+width of the angle used to filter the hexagons.
+
+This algorithm has only been tested using single countries, and does not
+consider definite borders of countries. While the buffer allows
+extention beyond the furthest centroids, there is no mechanism to
+protect the borders and ensure centroids are placed within the
+geographic borders of a country.
+
+This algorithm is an effective start to creating hexagon tile maps for
+many geographic units.
 
@@
 
-The code for sugarbag \citep{sugarbag} can be found on
+The code for \pkg{sugarbag} \citep{sugarbag} can be found on
 \href{https://cran.r-project.org/web/packages/sugarbag/index.html}{CRAN},
 along with vignettes on installation and usage.
+
+Australian Electoral Data can be found in the \pkg{eechidna} package for
+R.
 

### 2020-01-15 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
Earls suggestions included

@@
     email: \email{dicook@monash.edu}
+  - name: Earl Duncan
+    affiliation: Queensland University of Technology
+    address: >
+      School of Mathematical Sciences,
+      Science and Engineering Faculty,
+      Brisbane, QLD, Australia
+    email: \email{earl.duncan@qut.edu.au}
 title: 
@@
 Australian residents are increasingly congregating around major cities, the vast rural areas are often sparsely populated in comparison to the urban centres. 
-In Australia, government bodies such as the Australian Bureau of Statistics, and the Australian Electoral Commission hold the responsibility for the division of geographic units.
-These boundaries are adjusted as the population increases.
+In Australia, government bodies such as the Australian Bureau of Statistics (ABS), and the Australian Electoral Commission (AEC) hold the responsibility for the division of geographic units.
+If it absolutely necessary, the AEC may adjust as the population increases.
 The division of the population into approximately equal population areas results in dramatically different square meterage of the geographic areas.
@@
 Tilegrams, Rectangular cartograms \citep{ORC} and Dorling cartograms \citep{ACTUC}, all use one simple shape to represent each area.
-This allows preservation of spatial relationships and decreases the emphasis from the amount of geographic area.
+This allows preservation of spatial relationships and decreases the emphasis from the size of the geographic areas.
 These maps focus on the relationship between neighbours attempting to preserve connections, and disregard the unique shapes of the administrative boundaries.
@@
 
-This solution operates on a set of \pkg{sf} \citep{sf} polygons.
+This solution operates on a set of simple feature geometry objects, also known as \pkg{sf} \citep{sf} polygons.
 
@@
 The amount of rows in each latitude group and the amount of columns in each longitude group are used as the width of rolling windows.
-The rolling windows can be seen on the This will tailor the available grid points to those most likely to be used.
+The rolling windows can be seen on the bottom and right of Fig.
+\ref{fig:filter_grid}.
+This will tailor the available grid points to those most likely to be used.
 It also helps reduce the amount of time taken, as it decreases the amount of points considered for each centroid allocation.
@@
 If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded, only when a maximum distance is reached will the angle expand to accommodate more possible grid points.
-The angle begins at 30 degrees by default, and will increase if no points can be found within the \code{hex_filter} distance.
+By default the angle filter to hexagon grid points that fall within the bounds of the angle from the focal point to the geographic centroid, plus and minus 30 degrees.
+This will increase if no points can be found within the \code{hex_filter} distance.
+The angle of 30 was chosen to allow the algorithm to choose hexagons that best maintained the spatial relationship between the focal point and geographic centroid.
 The allocation is returned and combined with the data relating to each polygon.
@@
 
-It is possible to encourage the use of neighbourhood relationshipd, for stronger preservation of neighbour relations.
+It is possible to incorporate the neighbouring areas for each SA2, for stronger preservation of the spatial distribution.
 
-An additional step may be included to allow the neighbours that have alredy been allocated to influence the placement of the current centroid. 
+An additional step can be included to allow the neighbours that have alredy been allocated to influence the placement of the current centroid. 
 This requires respecifying the \code{sf} object as the argument for the \code{use_neighbours} parameter.
@@
 
-To create this choropleth map the SA2 polygons for 2011 from the Australian Bureau of Statistics. The Standardised Incidence Ratios for each geographic unit are joined to the appropriate polygons.
+To create this choropleth map the SA2 polygons for 2011 from the ABS. The Standardised Incidence Ratios for each geographic unit are joined to the appropriate polygons.
 
@@
 The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations.
-They would also like to thank Professor Kerrie Mengersen and Dr Earl Duncan for suggestions and comments.
+They would also like to thank Professor Kerrie Mengersen for suggestions and comments.
 Mitch O'Hara-Wild provided assistance with some parts of the algorithm and code.

### 2020-01-15 kobakian_sugarbag_jss/kobakian_sugarbag_jss.tex
Earls suggestions included

@@
 \author{
-Stephanie Kobakian\\Queensland University of Technology \And Dianne Cook\\Monash University
+Stephanie Kobakian\\Queensland University of Technology \And Dianne Cook\\Monash University \And Earl Duncan\\Queensland University of Technology
 }
@@
 
-\Plainauthor{Stephanie Kobakian, Dianne Cook}
+\Plainauthor{Stephanie Kobakian, Dianne Cook, Earl Duncan}
 \Plaintitle{An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With
@@
 
+      Earl Duncan\\
+  Queensland University of Technology\\
+  School of Mathematical Sciences, Science and Engineering Faculty,
+  Brisbane, QLD, Australia\\
+  E-mail: \email{earl.duncan@qut.edu.au}\\
+
   }
@@
 urban centres. In Australia, government bodies such as the Australian
-Bureau of Statistics, and the Australian Electoral Commission hold the
-responsibility for the division of geographic units. These boundaries
-are adjusted as the population increases. The division of the population
-into approximately equal population areas results in dramatically
-different square meterage of the geographic areas. This results in an
-unequal attention given to the statistic of each area, this can allow
-misrepresentation of the spatial distributions of human related
-statistics in geographic maps.
+Bureau of Statistics (ABS), and the Australian Electoral Commission
+(AEC) hold the responsibility for the division of geographic units. If
+it absolutely necessary, the AEC may adjust as the population increases.
+The division of the population into approximately equal population areas
+results in dramatically different square meterage of the geographic
+areas. This results in an unequal attention given to the statistic of
+each area, this can allow misrepresentation of the spatial distributions
+of human related statistics in geographic maps.
 
@@
 allows preservation of spatial relationships and decreases the emphasis
-from the amount of geographic area. These maps focus on the relationship
-between neighbours attempting to preserve connections, and disregard the
-unique shapes of the administrative boundaries.
+from the size of the geographic areas. These maps focus on the
+relationship between neighbours attempting to preserve connections, and
+disregard the unique shapes of the administrative boundaries.
 
@@
 
-This solution operates on a set of \pkg{sf} \citep{sf} polygons.
+This solution operates on a set of simple feature geometry objects, also
+known as \pkg{sf} \citep{sf} polygons.
 
@@
 columns in each longitude group are used as the width of rolling
-windows. The rolling windows can be seen on the This will tailor the
-available grid points to those most likely to be used. It also helps
-reduce the amount of time taken, as it decreases the amount of points
-considered for each centroid allocation.
+windows. The rolling windows can be seen on the bottom and right of Fig.
+\ref{fig:filter_grid}. This will tailor the available grid points to
+those most likely to be used. It also helps reduce the amount of time
+taken, as it decreases the amount of points considered for each centroid
+allocation.
 
@@
 grid points.\\
-The angle begins at 30 degrees by default, and will increase if no
-points can be found within the \code{hex_filter} distance. The
+By default the angle filter to hexagon grid points that fall within the
+bounds of the angle from the focal point to the geographic centroid,
+plus and minus 30 degrees. This will increase if no points can be found
+within the \code{hex_filter} distance. The angle of 30 was chosen to
+allow the algorithm to choose hexagons that best maintained the spatial
+relationship between the focal point and geographic centroid. The
 allocation is returned and combined with the data relating to each
@@
 
-It is possible to encourage the use of neighbourhood relationshipd, for
-stronger preservation of neighbour relations.
+It is possible to incorporate the neighbouring areas for each SA2, for
+stronger preservation of the spatial distribution.
 
-An additional step may be included to allow the neighbours that have
+An additional step can be included to allow the neighbours that have
 alredy been allocated to influence the placement of the current
@@
 
-To create this choropleth map the SA2 polygons for 2011 from the
-Australian Bureau of Statistics. The Standardised Incidence Ratios for
-each geographic unit are joined to the appropriate polygons.
+To create this choropleth map the SA2 polygons for 2011 from the ABS.
+The Standardised Incidence Ratios for each geographic unit are joined to
+the appropriate polygons.
 
@@
 discussions regarding alternative spatial visualizations. They would
-also like to thank Professor Kerrie Mengersen and Dr Earl Duncan for
-suggestions and comments. Mitch O'Hara-Wild provided assistance with
-some parts of the algorithm and code. Sayani Gupta provided helpful
-advice on parts of this paper.
+also like to thank Professor Kerrie Mengersen for suggestions and
+comments. Mitch O'Hara-Wild provided assistance with some parts of the
+algorithm and code. Sayani Gupta provided helpful advice on parts of
+this paper.
 

### 2020-01-16 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
parameter tables not used

@@
 library(sf)
+library(sugarbag)
 
@@
 
-The following must be provided to \code{create_hexmap}:
-```{r table_necessary, echo = FALSE, fig.cap = "This table details the parameters that must be provided to create a hexagon tile map using sugarbag."}
-library(sugarbag)
-library(tidyverse)
+The following parameters must be provided to \code{create_hexmap}:
 
-knitr::kable(tibble::tibble(parameter = c('shp', 
-  'sf_id',
-  'focal_points'),
-  description = c(
-    'an sf object containing the polygon information', 
-    'name of a column that distinguishes unique areas',
-    'a data frame of reference locations used to allocate hexagons'
-    )), format = "latex")
-```
+ - *shp:* an sf object containing the polygon information
+ - *sf_id:* name of a column that distinguishes unique areas
+ - *focal_points:* a data frame of reference locations used to allocate hexagons
 
@@
 
-```{r parameters, echo = FALSE, fig.cap = "This table details the additional parameters that are used to create a hexagon tile map using sugarbag."}
-knitr::kable(tibble(parameter = c('buffer_dist', 'hex_size',  'hex_filter', 'width'),
-  description = c('a float value for distance in degrees to extend beyond the geometry provided',
-    'a float value in degrees for the diameter of the hexagons', 'amount of hexagons around centroid to consider for allocation',
-    'the angle used to filter the grid points around a centroid')), format = "latex")
-```
+ - *buffer_dist:* a float value for distance in degrees to extend beyond the geometry provided
+ - *hex_size:* a float value in degrees for the diameter of the hexagons
+ - *hex_filter:* amount of hexagons around centroid to consider for allocation
+ - *width:* the angle used to filter the grid points around a centroid
 
@@
 
-```{r centroids_plot, out.width = "100%", echo = FALSE, eval = FALSE, fig.cap="The geographic shapes of the Statistical Areas of Tasmania at Level 2.
+```{r centroids_plot, out.width = "100%", echo = FALSE, eval = FALSE, fig.cap = "The geographic shapes of the Statistical Areas of Tasmania at Level 2.
 The points show the locations of the centroids of the SA2 areas."}
@@
 
-```{r grid2, fig.cap="Grid points to create a tilegram.", out.width = "100%", echo = FALSE}
+```{r grid2, fig.cap = "Grid points to create a tilegram.", out.width = "100%", echo = FALSE}
 knitr::include_graphics(path = "figures/2grid.png")
@@
 
-```{r buffers, echo = FALSE, out.width = "100%"}
+```{r buffers, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, out.width = "100%"}
 knitr::include_graphics(path = "figures/4grid.png")
@@
 
-```{r buffs, out.width = "100%", echo = FALSE}
+```{r buffs, fig.cap = "A complete hexagon tile map of Tasmania.", out.width = "100%", echo = FALSE}
 knitr::include_graphics(path = "figures/6allocate.png")
@@
 
-```{r eval=FALSE}
+```{r}
 library(sugarbag)

### 2020-01-16 kobakian_sugarbag_jss/kobakian_sugarbag_jss.tex
parameter tables not used

@@
 
-The following must be provided to \code{create_hexmap}:
+The following parameters must be provided to \code{create_hexmap}:
 
-\begin{CodeChunk}
-
-\begin{tabular}{l|l}
-\hline
-parameter & description\\
-\hline
-shp & an sf object containing the polygon information\\
-\hline
-sf\_id & name of a column that distinguishes unique areas\\
-\hline
-focal\_points & a data frame of reference locations used to allocate hexagons\\
-\hline
-\end{tabular}
-
-\end{CodeChunk}
+\begin{itemize}
+\tightlist
+\item
+  \emph{shp:} an sf object containing the polygon information
+\item
+  \emph{sf\_id:} name of a column that distinguishes unique areas
+\item
+  \emph{focal\_points:} a data frame of reference locations used to
+  allocate hexagons
+\end{itemize}
 
@@
 
-\begin{CodeChunk}
-
-\begin{tabular}{l|l}
-\hline
-parameter & description\\
-\hline
-buffer\_dist & a float value for distance in degrees to extend beyond the geometry provided\\
-\hline
-hex\_size & a float value in degrees for the diameter of the hexagons\\
-\hline
-hex\_filter & amount of hexagons around centroid to consider for allocation\\
-\hline
-width & the angle used to filter the grid points around a centroid\\
-\hline
-\end{tabular}
-
-\end{CodeChunk}
+\begin{itemize}
+\tightlist
+\item
+  \emph{buffer\_dist:} a float value for distance in degrees to extend
+  beyond the geometry provided
+\item
+  \emph{hex\_size:} a float value in degrees for the diameter of the
+  hexagons
+\item
+  \emph{hex\_filter:} amount of hexagons around centroid to consider for
+  allocation
+\item
+  \emph{width:} the angle used to filter the grid points around a
+  centroid
+\end{itemize}
 
@@
 \begin{CodeChunk}
+\begin{figure}
 
-\begin{center}\includegraphics[width=1\linewidth]{figures/4grid} \end{center}
+{\centering \includegraphics[width=1\linewidth]{figures/4grid}
 
+}
+
+\caption[Filter for grid points within a square, then circular, distance for those closest to the centroid]{Filter for grid points within a square, then circular, distance for those closest to the centroid.}\label{fig:buffers}
+\end{figure}
 \end{CodeChunk}
@@
 \begin{CodeChunk}
+\begin{figure}
 
-\begin{center}\includegraphics[width=1\linewidth]{figures/6allocate} \end{center}
+{\centering \includegraphics[width=1\linewidth]{figures/6allocate}
 
+}
+
+\caption[A complete hexagon tile map of Tasmania]{A complete hexagon tile map of Tasmania.}\label{fig:buffs}
+\end{figure}
 \end{CodeChunk}

### 2020-01-18 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
pdf files

@@
 title: 
-  formatted: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With Application to Australian Maps"
-  plain: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map,\nWith Application to Australian Maps"  
+  formatted: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map, \n With Application to Australian Maps"
+  plain: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With Application to Australian Maps"
+  short: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map"  
 abstract: >
@@
 ---
+
+\setcounter{page}{65}
 

### 2020-01-18 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
edits

@@
 
-The current practice for presenting geospatial data involves a choropleth map display. These maps highlight the geographic patterns in geospatially related statistics \citep{SAMGIS}.
+The current practice for presenting geospatial data is a choropleth map display. These maps highlight the geographic patterns in geospatially related statistics \citep{SAMGIS}.
 The land on the map space is divided into geographic units, these boundaries are usually administrative, such as states or counties.
@@
 Australian residents are increasingly congregating around major cities, the vast rural areas are often sparsely populated in comparison to the urban centres. 
-In Australia, government bodies such as the Australian Bureau of Statistics (ABS), and the Australian Electoral Commission (AEC) hold the responsibility for the division of geographic units.
-If it absolutely necessary, the AEC may adjust as the population increases.
+In Australia, government bodies such as the Australian Bureau of Statistics (ABS), and the Australian Electoral Commission (AEC) hold the responsibility for the division of the population into geographic units.
+If it necessary, the AEC may adjust the boundaries of the areas as the population increases.
 The division of the population into approximately equal population areas results in dramatically different square meterage of the geographic areas.
-This results in an unequal attention given to the statistic of each area, this can allow misrepresentation of the spatial distributions of human related statistics in geographic maps.
+This can give unequal attention to the statistic of each area, this can cause misrepresentation of the spatial distributions of human related statistics in geographic maps.
 
 <!-- solutions -->
-The solution to this visualisation problem begins with the geography.
+The solutions to this visualisation problem begin with the geography.
 Cartograms apply a transformation to the geographic boundaries based on the value of the statistic of interest.
 These displays result in a distortion of the map space to represent differences in the statistic across the areas \citep{ACCAC}.
-The statistic of interest is used to determine the layout. When using the
-Australian population, the result is a population cartogram that fails to preserve a recognisable display due to the difference in size of metropolitan and rural areas \citep{ACTUC}, \citep{GOINO}.
-Contiguous cartograms change the shape of an area, preserving boundary relationships of neighbours.
-Non-contiguous cartograms maintain the geographic shape of each area, but lose the connection to neighbours as each areas shrinks or grows.
+The statistic of interest is used to determine the cartogram layout. When the
+Australian population is the statistic of interest, the result is a population cartogram.
+They fail to preserve a recognisable display due to the difference in size of metropolitan and rural areas \citep{ACTUC}, \citep{GOINO}.
+Contiguous cartograms change the shape of areas, while preserving boundary relationships of neighbours.
+Non-contiguous cartograms maintain the geographic shape of each geographic area, but will lose the connection to neighbours as the polygon for each geographic area shrinks or grows.
 
@@
 Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing each administrative area.
-This acknowledges that the amount of residents can be different but recognises that each area, or person is equally important.
+This acknowledges that the amount of residents can be different but recognises that each area, or person within it is equally important.
 
-Tilegrams, Rectangular cartograms \citep{ORC} and Dorling cartograms \citep{ACTUC}, all use one simple shape to represent each area.
-This allows preservation of spatial relationships and decreases the emphasis from the size of the geographic areas.
-These maps focus on the relationship between neighbours attempting to preserve connections, and disregard the unique shapes of the administrative boundaries.
+tile maps, Rectangular cartograms \citep{ORC} and Dorling cartograms \citep{ACTUC}, all use one simple shape to represent each area.
+They place various importance on the preservation of spatial relationships, but all decrease the emphasis on the size of the geographic areas.
+These alternative map displays focus on the relationship between neighbours, attempting to preserve connections, and disregard the unique shapes of the administrative boundaries.
 
-The \pkg{sugarbag} package provides a new method to create tesselated hexagon tilegrams. 
-Extending the tilegram to Australian applications required preserving the spatial relationships.
+The \pkg{sugarbag} package provides a new algorithm to create tesselated hexagon tile maps. 
 It emphasises the capital cities as population hubs, and emphasises the distances rather than size of large, rural geographic units.
@@
 
-This solution operates on a set of simple feature geometry objects, also known as \pkg{sf} \citep{sf} polygons.
+The algorithm presented in \pkg{sugarbag} package operates on a set of simple feature geometry objects, also known as \pkg{sf} \citep{sf} polygons.
 
-There are four steps to create a tesselated hexagon tilegram.
+There are four steps performed to create a tesselated hexagon tile map.
 These steps can be executed by the main function, \code{create_hexmap}, or can be implemented separately for more flexibility.
-There are parameters used in the process that can be provided, if they are not, they will be automatically derived.
+There are parameters used in the process that can be provided by users, if they are not, they will be automatically derived.
 
@@
 The polygon set of Statistical Areas at Level 2 (SA2) \citep{abs2016} of Tasmania in 2016 is provided with the \pkg{sugarbag} package as \code{tas_sa2}. 
-A single column of the data set must be used to identify the unique areas. 
+A single column of the data set is used to identify the unique areas. 
 In this case, the unique SA2 names for each SA2 have been used.
 
-The longitude and latitude centre of the capital cities of Australia are used to allocate areas around the closest capital city.
+The longitude and latitude centre of the capital cities of Australia are used as focal points to allocate each geographic area around the closest capital city.
 Hobart will be the common focal point, as this example uses only the areas in the state of Tasmania.
@@
 
-The following parameters will be determined within \code{create_hexmap} if they are not provided. They are created throughout the following example:
+The following parameters will be determined within \code{create_hexmap} if they are not provided. They are created as they are needed throughout the following example:
 
@@
 
-Individual \pkg{sugarbag} functions can be used outside of the main function.
-The set of polygons should be provided as an \pkg{sf} object, this is a data frame containing a \code{geometry} column. The \code{read_shape} function can assist in creating this object.
+A set of centroids may be used directly.
+The set of polygons should be provided as an \pkg{sf} object, this is a data frame containing a \code{geometry} column.
+The \code{read_shape} function can assist in creating this object for use in `R`.
 
 The centroids can be derived from the set of polygons using the \code{create_centroids} function:
+
 ```{r cents}
@@
 
-A tilegram presents areas on a tellesated set of tiles.
-The grid is created to ensure tessellation between the hexagons.
+A grid is created to ensure tessellation between the hexagons that represent the geographic units on a hexagon tile map.
 
-The grid of possible hexagon centroids is made using the \code{create_grid} function.
-The grid creation requires several steps.
+The grid of possible hexagon locations is made using the \code{create_grid} function.
 It uses the centroids, the hexagon size and the buffer distance.
@@
 
-A set of longitude columns, and latitude rows are created to define the locations of the hexagons. The distance between each row and column is defined by the size specified as \code{hex_size}.
-The minimum and maximum, longitude and latitude values of the centroid locations are found.
+A set of longitude columns, and latitude rows are created to define the locations of the hexagons. The distance between each row and column is the size specified by \code{hex_size}.
 Equally spaced columns are created from the minimum longitude minus the buffer distance, up to the maximum longitude plus the buffer distance.
-The rows are then created from the latitude values and the buffer distance.
-An individual hexagon location is created from all intersections of the longitude columns and latitude rows.
+Similarly, the rows are created from the latitude values and the buffer distance.
+A unique hexagon location is created from all intersections of the longitude columns and latitude rows.
+Figure \ref{fig:grid2} shows the original grid on the left, to allow for tessellating hexagons, every second latitude row on the grid is shifted right, by half of the hexagon size.
+The grid for tessellation is shown on the right.
 
-A square grid could be used for sqaure tiles, but it will not facilitate tessellated hexagons.
-Figure \ref{fig:grid2} allows for hexagons, as every second latitude row on the grid is shifted right, by half of the hexagon size.
-
-```{r grid2, fig.cap = "Grid points to create a tilegram.", out.width = "100%", echo = FALSE}
+```{r grid2, fig.cap = "Grid points to create a tile map.", out.width = "100%", echo = FALSE}
 knitr::include_graphics(path = "figures/2grid.png")
@@
 Not all of the grid points will be used, especially if islands result in a large grid space.
-To filter the grid for appropriate points for allocation,
-the \code{create_buffer} function is called within \code{create_grid}.
+To filter the grid for appropriate hexagon locations for allocation, the \code{create_buffer} function is used by \code{create_grid}.
 It finds the grid points needed to best capture the set of centroids on a hexagon tile map.
 
-For each centroid location, the closest latitude row and longitude column are found. Then rows and columns of centroids are divided into 20 groups.
+The closest latitude row and longitude column are found for each centroid location. Then rows and columns of centroids are divided into 20 groups.
 The amount of rows in each latitude group and the amount of columns in each longitude group are used as the width of rolling windows.
-The rolling windows can be seen on the bottom and right of Fig.
+The rolling windows can be seen on the bottom and right of the gris shown in Fig.
 \ref{fig:filter_grid}.
@@
 
-Only the grid points between the rolling average of the minimum and maximum centroid values are kept, for each row and column of the grid.
+The grid points are kept only if they fall between the rolling average of the minimum and maximum centroid values after accounting for the buffer distance, for each row and column of the grid.
+The sparsely populated South-West region of National Park has much fewer points available compared to the South-East region containing the city of Hobart.
 
 ```{r filter_grid, fig.cap = "All possible hexagon locations from the initial grid are shown with blue outlines.
-The blue dots shown the grid points left as to choose from after the buffer step.
-The rolling windows to the right show the rows used to filter the hexagon locations.", echo = FALSE, out.width = "100%"}
+The blue dots show the grid points left to choose from after the buffer step.
+The rolling windows show the collections of rows and columns used to filter the hexagon locations.", echo = FALSE, out.width = "100%"}
 knitr::include_graphics(path = "figures/3grid.png", dpi = 300)
@@
 The name of the closest focal point, and the distance and angle from focal point to polygon centroid is joined to polygon data set.
-To minimise time taken for this step, only Tasmania's capital city Hobart is provided.
+To minimise time taken for this step only one option is provided, Tasmania's capital city Hobart.
 The order for allocation is determined by the distance between the polygon centroid and it's closest focal point.
-The points are arranged from the centroid closest to the focal points, to the furthest.
+The points are arranged from the centroid closest to the focal point(s), to the furthest.
 
@@
 This will preserve spatial relationships with the focal point, as the inner city areas are allocated first, they will be placed closest to the capital, and the areas that are further will then be accommodated.
-Only the hexagon grid points that have not yet been allocated are considered.
+The possible hexagon grid points reduces by one after each allocation, then only those that have not yet been allocated are considered.
 
-The possible hexagon locations consider for a centroid location are determined by the \code{hex_filter}.
+The possible hexagon locations to consider for a centroid are determined by the \code{hex_filter}.
 This is the maximum amount of hexagons between the centroid and the furthest considered hexagon.
 It is used to subset possible grid points to only those surrounding the polygon centroid within an appropriate range.
-A smaller distance will increase speed, but can decrease accuracy if the angle width increases.
+A smaller distance will increase speed, but can decrease accuracy when width of the angle increases.
 
@@
 
-The following example considers one of the Statistical Areas at Level 2. 
+The following example considers the first of the Statistical Areas at Level 2. 
 Within the algorithm, these steps are repeated for each polygon.
@@
 
-Keep only the available hexagon points, this will prevent multiple areas being allocated to the same hexagon.
+Keeping only the available hexagon points prevents multiple geographic units from being allocated to the same hexagon.
 
@@
 
-This will allow only the closest points that are not yet assigned, to be considered.
-
-A box of possible hexagon locations around the centroid. The corners of the box may not look square as the buffer has already removed unnecessary points from over the ocean.
+A box of possible hexagon locations around the centroid allows only the closest points that are not yet assigned to be considered.
+The corners of the box may not appear square if the buffer step has already removed unnecessary points from over the ocean.
 
@@
 The \code{width} parameter is used to take a slice of the remaining points.
-This uses the angle from the closest capital city, to the current centroid.
+The width is the amount of degrees used on either side of the angle from the focal point to centroid location.
+This uses the angle from the closest capital city, to the current centroid as seen in Figure \ref{fig:angles} .
 This allows the spatial relationship to be preserved, even when it is allocated to a hexagon that is further from the focal point then the original centroid location.
+
+```{r angles, fig.cap = "Filter for grid points within the angle from the focal point to the centroid.", echo = FALSE, out.width = "100%"}
+knitr::include_graphics(path = "figures/5allocate.png")
+```
 
@@
 This will increase if no points can be found within the \code{hex_filter} distance.
-The angle of 30 was chosen to allow the algorithm to choose hexagons that best maintained the spatial relationship between the focal point and geographic centroid.
-The allocation is returned and combined with the data relating to each polygon.
+The default angle of 30 was chosen to allow the algorithm to choose hexagons that best maintained the spatial relationship between the focal point and geographic centroid.
 
@@
 The small red areas visible in the choropleth map (a) along the north coast are much larger in the hexagon tile maps.
-The hexagon tile map shows less yellow, this no longer overwhelms the map space with the information regarding the more rural areas.
+The hexagon tile map shows less yellow, this no longer overwhelms the map space with the information regarding the rural areas.
 
@@
 
-It is possible to incorporate the neighbouring areas for each SA2, for stronger preservation of the spatial distribution.
+It is possible to consider the neighbouring areas for each SA2, for stronger preservation of the spatial distribution.
 
 An additional step can be included to allow the neighbours that have alredy been allocated to influence the placement of the current centroid. 
-This requires respecifying the \code{sf} object as the argument for the \code{use_neighbours} parameter.
+This requires specifying the \code{sf} object as the argument for the \code{use_neighbours} parameter.
 This calculates neighbours using intersections of their polygons.
@@
 
-For the current centroid, the list of neighbours is consulted.
-If any neighbour was already allocated, the surrounding hexagons on the grid are prioritised.
+During the allocation of each centroid, the list of neighbours is consulted.
+If any neighbour was already allocated, the hexagons surrounding the neighbours on the grid are prioritised.
 For multiple neighbours, the neighbouring hexagon grid points are aggregated and considered in order of distance from the original centroid.
@@
 The \pkg{gganimate} package can be used to make an animation.
-It requires connecting the polygons for each area in two displays two displays, which can be done using the \code{sf_id} variable, such as the SA2 name.
+It requires connecting the polygons for each area in two displays, which can be done using the \code{sf_id} variable, such as the SA2 name.
 The animation^[This animation can be viewed at: https://sugarbagjss.netlify.com/] connecting these two displays will highlight the rapid growth of the inner-city areas, and will decrease the large rural areas.
@@
 It is possible to use alternative maps to communicate spatial distributions.While a choropleth map display is the current practice spatial visualisation of geographical data.
-Current methods do not always work for Australia due to the large gaps between densely populated capital cities.
-The administrative boundaries may distract from the statistics, communicated using colour.
+Current methods do not always work for Australia due to the large geographic space between the densely populated capital cities.
+The administrative boundaries may also distract from the statistics communicated using colour.
 
@@
 This map algorithm is implemented in the \pkg{sugarbag} @sugarbag package written for \code{R} @R.
-The \pkg{sugarbag} package creates tesselated hexagon tilegrams.
+The \pkg{sugarbag} package creates tesselated hexagon tile maps.
 The Australian application preserves the spatial relationships, emphasising capital cities.
@@
 The algorithm is heavily dependent on the focal points used, as this determines the order of allocation.
-It works on the assumption that viewers can use directional assumptions to identify their neighbourhoods, this can be aided by the animation.
+It works on the assumption that viewers can use directional relationships to identify their neighbourhoods but this can be aided by the animation.
 
@@
 They would also like to thank Professor Kerrie Mengersen for suggestions and comments.
-Mitch O'Hara-Wild provided assistance with some parts of the algorithm and code.
+Mitchell O'Hara-Wild provided assistance with some parts of the algorithm and code.
 Sayani Gupta provided helpful advice on parts of this paper.
@@
 The code for \pkg{sugarbag} [@sugarbag] can be found on [CRAN](https://cran.r-project.org/web/packages/sugarbag/index.html), along with vignettes on installation and usage.
-
-Australian Electoral Data can be found in the \pkg{eechidna} package for R.

### 2020-01-18 kobakian_sugarbag_jss/kobakian_sugarbag_jss.tex
pdf files
edits

@@
 Application to Australian Maps}
+\Shorttitle{An Algorithm For Spatial Mapping Using a Hexagon Tile Map}
 
@@
 
+\setcounter{page}{65}
+
 \hypertarget{introduction}{%
@@
 
-The current practice for presenting geospatial data involves a
-choropleth map display. These maps highlight the geographic patterns in
-geospatially related statistics \citep{SAMGIS}. The land on the map
-space is divided into geographic units, these boundaries are usually
-administrative, such as states or counties. The units are filled with
-colour to represent the value of the statistic \citep{EI}.
+The current practice for presenting geospatial data is a choropleth map
+display. These maps highlight the geographic patterns in geospatially
+related statistics \citep{SAMGIS}. The land on the map space is divided
+into geographic units, these boundaries are usually administrative, such
+as states or counties. The units are filled with colour to represent the
+value of the statistic \citep{EI}.
 
@@
 Bureau of Statistics (ABS), and the Australian Electoral Commission
-(AEC) hold the responsibility for the division of geographic units. If
-it absolutely necessary, the AEC may adjust as the population increases.
-The division of the population into approximately equal population areas
-results in dramatically different square meterage of the geographic
-areas. This results in an unequal attention given to the statistic of
-each area, this can allow misrepresentation of the spatial distributions
-of human related statistics in geographic maps.
+(AEC) hold the responsibility for the division of the population into
+geographic units. If it necessary, the AEC may adjust the boundaries of
+the areas as the population increases. The division of the population
+into approximately equal population areas results in dramatically
+different square meterage of the geographic areas. This can give unequal
+attention to the statistic of each area, this can cause
+misrepresentation of the spatial distributions of human related
+statistics in geographic maps.
 
-The solution to this visualisation problem begins with the geography.
+The solutions to this visualisation problem begin with the geography.
 Cartograms apply a transformation to the geographic boundaries based on
@@
 across the areas \citep{ACCAC}. The statistic of interest is used to
-determine the layout. When using the Australian population, the result
-is a population cartogram that fails to preserve a recognisable display
-due to the difference in size of metropolitan and rural areas
-\citep{ACTUC}, \citep{GOINO}. Contiguous cartograms change the shape of
-an area, preserving boundary relationships of neighbours. Non-contiguous
-cartograms maintain the geographic shape of each area, but lose the
-connection to neighbours as each areas shrinks or grows.
+determine the cartogram layout. When the Australian population is the
+statistic of interest, the result is a population cartogram. They fail
+to preserve a recognisable display due to the difference in size of
+metropolitan and rural areas \citep{ACTUC}, \citep{GOINO}. Contiguous
+cartograms change the shape of areas, while preserving boundary
+relationships of neighbours. Non-contiguous cartograms maintain the
+geographic shape of each geographic area, but will lose the connection
+to neighbours as the polygon for each geographic area shrinks or grows.
 
@@
 acknowledges that the amount of residents can be different but
-recognises that each area, or person is equally important.
+recognises that each area, or person within it is equally important.
 
-Tilegrams, Rectangular cartograms \citep{ORC} and Dorling cartograms
-\citep{ACTUC}, all use one simple shape to represent each area. This
-allows preservation of spatial relationships and decreases the emphasis
-from the size of the geographic areas. These maps focus on the
-relationship between neighbours attempting to preserve connections, and
-disregard the unique shapes of the administrative boundaries.
+tile maps, Rectangular cartograms \citep{ORC} and Dorling cartograms
+\citep{ACTUC}, all use one simple shape to represent each area. They
+place various importance on the preservation of spatial relationships,
+but all decrease the emphasis on the size of the geographic areas. These
+alternative map displays focus on the relationship between neighbours,
+attempting to preserve connections, and disregard the unique shapes of
+the administrative boundaries.
 
-The \pkg{sugarbag} package provides a new method to create tesselated
-hexagon tilegrams. Extending the tilegram to Australian applications
-required preserving the spatial relationships. It emphasises the capital
-cities as population hubs, and emphasises the distances rather than size
-of large, rural geographic units.
+The \pkg{sugarbag} package provides a new algorithm to create tesselated
+hexagon tile maps. It emphasises the capital cities as population hubs,
+and emphasises the distances rather than size of large, rural geographic
+units.
 
@@
 
-This solution operates on a set of simple feature geometry objects, also
-known as \pkg{sf} \citep{sf} polygons.
+The algorithm presented in \pkg{sugarbag} package operates on a set of
+simple feature geometry objects, also known as \pkg{sf} \citep{sf}
+polygons.
 
-There are four steps to create a tesselated hexagon tilegram. These
-steps can be executed by the main function, \code{create_hexmap}, or can
-be implemented separately for more flexibility. There are parameters
-used in the process that can be provided, if they are not, they will be
-automatically derived.
+There are four steps performed to create a tesselated hexagon tile map.
+These steps can be executed by the main function, \code{create_hexmap},
+or can be implemented separately for more flexibility. There are
+parameters used in the process that can be provided by users, if they
+are not, they will be automatically derived.
 
@@
 Tasmania in 2016 is provided with the \pkg{sugarbag} package as
-\code{tas_sa2}. A single column of the data set must be used to identify
-the unique areas. In this case, the unique SA2 names for each SA2 have
-been used.
+\code{tas_sa2}. A single column of the data set is used to identify the
+unique areas. In this case, the unique SA2 names for each SA2 have been
+used.
 
 The longitude and latitude centre of the capital cities of Australia are
-used to allocate areas around the closest capital city. Hobart will be
-the common focal point, as this example uses only the areas in the state
-of Tasmania.
+used as focal points to allocate each geographic area around the closest
+capital city. Hobart will be the common focal point, as this example
+uses only the areas in the state of Tasmania.
 
@@
 The following parameters will be determined within \code{create_hexmap}
-if they are not provided. They are created throughout the following
-example:
+if they are not provided. They are created as they are needed throughout
+the following example:
 
@@
 
-Individual \pkg{sugarbag} functions can be used outside of the main
-function. The set of polygons should be provided as an \pkg{sf} object,
-this is a data frame containing a \code{geometry} column. The
-\code{read_shape} function can assist in creating this object.
+A set of centroids may be used directly. The set of polygons should be
+provided as an \pkg{sf} object, this is a data frame containing a
+\code{geometry} column. The \code{read_shape} function can assist in
+creating this object for use in \texttt{R}.
 
@@
 
-A tilegram presents areas on a tellesated set of tiles. The grid is
-created to ensure tessellation between the hexagons.
+A grid is created to ensure tessellation between the hexagons that
+represent the geographic units on a hexagon tile map.
 
-The grid of possible hexagon centroids is made using the
-\code{create_grid} function. The grid creation requires several steps.
-It uses the centroids, the hexagon size and the buffer distance.
+The grid of possible hexagon locations is made using the
+\code{create_grid} function. It uses the centroids, the hexagon size and
+the buffer distance.
 
@@
 locations of the hexagons. The distance between each row and column is
-defined by the size specified as \code{hex_size}. The minimum and
-maximum, longitude and latitude values of the centroid locations are
-found. Equally spaced columns are created from the minimum longitude
-minus the buffer distance, up to the maximum longitude plus the buffer
-distance. The rows are then created from the latitude values and the
-buffer distance. An individual hexagon location is created from all
-intersections of the longitude columns and latitude rows.
-
-A square grid could be used for sqaure tiles, but it will not facilitate
-tessellated hexagons. Figure \ref{fig:grid2} allows for hexagons, as
-every second latitude row on the grid is shifted right, by half of the
-hexagon size.
+the size specified by \code{hex_size}. Equally spaced columns are
+created from the minimum longitude minus the buffer distance, up to the
+maximum longitude plus the buffer distance. Similarly, the rows are
+created from the latitude values and the buffer distance. A unique
+hexagon location is created from all intersections of the longitude
+columns and latitude rows. Figure \ref{fig:grid2} shows the original
+grid on the left, to allow for tessellating hexagons, every second
+latitude row on the grid is shifted right, by half of the hexagon size.
+The grid for tessellation is shown on the right.
 
@@
 
-\caption[Grid points to create a tilegram]{Grid points to create a tilegram.}\label{fig:grid2}
+\caption[Grid points to create a tile map]{Grid points to create a tile map.}\label{fig:grid2}
 \end{figure}
@@
 Not all of the grid points will be used, especially if islands result in
-a large grid space. To filter the grid for appropriate points for
-allocation, the \code{create_buffer} function is called within
+a large grid space. To filter the grid for appropriate hexagon locations
+for allocation, the \code{create_buffer} function is used by
 \code{create_grid}. It finds the grid points needed to best capture the
@@
 
-For each centroid location, the closest latitude row and longitude
-column are found. Then rows and columns of centroids are divided into 20
-groups. The amount of rows in each latitude group and the amount of
+The closest latitude row and longitude column are found for each
+centroid location. Then rows and columns of centroids are divided into
+20 groups. The amount of rows in each latitude group and the amount of
 columns in each longitude group are used as the width of rolling
-windows. The rolling windows can be seen on the bottom and right of Fig.
-\ref{fig:filter_grid}. This will tailor the available grid points to
-those most likely to be used. It also helps reduce the amount of time
-taken, as it decreases the amount of points considered for each centroid
-allocation.
+windows. The rolling windows can be seen on the bottom and right of the
+gris shown in Fig. \ref{fig:filter_grid}. This will tailor the available
+grid points to those most likely to be used. It also helps reduce the
+amount of time taken, as it decreases the amount of points considered
+for each centroid allocation.
 
@@
 
-Only the grid points between the rolling average of the minimum and
-maximum centroid values are kept, for each row and column of the grid.
+The grid points are kept only if they fall between the rolling average
+of the minimum and maximum centroid values after accounting for the
+buffer distance, for each row and column of the grid. The sparsely
+populated South-West region of National Park has much fewer points
+available compared to the South-East region containing the city of
+Hobart.
 
@@
 \caption[All possible hexagon locations from the initial grid are shown with blue outlines]{All possible hexagon locations from the initial grid are shown with blue outlines.
-The blue dots shown the grid points left as to choose from after the buffer step.
-The rolling windows to the right show the rows used to filter the hexagon locations.}\label{fig:filter_grid}
+The blue dots show the grid points left to choose from after the buffer step.
+The rolling windows show the collections of rows and columns used to filter the hexagon locations.}\label{fig:filter_grid}
 \end{figure}
@@
 the distance and angle from focal point to polygon centroid is joined to
-polygon data set. To minimise time taken for this step, only Tasmania's
-capital city Hobart is provided. The order for allocation is determined
-by the distance between the polygon centroid and it's closest focal
-point. The points are arranged from the centroid closest to the focal
-points, to the furthest.
+polygon data set. To minimise time taken for this step only one option
+is provided, Tasmania's capital city Hobart. The order for allocation is
+determined by the distance between the polygon centroid and it's closest
+focal point. The points are arranged from the centroid closest to the
+focal point(s), to the furthest.
 
@@
 allocated first, they will be placed closest to the capital, and the
-areas that are further will then be accommodated. Only the hexagon grid
-points that have not yet been allocated are considered.
+areas that are further will then be accommodated. The possible hexagon
+grid points reduces by one after each allocation, then only those that
+have not yet been allocated are considered.
 
-The possible hexagon locations consider for a centroid location are
-determined by the \code{hex_filter}. This is the maximum amount of
-hexagons between the centroid and the furthest considered hexagon. It is
-used to subset possible grid points to only those surrounding the
-polygon centroid within an appropriate range. A smaller distance will
-increase speed, but can decrease accuracy if the angle width increases.
+The possible hexagon locations to consider for a centroid are determined
+by the \code{hex_filter}. This is the maximum amount of hexagons between
+the centroid and the furthest considered hexagon. It is used to subset
+possible grid points to only those surrounding the polygon centroid
+within an appropriate range. A smaller distance will increase speed, but
+can decrease accuracy when width of the angle increases.
 
@@
 
-The following example considers one of the Statistical Areas at Level 2.
-Within the algorithm, these steps are repeated for each polygon.
+The following example considers the first of the Statistical Areas at
+Level 2. Within the algorithm, these steps are repeated for each
+polygon.
 
@@
 
-Keep only the available hexagon points, this will prevent multiple areas
-being allocated to the same hexagon.
+Keeping only the available hexagon points prevents multiple geographic
+units from being allocated to the same hexagon.
 
@@
 
-This will allow only the closest points that are not yet assigned, to be
-considered.
-
-A box of possible hexagon locations around the centroid. The corners of
-the box may not look square as the buffer has already removed
+A box of possible hexagon locations around the centroid allows only the
+closest points that are not yet assigned to be considered. The corners
+of the box may not appear square if the buffer step has already removed
 unnecessary points from over the ocean.
@@
 The \code{width} parameter is used to take a slice of the remaining
-points. This uses the angle from the closest capital city, to the
-current centroid. This allows the spatial relationship to be preserved,
+points. The width is the amount of degrees used on either side of the
+angle from the focal point to centroid location. This uses the angle
+from the closest capital city, to the current centroid as seen in Figure
+\ref{fig:angles} . This allows the spatial relationship to be preserved,
 even when it is allocated to a hexagon that is further from the focal
 point then the original centroid location.
+
+\begin{CodeChunk}
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{figures/5allocate}
+
+}
+
+\caption[Filter for grid points within the angle from the focal point to the centroid]{Filter for grid points within the angle from the focal point to the centroid.}\label{fig:angles}
+\end{figure}
+\end{CodeChunk}
 
@@
 plus and minus 30 degrees. This will increase if no points can be found
-within the \code{hex_filter} distance. The angle of 30 was chosen to
-allow the algorithm to choose hexagons that best maintained the spatial
-relationship between the focal point and geographic centroid. The
-allocation is returned and combined with the data relating to each
-polygon.
+within the \code{hex_filter} distance. The default angle of 30 was
+chosen to allow the algorithm to choose hexagons that best maintained
+the spatial relationship between the focal point and geographic
+centroid.
 
@@
 hexagon tile map shows less yellow, this no longer overwhelms the map
-space with the information regarding the more rural areas.
+space with the information regarding the rural areas.
 
@@
 
-It is possible to incorporate the neighbouring areas for each SA2, for
+It is possible to consider the neighbouring areas for each SA2, for
 stronger preservation of the spatial distribution.
@@
 alredy been allocated to influence the placement of the current
-centroid. This requires respecifying the \code{sf} object as the
-argument for the \code{use_neighbours} parameter. This calculates
-neighbours using intersections of their polygons. This occurs for all
-areas before any allocations begin.
+centroid. This requires specifying the \code{sf} object as the argument
+for the \code{use_neighbours} parameter. This calculates neighbours
+using intersections of their polygons. This occurs for all areas before
+any allocations begin.
 
-For the current centroid, the list of neighbours is consulted. If any
-neighbour was already allocated, the surrounding hexagons on the grid
-are prioritised. For multiple neighbours, the neighbouring hexagon grid
-points are aggregated and considered in order of distance from the
-original centroid.
+During the allocation of each centroid, the list of neighbours is
+consulted. If any neighbour was already allocated, the hexagons
+surrounding the neighbours on the grid are prioritised. For multiple
+neighbours, the neighbouring hexagon grid points are aggregated and
+considered in order of distance from the original centroid.
 
@@
 The \pkg{gganimate} package can be used to make an animation. It
-requires connecting the polygons for each area in two displays two
-displays, which can be done using the \code{sf_id} variable, such as the
-SA2 name. The animation\footnote{This animation can be viewed at:
+requires connecting the polygons for each area in two displays, which
+can be done using the \code{sf_id} variable, such as the SA2 name. The
+animation\footnote{This animation can be viewed at:
   \url{https://sugarbagjss.netlify.com/}} connecting these two displays
@@
 spatial visualisation of geographical data. Current methods do not
-always work for Australia due to the large gaps between densely
-populated capital cities. The administrative boundaries may distract
-from the statistics, communicated using colour.
+always work for Australia due to the large geographic space between the
+densely populated capital cities. The administrative boundaries may also
+distract from the statistics communicated using colour.
 
@@
 the \pkg{sugarbag} \citet{sugarbag} package written for \code{R}
-\citet{R}. The \pkg{sugarbag} package creates tesselated hexagon
-tilegrams. The Australian application preserves the spatial
-relationships, emphasising capital cities. The hexagon tile map is a
-visualisation solution that highlights spatial distributions.
+\citet{R}. The \pkg{sugarbag} package creates tesselated hexagon tile
+maps. The Australian application preserves the spatial relationships,
+emphasising capital cities. The hexagon tile map is a visualisation
+solution that highlights spatial distributions.
 
@@
 the focal points used, as this determines the order of allocation. It
-works on the assumption that viewers can use directional assumptions to
-identify their neighbourhoods, this can be aided by the animation.
+works on the assumption that viewers can use directional relationships
+to identify their neighbourhoods but this can be aided by the animation.
 
@@
 also like to thank Professor Kerrie Mengersen for suggestions and
-comments. Mitch O'Hara-Wild provided assistance with some parts of the
-algorithm and code. Sayani Gupta provided helpful advice on parts of
+comments. Mitchell O'Hara-Wild provided assistance with some parts of
+the algorithm and code. Sayani Gupta provided helpful advice on parts of
 this paper.
@@
 
-Australian Electoral Data can be found in the \pkg{eechidna} package for
-R.
-
 \bibliography{sugarbag.bib}

### 2020-01-18 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
add angle

@@
 keywords:
-  # at least one keyword must be supplied
+  ## at least one keyword must be supplied
   formatted: [spatial, statistics, cartogram]
@@
 
-# Introduction
+## Introduction
 
@@
 
-# Algorithm
+## Algorithm
 
@@
 
-## Parameters
+#### Parameters
 
@@
 
-## Polygon set
+#### Polygon set
 
@@
 
-## Create the set of centroid points
+#### Create the set of centroid points
 
@@
 
-## Create the hexagon grid points
+#### Create the hexagon grid points
 
@@
 
-### Step 1: Creating a tesselated grid
+###### Step 1: Creating a tesselated grid
 
@@
 
-### Step 2: Rolling windows
+###### Step 2: Rolling windows
 
@@
 
-### Step 3: Filtering the grid
+###### Step 3: Filtering the grid
 
@@
 
-## Centroid to focal point distance
+#### Centroid to focal point distance
 
@@
 
-## Allocate each centroid to a hexagon grid point
+#### Allocate each centroid to a hexagon grid point
 
@@
   hex_grid = grid,
-  hex_size = 0.2, # same size used in create_grid
+  hex_size = 0.2, ## same size used in create_grid
   hex_filter = 10,
@@
 
-### Step 1: Filter the grid for unassigned hexagon points
+###### Step 1: Filter the grid for unassigned hexagon points
 
@@
 
-### Step 2: Filter the grid points for those closest to the centroid
+###### Step 2: Filter the grid points for those closest to the centroid
 
@@
 
-## Neighbour relationships
+#### Neighbour relationships
 
@@
 
-# Using sugarbag
+## Using sugarbag
 
-## Installation
+#### Installation
 
@@
 
-## Creating a hexagon tile map
+#### Creating a hexagon tile map
 
@@
 ```{r full_hexmapcode, echo = TRUE, warning = FALSE, message = FALSE, eval=FALSE}
-# Load data
+## Load data
 data(tas_sa2)
 
-# Create centroids set
+## Create centroids set
 centroids <- create_centroids(tas_sa2, "SA2_NAME16")
 
-# Create hexagon grid
+## Create hexagon grid
 grid <- create_grid(centroids = centroids,
@@
 
-# Allocate polygon centroids to hexagon grid points
+## Allocate polygon centroids to hexagon grid points
 hex_allocated <- allocate(
@@
   sf_id = "SA2_NAME16",
-  # same column used in create_centroids
+  ## same column used in create_centroids
   hex_size = 0.2,
-  # same size used in create_grid
+  ## same size used in create_grid
   hex_filter = 10,
@@
 
-# Prepare to plot
+## Prepare to plot
 fort_hex <- fortify_hexagon(data = hex_allocated, sf_id = "SA2_NAME16", hex_size = 0.2)
 
-# Make a plot
+## Make a plot
 library(ggplot2)
@@
 
-# Applications
+## Applications
 
-## Australian Cancer Atlas
+#### Australian Cancer Atlas
 
@@
 
-# Animation
+## Animation
 
@@
 
-# Conclusion
+## Conclusion
 
@@
 
-# Acknowledgements
+## Acknowledgements
 

### 2020-02-14 03-algorithm.Rmd
distill format

--- 2020-01-18 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
@@
 ---
-documentclass: jss
-author:
-  - name: Stephanie Kobakian
-    affiliation: Queensland University of Technology
-    address: >
-      School of Mathematical Sciences,
-      Science and Engineering Faculty,
-      Brisbane, QLD, Australia
-    email: \email{stephanie.kobakian@qut.edu.au}
-  - name: Dianne Cook
-    affiliation: Monash University
-    address: >
-      Department of Econometrics and Business Statistics,
-      Melbourne, VIC, Australia
-    email: \email{dicook@monash.edu}
-  - name: Earl Duncan
-    affiliation: Queensland University of Technology
-    address: >
-      School of Mathematical Sciences,
-      Science and Engineering Faculty,
-      Brisbane, QLD, Australia
-    email: \email{earl.duncan@qut.edu.au}
-title: 
-  formatted: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map, \n With Application to Australian Maps"
-  plain: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With Application to Australian Maps"
-  short: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map"  
-abstract: >
-  This algorithm creates a tesselated hexagon display to represent each of the spatial polygons.
+chapter: 3
+knit: "bookdown::render_book"
+---
+
+# An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With Application to Australian Maps {#algorithm}
+
+This chapter relates to the first research aim as stated in Section \ref{sec:aims}.
+The chapter introduces the steps of the algorithm.
+The steps follow the procedures implemented in the `sugarbag` [@sugarbag] package functions, that allow users to run the algorithm in `R` [@R].
+It uses the Statistical Areas of Australia at Level 2, taking a subset and considering only those located within the island of Tasmania.
+It also provides an example of how to animate between the choropleth map display and the hexagon tile map.
+
+This chapter will be submitted for publication to the *Journal of Statistical Software* for publication. 
+The steps in this algorithm are implemented in the `sugarbag` [@sugarbag] package for `R` [@R].
+
+## Abstract {-}
+
+This algorithm creates a tessellated hexagon display to represent each of the spatial polygons.
 It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units.
@@
 Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
-keywords:
-  ## at least one keyword must be supplied
-  formatted: [spatial, statistics, cartogram]
-preamble: >
-  \usepackage{amsmath}
-biblio-style: jss
-output:
-  rticles::jss_article:
-    fig_caption: true
-    citation_package: natbib
-bibliography: sugarbag.bib
-link-citations: true
----
-
-\setcounter{page}{65}
 
@@
 options("citation_format" = "pandoc")
-BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')
+BibOptions(check.entries = FALSE, style = "markdown")
 ```
@@
 
-The current practice for presenting geospatial data is a choropleth map display. These maps highlight the geographic patterns in geospatially related statistics \citep{SAMGIS}.
+The current practice for presenting geospatial data is a choropleth map display. These maps highlight the geographic patterns in geospatially related statistics [@SAMGIS].
 The land on the map space is divided into geographic units, these boundaries are usually administrative, such as states or counties.
-The units are filled with colour to represent the value of the statistic \citep{EI}.
+The units are filled with colour to represent the value of the statistic [@EI].
 
@@
 Cartograms apply a transformation to the geographic boundaries based on the value of the statistic of interest.
-These displays result in a distortion of the map space to represent differences in the statistic across the areas \citep{ACCAC}.
+These displays result in a distortion of the map space to represent differences in the statistic across the areas [@ACCAC].
 The statistic of interest is used to determine the cartogram layout. When the
 Australian population is the statistic of interest, the result is a population cartogram.
-They fail to preserve a recognisable display due to the difference in size of metropolitan and rural areas \citep{ACTUC}, \citep{GOINO}.
+They fail to preserve a recognisable display due to the difference in size of metropolitan and rural areas [@ACTUC], [@GOINO].
 Contiguous cartograms change the shape of areas, while preserving boundary relationships of neighbours.
@@
 
-tile maps, Rectangular cartograms \citep{ORC} and Dorling cartograms \citep{ACTUC}, all use one simple shape to represent each area.
+tile maps, Rectangular cartograms [@ORC] and Dorling cartograms [@ACTUC], all use one simple shape to represent each area.
 They place various importance on the preservation of spatial relationships, but all decrease the emphasis on the size of the geographic areas.
@@
 
-The \pkg{sugarbag} package provides a new algorithm to create tesselated hexagon tile maps. 
+The `sugarbag` package provides a new algorithm to create tessellated hexagon tile maps. 
 It emphasises the capital cities as population hubs, and emphasises the distances rather than size of large, rural geographic units.
@@
 
-The algorithm presented in \pkg{sugarbag} package operates on a set of simple feature geometry objects, also known as \pkg{sf} \citep{sf} polygons.
+The algorithm presented in `sugarbag` package operates on a set of simple feature geometry objects, also known as `sf` [@sf] polygons.
 
-There are four steps performed to create a tesselated hexagon tile map.
-These steps can be executed by the main function, \code{create_hexmap}, or can be implemented separately for more flexibility.
+There are four steps performed to create a tessellated hexagon tile map.
+These steps can be executed by the main function, `create_hexmap`, or can be implemented separately for more flexibility.
 There are parameters used in the process that can be provided by users, if they are not, they will be automatically derived.
@@
 
-The \code{create_hexmap} function requires several parameters, if they are not provided, the information will be derived from the simple features (\pkg{sf}) set of shapes used.
-Users may choose to only use the \code{allocate} function when they wish to use a set of centroids, rather than \pkg{sf} polygons.
+The `create_hexmap` function requires several parameters, if they are not provided, the information will be derived from the simple features (`sf`) set of shapes used.
+Users may choose to only use the `allocate` function when they wish to use a set of centroids, rather than [@sf] polygons.
 
-The following parameters must be provided to \code{create_hexmap}:
+The following parameters must be provided to `create_hexmap}:
 
@@
 
-The polygon set of Statistical Areas at Level 2 (SA2) \citep{abs2016} of Tasmania in 2016 is provided with the \pkg{sugarbag} package as \code{tas_sa2}. 
+The polygon set of Statistical Areas at Level 2 (SA2) [@abs2016] of Tasmania in 2016 is provided with the `sugarbag` package as `tas_sa2`. 
 A single column of the data set is used to identify the unique areas. 
@@
 
-The following parameters will be determined within \code{create_hexmap} if they are not provided. They are created as they are needed throughout the following example:
+The following parameters will be determined within `create_hexmap` if they are not provided. They are created as they are needed throughout the following example:
 
@@
 A set of centroids may be used directly.
-The set of polygons should be provided as an \pkg{sf} object, this is a data frame containing a \code{geometry} column.
-The \code{read_shape} function can assist in creating this object for use in `R`.
+The set of polygons should be provided as an `sf` object, this is a data frame containing a `geometry` column.
+The `read_shape` function can assist in creating this object for use in `R`.
 
-The centroids can be derived from the set of polygons using the \code{create_centroids} function:
+The centroids can be derived from the set of polygons using the `create_centroids` function:
 
@@
 
-```{r centroids_plot, out.width = "100%", echo = FALSE, eval = FALSE, fig.cap = "The geographic shapes of the Statistical Areas of Tasmania at Level 2.
-The points show the locations of the centroids of the SA2 areas."}
-knitr::include_graphics(path = "figures/1centroids.png")
-```
+<!-- ```{r centroids-plot, out.width = "100%", echo = FALSE, eval = FALSE, fig.cap = "The geographic shapes of the Statistical Areas of Tasmania at Level 2.
+The points show the locations of the centroids of the SA2 areas."} -->
+<!-- knitr::include_graphics(path = "figures/1centroids.png") -->
+<!-- ``` -->
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=14cm]{figures/1centroids.png}
+\caption{\label{fig:centroids_plot}The geographic shapes of the Statistical Areas of Tasmania at Level 2. The points show the locations of the centroids of the SA2 areas.}
+\end{figure}
 
@@
 
-The grid of possible hexagon locations is made using the \code{create_grid} function.
+The grid of possible hexagon locations is made using the `create_grid` function.
 It uses the centroids, the hexagon size and the buffer distance.
@@
 
-###### Step 1: Creating a tesselated grid
+###### Step 1: Creating a tessellated grid
 
-A set of longitude columns, and latitude rows are created to define the locations of the hexagons. The distance between each row and column is the size specified by \code{hex_size}.
+A set of longitude columns, and latitude rows are created to define the locations of the hexagons. The distance between each row and column is the size specified by `hex_size`.
 Equally spaced columns are created from the minimum longitude minus the buffer distance, up to the maximum longitude plus the buffer distance.
@@
 
-```{r grid2, fig.cap = "Grid points to create a tile map.", out.width = "100%", echo = FALSE}
-knitr::include_graphics(path = "figures/2grid.png")
-```
+<!-- ```{r grid2, fig.cap = "Grid points to create a tile map.", out.width = "100%", echo = FALSE} -->
+<!-- knitr::include_graphics(path = "figures/2grid.png") -->
+<!-- ``` -->
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=14cm]{figures/2grid.png}
+\caption{\label{fig:grid2}Grid points to create a tile map.}
+\end{figure}
 
@@
 Not all of the grid points will be used, especially if islands result in a large grid space.
-To filter the grid for appropriate hexagon locations for allocation, the \code{create_buffer} function is used by \code{create_grid}.
+To filter the grid for appropriate hexagon locations for allocation, the `create_buffer` function is used by `create_grid`.
 It finds the grid points needed to best capture the set of centroids on a hexagon tile map.
@@
 The amount of rows in each latitude group and the amount of columns in each longitude group are used as the width of rolling windows.
-The rolling windows can be seen on the bottom and right of the gris shown in Fig.
-\ref{fig:filter_grid}.
+The rolling windows can be seen on the bottom and right of the grid shown in Fig.
+\ref{fig:filter-grid}.
 This will tailor the available grid points to those most likely to be used.
@@
 
-```{r filter_grid, fig.cap = "All possible hexagon locations from the initial grid are shown with blue outlines.
+<!-- ```{r filter-grid, fig.cap = "All possible hexagon locations from the initial grid are shown with blue outlines.
 The blue dots show the grid points left to choose from after the buffer step.
-The rolling windows show the collections of rows and columns used to filter the hexagon locations.", echo = FALSE, out.width = "100%"}
-knitr::include_graphics(path = "figures/3grid.png", dpi = 300)
-```
+The rolling windows show the collections of rows and columns used to filter the hexagon locations.", echo = FALSE, out.width = "100%"} -->
+<!-- knitr::include_graphics(path = "figures/3grid.png", dpi = 300) -->
+<!-- ``` -->
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=8cm]{figures/3grid.png}
+\caption{\label{fig:filter-grid}All possible hexagon locations from the initial grid are shown with blue outlines.
+The blue dots show the grid points left to choose from after the buffer step.
+The rolling windows show the collections of rows and columns used to filter the hexagon locations.}
+\end{figure}
 
@@
 
-The possible hexagon locations to consider for a centroid are determined by the \code{hex_filter}.
+The possible hexagon locations to consider for a centroid are determined by the `hex_filter`.
 This is the maximum amount of hexagons between the centroid and the furthest considered hexagon.
@@
 
-```{r buffers, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, out.width = "100%"}
-knitr::include_graphics(path = "figures/4grid.png")
-```
+<!-- ```{r buffers, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, out.width = "100%"} -->
+<!-- knitr::include_graphics(path = "figures/4grid.png") -->
+<!-- ``` -->
 
-The \code{width} parameter is used to take a slice of the remaining points.
+\begin{figure}[H]
+\centering
+\includegraphics[width=14cm]{figures/4grid.png}
+\caption{\label{fig:buffers}Filter for grid points within a square, then circular, distance for those closest to the centroid.}
+\end{figure}
+
+The `width` parameter is used to take a slice of the remaining points.
 The width is the amount of degrees used on either side of the angle from the focal point to centroid location.
@@
 
-```{r angles, fig.cap = "Filter for grid points within the angle from the focal point to the centroid.", echo = FALSE, out.width = "100%"}
-knitr::include_graphics(path = "figures/5allocate.png")
-```
+<!-- ```{r angles, fig.cap = "Filter for grid points within the angle from the focal point to the centroid.", echo = FALSE, out.width = "100%"} -->
+<!-- knitr::include_graphics(path = "figures/5allocate.png") -->
+<!-- ``` -->
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=14cm]{figures/5allocate.png}
+\caption{\label{fig:angles}Filter for grid points within the angle from the focal point to the centroid.}
+\end{figure}
 
@@
 By default the angle filter to hexagon grid points that fall within the bounds of the angle from the focal point to the geographic centroid, plus and minus 30 degrees.
-This will increase if no points can be found within the \code{hex_filter} distance.
+This will increase if no points can be found within the `hex_filter` distance.
 The default angle of 30 was chosen to allow the algorithm to choose hexagons that best maintained the spatial relationship between the focal point and geographic centroid.
 
-```{r buffs, fig.cap = "A complete hexagon tile map of Tasmania.", out.width = "100%", echo = FALSE}
-knitr::include_graphics(path = "figures/6allocate.png")
-```
+<!-- ```{r buffs, fig.cap = "A complete hexagon tile map of Tasmania.", out.width = "100%", echo = FALSE} -->
+<!-- knitr::include_graphics(path = "figures/6allocate.png") -->
+<!-- ``` -->
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=14cm]{figures/6allocate.png}
+\caption{\label{fig:buffs}A complete hexagon tile map of Tasmania.}
+\end{figure}
 
@@
 
-```{r sir, out.width = "100%", echo = FALSE, fig.cap = "The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2.
-A choropleth map (a) of Standardised Incidence Rates (SIRs) is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented."}
-knitr::include_graphics(path = "figures/7SIR.png")
-```
+<!-- ```{r sir, out.width = "100%", echo = FALSE, fig.cap = "The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2.
+A choropleth map (a) of Standardised Incidence Rates (SIRs) is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented."} -->
+<!-- knitr::include_graphics(path = "figures/7SIR.png") -->
+<!-- ``` -->
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=14cm]{figures/7SIR.png}
+\caption{\label{fig:sir}The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2.
+A choropleth map (a) of SIR is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented.}
+\end{figure}
 
@@
 
-An additional step can be included to allow the neighbours that have alredy been allocated to influence the placement of the current centroid. 
-This requires specifying the \code{sf} object as the argument for the \code{use_neighbours} parameter.
+An additional step can be included to allow the neighbours that have already been allocated to influence the placement of the current centroid. 
+This requires specifying the `sf` object as the argument for the `use_neighbours` parameter.
 This calculates neighbours using intersections of their polygons.
@@
 ## Prepare to plot
-fort_hex <- fortify_hexagon(data = hex_allocated, sf_id = "SA2_NAME16", hex_size = 0.2)
+fort_hex <- fortify_hexagon(data = hex_allocated,
+  sf_id = "SA2_NAME16", hex_size = 0.2)
 
@@
 
-The Australian Cancer Atlas [@TACA] allows estimates derived from the models of Standardised Incidence Rates and excess deaths to be downloaded. 
-Figure \ref{fig:melanoma-geo} is a choropleth map that uses colour to display the estimated Standardised Incidence Rate of melanoma cancer for all persons for each SA2.
+The Australian Cancer Atlas [@TACA] allows estimates derived from the models of SIRs and excess deaths to be downloaded. 
+Figure \ref{fig:melanoma-geo} is a choropleth map that uses colour to display the estimated SIRs of melanoma cancer for all persons for each SA2.
 The Australian choropleth map display draws attention to the expanse of light blue areas across the rural communities in all states.
@@
 With careful consideration of the choropleth map, the small geographic inner city areas may have been noticed by viewers, but the hexagon tile map display emphasises them.
-The communities in northern Queensland and the Northern territory do not draw attention because of their size as in the choropleth, but their colour is still noticably below average when contrasted with the heaxgons further south.
+The communities in northern Queensland and the Northern territory do not draw attention because of their size as in the choropleth, but their colour is still noticeably below average when contrasted with the hexagons further south.
 
-To create this choropleth map the SA2 polygons for 2011 from the ABS. The Standardised Incidence Ratios for each geographic unit are joined to the appropriate polygons.
+To create this choropleth map the SA2 polygons for 2011 from the ABS. The SIRs for each geographic unit are joined to the appropriate polygons.
 
-```{r melanoma-geo, fig.cap = "A choropleth map of the Statistical Areas of Australia at Level 2.
-The colours communicate the value of the estimated Standardised Incidence Rate of Melanoma for all persons, they range from much lower than average (blue) to much higher than average (red)", results = "asis", echo = FALSE, out.width = "60%"}
-knitr::include_graphics("figures/aus_melanoma_p.png")
-```
+<!-- ```{r melanoma-geo, fig.cap = "A choropleth map of the Statistical Areas of Australia at Level 2.
+The colours communicate the value of the estimated Standardised Incidence Rate of Melanoma for all persons, they range from much lower than average (blue) to much higher than average (red)", results = "asis", echo = FALSE, out.width = "60%"} -->
+<!-- knitr::include_graphics("figures/aus_melanoma_p.png") -->
+<!-- ``` -->
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=14cm]{figures/aus_melanoma_p.pdf}
+\caption{\label{fig:melanoma-geo}A choropleth map of the Statistical Areas of Australia at Level 2.
+The colours communicate the value of the estimated SIR of Melanoma for all persons, they range from much lower than average (blue) to much higher than average (red)}
+\end{figure}
 
@@
 
-```{r melanoma-hex, fig.cap = "A hexagon tile map of the Statistical Areas of Australia at Level 2.
-The colours communicate the value of the estimated Standardised Incidence Rate, they range from much lower than average (blue) to much higher than average (red)", results = "asis", echo = FALSE, out.width = "60%"}
-knitr::include_graphics("figures/aus_melanoma_p_hex.png")
-```
+<!-- ```{r melanoma-hex, fig.cap = "A hexagon tile map of the Statistical Areas of Australia at Level 2.
+The colours communicate the value of the estimated Standardised Incidence Rate, they range from much lower than average (blue) to much higher than average (red)", results = "asis", echo = FALSE, out.width = "60%"} -->
+<!-- knitr::include_graphics("figures/aus_melanoma_p_hex.png") -->
+<!-- ``` -->
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=14cm]{figures/aus_melanoma_p_hex.pdf}
+\caption{\label{fig:melanoma-hex}A hexagon tile map of the Statistical Areas of Australia at Level 2.
+The colours communicate the value of the estimated SIR, they range from much lower than average (blue) to much higher than average (red)}
+\end{figure}
 
@@
 
-The \pkg{gganimate} package can be used to make an animation.
-It requires connecting the polygons for each area in two displays, which can be done using the \code{sf_id} variable, such as the SA2 name.
+The `gganimate` [@gganimate] package can be used to make an animation.
+It requires connecting the polygons for each area in two displays, which can be done using the `sf_id` variable, such as the SA2 name.
 The animation^[This animation can be viewed at: https://sugarbagjss.netlify.com/] connecting these two displays will highlight the rapid growth of the inner-city areas, and will decrease the large rural areas.
@@
 The solution to this visualisation problem has equally sized areas, with neighbourhood boundary connections.
-This map algorithm is implemented in the \pkg{sugarbag} @sugarbag package written for \code{R} @R.
-The \pkg{sugarbag} package creates tesselated hexagon tile maps.
+This map algorithm is implemented in the `sugarbag` [@sugarbag] package written for `R` [@R].
+The `sugarbag` package creates tessellated hexagon tile maps.
 The Australian application preserves the spatial relationships, emphasising capital cities.
@@
 
-These hexagons equally represent each area. However, the tesselation does not allow the size of the hexagons to represent another variable, similar to the choropleth maps.
+These hexagons equally represent each area. However, the tessellation does not allow the size of the hexagons to represent another variable, similar to the choropleth maps.
 The algorithm is heavily dependent on the focal points used, as this determines the order of allocation.
@@
 This algorithm has only been tested using single countries, and does not consider definite borders of countries.
-While the buffer allows extention beyond the furthest centroids, there is no mechanism to protect the borders and ensure centroids are placed within the geographic borders of a country.
+While the buffer allows extension beyond the furthest centroids, there is no mechanism to protect the borders and ensure centroids are placed within the geographic borders of a country.
 
 This algorithm is an effective start to creating hexagon tile maps for many geographic units.
-
-## Acknowledgements
-
-The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations.
-They would also like to thank Professor Kerrie Mengersen for suggestions and comments.
-Mitchell O'Hara-Wild provided assistance with some parts of the algorithm and code.
-Sayani Gupta provided helpful advice on parts of this paper.
-
-The code for \pkg{sugarbag} [@sugarbag] can be found on [CRAN](https://cran.r-project.org/web/packages/sugarbag/index.html), along with vignettes on installation and usage.

### 2020-02-14 paper_distill.Rmd
distill format

--- 2020-01-18 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
@@
 ---
-documentclass: jss
+date: "`r Sys.Date()`"
+output: 
+  distill::distill_article:
+    fig_caption: true
+    citation_package: natbib
+    link-citations: true
 author:
@@
     email: \email{dicook@monash.edu}
-  - name: Earl Duncan
-    affiliation: Queensland University of Technology
-    address: >
-      School of Mathematical Sciences,
-      Science and Engineering Faculty,
-      Brisbane, QLD, Australia
-    email: \email{earl.duncan@qut.edu.au}
-title: 
-  formatted: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map, \n With Application to Australian Maps"
-  plain: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With Application to Australian Maps"
-  short: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map"  
-abstract: >
+title: An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With Application to Australian Maps
+description: >
   This algorithm creates a tesselated hexagon display to represent each of the spatial polygons.
@@
   \usepackage{amsmath}
-biblio-style: jss
-output:
-  rticles::jss_article:
-    fig_caption: true
-    citation_package: natbib
 bibliography: sugarbag.bib
-link-citations: true
 ---
-
-\setcounter{page}{65}
 
@@
 These displays result in a distortion of the map space to represent differences in the statistic across the areas \citep{ACCAC}.
-The statistic of interest is used to determine the cartogram layout. When the
-Australian population is the statistic of interest, the result is a population cartogram.
+The statistic of interest is used to determine the cartogram layout, Cheng [@IVMVTSAD] reviews these methods discusses the shape errors that occurs when creating cartgorams.
+When the Australian population is the statistic of interest, the result is a population cartogram.
 They fail to preserve a recognisable display due to the difference in size of metropolitan and rural areas \citep{ACTUC}, \citep{GOINO}.
@@
 
-tile maps, Rectangular cartograms \citep{ORC} and Dorling cartograms \citep{ACTUC}, all use one simple shape to represent each area.
+Tile maps, Rectangular cartograms \citep{ORC} and Dorling cartograms \citep{ACTUC}, all use one simple shape to represent each area.
 They place various importance on the preservation of spatial relationships, but all decrease the emphasis on the size of the geographic areas.
@@
 
-```{r centroids_plot, out.width = "100%", echo = FALSE, eval = FALSE, fig.cap = "The geographic shapes of the Statistical Areas of Tasmania at Level 2.
-The points show the locations of the centroids of the SA2 areas."}
-knitr::include_graphics(path = "figures/1centroids.png")
+```{r algorithm, out.width = "100%", echo = FALSE, fig.cap = "The grid of points used to create a hexagon tile map for the Australian state of Tasmania, at each step in the sugarbag algorithm.
+The steps in the create a hexagon tile map from the centroids of geographic shapes of the Statistical Areas of Tasmania at Level 2.
+The green points show the locations of the centroids of the SA2 areas.
+The blue dots show the grid points available for allocation at each buffer step.", fig.height = 12, fig.width = 9}
+knitr::include_graphics(path = "figures/filter.png")
 ```
@@
 A unique hexagon location is created from all intersections of the longitude columns and latitude rows.
-Figure \ref{fig:grid2} shows the original grid on the left, to allow for tessellating hexagons, every second latitude row on the grid is shifted right, by half of the hexagon size.
-The grid for tessellation is shown on the right.
+Figure \ref{fig:algorithm}a shows the original grid on the left, to allow for tessellating hexagons, every second latitude row on the grid is shifted right, by half of the hexagon size.
+The grid for tessellation is shown on the right in Figure \ref{fig:algorithm}b.
 
-```{r grid2, fig.cap = "Grid points to create a tile map.", out.width = "100%", echo = FALSE}
-knitr::include_graphics(path = "figures/2grid.png")
-```
+<!-- ```{r grid2, fig.cap = "Grid points to create a tile map.", out.width = "100%", echo = FALSE} -->
+<!-- knitr::include_graphics(path = "figures/2grid.png") -->
+<!-- ``` -->
 
@@
 
-```{r filter_grid, fig.cap = "All possible hexagon locations from the initial grid are shown with blue outlines.
+<!-- ```{r filter_grid, fig.cap = "All possible hexagon locations from the initial grid are shown with blue outlines.
 The blue dots show the grid points left to choose from after the buffer step.
-The rolling windows show the collections of rows and columns used to filter the hexagon locations.", echo = FALSE, out.width = "100%"}
-knitr::include_graphics(path = "figures/3grid.png", dpi = 300)
-```
+The rolling windows show the collections of rows and columns used to filter the hexagon locations.", echo = FALSE, out.width = "100%"} -->
+<!-- knitr::include_graphics(path = "figures/3grid.png", dpi = 300) -->
+<!-- ``` -->
 
@@
 
-```{r buffers, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, out.width = "100%"}
-knitr::include_graphics(path = "figures/4grid.png")
-```
+<!-- ```{r buffers, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, out.width = "100%"} -->
+<!-- knitr::include_graphics(path = "figures/4grid.png") -->
+<!-- ``` -->
 
@@
 The width is the amount of degrees used on either side of the angle from the focal point to centroid location.
-This uses the angle from the closest capital city, to the current centroid as seen in Figure \ref{fig:angles} .
+This uses the angle from the closest capital city, to the current centroid as seen in Figure \ref{fig:algorithm}c and \ref{fig:algorithm}d.
 This allows the spatial relationship to be preserved, even when it is allocated to a hexagon that is further from the focal point then the original centroid location.
 
-```{r angles, fig.cap = "Filter for grid points within the angle from the focal point to the centroid.", echo = FALSE, out.width = "100%"}
-knitr::include_graphics(path = "figures/5allocate.png")
-```
+<!-- ```{r angles, fig.cap = "Filter for grid points within the angle from the focal point to the centroid.", echo = FALSE, out.width = "100%"} -->
+<!-- knitr::include_graphics(path = "figures/5allocate.png") -->
+<!-- ``` -->
 

### 2020-02-14 paper_distill.R

@@ -1,0 +1,481 @@
+
+###########################################################
+## LIBRARIES
+## sugarbag to create tesellated hexagon map
+## tidyverse for tidy data manipulation, not necessary
+
+library(sugarbag)
+library(dplyr)
+library(ggplot2)
+library(gridExtra)
+library(purrr)
+library(sf)
+library(readr)
+
+###########################################################
+## DATA
+## load data files from sugarbag
+data(capital_cities)
+
+sa2 <- absmapsdata::sa22011  %>% 
+  filter(state_name_2011 == "Tasmania")
+
+# Join with cancer data from Australian Cancer Atlas
+aus_colours <- function(sir_p50){
+  value <- case_when(
+    sir_p50 < 0.5 ~ "#33809d",
+    sir_p50 >= 0.5 & sir_p50 < 0.75 ~ "#aec6c7",
+    sir_p50 >= 0.75 & sir_p50 < 1.5 ~ "#fff4bc",
+    sir_p50 >= 1.25 & sir_p50 < 1.5 ~ "#ff9a64",
+    sir_p50 >= 1.5 ~ "#ff3500",
+    TRUE ~ "#FFFFFF")
+  return(value)
+}
+
+SIR <- read_csv("kobakian_sugarbag_jss/data/SIR Downloadable Data.csv") %>% 
+  dplyr::select(Cancer_name, SA2_name, Sex_name, p50) %>% 
+  filter(Cancer_name == "Lung", Sex_name == "Males") %>% 
+  filter(SA2_name %in% sa2$sa2_name_2011) %>% 
+  mutate(SIR = map_chr(p50, aus_colours)) 
+
+# No data for "Mount Wellington", "Wilderness - East", "Wilderness - West" 
+###########################################################
+## CENTROIDS
+## Use the create_centroids function to find polygon centroids:
+centroids <- create_centroids(shp_sf = sa2, sf_id = "sa2_name_2011")
+
+## Join the data from the original data set to the set of centroids by sf_id
+centroids <- left_join(centroids,
+  sf::st_drop_geometry(sa2), by = "sa2_name_2011")
+
+###########################################################
+## CENTROID PLOTS
+## Fortify the underlying geographical areas for plotting
+fort_sa2 <- fortify_sfc(sa2)
+
+cents <- ggplot() + 
[…]

### 2020-02-14 paper_distill.Rmd
title and abstract

@@
     email: \email{dicook@monash.edu}
-title: An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With Application to Australian Maps
+title: "sugarbag: An Algorithm for Transforming Spatial Polygons into a Hexagon Tile Map, Implemented in R"
 description: >
-  This algorithm creates a tesselated hexagon display to represent each of the spatial polygons.
-It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units.
-It showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps.
-Spatial distributions have been presented on alternative representations of geography for many years.
-In modern times, interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption.
-Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
+  Maps of geographic areas are constructed from a set of spatial polygons.
+These are commonly used to create a choropleth map, where polygons are colored to indicate the value of some variable of interest.
+Information on small areas can get lost on the map, and a solution is to tesselate hexagons so that all areas are equal size.
+This paper describes a new algorithm to automatically construct a spatial layout of tesselated hexagons, where the hexagons don't need to  be contiguous.
+The result is called a hexagoon tile map, and the implementation is available in the R package, sugarbag.
+Applications of choropleth and hence HTM: atlases, ..
 keywords:
@@
 ---
+
+<!-- This algorithm creates a hexagon tile map to represent a set of spatial polygons.
+It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units.
+It showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps.
+Spatial distributions have been presented on alternative representations of geography for many years.
+In modern times, interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption.
+Applications are increasingly widespread, especially in the areas of disease mapping, and election results.-->
 

### 2020-07-20 UK areas.Rmd
Hexagon tile map of the United Kingdom

---
title: "UK"
author: "Stephanie"
date: "18/07/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sf)
library(ggplot2)
library(sugarbag)
```

```{r}
uk <- st_read("data/Westminster_Parliamentary_Constituencies__December_2017__Boundaries_UK.shp") %>% st_transform(crs = "+proj=longlat +datum=WGS84 +no_defs")
ggplot(uk) + geom_sf()
```
```{r, dpi = 300}
uk_cities <- tibble(
  cities = c("London", "Edinburgh", "Cardiff", "Belfast"), 
  longitude = c(51.50853, 55.95206, 51.48, 54.58333), 
  latitude = c(-0.12574, -3.19648, -3.18, -5.93333))

#uk_hexmap <- create_hexmap(
#  shp = uk,
#  sf_id = "pcon17nm",
#  hex_size = 0.12,
#  focal_points = uk_cities,
#  verbose = TRUE)

#save(uk_hexmap, file = "data/uk_hexmap.rda")
load("data/uk_hexmap.rda")

fort_hexagon <- uk_hexmap %>% 
  fortify_hexagon("pcon17nm", hex_size = 0.12)
fort_uk <- uk %>% select(-long, -lat) %>% fortify_sfc()

ukhexmap <- ggplot() + 
  geom_polygon(aes(x = long, y = lat, group = interaction(pcon17nm,polygon)), fill = "white", colour = "lightgrey", data = fort_uk) +
  geom_polygon(aes(x = long, y = lat, group = pcon17nm), fill = "grey", colour = "black",  data = fort_hexagon) +
  coord_equal() + theme_void()

ggsave(plot = ukhexmap, filename = "ukhexmap.png", device = "png", dpi = 300)

```

### 2020-07-20 kobakian_sugarbag_jss/kobakian_sugarbag_jss.tex

@@
 \hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\subsection{Introduction}\label{introduction}}
 
@@
 \hypertarget{algorithm}{%
-\section{Algorithm}\label{algorithm}}
+\subsection{Algorithm}\label{algorithm}}
 
@@
 \hypertarget{parameters}{%
-\subsection{Parameters}\label{parameters}}
+\paragraph{Parameters}\label{parameters}}
 
@@
 \hypertarget{polygon-set}{%
-\subsection{Polygon set}\label{polygon-set}}
+\paragraph{Polygon set}\label{polygon-set}}
 
@@
 \hypertarget{create-the-set-of-centroid-points}{%
-\subsection{Create the set of centroid
+\paragraph{Create the set of centroid
 points}\label{create-the-set-of-centroid-points}}
@@
 \hypertarget{create-the-hexagon-grid-points}{%
-\subsection{Create the hexagon grid
+\paragraph{Create the hexagon grid
 points}\label{create-the-hexagon-grid-points}}
@@
 
-\hypertarget{step-1-creating-a-tesselated-grid}{%
-\subsubsection{Step 1: Creating a tesselated
-grid}\label{step-1-creating-a-tesselated-grid}}
+Step 1: Creating a tesselated grid
 
@@
 
-\hypertarget{step-2-rolling-windows}{%
-\subsubsection{Step 2: Rolling windows}\label{step-2-rolling-windows}}
+Step 2: Rolling windows
 
@@
 
-\hypertarget{step-3-filtering-the-grid}{%
-\subsubsection{Step 3: Filtering the
-grid}\label{step-3-filtering-the-grid}}
+Step 3: Filtering the grid
 
@@
 \hypertarget{centroid-to-focal-point-distance}{%
-\subsection{Centroid to focal point
+\paragraph{Centroid to focal point
 distance}\label{centroid-to-focal-point-distance}}
@@
 \hypertarget{allocate-each-centroid-to-a-hexagon-grid-point}{%
-\subsection{Allocate each centroid to a hexagon grid
+\paragraph{Allocate each centroid to a hexagon grid
 point}\label{allocate-each-centroid-to-a-hexagon-grid-point}}
@@
 R>   hex_grid = grid,
-R>   hex_size = 0.2, # same size used in create_grid
+R>   hex_size = 0.2, ## same size used in create_grid
 R>   hex_filter = 10,
@@
 
-\hypertarget{step-1-filter-the-grid-for-unassigned-hexagon-points}{%
-\subsubsection{Step 1: Filter the grid for unassigned hexagon
-points}\label{step-1-filter-the-grid-for-unassigned-hexagon-points}}
+Step 1: Filter the grid for unassigned hexagon points
 
@@
 
-\hypertarget{step-2-filter-the-grid-points-for-those-closest-to-the-centroid}{%
-\subsubsection{Step 2: Filter the grid points for those closest to the
-centroid}\label{step-2-filter-the-grid-points-for-those-closest-to-the-centroid}}
+Step 2: Filter the grid points for those closest to the centroid
 
@@
 \hypertarget{neighbour-relationships}{%
-\subsection{Neighbour relationships}\label{neighbour-relationships}}
+\paragraph{Neighbour relationships}\label{neighbour-relationships}}
 
@@
 \hypertarget{using-sugarbag}{%
-\section{Using sugarbag}\label{using-sugarbag}}
+\subsection{Using sugarbag}\label{using-sugarbag}}
 
 \hypertarget{installation}{%
-\subsection{Installation}\label{installation}}
+\paragraph{Installation}\label{installation}}
 
@@
 \hypertarget{creating-a-hexagon-tile-map}{%
-\subsection{Creating a hexagon tile
+\paragraph{Creating a hexagon tile
 map}\label{creating-a-hexagon-tile-map}}
@@
 \begin{CodeInput}
-R> # Load data
+R> ## Load data
 R> data(tas_sa2)
 R> 
-R> # Create centroids set
+R> ## Create centroids set
 R> centroids <- create_centroids(tas_sa2, "SA2_NAME16")
 R> 
-R> # Create hexagon grid
+R> ## Create hexagon grid
 R> grid <- create_grid(centroids = centroids,
@@
 R> 
-R> # Allocate polygon centroids to hexagon grid points
+R> ## Allocate polygon centroids to hexagon grid points
 R> hex_allocated <- allocate(
@@
 R>   sf_id = "SA2_NAME16",
-R>   # same column used in create_centroids
+R>   ## same column used in create_centroids
 R>   hex_size = 0.2,
-R>   # same size used in create_grid
+R>   ## same size used in create_grid
 R>   hex_filter = 10,
@@
 R> 
-R> # Prepare to plot
+R> ## Prepare to plot
 R> fort_hex <- fortify_hexagon(data = hex_allocated, sf_id = "SA2_NAME16", hex_size = 0.2)
 R> 
-R> # Make a plot
+R> ## Make a plot
 R> library(ggplot2)
@@
 \hypertarget{applications}{%
-\section{Applications}\label{applications}}
+\subsection{Applications}\label{applications}}
 
 \hypertarget{australian-cancer-atlas}{%
-\subsection{Australian Cancer Atlas}\label{australian-cancer-atlas}}
+\paragraph{Australian Cancer Atlas}\label{australian-cancer-atlas}}
 
@@
 \hypertarget{animation}{%
-\section{Animation}\label{animation}}
+\subsection{Animation}\label{animation}}
 
@@
 \hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
+\subsection{Conclusion}\label{conclusion}}
 
@@
 \hypertarget{acknowledgements}{%
-\section{Acknowledgements}\label{acknowledgements}}
+\subsection{Acknowledgements}\label{acknowledgements}}
 

### 2020-09-28 UK/UK areas.Rmd
clean up for journal submission

--- 2020-07-20 UK areas.Rmd
@@
 ```{r}
-uk <- st_read("data/Westminster_Parliamentary_Constituencies__December_2017__Boundaries_UK.shp") %>% st_transform(crs = "+proj=longlat +datum=WGS84 +no_defs")
+uk <- st_read("data/Westminster_Parliamentary_Constituencies__December_2017__Boundaries_UK.shp") %>% 
+  st_transform(crs = "+proj=longlat +datum=WGS84 +no_defs")
 ggplot(uk) + geom_sf()
@@
 
-#uk_hexmap <- create_hexmap(
-#  shp = uk,
-#  sf_id = "pcon17nm",
-#  hex_size = 0.12,
-#  focal_points = uk_cities,
-#  verbose = TRUE)
+uk_hexmap <- create_hexmap(
+  shp = uk,
+  sf_id = "pcon17nm",
+  hex_size = 0.12,
+  focal_points = uk_cities,
+  verbose = TRUE)
 
@@
 ggsave(plot = ukhexmap, filename = "ukhexmap.png", device = "png", dpi = 300)
-
 ```

### 2020-09-28 algorithm.Rmd
clean up for journal submission

---
title: A Hexagon Tile Map Algorithm For Spatial Mapping To Create Alternative Australian Maps
author:
  # see ?rjournal_article for more information
  - name: Stephanie Kobakian
    affiliation: Monash University
    address:
    - Department of Econometrics and Business Statistics
    email:  stephanie.kobakian@monash.edu 
  - name: Dianne Cook
    affiliation: Monash University
    address:
    - Department of Econometrics and Business Statistics
    email:  dicook@monash.edu 
abstract: >
  This algorithm creates a tessellated hexagon display to represent a set of the spatial polygons. It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units. The algorithm creates a display that showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps. Spatial distributions have been presented on alternative representations of geography for many years. In modern times, interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption. Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
preamble: |
  % Any extra LaTeX you need in the preamble
bibliography: sugarbag.bib
output: rticles::rjournal_article
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE, comment = FALSE}
library(knitcitations)
library(RefManageR)
library(sf)
library(sugarbag)
library(kableExtra)

knitr::opts_chunk$set(warning = FALSE, message = FALSE)
options("citation_format" = "pandoc")
BibOptions(check.entries = FALSE, style = "markdown")
```

## Introduction

<!-- Motivation to map -->
Many cancer atlases present geospatial cancer data on a choropleth map display.
The Australian Cancer Atlas [@TACA] is a recent addition to the many cancer atlas maps worldwide. The ground-breaking atlas for Australia presents a central map that shows the landmass overlaid with administrative boundaries. This choropleth display can highlight the geographic patterns in geospatially related cancer statistics [@SAMGIS].

<!-- Issues with choropleth map displays... -->
In many countries, residents are increasingly gathering to live in urban areas around major cities [@ACTUC].
The creation of approximately equal population areas results in dramatically different square meterage of the geographic units. The geographic units are usually administrative, such as states or electorates. The units are filled with colour to represent the value of the statistic for each unit [@EI].
This can lead to unequal emphasis on the statistical value of each of the geographic units. This allows choropleth map displays to misrepresent the spatial distributions of human related statistics due to area-size bias [@BCM].
Figure \ref{fig:melanoma-geo} is a choropleth map that uses colour to display the estimated Standardised Incidence Ratios (SIRs) of melanoma cancer for males for each of the Statistical Areas at Level 2 (SA2) used by the Australian Bureau of Statistics [-@abs2011]. The Australian choropleth map display draws attention to the expanse of light blue areas across the rural communities in all states. The SA2s around Brisbane stand out as more orange and red. To create this choropleth map the SA2 polygons for 2011 from the Australian Bureau of Statistics.

<!-- solutions -->
The solutions to this visualisation problem begin with the geography. Alternative maps shift the focus from land area and shape, to the value of the statistics in a group of areas [@ACCAC]. Different styles of cartograms apply transformations to the geographic areas, to highlight the values of the value of the statistic of interest. These displays result in a distortion of the map space to represent differences in the statistic across the areas [@ACCAC] as the statistic of interest is used to determine the cartogram layout.

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figures/aus_melanoma_p.pdf}
\caption{\label{fig:melanoma-geo}A choropleth map of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated SIR of Melanoma for males, they range from much lower than average (blue) to much higher than average (red)}
\end{figure}

Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing the population in each administrative area [@TAAM]. This acknowledges that the number of residents can be different but recognises that each area, or person within it is equally important.

This paper contains a discussion of Existing Mapping Practices in Section 2. This is followed by details of the Algorithm in Section 3. Section 4 describes the implementation of the algorithm in the `sugarbag` package. Section 5 outlines the use and benefits of animation.

## Existing Mapping Practices

There are several established alternative visualisation methods. 
Tile maps, Rectangular cartograms [@ORC] and Dorling cartograms [@ACTUC] all use one simple shape to represent each geographic unit. They all minimise the emphasis on the size or shape of the geographic areas. These alternative map displays focus on the relationship between neighbours, attempting to preserve connections, and disregard the unique shapes of the administrative boundaries. Figure \ref{fig:qld_grid} shows a collection of alternative map displays, this includes a) a contiguous cartogram, b) a non-contiguous cartogram, c) a Dorling cartogram and d) a hexagon tile map. 
Each Statistical Area at Level 2 (SA2) [@abs2011] was designed to represent a community. These administrative areas are often used to aggregate census data and used to understand demographics of the Australian population.

<!-- choropleth -->
The familiar choropleth map display is often used to allow the user to orient themselves. However, the emphasis on the land mass diminishes the features of the distribution in densely populated communities due to the small size on the display [@ACTUC].
The unique shapes of boundaries can be helpful for orienting users but may not contribute to their understanding of the spatial disease distribution as many of the communities are not visible in a choropleth display [@TVSSS]. This presents an opportunity for explicit map transformations to improve communication of distributions [@CBATCC]. In figure \ref{fig:qld_grid}a) the choropleth map is presented with the alternative maps to allow for comparisons to be made.

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figures/qld_grid.pdf}
\caption{\label{fig:qld_grid}A collection of alternative maps of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated SIR of Melanoma for males, ranging from much lower than average (blue) to much higher than average (red)}
\end{figure}

<!-- contiguous -->
When communicating information that is relevant to the population, each member of the population can be given equal representation by transforming the map [@TVSSS].
The impact of a disease over connected communities can be seen by allowing the boundaries to maintain connection in the transformed display. The contiguous cartogram displayed in figure \ref{fig:qld_grid}b) draws attention to smaller geographic units when they are rescaled according to the population [@DMAHP]. These new shapes can now be coloured to represent a second variable. This display can create twisted and unfamiliar shapes from the geographic units as the algorithms must satisfy the topology conditions, especially when there are communities located geographically far from their neighbours [@TVSSS]. This shown in the northern SA2s of Queensland with an average (yellow) estimated SIR of Melanoma for males.

<!-- non-contiguous -->
The non-contiguous cartogram in figure \ref{fig:qld_grid}c) also uses the population to rescale the geographic units. Unlike the contiguous cartogram, the SA2 areas maintain their geographic shape, but they may not retain the connection with their neighbours. The population of the SA2 areas is used to scale the geographic units in the non-contiguous cartogram [@NAC]. The amount of white space can be meaningful in non-contiguous cartograms [@ECGC], in this example the disparity between large rural areas and small urban areas means that the city of Brisbane, shown in the inset map looks reasonable, but these units are not visible in the context of the Queensland state map. Depending on the difference between the population and geographic land size, the amount of white space can also prevent meaningful understanding of the distribution [@TVSSS].

<!-- Dorling -->
The Dorling cartogram presents each geographic unit as a circle, the size of the circle is scaled according to the population value of each area [@ACTUC]. Figure \ref{fig:qld_grid}d) shows the Queensland SA2 areas as an individual circle located as close as possible to the geographic centroid location. This map draws attention to the collection of coastal cities in Queensland that were not apparent in figure \ref{fig:qld_grid} a), b) or c).

<!-- When the population is the statistic of interest, the result is a population cartogram. They fail to preserve a recognisable display due to the difference in size of metropolitan and rural areas [@ACTUC], [@GOINO]. -->
<!-- Contiguous cartograms alter the shape of areas, while preserving boundary relationships of neighbours. Non-contiguous cartograms maintain the geographic shape of each geographic area, but will lose the connection to neighbours as the polygon for each geographic area shrinks or grows. -->

## Algorithm

The purpose of this algorithm is to create a map display that highlights the spatial distributions for populations. There has been an increasing need for displays that recognise the large number of people that live in dense urban environments. The algorithm intends to maintain the spatial relationships of a group of geographic units in two ways: between each unit and its neighbours; and between each unit and the closest focal point. The algorithm allocates geographic units to a representative hexagon, in order of their proximity to the closest focal point.

The algorithm is named for the *Trigona carbonaria* bee species. Native to northern and eastern Australia this stingless species builds flat layers of hexagonal brood cells, spiralling out from a central point [@PH]. This hive design inspired the use of multiple focal points in the algorithm, individual spirals are constructed outward from various points on the geographic map base.

There are three key steps performed to create a tessellated hexagon tile map. First create the set of centroids from the polygons to allocate, then create the grid of hexagons locations. Each centroid can then be allocated to an available hexagon location. To make tessellated plots the points can be converted to hexagon shapes, with the hexagon size equal to the size used in the grid.

\begin{figure}
\includegraphics[width=14cm]{figures/flowchart.pdf}
\caption{\label{fig:sugarbag_flow}A flow diagram detailing the necessary steps to create a hexagon tile map.}
\end{figure}

#### User choices

<!-- The`create_hexmap` function will -->
<!-- Derive the centroids of the geographic units to calculate a grid of possible hexagon locations, and allocate each geographic unit to a single hexagon. -->
Only two inputs are necessary to begin using the algorithm, the shape file, and the id variable. The id column should uniquely identify each geographic unit in the shape file.

The centroids can be derived from the shape file. The amount of centroids is used to determine a hexagon size. 
The derived centroids are a necessary input for an appropriate grid to be constructed, in which each grid point is located a hexagon size distance from the next closest point in all six directions. 
The grid will initially cover the entire map space, encompassing all the centroid locations and will extend in all directions to the extent of the buffer distance. This buffer distance can be helpful to account for densely populated coastal areas, allowing the use of the sea for hexagon locations. The hexagon size will likely need adjustments depending on the density of the population.

The centroids derived from the shape file are necessary inputs when creating a grid. The creation of the grid and filtering out the points unlikely to be used in the hexagon map results in the hexagon tile map grid. At this point, the centroid set and the grid become the necessary inputs to the allocation process.

A set of reference locations can be provided as focal points, such as capital cities of states or countries. Using focal points, the algorithm will create the order of allocation in order of the closest centroid locations to the focal points.
Alternatively, a user can specify the variable that should be used to determine the order for the allocation. 
When allocating representative hexagons, the width parameter can be used to determine the flexibility of positioning using the relationship with the nearest reference location. A larger width parameter will increase the amount of available hexagon locations nearer to the centroid of the geographic location. A smaller width will maintain the orientation from the focal point to the centroid when selecting the hexagon location, however this could mean it is placed further from the centre of the cluster.

## Implementation

<!-- Motivate the value of the the package and algorithm -->
Hexagon tile maps can be useful to understand a distribution across a collection of geographic areas. However, these maps are not easily drawn, especially as the number of areas increases. This algorithm was created to automate this process, and reduce the manual load involved in creating and implementing alternative displays. This allows map makers and data communicators to allocate their time to choosing the most effective display, rather than manually creating them.

The `sugarbag` package has been written for R software, it contains a set of functions that help R users to create a hexagon tile map.
The algorithm presented in the `sugarbag` package operates on a set of simple feature geometry objects [@sf], this package allows R users to create `sf` objects by importing polygons stored in various formats.
Users should provide a set of polygons that define geographic units by their administrative boundaries. The functions arrange the geographic units in order of proximity to a set of locations provided, such as the centre of capital cities. 
The centroid location of each geographic unit is used to measure the proximity.
It emphasises the capital cities as population hubs, rather than emphasizing the size of large, rural geographic units.

A user can tweak the parameters of the hexagon map using the additional arguments to the `create_hexmap` function, these options may affect the speed of the creation.

#### Installation

The package can be installed from CRAN:

```{r eval=FALSE}
install.packages("sugarbag")
```

and the development version can be install from the GitHub repository:

```{r eval=FALSE}
devtools::install_github("srkobakian","sugarbag")
```

Load the library into your R session with:

```{r}
library(sugarbag)
```

#### Creating a hexagon tile map

The following code creates the hexagon tile map for all the Statistical Areas at Level 2 in Queensland. These steps can be executed by the main function, `create_hexmap`, or can be implemented separately for more flexibility.

If a user would like to perform each of the steps of the algorithm themselves, the necessary inputs will change for each function.

Users may choose to only use the `allocate` function when they wish to use a set of centroids, rather than [@sf] polygons.

```{r full_hexmapcode, echo = TRUE, warning = FALSE, message = FALSE, eval=FALSE}
## Load data
qld_sa2 <- absmapsdata::sa22011 %>% 
  filter(state_name_2011 == "Queensland")

## Create centroids set
centroids <- create_centroids(qld_sa2, "sa2_name_2011")

## Create hexagon grid
grid <- create_grid(centroids = centroids,
                    hex_size = 0.12,
                    buffer_dist = 1.2)

## Allocate polygon centroids to hexagon grid points
hex_allocated <- allocate(
  centroids = centroids,
  hex_grid = grid,
  sf_id = "sa2_name_2011",
  ## same column used in create_centroids
  hex_size = 0.12,
  ## same size used in create_grid
  hex_filter = 10,
  use_neighbours = qld_sa2,
  focal_points = capital_cities %>%
    filter(points == "Brisbane"),
  width = 35,
  verbose = FALSE
)

## Prepare to plot
fort_hex <- fortify_hexagon(data = hex_allocated,
                            sf_id = "sa2_name_2011",
                            hex_size = 0.12)

fort_qld <- qld_sa2 %>%
  fortify_sfc()

## Make a plot
library(ggplot2)
qld_hexmap <- ggplot() +
  geom_polygon(aes(
      x = long,
      y = lat,
      group = interaction(sa2_name_2011, polygon)
    ),
    fill = "white",
    colour = "lightgrey",
    data = fort_qld
  ) +
  geom_polygon(aes(
    x = long,
    y = lat,
    group = hex_id,
    fill = rownumber
  ),
  data = fort_hex) +
  scale_fill_distiller("", palette = "PRGn") +
  coord_equal() + theme_void()
qld_hexmap
```

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figures/aus_gghexmap.pdf}
\caption{\label{fig:melanoma-hex}A hexagon tile map of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated SIR, they range from much lower than average (blue) to much higher than average (red)}
\end{figure}

#### Polygon set

The polygon set of Statistical Areas at Level 2 (SA2) [@abs2011] of Queensland in 2011 is provided with the `sugarbag` package as `tas_sa2`. 
A single column of the data set is used to identify the unique areas. 
In this case, the unique SA2 names for each SA2 have been used.

The longitude and latitude centre of the capital cities of Australia are used as focal points to allocate each geographic area around the closest capital city. Brisbane will be the common focal point, as this example uses only the areas in the state of Queensland.

```{r capital_cities}
data(capital_cities)
```

The buffer distance, hexagon size, hexagon amount to filter and width of angle are parameters that will be determined within `create_hexmap` if they are not provided. They are created as they are needed throughout the following example.

#### Step 1: Derive the set of centroid points

A set of centroids may be used directly. The set of polygons should be provided as an `sf` object, this is a data frame containing a `geometry` column. The `read_shape` function can assist in creating this object for use in `R`.

The centroids can be derived from the set of polygons using the `create_centroids` function:

```{r cents}
centroids <- create_centroids(shp_sf = tas_sa2, sf_id = "SA2_NAME16")
```

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figures/1centroids.pdf}
\caption{\label{fig:centroids_plot}The geographic shapes of the Statistical Areas of Queensland at Level 2. The points show the locations of the centroids of the SA2 areas.}
\end{figure}

#### Step 2: Create the hexagon grid points

A grid is created to ensure tessellation between the hexagons that represent the geographic units on a hexagon tile map.

The grid of possible hexagon locations is made using the `create_grid` function.
It uses the centroids, the hexagon size and the buffer distance.

```{r grid}
grid <- create_grid(centroids = centroids, hex_size = 0.2, buffer_dist = 1.2)
```

##### Creating a tessellated grid

A set of longitude columns, and latitude rows are created to define the locations of the hexagons. The distance between each row and column is the size specified by `hex_size`.
Equally spaced columns are created from the minimum longitude minus the buffer distance, up to the maximum longitude plus the buffer distance. Similarly, the rows are created from the latitude values and the buffer distance.
A unique hexagon location is created from all intersections of the longitude columns and latitude rows.
Figure \ref{fig:grid2} shows the original grid on the left, to allow for tessellating hexagons, every second latitude row on the grid is shifted right, by half of the hexagon size. The grid for tessellation is shown on the right.

<!-- ```{r grid2, fig.cap = "Grid points to create a tile map.", out.width = "100%", echo = FALSE} -->
<!-- knitr::include_graphics(path = "figures/2grid.pdf") -->
<!-- ``` -->

\begin{figure}[h]
\centering
\includegraphics[width=16cm]{figures/2grid.pdf}
\caption{\label{fig:grid2}Grid points to create a hexagon tile map.}
\end{figure}

##### Rolling windows

Not all of the grid points will be used, especially if islands result in a large grid space.
To filter the grid for appropriate hexagon locations for allocation, the `create_buffer` function is used by `create_grid`.
It finds the grid points needed to best capture the set of centroids on a hexagon tile map.

The closest latitude row and longitude column are found for each centroid location. Then rows and columns of centroids are divided into 20 groups.
The amount of rows in each latitude group and the amount of columns in each longitude group are used as the width of rolling windows. The rolling windows can be seen on the bottom and right of the grid shown in Figure \ref{fig:filter-grid}.
This will tailor the available grid points to those most likely to be used.
It also helps reduce the amount of time taken, as it decreases the amount of points considered for each centroid allocation.

The first rolling window function finds the minimum and maximum centroid values for the sliding window groups of longitude columns and the groups of latitude rows.

The second rolling window function finds the average of the rolling minimum and maximum centroid values, for the longitude columns and latitude rows.

##### Filtering the grid

The grid points are kept only if they fall between the rolling average of the minimum and maximum centroid values after accounting for the buffer distance, for each row and column of the grid. The sparsely populated South-West region of National Park has much fewer points available compared to the South-East region containing the city of Brisbane.

<!-- ```{r filter-grid, fig.cap = "All possible hexagon locations from the initial grid are shown with blue outlines. The blue dots show the grid points left to choose from after the buffer step. The rolling windows show the collections of rows and columns used to filter the hexagon locations.", echo = FALSE, out.width = "100%"} -->
<!-- knitr::include_graphics(path = "figures/3grid.pdf", dpi = 300) -->
<!-- ``` -->

\begin{figure}[h]
\centering
\includegraphics[width=10cm]{figures/3grid.pdf}
\caption{\label{fig:filter-grid}The remaining hexagon locations from all the possible points in the initial grid after the buffer is applied. The blue dots show the grid points left to choose from after the buffer step.}
\end{figure}

##### Centroid to focal point distance

The distance between each centroid in the set, and each of the focal points provided is calculated. The name of the closest focal point, and the distance and angle from focal point to polygon centroid is joined to polygon data set. To minimise time taken for this step only one option is provided, Queensland's capital city Brisbane.
The order for allocation is determined by the distance between the polygon centroid and it's closest focal point. The points are arranged from the centroid closest to the focal point(s), to the furthest.

#### Step 3: Allocate each centroid to a hexagon grid point

Allocation of all centroids takes place using the set of polygon centroids and the hexagon map grid. 
Centroid allocation begins with the closest centroid to a focal point.
This will preserve spatial relationships with the focal point, as the inner city areas are allocated first, they will be placed closest to the capital, and the areas that are further will then be accommodated.
The possible hexagon grid points reduces by one after each allocation, then only those that have not yet been allocated are considered.

The possible hexagon locations to consider for a centroid are determined by the `hex_filter`. This is the maximum amount of hexagons between the centroid and the furthest considered hexagon. It is used to subset possible grid points to only those surrounding the polygon centroid within an appropriate range. A smaller distance will increase speed, but can decrease accuracy when width of the angle increases.

```{r centroids, eval = FALSE}
hexmap_allocation <- allocate(
  centroids = centroids %>% select(SA2_NAME16, longitude, latitude),
  sf_id = "SA2_NAME16",
  hex_grid = grid,
  hex_size = 0.2, ## same size used in create_grid
  hex_filter = 10,
  width = 35,
  focal_points = capital_cities,
  verbose = TRUE)
```

The following example considers the first of the Statistical Areas at Level 2. 
Within the algorithm, these steps are repeated for each polygon.

##### Filter the grid for unassigned hexagon points

Keeping only the available hexagon points prevents multiple geographic units from being allocated to the same hexagon.

##### Filter the grid points for those closest to the centroid

A box of possible hexagon locations around the centroid allows only the closest points that are not yet assigned to be considered. The corners of the box may not appear square if the buffer step has already removed unnecessary points from over the ocean.

The algorithm then removes the outer corners of the square, creating a circle of points, by only keeping points within a certain radial distance around the original centroid location.

<!-- ```{r buffers, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, out.width = "100%"} -->
<!-- knitr::include_graphics(path = "figures/4grid.pdf") -->
<!-- ``` -->

\begin{figure}[h]
\centering
\includegraphics[width=16cm]{figures/4grid.pdf}
\caption{\label{fig:buffers}The remaining available hexagon locations after filtering for the grid points within a square distance, then circular around the centroid.}
\end{figure}

The `width` parameter is used to take a slice of the remaining points. The width is the amount of degrees used on either side of the angle from the focal point to centroid location. This uses the angle from the closest capital city, to the current centroid as seen in Figure \ref{fig:angles} . This allows the spatial relationship to be preserved, even when it is allocated to a hexagon that is further from the focal point then the original centroid location.

<!-- ```{r angles, fig.cap = "Filter for grid points within the angle from the focal point to the centroid.", echo = FALSE, out.width = "100%"} -->
<!-- knitr::include_graphics(path = "figures/5allocate.png") -->
<!-- ``` -->

\begin{figure}[h]
\centering
\includegraphics[width=16cm]{figures/5allocate.pdf}
\caption{\label{fig:angles}The remaining available hexagon locations after filtering for grid points within the angle from the focal point to the centroid.}
\end{figure}

If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded, only when a maximum distance is reached will the angle expand to accommodate more possible grid points.  
By default the angle filter to hexagon grid points that fall within the bounds of the angle from the focal point to the geographic centroid, plus and minus 30 degrees. This will increase if no points can be found within the `hex_filter` distance. The default angle of 30 was chosen to allow the algorithm to choose hexagons that best maintained the spatial relationship between the focal point and geographic centroid.

<!-- ```{r buffs, fig.cap = "A complete hexagon tile map of Queensland.", out.width = "100%", echo = FALSE} -->
<!-- knitr::include_graphics(path = "figures/6allocate.png") -->
<!-- ``` -->

\begin{figure}[h]
\centering
\includegraphics[width=16cm]{figures/6allocate.pdf}
\caption{\label{fig:buffs}A complete hexagon tile map of Queensland.}
\end{figure}

A complete hexagon tile map of Queensland is created by applying the algorithm steps to each centroid.
The hexagon tile map visualisation is used below to visualise the Australian Cancer Atlas data [@TACA]. Two views of the same data are produced by filling according to the Lung Cancer Standardised Incidence Rates (SIRs) downloaded from the Australian Cancer Atlas site. This small example in Figure \ref{fig:sir} shows the group of blue areas in the Brisbane CBD more prominently in the hexagon tile map (b).
The small red areas visible in the choropleth map (a) along the north coast are much larger in the hexagon tile maps. The hexagon tile map shows less yellow, this no longer overwhelms the map space with the information regarding the rural areas.

<!-- ```{r sir, out.width = "100%", echo = FALSE, fig.cap = "The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2. A choropleth map (a) of Standardised Incidence Rates (SIRs) is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented."} -->
<!-- knitr::include_graphics(path = "figures/7SIR.png") -->
<!-- ``` -->

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figures/7SIR.pdf}
\caption{\label{fig:sir}The Australian Cancer Atlas data displayed on a choropleth and hexagon tile map. The colour of each Statistical Area of Australian at Level 2 coloured by SIR. A choropleth map (a) of SIR is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented.}
\end{figure}

#### Neighbour relationships

It is possible to consider the neighbouring areas for each SA2, for stronger preservation of the spatial distribution.

An additional step can be included to allow the neighbours that have already been allocated to influence the placement of the current centroid. 
This requires specifying the `sf` object as the argument for the `use_neighbours` parameter. This calculates neighbours using intersections of their polygons. This occurs for all areas before any allocations begin.

During the allocation of each centroid, the list of neighbours is consulted. If any neighbour was already allocated, the hexagons surrounding the neighbours on the grid are prioritised. For multiple neighbours, the neighbouring hexagon grid points are aggregated and considered in order of distance from the original centroid.

## Hexagon tile map of Australia

This algorithm has been applied to the complete set of all Australian Statistical Areas at Level 2. This display highlights the density of Australian capital cities, as it draws attention to the many communities in Sydney, Melbourne and Brisbane. This display also highlights the disparity in the burden of Melanoma cancer for males in the communities of these three cities. There are several collections of red hexagons in Brisbane that draw attention and they represent the communities with much higher rates of diagnosis than the Australian average. The communities south of Brisbane show a gradient of colour as the values progress from higher than average, to much lower than average for the communities closer to the Sydney CBD. This pattern progresses into the communities with lower than average rates in Melbourne and Tasmania.

Compared to the choropleth map display, the low rates in the rural Australian communities are no longer dominating the display. The much higher than average rates in Sydney draw more attention in the hexagon tile map display unlike the red and orange areas in the city of Brisbane that draw attention in both displays.

\begin{figure}[h]
\centering
\includegraphics[width=14cm]{figures/aus_gghexmap.pdf}
\caption{\label{fig:melanoma-geo}A hexagon tile map of the Statistical Areas of Australia at Level 2. The colours communicate the value of the estimated SIR of Melanoma for males, they range from much lower than average (blue) to much higher than average (red).}
\end{figure}

## Animation

The `gganimate` [@gganimate] package can be used to make an animation.
It requires connecting the polygons for each area in two displays, which can be done using the `sf_id` variable, such as the SA2 name.
The animation^[This animation can be viewed at: https://sugarbagjss.netlify.com/] connecting these two displays will highlight the rapid growth of the inner-city areas that emphasises the density of the communities. The hexagons that move the furthest will move rapidly in the animation. The rapid decreases of the large rural areas also show how much greater the landmass of Statistical Areas can be.

## Conclusion  {#conclusion-03}

It is possible to use alternative maps to communicate spatial distributions.While a choropleth map display is the current practice spatial visualisation of geographical data. Current methods do not always work for Australia due to the large geographic space between the densely populated capital cities. The administrative boundaries may also distract from the statistics communicated using colour.

Alternative maps highlight the value of the statistics across the geographic units. Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing each administrative area. This acknowledges that the amount of residents can be different but recognises that each population area is equally important. The solution to this visualisation problem has equally sized areas, with neighbourhood boundary connections. This map algorithm is implemented in the `sugarbag` [@sugarbag] package written for `R` [@R].
The `sugarbag` package creates tessellated hexagon tile maps. The Australian application preserves the spatial relationships, emphasising capital cities. The hexagon tile map is a visualisation solution that highlights spatial distributions.

These hexagons equally represent each area. However, the tessellation does not allow the size of the hexagons to represent another variable, similar to the choropleth maps.
The algorithm is heavily dependent on the focal points used, as this determines the order of allocation. It works on the assumption that viewers can use directional relationships to identify their neighbourhoods but this can be aided by the animation.
With careful consideration of the choropleth map, the small geographic inner city areas may have been noticed by viewers, but the hexagon tile map display emphasises them. The communities in northern Queensland and the Northern territory do not draw attention because of their size as in the choropleth, but their colour is still noticeably below average when contrasted with the hexagons further south.

<!-- why hexagon tile map addresses deficiencies -->
The Dorling cartogram was the most influential in the design of the hexagon tile map.
The use of a hexagon provides a simple shape that shifts the focus of the visualisation from the shape of SA2s to the distribution effects of a disease on communities.  not impeded by the irregular and unusual shapes created by a contiguous cartogram and the immense white space created on the non-contiguous cartogram.
Hexagons can emphasise the relationship between neighbouring communities by allowing their sides to touch. The tessellation crated by adjoining hexagons for densely populated areas is helpful as it shows that most communities are not islands onto themselves, but are intrinsically connected to those around them. As seen in the Dorling cartogram in figure \ref{fig:qld_grid}c), the tessellation that allows boundary connections was not imposed for rural communities, where centroid of the geographic unit was located far from others, a feature that allows distant but dense populations of the coastal towns of Queensland to be recognised.

The choropleth map that uses the geographic shapes of areas can be seen in figure \ref{fig:melanoma-geo}.
Figure \ref{fig:melanoma-hex} displays the Australian areas with equally sized hexagons. This display allows the small and densely populated inner city areas to be easily contrasted with their neighbouring areas.

<!-- future -->
Future work will include refining the algorithm. It would be possible to take a logarithmic function rather than a direct angle to help choose a closer hexagon to the original centroid location, before increasing the width of the angle used to filter the hexagons.

This algorithm has only been tested using single countries, and does not consider definite borders of countries. While the buffer allows extension beyond the furthest centroids, there is no mechanism to protect the borders and ensure centroids are placed within the geographic borders of a country.

This algorithm is an effective start to creating hexagon tile maps for many geographic units.

### 2020-09-28 algorithm.tex
clean up for journal submission

--- 2020-09-28 algorithm.Rmd
@@
----
-title: A Hexagon Tile Map Algorithm For Spatial Mapping To Create Alternative Australian Maps
-author:
-  # see ?rjournal_article for more information
-  - name: Stephanie Kobakian
-    affiliation: Monash University
-    address:
-    - Department of Econometrics and Business Statistics
-    email:  stephanie.kobakian@monash.edu 
-  - name: Dianne Cook
-    affiliation: Monash University
-    address:
-    - Department of Econometrics and Business Statistics
-    email:  dicook@monash.edu 
-abstract: >
-  This algorithm creates a tessellated hexagon display to represent a set of the spatial polygons.
-It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units.
-The algorithm creates a display that showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps.
-Spatial distributions have been presented on alternative representations of geography for many years.
-In modern times, interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption.
-Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
-preamble: |
-  % Any extra LaTeX you need in the preamble
-bibliography: sugarbag.bib
-output: rticles::rjournal_article
----
+% !TeX root = RJwrapper.tex
+\title{A Hexagon Tile Map Algorithm For Spatial Mapping To Create Alternative
+Australian Maps}
+\author{by Stephanie Kobakian and Dianne Cook}
 
-```{r setup, echo=FALSE, message=FALSE, warning=FALSE, comment = FALSE}
-library(knitcitations)
-library(RefManageR)
-library(sf)
-library(sugarbag)
-library(kableExtra)
+\maketitle
 
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-options("citation_format" = "pandoc")
-BibOptions(check.entries = FALSE, style = "markdown")
-```
+\abstract{%
+This algorithm creates a tessellated hexagon display to represent a set
+of the spatial polygons. It allocates these hexagon in a manner that
+preserves the spatial relationship of the geographic units. The
+algorithm creates a display that showcases spatial distributions, by
+emphasising the small geographical regions that are often difficult to
+locate on geographic maps. Spatial distributions have been presented on
+alternative representations of geography for many years. In modern
+times, interactivity and animation have begun to play a larger role, as
+alternative representations have been popularised by online news sites,
+and atlas websites with a focus on public consumption. Applications are
+increasingly widespread, especially in the areas of disease mapping, and
+election results.
+}
 
-## Introduction
+\hypertarget{introduction}{%
+\subsection{Introduction}\label{introduction}}
 
-<!-- Motivation to map -->
-Many cancer atlases present geospatial cancer data on a choropleth map display.
-The Australian Cancer Atlas [@TACA] is a recent addition to the many cancer atlas maps worldwide.
-The ground-breaking atlas for Australia presents a central map that shows the landmass overlaid with administrative boundaries.
-This choropleth display can highlight the geographic patterns in geospatially related cancer statistics [@SAMGIS].
+Many cancer atlases present geospatial cancer data on a choropleth map
+display. The Australian Cancer Atlas \citep{TACA} is a recent addition
+to the many cancer atlas maps worldwide. The ground-breaking atlas for
+Australia presents a central map that shows the landmass overlaid with
+administrative boundaries. This choropleth display can highlight the
+geographic patterns in geospatially related cancer statistics
+\citep{SAMGIS}.
 
-<!-- Issues with choropleth map displays... -->
-In many countries, residents are increasingly gathering to live in urban areas around major cities [@ACTUC].
-The creation of approximately equal population areas results in dramatically different square meterage of the geographic units.
-The geographic units are usually administrative, such as states or electorates.
-The units are filled with colour to represent the value of the statistic for each unit [@EI].
-This can lead to unequal emphasis on the statistical value of each of the geographic units.
-This allows choropleth map displays to misrepresent the spatial distributions of human related statistics due to area-size bias [@BCM].
-Figure \ref{fig:melanoma-geo} is a choropleth map that uses colour to display the estimated Standardised Incidence Ratios (SIRs) of melanoma cancer for males for each of the Statistical Areas at Level 2 (SA2) used by the Australian Bureau of Statistics [-@abs2011].
-The Australian choropleth map display draws attention to the expanse of light blue areas across the rural communities in all states.
-The SA2s around Brisbane stand out as more orange and red.
-To create this choropleth map the SA2 polygons for 2011 from the Australian Bureau of Statistics.
+In many countries, residents are increasingly gathering to live in urban
+areas around major cities \citep{ACTUC}. The creation of approximately
+equal population areas results in dramatically different square meterage
+of the geographic units. The geographic units are usually
+administrative, such as states or electorates. The units are filled with
+colour to represent the value of the statistic for each unit \citep{EI}.
+This can lead to unequal emphasis on the statistical value of each of
+the geographic units. This allows choropleth map displays to
+misrepresent the spatial distributions of human related statistics due
+to area-size bias \citep{BCM}. Figure \ref{fig:melanoma-geo} is a
+choropleth map that uses colour to display the estimated Standardised
+Incidence Ratios (SIRs) of melanoma cancer for males for each of the
+Statistical Areas at Level 2 (SA2) used by the Australian Bureau of
+Statistics \citeyearpar{abs2011}. The Australian choropleth map display
+draws attention to the expanse of light blue areas across the rural
+communities in all states. The SA2s around Brisbane stand out as more
+orange and red. To create this choropleth map the SA2 polygons for 2011
+from the Australian Bureau of Statistics.
 
-<!-- solutions -->
 The solutions to this visualisation problem begin with the geography.
-Alternative maps shift the focus from land area and shape, to the value of the statistics in a group of areas [@ACCAC].
-Different styles of cartograms apply transformations to the geographic areas, to highlight the values of the value of the statistic of interest.
-These displays result in a distortion of the map space to represent differences in the statistic across the areas [@ACCAC] as the statistic of interest is used to determine the cartogram layout.
+Alternative maps shift the focus from land area and shape, to the value
+of the statistics in a group of areas \citep{ACCAC}. Different styles of
+cartograms apply transformations to the geographic areas, to highlight
+the values of the value of the statistic of interest. These displays
+result in a distortion of the map space to represent differences in the
+statistic across the areas \citep{ACCAC} as the statistic of interest is
+used to determine the cartogram layout.
 
@@
 
-Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing the population in each administrative area [@TAAM].
-This acknowledges that the number of residents can be different but recognises that each area, or person within it is equally important.
+Alternative mapping methods allow increased understanding of the spatial
+distribution of a variable across the population, by fairly representing
+the population in each administrative area \citep{TAAM}. This
+acknowledges that the number of residents can be different but
+recognises that each area, or person within it is equally important.
 
-This paper contains a discussion of Existing Mapping Practices in Section 2.
-This is followed by details of the Algorithm in Section 3.
-Section 4 describes the implementation of the algorithm in the `sugarbag` package.
-Section 5 outlines the use and benefits of animation.
+This paper contains a discussion of Existing Mapping Practices in
+Section 2. This is followed by details of the Algorithm in Section 3.
+Section 4 describes the implementation of the algorithm in the
+\texttt{sugarbag} package. Section 5 outlines the use and benefits of
+animation.
 
-## Existing Mapping Practices
+\hypertarget{existing-mapping-practices}{%
+\subsection{Existing Mapping
+Practices}\label{existing-mapping-practices}}
 
-There are several established alternative visualisation methods. 
-Tile maps, Rectangular cartograms [@ORC] and Dorling cartograms [@ACTUC] all use one simple shape to represent each geographic unit.
-They all minimise the emphasis on the size or shape of the geographic areas.
-These alternative map displays focus on the relationship between neighbours, attempting to preserve connections, and disregard the unique shapes of the administrative boundaries.
-Figure \ref{fig:qld_grid} shows a collection of alternative map displays, this includes a) a contiguous cartogram, b) a non-contiguous cartogram, c) a Dorling cartogram and d) a hexagon tile map.
-Each Statistical Area at Level 2 (SA2) [@abs2011] was designed to represent a community.
-These administrative areas are often used to aggregate census data and used to understand demographics of the Australian population.
+There are several established alternative visualisation methods. Tile
+maps, Rectangular cartograms \citep{ORC} and Dorling cartograms
+\citep{ACTUC} all use one simple shape to represent each geographic
+unit. They all minimise the emphasis on the size or shape of the
+geographic areas. These alternative map displays focus on the
+relationship between neighbours, attempting to preserve connections, and
+disregard the unique shapes of the administrative boundaries. Figure
+\ref{fig:qld_grid} shows a collection of alternative map displays, this
+includes a) a contiguous cartogram, b) a non-contiguous cartogram, c) a
+Dorling cartogram and d) a hexagon tile map. Each Statistical Area at
+Level 2 (SA2) \citep{abs2011} was designed to represent a community.
+These administrative areas are often used to aggregate census data and
+used to understand demographics of the Australian population.
 
-<!-- choropleth -->
-The familiar choropleth map display is often used to allow the user to orient themselves.
-However, the emphasis on the land mass diminishes the features of the distribution in densely populated communities due to the small size on the display [@ACTUC].
-The unique shapes of boundaries can be helpful for orienting users but may not contribute to their understanding of the spatial disease distribution as many of the communities are not visible in a choropleth display [@TVSSS].
-This presents an opportunity for explicit map transformations to improve communication of distributions [@CBATCC].
-In figure \ref{fig:qld_grid}a) the choropleth map is presented with the alternative maps to allow for comparisons to be made.
+The familiar choropleth map display is often used to allow the user to
+orient themselves. However, the emphasis on the land mass diminishes the
+features of the distribution in densely populated communities due to the
+small size on the display \citep{ACTUC}. The unique shapes of boundaries
+can be helpful for orienting users but may not contribute to their
+understanding of the spatial disease distribution as many of the
+communities are not visible in a choropleth display \citep{TVSSS}. This
+presents an opportunity for explicit map transformations to improve
+communication of distributions \citep{CBATCC}. In figure
+\ref{fig:qld_grid}a) the choropleth map is presented with the
+alternative maps to allow for comparisons to be made.
 
@@
 
-<!-- contiguous -->
-When communicating information that is relevant to the population, each member of the population can be given equal representation by transforming the map [@TVSSS].
-The impact of a disease over connected communities can be seen by allowing the boundaries to maintain connection in the transformed display.
-The contiguous cartogram displayed in figure \ref{fig:qld_grid}b) draws attention to smaller geographic units when they are rescaled according to the population [@DMAHP].
-These new shapes can now be coloured to represent a second variable.
-This display can create twisted and unfamiliar shapes from the geographic units as the algorithms must satisfy the topology conditions, especially when there are communities located geographically far from their neighbours [@TVSSS].
-This shown in the northern SA2s of Queensland with an average (yellow) estimated SIR of Melanoma for males.
+When communicating information that is relevant to the population, each
+member of the population can be given equal representation by
+transforming the map \citep{TVSSS}. The impact of a disease over
+connected communities can be seen by allowing the boundaries to maintain
+connection in the transformed display. The contiguous cartogram
+displayed in figure \ref{fig:qld_grid}b) draws attention to smaller
+geographic units when they are rescaled according to the population
+\citep{DMAHP}. These new shapes can now be coloured to represent a
+second variable. This display can create twisted and unfamiliar shapes
+from the geographic units as the algorithms must satisfy the topology
+conditions, especially when there are communities located geographically
+far from their neighbours \citep{TVSSS}. This shown in the northern SA2s
+of Queensland with an average (yellow) estimated SIR of Melanoma for
+males.
 
-<!-- non-contiguous -->
-The non-contiguous cartogram in figure \ref{fig:qld_grid}c) also uses the population to rescale the geographic units.
-Unlike the contiguous cartogram, the SA2 areas maintain their geographic shape, but they may not retain the connection with their neighbours.
-The population of the SA2 areas is used to scale the geographic units in the non-contiguous cartogram [@NAC].
-The amount of white space can be meaningful in non-contiguous cartograms [@ECGC], in this example the disparity between large rural areas and small urban areas means that the city of Brisbane, shown in the inset map looks reasonable, but these units are not visible in the context of the Queensland state map.
-Depending on the difference between the population and geographic land size, the amount of white space can also prevent meaningful understanding of the distribution [@TVSSS].
+The non-contiguous cartogram in figure \ref{fig:qld_grid}c) also uses
+the population to rescale the geographic units. Unlike the contiguous
+cartogram, the SA2 areas maintain their geographic shape, but they may
+not retain the connection with their neighbours. The population of the
+SA2 areas is used to scale the geographic units in the non-contiguous
+cartogram \citep{NAC}. The amount of white space can be meaningful in
+non-contiguous cartograms \citep{ECGC}, in this example the disparity
+between large rural areas and small urban areas means that the city of
+Brisbane, shown in the inset map looks reasonable, but these units are
+not visible in the context of the Queensland state map. Depending on the
+difference between the population and geographic land size, the amount
+of white space can also prevent meaningful understanding of the
+distribution \citep{TVSSS}.
 
-<!-- Dorling -->
-The Dorling cartogram presents each geographic unit as a circle, the size of the circle is scaled according to the population value of each area [@ACTUC].
-Figure \ref{fig:qld_grid}d) shows the Queensland SA2 areas as an individual circle located as close as possible to the geographic centroid location.
-This map draws attention to the collection of coastal cities in Queensland that were not apparent in figure \ref{fig:qld_grid} a), b) or c).
+The Dorling cartogram presents each geographic unit as a circle, the
+size of the circle is scaled according to the population value of each
+area \citep{ACTUC}. Figure \ref{fig:qld_grid}d) shows the Queensland SA2
+areas as an individual circle located as close as possible to the
+geographic centroid location. This map draws attention to the collection
+of coastal cities in Queensland that were not apparent in figure
+\ref{fig:qld_grid} a), b) or c).
 
-<!-- When the population is the statistic of interest, the result is a population cartogram.
-They fail to preserve a recognisable display due to the difference in size of metropolitan and rural areas [@ACTUC], [@GOINO].
--->
-<!-- Contiguous cartograms alter the shape of areas, while preserving boundary relationships of neighbours.
-Non-contiguous cartograms maintain the geographic shape of each geographic area, but will lose the connection to neighbours as the polygon for each geographic area shrinks or grows.
--->
+\hypertarget{algorithm}{%
+\subsection{Algorithm}\label{algorithm}}
 
-## Algorithm
+The purpose of this algorithm is to create a map display that highlights
+the spatial distributions for populations. There has been an increasing
+need for displays that recognise the large number of people that live in
+dense urban environments. The algorithm intends to maintain the spatial
+relationships of a group of geographic units in two ways: between each
+unit and its neighbours; and between each unit and the closest focal
+point. The algorithm allocates geographic units to a representative
+hexagon, in order of their proximity to the closest focal point.
 
-The purpose of this algorithm is to create a map display that highlights the spatial distributions for populations.
-There has been an increasing need for displays that recognise the large number of people that live in dense urban environments.
-The algorithm intends to maintain the spatial relationships of a group of geographic units in two ways: between each unit and its neighbours; and between each unit and the closest focal point.
-The algorithm allocates geographic units to a representative hexagon, in order of their proximity to the closest focal point.
+The algorithm is named for the \emph{Trigona carbonaria} bee species.
+Native to northern and eastern Australia this stingless species builds
+flat layers of hexagonal brood cells, spiralling out from a central
+point \citep{PH}. This hive design inspired the use of multiple focal
+points in the algorithm, individual spirals are constructed outward from
+various points on the geographic map base.
 
-The algorithm is named for the *Trigona carbonaria* bee species.
-Native to northern and eastern Australia this stingless species builds flat layers of hexagonal brood cells, spiralling out from a central point [@PH].
-This hive design inspired the use of multiple focal points in the algorithm, individual spirals are constructed outward from various points on the geographic map base.
-
-There are three key steps performed to create a tessellated hexagon tile map.
-First create the set of centroids from the polygons to allocate, then create the grid of hexagons locations.
-Each centroid can then be allocated to an available hexagon location.
-To make tessellated plots the points can be converted to hexagon shapes, with the hexagon size equal to the size used in the grid.
+There are three key steps performed to create a tessellated hexagon tile
+map. First create the set of centroids from the polygons to allocate,
+then create the grid of hexagons locations. Each centroid can then be
+allocated to an available hexagon location. To make tessellated plots
+the points can be converted to hexagon shapes, with the hexagon size
+equal to the size used in the grid.
 
@@
 
-#### User choices
+\hypertarget{user-choices}{%
+\paragraph{User choices}\label{user-choices}}
 
-<!-- The`create_hexmap` function will -->
-<!-- Derive the centroids of the geographic units to calculate a grid of possible hexagon locations, and allocate each geographic unit to a single hexagon. -->
-Only two inputs are necessary to begin using the algorithm, the shape file, and the id variable. The id column should uniquely identify each geographic unit in the shape file.
+Only two inputs are necessary to begin using the algorithm, the shape
+file, and the id variable. The id column should uniquely identify each
+geographic unit in the shape file.
 
-The centroids can be derived from the shape file. The amount of centroids is used to determine a hexagon size. 
-The derived centroids are a necessary input for an appropriate grid to be constructed, in which each grid point is located a hexagon size distance from the next closest point in all six directions. 
-The grid will initially cover the entire map space, encompassing all the centroid locations and will extend in all directions to the extent of the buffer distance.
-This buffer distance can be helpful to account for densely populated coastal areas, allowing the use of the sea for hexagon locations.
-The hexagon size will likely need adjustments depending on the density of the population.
+The centroids can be derived from the shape file. The amount of
+centroids is used to determine a hexagon size. The derived centroids are
+a necessary input for an appropriate grid to be constructed, in which
+each grid point is located a hexagon size distance from the next closest
+point in all six directions. The grid will initially cover the entire
+map space, encompassing all the centroid locations and will extend in
+all directions to the extent of the buffer distance. This buffer
+distance can be helpful to account for densely populated coastal areas,
+allowing the use of the sea for hexagon locations. The hexagon size will
+likely need adjustments depending on the density of the population.
 
-The centroids derived from the shape file are necessary inputs when creating a grid.
-The creation of the grid and filtering out the points unlikely to be used in the hexagon map results in the hexagon tile map grid.
-At this point, the centroid set and the grid become the necessary inputs to the allocation process.
+The centroids derived from the shape file are necessary inputs when
+creating a grid. The creation of the grid and filtering out the points
+unlikely to be used in the hexagon map results in the hexagon tile map
+grid. At this point, the centroid set and the grid become the necessary
+inputs to the allocation process.
 
-A set of reference locations can be provided as focal points, such as capital cities of states or countries.
-Using focal points, the algorithm will create the order of allocation in order of the closest centroid locations to the focal points.
-Alternatively, a user can specify the variable that should be used to determine the order for the allocation. 
-When allocating representative hexagons, the width parameter can be used to determine the flexibility of positioning using the relationship with the nearest reference location.
-A larger width parameter will increase the amount of available hexagon locations nearer to the centroid of the geographic location.
-A smaller width will maintain the orientation from the focal point to the centroid when selecting the hexagon location, however this could mean it is placed further from the centre of the cluster.
+A set of reference locations can be provided as focal points, such as
+capital cities of states or countries. Using focal points, the algorithm
+will create the order of allocation in order of the closest centroid
+locations to the focal points. Alternatively, a user can specify the
+variable that should be used to determine the order for the allocation.
+When allocating representative hexagons, the width parameter can be used
+to determine the flexibility of positioning using the relationship with
+the nearest reference location. A larger width parameter will increase
+the amount of available hexagon locations nearer to the centroid of the
+geographic location. A smaller width will maintain the orientation from
+the focal point to the centroid when selecting the hexagon location,
+however this could mean it is placed further from the centre of the
+cluster.
 
-## Implementation
+\hypertarget{implementation}{%
+\subsection{Implementation}\label{implementation}}
 
-<!-- Motivate the value of the the package and algorithm -->
-Hexagon tile maps can be useful to understand a distribution across a collection of geographic areas.
-However, these maps are not easily drawn, especially as the number of areas increases.
-This algorithm was created to automate this process, and reduce the manual load involved in creating and implementing alternative displays.
-This allows map makers and data communicators to allocate their time to choosing the most effective display, rather than manually creating them.
+Hexagon tile maps can be useful to understand a distribution across a
+collection of geographic areas. However, these maps are not easily
+drawn, especially as the number of areas increases. This algorithm was
+created to automate this process, and reduce the manual load involved in
+creating and implementing alternative displays. This allows map makers
+and data communicators to allocate their time to choosing the most
+effective display, rather than manually creating them.
 
-The `sugarbag` package has been written for R software, it contains a set of functions that help R users to create a hexagon tile map.
-The algorithm presented in the `sugarbag` package operates on a set of simple feature geometry objects [@sf], this package allows R users to create `sf` objects by importing polygons stored in various formats.
-Users should provide a set of polygons that define geographic units by their administrative boundaries.
-The functions arrange the geographic units in order of proximity to a set of locations provided, such as the centre of capital cities.
-The centroid location of each geographic unit is used to measure the proximity.
-It emphasises the capital cities as population hubs, rather than emphasizing the size of large, rural geographic units.
+The \texttt{sugarbag} package has been written for R software, it
+contains a set of functions that help R users to create a hexagon tile
+map. The algorithm presented in the \texttt{sugarbag} package operates
+on a set of simple feature geometry objects \citep{sf}, this package
+allows R users to create \texttt{sf} objects by importing polygons
+stored in various formats. Users should provide a set of polygons that
+define geographic units by their administrative boundaries. The
+functions arrange the geographic units in order of proximity to a set of
+locations provided, such as the centre of capital cities. The centroid
+location of each geographic unit is used to measure the proximity. It
+emphasises the capital cities as population hubs, rather than
+emphasizing the size of large, rural geographic units.
 
-A user can tweak the parameters of the hexagon map using the additional arguments to the `create_hexmap` function, these options may affect the speed of the creation.
+A user can tweak the parameters of the hexagon map using the additional
+arguments to the \texttt{create\_hexmap} function, these options may
+affect the speed of the creation.
 
-#### Installation
+\hypertarget{installation}{%
+\paragraph{Installation}\label{installation}}
 
@@
 
-```{r eval=FALSE}
+\begin{Schunk}
+\begin{Sinput}
 install.packages("sugarbag")
-```
+\end{Sinput}
+\end{Schunk}
 
@@
 
-```{r eval=FALSE}
+\begin{Schunk}
+\begin{Sinput}
 devtools::install_github("srkobakian","sugarbag")
-```
+\end{Sinput}
+\end{Schunk}
 
@@
 
-```{r}
+\begin{Schunk}
+\begin{Sinput}
 library(sugarbag)
-```
+\end{Sinput}
+\end{Schunk}
 
-#### Creating a hexagon tile map
+\hypertarget{creating-a-hexagon-tile-map}{%
+\paragraph{Creating a hexagon tile
+map}\label{creating-a-hexagon-tile-map}}
 
-The following code creates the hexagon tile map for all the Statistical Areas at Level 2 in Queensland.
-These steps can be executed by the main function, `create_hexmap`, or can be implemented separately for more flexibility.
+The following code creates the hexagon tile map for all the Statistical
+Areas at Level 2 in Queensland. These steps can be executed by the main
+function, \texttt{create\_hexmap}, or can be implemented separately for
+more flexibility.
 
-If a user would like to perform each of the steps of the algorithm themselves, the necessary inputs will change for each function.
+If a user would like to perform each of the steps of the algorithm
+themselves, the necessary inputs will change for each function.
 
-Users may choose to only use the `allocate` function when they wish to use a set of centroids, rather than [@sf] polygons.
+Users may choose to only use the \texttt{allocate} function when they
+wish to use a set of centroids, rather than \citep{sf} polygons.
 
-```{r full_hexmapcode, echo = TRUE, warning = FALSE, message = FALSE, eval=FALSE}
+\begin{Schunk}
+\begin{Sinput}
 ## Load data
@@
 qld_hexmap
-```
+\end{Sinput}
+\end{Schunk}
 
@@
 
-#### Polygon set
+\hypertarget{polygon-set}{%
+\paragraph{Polygon set}\label{polygon-set}}
 
-The polygon set of Statistical Areas at Level 2 (SA2) [@abs2011] of Queensland in 2011 is provided with the `sugarbag` package as `tas_sa2`. 
-A single column of the data set is used to identify the unique areas. 
-In this case, the unique SA2 names for each SA2 have been used.
+The polygon set of Statistical Areas at Level 2 (SA2) \citep{abs2011} of
+Queensland in 2011 is provided with the \texttt{sugarbag} package as
+\texttt{tas\_sa2}. A single column of the data set is used to identify
+the unique areas. In this case, the unique SA2 names for each SA2 have
+been used.
 
-The longitude and latitude centre of the capital cities of Australia are used as focal points to allocate each geographic area around the closest capital city.
-Brisbane will be the common focal point, as this example uses only the areas in the state of Queensland.
+The longitude and latitude centre of the capital cities of Australia are
+used as focal points to allocate each geographic area around the closest
+capital city. Brisbane will be the common focal point, as this example
+uses only the areas in the state of Queensland.
 
-```{r capital_cities}
+\begin{Schunk}
+\begin{Sinput}
 data(capital_cities)
-```
+\end{Sinput}
+\end{Schunk}
 
-The buffer distance, hexagon size, hexagon amount to filter and width of angle are parameters that will be determined within `create_hexmap` if they are not provided.
-They are created as they are needed throughout the following example.
+The buffer distance, hexagon size, hexagon amount to filter and width of
+angle are parameters that will be determined within
+\texttt{create\_hexmap} if they are not provided. They are created as
+they are needed throughout the following example.
 
-#### Step 1: Derive the set of centroid points
+\hypertarget{step-1-derive-the-set-of-centroid-points}{%
+\paragraph{Step 1: Derive the set of centroid
+points}\label{step-1-derive-the-set-of-centroid-points}}
 
-A set of centroids may be used directly.
-The set of polygons should be provided as an `sf` object, this is a data frame containing a `geometry` column.
-The `read_shape` function can assist in creating this object for use in `R`.
+A set of centroids may be used directly. The set of polygons should be
+provided as an \texttt{sf} object, this is a data frame containing a
+\texttt{geometry} column. The \texttt{read\_shape} function can assist
+in creating this object for use in \texttt{R}.
 
-The centroids can be derived from the set of polygons using the `create_centroids` function:
+The centroids can be derived from the set of polygons using the
+\texttt{create\_centroids} function:
 
-```{r cents}
+\begin{Schunk}
+\begin{Sinput}
 centroids <- create_centroids(shp_sf = tas_sa2, sf_id = "SA2_NAME16")
-```
+\end{Sinput}
+\end{Schunk}
 
@@
 
-#### Step 2: Create the hexagon grid points
+\hypertarget{step-2-create-the-hexagon-grid-points}{%
+\paragraph{Step 2: Create the hexagon grid
+points}\label{step-2-create-the-hexagon-grid-points}}
 
-A grid is created to ensure tessellation between the hexagons that represent the geographic units on a hexagon tile map.
+A grid is created to ensure tessellation between the hexagons that
+represent the geographic units on a hexagon tile map.
 
-The grid of possible hexagon locations is made using the `create_grid` function.
-It uses the centroids, the hexagon size and the buffer distance.
+The grid of possible hexagon locations is made using the
+\texttt{create\_grid} function. It uses the centroids, the hexagon size
+and the buffer distance.
 
-```{r grid}
+\begin{Schunk}
+\begin{Sinput}
 grid <- create_grid(centroids = centroids, hex_size = 0.2, buffer_dist = 1.2)
-```
+\end{Sinput}
+\end{Schunk}
 
-##### Creating a tessellated grid
+\hypertarget{creating-a-tessellated-grid}{%
+\subparagraph{Creating a tessellated
+grid}\label{creating-a-tessellated-grid}}
 
-A set of longitude columns, and latitude rows are created to define the locations of the hexagons. The distance between each row and column is the size specified by `hex_size`.
-Equally spaced columns are created from the minimum longitude minus the buffer distance, up to the maximum longitude plus the buffer distance.
-Similarly, the rows are created from the latitude values and the buffer distance.
-A unique hexagon location is created from all intersections of the longitude columns and latitude rows.
-Figure \ref{fig:grid2} shows the original grid on the left, to allow for tessellating hexagons, every second latitude row on the grid is shifted right, by half of the hexagon size.
+A set of longitude columns, and latitude rows are created to define the
+locations of the hexagons. The distance between each row and column is
+the size specified by \texttt{hex\_size}. Equally spaced columns are
+created from the minimum longitude minus the buffer distance, up to the
+maximum longitude plus the buffer distance. Similarly, the rows are
+created from the latitude values and the buffer distance. A unique
+hexagon location is created from all intersections of the longitude
+columns and latitude rows. Figure \ref{fig:grid2} shows the original
+grid on the left, to allow for tessellating hexagons, every second
+latitude row on the grid is shifted right, by half of the hexagon size.
 The grid for tessellation is shown on the right.
-
-<!-- ```{r grid2, fig.cap = "Grid points to create a tile map.", out.width = "100%", echo = FALSE} -->
-<!-- knitr::include_graphics(path = "figures/2grid.pdf") -->
-<!-- ``` -->
 
@@
 
-##### Rolling windows
+\hypertarget{rolling-windows}{%
+\subparagraph{Rolling windows}\label{rolling-windows}}
 
-Not all of the grid points will be used, especially if islands result in a large grid space.
-To filter the grid for appropriate hexagon locations for allocation, the `create_buffer` function is used by `create_grid`.
-It finds the grid points needed to best capture the set of centroids on a hexagon tile map.
+Not all of the grid points will be used, especially if islands result in
+a large grid space. To filter the grid for appropriate hexagon locations
+for allocation, the \texttt{create\_buffer} function is used by
+\texttt{create\_grid}. It finds the grid points needed to best capture
+the set of centroids on a hexagon tile map.
 
-The closest latitude row and longitude column are found for each centroid location. Then rows and columns of centroids are divided into 20 groups.
-The amount of rows in each latitude group and the amount of columns in each longitude group are used as the width of rolling windows.
-The rolling windows can be seen on the bottom and right of the grid shown in Figure \ref{fig:filter-grid}.
-This will tailor the available grid points to those most likely to be used.
-It also helps reduce the amount of time taken, as it decreases the amount of points considered for each centroid allocation.
+The closest latitude row and longitude column are found for each
+centroid location. Then rows and columns of centroids are divided into
+20 groups. The amount of rows in each latitude group and the amount of
+columns in each longitude group are used as the width of rolling
+windows. The rolling windows can be seen on the bottom and right of the
+grid shown in Figure \ref{fig:filter-grid}. This will tailor the
+available grid points to those most likely to be used. It also helps
+reduce the amount of time taken, as it decreases the amount of points
+considered for each centroid allocation.
 
-The first rolling window function finds the minimum and maximum centroid values for the sliding window groups of longitude columns and the groups of latitude rows.
+The first rolling window function finds the minimum and maximum centroid
+values for the sliding window groups of longitude columns and the groups
+of latitude rows.
 
-The second rolling window function finds the average of the rolling minimum and maximum centroid values, for the longitude columns and latitude rows.
+The second rolling window function finds the average of the rolling
+minimum and maximum centroid values, for the longitude columns and
+latitude rows.
 
-##### Filtering the grid
+\hypertarget{filtering-the-grid}{%
+\subparagraph{Filtering the grid}\label{filtering-the-grid}}
 
-The grid points are kept only if they fall between the rolling average of the minimum and maximum centroid values after accounting for the buffer distance, for each row and column of the grid.
-The sparsely populated South-West region of National Park has much fewer points available compared to the South-East region containing the city of Brisbane.
-
-<!-- ```{r filter-grid, fig.cap = "All possible hexagon locations from the initial grid are shown with blue outlines.
-The blue dots show the grid points left to choose from after the buffer step.
-The rolling windows show the collections of rows and columns used to filter the hexagon locations.", echo = FALSE, out.width = "100%"} -->
-<!-- knitr::include_graphics(path = "figures/3grid.pdf", dpi = 300) -->
-<!-- ``` -->
+The grid points are kept only if they fall between the rolling average
+of the minimum and maximum centroid values after accounting for the
+buffer distance, for each row and column of the grid. The sparsely
+populated South-West region of National Park has much fewer points
+available compared to the South-East region containing the city of
+Brisbane.
 
@@
 
-##### Centroid to focal point distance
+\hypertarget{centroid-to-focal-point-distance}{%
+\subparagraph{Centroid to focal point
+distance}\label{centroid-to-focal-point-distance}}
 
-The distance between each centroid in the set, and each of the focal points provided is calculated.
-The name of the closest focal point, and the distance and angle from focal point to polygon centroid is joined to polygon data set.
-To minimise time taken for this step only one option is provided, Queensland's capital city Brisbane.
-The order for allocation is determined by the distance between the polygon centroid and it's closest focal point.
-The points are arranged from the centroid closest to the focal point(s), to the furthest.
+The distance between each centroid in the set, and each of the focal
+points provided is calculated. The name of the closest focal point, and
+the distance and angle from focal point to polygon centroid is joined to
+polygon data set. To minimise time taken for this step only one option
+is provided, Queensland's capital city Brisbane. The order for
+allocation is determined by the distance between the polygon centroid
+and it's closest focal point. The points are arranged from the centroid
+closest to the focal point(s), to the furthest.
 
-#### Step 3: Allocate each centroid to a hexagon grid point
+\hypertarget{step-3-allocate-each-centroid-to-a-hexagon-grid-point}{%
+\paragraph{Step 3: Allocate each centroid to a hexagon grid
+point}\label{step-3-allocate-each-centroid-to-a-hexagon-grid-point}}
 
-Allocation of all centroids takes place using the set of polygon centroids and the hexagon map grid. 
-Centroid allocation begins with the closest centroid to a focal point.
-This will preserve spatial relationships with the focal point, as the inner city areas are allocated first, they will be placed closest to the capital, and the areas that are further will then be accommodated.
-The possible hexagon grid points reduces by one after each allocation, then only those that have not yet been allocated are considered.
+Allocation of all centroids takes place using the set of polygon
+centroids and the hexagon map grid. Centroid allocation begins with the
+closest centroid to a focal point. This will preserve spatial
+relationships with the focal point, as the inner city areas are
+allocated first, they will be placed closest to the capital, and the
+areas that are further will then be accommodated. The possible hexagon
+grid points reduces by one after each allocation, then only those that
+have not yet been allocated are considered.
 
-The possible hexagon locations to consider for a centroid are determined by the `hex_filter`.
-This is the maximum amount of hexagons between the centroid and the furthest considered hexagon.
-It is used to subset possible grid points to only those surrounding the polygon centroid within an appropriate range.
-A smaller distance will increase speed, but can decrease accuracy when width of the angle increases.
+The possible hexagon locations to consider for a centroid are determined
+by the \texttt{hex\_filter}. This is the maximum amount of hexagons
+between the centroid and the furthest considered hexagon. It is used to
+subset possible grid points to only those surrounding the polygon
+centroid within an appropriate range. A smaller distance will increase
+speed, but can decrease accuracy when width of the angle increases.
 
-```{r centroids, eval = FALSE}
+\begin{Schunk}
+\begin{Sinput}
 hexmap_allocation <- allocate(
@@
   verbose = TRUE)
-```
+\end{Sinput}
+\end{Schunk}
 
-The following example considers the first of the Statistical Areas at Level 2. 
-Within the algorithm, these steps are repeated for each polygon.
+The following example considers the first of the Statistical Areas at
+Level 2. Within the algorithm, these steps are repeated for each
+polygon.
 
-##### Filter the grid for unassigned hexagon points
+\hypertarget{filter-the-grid-for-unassigned-hexagon-points}{%
+\subparagraph{Filter the grid for unassigned hexagon
+points}\label{filter-the-grid-for-unassigned-hexagon-points}}
 
-Keeping only the available hexagon points prevents multiple geographic units from being allocated to the same hexagon.
+Keeping only the available hexagon points prevents multiple geographic
+units from being allocated to the same hexagon.
 
-##### Filter the grid points for those closest to the centroid
+\hypertarget{filter-the-grid-points-for-those-closest-to-the-centroid}{%
+\subparagraph{Filter the grid points for those closest to the
+centroid}\label{filter-the-grid-points-for-those-closest-to-the-centroid}}
 
-A box of possible hexagon locations around the centroid allows only the closest points that are not yet assigned to be considered.
-The corners of the box may not appear square if the buffer step has already removed unnecessary points from over the ocean.
+A box of possible hexagon locations around the centroid allows only the
+closest points that are not yet assigned to be considered. The corners
+of the box may not appear square if the buffer step has already removed
+unnecessary points from over the ocean.
 
-The algorithm then removes the outer corners of the square, creating a circle of points, by only keeping points within a certain radial distance around the original centroid location.
-
-<!-- ```{r buffers, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, out.width = "100%"} -->
-<!-- knitr::include_graphics(path = "figures/4grid.pdf") -->
-<!-- ``` -->
+The algorithm then removes the outer corners of the square, creating a
+circle of points, by only keeping points within a certain radial
+distance around the original centroid location.
 
@@
 
-The `width` parameter is used to take a slice of the remaining points.
-The width is the amount of degrees used on either side of the angle from the focal point to centroid location.
-This uses the angle from the closest capital city, to the current centroid as seen in Figure \ref{fig:angles} .
-This allows the spatial relationship to be preserved, even when it is allocated to a hexagon that is further from the focal point then the original centroid location.
-
-<!-- ```{r angles, fig.cap = "Filter for grid points within the angle from the focal point to the centroid.", echo = FALSE, out.width = "100%"} -->
-<!-- knitr::include_graphics(path = "figures/5allocate.png") -->
-<!-- ``` -->
+The \texttt{width} parameter is used to take a slice of the remaining
+points. The width is the amount of degrees used on either side of the
+angle from the focal point to centroid location. This uses the angle
+from the closest capital city, to the current centroid as seen in Figure
+\ref{fig:angles} . This allows the spatial relationship to be preserved,
+even when it is allocated to a hexagon that is further from the focal
+point then the original centroid location.
 
@@
 
-If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded, only when a maximum distance is reached will the angle expand to accommodate more possible grid points.
-By default the angle filter to hexagon grid points that fall within the bounds of the angle from the focal point to the geographic centroid, plus and minus 30 degrees.
-This will increase if no points can be found within the `hex_filter` distance.
-The default angle of 30 was chosen to allow the algorithm to choose hexagons that best maintained the spatial relationship between the focal point and geographic centroid.
-
-<!-- ```{r buffs, fig.cap = "A complete hexagon tile map of Queensland.", out.width = "100%", echo = FALSE} -->
-<!-- knitr::include_graphics(path = "figures/6allocate.png") -->
-<!-- ``` -->
+If no available hexagon grid point is found within the original filter
+distance and angle, the distance is expanded, only when a maximum
+distance is reached will the angle expand to accommodate more possible
+grid points.\\
+By default the angle filter to hexagon grid points that fall within the
+bounds of the angle from the focal point to the geographic centroid,
+plus and minus 30 degrees. This will increase if no points can be found
+within the \texttt{hex\_filter} distance. The default angle of 30 was
+chosen to allow the algorithm to choose hexagons that best maintained
+the spatial relationship between the focal point and geographic
+centroid.
 
@@
 
-A complete hexagon tile map of Queensland is created by applying the algorithm steps to each centroid.
-The hexagon tile map visualisation is used below to visualise the Australian Cancer Atlas data [@TACA].
-Two views of the same data are produced by filling according to the Lung Cancer Standardised Incidence Rates (SIRs) downloaded from the Australian Cancer Atlas site.
-This small example in Figure \ref{fig:sir} shows the group of blue areas in the Brisbane CBD more prominently in the hexagon tile map (b).
-The small red areas visible in the choropleth map (a) along the north coast are much larger in the hexagon tile maps.
-The hexagon tile map shows less yellow, this no longer overwhelms the map space with the information regarding the rural areas.
-
-<!-- ```{r sir, out.width = "100%", echo = FALSE, fig.cap = "The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2.
-A choropleth map (a) of Standardised Incidence Rates (SIRs) is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented."} -->
-<!-- knitr::include_graphics(path = "figures/7SIR.png") -->
-<!-- ``` -->
+A complete hexagon tile map of Queensland is created by applying the
+algorithm steps to each centroid. The hexagon tile map visualisation is
+used below to visualise the Australian Cancer Atlas data \citep{TACA}.
+Two views of the same data are produced by filling according to the Lung
+Cancer Standardised Incidence Rates (SIRs) downloaded from the
+Australian Cancer Atlas site. This small example in Figure \ref{fig:sir}
+shows the group of blue areas in the Brisbane CBD more prominently in
+the hexagon tile map (b). The small red areas visible in the choropleth
+map (a) along the north coast are much larger in the hexagon tile maps.
+The hexagon tile map shows less yellow, this no longer overwhelms the
+map space with the information regarding the rural areas.
 
@@
 
-#### Neighbour relationships
+\hypertarget{neighbour-relationships}{%
+\paragraph{Neighbour relationships}\label{neighbour-relationships}}
 
-It is possible to consider the neighbouring areas for each SA2, for stronger preservation of the spatial distribution.
+It is possible to consider the neighbouring areas for each SA2, for
+stronger preservation of the spatial distribution.
 
-An additional step can be included to allow the neighbours that have already been allocated to influence the placement of the current centroid. 
-This requires specifying the `sf` object as the argument for the `use_neighbours` parameter.
-This calculates neighbours using intersections of their polygons.
-This occurs for all areas before any allocations begin.
+An additional step can be included to allow the neighbours that have
+already been allocated to influence the placement of the current
+centroid. This requires specifying the \texttt{sf} object as the
+argument for the \texttt{use\_neighbours} parameter. This calculates
+neighbours using intersections of their polygons. This occurs for all
+areas before any allocations begin.
 
-During the allocation of each centroid, the list of neighbours is consulted.
-If any neighbour was already allocated, the hexagons surrounding the neighbours on the grid are prioritised.
-For multiple neighbours, the neighbouring hexagon grid points are aggregated and considered in order of distance from the original centroid.
+During the allocation of each centroid, the list of neighbours is
+consulted. If any neighbour was already allocated, the hexagons
+surrounding the neighbours on the grid are prioritised. For multiple
+neighbours, the neighbouring hexagon grid points are aggregated and
+considered in order of distance from the original centroid.
 
-## Hexagon tile map of Australia
+\hypertarget{hexagon-tile-map-of-australia}{%
+\subsection{Hexagon tile map of
+Australia}\label{hexagon-tile-map-of-australia}}
 
-This algorithm has been applied to the complete set of all Australian Statistical Areas at Level 2.
-This display highlights the density of Australian capital cities, as it draws attention to the many communities in Sydney, Melbourne and Brisbane.
-This display also highlights the disparity in the burden of Melanoma cancer for males in the communities of these three cities.
-There are several collections of red hexagons in Brisbane that draw attention and they represent the communities with much higher rates of diagnosis than the Australian average.
-The communities south of Brisbane show a gradient of colour as the values progress from higher than average, to much lower than average for the communities closer to the Sydney CBD.
-This pattern progresses into the communities with lower than average rates in Melbourne and Tasmania.
+This algorithm has been applied to the complete set of all Australian
+Statistical Areas at Level 2. This display highlights the density of
+Australian capital cities, as it draws attention to the many communities
+in Sydney, Melbourne and Brisbane. This display also highlights the
+disparity in the burden of Melanoma cancer for males in the communities
+of these three cities. There are several collections of red hexagons in
+Brisbane that draw attention and they represent the communities with
+much higher rates of diagnosis than the Australian average. The
+communities south of Brisbane show a gradient of colour as the values
+progress from higher than average, to much lower than average for the
+communities closer to the Sydney CBD. This pattern progresses into the
+communities with lower than average rates in Melbourne and Tasmania.
 
-Compared to the choropleth map display, the low rates in the rural Australian communities are no longer dominating the display.
-The much higher than average rates in Sydney draw more attention in the hexagon tile map display unlike the red and orange areas in the city of Brisbane that draw attention in both displays.
+Compared to the choropleth map display, the low rates in the rural
+Australian communities are no longer dominating the display. The much
+higher than average rates in Sydney draw more attention in the hexagon
+tile map display unlike the red and orange areas in the city of Brisbane
+that draw attention in both displays.
 
@@
 
-## Animation
+\hypertarget{animation}{%
+\subsection{Animation}\label{animation}}
 
-The `gganimate` [@gganimate] package can be used to make an animation.
-It requires connecting the polygons for each area in two displays, which can be done using the `sf_id` variable, such as the SA2 name.
-The animation^[This animation can be viewed at: https://sugarbagjss.netlify.com/] connecting these two displays will highlight the rapid growth of the inner-city areas that emphasises the density of the communities.
-The hexagons that move the furthest will move rapidly in the animation.
-The rapid decreases of the large rural areas also show how much greater the landmass of Statistical Areas can be.
+The \texttt{gganimate} \citep{gganimate} package can be used to make an
+animation. It requires connecting the polygons for each area in two
+displays, which can be done using the \texttt{sf\_id} variable, such as
+the SA2 name. The animation\footnote{This animation can be viewed at:
+  \url{https://sugarbagjss.netlify.com/}} connecting these two displays
+will highlight the rapid growth of the inner-city areas that emphasises
+the density of the communities. The hexagons that move the furthest will
+move rapidly in the animation. The rapid decreases of the large rural
+areas also show how much greater the landmass of Statistical Areas can
+be.
 
-## Conclusion  {#conclusion-03}
+\hypertarget{conclusion-03}{%
+\subsection{Conclusion}\label{conclusion-03}}
 
-It is possible to use alternative maps to communicate spatial distributions.While a choropleth map display is the current practice spatial visualisation of geographical data.
-Current methods do not always work for Australia due to the large geographic space between the densely populated capital cities.
-The administrative boundaries may also distract from the statistics communicated using colour.
+It is possible to use alternative maps to communicate spatial
+distributions.While a choropleth map display is the current practice
+spatial visualisation of geographical data. Current methods do not
+always work for Australia due to the large geographic space between the
+densely populated capital cities. The administrative boundaries may also
+distract from the statistics communicated using colour.
 
-Alternative maps highlight the value of the statistics across the geographic units.
-Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing each administrative area.
-This acknowledges that the amount of residents can be different but recognises that each population area is equally important.
-The solution to this visualisation problem has equally sized areas, with neighbourhood boundary connections.
-This map algorithm is implemented in the `sugarbag` [@sugarbag] package written for `R` [@R].
-The `sugarbag` package creates tessellated hexagon tile maps.
-The Australian application preserves the spatial relationships, emphasising capital cities.
-The hexagon tile map is a visualisation solution that highlights spatial distributions.
+Alternative maps highlight the value of the statistics across the
+geographic units. Alternative mapping methods allow increased
+understanding of the spatial distribution of a variable across the
+population, by fairly representing each administrative area. This
+acknowledges that the amount of residents can be different but
+recognises that each population area is equally important. The solution
+to this visualisation problem has equally sized areas, with
+neighbourhood boundary connections. This map algorithm is implemented in
+the \texttt{sugarbag} \citep{sugarbag} package written for \texttt{R}
+\citep{R}. The \texttt{sugarbag} package creates tessellated hexagon
+tile maps. The Australian application preserves the spatial
+relationships, emphasising capital cities. The hexagon tile map is a
+visualisation solution that highlights spatial distributions.
 
-These hexagons equally represent each area. However, the tessellation does not allow the size of the hexagons to represent another variable, similar to the choropleth maps.
-The algorithm is heavily dependent on the focal points used, as this determines the order of allocation.
-It works on the assumption that viewers can use directional relationships to identify their neighbourhoods but this can be aided by the animation.
-With careful consideration of the choropleth map, the small geographic inner city areas may have been noticed by viewers, but the hexagon tile map display emphasises them.
-The communities in northern Queensland and the Northern territory do not draw attention because of their size as in the choropleth, but their colour is still noticeably below average when contrasted with the hexagons further south.
+These hexagons equally represent each area. However, the tessellation
+does not allow the size of the hexagons to represent another variable,
+similar to the choropleth maps. The algorithm is heavily dependent on
+the focal points used, as this determines the order of allocation. It
+works on the assumption that viewers can use directional relationships
+to identify their neighbourhoods but this can be aided by the animation.
+With careful consideration of the choropleth map, the small geographic
+inner city areas may have been noticed by viewers, but the hexagon tile
+map display emphasises them. The communities in northern Queensland and
+the Northern territory do not draw attention because of their size as in
+the choropleth, but their colour is still noticeably below average when
+contrasted with the hexagons further south.
 
-<!-- why hexagon tile map addresses deficiencies -->
-The Dorling cartogram was the most influential in the design of the hexagon tile map.
-The use of a hexagon provides a simple shape that shifts the focus of the visualisation from the shape of SA2s to the distribution effects of a disease on communities.
-not impeded by the irregular and unusual shapes created by a contiguous cartogram and the immense white space created on the non-contiguous cartogram.
-Hexagons can emphasise the relationship between neighbouring communities by allowing their sides to touch.
-The tessellation crated by adjoining hexagons for densely populated areas is helpful as it shows that most communities are not islands onto themselves, but are intrinsically connected to those around them.
-As seen in the Dorling cartogram in figure \ref{fig:qld_grid}c), the tessellation that allows boundary connections was not imposed for rural communities, where centroid of the geographic unit was located far from others, a feature that allows distant but dense populations of the coastal towns of Queensland to be recognised.
+The Dorling cartogram was the most influential in the design of the
+hexagon tile map. The use of a hexagon provides a simple shape that
+shifts the focus of the visualisation from the shape of SA2s to the
+distribution effects of a disease on communities. not impeded by the
+irregular and unusual shapes created by a contiguous cartogram and the
+immense white space created on the non-contiguous cartogram. Hexagons
+can emphasise the relationship between neighbouring communities by
+allowing their sides to touch. The tessellation crated by adjoining
+hexagons for densely populated areas is helpful as it shows that most
+communities are not islands onto themselves, but are intrinsically
+connected to those around them. As seen in the Dorling cartogram in
+figure \ref{fig:qld_grid}c), the tessellation that allows boundary
+connections was not imposed for rural communities, where centroid of the
+geographic unit was located far from others, a feature that allows
+distant but dense populations of the coastal towns of Queensland to be
+recognised.
 
-The choropleth map that uses the geographic shapes of areas can be seen in figure \ref{fig:melanoma-geo}.
-Figure \ref{fig:melanoma-hex} displays the Australian areas with equally sized hexagons.
-This display allows the small and densely populated inner city areas to be easily contrasted with their neighbouring areas.
+The choropleth map that uses the geographic shapes of areas can be seen
+in figure \ref{fig:melanoma-geo}. Figure \ref{fig:melanoma-hex} displays
+the Australian areas with equally sized hexagons. This display allows
+the small and densely populated inner city areas to be easily contrasted
+with their neighbouring areas.
 
-<!-- future -->
-Future work will include refining the algorithm.
-It would be possible to take a logarithmic function rather than a direct angle to help choose a closer hexagon to the original centroid location, before increasing the width of the angle used to filter the hexagons.
+Future work will include refining the algorithm. It would be possible to
+take a logarithmic function rather than a direct angle to help choose a
+closer hexagon to the original centroid location, before increasing the
+width of the angle used to filter the hexagons.
 
-This algorithm has only been tested using single countries, and does not consider definite borders of countries.
-While the buffer allows extension beyond the furthest centroids, there is no mechanism to protect the borders and ensure centroids are placed within the geographic borders of a country.
+This algorithm has only been tested using single countries, and does not
+consider definite borders of countries. While the buffer allows
+extension beyond the furthest centroids, there is no mechanism to
+protect the borders and ensure centroids are placed within the
+geographic borders of a country.
 
-This algorithm is an effective start to creating hexagon tile maps for many geographic units.
+This algorithm is an effective start to creating hexagon tile maps for
+many geographic units.
+
+\bibliography{sugarbag.bib}
+
+\address{%
+Stephanie Kobakian\\
+Monash University\\%
+Department of Econometrics and Business Statistics\\
+%
+%
+%
+\\\href{mailto:stephanie.kobakian@monash.edu}{\nolinkurl{stephanie.kobakian@monash.edu}}
+}
+
+\address{%
+Dianne Cook\\
+Monash University\\%
+Department of Econometrics and Business Statistics\\
+%
+%
+%
+\\\href{mailto:dicook@monash.edu}{\nolinkurl{dicook@monash.edu}}
+}

### 2020-09-28 algorithm.R

@@ -1,0 +1,108 @@
+## ----setup, echo=FALSE, message=FALSE, warning=FALSE, comment = FALSE----
+library(knitcitations)
+library(RefManageR)
+library(sf)
+library(sugarbag)
+library(kableExtra)
+ 
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+options("citation_format" = "pandoc")
+BibOptions(check.entries = FALSE, style = "markdown")
+
+
+## ----eval=FALSE-------------------------------------------------------
+## install.packages("sugarbag")
+
+
+## ----eval=FALSE-------------------------------------------------------
+## devtools::install_github("srkobakian","sugarbag")
+
+
+## ---------------------------------------------------------------------
+library(sugarbag)
+
+
+## ----full_hexmapcode, echo = TRUE, warning = FALSE, message = FALSE, eval=FALSE----
+## ## Load data
+## qld_sa2 <- absmapsdata::sa22011 %>%
+##   filter(state_name_2011 == "Queensland")
+## 
+## ## Create centroids set
+## centroids <- create_centroids(qld_sa2, "sa2_name_2011")
+## 
+## ## Create hexagon grid
+## grid <- create_grid(centroids = centroids,
+##                     hex_size = 0.12,
+##                     buffer_dist = 1.2)
+## 
+## ## Allocate polygon centroids to hexagon grid points
+## hex_allocated <- allocate(
+##   centroids = centroids,
+##   hex_grid = grid,
+##   sf_id = "sa2_name_2011",
+##   ## same column used in create_centroids
+##   hex_size = 0.12,
+##   ## same size used in create_grid
+##   hex_filter = 10,
+##   use_neighbours = qld_sa2,
+##   focal_points = capital_cities %>%
+##     filter(points == "Brisbane"),
+##   width = 35,
+##   verbose = FALSE
+## )
+## 
+## ## Prepare to plot
+## fort_hex <- fortify_hexagon(data = hex_allocated,
+##                             sf_id = "sa2_name_2011",
+##                             hex_size = 0.12)
+## 
+## fort_qld <- qld_sa2 %>%
+##   fortify_sfc()
+## 
+## ## Make a plot
+## library(ggplot2)
+## qld_hexmap <- ggplot() +
+##   geom_polygon(aes(
+##       x = long,
+##       y = lat,
+##       group = interaction(sa2_name_2011, polygon)
+##     ),
+##     fill = "white",
+##     colour = "lightgrey",
[…]

### 2020-09-28 kobakian_sugarbag_jss/kobakian_sugarbag_jss.R

@@ -1,485 +1,0 @@
-
-###########################################################
-## LIBRARIES
-## sugarbag to create tesellated hexagon map
-## tidyverse for tidy data manipulation, not necessary
-
-library(sugarbag)
-library(dplyr)
-library(ggplot2)
-library(gridExtra)
-library(purrr)
-library(sf)
-
-
-###########################################################
-## DATA
-## load data files from sugarbag
-data(capital_cities)
-
-sa2 <- absmapsdata::sa22011  %>% 
-  filter(state_name_2011 == "Tasmania")
-
-# Join with cancer data from Australian Cancer Atlas
-aus_colours <- function(sir_p50){
-  value <- case_when(
-    sir_p50 < 0.5 ~ "#33809d",
-    sir_p50 >= 0.5 & sir_p50 < 0.75 ~ "#aec6c7",
-    sir_p50 >= 0.75 & sir_p50 < 1.5 ~ "#fff4bc",
-    sir_p50 >= 1.25 & sir_p50 < 1.5 ~ "#ff9a64",
-    sir_p50 >= 1.5 ~ "#ff3500",
-    TRUE ~ "#FFFFFF")
-  return(value)
-}
-
-SIR <- read_csv("kobakian_sugarbag_jss/data/SIR Downloadable Data.csv") %>% 
-  dplyr::select(Cancer_name, SA2_name, Sex_name, p50) %>% 
-  filter(Cancer_name == "Lung", Sex_name == "Males") %>% 
-  filter(SA2_name %in% sa2$sa2_name_2011) %>% 
-  mutate(SIR = map_chr(p50, aus_colours)) 
-
-# No data for "Mount Wellington", "Wilderness - East", "Wilderness - West" 
-###########################################################
-## CENTROIDS
-## Use the create_centroids function to find polygon centroids:
-centroids <- create_centroids(shp_sf = sa2, sf_id = "sa2_name_2011")
-
-## Join the data from the original data set to the set of centroids by sf_id
-centroids <- left_join(centroids,
-  sf::st_drop_geometry(sa2), by = "sa2_name_2011")
-
-###########################################################
-## CENTROID PLOTS
-## Fortify the underlying geographical areas for plotting
-fort_sa2 <- fortify_sfc(sa2)
-
-cents <- ggplot() + 
[…]

### 2020-09-28 paper_distill.R

@@ -1,481 +1,0 @@
-
-###########################################################
-## LIBRARIES
-## sugarbag to create tesellated hexagon map
-## tidyverse for tidy data manipulation, not necessary
-
-library(sugarbag)
-library(dplyr)
-library(ggplot2)
-library(gridExtra)
-library(purrr)
-library(sf)
-library(readr)
-
-###########################################################
-## DATA
-## load data files from sugarbag
-data(capital_cities)
-
-sa2 <- absmapsdata::sa22011  %>% 
-  filter(state_name_2011 == "Tasmania")
-
-# Join with cancer data from Australian Cancer Atlas
-aus_colours <- function(sir_p50){
-  value <- case_when(
-    sir_p50 < 0.5 ~ "#33809d",
-    sir_p50 >= 0.5 & sir_p50 < 0.75 ~ "#aec6c7",
-    sir_p50 >= 0.75 & sir_p50 < 1.5 ~ "#fff4bc",
-    sir_p50 >= 1.25 & sir_p50 < 1.5 ~ "#ff9a64",
-    sir_p50 >= 1.5 ~ "#ff3500",
-    TRUE ~ "#FFFFFF")
-  return(value)
-}
-
-SIR <- read_csv("kobakian_sugarbag_jss/data/SIR Downloadable Data.csv") %>% 
-  dplyr::select(Cancer_name, SA2_name, Sex_name, p50) %>% 
-  filter(Cancer_name == "Lung", Sex_name == "Males") %>% 
-  filter(SA2_name %in% sa2$sa2_name_2011) %>% 
-  mutate(SIR = map_chr(p50, aus_colours)) 
-
-# No data for "Mount Wellington", "Wilderness - East", "Wilderness - West" 
-###########################################################
-## CENTROIDS
-## Use the create_centroids function to find polygon centroids:
-centroids <- create_centroids(shp_sf = sa2, sf_id = "sa2_name_2011")
-
-## Join the data from the original data set to the set of centroids by sf_id
-centroids <- left_join(centroids,
-  sf::st_drop_geometry(sa2), by = "sa2_name_2011")
-
-###########################################################
-## CENTROID PLOTS
-## Fortify the underlying geographical areas for plotting
-fort_sa2 <- fortify_sfc(sa2)
-
-cents <- ggplot() + 
[…]

### 2020-09-30 figures.R
Thyroid figures

@@ -1,0 +1,661 @@
+# Young statisticians conference presentation plots
+
+library(absmapsdata)
+library(tidyverse)
+library(cartogram)
+library(ggthemes)
+library(cowplot)
+library(sf)
+library(sp)
+
+### Theme set up
+
+invthm <- theme_map() + 
+  theme(
+    panel.background = element_rect(fill = "transparent", colour = NA), 
+    plot.background = element_rect(fill = "transparent", colour = NA),
+    legend.background = element_rect(fill = "transparent", colour = NA),
+    legend.key = element_rect(fill = "transparent", colour = NA),
+    text = element_text(colour = "white"),
+    axis.text = element_text(colour = "white")
+  )
+
+## States of Australia
+
+states <- absmapsdata::state2011 %>% 
+  filter(state_name_2011 != "Other Territories")
+
+# Act pop out plot
+act_map <- absmapsdata::state2011 %>% 
+  filter(state_name_2011 == "Australian Capital Territory") %>% st_transform(., 3112) %>% 
+  ggplot() + 
+  theme_void() +
+  geom_sf(fill = "white") + 
+  geom_rect(aes(xmin =1323014, xmax = 1404210, ymin=-4132815, ymax=-4026022), fill = NA, colour = "black")
+
+
+# Australian map
+aus_map <- ggplot(states) + 
+  geom_sf(aes(fill = albers_sqkm)) +
+  scale_fill_distiller(type = "seq", palette = "BuGn",  direction = 1, na.value = "light grey") + 
+  theme_void() +
+  coord_sf(crs = 3112) +
+   theme(legend.position ="left", legend.title = element_text("Area (sqkm)"))
+
+ggsave(filename = "figures/aus.png", plot = aus_map,
+  device = "png", bg = "transparent", dpi = 300,  width = 10, height = 8)
+
+# Australian map with pop out
+aus_states <- ggdraw() + 
+  draw_plot(aus_map, 0, 0, 1, 1) +
+  draw_plot(act_map, 0.82, 0.01, 0.17, 0.3)
+
+ggsave(filename = "figures/aus_states.png", plot = aus_states,
+  device = "png", bg = "transparent", dpi = 300,  width = 10, height = 8)
+
+
+###############################################################################
[…]

### 2020-09-30 algorithm.Rmd
New title

@@
 ---
-title: A Hexagon Tile Map Algorithm For Spatial Mapping To Create Alternative Australian Maps
+title: A Hexagon Tile Map Algorithm for Displaying Spatial Data
 author:
@@
 \centering
-\includegraphics[width=14cm]{figures/aus_melanoma_p.pdf}
+\includegraphics[width=14cm]{figs/aus_melanoma_p.pdf}
 \caption{\label{fig:melanoma-geo}A choropleth map of the Statistical Areas of Australia at Level 2.
@@
 \centering
-\includegraphics[width=14cm]{figures/qld_grid.pdf}
+\includegraphics[width=14cm]{figs/qld_grid.pdf}
 \caption{\label{fig:qld_grid}A collection of alternative maps of the Statistical Areas of Australia at Level 2.
@@
 \begin{figure}
-\includegraphics[width=14cm]{figures/flowchart.pdf}
+\includegraphics[width=14cm]{figs/flowchart.pdf}
 \caption{\label{fig:sugarbag_flow}A flow diagram detailing the necessary steps to create a hexagon tile map.}
@@
 \centering
-\includegraphics[width=14cm]{figures/aus_gghexmap.pdf}
+\includegraphics[width=14cm]{figs/aus_gghexmap.pdf}
 \caption{\label{fig:melanoma-hex}A hexagon tile map of the Statistical Areas of Australia at Level 2.
@@
 \centering
-\includegraphics[width=14cm]{figures/1centroids.pdf}
+\includegraphics[width=14cm]{figs/1centroids.pdf}
 \caption{\label{fig:centroids_plot}The geographic shapes of the Statistical Areas of Queensland at Level 2. The points show the locations of the centroids of the SA2 areas.}
@@
 \centering
-\includegraphics[width=16cm]{figures/2grid.pdf}
+\includegraphics[width=16cm]{figs/2grid.pdf}
 \caption{\label{fig:grid2}Grid points to create a hexagon tile map.}
@@
 \centering
-\includegraphics[width=10cm]{figures/3grid.pdf}
+\includegraphics[width=10cm]{figs/3grid.pdf}
 \caption{\label{fig:filter-grid}The remaining hexagon locations from all the possible points in the initial grid after the buffer is applied.
@@
 \centering
-\includegraphics[width=16cm]{figures/4grid.pdf}
+\includegraphics[width=16cm]{figs/4grid.pdf}
 \caption{\label{fig:buffers}The remaining available hexagon locations after filtering for the grid points within a square distance, then circular around the centroid.}
@@
 \centering
-\includegraphics[width=16cm]{figures/5allocate.pdf}
+\includegraphics[width=16cm]{figs/5allocate.pdf}
 \caption{\label{fig:angles}The remaining available hexagon locations after filtering for grid points within the angle from the focal point to the centroid.}
@@
 \centering
-\includegraphics[width=16cm]{figures/6allocate.pdf}
+\includegraphics[width=16cm]{figs/6allocate.pdf}
 \caption{\label{fig:buffs}A complete hexagon tile map of Queensland.}
@@
 \centering
-\includegraphics[width=14cm]{figures/7SIR.pdf}
+\includegraphics[width=14cm]{figs/7SIR.pdf}
 \caption{\label{fig:sir}The Australian Cancer Atlas data displayed on a choropleth and hexagon tile map.
@@
 \centering
-\includegraphics[width=14cm]{figures/aus_gghexmap.pdf}
+\includegraphics[width=14cm]{figs/aus_gghexmap.pdf}
 \caption{\label{fig:melanoma-geo}A hexagon tile map of the Statistical Areas of Australia at Level 2.

### 2020-09-30 algorithm.tex
New title

@@
 % !TeX root = RJwrapper.tex
-\title{A Hexagon Tile Map Algorithm For Spatial Mapping To Create Alternative
-Australian Maps}
+\title{A Hexagon Tile Map Algorithm for Displaying Spatial Data}
 \author{by Stephanie Kobakian and Dianne Cook}

### 2020-10-02 kobakian-cook.tex
Potentially use NSW for thyroid example?

--- 2020-09-30 algorithm.tex
@@
 equal population areas results in dramatically different square meterage
-of the geographic units. The geographic units are usually
-administrative, such as states or electorates. The units are filled with
-colour to represent the value of the statistic for each unit \citep{EI}.
-This can lead to unequal emphasis on the statistical value of each of
-the geographic units. This allows choropleth map displays to
-misrepresent the spatial distributions of human related statistics due
-to area-size bias \citep{BCM}. Figure \ref{fig:melanoma-geo} is a
-choropleth map that uses colour to display the estimated Standardised
-Incidence Ratios (SIRs) of melanoma cancer for males for each of the
-Statistical Areas at Level 2 (SA2) used by the Australian Bureau of
-Statistics \citeyearpar{abs2011}. The Australian choropleth map display
-draws attention to the expanse of light blue areas across the rural
-communities in all states. The SA2s around Brisbane stand out as more
-orange and red. To create this choropleth map the SA2 polygons for 2011
-from the Australian Bureau of Statistics.
+of the administrative geographic units, such as states or electorates.
+The units are filled with colour to represent the value of the statistic
+for each unit \citep{EI}. This can lead to unequal emphasis on the
+statistical value of each of the geographic units. This allows
+choropleth map displays to misrepresent the spatial distributions of
+human related statistics due to area-size bias \citep{BCM}. Figure
+\ref{fig:melanoma-geo} is a choropleth map that uses colour to display
+the estimated Standardised Incidence Ratios (SIRs) of melanoma cancer
+for males for each of the Statistical Areas at Level 2 (SA2) used by the
+Australian Bureau of Statistics \citeyearpar{abs2011}. The Australian
+choropleth map display draws attention to the expanse of light blue
+areas across the rural communities in all states. The SA2s around Hobart
+stand out as more orange and red. To create this choropleth map the SA2
+polygons for 2011 from the Australian Bureau of Statistics.
 
@@
 \centering
-\includegraphics[width=14cm]{figs/aus_melanoma_p.pdf}
+\includegraphics[width=14cm]{figs/aus_melanoma_p.png}
 \caption{\label{fig:melanoma-geo}A choropleth map of the Statistical Areas of Australia at Level 2.
@@
 disregard the unique shapes of the administrative boundaries. Figure
-\ref{fig:qld_grid} shows a collection of alternative map displays, this
+\ref{fig:nsw_grid} shows a collection of alternative map displays, this
 includes a) a contiguous cartogram, b) a non-contiguous cartogram, c) a
@@
 communication of distributions \citep{CBATCC}. In figure
-\ref{fig:qld_grid}a) the choropleth map is presented with the
+\ref{fig:nsw_grid}a) the choropleth map is presented with the
 alternative maps to allow for comparisons to be made.
+
+\begin{Schunk}
+\begin{Sinput}
+states <- absmapsdata::state2011 %>% 
+  rmapshaper::ms_simplify(keep = 0.25, keep_shapes = TRUE) %>% 
+  filter(!state_name_2011 == "Other Territories")
+
+sa2 <- absmapsdata::sa22011 %>% 
+  filter(state_name_2011 == "New South Wales") %>% 
+  filter(!st_is_empty(geometry))
+
+# sa2 <- sa2 %>% rmapshaper::ms_simplify(keep = 0.05, keep_shapes = TRUE)
+
+SIR <- read_csv("data/SIR Downloadable Data.csv") %>% 
+  filter(SA2_name %in% sa2$sa2_name_2011) %>% 
+  dplyr::select(Cancer_name, SA2_name, Sex_name, p50) %>% 
+  filter(Cancer_name == "Thyroid", Sex_name == "Females")
+ERP <- read_csv("data/ERP.csv") %>%
+  filter(REGIONTYPE == "SA2", Time == 2011, Region %in% SIR$SA2_name) %>% 
+  dplyr::select(Region, Value)
+
+# Alternative maps
+# Join with sa2 sf object
+sa2thyroid_ERP <- SIR %>% 
+  left_join(sa2, ., by = c("sa2_name_2011" = "SA2_name")) %>%
+  left_join(., ERP %>% 
+              dplyr::select(Region, 
+              Population = Value), by = c("sa2_name_2011"= "Region")) %>% 
+  filter(!st_is_empty(geometry))
+
+sa2thyroid_ERP <- sa2thyroid_ERP %>% 
+  filter(!is.na(Population)) %>% 
+  mutate(SIR = map_chr(p50, aus_colours)) %>% 
+  st_as_sf()
+
+aus_ggchoro <- ggplot(sa2thyroid_ERP) + 
+  #geom_sf(fill = "lightgrey", data = states) + 
+  geom_sf(aes(fill = SIR)) + 
+  scale_fill_identity()
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+###############################################################################
+
+sa2thyroid_ERP <- st_transform(sa2thyroid_ERP, 3112)
+sa2thyroid_ERP <- sa2thyroid_ERP %>% 
+  mutate(sva = sqrt(as.numeric(Population)/as.numeric(albers_sqkm)))
+
+###############################################################################
+# Contiguous Cartograms
+
+cont <- sa2thyroid_ERP %>% 
+  mutate(Population = Population + 1) %>% 
+  cartogram_cont(., weight = "Population", itermax = 20) %>%
+  st_as_sf()
+
+save(cont, file = "data/cont.rda")
+load("data/cont.rda")
+
+aus_ggcont <- ggplot(cont) + 
+  geom_sf(aes(fill = SIR), colour = NA) + 
+  scale_fill_identity() + 
+  invthm + guides(fill=FALSE)
+aus_ggcont
+
+ggsave(filename = "figures/aus_ggcont.png", plot = aus_ggcont,
+       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+###############################################################################
+# Non - Contiguous Cartograms
+
+ncont <- cartogram_ncont(sa2thyroid_ERP, k = 1/10,
+                         weight = "Population") %>% st_as_sf()
+
+save(ncont, file = "data/ncont.rda")
+load("data/ncont.rda")
+
+aus_ggncont <- ggplot(ncont) + 
+  geom_sf(aes(fill = SIR), colour = NA) + 
+  scale_fill_identity() + 
+  invthm + guides(fill=FALSE)
+aus_ggncont
+
+ggsave(filename = "figures/aus_ggncont.png", plot = aus_ggncont,
+       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+###############################################################################
+# Non - Contiguous Dorling Cartograms
+
+dorl <- sa2lung_ERP %>%
+  mutate(pop = (Population/max(Population))*10) %>% 
+  cartogram_dorling(., k = 0.01, weight = "pop", m_weight = 1) %>% st_as_sf()
+d <- st_bbox(dorl)
+aus_ggdorl <- ggplot(dorl) + 
+  geom_sf(aes(fill = SIR)) + 
+  scale_fill_identity()+
+  invthm + guides(fill = FALSE)
+aus_ggdorl
+
+ggsave(filename = "figures/aus_ggdorl.png", plot = aus_ggdorl,
+       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+## Load data
+tas_sa2 <- absmapsdata::sa22011 %>% 
+  filter(state_name_2011 == "New South Wales")
+
+## Create centroids set
+centroids <- create_centroids(tas_sa2, "sa2_name_2011")
+
+## Create hexagon grid
+grid <- create_grid(centroids = centroids,
+                    hex_size = 0.12,
+                    buffer_dist = 1.2)
+
+## Allocate polygon centroids to hexagon grid points
+hex_allocated <- allocate(
+  centroids = centroids,
+  hex_grid = grid,
+  sf_id = "sa2_name_2011",
+  ## same column used in create_centroids
+  hex_size = 0.12,
+  ## same size used in create_grid
+  hex_filter = 10,
+  use_neighbours = tas_sa2,
+  focal_points = capital_cities %>%
+    filter(points == "Hobart"),
+  width = 35,
+  verbose = FALSE
+)
+
+## Prepare to plot
+fort_hex <- fortify_hexagon(data = hex_allocated,
+                            sf_id = "sa2_name_2011",
+                            hex_size = 0.12)
+
+fort_tas <- tas_sa2 %>%
+  fortify_sfc()
+
+## Make a plot
+library(ggplot2)
+tas_hexmap <- ggplot() +
+  geom_polygon(aes(
+      x = long,
+      y = lat,
+      group = interaction(sa2_name_2011, polygon)
+    ),
+    fill = "white",
+    colour = "lightgrey",
+    data = fort_tas
+  ) +
+  geom_polygon(aes(
+    x = long,
+    y = lat,
+    group = hex_id,
+    fill = rownumber
+  ),
+  data = fort_hex) +
+  scale_fill_distiller("", palette = "PRGn") +
+  coord_equal() + theme_void()
+tas_hexmap
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+###############################################################################
+
+aus_grid <- gridExtra::grid.arrange(aus_ggchoro, aus_ggcont, aus_ggncont, aus_ggdorl, nrow = 2)
+
+aus_grid
+ggsave(filename = "figures/aus_grid.png", plot = aus_grid,
+  device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
+\end{Sinput}
+\end{Schunk}
 
@@
 \centering
-\includegraphics[width=14cm]{figs/qld_grid.pdf}
-\caption{\label{fig:qld_grid}A collection of alternative maps of the Statistical Areas of Australia at Level 2.
+\includegraphics[width=14cm]{figs/nsw_grid.png}
+\caption{\label{fig:nsw_grid}A collection of alternative maps of the Statistical Areas of Australia at Level 2.
 The colours communicate the value of the estimated SIR of Melanoma for males, ranging from much lower than average (blue) to much higher than average (red)}
@@
 connection in the transformed display. The contiguous cartogram
-displayed in figure \ref{fig:qld_grid}b) draws attention to smaller
+displayed in figure \ref{fig:nsw_grid}b) draws attention to smaller
 geographic units when they are rescaled according to the population
@@
 far from their neighbours \citep{TVSSS}. This shown in the northern SA2s
-of Queensland with an average (yellow) estimated SIR of Melanoma for
-males.
+of New South Wales with an average (yellow) estimated SIR of Melanoma
+for males.
 
-The non-contiguous cartogram in figure \ref{fig:qld_grid}c) also uses
+The non-contiguous cartogram in figure \ref{fig:nsw_grid}c) also uses
 the population to rescale the geographic units. Unlike the contiguous
@@
 between large rural areas and small urban areas means that the city of
-Brisbane, shown in the inset map looks reasonable, but these units are
-not visible in the context of the Queensland state map. Depending on the
-difference between the population and geographic land size, the amount
-of white space can also prevent meaningful understanding of the
+Hobart, shown in the inset map looks reasonable, but these units are not
+visible in the context of the New South Wales state map. Depending on
+the difference between the population and geographic land size, the
+amount of white space can also prevent meaningful understanding of the
 distribution \citep{TVSSS}.
@@
 size of the circle is scaled according to the population value of each
-area \citep{ACTUC}. Figure \ref{fig:qld_grid}d) shows the Queensland SA2
-areas as an individual circle located as close as possible to the
-geographic centroid location. This map draws attention to the collection
-of coastal cities in Queensland that were not apparent in figure
-\ref{fig:qld_grid} a), b) or c).
+area \citep{ACTUC}. Figure \ref{fig:nsw_grid}d) shows the New South
+Wales SA2 areas as an individual circle located as close as possible to
+the geographic centroid location. This map draws attention to the
+collection of coastal cities in New South Wales that were not apparent
+in figure \ref{fig:nsw_grid} a), b) or c).
 
@@
 \begin{figure}
-\includegraphics[width=14cm]{figs/flowchart.pdf}
+\includegraphics[width=14cm]{figs/flowchart.png}
 \caption{\label{fig:sugarbag_flow}A flow diagram detailing the necessary steps to create a hexagon tile map.}
@@
 
-\hypertarget{installation}{%
-\paragraph{Installation}\label{installation}}
-
-The package can be installed from CRAN:
-
-\begin{Schunk}
-\begin{Sinput}
-install.packages("sugarbag")
-\end{Sinput}
-\end{Schunk}
-
-and the development version can be install from the GitHub repository:
-
-\begin{Schunk}
-\begin{Sinput}
-devtools::install_github("srkobakian","sugarbag")
-\end{Sinput}
-\end{Schunk}
-
-Load the library into your R session with:
-
-\begin{Schunk}
-\begin{Sinput}
-library(sugarbag)
-\end{Sinput}
-\end{Schunk}
-
 \hypertarget{creating-a-hexagon-tile-map}{%
@@
 The following code creates the hexagon tile map for all the Statistical
-Areas at Level 2 in Queensland. These steps can be executed by the main
-function, \texttt{create\_hexmap}, or can be implemented separately for
-more flexibility.
+Areas at Level 2 in New South Wales. These steps can be executed by the
+main function, \texttt{create\_hexmap}, or can be implemented separately
+for more flexibility.
 
@@
 
-\begin{Schunk}
-\begin{Sinput}
-## Load data
-qld_sa2 <- absmapsdata::sa22011 %>% 
-  filter(state_name_2011 == "Queensland")
-
-## Create centroids set
-centroids <- create_centroids(qld_sa2, "sa2_name_2011")
-
-## Create hexagon grid
-grid <- create_grid(centroids = centroids,
-                    hex_size = 0.12,
-                    buffer_dist = 1.2)
-
-## Allocate polygon centroids to hexagon grid points
-hex_allocated <- allocate(
-  centroids = centroids,
-  hex_grid = grid,
-  sf_id = "sa2_name_2011",
-  ## same column used in create_centroids
-  hex_size = 0.12,
-  ## same size used in create_grid
-  hex_filter = 10,
-  use_neighbours = qld_sa2,
-  focal_points = capital_cities %>%
-    filter(points == "Brisbane"),
-  width = 35,
-  verbose = FALSE
-)
-
-## Prepare to plot
-fort_hex <- fortify_hexagon(data = hex_allocated,
-                            sf_id = "sa2_name_2011",
-                            hex_size = 0.12)
-
-fort_qld <- qld_sa2 %>%
-  fortify_sfc()
-
-## Make a plot
-library(ggplot2)
-qld_hexmap <- ggplot() +
-  geom_polygon(aes(
-      x = long,
-      y = lat,
-      group = interaction(sa2_name_2011, polygon)
-    ),
-    fill = "white",
-    colour = "lightgrey",
-    data = fort_qld
-  ) +
-  geom_polygon(aes(
-    x = long,
-    y = lat,
-    group = hex_id,
-    fill = rownumber
-  ),
-  data = fort_hex) +
-  scale_fill_distiller("", palette = "PRGn") +
-  coord_equal() + theme_void()
-qld_hexmap
-\end{Sinput}
-\end{Schunk}
-
 \begin{figure}[h]
 \centering
-\includegraphics[width=14cm]{figs/aus_gghexmap.pdf}
+\includegraphics[width=14cm]{figs/aus_gghexmap.png}
 \caption{\label{fig:melanoma-hex}A hexagon tile map of the Statistical Areas of Australia at Level 2.
@@
 The polygon set of Statistical Areas at Level 2 (SA2) \citep{abs2011} of
-Queensland in 2011 is provided with the \texttt{sugarbag} package as
-\texttt{tas\_sa2}. A single column of the data set is used to identify
-the unique areas. In this case, the unique SA2 names for each SA2 have
-been used.
+New South Wales in 2011 is provided with the \texttt{sugarbag} package
+as \texttt{tas\_sa2}. A single column of the data set is used to
+identify the unique areas. In this case, the unique SA2 names for each
+SA2 have been used.
 
@@
 used as focal points to allocate each geographic area around the closest
-capital city. Brisbane will be the common focal point, as this example
-uses only the areas in the state of Queensland.
+capital city. Hobart will be the common focal point, as this example
+uses only the areas in the state of New South Wales.
 
@@
 \centering
-\includegraphics[width=14cm]{figs/1centroids.pdf}
-\caption{\label{fig:centroids_plot}The geographic shapes of the Statistical Areas of Queensland at Level 2. The points show the locations of the centroids of the SA2 areas.}
+\includegraphics[width=14cm]{figs/1centroids.png}
+\caption{\label{fig:centroids_plot}The geographic shapes of the Statistical Areas of New South Wales at Level 2. The points show the locations of the centroids of the SA2 areas.}
 \end{figure}
@@
 \centering
-\includegraphics[width=16cm]{figs/2grid.pdf}
+\includegraphics[width=16cm]{figs/2grid.png}
 \caption{\label{fig:grid2}Grid points to create a hexagon tile map.}
@@
 available compared to the South-East region containing the city of
-Brisbane.
+Hobart.
 
@@
 \centering
-\includegraphics[width=10cm]{figs/3grid.pdf}
+\includegraphics[width=10cm]{figs/3grid.png}
 \caption{\label{fig:filter-grid}The remaining hexagon locations from all the possible points in the initial grid after the buffer is applied.
@@
 polygon data set. To minimise time taken for this step only one option
-is provided, Queensland's capital city Brisbane. The order for
+is provided, New South Wales's capital city Hobart. The order for
 allocation is determined by the distance between the polygon centroid
@@
 \centering
-\includegraphics[width=16cm]{figs/4grid.pdf}
+\includegraphics[width=16cm]{figs/4grid.png}
 \caption{\label{fig:buffers}The remaining available hexagon locations after filtering for the grid points within a square distance, then circular around the centroid.}
@@
 \centering
-\includegraphics[width=16cm]{figs/5allocate.pdf}
+\includegraphics[width=16cm]{figs/5allocate.png}
 \caption{\label{fig:angles}The remaining available hexagon locations after filtering for grid points within the angle from the focal point to the centroid.}
@@
 \centering
-\includegraphics[width=16cm]{figs/6allocate.pdf}
-\caption{\label{fig:buffs}A complete hexagon tile map of Queensland.}
+\includegraphics[width=16cm]{figs/6allocate.png}
+\caption{\label{fig:buffs}A complete hexagon tile map of New South Wales.}
 \end{figure}
 
-A complete hexagon tile map of Queensland is created by applying the
-algorithm steps to each centroid. The hexagon tile map visualisation is
-used below to visualise the Australian Cancer Atlas data \citep{TACA}.
-Two views of the same data are produced by filling according to the Lung
-Cancer Standardised Incidence Rates (SIRs) downloaded from the
-Australian Cancer Atlas site. This small example in Figure \ref{fig:sir}
-shows the group of blue areas in the Brisbane CBD more prominently in
-the hexagon tile map (b). The small red areas visible in the choropleth
-map (a) along the north coast are much larger in the hexagon tile maps.
-The hexagon tile map shows less yellow, this no longer overwhelms the
-map space with the information regarding the rural areas.
+A complete hexagon tile map of New South Wales is created by applying
+the algorithm steps to each centroid. The hexagon tile map visualisation
+is used below to visualise the Australian Cancer Atlas data
+\citep{TACA}. Two views of the same data are produced by filling
+according to the thyroid Cancer Standardised Incidence Rates (SIRs)
+downloaded from the Australian Cancer Atlas site. This small example in
+Figure \ref{fig:sir} shows the group of blue areas in the Hobart CBD
+more prominently in the hexagon tile map (b). The small red areas
+visible in the choropleth map (a) along the north coast are much larger
+in the hexagon tile maps. The hexagon tile map shows less yellow, this
+no longer overwhelms the map space with the information regarding the
+rural areas.
 
@@
 \centering
-\includegraphics[width=14cm]{figs/7SIR.pdf}
+\includegraphics[width=14cm]{figs/7SIR.png}
 \caption{\label{fig:sir}The Australian Cancer Atlas data displayed on a choropleth and hexagon tile map.
@@
 Australian capital cities, as it draws attention to the many communities
-in Sydney, Melbourne and Brisbane. This display also highlights the
+in Sydney, Melbourne and Hobart. This display also highlights the
 disparity in the burden of Melanoma cancer for males in the communities
 of these three cities. There are several collections of red hexagons in
-Brisbane that draw attention and they represent the communities with
-much higher rates of diagnosis than the Australian average. The
-communities south of Brisbane show a gradient of colour as the values
-progress from higher than average, to much lower than average for the
-communities closer to the Sydney CBD. This pattern progresses into the
-communities with lower than average rates in Melbourne and Tasmania.
+Hobart that draw attention and they represent the communities with much
+higher rates of diagnosis than the Australian average. The communities
+south of Hobart show a gradient of colour as the values progress from
+higher than average, to much lower than average for the communities
+closer to the Sydney CBD. This pattern progresses into the communities
+with lower than average rates in Melbourne and New South Wales.
 
@@
 higher than average rates in Sydney draw more attention in the hexagon
-tile map display unlike the red and orange areas in the city of Brisbane
+tile map display unlike the red and orange areas in the city of Hobart
 that draw attention in both displays.
@@
 \centering
-\includegraphics[width=14cm]{figs/aus_gghexmap.pdf}
+\includegraphics[width=14cm]{figs/aus_gghexmap.png}
 \caption{\label{fig:melanoma-geo}A hexagon tile map of the Statistical Areas of Australia at Level 2.
@@
 displays, which can be done using the \texttt{sf\_id} variable, such as
-the SA2 name. The animation\footnote{This animation can be viewed at:
-  \url{https://sugarbagjss.netlify.com/}} connecting these two displays
-will highlight the rapid growth of the inner-city areas that emphasises
-the density of the communities. The hexagons that move the furthest will
-move rapidly in the animation. The rapid decreases of the large rural
-areas also show how much greater the landmass of Statistical Areas can
-be.
+the SA2 name. The animation connecting these two displays will highlight
+the rapid growth of the inner-city areas that emphasises the density of
+the communities. The hexagons that move the furthest will move rapidly
+in the animation. The rapid decreases of the large rural areas also show
+how much greater the landmass of Statistical Areas can be.
 
@@
 neighbourhood boundary connections. This map algorithm is implemented in
-the \texttt{sugarbag} \citep{sugarbag} package written for \texttt{R}
-\citep{R}. The \texttt{sugarbag} package creates tessellated hexagon
-tile maps. The Australian application preserves the spatial
-relationships, emphasising capital cities. The hexagon tile map is a
-visualisation solution that highlights spatial distributions.
+the \texttt{sugarbag} \citep{sugarbag} package written for \texttt{R}.
+The \texttt{sugarbag} package creates tessellated hexagon tile maps. The
+Australian application preserves the spatial relationships, emphasising
+capital cities. The hexagon tile map is a visualisation solution that
+highlights spatial distributions.
 
@@
 inner city areas may have been noticed by viewers, but the hexagon tile
-map display emphasises them. The communities in northern Queensland and
-the Northern territory do not draw attention because of their size as in
-the choropleth, but their colour is still noticeably below average when
-contrasted with the hexagons further south.
+map display emphasises them. The communities in northern New South Wales
+and the Northern territory do not draw attention because of their size
+as in the choropleth, but their colour is still noticeably below average
+when contrasted with the hexagons further south.
 
@@
 connected to those around them. As seen in the Dorling cartogram in
-figure \ref{fig:qld_grid}c), the tessellation that allows boundary
+figure \ref{fig:nsw_grid}c), the tessellation that allows boundary
 connections was not imposed for rural communities, where centroid of the
 geographic unit was located far from others, a feature that allows
-distant but dense populations of the coastal towns of Queensland to be
-recognised.
+distant but dense populations of the coastal towns of New South Wales to
+be recognised.
 
@@
 many geographic units.
+
+\hypertarget{installation}{%
+\paragraph{Installation}\label{installation}}
+
+The package can be installed from CRAN:
+
+\begin{Schunk}
+\begin{Sinput}
+install.packages("sugarbag")
+\end{Sinput}
+\end{Schunk}
+
+and the development version can be install from the GitHub repository:
+
+\begin{Schunk}
+\begin{Sinput}
+devtools::install_github("srkobakian","sugarbag")
+\end{Sinput}
+\end{Schunk}
+
+Load the library into your R session with:
+
+\begin{Schunk}
+\begin{Sinput}
+library(sugarbag)
+\end{Sinput}
+\end{Schunk}
 

### 2020-10-02 kobakian_cook.Rmd
Potentially use NSW for thyroid example?

--- 2020-09-30 algorithm.Rmd
@@
 library(knitcitations)
+library(kableExtra)
 library(RefManageR)
+library(sp)
 library(sf)
 library(sugarbag)
-library(kableExtra)
+library(absmapsdata)
+library(tidyverse)
+library(cartogram)
+library(ggthemes)
+library(cowplot)
 
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
+knitr::opts_chunk$set(warning = FALSE, message = FALSE, eval = FALSE)
 options("citation_format" = "pandoc")
 BibOptions(check.entries = FALSE, style = "markdown")
+
+invthm <- theme_map() + 
+  theme(
+    panel.background = element_rect(fill = "transparent", colour = NA), 
+    plot.background = element_rect(fill = "transparent", colour = NA),
+    legend.background = element_rect(fill = "transparent", colour = NA),
+    legend.key = element_rect(fill = "transparent", colour = NA),
+    text = element_text(colour = "white"),
+    axis.text = element_text(colour = "white")
+  )
+
+# function to allocate colours to regions
+aus_colours <- function(sir_p50){
+  value <- case_when(
+    sir_p50 <  0.74 ~ "#33809d",
+    sir_p50 >= 0.74 & sir_p50 < 0.98 ~ "#aec6c7",
+    sir_p50 >= 0.98 & sir_p50 < 1.05 ~ "#fff4bc",
+    sir_p50 >= 1.05 & sir_p50 < 1.45 ~ "#ff9a64",
+    sir_p50 >= 1.45 ~ "#ff3500",
+    TRUE ~ "#FFFFFF")
+  return(value)
+}
+
 ```
@@
 In many countries, residents are increasingly gathering to live in urban areas around major cities [@ACTUC].
-The creation of approximately equal population areas results in dramatically different square meterage of the geographic units.
-The geographic units are usually administrative, such as states or electorates.
+The creation of approximately equal population areas results in dramatically different square meterage of the administrative geographic units, such as states or electorates.
 The units are filled with colour to represent the value of the statistic for each unit [@EI].
@@
 The Australian choropleth map display draws attention to the expanse of light blue areas across the rural communities in all states.
-The SA2s around Brisbane stand out as more orange and red.
+The SA2s around Hobart stand out as more orange and red.
 To create this choropleth map the SA2 polygons for 2011 from the Australian Bureau of Statistics.
@@
 These alternative map displays focus on the relationship between neighbours, attempting to preserve connections, and disregard the unique shapes of the administrative boundaries.
-Figure \ref{fig:qld_grid} shows a collection of alternative map displays, this includes a) a contiguous cartogram, b) a non-contiguous cartogram, c) a Dorling cartogram and d) a hexagon tile map.
+Figure \ref{fig:nsw_grid} shows a collection of alternative map displays, this includes a) a contiguous cartogram, b) a non-contiguous cartogram, c) a Dorling cartogram and d) a hexagon tile map.
 Each Statistical Area at Level 2 (SA2) [@abs2011] was designed to represent a community.
@@
 This presents an opportunity for explicit map transformations to improve communication of distributions [@CBATCC].
-In figure \ref{fig:qld_grid}a) the choropleth map is presented with the alternative maps to allow for comparisons to be made.
+In figure \ref{fig:nsw_grid}a) the choropleth map is presented with the alternative maps to allow for comparisons to be made.
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=14cm]{figs/qld_grid.pdf}
-\caption{\label{fig:qld_grid}A collection of alternative maps of the Statistical Areas of Australia at Level 2.
-The colours communicate the value of the estimated SIR of Melanoma for males, ranging from much lower than average (blue) to much higher than average (red)}
-\end{figure}
+```{r}
+states <- absmapsdata::state2011 %>% 
+  rmapshaper::ms_simplify(keep = 0.25, keep_shapes = TRUE) %>% 
+  filter(!state_name_2011 == "Other Territories")
+
+sa2 <- absmapsdata::sa22011 %>% 
+  filter(state_name_2011 == "New South Wales") %>% 
+  filter(!st_is_empty(geometry))
+
+# sa2 <- sa2 %>% rmapshaper::ms_simplify(keep = 0.05, keep_shapes = TRUE)
+
+SIR <- read_csv("data/SIR Downloadable Data.csv") %>% 
+  filter(SA2_name %in% sa2$sa2_name_2011) %>% 
+  dplyr::select(Cancer_name, SA2_name, Sex_name, p50) %>% 
+  filter(Cancer_name == "Thyroid", Sex_name == "Females")
+ERP <- read_csv("data/ERP.csv") %>%
+  filter(REGIONTYPE == "SA2", Time == 2011, Region %in% SIR$SA2_name) %>% 
+  dplyr::select(Region, Value)
+
+# Alternative maps
+# Join with sa2 sf object
+sa2thyroid_ERP <- SIR %>% 
+  left_join(sa2, ., by = c("sa2_name_2011" = "SA2_name")) %>%
+  left_join(., ERP %>% 
+              dplyr::select(Region, 
+              Population = Value), by = c("sa2_name_2011"= "Region")) %>% 
+  filter(!st_is_empty(geometry))
+
+sa2thyroid_ERP <- sa2thyroid_ERP %>% 
+  filter(!is.na(Population)) %>% 
+  mutate(SIR = map_chr(p50, aus_colours)) %>% 
+  st_as_sf()
+
+aus_ggchoro <- ggplot(sa2thyroid_ERP) + 
+  #geom_sf(fill = "lightgrey", data = states) + 
+  geom_sf(aes(fill = SIR)) + 
+  scale_fill_identity()
+```
+
+```{r alternatives}
+
+###############################################################################
+
+sa2thyroid_ERP <- st_transform(sa2thyroid_ERP, 3112)
+sa2thyroid_ERP <- sa2thyroid_ERP %>% 
+  mutate(sva = sqrt(as.numeric(Population)/as.numeric(albers_sqkm)))
+
+###############################################################################
+# Contiguous Cartograms
+
+cont <- sa2thyroid_ERP %>% 
+  mutate(Population = Population + 1) %>% 
+  cartogram_cont(., weight = "Population", itermax = 20) %>%
+  st_as_sf()
+
+save(cont, file = "data/cont.rda")
+load("data/cont.rda")
+
+aus_ggcont <- ggplot(cont) + 
+  geom_sf(aes(fill = SIR), colour = NA) + 
+  scale_fill_identity() + 
+  invthm + guides(fill=FALSE)
+aus_ggcont
+
+ggsave(filename = "figures/aus_ggcont.png", plot = aus_ggcont,
+       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
+
+```
+
+```{r}
+
+###############################################################################
+# Non - Contiguous Cartograms
+
+ncont <- cartogram_ncont(sa2thyroid_ERP, k = 1/10,
+                         weight = "Population") %>% st_as_sf()
+
+save(ncont, file = "data/ncont.rda")
+load("data/ncont.rda")
+
+aus_ggncont <- ggplot(ncont) + 
+  geom_sf(aes(fill = SIR), colour = NA) + 
+  scale_fill_identity() + 
+  invthm + guides(fill=FALSE)
+aus_ggncont
+
+ggsave(filename = "figures/aus_ggncont.png", plot = aus_ggncont,
+       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
+
+```
+
+```{r}
+
+###############################################################################
+# Non - Contiguous Dorling Cartograms
+
+dorl <- sa2lung_ERP %>%
+  mutate(pop = (Population/max(Population))*10) %>% 
+  cartogram_dorling(., k = 0.01, weight = "pop", m_weight = 1) %>% st_as_sf()
+d <- st_bbox(dorl)
+aus_ggdorl <- ggplot(dorl) + 
+  geom_sf(aes(fill = SIR)) + 
+  scale_fill_identity()+
+  invthm + guides(fill = FALSE)
+aus_ggdorl
+
+ggsave(filename = "figures/aus_ggdorl.png", plot = aus_ggdorl,
+       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
+
+```
+
+```{r full_hexmapcode}
+## Load data
+tas_sa2 <- absmapsdata::sa22011 %>% 
+  filter(state_name_2011 == "New South Wales")
+
+## Create centroids set
+centroids <- create_centroids(tas_sa2, "sa2_name_2011")
+
+## Create hexagon grid
+grid <- create_grid(centroids = centroids,
+                    hex_size = 0.12,
+                    buffer_dist = 1.2)
+
+## Allocate polygon centroids to hexagon grid points
+hex_allocated <- allocate(
+  centroids = centroids,
+  hex_grid = grid,
+  sf_id = "sa2_name_2011",
+  ## same column used in create_centroids
+  hex_size = 0.12,
+  ## same size used in create_grid
+  hex_filter = 10,
+  use_neighbours = tas_sa2,
+  focal_points = capital_cities %>%
+    filter(points == "Hobart"),
+  width = 35,
+  verbose = FALSE
+)
+
+## Prepare to plot
+fort_hex <- fortify_hexagon(data = hex_allocated,
+                            sf_id = "sa2_name_2011",
+                            hex_size = 0.12)
+
+fort_tas <- tas_sa2 %>%
+  fortify_sfc()
+
+## Make a plot
+library(ggplot2)
+tas_hexmap <- ggplot() +
+  geom_polygon(aes(
+      x = long,
+      y = lat,
+      group = interaction(sa2_name_2011, polygon)
+    ),
+    fill = "white",
+    colour = "lightgrey",
+    data = fort_tas
+  ) +
+  geom_polygon(aes(
+    x = long,
+    y = lat,
+    group = hex_id,
+    fill = rownumber
+  ),
+  data = fort_hex) +
+  scale_fill_distiller("", palette = "PRGn") +
+  coord_equal() + theme_void()
+tas_hexmap
+```
+
+```{r mapgrid}
+
+###############################################################################
+
+aus_grid <- gridExtra::grid.arrange(aus_ggchoro, aus_ggcont, aus_ggncont, aus_ggdorl, nrow = 2)
+
+aus_grid
+ggsave(filename = "figures/aus_grid.png", plot = aus_grid,
+  device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
+```
+
+<!-- \begin{figure}[h] -->
+<!-- \centering -->
+<!-- \includegraphics[width=14cm]{figs/nsw_grid.png} -->
+<!-- \caption{\label{fig:nsw_grid}A collection of alternative maps of the Statistical Areas of Australia at Level 2.
+The colours communicate the value of the estimated SIR of Melanoma for males, ranging from much lower than average (blue) to much higher than average (red)} -->
+<!-- \end{figure} -->
 
@@
 The impact of a disease over connected communities can be seen by allowing the boundaries to maintain connection in the transformed display.
-The contiguous cartogram displayed in figure \ref{fig:qld_grid}b) draws attention to smaller geographic units when they are rescaled according to the population [@DMAHP].
+The contiguous cartogram displayed in figure \ref{fig:nsw_grid}b) draws attention to smaller geographic units when they are rescaled according to the population [@DMAHP].
 These new shapes can now be coloured to represent a second variable.
 This display can create twisted and unfamiliar shapes from the geographic units as the algorithms must satisfy the topology conditions, especially when there are communities located geographically far from their neighbours [@TVSSS].
-This shown in the northern SA2s of Queensland with an average (yellow) estimated SIR of Melanoma for males.
+This shown in the northern SA2s of New South Wales with an average (yellow) estimated SIR of Melanoma for males.
 
 <!-- non-contiguous -->
-The non-contiguous cartogram in figure \ref{fig:qld_grid}c) also uses the population to rescale the geographic units.
+The non-contiguous cartogram in figure \ref{fig:nsw_grid}c) also uses the population to rescale the geographic units.
 Unlike the contiguous cartogram, the SA2 areas maintain their geographic shape, but they may not retain the connection with their neighbours.
 The population of the SA2 areas is used to scale the geographic units in the non-contiguous cartogram [@NAC].
-The amount of white space can be meaningful in non-contiguous cartograms [@ECGC], in this example the disparity between large rural areas and small urban areas means that the city of Brisbane, shown in the inset map looks reasonable, but these units are not visible in the context of the Queensland state map.
+The amount of white space can be meaningful in non-contiguous cartograms [@ECGC], in this example the disparity between large rural areas and small urban areas means that the city of Hobart, shown in the inset map looks reasonable, but these units are not visible in the context of the New South Wales state map.
 Depending on the difference between the population and geographic land size, the amount of white space can also prevent meaningful understanding of the distribution [@TVSSS].
@@
 The Dorling cartogram presents each geographic unit as a circle, the size of the circle is scaled according to the population value of each area [@ACTUC].
-Figure \ref{fig:qld_grid}d) shows the Queensland SA2 areas as an individual circle located as close as possible to the geographic centroid location.
-This map draws attention to the collection of coastal cities in Queensland that were not apparent in figure \ref{fig:qld_grid} a), b) or c).
+Figure \ref{fig:nsw_grid}d) shows the New South Wales SA2 areas as an individual circle located as close as possible to the geographic centroid location.
+This map draws attention to the collection of coastal cities in New South Wales that were not apparent in figure \ref{fig:nsw_grid} a), b) or c).
 
@@
 
-#### Installation
-
-The package can be installed from CRAN:
-
-```{r eval=FALSE}
-install.packages("sugarbag")
-```
-
-and the development version can be install from the GitHub repository:
-
-```{r eval=FALSE}
-devtools::install_github("srkobakian","sugarbag")
-```
-
-Load the library into your R session with:
-
-```{r}
-library(sugarbag)
-```
-
 #### Creating a hexagon tile map
 
-The following code creates the hexagon tile map for all the Statistical Areas at Level 2 in Queensland.
+The following code creates the hexagon tile map for all the Statistical Areas at Level 2 in New South Wales.
 These steps can be executed by the main function, `create_hexmap`, or can be implemented separately for more flexibility.
@@
 
-```{r full_hexmapcode, echo = TRUE, warning = FALSE, message = FALSE, eval=FALSE}
-## Load data
-qld_sa2 <- absmapsdata::sa22011 %>% 
-  filter(state_name_2011 == "Queensland")
-
-## Create centroids set
-centroids <- create_centroids(qld_sa2, "sa2_name_2011")
-
-## Create hexagon grid
-grid <- create_grid(centroids = centroids,
-                    hex_size = 0.12,
-                    buffer_dist = 1.2)
-
-## Allocate polygon centroids to hexagon grid points
-hex_allocated <- allocate(
-  centroids = centroids,
-  hex_grid = grid,
-  sf_id = "sa2_name_2011",
-  ## same column used in create_centroids
-  hex_size = 0.12,
-  ## same size used in create_grid
-  hex_filter = 10,
-  use_neighbours = qld_sa2,
-  focal_points = capital_cities %>%
-    filter(points == "Brisbane"),
-  width = 35,
-  verbose = FALSE
-)
-
-## Prepare to plot
-fort_hex <- fortify_hexagon(data = hex_allocated,
-                            sf_id = "sa2_name_2011",
-                            hex_size = 0.12)
-
-fort_qld <- qld_sa2 %>%
-  fortify_sfc()
-
-## Make a plot
-library(ggplot2)
-qld_hexmap <- ggplot() +
-  geom_polygon(aes(
-      x = long,
-      y = lat,
-      group = interaction(sa2_name_2011, polygon)
-    ),
-    fill = "white",
-    colour = "lightgrey",
-    data = fort_qld
-  ) +
-  geom_polygon(aes(
-    x = long,
-    y = lat,
-    group = hex_id,
-    fill = rownumber
-  ),
-  data = fort_hex) +
-  scale_fill_distiller("", palette = "PRGn") +
-  coord_equal() + theme_void()
-qld_hexmap
-```
-
 \begin{figure}[h]
 \centering
-\includegraphics[width=14cm]{figs/aus_gghexmap.pdf}
+\includegraphics[width=14cm]{figs/aus_gghexmap.png}
 \caption{\label{fig:melanoma-hex}A hexagon tile map of the Statistical Areas of Australia at Level 2.
@@
 
-The polygon set of Statistical Areas at Level 2 (SA2) [@abs2011] of Queensland in 2011 is provided with the `sugarbag` package as `tas_sa2`. 
+The polygon set of Statistical Areas at Level 2 (SA2) [@abs2011] of New South Wales in 2011 is provided with the `sugarbag` package as `tas_sa2`. 
 A single column of the data set is used to identify the unique areas. 
@@
 The longitude and latitude centre of the capital cities of Australia are used as focal points to allocate each geographic area around the closest capital city.
-Brisbane will be the common focal point, as this example uses only the areas in the state of Queensland.
+Hobart will be the common focal point, as this example uses only the areas in the state of New South Wales.
 
@@
 <!-- ```{r grid2, fig.cap = "Grid points to create a tile map.", out.width = "100%", echo = FALSE} -->
-<!-- knitr::include_graphics(path = "figures/2grid.pdf") -->
+<!-- knitr::include_graphics(path = "figures/2grid.png") -->
 <!-- ``` -->
@@
 The grid points are kept only if they fall between the rolling average of the minimum and maximum centroid values after accounting for the buffer distance, for each row and column of the grid.
-The sparsely populated South-West region of National Park has much fewer points available compared to the South-East region containing the city of Brisbane.
+The sparsely populated South-West region of National Park has much fewer points available compared to the South-East region containing the city of Hobart.
 
@@
 The rolling windows show the collections of rows and columns used to filter the hexagon locations.", echo = FALSE, out.width = "100%"} -->
-<!-- knitr::include_graphics(path = "figures/3grid.pdf", dpi = 300) -->
+<!-- knitr::include_graphics(path = "figures/3grid.png", dpi = 300) -->
 <!-- ``` -->
@@
 The name of the closest focal point, and the distance and angle from focal point to polygon centroid is joined to polygon data set.
-To minimise time taken for this step only one option is provided, Queensland's capital city Brisbane.
+To minimise time taken for this step only one option is provided, New South Wales's capital city Hobart.
 The order for allocation is determined by the distance between the polygon centroid and it's closest focal point.
@@
 <!-- ```{r buffers, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, out.width = "100%"} -->
-<!-- knitr::include_graphics(path = "figures/4grid.pdf") -->
+<!-- knitr::include_graphics(path = "figures/4grid.png") -->
 <!-- ``` -->
@@
 
-<!-- ```{r buffs, fig.cap = "A complete hexagon tile map of Queensland.", out.width = "100%", echo = FALSE} -->
+<!-- ```{r buffs, fig.cap = "A complete hexagon tile map of New South Wales.", out.width = "100%", echo = FALSE} -->
 <!-- knitr::include_graphics(path = "figures/6allocate.png") -->
@@
 \centering
-\includegraphics[width=16cm]{figs/6allocate.pdf}
-\caption{\label{fig:buffs}A complete hexagon tile map of Queensland.}
+\includegraphics[width=16cm]{figs/6allocate.png}
+\caption{\label{fig:buffs}A complete hexagon tile map of New South Wales.}
 \end{figure}
 
-A complete hexagon tile map of Queensland is created by applying the algorithm steps to each centroid.
+A complete hexagon tile map of New South Wales is created by applying the algorithm steps to each centroid.
 The hexagon tile map visualisation is used below to visualise the Australian Cancer Atlas data [@TACA].
-Two views of the same data are produced by filling according to the Lung Cancer Standardised Incidence Rates (SIRs) downloaded from the Australian Cancer Atlas site.
-This small example in Figure \ref{fig:sir} shows the group of blue areas in the Brisbane CBD more prominently in the hexagon tile map (b).
+Two views of the same data are produced by filling according to the thyroid Cancer Standardised Incidence Rates (SIRs) downloaded from the Australian Cancer Atlas site.
+This small example in Figure \ref{fig:sir} shows the group of blue areas in the Hobart CBD more prominently in the hexagon tile map (b).
 The small red areas visible in the choropleth map (a) along the north coast are much larger in the hexagon tile maps.
@@
 This algorithm has been applied to the complete set of all Australian Statistical Areas at Level 2.
-This display highlights the density of Australian capital cities, as it draws attention to the many communities in Sydney, Melbourne and Brisbane.
+This display highlights the density of Australian capital cities, as it draws attention to the many communities in Sydney, Melbourne and Hobart.
 This display also highlights the disparity in the burden of Melanoma cancer for males in the communities of these three cities.
-There are several collections of red hexagons in Brisbane that draw attention and they represent the communities with much higher rates of diagnosis than the Australian average.
-The communities south of Brisbane show a gradient of colour as the values progress from higher than average, to much lower than average for the communities closer to the Sydney CBD.
-This pattern progresses into the communities with lower than average rates in Melbourne and Tasmania.
+There are several collections of red hexagons in Hobart that draw attention and they represent the communities with much higher rates of diagnosis than the Australian average.
+The communities south of Hobart show a gradient of colour as the values progress from higher than average, to much lower than average for the communities closer to the Sydney CBD.
+This pattern progresses into the communities with lower than average rates in Melbourne and New South Wales.
 
 Compared to the choropleth map display, the low rates in the rural Australian communities are no longer dominating the display.
-The much higher than average rates in Sydney draw more attention in the hexagon tile map display unlike the red and orange areas in the city of Brisbane that draw attention in both displays.
+The much higher than average rates in Sydney draw more attention in the hexagon tile map display unlike the red and orange areas in the city of Hobart that draw attention in both displays.
 
@@
 It requires connecting the polygons for each area in two displays, which can be done using the `sf_id` variable, such as the SA2 name.
-The animation^[This animation can be viewed at: https://sugarbagjss.netlify.com/] connecting these two displays will highlight the rapid growth of the inner-city areas that emphasises the density of the communities.
+The animation connecting these two displays will highlight the rapid growth of the inner-city areas that emphasises the density of the communities.
 The hexagons that move the furthest will move rapidly in the animation.
@@
 The solution to this visualisation problem has equally sized areas, with neighbourhood boundary connections.
-This map algorithm is implemented in the `sugarbag` [@sugarbag] package written for `R` [@R].
+This map algorithm is implemented in the `sugarbag` [@sugarbag] package written for `R`.
 The `sugarbag` package creates tessellated hexagon tile maps.
@@
 With careful consideration of the choropleth map, the small geographic inner city areas may have been noticed by viewers, but the hexagon tile map display emphasises them.
-The communities in northern Queensland and the Northern territory do not draw attention because of their size as in the choropleth, but their colour is still noticeably below average when contrasted with the hexagons further south.
+The communities in northern New South Wales and the Northern territory do not draw attention because of their size as in the choropleth, but their colour is still noticeably below average when contrasted with the hexagons further south.
 
@@
 The tessellation crated by adjoining hexagons for densely populated areas is helpful as it shows that most communities are not islands onto themselves, but are intrinsically connected to those around them.
-As seen in the Dorling cartogram in figure \ref{fig:qld_grid}c), the tessellation that allows boundary connections was not imposed for rural communities, where centroid of the geographic unit was located far from others, a feature that allows distant but dense populations of the coastal towns of Queensland to be recognised.
+As seen in the Dorling cartogram in figure \ref{fig:nsw_grid}c), the tessellation that allows boundary connections was not imposed for rural communities, where centroid of the geographic unit was located far from others, a feature that allows distant but dense populations of the coastal towns of New South Wales to be recognised.
 
@@
 This algorithm is an effective start to creating hexagon tile maps for many geographic units.
+
+#### Installation
+
+The package can be installed from CRAN:
+
+```{r eval=FALSE}
+install.packages("sugarbag")
+```
+
+and the development version can be install from the GitHub repository:
+
+```{r eval=FALSE}
+devtools::install_github("srkobakian","sugarbag")
+```
+
+Load the library into your R session with:
+
+```{r}
+library(sugarbag)
+```

### 2020-10-02 algorithm.R

@@ -1,108 +1,0 @@
-## ----setup, echo=FALSE, message=FALSE, warning=FALSE, comment = FALSE----
-library(knitcitations)
-library(RefManageR)
-library(sf)
-library(sugarbag)
-library(kableExtra)
- 
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-options("citation_format" = "pandoc")
-BibOptions(check.entries = FALSE, style = "markdown")
-
-
-## ----eval=FALSE-------------------------------------------------------
-## install.packages("sugarbag")
-
-
-## ----eval=FALSE-------------------------------------------------------
-## devtools::install_github("srkobakian","sugarbag")
-
-
-## ---------------------------------------------------------------------
-library(sugarbag)
-
-
-## ----full_hexmapcode, echo = TRUE, warning = FALSE, message = FALSE, eval=FALSE----
-## ## Load data
-## qld_sa2 <- absmapsdata::sa22011 %>%
-##   filter(state_name_2011 == "Queensland")
-## 
-## ## Create centroids set
-## centroids <- create_centroids(qld_sa2, "sa2_name_2011")
-## 
-## ## Create hexagon grid
-## grid <- create_grid(centroids = centroids,
-##                     hex_size = 0.12,
-##                     buffer_dist = 1.2)
-## 
-## ## Allocate polygon centroids to hexagon grid points
-## hex_allocated <- allocate(
-##   centroids = centroids,
-##   hex_grid = grid,
-##   sf_id = "sa2_name_2011",
-##   ## same column used in create_centroids
-##   hex_size = 0.12,
-##   ## same size used in create_grid
-##   hex_filter = 10,
-##   use_neighbours = qld_sa2,
-##   focal_points = capital_cities %>%
-##     filter(points == "Brisbane"),
-##   width = 35,
-##   verbose = FALSE
-## )
-## 
-## ## Prepare to plot
-## fort_hex <- fortify_hexagon(data = hex_allocated,
-##                             sf_id = "sa2_name_2011",
-##                             hex_size = 0.12)
-## 
-## fort_qld <- qld_sa2 %>%
-##   fortify_sfc()
-## 
-## ## Make a plot
-## library(ggplot2)
-## qld_hexmap <- ggplot() +
-##   geom_polygon(aes(
-##       x = long,
-##       y = lat,
-##       group = interaction(sa2_name_2011, polygon)
-##     ),
-##     fill = "white",
-##     colour = "lightgrey",
[…]

### 2020-10-02 figures.R

@@ -1,661 +1,0 @@
-# Young statisticians conference presentation plots
-
-library(absmapsdata)
-library(tidyverse)
-library(cartogram)
-library(ggthemes)
-library(cowplot)
-library(sf)
-library(sp)
-
-### Theme set up
-
-invthm <- theme_map() + 
-  theme(
-    panel.background = element_rect(fill = "transparent", colour = NA), 
-    plot.background = element_rect(fill = "transparent", colour = NA),
-    legend.background = element_rect(fill = "transparent", colour = NA),
-    legend.key = element_rect(fill = "transparent", colour = NA),
-    text = element_text(colour = "white"),
-    axis.text = element_text(colour = "white")
-  )
-
-## States of Australia
-
-states <- absmapsdata::state2011 %>% 
-  filter(state_name_2011 != "Other Territories")
-
-# Act pop out plot
-act_map <- absmapsdata::state2011 %>% 
-  filter(state_name_2011 == "Australian Capital Territory") %>% st_transform(., 3112) %>% 
-  ggplot() + 
-  theme_void() +
-  geom_sf(fill = "white") + 
-  geom_rect(aes(xmin =1323014, xmax = 1404210, ymin=-4132815, ymax=-4026022), fill = NA, colour = "black")
-
-
-# Australian map
-aus_map <- ggplot(states) + 
-  geom_sf(aes(fill = albers_sqkm)) +
-  scale_fill_distiller(type = "seq", palette = "BuGn",  direction = 1, na.value = "light grey") + 
-  theme_void() +
-  coord_sf(crs = 3112) +
-   theme(legend.position ="left", legend.title = element_text("Area (sqkm)"))
-
-ggsave(filename = "figures/aus.png", plot = aus_map,
-  device = "png", bg = "transparent", dpi = 300,  width = 10, height = 8)
-
-# Australian map with pop out
-aus_states <- ggdraw() + 
-  draw_plot(aus_map, 0, 0, 1, 1) +
-  draw_plot(act_map, 0.82, 0.01, 0.17, 0.3)
-
-ggsave(filename = "figures/aus_states.png", plot = aus_states,
-  device = "png", bg = "transparent", dpi = 300,  width = 10, height = 8)
-
-
-###############################################################################
[…]

### 2020-10-02 kobakian-cook.R

@@ -1,0 +1,262 @@
+## ----setup, echo=FALSE, message=FALSE, warning=FALSE, comment = FALSE---------
+library(knitcitations)
+library(kableExtra)
+library(RefManageR)
+library(sp)
+library(sf)
+library(sugarbag)
+library(absmapsdata)
+library(tidyverse)
+library(cartogram)
+library(ggthemes)
+library(cowplot)
+
+knitr::opts_chunk$set(warning = FALSE, message = FALSE, eval = FALSE)
+options("citation_format" = "pandoc")
+BibOptions(check.entries = FALSE, style = "markdown")
+
+
+invthm <- theme_map() + 
+  theme(
+    panel.background = element_rect(fill = "transparent", colour = NA), 
+    plot.background = element_rect(fill = "transparent", colour = NA),
+    legend.background = element_rect(fill = "transparent", colour = NA),
+    legend.key = element_rect(fill = "transparent", colour = NA),
+    text = element_text(colour = "white"),
+    axis.text = element_text(colour = "white")
+  )
+
+
+# function to allocate colours to regions
+aus_colours <- function(sir_p50){
+  value <- case_when(
+    sir_p50 <  0.74 ~ "#33809d",
+    sir_p50 >= 0.74 & sir_p50 < 0.98 ~ "#aec6c7",
+    sir_p50 >= 0.98 & sir_p50 < 1.05 ~ "#fff4bc",
+    sir_p50 >= 1.05 & sir_p50 < 1.45 ~ "#ff9a64",
+    sir_p50 >= 1.45 ~ "#ff3500",
+    TRUE ~ "#FFFFFF")
+  return(value)
+}
+
+
+
+## -----------------------------------------------------------------------------
+states <- absmapsdata::state2011 %>% 
+  rmapshaper::ms_simplify(keep = 0.25, keep_shapes = TRUE) %>% 
+  filter(!state_name_2011 == "Other Territories")
+
+sa2 <- absmapsdata::sa22011 %>% 
+  filter(state_name_2011 == "New South Wales") %>% 
+  filter(!st_is_empty(geometry))
+
+# sa2 <- sa2 %>% rmapshaper::ms_simplify(keep = 0.05, keep_shapes = TRUE)
+
+SIR <- read_csv("data/SIR Downloadable Data.csv") %>% 
+  filter(SA2_name %in% sa2$sa2_name_2011) %>% 
[…]

### 2020-10-02 kobakian_cook.R

@@ -1,0 +1,631 @@
+# Young statisticians conference presentation plots
+
+library(absmapsdata)
+library(tidyverse)
+library(cartogram)
+library(ggthemes)
+library(cowplot)
+library(sf)
+library(sp)
+
+### Theme set up
+
+invthm <- theme_map() + 
+  theme(
+    panel.background = element_rect(fill = "transparent", colour = NA), 
+    plot.background = element_rect(fill = "transparent", colour = NA),
+    legend.background = element_rect(fill = "transparent", colour = NA),
+    legend.key = element_rect(fill = "transparent", colour = NA),
+    text = element_text(colour = "white"),
+    axis.text = element_text(colour = "white")
+  )
+
+## States of Australia
+
+states <- absmapsdata::state2011 %>% 
+  filter(state_name_2011 != "Other Territories")
+
+###############################################################################
+###########################        ABS AREAS        ###########################
+## sa2
+sa2 <- absmapsdata::sa22011 %>% 
+  filter(state_name_2011 != "Other Territories") %>% st_transform(., crs = 3112)
+
+sa2_map <- ggplot(sa2) + 
+  geom_sf(aes(fill = albers_sqkm)) +
+  scale_fill_distiller(type = "seq", palette = "BuGn",  direction = 1, na.value = "light grey") + 
+  theme_void() +
+  coord_sf(crs = 3112) +
+   theme(legend.position ="left", legend.title = element_text("Area (sqkm)"))
+
+ggsave(filename = "figures/aus_sa2.png", plot = sa2_map,
+  device = "png", bg = "transparent", dpi = 300,  width = 10, height = 8)
+
+
+###############################################################################
+###########################     CARTOGRAMS
+# 
+# ERP <- read_csv("data/ERP.csv")
+# 
+# ERP_sa4 <- ERP %>% filter(`Geography Level` == "Statistical Area Level 4", Time == 2011) %>% arrange(`Geography Level`)
+# 
+# aus_ggcont <- ggplot(ERP_sa4) + 
+#   geom_sf(aes(fill = `Age-standardised rate (per 100,000)`)) + 
[…]

### 2020-10-02 sa1 Greater Melb.R

@@ -1,0 +1,52 @@
+
+# create a hexagon map
+library(sugarbag)
+library(sf)
+library(absmapsdata)
+library(ggplot2)
+
+## sa1
+## areas from absmapsdata package
+sa1 <- absmapsdata::sa12011 %>% 
+  filter(state_name_2011 != "Other Territories") %>% 
+  filter(gcc_name_2011 == "Greater Melbourne") %>% 
+  st_transform(., crs = "+proj=longlat +datum=WGS84")
+
+# Create centroids set
+centroids <- create_centroids(sa1, "sa1_7dig_2011")
+
+# choropleth map display
+ggplot(sa1) + 
+  geom_sf(aes(fill = albers_sqkm)) +
+  geom_point(aes(x = longitude, y = latitude), 
+             colour = "grey", size = 0.5, data = centroids) +
+  scale_fill_distiller(type = "seq", palette = "BuGn",
+                       direction = 1, na.value = "light grey") + 
+  theme_void() +
+  coord_sf(crs = "+proj=longlat +datum=WGS84") +
+  theme(legend.position ="left", legend.title = element_text("Area (sqkm)"))
+
+
+# Create hexagon location grid
+grid <- create_grid(centroids = centroids, hex_size = 0.02, buffer_dist = 1)
+
+# Allocate polygon centroids to hexagon grid points
+sa1_melb <- allocate(centroids = centroids,
+                          hex_grid = grid,
+                          sf_id = "sa1_7dig_2011",
+                          hex_size = 0.02, # same size used in create_grid
+                          hex_filter = 10,
+                          focal_points = capital_cities,
+                          width = 30, verbose = TRUE) # same column used in create_centroids
+
+save(hex_allocated, file = "hex_allocated.rda")
+load("hex_allocated.rda")
+
+
+
+
+
+
+ggsave(filename = "figures/aus_sa1.png", plot = sa1_map,
+       device = "png", bg = "transparent", dpi = 300,  width = 10, height = 8)
+

### 2020-10-05 kobakian-cook.Rmd
Fix name repair in sugarbag, then update

--- 2020-10-02 kobakian_cook.Rmd
@@
   % Any extra LaTeX you need in the preamble
-bibliography: sugarbag.bib
+bibliography: kobakian-cook.bib
 output: rticles::rjournal_article
+editor_options: 
+  chunk_output_type: console
 ---
@@
 
-knitr::opts_chunk$set(warning = FALSE, message = FALSE, eval = FALSE)
+knitr::opts_chunk$set(warning = FALSE, message = FALSE)
 options("citation_format" = "pandoc")
@@
   theme(
-    panel.background = element_rect(fill = "transparent", colour = NA), 
-    plot.background = element_rect(fill = "transparent", colour = NA),
+    panel.background = element_rect(fill = "black", colour = NA), 
+    plot.background = element_rect(fill = "black", colour = NA),
     legend.background = element_rect(fill = "transparent", colour = NA),
@@
     text = element_text(colour = "white"),
-    axis.text = element_text(colour = "white")
+    axis.text = element_blank()
   )
@@
 <!-- Motivation to map -->
+
 Many cancer atlases present geospatial cancer data on a choropleth map display.
@@
 <!-- Issues with choropleth map displays... -->
+
 In many countries, residents are increasingly gathering to live in urban areas around major cities [@ACTUC].
@@
 <!-- solutions -->
+
 The solutions to this visualisation problem begin with the geography.
@@
 
+```{=tex}
 \begin{figure}[h]
@@
 \end{figure}
-
+```
 Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing the population in each administrative area [@TAAM].
@@
 <!-- choropleth -->
+
 The familiar choropleth map display is often used to allow the user to orient themselves.
@@
 
-```{r}
+```{r choro}
 states <- absmapsdata::state2011 %>% 
-  rmapshaper::ms_simplify(keep = 0.25, keep_shapes = TRUE) %>% 
-  filter(!state_name_2011 == "Other Territories")
+  filter(!state_name_2011 == "Other Territories") %>% 
+  rmapshaper::ms_simplify(keep = 0.25, keep_shapes = TRUE)
 
 sa2 <- absmapsdata::sa22011 %>% 
-  filter(state_name_2011 == "New South Wales") %>% 
-  filter(!st_is_empty(geometry))
+  filter(state_name_2011 == "Tasmania") %>% 
+  filter(!st_is_empty(geometry)) %>% 
+  filter(!state_name_2011 == "Other Territories")
 
@@
 aus_ggchoro <- ggplot(sa2thyroid_ERP) + 
-  #geom_sf(fill = "lightgrey", data = states) + 
+  geom_sf(fill = "lightgrey", data = states %>% filter(state_name_2011=="Tasmania")) + 
   geom_sf(aes(fill = SIR)) + 
-  scale_fill_identity()
+  scale_fill_identity() +invthm
+```
+
+```{r fullhexmap}
+## Create centroids set
+centroids <- absmapsdata::sa22011 %>% 
+  filter(!st_is_empty(geometry)) %>% 
+  filter(state_name_2011 == "Tasmania") %>% 
+ # filter(!sa2_name_2011 == "Lord Howe Island") %>% 
+  create_centroids(., "sa2_name_2011")
+
+## Create hexagon grid
+grid <- create_grid(centroids = centroids,
+                    hex_size = 0.2,
+                    buffer_dist = 5)
+
+## Allocate polygon centroids to hexagon grid points
+hex_allocated <- allocate(
+  centroids = centroids,
+  hex_grid = grid,
+  sf_id = "sa2_name_2011",
+  ## same column used in create_centroids
+  hex_size = 0.2,
+  ## same size used in create_grid
+  hex_filter = 10,
+  focal_points = capital_cities,
+  width = 35,
+  verbose = FALSE
+)
+
+## Prepare to plot
+fort_hex <- fortify_hexagon(data = hex_allocated,
+                            sf_id = "sa2_name_2011",
+                            hex_size = 0.2) %>% 
+            left_join(sa2thyroid_ERP %>% select(sa2_name_2011, SIR, p50))
+
+fort_aus <- sa2thyroid_ERP %>%
+ # filter(!sa2_name_2011 == "Lord Howe Island") %>% 
+  fortify_sfc()
+
+fort_state <- states %>% 
+  filter(state_name_2011 == "Tasmania") %>% 
+  fortify_sfc() %>% 
+  filter(long < 159)
+
+## Make a plot
+library(ggplot2)
+aus_hexmap <- ggplot() +
+  geom_polygon(aes(x = long,  y = lat, group = interaction(state_name_2011, polygon)),
+               fill = "darkgrey",  data = fort_state) +
+  geom_polygon(aes(x = long,  y = lat,  group = interaction(sa2_name_2011, polygon)),
+               fill = "black",  colour = "darkgrey",  size = 0.1, data = fort_aus) +
+  geom_polygon(aes(x = long, y = lat, group = hex_id, fill = SIR), data = fort_hex) +
+  scale_fill_identity() +
+  invthm + coord_equal()
+aus_hexmap
 ```
@@
 ```{r alternatives}
-
-###############################################################################
-
 sa2thyroid_ERP <- st_transform(sa2thyroid_ERP, 3112)
@@
 aus_ggcont <- ggplot(cont) + 
+  geom_sf(fill = "darkgrey",  data = states %>% st_transform(., 3112) %>% filter(state_name_2011 == "Tasmania")) +
+  geom_sf(fill = "darkgrey",  data = sa2thyroid_ERP) +
   geom_sf(aes(fill = SIR), colour = NA) + 
@@
 
-ggsave(filename = "figures/aus_ggcont.png", plot = aus_ggcont,
+ggsave(filename = "figs/aus_ggcont.png", plot = aus_ggcont,
        device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
@@
 
-ncont <- cartogram_ncont(sa2thyroid_ERP, k = 1/10,
-                         weight = "Population") %>% st_as_sf()
+ncont <- cartogram_ncont(sa2thyroid_ERP, k = 1.5,
+                         weight = "Population") %>% 
+                          st_as_sf()
 
@@
 
-aus_ggncont <- ggplot(ncont) + 
+tas_ggncont <- ggplot(ncont %>% filter(state_name_2011 == "Tasmania")) + 
+  geom_sf(fill = "darkgrey",  data = states %>% st_transform(., 3112) %>% filter(state_name_2011 == "Tasmania")) +
+  geom_sf(fill = "darkgrey",  data = sa2thyroid_ERP) +
   geom_sf(aes(fill = SIR), colour = NA) + 
@@
   invthm + guides(fill=FALSE)
+tas_ggncont
+
+# Hobart
+hobart <- ggplot(ncont %>% filter(gcc_name_2011 == "Greater Hobart")) + 
+  geom_sf(fill = "darkgrey",  data = sa2thyroid_ERP %>% filter(gcc_name_2011 == "Greater Hobart")) +
+  geom_sf(aes(fill = SIR, size = 0.001), colour = "black") + 
+  scale_fill_identity() + 
+  scale_size_identity() +
+  invthm + guides(fill=FALSE) + 
+  theme(plot.background = element_rect(fill = "transparent", colour = NA)) + 
+  theme(panel.background = element_rect(fill = "transparent", colour = "white"))
+
+aus_ggncont <- ggdraw(xlim = c(0, 1), ylim = c(0, 2)) +
+  draw_plot(tas_ggncont, width = 1, height = 2) +
+  draw_plot(hobart, x = 0, width = 0.4, height = 0.4)
 aus_ggncont
 
-ggsave(filename = "figures/aus_ggncont.png", plot = aus_ggncont,
+ggsave(filename = "figs/aus_ggncont.png", plot = aus_ggncont,
        device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
@@
 
-dorl <- sa2lung_ERP %>%
-  mutate(pop = (Population/max(Population))*10) %>% 
-  cartogram_dorling(., k = 0.01, weight = "pop", m_weight = 1) %>% st_as_sf()
+dorl <- sa2thyroid_ERP %>%
+  #mutate(pop = (Population/max(Population))*10) %>% # helpful for all of Australia
+  cartogram_dorling(., weight = "Population", k = 0.2, m_weight = 1) %>% st_as_sf()
 d <- st_bbox(dorl)
 aus_ggdorl <- ggplot(dorl) +
+  geom_sf(fill = "darkgrey",  data = states %>% st_transform(., 3112) %>% filter(state_name_2011 == "Tasmania")) +
+  geom_sf(fill = "darkgrey",  data = sa2thyroid_ERP) + 
   geom_sf(aes(fill = SIR)) + 
@@
 
-ggsave(filename = "figures/aus_ggdorl.png", plot = aus_ggdorl,
+ggsave(filename = "figs/aus_ggdorl.png", plot = aus_ggdorl,
        device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
@@
 
-```{r full_hexmapcode}
-## Load data
-tas_sa2 <- absmapsdata::sa22011 %>% 
-  filter(state_name_2011 == "New South Wales")
+```{r mapgrid, width = 8, height = 10}
+aus_grid <- ggdraw(xlim = c(0, 2), ylim = c(0, 4)) +
+  draw_plot(aus_ggchoro, x = 0, y = 2, width = 1, height = 2) +
+  draw_plot(aus_ggcont,  x = 1, y = 2, width = 1, height = 2) +
+  draw_plot(aus_ggncont, x = 0, y = 0, width = 1, height = 2) +
+  draw_plot(aus_ggdorl,  x = 1, y = 0, width = 1, height = 2)
 
-## Create centroids set
-centroids <- create_centroids(tas_sa2, "sa2_name_2011")
+aus_grid
 
-## Create hexagon grid
-grid <- create_grid(centroids = centroids,
-                    hex_size = 0.12,
-                    buffer_dist = 1.2)
-
-## Allocate polygon centroids to hexagon grid points
-hex_allocated <- allocate(
-  centroids = centroids,
-  hex_grid = grid,
-  sf_id = "sa2_name_2011",
-  ## same column used in create_centroids
-  hex_size = 0.12,
-  ## same size used in create_grid
-  hex_filter = 10,
-  use_neighbours = tas_sa2,
-  focal_points = capital_cities %>%
-    filter(points == "Hobart"),
-  width = 35,
-  verbose = FALSE
-)
-
-## Prepare to plot
-fort_hex <- fortify_hexagon(data = hex_allocated,
-                            sf_id = "sa2_name_2011",
-                            hex_size = 0.12)
-
-fort_tas <- tas_sa2 %>%
-  fortify_sfc()
-
-## Make a plot
-library(ggplot2)
-tas_hexmap <- ggplot() +
-  geom_polygon(aes(
-      x = long,
-      y = lat,
-      group = interaction(sa2_name_2011, polygon)
-    ),
-    fill = "white",
-    colour = "lightgrey",
-    data = fort_tas
-  ) +
-  geom_polygon(aes(
-    x = long,
-    y = lat,
-    group = hex_id,
-    fill = rownumber
-  ),
-  data = fort_hex) +
-  scale_fill_distiller("", palette = "PRGn") +
-  coord_equal() + theme_void()
-tas_hexmap
+ggsave(filename = "figs/aus_grid.png", plot = aus_grid,
+  device = "png", bg = "transparent", dpi = 300, width = 8, height = 10)
 ```
 
-```{r mapgrid}
-
-###############################################################################
-
-aus_grid <- gridExtra::grid.arrange(aus_ggchoro, aus_ggcont, aus_ggncont, aus_ggdorl, nrow = 2)
-
-aus_grid
-ggsave(filename = "figures/aus_grid.png", plot = aus_grid,
-  device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
-```
-
-<!-- \begin{figure}[h] -->
-<!-- \centering -->
-<!-- \includegraphics[width=14cm]{figs/nsw_grid.png} -->
-<!-- \caption{\label{fig:nsw_grid}A collection of alternative maps of the Statistical Areas of Australia at Level 2.
-The colours communicate the value of the estimated SIR of Melanoma for males, ranging from much lower than average (blue) to much higher than average (red)} -->
-<!-- \end{figure} -->
-
-<!-- contiguous -->
 When communicating information that is relevant to the population, each member of the population can be given equal representation by transforming the map [@TVSSS].
@@
 This display can create twisted and unfamiliar shapes from the geographic units as the algorithms must satisfy the topology conditions, especially when there are communities located geographically far from their neighbours [@TVSSS].
-This shown in the northern SA2s of New South Wales with an average (yellow) estimated SIR of Melanoma for males.
+This shown in the northern SA2s of Tasmania with an average (yellow) estimated SIR of Melanoma for males.
 
 <!-- non-contiguous -->
+
 The non-contiguous cartogram in figure \ref{fig:nsw_grid}c) also uses the population to rescale the geographic units.
@@
 The population of the SA2 areas is used to scale the geographic units in the non-contiguous cartogram [@NAC].
-The amount of white space can be meaningful in non-contiguous cartograms [@ECGC], in this example the disparity between large rural areas and small urban areas means that the city of Hobart, shown in the inset map looks reasonable, but these units are not visible in the context of the New South Wales state map.
+The amount of white space can be meaningful in non-contiguous cartograms [@ECGC], in this example the disparity between large rural areas and small urban areas means that the city of Hobart, shown in the inset map looks reasonable, but these units are not visible in the context of the Tasmania state map.
 Depending on the difference between the population and geographic land size, the amount of white space can also prevent meaningful understanding of the distribution [@TVSSS].
@@
 <!-- Dorling -->
+
 The Dorling cartogram presents each geographic unit as a circle, the size of the circle is scaled according to the population value of each area [@ACTUC].
-Figure \ref{fig:nsw_grid}d) shows the New South Wales SA2 areas as an individual circle located as close as possible to the geographic centroid location.
-This map draws attention to the collection of coastal cities in New South Wales that were not apparent in figure \ref{fig:nsw_grid} a), b) or c).
+Figure \ref{fig:nsw_grid}d) shows the Tasmania SA2 areas as an individual circle located as close as possible to the geographic centroid location.
+This map draws attention to the collection of coastal cities in Tasmania that were not apparent in figure \ref{fig:nsw_grid} a), b) or c).
 
@@
 -->
+
 <!-- Contiguous cartograms alter the shape of areas, while preserving boundary relationships of neighbours.
@@
 There are three key steps performed to create a tessellated hexagon tile map.
-First create the set of centroids from the polygons to allocate, then create the grid of hexagons locations.
+First derive the set of centroids from the polygons provided, then create the grid of hexagons locations.
+These two steps are defined in the blue left column of the flow chart in Figure \ref{fig:sugarbag_flow}.
 Each centroid can then be allocated to an available hexagon location.
-To make tessellated plots the points can be converted to hexagon shapes, with the hexagon size equal to the size used in the grid.
+The steps for the allocation process are detailed in the right column of Figure \ref{fig:sugarbag_flow}.
+To make tessellated plots, the point locations are converted to hexagon shapes, with the hexagon size used in the grid.
 
 \begin{figure}
-\includegraphics[width=14cm]{figs/flowchart.png}
+\includegraphics[width=14cm]{figs/sugarbag flow.png}
 \caption{\label{fig:sugarbag_flow}A flow diagram detailing the necessary steps to create a hexagon tile map.}
@@
 <!-- The`create_hexmap` function will -->
+
 <!-- Derive the centroids of the geographic units to calculate a grid of possible hexagon locations, and allocate each geographic unit to a single hexagon. -->
+
 Only two inputs are necessary to begin using the algorithm, the shape file, and the id variable. The id column should uniquely identify each geographic unit in the shape file.
 
-The centroids can be derived from the shape file. The amount of centroids is used to determine a hexagon size. 
+The centroids can be derived from the shape file.
+The amount of centroids is used to determine a hexagon size.
 The derived centroids are a necessary input for an appropriate grid to be constructed, in which each grid point is located a hexagon size distance from the next closest point in all six directions.
@@
 <!-- Motivate the value of the the package and algorithm -->
+
 Hexagon tile maps can be useful to understand a distribution across a collection of geographic areas.
@@
 
-The following code creates the hexagon tile map for all the Statistical Areas at Level 2 in New South Wales.
+The following code creates the hexagon tile map for all the Statistical Areas at Level 2 in Tasmania.
 These steps can be executed by the main function, `create_hexmap`, or can be implemented separately for more flexibility.
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=14cm]{figs/aus_gghexmap.png}
-\caption{\label{fig:melanoma-hex}A hexagon tile map of the Statistical Areas of Australia at Level 2.
-The colours communicate the value of the estimated SIR, they range from much lower than average (blue) to much higher than average (red)}
-\end{figure}
+```{hexmap, fig.cap = "A hexagon tile map of the Statistical Areas of Australia at Level 2.
+The colours communicate the value of the estimated SIR of Melanoma for males, they range from much lower than average (blue) to much higher than average (red)."}
+aus_hexmap
+```
 
@@
 
-The polygon set of Statistical Areas at Level 2 (SA2) [@abs2011] of New South Wales in 2011 is provided with the `sugarbag` package as `tas_sa2`. 
+The polygon set of Statistical Areas at Level 2 (SA2) [@abs2011] of Tasmania in 2011 is provided with the `sugarbag` package as `tas_sa2`.
 A single column of the data set is used to identify the unique areas.
@@
 The longitude and latitude centre of the capital cities of Australia are used as focal points to allocate each geographic area around the closest capital city.
-Hobart will be the common focal point, as this example uses only the areas in the state of New South Wales.
+Hobart will be the common focal point, as this example uses only the areas in the state of Tasmania.
 
@@
 \includegraphics[width=14cm]{figs/1centroids.png}
-\caption{\label{fig:centroids_plot}The geographic shapes of the Statistical Areas of New South Wales at Level 2. The points show the locations of the centroids of the SA2 areas.}
+\caption{\label{fig:centroids_plot}The geographic shapes of the Statistical Areas of Tasmania at Level 2. The points show the locations of the centroids of the SA2 areas.}
 \end{figure}
-
+```
 #### Step 2: Create the hexagon grid points
@@
 
-The grid of possible hexagon locations is made using the `create_grid` function.
-It uses the centroids, the hexagon size and the buffer distance.
+The grid of possible hexagon locations is made using the `create_grid` function. It uses the centroids, the hexagon size and the buffer distance.
 
@@
 
-A set of longitude columns, and latitude rows are created to define the locations of the hexagons. The distance between each row and column is the size specified by `hex_size`.
+A set of longitude columns, and latitude rows are created to define the locations of the hexagons.
+The distance between each row and column is the size specified by `hex_size`.
 Equally spaced columns are created from the minimum longitude minus the buffer distance, up to the maximum longitude plus the buffer distance.
@@
 <!-- ```{r grid2, fig.cap = "Grid points to create a tile map.", out.width = "100%", echo = FALSE} -->
-<!-- knitr::include_graphics(path = "figures/2grid.png") -->
+
+<!-- knitr::include_graphics(path = "figs2grid.png") -->
+
 <!-- ``` -->
 
+```{=tex}
 \begin{figure}[h]
@@
 \end{figure}
-
+```
 ##### Rolling windows
@@
 
-The closest latitude row and longitude column are found for each centroid location. Then rows and columns of centroids are divided into 20 groups.
+The closest latitude row and longitude column are found for each centroid location.
+Then rows and columns of centroids are divided into 20 groups.
 The amount of rows in each latitude group and the amount of columns in each longitude group are used as the width of rolling windows.
@@
 The rolling windows show the collections of rows and columns used to filter the hexagon locations.", echo = FALSE, out.width = "100%"} -->
-<!-- knitr::include_graphics(path = "figures/3grid.png", dpi = 300) -->
+
+<!-- knitr::include_graphics(path = "figs3grid.png", dpi = 300) -->
+
 <!-- ``` -->
 
+```{=tex}
 \begin{figure}[h]
@@
 \end{figure}
-
+```
 ##### Centroid to focal point distance
@@
 The name of the closest focal point, and the distance and angle from focal point to polygon centroid is joined to polygon data set.
-To minimise time taken for this step only one option is provided, New South Wales's capital city Hobart.
+To minimise time taken for this step only one option is provided, Tasmania's capital city Hobart.
 The order for allocation is determined by the distance between the polygon centroid and it's closest focal point.
@@
 
-The following example considers the first of the Statistical Areas at Level 2. 
-Within the algorithm, these steps are repeated for each polygon.
+The following example considers the first of the Statistical Areas at Level 2. Within the algorithm, these steps are repeated for each polygon.
 
@@
 <!-- ```{r buffers, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, out.width = "100%"} -->
-<!-- knitr::include_graphics(path = "figures/4grid.png") -->
+
+<!-- knitr::include_graphics(path = "figs4grid.png") -->
+
 <!-- ``` -->
 
+```{=tex}
 \begin{figure}[h]
@@
 \end{figure}
-
+```
 The `width` parameter is used to take a slice of the remaining points.
@@
 <!-- ```{r angles, fig.cap = "Filter for grid points within the angle from the focal point to the centroid.", echo = FALSE, out.width = "100%"} -->
-<!-- knitr::include_graphics(path = "figures/5allocate.png") -->
+
+<!-- knitr::include_graphics(path = "figs5allocate.png") -->
+
 <!-- ``` -->
 
+```{=tex}
 \begin{figure}[h]
@@
 \end{figure}
-
-If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded, only when a maximum distance is reached will the angle expand to accommodate more possible grid points.
+```
+If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded, only when a maximum distance is reached will the angle expand to accommodate more possible grid points.\
 By default the angle filter to hexagon grid points that fall within the bounds of the angle from the focal point to the geographic centroid, plus and minus 30 degrees.
@@
 
-<!-- ```{r buffs, fig.cap = "A complete hexagon tile map of New South Wales.", out.width = "100%", echo = FALSE} -->
-<!-- knitr::include_graphics(path = "figures/6allocate.png") -->
+<!-- ```{r buffs, fig.cap = "A complete hexagon tile map of Tasmania.", out.width = "100%", echo = FALSE} -->
+
+<!-- knitr::include_graphics(path = "figs6allocate.png") -->
+
 <!-- ``` -->
 
+```{=tex}
 \begin{figure}[h]
@@
 \includegraphics[width=16cm]{figs/6allocate.png}
-\caption{\label{fig:buffs}A complete hexagon tile map of New South Wales.}
+\caption{\label{fig:buffs}A complete hexagon tile map of Tasmania.}
 \end{figure}
-
-A complete hexagon tile map of New South Wales is created by applying the algorithm steps to each centroid.
+```
+A complete hexagon tile map of Tasmania is created by applying the algorithm steps to each centroid.
 The hexagon tile map visualisation is used below to visualise the Australian Cancer Atlas data [@TACA].
@@
 A choropleth map (a) of Standardised Incidence Rates (SIRs) is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented."} -->
-<!-- knitr::include_graphics(path = "figures/7SIR.png") -->
+
+<!-- knitr::include_graphics(path = "figs7SIR.png") -->
+
 <!-- ``` -->
 
+```{=tex}
 \begin{figure}[h]
@@
 \end{figure}
-
+```
 #### Neighbour relationships
@@
 The communities south of Hobart show a gradient of colour as the values progress from higher than average, to much lower than average for the communities closer to the Sydney CBD.
-This pattern progresses into the communities with lower than average rates in Melbourne and New South Wales.
+This pattern progresses into the communities with lower than average rates in Melbourne and Tasmania.
 
@@
 The much higher than average rates in Sydney draw more attention in the hexagon tile map display unlike the red and orange areas in the city of Hobart that draw attention in both displays.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=14cm]{figs/aus_gghexmap.png}
-\caption{\label{fig:melanoma-geo}A hexagon tile map of the Statistical Areas of Australia at Level 2.
-The colours communicate the value of the estimated SIR of Melanoma for males, they range from much lower than average (blue) to much higher than average (red).}
-\end{figure}
 
@@
 
-These hexagons equally represent each area. However, the tessellation does not allow the size of the hexagons to represent another variable, similar to the choropleth maps.
+These hexagons equally represent each area.
+However, the tessellation does not allow the size of the hexagons to represent another variable, similar to the choropleth maps.
 The algorithm is heavily dependent on the focal points used, as this determines the order of allocation.
@@
 With careful consideration of the choropleth map, the small geographic inner city areas may have been noticed by viewers, but the hexagon tile map display emphasises them.
-The communities in northern New South Wales and the Northern territory do not draw attention because of their size as in the choropleth, but their colour is still noticeably below average when contrasted with the hexagons further south.
+The communities in northern Tasmania and the Northern territory do not draw attention because of their size as in the choropleth, but their colour is still noticeably below average when contrasted with the hexagons further south.
 
 <!-- why hexagon tile map addresses deficiencies -->
+
 The Dorling cartogram was the most influential in the design of the hexagon tile map.
@@
 The tessellation crated by adjoining hexagons for densely populated areas is helpful as it shows that most communities are not islands onto themselves, but are intrinsically connected to those around them.
-As seen in the Dorling cartogram in figure \ref{fig:nsw_grid}c), the tessellation that allows boundary connections was not imposed for rural communities, where centroid of the geographic unit was located far from others, a feature that allows distant but dense populations of the coastal towns of New South Wales to be recognised.
+As seen in the Dorling cartogram in figure \ref{fig:nsw_grid}c), the tessellation that allows boundary connections was not imposed for rural communities, where centroid of the geographic unit was located far from others, a feature that allows distant but dense populations of the coastal towns of Tasmania to be recognised.
 
@@
 <!-- future -->
+
 Future work will include refining the algorithm.

### 2020-10-05 kobakian-cook.tex
Fix name repair in sugarbag, then update

@@
 states <- absmapsdata::state2011 %>% 
-  rmapshaper::ms_simplify(keep = 0.25, keep_shapes = TRUE) %>% 
-  filter(!state_name_2011 == "Other Territories")
+  filter(!state_name_2011 == "Other Territories") %>% 
+  rmapshaper::ms_simplify(keep = 0.25, keep_shapes = TRUE)
 
 sa2 <- absmapsdata::sa22011 %>% 
-  filter(state_name_2011 == "New South Wales") %>% 
-  filter(!st_is_empty(geometry))
+  filter(state_name_2011 == "Tasmania") %>% 
+  filter(!st_is_empty(geometry)) %>% 
+  filter(!state_name_2011 == "Other Territories")
 
@@
 aus_ggchoro <- ggplot(sa2thyroid_ERP) + 
-  #geom_sf(fill = "lightgrey", data = states) + 
+  geom_sf(fill = "lightgrey", data = states %>% filter(state_name_2011=="Tasmania")) + 
   geom_sf(aes(fill = SIR)) + 
-  scale_fill_identity()
+  scale_fill_identity() +invthm
 \end{Sinput}
@@
 \begin{Sinput}
-###############################################################################
+## Create centroids set
+centroids <- absmapsdata::sa22011 %>% 
+  filter(!st_is_empty(geometry)) %>% 
+  filter(state_name_2011 == "Tasmania") %>% 
+ # filter(!sa2_name_2011 == "Lord Howe Island") %>% 
+  create_centroids(., "sa2_name_2011")
 
+## Create hexagon grid
+grid <- create_grid(centroids = centroids,
+                    hex_size = 0.2,
+                    buffer_dist = 5)
+
+## Allocate polygon centroids to hexagon grid points
+hex_allocated <- allocate(
+  centroids = centroids,
+  hex_grid = grid,
+  sf_id = "sa2_name_2011",
+  ## same column used in create_centroids
+  hex_size = 0.2,
+  ## same size used in create_grid
+  hex_filter = 10,
+  focal_points = capital_cities,
+  width = 35,
+  verbose = FALSE
+)
+
+## Prepare to plot
+fort_hex <- fortify_hexagon(data = hex_allocated,
+                            sf_id = "sa2_name_2011",
+                            hex_size = 0.2) %>% 
+            left_join(sa2thyroid_ERP %>% select(sa2_name_2011, SIR, p50))
+
+fort_aus <- sa2thyroid_ERP %>%
+ # filter(!sa2_name_2011 == "Lord Howe Island") %>% 
+  fortify_sfc()
+
+fort_state <- states %>% 
+  filter(state_name_2011 == "Tasmania") %>% 
+  fortify_sfc() %>% 
+  filter(long < 159)
+
+## Make a plot
+library(ggplot2)
+aus_hexmap <- ggplot() +
+  geom_polygon(aes(x = long,  y = lat, group = interaction(state_name_2011, polygon)),
+               fill = "darkgrey",  data = fort_state) +
+  geom_polygon(aes(x = long,  y = lat,  group = interaction(sa2_name_2011, polygon)),
+               fill = "black",  colour = "darkgrey",  size = 0.1, data = fort_aus) +
+  geom_polygon(aes(x = long, y = lat, group = hex_id, fill = SIR), data = fort_hex) +
+  scale_fill_identity() +
+  invthm + coord_equal()
+aus_hexmap
+\end{Sinput}
+
+\includegraphics{kobakian-cook_files/figure-latex/fullhexmap-1} \end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
 sa2thyroid_ERP <- st_transform(sa2thyroid_ERP, 3112)
@@
 aus_ggcont
+\end{Sinput}
 
-ggsave(filename = "figures/aus_ggcont.png", plot = aus_ggcont,
+\includegraphics{kobakian-cook_files/figure-latex/alternatives-1} \begin{Sinput}
+ggsave(filename = "figs/aus_ggcont.png", plot = aus_ggcont,
        device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
@@
   invthm + guides(fill=FALSE)
+tas_ggncont
+\end{Sinput}
+
+\includegraphics{kobakian-cook_files/figure-latex/unnamed-chunk-1-1} \begin{Sinput}
+# Hobart
+hobart <- ggplot(ncont %>% filter(gcc_name_2011 == "Greater Hobart")) + 
+  geom_sf(fill = "darkgrey",  data = sa2thyroid_ERP %>% filter(gcc_name_2011 == "Greater Hobart")) +
+  geom_sf(aes(fill = SIR, size = 0.001), colour = "black") + 
+  scale_fill_identity() + 
+  scale_size_identity() +
+  invthm + guides(fill=FALSE) + 
+  theme(plot.background = element_rect(fill = "transparent", colour = NA)) + 
+  theme(panel.background = element_rect(fill = "transparent", colour = "white"))
+
+aus_ggncont <- ggdraw(xlim = c(0, 1), ylim = c(0, 2)) +
+  draw_plot(tas_ggncont, width = 1, height = 2) +
+  draw_plot(hobart, x = 0, width = 0.4, height = 0.4)
 aus_ggncont
+\end{Sinput}
 
-ggsave(filename = "figures/aus_ggncont.png", plot = aus_ggncont,
+\includegraphics{kobakian-cook_files/figure-latex/unnamed-chunk-1-2} \begin{Sinput}
+ggsave(filename = "figs/aus_ggncont.png", plot = aus_ggncont,
        device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
@@
 aus_ggdorl
+\end{Sinput}
 
-ggsave(filename = "figures/aus_ggdorl.png", plot = aus_ggdorl,
+\includegraphics{kobakian-cook_files/figure-latex/unnamed-chunk-2-1} \begin{Sinput}
+ggsave(filename = "figs/aus_ggdorl.png", plot = aus_ggdorl,
        device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
@@
 \begin{Sinput}
-## Load data
-tas_sa2 <- absmapsdata::sa22011 %>% 
-  filter(state_name_2011 == "New South Wales")
+aus_grid <- ggdraw(xlim = c(0, 2), ylim = c(0, 4)) +
+  draw_plot(aus_ggchoro, x = 0, y = 2, width = 1, height = 2) +
+  draw_plot(aus_ggcont,  x = 1, y = 2, width = 1, height = 2) +
+  draw_plot(aus_ggncont, x = 0, y = 0, width = 1, height = 2) +
+  draw_plot(aus_ggdorl,  x = 1, y = 0, width = 1, height = 2)
 
-## Create centroids set
-centroids <- create_centroids(tas_sa2, "sa2_name_2011")
+aus_grid
+\end{Sinput}
 
-## Create hexagon grid
-grid <- create_grid(centroids = centroids,
-                    hex_size = 0.12,
-                    buffer_dist = 1.2)
-
-## Allocate polygon centroids to hexagon grid points
-hex_allocated <- allocate(
-  centroids = centroids,
-  hex_grid = grid,
-  sf_id = "sa2_name_2011",
-  ## same column used in create_centroids
-  hex_size = 0.12,
-  ## same size used in create_grid
-  hex_filter = 10,
-  use_neighbours = tas_sa2,
-  focal_points = capital_cities %>%
-    filter(points == "Hobart"),
-  width = 35,
-  verbose = FALSE
-)
-
-## Prepare to plot
-fort_hex <- fortify_hexagon(data = hex_allocated,
-                            sf_id = "sa2_name_2011",
-                            hex_size = 0.12)
-
-fort_tas <- tas_sa2 %>%
-  fortify_sfc()
-
-## Make a plot
-library(ggplot2)
-tas_hexmap <- ggplot() +
-  geom_polygon(aes(
-      x = long,
-      y = lat,
-      group = interaction(sa2_name_2011, polygon)
-    ),
-    fill = "white",
-    colour = "lightgrey",
-    data = fort_tas
-  ) +
-  geom_polygon(aes(
-    x = long,
-    y = lat,
-    group = hex_id,
-    fill = rownumber
-  ),
-  data = fort_hex) +
-  scale_fill_distiller("", palette = "PRGn") +
-  coord_equal() + theme_void()
-tas_hexmap
+\includegraphics{kobakian-cook_files/figure-latex/mapgrid-1} \begin{Sinput}
+ggsave(filename = "figs/aus_grid.png", plot = aus_grid,
+  device = "png", bg = "transparent", dpi = 300, width = 8, height = 10)
 \end{Sinput}
 \end{Schunk}
-
-\begin{Schunk}
-\begin{Sinput}
-###############################################################################
-
-aus_grid <- gridExtra::grid.arrange(aus_ggchoro, aus_ggcont, aus_ggncont, aus_ggdorl, nrow = 2)
-
-aus_grid
-ggsave(filename = "figures/aus_grid.png", plot = aus_grid,
-  device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
-\end{Sinput}
-\end{Schunk}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=14cm]{figs/nsw_grid.png}
-\caption{\label{fig:nsw_grid}A collection of alternative maps of the Statistical Areas of Australia at Level 2.
-The colours communicate the value of the estimated SIR of Melanoma for males, ranging from much lower than average (blue) to much higher than average (red)}
-\end{figure}
 
@@
 far from their neighbours \citep{TVSSS}. This shown in the northern SA2s
-of New South Wales with an average (yellow) estimated SIR of Melanoma
-for males.
+of Tasmania with an average (yellow) estimated SIR of Melanoma for
+males.
 
@@
 Hobart, shown in the inset map looks reasonable, but these units are not
-visible in the context of the New South Wales state map. Depending on
-the difference between the population and geographic land size, the
-amount of white space can also prevent meaningful understanding of the
+visible in the context of the Tasmania state map. Depending on the
+difference between the population and geographic land size, the amount
+of white space can also prevent meaningful understanding of the
 distribution \citep{TVSSS}.
@@
 size of the circle is scaled according to the population value of each
-area \citep{ACTUC}. Figure \ref{fig:nsw_grid}d) shows the New South
-Wales SA2 areas as an individual circle located as close as possible to
-the geographic centroid location. This map draws attention to the
-collection of coastal cities in New South Wales that were not apparent
-in figure \ref{fig:nsw_grid} a), b) or c).
+area \citep{ACTUC}. Figure \ref{fig:nsw_grid}d) shows the Tasmania SA2
+areas as an individual circle located as close as possible to the
+geographic centroid location. This map draws attention to the collection
+of coastal cities in Tasmania that were not apparent in figure
+\ref{fig:nsw_grid} a), b) or c).
 
@@
 There are three key steps performed to create a tessellated hexagon tile
-map. First create the set of centroids from the polygons to allocate,
-then create the grid of hexagons locations. Each centroid can then be
-allocated to an available hexagon location. To make tessellated plots
-the points can be converted to hexagon shapes, with the hexagon size
-equal to the size used in the grid.
+map. First derive the set of centroids from the polygons provided, then
+create the grid of hexagons locations. These two steps are defined in
+the blue left column of the flow chart in Figure
+\ref{fig:sugarbag_flow}. Each centroid can then be allocated to an
+available hexagon location. The steps for the allocation process are
+detailed in the right column of Figure \ref{fig:sugarbag_flow}. To make
+tessellated plots, the point locations are converted to hexagon shapes,
+with the hexagon size used in the grid.
 
 \begin{figure}
-\includegraphics[width=14cm]{figs/flowchart.png}
+\includegraphics[width=14cm]{figs/sugarbag flow.png}
 \caption{\label{fig:sugarbag_flow}A flow diagram detailing the necessary steps to create a hexagon tile map.}
@@
 The following code creates the hexagon tile map for all the Statistical
-Areas at Level 2 in New South Wales. These steps can be executed by the
-main function, \texttt{create\_hexmap}, or can be implemented separately
-for more flexibility.
+Areas at Level 2 in Tasmania. These steps can be executed by the main
+function, \texttt{create\_hexmap}, or can be implemented separately for
+more flexibility.
 
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=14cm]{figs/aus_gghexmap.png}
-\caption{\label{fig:melanoma-hex}A hexagon tile map of the Statistical Areas of Australia at Level 2.
-The colours communicate the value of the estimated SIR, they range from much lower than average (blue) to much higher than average (red)}
-\end{figure}
+\begin{Schunk}
+\begin{Sinput}
+aus_hexmap
+\end{Sinput}
+\end{Schunk}
 
@@
 The polygon set of Statistical Areas at Level 2 (SA2) \citep{abs2011} of
-New South Wales in 2011 is provided with the \texttt{sugarbag} package
-as \texttt{tas\_sa2}. A single column of the data set is used to
-identify the unique areas. In this case, the unique SA2 names for each
-SA2 have been used.
+Tasmania in 2011 is provided with the \texttt{sugarbag} package as
+\texttt{tas\_sa2}. A single column of the data set is used to identify
+the unique areas. In this case, the unique SA2 names for each SA2 have
+been used.
 
@@
 capital city. Hobart will be the common focal point, as this example
-uses only the areas in the state of New South Wales.
+uses only the areas in the state of Tasmania.
 
@@
 \includegraphics[width=14cm]{figs/1centroids.png}
-\caption{\label{fig:centroids_plot}The geographic shapes of the Statistical Areas of New South Wales at Level 2. The points show the locations of the centroids of the SA2 areas.}
+\caption{\label{fig:centroids_plot}The geographic shapes of the Statistical Areas of Tasmania at Level 2. The points show the locations of the centroids of the SA2 areas.}
 \end{figure}
@@
 polygon data set. To minimise time taken for this step only one option
-is provided, New South Wales's capital city Hobart. The order for
-allocation is determined by the distance between the polygon centroid
-and it's closest focal point. The points are arranged from the centroid
-closest to the focal point(s), to the furthest.
+is provided, Tasmania's capital city Hobart. The order for allocation is
+determined by the distance between the polygon centroid and it's closest
+focal point. The points are arranged from the centroid closest to the
+focal point(s), to the furthest.
 
@@
 \includegraphics[width=16cm]{figs/6allocate.png}
-\caption{\label{fig:buffs}A complete hexagon tile map of New South Wales.}
+\caption{\label{fig:buffs}A complete hexagon tile map of Tasmania.}
 \end{figure}
 
-A complete hexagon tile map of New South Wales is created by applying
-the algorithm steps to each centroid. The hexagon tile map visualisation
-is used below to visualise the Australian Cancer Atlas data
-\citep{TACA}. Two views of the same data are produced by filling
-according to the thyroid Cancer Standardised Incidence Rates (SIRs)
-downloaded from the Australian Cancer Atlas site. This small example in
-Figure \ref{fig:sir} shows the group of blue areas in the Hobart CBD
-more prominently in the hexagon tile map (b). The small red areas
-visible in the choropleth map (a) along the north coast are much larger
-in the hexagon tile maps. The hexagon tile map shows less yellow, this
-no longer overwhelms the map space with the information regarding the
-rural areas.
+A complete hexagon tile map of Tasmania is created by applying the
+algorithm steps to each centroid. The hexagon tile map visualisation is
+used below to visualise the Australian Cancer Atlas data \citep{TACA}.
+Two views of the same data are produced by filling according to the
+thyroid Cancer Standardised Incidence Rates (SIRs) downloaded from the
+Australian Cancer Atlas site. This small example in Figure \ref{fig:sir}
+shows the group of blue areas in the Hobart CBD more prominently in the
+hexagon tile map (b). The small red areas visible in the choropleth map
+(a) along the north coast are much larger in the hexagon tile maps. The
+hexagon tile map shows less yellow, this no longer overwhelms the map
+space with the information regarding the rural areas.
 
@@
 closer to the Sydney CBD. This pattern progresses into the communities
-with lower than average rates in Melbourne and New South Wales.
+with lower than average rates in Melbourne and Tasmania.
 
@@
 that draw attention in both displays.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=14cm]{figs/aus_gghexmap.png}
-\caption{\label{fig:melanoma-geo}A hexagon tile map of the Statistical Areas of Australia at Level 2.
-The colours communicate the value of the estimated SIR of Melanoma for males, they range from much lower than average (blue) to much higher than average (red).}
-\end{figure}
 
@@
 inner city areas may have been noticed by viewers, but the hexagon tile
-map display emphasises them. The communities in northern New South Wales
-and the Northern territory do not draw attention because of their size
-as in the choropleth, but their colour is still noticeably below average
-when contrasted with the hexagons further south.
+map display emphasises them. The communities in northern Tasmania and
+the Northern territory do not draw attention because of their size as in
+the choropleth, but their colour is still noticeably below average when
+contrasted with the hexagons further south.
 
@@
 geographic unit was located far from others, a feature that allows
-distant but dense populations of the coastal towns of New South Wales to
-be recognised.
+distant but dense populations of the coastal towns of Tasmania to be
+recognised.
 
@@
 
-\bibliography{sugarbag.bib}
+\bibliography{kobakian-cook.bib}
 

### 2020-10-05 kobakian-cook.R

@@ -1,20 +1,14 @@
-## ----setup, echo=FALSE, message=FALSE, warning=FALSE, comment = FALSE---------
-library(knitcitations)
-library(kableExtra)
-library(RefManageR)
-library(sp)
-library(sf)
-library(sugarbag)
+# Young statisticians conference presentation plots
+
 library(absmapsdata)
 library(tidyverse)
 library(cartogram)
 library(ggthemes)
 library(cowplot)
+library(sf)
+library(sp)
 
-knitr::opts_chunk$set(warning = FALSE, message = FALSE, eval = FALSE)
-options("citation_format" = "pandoc")
-BibOptions(check.entries = FALSE, style = "markdown")
-
+### Theme set up
 
 invthm <- theme_map() + 
   theme(
@@ -26,237 +20,612 @@ invthm <- theme_map() +
     axis.text = element_text(colour = "white")
   )
 
+## States of Australia
+
+states <- absmapsdata::state2011 %>% 
+  filter(state_name_2011 != "Other Territories")
+
+###############################################################################
+###########################        ABS AREAS        ###########################
+## sa2
+sa2 <- absmapsdata::sa22011 %>% 
+  filter(state_name_2011 != "Other Territories") %>% st_transform(., crs = 3112)
+
+sa2_map <- ggplot(sa2) + 
+  geom_sf(aes(fill = albers_sqkm)) +
+  scale_fill_distiller(type = "seq", palette = "BuGn",  direction = 1, na.value = "light grey") + 
+  theme_void() +
+  coord_sf(crs = 3112) +
+   theme(legend.position ="left", legend.title = element_text("Area (sqkm)"))
+
+ggsave(filename = "figures/aus_sa2.png", plot = sa2_map,
+  device = "png", bg = "transparent", dpi = 300,  width = 10, height = 8)
+
+
+###############################################################################
+###########################     CARTOGRAMS
+# 
+# ERP <- read_csv("data/ERP.csv")
+# 
+# ERP_sa4 <- ERP %>% filter(`Geography Level` == "Statistical Area Level 4", Time == 2011) %>% arrange(`Geography Level`)
+# 
[…]

### 2020-10-05 kobakian_cook.R

@@ -1,631 +1,0 @@
-# Young statisticians conference presentation plots
-
-library(absmapsdata)
-library(tidyverse)
-library(cartogram)
-library(ggthemes)
-library(cowplot)
-library(sf)
-library(sp)
-
-### Theme set up
-
-invthm <- theme_map() + 
-  theme(
-    panel.background = element_rect(fill = "transparent", colour = NA), 
-    plot.background = element_rect(fill = "transparent", colour = NA),
-    legend.background = element_rect(fill = "transparent", colour = NA),
-    legend.key = element_rect(fill = "transparent", colour = NA),
-    text = element_text(colour = "white"),
-    axis.text = element_text(colour = "white")
-  )
-
-## States of Australia
-
-states <- absmapsdata::state2011 %>% 
-  filter(state_name_2011 != "Other Territories")
-
-###############################################################################
-###########################        ABS AREAS        ###########################
-## sa2
-sa2 <- absmapsdata::sa22011 %>% 
-  filter(state_name_2011 != "Other Territories") %>% st_transform(., crs = 3112)
-
-sa2_map <- ggplot(sa2) + 
-  geom_sf(aes(fill = albers_sqkm)) +
-  scale_fill_distiller(type = "seq", palette = "BuGn",  direction = 1, na.value = "light grey") + 
-  theme_void() +
-  coord_sf(crs = 3112) +
-   theme(legend.position ="left", legend.title = element_text("Area (sqkm)"))
-
-ggsave(filename = "figures/aus_sa2.png", plot = sa2_map,
-  device = "png", bg = "transparent", dpi = 300,  width = 10, height = 8)
-
-
-###############################################################################
-###########################     CARTOGRAMS
-# 
-# ERP <- read_csv("data/ERP.csv")
-# 
-# ERP_sa4 <- ERP %>% filter(`Geography Level` == "Statistical Area Level 4", Time == 2011) %>% arrange(`Geography Level`)
-# 
-# aus_ggcont <- ggplot(ERP_sa4) + 
-#   geom_sf(aes(fill = `Age-standardised rate (per 100,000)`)) + 
[…]

### 2020-10-05 kobakian-cook.Rmd
tassie plots

@@
 
-```{r setup, echo=FALSE, message=FALSE, warning=FALSE, comment = FALSE}
+```{r defaults, echo=FALSE, message=FALSE, warning=FALSE, comment = FALSE}
+knitr::opts_chunk$set(warning = FALSE, 
+                      message = FALSE, 
+                      comment = FALSE,
+                      echo = FALSE,
+                      eval = TRUE,
+                      out.width = "90%",
+                      retina = 3,
+                      dev = "png",
+                      fig.pos = "center")
+```
+
+```{r setup}
 library(knitcitations)
@@
 library(RefManageR)
+options("citation_format" = "pandoc")
+BibOptions(check.entries = FALSE, style = "markdown")
+
 library(sp)
@@
 library(sugarbag)
+# remotes::install_github("wfmackey/absmapsdata")
 library(absmapsdata)
@@
 library(cowplot)
-
-knitr::opts_chunk$set(warning = FALSE, message = FALSE)
-options("citation_format" = "pandoc")
-BibOptions(check.entries = FALSE, style = "markdown")
 
@@
 
-```{r choro}
+```{r thyroiddata}
 states <- absmapsdata::state2011 %>% 
@@
   st_as_sf() 
+```
 
+```{r choro, eval=FALSE}
 aus_ggchoro <- ggplot(sa2thyroid_ERP) + 
@@
   invthm + coord_equal()
-aus_hexmap
+#aus_hexmap
 ```
@@
   invthm + guides(fill=FALSE)
-aus_ggcont
+#aus_ggcont
 
-ggsave(filename = "figs/aus_ggcont.png", plot = aus_ggcont,
-       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
+#ggsave(filename = "figs/aus_ggcont.png", plot = aus_ggcont,
+#       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
 
@@
 
-```{r}
+```{r contcart}
 
@@
 # Non - Contiguous Cartograms
-
+if (!file.exists("data/ncont.rda")) {
 ncont <- cartogram_ncont(sa2thyroid_ERP, k = 1.5,
@@
 save(ncont, file = "data/ncont.rda")
+}
+
+```
+
+```{r plotcontcart}
 load("data/ncont.rda")
@@
   invthm + guides(fill=FALSE)
-tas_ggncont
+#tas_ggncont
 
@@
   draw_plot(hobart, x = 0, width = 0.4, height = 0.4)
-aus_ggncont
+# aus_ggncont
 
-ggsave(filename = "figs/aus_ggncont.png", plot = aus_ggncont,
-       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
+#ggsave(filename = "figs/aus_ggncont.png", plot = aus_ggncont,
+#       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
 
@@
 
-```{r}
+```{r dorl}
 
@@
   geom_sf(aes(fill = SIR)) + 
-  scale_fill_identity()+
+  scale_fill_identity() +
   invthm + guides(fill = FALSE)
-aus_ggdorl
+# aus_ggdorl
 
-ggsave(filename = "figs/aus_ggdorl.png", plot = aus_ggdorl,
-       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
+#ggsave(filename = "figs/aus_ggdorl.png", plot = aus_ggdorl,
+#       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
 
@@
 
-```{r mapgrid, width = 8, height = 10}
+```{r mapgrid, width = 8, height = 10, eval=FALSE}
 aus_grid <- ggdraw(xlim = c(0, 2), ylim = c(0, 4)) +
@@
   device = "png", bg = "transparent", dpi = 300, width = 8, height = 10)
+```
+
+```{r tas_displays, width = 10, height = 4}
+library(gridExtra)
+grid.arrange(aus_ggcont, tas_ggncont, aus_ggdorl, ncol=3)
 ```

### 2020-10-05 kobakian-cook.tex
tassie plots

@@
 \begin{Schunk}
-\begin{Sinput}
-states <- absmapsdata::state2011 %>% 
-  filter(!state_name_2011 == "Other Territories") %>% 
-  rmapshaper::ms_simplify(keep = 0.25, keep_shapes = TRUE)
 
-sa2 <- absmapsdata::sa22011 %>% 
-  filter(state_name_2011 == "Tasmania") %>% 
-  filter(!st_is_empty(geometry)) %>% 
-  filter(!state_name_2011 == "Other Territories")
-
-# sa2 <- sa2 %>% rmapshaper::ms_simplify(keep = 0.05, keep_shapes = TRUE)
-
-SIR <- read_csv("data/SIR Downloadable Data.csv") %>% 
-  filter(SA2_name %in% sa2$sa2_name_2011) %>% 
-  dplyr::select(Cancer_name, SA2_name, Sex_name, p50) %>% 
-  filter(Cancer_name == "Thyroid", Sex_name == "Females")
-ERP <- read_csv("data/ERP.csv") %>%
-  filter(REGIONTYPE == "SA2", Time == 2011, Region %in% SIR$SA2_name) %>% 
-  dplyr::select(Region, Value)
-
-# Alternative maps
-# Join with sa2 sf object
-sa2thyroid_ERP <- SIR %>% 
-  left_join(sa2, ., by = c("sa2_name_2011" = "SA2_name")) %>%
-  left_join(., ERP %>% 
-              dplyr::select(Region, 
-              Population = Value), by = c("sa2_name_2011"= "Region")) %>% 
-  filter(!st_is_empty(geometry))
-
-sa2thyroid_ERP <- sa2thyroid_ERP %>% 
-  filter(!is.na(Population)) %>% 
-  mutate(SIR = map_chr(p50, aus_colours)) %>% 
-  st_as_sf()
-
-aus_ggchoro <- ggplot(sa2thyroid_ERP) + 
-  geom_sf(fill = "lightgrey", data = states %>% filter(state_name_2011=="Tasmania")) + 
-  geom_sf(aes(fill = SIR)) + 
-  scale_fill_identity() +invthm
-\end{Sinput}
-\end{Schunk}
-
-\begin{Schunk}
-\begin{Sinput}
-## Create centroids set
-centroids <- absmapsdata::sa22011 %>% 
-  filter(!st_is_empty(geometry)) %>% 
-  filter(state_name_2011 == "Tasmania") %>% 
- # filter(!sa2_name_2011 == "Lord Howe Island") %>% 
-  create_centroids(., "sa2_name_2011")
-
-## Create hexagon grid
-grid <- create_grid(centroids = centroids,
-                    hex_size = 0.2,
-                    buffer_dist = 5)
-
-## Allocate polygon centroids to hexagon grid points
-hex_allocated <- allocate(
-  centroids = centroids,
-  hex_grid = grid,
-  sf_id = "sa2_name_2011",
-  ## same column used in create_centroids
-  hex_size = 0.2,
-  ## same size used in create_grid
-  hex_filter = 10,
-  focal_points = capital_cities,
-  width = 35,
-  verbose = FALSE
-)
-
-## Prepare to plot
-fort_hex <- fortify_hexagon(data = hex_allocated,
-                            sf_id = "sa2_name_2011",
-                            hex_size = 0.2) %>% 
-            left_join(sa2thyroid_ERP %>% select(sa2_name_2011, SIR, p50))
-
-fort_aus <- sa2thyroid_ERP %>%
- # filter(!sa2_name_2011 == "Lord Howe Island") %>% 
-  fortify_sfc()
-
-fort_state <- states %>% 
-  filter(state_name_2011 == "Tasmania") %>% 
-  fortify_sfc() %>% 
-  filter(long < 159)
-
-## Make a plot
-library(ggplot2)
-aus_hexmap <- ggplot() +
-  geom_polygon(aes(x = long,  y = lat, group = interaction(state_name_2011, polygon)),
-               fill = "darkgrey",  data = fort_state) +
-  geom_polygon(aes(x = long,  y = lat,  group = interaction(sa2_name_2011, polygon)),
-               fill = "black",  colour = "darkgrey",  size = 0.1, data = fort_aus) +
-  geom_polygon(aes(x = long, y = lat, group = hex_id, fill = SIR), data = fort_hex) +
-  scale_fill_identity() +
-  invthm + coord_equal()
-aus_hexmap
-\end{Sinput}
-
-\includegraphics{kobakian-cook_files/figure-latex/fullhexmap-1} \end{Schunk}
-
-\begin{Schunk}
-\begin{Sinput}
-sa2thyroid_ERP <- st_transform(sa2thyroid_ERP, 3112)
-sa2thyroid_ERP <- sa2thyroid_ERP %>% 
-  mutate(sva = sqrt(as.numeric(Population)/as.numeric(albers_sqkm)))
-
-###############################################################################
-# Contiguous Cartograms
-
-cont <- sa2thyroid_ERP %>% 
-  mutate(Population = Population + 1) %>% 
-  cartogram_cont(., weight = "Population", itermax = 20) %>%
-  st_as_sf()
-
-save(cont, file = "data/cont.rda")
-load("data/cont.rda")
-
-aus_ggcont <- ggplot(cont) + 
-  geom_sf(fill = "darkgrey",  data = states %>% st_transform(., 3112) %>% filter(state_name_2011 == "Tasmania")) +
-  geom_sf(fill = "darkgrey",  data = sa2thyroid_ERP) +
-  geom_sf(aes(fill = SIR), colour = NA) + 
-  scale_fill_identity() + 
-  invthm + guides(fill=FALSE)
-aus_ggcont
-\end{Sinput}
-
-\includegraphics{kobakian-cook_files/figure-latex/alternatives-1} \begin{Sinput}
-ggsave(filename = "figs/aus_ggcont.png", plot = aus_ggcont,
-       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
-\end{Sinput}
-\end{Schunk}
-
-\begin{Schunk}
-\begin{Sinput}
-###############################################################################
-# Non - Contiguous Cartograms
-
-ncont <- cartogram_ncont(sa2thyroid_ERP, k = 1.5,
-                         weight = "Population") %>% 
-                          st_as_sf()
-
-save(ncont, file = "data/ncont.rda")
-load("data/ncont.rda")
-
-tas_ggncont <- ggplot(ncont %>% filter(state_name_2011 == "Tasmania")) + 
-  geom_sf(fill = "darkgrey",  data = states %>% st_transform(., 3112) %>% filter(state_name_2011 == "Tasmania")) +
-  geom_sf(fill = "darkgrey",  data = sa2thyroid_ERP) +
-  geom_sf(aes(fill = SIR), colour = NA) + 
-  scale_fill_identity() + 
-  invthm + guides(fill=FALSE)
-tas_ggncont
-\end{Sinput}
-
-\includegraphics{kobakian-cook_files/figure-latex/unnamed-chunk-1-1} \begin{Sinput}
-# Hobart
-hobart <- ggplot(ncont %>% filter(gcc_name_2011 == "Greater Hobart")) + 
-  geom_sf(fill = "darkgrey",  data = sa2thyroid_ERP %>% filter(gcc_name_2011 == "Greater Hobart")) +
-  geom_sf(aes(fill = SIR, size = 0.001), colour = "black") + 
-  scale_fill_identity() + 
-  scale_size_identity() +
-  invthm + guides(fill=FALSE) + 
-  theme(plot.background = element_rect(fill = "transparent", colour = NA)) + 
-  theme(panel.background = element_rect(fill = "transparent", colour = "white"))
-
-aus_ggncont <- ggdraw(xlim = c(0, 1), ylim = c(0, 2)) +
-  draw_plot(tas_ggncont, width = 1, height = 2) +
-  draw_plot(hobart, x = 0, width = 0.4, height = 0.4)
-aus_ggncont
-\end{Sinput}
-
-\includegraphics{kobakian-cook_files/figure-latex/unnamed-chunk-1-2} \begin{Sinput}
-ggsave(filename = "figs/aus_ggncont.png", plot = aus_ggncont,
-       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
-\end{Sinput}
-\end{Schunk}
-
-\begin{Schunk}
-\begin{Sinput}
-###############################################################################
-# Non - Contiguous Dorling Cartograms
-
-dorl <- sa2thyroid_ERP %>%
-  #mutate(pop = (Population/max(Population))*10) %>% # helpful for all of Australia
-  cartogram_dorling(., weight = "Population", k = 0.2, m_weight = 1) %>% st_as_sf()
-d <- st_bbox(dorl)
-aus_ggdorl <- ggplot(dorl) +
-  geom_sf(fill = "darkgrey",  data = states %>% st_transform(., 3112) %>% filter(state_name_2011 == "Tasmania")) +
-  geom_sf(fill = "darkgrey",  data = sa2thyroid_ERP) + 
-  geom_sf(aes(fill = SIR)) + 
-  scale_fill_identity()+
-  invthm + guides(fill = FALSE)
-aus_ggdorl
-\end{Sinput}
-
-\includegraphics{kobakian-cook_files/figure-latex/unnamed-chunk-2-1} \begin{Sinput}
-ggsave(filename = "figs/aus_ggdorl.png", plot = aus_ggdorl,
-       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
-\end{Sinput}
-\end{Schunk}
-
-\begin{Schunk}
-\begin{Sinput}
-aus_grid <- ggdraw(xlim = c(0, 2), ylim = c(0, 4)) +
-  draw_plot(aus_ggchoro, x = 0, y = 2, width = 1, height = 2) +
-  draw_plot(aus_ggcont,  x = 1, y = 2, width = 1, height = 2) +
-  draw_plot(aus_ggncont, x = 0, y = 0, width = 1, height = 2) +
-  draw_plot(aus_ggdorl,  x = 1, y = 0, width = 1, height = 2)
-
-aus_grid
-\end{Sinput}
-
-\includegraphics{kobakian-cook_files/figure-latex/mapgrid-1} \begin{Sinput}
-ggsave(filename = "figs/aus_grid.png", plot = aus_grid,
-  device = "png", bg = "transparent", dpi = 300, width = 8, height = 10)
-\end{Sinput}
-\end{Schunk}
+\includegraphics[width=0.9\linewidth]{kobakian-cook_files/figure-latex/tas_displays-1} \end{Schunk}
 
@@
 
-\begin{Schunk}
-\begin{Sinput}
-aus_hexmap
-\end{Sinput}
-\end{Schunk}
-
 \hypertarget{polygon-set}{%
@@
 uses only the areas in the state of Tasmania.
-
-\begin{Schunk}
-\begin{Sinput}
-data(capital_cities)
-\end{Sinput}
-\end{Schunk}
 
@@
 
-\begin{Schunk}
-\begin{Sinput}
-centroids <- create_centroids(shp_sf = tas_sa2, sf_id = "SA2_NAME16")
-\end{Sinput}
-\end{Schunk}
-
 \begin{figure}[h]
@@
 and the buffer distance.
-
-\begin{Schunk}
-\begin{Sinput}
-grid <- create_grid(centroids = centroids, hex_size = 0.2, buffer_dist = 1.2)
-\end{Sinput}
-\end{Schunk}
 
@@
 speed, but can decrease accuracy when width of the angle increases.
-
-\begin{Schunk}
-\begin{Sinput}
-hexmap_allocation <- allocate(
-  centroids = centroids %>% select(SA2_NAME16, longitude, latitude),
-  sf_id = "SA2_NAME16",
-  hex_grid = grid,
-  hex_size = 0.2, ## same size used in create_grid
-  hex_filter = 10,
-  width = 35,
-  focal_points = capital_cities,
-  verbose = TRUE)
-\end{Sinput}
-\end{Schunk}
 
@@
 
-\begin{Schunk}
-\begin{Sinput}
-install.packages("sugarbag")
-\end{Sinput}
-\end{Schunk}
-
 and the development version can be install from the GitHub repository:
 
-\begin{Schunk}
-\begin{Sinput}
-devtools::install_github("srkobakian","sugarbag")
-\end{Sinput}
-\end{Schunk}
-
 Load the library into your R session with:
-
-\begin{Schunk}
-\begin{Sinput}
-library(sugarbag)
-\end{Sinput}
-\end{Schunk}
 

### 2020-10-05 kobakian-cook.Rmd
added shortauthor to bib

@@
 This allows choropleth map displays to misrepresent the spatial distributions of human related statistics due to area-size bias [@BCM].
-Figure \ref{fig:melanoma-geo} is a choropleth map that uses colour to display the estimated Standardised Incidence Ratios (SIRs) of melanoma cancer for males for each of the Statistical Areas at Level 2 (SA2) used by the Australian Bureau of Statistics [-@abs2011].
+Figure \ref{fig:melanoma-geo} is a choropleth map that uses colour to display the estimated Standardised Incidence Ratios (SIRs) of melanoma cancer for males for each of the Statistical Areas at Level 2 (SA2) used by the @abs2011.
 The Australian choropleth map display draws attention to the expanse of light blue areas across the rural communities in all states.

### 2020-10-05 kobakian-cook.tex
added shortauthor to bib

@@
 for males for each of the Statistical Areas at Level 2 (SA2) used by the
-Australian Bureau of Statistics \citeyearpar{abs2011}. The Australian
-choropleth map display draws attention to the expanse of light blue
-areas across the rural communities in all states. The SA2s around Hobart
-stand out as more orange and red. To create this choropleth map the SA2
-polygons for 2011 from the Australian Bureau of Statistics.
+\citet{abs2011}. The Australian choropleth map display draws attention
+to the expanse of light blue areas across the rural communities in all
+states. The SA2s around Hobart stand out as more orange and red. To
+create this choropleth map the SA2 polygons for 2011 from the Australian
+Bureau of Statistics.
 

### 2020-10-06 kobakian-cook.Rmd
Rearrange figures and replace references

@@
 library(kableExtra)
-library(RefManageR)
-options("citation_format" = "pandoc")
-BibOptions(check.entries = FALSE, style = "markdown")
-
 library(sp)
@@
 library(sugarbag)
-# remotes::install_github("wfmackey/absmapsdata")
-library(absmapsdata)
 library(tidyverse)
@@
 library(cowplot)
+
+# remotes::install_github("wfmackey/absmapsdata")
+library(absmapsdata)
+
+library(RefManageR)
+options("citation_format" = "pandoc")
+BibOptions(check.entries = FALSE, style = "markdown")
 
@@
 This allows choropleth map displays to misrepresent the spatial distributions of human related statistics due to area-size bias [@BCM].
-Figure \ref{fig:melanoma-geo} is a choropleth map that uses colour to display the estimated Standardised Incidence Ratios (SIRs) of melanoma cancer for males for each of the Statistical Areas at Level 2 (SA2) used by the @abs2011.
+Figure \ref{fig:thyroid-geo} is a choropleth map that uses colour to display the estimated Standardised Incidence Ratios (SIRs) of melanoma cancer for males for each of the Statistical Areas at Level 2 (SA2) used by the @abs2011.
 The Australian choropleth map display draws attention to the expanse of light blue areas across the rural communities in all states.
@@
 To create this choropleth map the SA2 polygons for 2011 from the Australian Bureau of Statistics.
+
+```{r thyroiddata}
+sa2 <- absmapsdata::sa22011 %>% 
+  filter(!st_is_empty(geometry)) %>% 
+  filter(!state_name_2011 == "Other Territories") %>% 
+  filter(!sa2_name_2011 == "Lord Howe Island")
+
+# sa2 <- sa2 %>% rmapshaper::ms_simplify(keep = 0.05, keep_shapes = TRUE)
+
+SIR <- read_csv("data/SIR Downloadable Data.csv") %>% 
+  filter(SA2_name %in% sa2$sa2_name_2011) %>% 
+  dplyr::select(Cancer_name, SA2_name, Sex_name, p50) %>% 
+  filter(Cancer_name == "Thyroid", Sex_name == "Females")
+ERP <- read_csv("data/ERP.csv") %>%
+  filter(REGIONTYPE == "SA2", Time == 2011, Region %in% SIR$SA2_name) %>% 
+  dplyr::select(Region, Value)
+
+# Alternative maps
+# Join with sa2 sf object
+sa2thyroid_ERP <- SIR %>% 
+  left_join(sa2, ., by = c("sa2_name_2011" = "SA2_name")) %>%
+  left_join(., ERP %>% 
+              dplyr::select(Region, 
+              Population = Value), by = c("sa2_name_2011"= "Region")) %>% 
+  filter(!st_is_empty(geometry))
+
+sa2thyroid_ERP <- sa2thyroid_ERP %>% 
+  #filter(!is.na(Population)) %>% 
+  filter(!sa2_name_2011 == "Lord Howe Island") %>% 
+  mutate(SIR = map_chr(p50, aus_colours)) %>% 
+  st_as_sf() 
+```
+
+```{r choro, fig.cap = "A choropleth map of the Statistical Areas of Australia at Level 2.
+The colours communicate the value of the estimated SIR of Thyroid cancer for females, ranging from much lower than average (blue) to much higher than average (red)"}
+aus_ggchoro <- ggplot(sa2thyroid_ERP) + 
+  geom_sf(aes(fill = SIR), size = 0.1) + 
+  scale_fill_identity() + invthm
+```
 
@@
 
-```{=tex}
-\begin{figure}[h]
-\centering
-\includegraphics[width=14cm]{figs/aus_melanoma_p.png}
-\caption{\label{fig:melanoma-geo}A choropleth map of the Statistical Areas of Australia at Level 2.
-The colours communicate the value of the estimated SIR of Melanoma for males, they range from much lower than average (blue) to much higher than average (red)}
-\end{figure}
-```
 Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing the population in each administrative area [@TAAM].
@@
 
-```{r thyroiddata}
-states <- absmapsdata::state2011 %>% 
-  filter(!state_name_2011 == "Other Territories") %>% 
-  rmapshaper::ms_simplify(keep = 0.25, keep_shapes = TRUE)
-
-sa2 <- absmapsdata::sa22011 %>% 
-  filter(state_name_2011 == "Tasmania") %>% 
-  filter(!st_is_empty(geometry)) %>% 
-  filter(!state_name_2011 == "Other Territories")
-
-# sa2 <- sa2 %>% rmapshaper::ms_simplify(keep = 0.05, keep_shapes = TRUE)
-
-SIR <- read_csv("data/SIR Downloadable Data.csv") %>% 
-  filter(SA2_name %in% sa2$sa2_name_2011) %>% 
-  dplyr::select(Cancer_name, SA2_name, Sex_name, p50) %>% 
-  filter(Cancer_name == "Thyroid", Sex_name == "Females")
-ERP <- read_csv("data/ERP.csv") %>%
-  filter(REGIONTYPE == "SA2", Time == 2011, Region %in% SIR$SA2_name) %>% 
-  dplyr::select(Region, Value)
-
-# Alternative maps
-# Join with sa2 sf object
-sa2thyroid_ERP <- SIR %>% 
-  left_join(sa2, ., by = c("sa2_name_2011" = "SA2_name")) %>%
-  left_join(., ERP %>% 
-              dplyr::select(Region, 
-              Population = Value), by = c("sa2_name_2011"= "Region")) %>% 
-  filter(!st_is_empty(geometry))
-
-sa2thyroid_ERP <- sa2thyroid_ERP %>% 
-  filter(!is.na(Population)) %>% 
-  mutate(SIR = map_chr(p50, aus_colours)) %>% 
-  st_as_sf() 
-```
-
-```{r choro, eval=FALSE}
-aus_ggchoro <- ggplot(sa2thyroid_ERP) + 
-  geom_sf(fill = "lightgrey", data = states %>% filter(state_name_2011=="Tasmania")) + 
-  geom_sf(aes(fill = SIR)) + 
-  scale_fill_identity() +invthm
-```
-
-```{r fullhexmap}
+```{r fullhexmap, fig.cap = "A choropleth hexagon tile map of the Statistical Areas of Australia at Level 2.
+The colours communicate the value of the estimated SIR of Thyroid cancer for females, ranging from much lower than average (blue) to much higher than average (red)"}
 ## Create centroids set
-centroids <- absmapsdata::sa22011 %>% 
-  filter(!st_is_empty(geometry)) %>% 
-  filter(state_name_2011 == "Tasmania") %>% 
- # filter(!sa2_name_2011 == "Lord Howe Island") %>% 
+centroids <- sa2 %>% 
   create_centroids(., "sa2_name_2011")
@@
 fort_aus <- sa2thyroid_ERP %>%
- # filter(!sa2_name_2011 == "Lord Howe Island") %>% 
   fortify_sfc()
 
-fort_state <- states %>% 
-  filter(state_name_2011 == "Tasmania") %>% 
-  fortify_sfc() %>% 
-  filter(long < 159)
-
 ## Make a plot
-library(ggplot2)
 aus_hexmap <- ggplot() +
-  geom_polygon(aes(x = long,  y = lat, group = interaction(state_name_2011, polygon)),
-               fill = "darkgrey",  data = fort_state) +
   geom_polygon(aes(x = long,  y = lat,  group = interaction(sa2_name_2011, polygon)),
@@
   invthm + coord_equal()
-#aus_hexmap
+aus_hexmap
 ```
@@
 ```{r alternatives}
+# Project data 
 sa2thyroid_ERP <- st_transform(sa2thyroid_ERP, 3112)
@@
 
+if (!file.exists("data/ncont.rda")) {
 cont <- sa2thyroid_ERP %>% 
@@
 
-save(cont, file = "data/cont.rda")
+save(cont, file = "data/cont.rda") }
+
 load("data/cont.rda")
@@
 aus_ggcont <- ggplot(cont) +
-  geom_sf(fill = "darkgrey",  data = states %>% st_transform(., 3112) %>% filter(state_name_2011 == "Tasmania")) +
+
   geom_sf(fill = "darkgrey",  data = sa2thyroid_ERP) +
   geom_sf(aes(fill = SIR), colour = NA) + 
-  scale_fill_identity() + 
-  invthm + guides(fill=FALSE)
+  scale_fill_identity() + guides(fill=FALSE)
 #aus_ggcont
@@
 
-tas_ggncont <- ggplot(ncont %>% filter(state_name_2011 == "Tasmania")) + 
-  geom_sf(fill = "darkgrey",  data = states %>% st_transform(., 3112) %>% filter(state_name_2011 == "Tasmania")) +
+aus_ggncont <- ggplot(ncont %>% filter(state_name_2011 == "Tasmania")) + 
   geom_sf(fill = "darkgrey",  data = sa2thyroid_ERP) +
@@
   scale_fill_identity() + 
-  invthm + guides(fill=FALSE)
-#tas_ggncont
-
-# Hobart
-hobart <- ggplot(ncont %>% filter(gcc_name_2011 == "Greater Hobart")) + 
-  geom_sf(fill = "darkgrey",  data = sa2thyroid_ERP %>% filter(gcc_name_2011 == "Greater Hobart")) +
-  geom_sf(aes(fill = SIR, size = 0.001), colour = "black") + 
-  scale_fill_identity() + 
-  scale_size_identity() +
-  invthm + guides(fill=FALSE) + 
-  theme(plot.background = element_rect(fill = "transparent", colour = NA)) + 
-  theme(panel.background = element_rect(fill = "transparent", colour = "white"))
-
-aus_ggncont <- ggdraw(xlim = c(0, 1), ylim = c(0, 2)) +
-  draw_plot(tas_ggncont, width = 1, height = 2) +
-  draw_plot(hobart, x = 0, width = 0.4, height = 0.4)
-# aus_ggncont
-
-#ggsave(filename = "figs/aus_ggncont.png", plot = aus_ggncont,
-#       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
+  guides(fill=FALSE)
+#aus_ggncont
 
@@
 
-###############################################################################
 # Non - Contiguous Dorling Cartograms
@@
 aus_ggdorl <- ggplot(dorl) +
-  geom_sf(fill = "darkgrey",  data = states %>% st_transform(., 3112) %>% filter(state_name_2011 == "Tasmania")) +
   geom_sf(fill = "darkgrey",  data = sa2thyroid_ERP) + 
@@
 
-The choropleth map that uses the geographic shapes of areas can be seen in figure \ref{fig:melanoma-geo}.
+The choropleth map that uses the geographic shapes of areas can be seen in figure \ref{fig:thyroid-geo}.
 Figure \ref{fig:melanoma-hex} displays the Australian areas with equally sized hexagons.

### 2020-10-12 kobakian-cook.Rmd
New tas displays

@@
 abstract: >
-  This algorithm creates a tessellated hexagon display to represent a set of the spatial polygons.
-It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units.
-The algorithm creates a display that showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps.
+  The algorithm presented creates a display that uses tessellated hexagons to represent a set of spatial polygons.
+It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units, in light of their positions to points of interest.
+The display showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps.
 Spatial distributions have been presented on alternative representations of geography for many years.
-In modern times, interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption.
+In modern times, interactivity and animation have allowed alternative displays to play a larger role.
+Alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption.
 Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
@@
                       eval = TRUE,
-                      out.width = "90%",
+                      out.width = "95%",
                       retina = 3,
                       dev = "png",
-                      fig.pos = "center")
+                      dpi = 300)
 ```
@@
 options("citation_format" = "pandoc")
-BibOptions(check.entries = FALSE, style = "markdown")
+BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')
 
@@
 This allows choropleth map displays to misrepresent the spatial distributions of human related statistics due to area-size bias [@BCM].
-Figure \ref{fig:thyroid-geo} is a choropleth map that uses colour to display the estimated Standardised Incidence Ratios (SIRs) of melanoma cancer for males for each of the Statistical Areas at Level 2 (SA2) used by the @abs2011.
-The Australian choropleth map display draws attention to the expanse of light blue areas across the rural communities in all states.
-The SA2s around Hobart stand out as more orange and red.
-To create this choropleth map the SA2 polygons for 2011 from the Australian Bureau of Statistics.
+Figure \ref{fig:choro} is a choropleth map that uses colour to display the estimated Standardised Incidence Ratios (SIRs) of thyroid cancer for males for each of the Statistical Areas at Level 2 (SA2) used by the @abs2011.
+The Australian choropleth map display draws attention to the expanse of dark and light blue areas across the rural communities in all states.
+The SA2s around Brisbane stand out as more orange and red.
 
@@
   scale_fill_identity() + invthm
+aus_ggchoro
 ```
@@
 The solutions to this visualisation problem begin with the geography.
-Alternative maps shift the focus from land area and shape, to the value of the statistics in a group of areas [@ACCAC].
-Different styles of cartograms apply transformations to the geographic areas, to highlight the values of the value of the statistic of interest.
-These displays result in a distortion of the map space to represent differences in the statistic across the areas [@ACCAC] as the statistic of interest is used to determine the cartogram layout.
+Alternative maps shift the focus from land area and shape, to the value of the statistics in a collection of areas [@ACCAC].
+Each style of cartogram applies a different transformation to the geographic areas, to highlight the values of the statistic of interest.
+These displays result in a distortion of the map space to represent features of the distribution across the areas [@ACCAC] as the statistic of interest is used to determine the cartogram layout.
 
@@
 These alternative map displays focus on the relationship between neighbours, attempting to preserve connections, and disregard the unique shapes of the administrative boundaries.
-Figure \ref{fig:nsw_grid} shows a collection of alternative map displays, this includes a) a contiguous cartogram, b) a non-contiguous cartogram, c) a Dorling cartogram and d) a hexagon tile map.
-Each Statistical Area at Level 2 (SA2) [@abs2011] was designed to represent a community.
-These administrative areas are often used to aggregate census data and used to understand demographics of the Australian population.
+Figure \ref{fig:tas_displays} shows a collection of alternative map displays, this includes a) a contiguous cartogram, b) a non-contiguous cartogram, and c) a Dorling cartogram.
 
@@
 The unique shapes of boundaries can be helpful for orienting users but may not contribute to their understanding of the spatial disease distribution as many of the communities are not visible in a choropleth display [@TVSSS].
+Each Statistical Area at Level 2 (SA2) [@abs2011] was designed to represent a community.
+These administrative areas are often used to aggregate census data and used to understand demographics within communities of the Australian population.
 This presents an opportunity for explicit map transformations to improve communication of distributions [@CBATCC].
-In figure \ref{fig:nsw_grid}a) the choropleth map is presented with the alternative maps to allow for comparisons to be made.
+In figure \ref{fig:tas_displays} the choropleth map can be seen underneath each alternative map display to allow for comparisons to be made.
 
-```{r fullhexmap, fig.cap = "A choropleth hexagon tile map of the Statistical Areas of Australia at Level 2.
-The colours communicate the value of the estimated SIR of Thyroid cancer for females, ranging from much lower than average (blue) to much higher than average (red)"}
+```{r fullhexmap, fig.cap = "A hexagon tile map of the Statistical Areas of Australia at Level 2.
+The colours communicate the value of the estimated SIR of thyroid cancer for females, ranging from much lower than average (blue) to much higher than average (red)"}
+
+if (!file.exists("data/aus_hexmap.rda")) {
+
 ## Create centroids set
@@
 ## Allocate polygon centroids to hexagon grid points
-hex_allocated <- allocate(
+aus_hexmap <- allocate(
   centroids = centroids,
@@
 
+save(aus_hexmap, file = "data/aus_hexmap.rda") }
+
+load("data/aus_hexmap.rda")
+
 ## Prepare to plot
-fort_hex <- fortify_hexagon(data = hex_allocated,
+fort_hex <- fortify_hexagon(data = aus_hexmap,
                             sf_id = "sa2_name_2011",
@@
   invthm + coord_equal()
-aus_hexmap
+
 ```
@@
 ```{r alternatives}
-# Project data 
-sa2thyroid_ERP <- st_transform(sa2thyroid_ERP, 3112)
+# Projected data 
+sa2thyroid_ERP <- st_transform(sa2thyroid_ERP, 3112) %>% filter(state_name_2011 == "Tasmania")
 sa2thyroid_ERP <- sa2thyroid_ERP %>% 
@@
 
-###############################################################################
 # Contiguous Cartograms
@@
 
-aus_ggcont <- ggplot(cont) +
-
-  geom_sf(fill = "darkgrey",  data = sa2thyroid_ERP) +
+tas_ggcont <- ggplot(cont) + 
+  geom_sf(fill = "lightgrey", colour = "black", data = sa2thyroid_ERP) +
   geom_sf(aes(fill = SIR), colour = NA) + 
-  scale_fill_identity() + guides(fill=FALSE)
-#aus_ggcont
-
-#ggsave(filename = "figs/aus_ggcont.png", plot = aus_ggcont,
-#       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
+  scale_fill_identity() + guides(fill=FALSE) +
+  theme_map() + ggtitle("a")
+#tas_ggcont
 
@@
 ```{r contcart}
+# Non - Contiguous Cartograms
 
-###############################################################################
-# Non - Contiguous Cartograms
 if (!file.exists("data/ncont.rda")) {
@@
 
-aus_ggncont <- ggplot(ncont %>% filter(state_name_2011 == "Tasmania")) + 
-  geom_sf(fill = "darkgrey",  data = sa2thyroid_ERP) +
+tas_ggncont <- ggplot(ncont %>% filter(state_name_2011 == "Tasmania")) + 
+  geom_sf(fill = "lightgrey", colour = "black",  data = sa2thyroid_ERP) +
   geom_sf(aes(fill = SIR), colour = NA) + 
   scale_fill_identity() + 
-  guides(fill=FALSE)
-#aus_ggncont
+  guides(fill=FALSE) +
+  theme_map() + ggtitle("b")
+#tas_ggncont
 
@@
 ```{r dorl}
-
 # Non - Contiguous Dorling Cartograms
@@
 dorl <- sa2thyroid_ERP %>% 
+  filter(!is.na(Population)) %>% 
   #mutate(pop = (Population/max(Population))*10) %>% # helpful for all of Australia
@@
 d <- st_bbox(dorl)
-aus_ggdorl <- ggplot(dorl) +
-  geom_sf(fill = "darkgrey",  data = sa2thyroid_ERP) + 
+tas_ggdorl <- ggplot(dorl) +
+  geom_sf(fill = "lightgrey", colour = "black",  data = sa2thyroid_ERP) + 
   geom_sf(aes(fill = SIR)) + 
   scale_fill_identity() +
-  invthm + guides(fill = FALSE)
-# aus_ggdorl
-
-#ggsave(filename = "figs/aus_ggdorl.png", plot = aus_ggdorl,
-#       device = "png", bg = "transparent", dpi = 300,  width = 7, height = 6)
-
+  guides(fill = FALSE) +
+  theme_map() + ggtitle("c")
+#tas_ggdorl
 ```
 
-```{r mapgrid, width = 8, height = 10, eval=FALSE}
-aus_grid <- ggdraw(xlim = c(0, 2), ylim = c(0, 4)) +
-  draw_plot(aus_ggchoro, x = 0, y = 2, width = 1, height = 2) +
-  draw_plot(aus_ggcont,  x = 1, y = 2, width = 1, height = 2) +
-  draw_plot(aus_ggncont, x = 0, y = 0, width = 1, height = 2) +
-  draw_plot(aus_ggdorl,  x = 1, y = 0, width = 1, height = 2)
-
-aus_grid
-
-ggsave(filename = "figs/aus_grid.png", plot = aus_grid,
-  device = "png", bg = "transparent", dpi = 300, width = 8, height = 10)
-```
-
-```{r tas_displays, width = 10, height = 4}
+```{r tas_displays, width = 10, height = 3, fig.cap = "The three displays show alternative maps of the Statistical Areas at Level 2 in the Australian state of Tasmania.
+These alternatives show the (a) contiguous cartogram, (b) non-contiguous cartogram and (c) Dorling cartogram of Tasmania."}
 library(gridExtra)
-grid.arrange(aus_ggcont, tas_ggncont, aus_ggdorl, ncol=3)
+grid.arrange(tas_ggcont, tas_ggncont, tas_ggdorl, ncol=3)
 ```
@@
 The impact of a disease over connected communities can be seen by allowing the boundaries to maintain connection in the transformed display.
-The contiguous cartogram displayed in figure \ref{fig:nsw_grid}b) draws attention to smaller geographic units when they are rescaled according to the population [@DMAHP].
+The contiguous cartogram displayed in figure \ref{fig:tas_displays}b) draws attention to smaller geographic units when they are rescaled according to the population [@DMAHP].
 These new shapes can now be coloured to represent a second variable.
 This display can create twisted and unfamiliar shapes from the geographic units as the algorithms must satisfy the topology conditions, especially when there are communities located geographically far from their neighbours [@TVSSS].
-This shown in the northern SA2s of Tasmania with an average (yellow) estimated SIR of Melanoma for males.
+This shown in the northern SA2s of Tasmania with an average (yellow) estimated SIR of thyroid for males.
 
@@
 
-The non-contiguous cartogram in figure \ref{fig:nsw_grid}c) also uses the population to rescale the geographic units.
+The non-contiguous cartogram in figure \ref{fig:tas_displays}c) also uses the population to rescale the geographic units.
 Unlike the contiguous cartogram, the SA2 areas maintain their geographic shape, but they may not retain the connection with their neighbours.
@@
 The Dorling cartogram presents each geographic unit as a circle, the size of the circle is scaled according to the population value of each area [@ACTUC].
-Figure \ref{fig:nsw_grid}d) shows the Tasmania SA2 areas as an individual circle located as close as possible to the geographic centroid location.
-This map draws attention to the collection of coastal cities in Tasmania that were not apparent in figure \ref{fig:nsw_grid} a), b) or c).
-
-<!-- When the population is the statistic of interest, the result is a population cartogram.
-They fail to preserve a recognisable display due to the difference in size of metropolitan and rural areas [@ACTUC], [@GOINO].
--->
-
-<!-- Contiguous cartograms alter the shape of areas, while preserving boundary relationships of neighbours.
-Non-contiguous cartograms maintain the geographic shape of each geographic area, but will lose the connection to neighbours as the polygon for each geographic area shrinks or grows.
--->
+Figure \ref{fig:tas_displays}c) shows the Tasmania SA2 areas as an individual circle located as close as possible to the geographic centroid location.
+This map draws attention to the collection of coastal cities in Tasmania that were not apparent in figure \ref{fig:tas_displays} a), or b).
 
@@
 
-There are three key steps performed to create a tessellated hexagon tile map.
-First derive the set of centroids from the polygons provided, then create the grid of hexagons locations.
+The result of the algorithm is a display that emphasises the densely populated geographic regions surrounding the capital cities in Australia.
+Each capital city forms it's own layer of connected hexagons.
+Figure \ref{fig:hexmap} allows the distributions in the capital cities to be viewed at a deeper scale.
+Sydney is now notable for the considerable amount of red areas, not just for the surrounding orange areas around the New South Wales capital visible in the choropleth display in Figure \ref{fig:choro}.
+Brisbane and Perth also draw attention for the many orange areas.
+Interestingly there is no clear divide between rural and urban SA2 areas as Melbourne, Darwin, Adelaide and Hobart have low rates of thyroid cancer diagnosis.
+
+```{r hexmap, fig.cap = "A hexagon tile map of the Statistical Areas of Australia at Level 2.
+The colours communicate the value of the estimated SIR of thyroid for males, they range from much lower than average (blue) to much higher than average (red)."}
+aus_hexmap
+```
+
+There are three key steps performed to create the tessellated hexagon tile map shown in Figure \ref{fig:hexmap}.
+First, derive the set of centroids from the polygons provided, then create the grid of hexagons locations.
 These two steps are defined in the blue left column of the flow chart in Figure \ref{fig:sugarbag_flow}.
@@
 
-Only two inputs are necessary to begin using the algorithm, the shape file, and the id variable. The id column should uniquely identify each geographic unit in the shape file.
+Only two inputs are necessary to begin using the algorithm, the shape file, and the id variable. The id variable should uniquely identify each geographic unit in the shape file.
 
@@
 
-```{hexmap, fig.cap = "A hexagon tile map of the Statistical Areas of Australia at Level 2.
-The colours communicate the value of the estimated SIR of Melanoma for males, they range from much lower than average (blue) to much higher than average (red)."}
-aus_hexmap
-```
-
 #### Polygon set
@@
 
-```{r cents}
-centroids <- create_centroids(shp_sf = tas_sa2, sf_id = "SA2_NAME16")
+```{r centroids_plot, fig.cap = "The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2.
+A choropleth map (a) of Standardised Incidence Rates (SIRs) is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented."}
+centroids <- create_centroids(
+  shp_sf = sa2 %>% filter(state_name_2011 == "Tasmania"), 
+  sf_id = "sa2_name_2011")
+
+hex_size <- .2
+buffer_dist <- 2
+
+bbox <- tibble(min = c(min(centroids$longitude), min(centroids$latitude)),
+  max = c(max(centroids$longitude), max(centroids$latitude)))
+
+grid <- tibble::as_tibble(expand.grid(hex_long = seq(bbox$min[1] - buffer_dist,
+  bbox$max[1] + buffer_dist,
+  hex_size),
+  hex_lat = seq(bbox$min[2] - buffer_dist,
+    bbox$max[2] + buffer_dist,
+    hex_size)))
+
+fort_tas <- fort_aus %>% filter(state_name_2011 == "Tasmania")
+
+tas_centroids <- ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "lightgrey", colour = "black", size = 0.01) + 
+  geom_point(aes(x=longitude, y = latitude, colour = SIR), size = 3, shape = 19,
+             data = st_drop_geometry(sa2thyroid_ERP) %>% 
+               select(sa2_name_2011, SIR) %>%  
+               left_join(centroids)) +
+  scale_colour_identity() +
+  theme_void() + 
+  coord_equal()
+
+tas_hexmap <- ggplot() +
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "lightgrey", colour = "black", size = 0.01) + 
+  geom_polygon(aes(x = long, y = lat, group = hex_id, fill = SIR),
+               data = fort_hex %>% filter(sa2_name_2011 %in% fort_tas$sa2_name_2011)) +
+  scale_fill_identity() +
+  theme_void() + 
+  coord_equal()
+
+grid.arrange(tas_centroids, tas_hexmap, nrow=1)
 ```
 
-```{=tex}
-\begin{figure}[h]
-\centering
-\includegraphics[width=14cm]{figs/1centroids.png}
-\caption{\label{fig:centroids_plot}The geographic shapes of the Statistical Areas of Tasmania at Level 2. The points show the locations of the centroids of the SA2 areas.}
-\end{figure}
-```
 #### Step 2: Create the hexagon grid points
@@
 
-```{r grid}
-grid <- create_grid(centroids = centroids, hex_size = 0.2, buffer_dist = 1.2)
+```{r grid1}
+#grid <- create_grid(centroids = centroids, hex_size = 0.2, buffer_dist = 1.2)
+
+g1 <- ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "lightgrey", colour = "black", size = 0.01) + 
+  geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#374926") + theme_void() + 
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#64b1be", data = grid, size = 1.5) +
+  coord_equal() + ggtitle("a")
 ```
@@
 
-<!-- ```{r grid2, fig.cap = "Grid points to create a tile map.", out.width = "100%", echo = FALSE} -->
+```{r grid2, fig.cap = "Complete set of grid points to create a tile map.", height = 4}
+# Find every second latitude
+shift_lat <- grid %>% dplyr::select(hex_lat) %>%
+  dplyr::distinct() %>%
+  dplyr::filter(dplyr::row_number() %% 2 == 1) %>% unlist()
 
-<!-- knitr::include_graphics(path = "figs2grid.png") -->
+# Shift the longitude of every second latitude to the right to make hex structure
+grid <- grid %>%
+  dplyr::mutate(hex_long = ifelse(hex_lat %in% shift_lat, hex_long,
+    hex_long + (hex_size / 2))) %>%
+  dplyr::mutate(id=1:NROW(.))  %>%
+  dplyr::mutate(assigned=FALSE)
 
-<!-- ``` -->
+g2 <- ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "lightgrey", colour = "black", size = 0.01) + 
+  geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#374926") + theme_void() + 
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#64b1be", data = grid, size = 1.5) +
+  coord_equal() + ggtitle("b")
 
-```{=tex}
-\begin{figure}[h]
-\centering
-\includegraphics[width=16cm]{figs/2grid.png}
-\caption{\label{fig:grid2}Grid points to create a hexagon tile map.}
-\end{figure}
+grid.arrange(g1, g2, nrow = 1)
 ```
+
 ##### Rolling windows
@@
 The amount of rows in each latitude group and the amount of columns in each longitude group are used as the width of rolling windows.
-The rolling windows can be seen on the bottom and right of the grid shown in Figure \ref{fig:filter-grid}.
+The rolling windows can be seen on the bottom and right of the grid shown in Figure \ref{fig:grid3}.
 This will tailor the available grid points to those most likely to be used.
@@
 
-<!-- ```{r filter-grid, fig.cap = "All possible hexagon locations from the initial grid are shown with blue outlines.
-The blue dots show the grid points left to choose from after the buffer step.
-The rolling windows show the collections of rows and columns used to filter the hexagon locations.", echo = FALSE, out.width = "100%"} -->
+```{r grid3, fig.cap = "The remaining hexagon locations from all the possible points in the initial grid after the buffer is applied.
+The blue dots show the grid points left to choose from after the buffer step."}
 
-<!-- knitr::include_graphics(path = "figs3grid.png", dpi = 300) -->
+full_grid <- grid <- grid %>%
+  mutate(hex_long_int = dense_rank(hex_long)-1,
+    hex_lat_int = dense_rank(hex_lat)-1)
 
-<!-- ``` -->
+nlong <- length(unique(grid$hex_long))
+nlat <- length(unique(grid$hex_lat))
 
-```{=tex}
-\begin{figure}[h]
-\centering
-\includegraphics[width=10cm]{figs/3grid.png}
-\caption{\label{fig:filter-grid}The remaining hexagon locations from all the possible points in the initial grid after the buffer is applied.
-The blue dots show the grid points left to choose from after the buffer step.}
-\end{figure}
+  # Add grid row and column values to centroids data set 
+  centroids <- centroids %>%
+    mutate(
+      # long int for integer value of longitude column
+      long_int = round((longitude - min(grid$hex_long)) / 
+                         (max(grid$hex_long) - min(grid$hex_long)) * nlong, 0),
+      # lat int for integer value of latitude column
+      lat_int = round((latitude - min(grid$hex_lat)) / 
+                        (max(grid$hex_lat) - min(grid$hex_lat)) * nlat, 0)
+    )
+
+  # Amount of lats and longs in each group of rows and columns
+  lat_size <- round(nlat / 20, 0)
+  long_size <- round(nlong / 20, 0)
+
+  # Make a list of the min and max of the groups
+  # Effectively creates manual sliding windows
+  nlat_list <- purrr::map2(seq(1:nlat), lat_size + seq(1:nlat), c)
+  nlong_list <- purrr::map2(seq(1:nlong), long_size + seq(1:nlong), c)
+
+  # LATITUDE ROWS FILTER
+
+  # Function to return the centroids that fall in the latitude window
+  lat_window <- function(bounds, cents = centroids, maximum = nlat) {
+
+    max_int <- min(bounds[2], maximum)
+
+    cents_in <- filter(cents, between(lat_int, bounds[1], max_int))
+    return(cents_in)
+  }
+
+  # Function to return the centroids that fall in the longitude window
+  long_window <- function(bounds, cents = centroids, maximum = nlong) {
+
+    max_int <- bounds[2]
+
+    while (max_int > maximum) {
+      max_int <- max_int - 1
+    }
+
+    cents_in <- filter(cents, between(long_int, bounds[1], max_int))
+    return(cents_in)
+  }
+
+  # amount of latitude in sliding window
+  lat_windows <- purrr::map(.x = nlat_list, .f = lat_window, centroids, nlat)
+
+  # LONGITUDE COLS FILTER
+  long_windows <- purrr::map(.x = nlong_list, .f = long_window, centroids, nlong)
+
+  #########################################################
+  ###                ROLLING MIN & MAX                  ###
+
+  # DEFINE FUNCTION
+  # find the min and max longitude for each latitude
+  range_rows <- purrr::map_dfr(
+    .x = lat_windows,
+    .f = function(data) {
+      data %>%
+        dplyr::summarise(
+          long_min = ifelse(purrr::is_empty(long_int), NA, min(data$long_int)),
+          long_max = ifelse(purrr::is_empty(long_int), NA, max(data$long_int))
+        )
+    }
+  )
+
+  # find the min and max longitude for each latitude
+  range_cols <- purrr::map_dfr(.x = long_windows, .f = function(data) {
+    data %>%
+      dplyr::summarise(
+        lat_min = ifelse(purrr::is_empty(lat_int), NA, min(data$lat_int)),
+        lat_max = ifelse(purrr::is_empty(lat_int), NA, max(data$lat_int))
+      )
+  })
+
+  # find the min and max longitude for each latitude
+  range_rows <- purrr::map_dfr(.x = lat_windows, .f = function(data) {
+      data %>%
+        dplyr::summarise(
+          long_min = ifelse(purrr::is_empty(long_int), NA, min(data$long_int)),
+          long_max = ifelse(purrr::is_empty(long_int), NA, max(data$long_int))
+        )
+    }
+  )
+
+  # find the min and max longitude for each latitude
+  range_cols <- purrr::map_dfr(.x = long_windows, .f = function(data) {
+    data %>%
+      dplyr::summarise(
+        lat_min = ifelse(purrr::is_empty(lat_int), NA, min(data$lat_int)),
+        lat_max = ifelse(purrr::is_empty(lat_int), NA, max(data$lat_int))
+      )
+  })
+
+  #########################################################
+  ###                ROLLING AVERAGES                   ###
+
+  mean_range <- function(bounds, data) {
+    data[bounds[1]:min(bounds[2], NROW(data)), ] %>%
+      dplyr::summarise(across(ends_with("min"), 
+                         ~mean(.x, na.rm = TRUE), .names = "mean_{col}"),
+                       across(ends_with("max"), 
+                              ~mean(.x, na.rm = TRUE), .names = "mean_{col}")) %>% 
+      # in cases where all values are NA mean is Nan
+      # make mean value of NaN be NA
+      dplyr::summarise(across(starts_with("mean"), ~ifelse(.x == "NaN", NA, .x)))
+  }
+
+  # smooth the minimums
+  av_range_rows <- purrr::map_dfr(.x = nlat_list, mean_range, range_rows) %>%
+    bind_cols(lat_id = c(seq(1:nlat) + lat_size), .)
+
+  # smooth the minimums
+  av_range_cols <- purrr::map_dfr(.x = nlong_list, mean_range, range_cols) %>%
+    bind_cols(long_id = c(seq(1:nlong) + round(long_size / 2)), .)
+
+  # APPLY A BUFFER
+  # change buffer to amount of hexagons (ints) either side
+  hex_buffer <- floor(buffer_dist / hex_size)
+
+grid <- grid %>%
+    left_join(., av_range_rows, by = c("hex_lat_int" = "lat_id")) %>%
+    left_join(., av_range_cols, by = c("hex_long_int" = "long_id")) %>%
+    rowwise() %>%
+    mutate(long_buffer = ifelse(between(
+      hex_long_int, mean_long_min - hex_buffer,
+      mean_long_max + hex_buffer), "in", "out")) %>%
+    mutate(lat_buffer = ifelse(between(
+      hex_lat_int, mean_lat_min - hex_buffer,
+      mean_lat_max + hex_buffer), "in", "out")) %>%
+    filter(lat_buffer == "in" | long_buffer == "in")
+
+ggplot() + 
+   geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "lightgrey", colour = "black", size = 0.01) + 
+  geom_point(aes(x=longitude, y = latitude),data = centroids, colour = "#374926") + 
+  theme_void() + coord_equal() +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#9ad5c0", data = full_grid, size = 0.5) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#64b1be", data = grid, size = 2)
+
 ```
+
 ##### Centroid to focal point distance
@@
 hexmap_allocation <- allocate(
-  centroids = centroids %>% select(SA2_NAME16, longitude, latitude),
-  sf_id = "SA2_NAME16",
+  centroids = centroids %>% select(sa2_name_2011, longitude, latitude),
+  sf_id = "sa2_name_2011",
   hex_grid = grid,
@@
 
-<!-- ```{r buffers, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, out.width = "100%"} -->
+```{r buffers, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, out.width = "100%", height = 4}
 
-<!-- knitr::include_graphics(path = "figs4grid.png") -->
+centroids <- centroids %>%
+        group_nest(sa2_name_2011) %>%
+        mutate(closest = purrr::map(data, closest_focal_point, 
+                                    focal_points = capital_cities)) %>%
+        unnest(c("data", "closest")) %>%
+        arrange(focal_distance) %>% 
+        mutate(rownumber = row_number())
 
-<!-- ``` -->
+f_centroid <- centroids %>%
+        filter(rownumber == 1)
 
-```{=tex}
-\begin{figure}[h]
-\centering
-\includegraphics[width=16cm]{figs/4grid.png}
-\caption{\label{fig:buffers}The remaining available hexagon locations after filtering for the grid points within a square distance, then circular around the centroid.}
-\end{figure}
+# filter_grid_points
+
+distance <- (((f_centroid$latitude - f_centroid$focal_latitude) ^ 2) + 
+         ((f_centroid$longitude - f_centroid$focal_longitude) ^ 2)) ^ (1 / 2)
+
+flong <- f_centroid$longitude
+flat <- f_centroid$latitude
+f_dist <- 10 * hex_size
+angle_width <- 35
+
+f_grid <- grid %>%
+  ungroup() %>%
+  filter((flat - f_dist) < hex_lat & hex_lat < (flat + f_dist)) %>%
+  filter((flong - f_dist) < hex_long & hex_long < (flong + f_dist))
+
+f1 <- ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "lightgrey", colour = "black", size = 0.01) +
+  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "red", size = 2) + 
+  geom_point(aes(x=longitude, y = latitude), data = f_centroid, colour = "#374926") + 
+  theme_void() + coord_equal() +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#9ad5c0", data = grid, size = 0.5) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#64b1be", data = f_grid, size = 2) + ggtitle("a")
+
+f_grid <- f_grid %>%
+  group_by(id) %>%
+  mutate(
+    hex_lat_c = (hex_lat - flat),
+    hex_long_c = (hex_long - flong)) %>%
+  mutate(hyp = ((hex_lat_c^2) + (hex_long_c^2))^(1 / 2))
+
+f_angle <- f_centroid %>%
+      mutate(atan = atan2(latitude - focal_latitude, longitude - focal_longitude),
+        angle = (atan * 180 / pi),
+        pangle = ifelse(angle < 0, angle + 360, angle)) %>%
+      pull(pangle)
+
+f_grid <- f_grid %>%
+  # create circle of radius: f_dist
+  filter(hyp < f_dist) %>%
+  mutate(
+    # geosphere takes a long time
+    angle = f_angle,
+    angle_plus = (angle + angle_width) %% 360,
+    angle_minus = (angle - angle_width) %% 360,
+    atan = atan2(hex_lat_c, hex_long_c),
+    hex_angle = (atan * 180 / pi),
+    hex_angle = ifelse(hex_angle < 0, hex_angle + 360, hex_angle))
+
+f2 <- ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "lightgrey", colour = "black", size = 0.01) +
+  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "red", size = 2) + 
+  geom_point(aes(x=longitude, y = latitude), data = f_centroid, colour = "#374926") + 
+  theme_void() + coord_equal() +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#9ad5c0", data = grid, size = 0.5) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#64b1be", data = f_grid, size = 2) + ggtitle("b")
+
+grid.arrange(f1,f2, nrow = 1)
 ```
+
 The `width` parameter is used to take a slice of the remaining points.
 The width is the amount of degrees used on either side of the angle from the focal point to centroid location.
-This uses the angle from the closest capital city, to the current centroid as seen in Figure \ref{fig:angles} .
+This uses the angle from the closest capital city, to the current centroid as seen in Figure \ref{fig:buffers2} .
 This allows the spatial relationship to be preserved, even when it is allocated to a hexagon that is further from the focal point then the original centroid location.
 
-<!-- ```{r angles, fig.cap = "Filter for grid points within the angle from the focal point to the centroid.", echo = FALSE, out.width = "100%"} -->
+```{r buffers2, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, out.width = "100%", height = 4}
 
-<!-- knitr::include_graphics(path = "figs5allocate.png") -->
+full_grid <- full_grid %>% filter(hex_long > bbox$min[1], hex_long < bbox$max[1],
+                                  hex_lat > bbox$min[2], hex_lat < bbox$max[2])
 
-<!-- ``` -->
+# Check that there were available points within hyp distance
+f_grid <- f_grid %>%
+        # create slice of width *2 degrees from centroid
+        filter(angle_minus < hex_angle & hex_angle < angle_plus)
 
-```{=tex}
-\begin{figure}[h]
-\centering
-\includegraphics[width=16cm]{figs/5allocate.png}
-\caption{\label{fig:angles}The remaining available hexagon locations after filtering for grid points within the angle from the focal point to the centroid.}
-\end{figure}
+f3 <- ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "lightgrey", colour = "black", size = 0.01) +
+  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "red", size = 2) + 
+  geom_point(aes(x=longitude, y = latitude), data = f_centroid, colour = "#374926") + 
+  theme_void() + coord_equal() +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#9ad5c0", data = grid, size = 0.5) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#64b1be", data = f_grid, size = 2) + ggtitle("a")
+
+hex <- f_grid %>%
+        ungroup() %>%
+        filter(hyp == min(hyp)) %>%
+        select(hex_long, hex_lat, hex_id = id)
+
+f4 <- ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "lightgrey", colour = "black", size = 0.01) +
+  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "red", size = 2) + 
+  geom_point(aes(x=longitude, y = latitude), data = f_centroid, colour = "#374926") + 
+  theme_void() + coord_equal() +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#9ad5c0", data = grid, size = 0.5) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#64b1be", data = f_grid, size = 2) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "orange", data = hex, size = 2.5) + ggtitle("b")
+
+grid.arrange(f3, f4, nrow = 1)
+
 ```
+
 If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded, only when a maximum distance is reached will the angle expand to accommodate more possible grid points.\
@@
 
-<!-- ```{r buffs, fig.cap = "A complete hexagon tile map of Tasmania.", out.width = "100%", echo = FALSE} -->
-
-<!-- knitr::include_graphics(path = "figs6allocate.png") -->
-
-<!-- ``` -->
-
-```{=tex}
-\begin{figure}[h]
-\centering
-\includegraphics[width=16cm]{figs/6allocate.png}
-\caption{\label{fig:buffs}A complete hexagon tile map of Tasmania.}
-\end{figure}
-```
 A complete hexagon tile map of Tasmania is created by applying the algorithm steps to each centroid.
-The hexagon tile map visualisation is used below to visualise the Australian Cancer Atlas data [@TACA].
+The hexagon tile map is used to visualise the Australian Cancer Atlas data [@TACA].
 Two views of the same data are produced by filling according to the thyroid Cancer Standardised Incidence Rates (SIRs) downloaded from the Australian Cancer Atlas site.
-This small example in Figure \ref{fig:sir} shows the group of blue areas in the Hobart CBD more prominently in the hexagon tile map (b).
+This small example in Figure \ref{fig:centroids_plot} shows the group of blue areas in the Hobart CBD more prominently in the hexagon tile map (b).
 The small red areas visible in the choropleth map (a) along the north coast are much larger in the hexagon tile maps.
 The hexagon tile map shows less yellow, this no longer overwhelms the map space with the information regarding the rural areas.
-
-<!-- ```{r sir, out.width = "100%", echo = FALSE, fig.cap = "The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2.
-A choropleth map (a) of Standardised Incidence Rates (SIRs) is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented."} -->
-
-<!-- knitr::include_graphics(path = "figs7SIR.png") -->
-
-<!-- ``` -->
-
-```{=tex}
-\begin{figure}[h]
-\centering
-\includegraphics[width=14cm]{figs/7SIR.png}
-\caption{\label{fig:sir}The Australian Cancer Atlas data displayed on a choropleth and hexagon tile map.
-The colour of each Statistical Area of Australian at Level 2 coloured by SIR.
-A choropleth map (a) of SIR is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented.}
-\end{figure}
-```
-#### Neighbour relationships
-
-It is possible to consider the neighbouring areas for each SA2, for stronger preservation of the spatial distribution.
-
-An additional step can be included to allow the neighbours that have already been allocated to influence the placement of the current centroid.
-This requires specifying the `sf` object as the argument for the `use_neighbours` parameter.
-This calculates neighbours using intersections of their polygons.
-This occurs for all areas before any allocations begin.
-
-During the allocation of each centroid, the list of neighbours is consulted.
-If any neighbour was already allocated, the hexagons surrounding the neighbours on the grid are prioritised.
-For multiple neighbours, the neighbouring hexagon grid points are aggregated and considered in order of distance from the original centroid.
 
@@
 This display highlights the density of Australian capital cities, as it draws attention to the many communities in Sydney, Melbourne and Hobart.
-This display also highlights the disparity in the burden of Melanoma cancer for males in the communities of these three cities.
+This display also highlights the disparity in the burden of thyroid cancer for males in the communities of these three cities.
 There are several collections of red hexagons in Hobart that draw attention and they represent the communities with much higher rates of diagnosis than the Australian average.
@@
 The tessellation crated by adjoining hexagons for densely populated areas is helpful as it shows that most communities are not islands onto themselves, but are intrinsically connected to those around them.
-As seen in the Dorling cartogram in figure \ref{fig:nsw_grid}c), the tessellation that allows boundary connections was not imposed for rural communities, where centroid of the geographic unit was located far from others, a feature that allows distant but dense populations of the coastal towns of Tasmania to be recognised.
+As seen in the Dorling cartogram in figure \ref{fig:tas_displays}c), the tessellation that allows boundary connections was not imposed for rural communities, where centroid of the geographic unit was located far from others, a feature that allows distant but dense populations of the coastal towns of Tasmania to be recognised.
 
-The choropleth map that uses the geographic shapes of areas can be seen in figure \ref{fig:thyroid-geo}.
-Figure \ref{fig:melanoma-hex} displays the Australian areas with equally sized hexagons.
+The choropleth map that uses the geographic shapes of areas can be seen in figure \ref{fig:choro}.
+Figure \ref{fig:hexmap} displays the Australian areas with equally sized hexagons.
 This display allows the small and densely populated inner city areas to be easily contrasted with their neighbouring areas.

### 2020-10-12 kobakian-cook.tex
New tas displays

@@
 \abstract{%
-This algorithm creates a tessellated hexagon display to represent a set
-of the spatial polygons. It allocates these hexagon in a manner that
-preserves the spatial relationship of the geographic units. The
-algorithm creates a display that showcases spatial distributions, by
-emphasising the small geographical regions that are often difficult to
-locate on geographic maps. Spatial distributions have been presented on
-alternative representations of geography for many years. In modern
-times, interactivity and animation have begun to play a larger role, as
-alternative representations have been popularised by online news sites,
-and atlas websites with a focus on public consumption. Applications are
+The algorithm presented creates a display that uses tessellated hexagons
+to represent a set of spatial polygons. It allocates these hexagon in a
+manner that preserves the spatial relationship of the geographic units,
+in light of their positions to points of interest. The display showcases
+spatial distributions, by emphasising the small geographical regions
+that are often difficult to locate on geographic maps. Spatial
+distributions have been presented on alternative representations of
+geography for many years. In modern times, interactivity and animation
+have allowed alternative displays to play a larger role. Alternative
+representations have been popularised by online news sites, and atlas
+websites with a focus on public consumption. Applications are
 increasingly widespread, especially in the areas of disease mapping, and
@@
 human related statistics due to area-size bias \citep{BCM}. Figure
-\ref{fig:melanoma-geo} is a choropleth map that uses colour to display
-the estimated Standardised Incidence Ratios (SIRs) of melanoma cancer
-for males for each of the Statistical Areas at Level 2 (SA2) used by the
+\ref{fig:choro} is a choropleth map that uses colour to display the
+estimated Standardised Incidence Ratios (SIRs) of thyroid cancer for
+males for each of the Statistical Areas at Level 2 (SA2) used by the
 \citet{abs2011}. The Australian choropleth map display draws attention
-to the expanse of light blue areas across the rural communities in all
-states. The SA2s around Hobart stand out as more orange and red. To
-create this choropleth map the SA2 polygons for 2011 from the Australian
-Bureau of Statistics.
+to the expanse of dark and light blue areas across the rural communities
+in all states. The SA2s around Brisbane stand out as more orange and
+red.
+
+\begin{Schunk}
+\begin{figure}
+\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/choro-1} \caption[A choropleth map of the Statistical Areas of Australia at Level 2]{A choropleth map of the Statistical Areas of Australia at Level 2.
+The colours communicate the value of the estimated SIR of Thyroid cancer for females, ranging from much lower than average (blue) to much higher than average (red)}\label{fig:choro}
+\end{figure}
+\end{Schunk}
 
@@
 Alternative maps shift the focus from land area and shape, to the value
-of the statistics in a group of areas \citep{ACCAC}. Different styles of
-cartograms apply transformations to the geographic areas, to highlight
-the values of the value of the statistic of interest. These displays
-result in a distortion of the map space to represent differences in the
-statistic across the areas \citep{ACCAC} as the statistic of interest is
-used to determine the cartogram layout.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=14cm]{figs/aus_melanoma_p.png}
-\caption{\label{fig:melanoma-geo}A choropleth map of the Statistical Areas of Australia at Level 2.
-The colours communicate the value of the estimated SIR of Melanoma for males, they range from much lower than average (blue) to much higher than average (red)}
-\end{figure}
+of the statistics in a collection of areas \citep{ACCAC}. Each style of
+cartogram applies a different transformation to the geographic areas, to
+highlight the values of the statistic of interest. These displays result
+in a distortion of the map space to represent features of the
+distribution across the areas \citep{ACCAC} as the statistic of interest
+is used to determine the cartogram layout.
 
@@
 disregard the unique shapes of the administrative boundaries. Figure
-\ref{fig:nsw_grid} shows a collection of alternative map displays, this
-includes a) a contiguous cartogram, b) a non-contiguous cartogram, c) a
-Dorling cartogram and d) a hexagon tile map. Each Statistical Area at
-Level 2 (SA2) \citep{abs2011} was designed to represent a community.
-These administrative areas are often used to aggregate census data and
-used to understand demographics of the Australian population.
+\ref{fig:tas_displays} shows a collection of alternative map displays,
+this includes a) a contiguous cartogram, b) a non-contiguous cartogram,
+and c) a Dorling cartogram.
 
@@
 understanding of the spatial disease distribution as many of the
-communities are not visible in a choropleth display \citep{TVSSS}. This
-presents an opportunity for explicit map transformations to improve
-communication of distributions \citep{CBATCC}. In figure
-\ref{fig:nsw_grid}a) the choropleth map is presented with the
-alternative maps to allow for comparisons to be made.
+communities are not visible in a choropleth display \citep{TVSSS}. Each
+Statistical Area at Level 2 (SA2) \citep{abs2011} was designed to
+represent a community. These administrative areas are often used to
+aggregate census data and used to understand demographics within
+communities of the Australian population. This presents an opportunity
+for explicit map transformations to improve communication of
+distributions \citep{CBATCC}. In figure \ref{fig:tas_displays} the
+choropleth map can be seen underneath each alternative map display to
+allow for comparisons to be made.
 
 \begin{Schunk}
-
-\includegraphics[width=0.9\linewidth]{kobakian-cook_files/figure-latex/tas_displays-1} \end{Schunk}
+\begin{figure}
+\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/tas_displays-1} \caption[The three displays show alternative maps of the Statistical Areas at Level 2 in the Australian state of Tasmania]{The three displays show alternative maps of the Statistical Areas at Level 2 in the Australian state of Tasmania.
+These alternatives show the (a) contiguous cartogram, (b) non-contiguous cartogram and (c) Dorling cartogram of Tasmania.}\label{fig:tas_displays}
+\end{figure}
+\end{Schunk}
 
@@
 connection in the transformed display. The contiguous cartogram
-displayed in figure \ref{fig:nsw_grid}b) draws attention to smaller
+displayed in figure \ref{fig:tas_displays}b) draws attention to smaller
 geographic units when they are rescaled according to the population
@@
 far from their neighbours \citep{TVSSS}. This shown in the northern SA2s
-of Tasmania with an average (yellow) estimated SIR of Melanoma for
-males.
+of Tasmania with an average (yellow) estimated SIR of thyroid for males.
 
-The non-contiguous cartogram in figure \ref{fig:nsw_grid}c) also uses
-the population to rescale the geographic units. Unlike the contiguous
-cartogram, the SA2 areas maintain their geographic shape, but they may
-not retain the connection with their neighbours. The population of the
-SA2 areas is used to scale the geographic units in the non-contiguous
-cartogram \citep{NAC}. The amount of white space can be meaningful in
-non-contiguous cartograms \citep{ECGC}, in this example the disparity
-between large rural areas and small urban areas means that the city of
-Hobart, shown in the inset map looks reasonable, but these units are not
-visible in the context of the Tasmania state map. Depending on the
-difference between the population and geographic land size, the amount
-of white space can also prevent meaningful understanding of the
-distribution \citep{TVSSS}.
+The non-contiguous cartogram in figure \ref{fig:tas_displays}c) also
+uses the population to rescale the geographic units. Unlike the
+contiguous cartogram, the SA2 areas maintain their geographic shape, but
+they may not retain the connection with their neighbours. The population
+of the SA2 areas is used to scale the geographic units in the
+non-contiguous cartogram \citep{NAC}. The amount of white space can be
+meaningful in non-contiguous cartograms \citep{ECGC}, in this example
+the disparity between large rural areas and small urban areas means that
+the city of Hobart, shown in the inset map looks reasonable, but these
+units are not visible in the context of the Tasmania state map.
+Depending on the difference between the population and geographic land
+size, the amount of white space can also prevent meaningful
+understanding of the distribution \citep{TVSSS}.
 
@@
 size of the circle is scaled according to the population value of each
-area \citep{ACTUC}. Figure \ref{fig:nsw_grid}d) shows the Tasmania SA2
-areas as an individual circle located as close as possible to the
+area \citep{ACTUC}. Figure \ref{fig:tas_displays}c) shows the Tasmania
+SA2 areas as an individual circle located as close as possible to the
 geographic centroid location. This map draws attention to the collection
 of coastal cities in Tasmania that were not apparent in figure
-\ref{fig:nsw_grid} a), b) or c).
+\ref{fig:tas_displays} a), or b).
 
@@
 
-There are three key steps performed to create a tessellated hexagon tile
-map. First derive the set of centroids from the polygons provided, then
-create the grid of hexagons locations. These two steps are defined in
-the blue left column of the flow chart in Figure
-\ref{fig:sugarbag_flow}. Each centroid can then be allocated to an
-available hexagon location. The steps for the allocation process are
-detailed in the right column of Figure \ref{fig:sugarbag_flow}. To make
-tessellated plots, the point locations are converted to hexagon shapes,
-with the hexagon size used in the grid.
+The result of the algorithm is a display that emphasises the densely
+populated geographic regions surrounding the capital cities in
+Australia. Each capital city forms it's own layer of connected hexagons.
+Figure \ref{fig:hexmap} allows the distributions in the capital cities
+to be viewed at a deeper scale. Sydney is now notable for the
+considerable amount of red areas, not just for the surrounding orange
+areas around the New South Wales capital visible in the choropleth
+display in Figure \ref{fig:choro}. Brisbane and Perth also draw
+attention for the many orange areas. Interestingly there is no clear
+divide between rural and urban SA2 areas as Melbourne, Darwin, Adelaide
+and Hobart have low rates of thyroid cancer diagnosis.
+
+\begin{Schunk}
+\begin{figure}
+\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/hexmap-1} \caption[A hexagon tile map of the Statistical Areas of Australia at Level 2]{A hexagon tile map of the Statistical Areas of Australia at Level 2.
+The colours communicate the value of the estimated SIR of thyroid for males, they range from much lower than average (blue) to much higher than average (red).}\label{fig:hexmap}
+\end{figure}
+\end{Schunk}
+
+There are three key steps performed to create the tessellated hexagon
+tile map shown in Figure \ref{fig:hexmap}. First, derive the set of
+centroids from the polygons provided, then create the grid of hexagons
+locations. These two steps are defined in the blue left column of the
+flow chart in Figure \ref{fig:sugarbag_flow}. Each centroid can then be
+allocated to an available hexagon location. The steps for the allocation
+process are detailed in the right column of Figure
+\ref{fig:sugarbag_flow}. To make tessellated plots, the point locations
+are converted to hexagon shapes, with the hexagon size used in the grid.
 
@@
 Only two inputs are necessary to begin using the algorithm, the shape
-file, and the id variable. The id column should uniquely identify each
+file, and the id variable. The id variable should uniquely identify each
 geographic unit in the shape file.
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=14cm]{figs/1centroids.png}
-\caption{\label{fig:centroids_plot}The geographic shapes of the Statistical Areas of Tasmania at Level 2. The points show the locations of the centroids of the SA2 areas.}
+\begin{Schunk}
+\begin{figure}
+\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/centroids_plot-1} \caption[The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2]{The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2.
+A choropleth map (a) of Standardised Incidence Rates (SIRs) is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented.}\label{fig:centroids_plot}
 \end{figure}
+\end{Schunk}
 
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=16cm]{figs/2grid.png}
-\caption{\label{fig:grid2}Grid points to create a hexagon tile map.}
+\begin{Schunk}
+\begin{figure}
+\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/grid2-1} \caption[Complete set of grid points to create a tile map]{Complete set of grid points to create a tile map.}\label{fig:grid2}
 \end{figure}
+\end{Schunk}
 
@@
 windows. The rolling windows can be seen on the bottom and right of the
-grid shown in Figure \ref{fig:filter-grid}. This will tailor the
-available grid points to those most likely to be used. It also helps
-reduce the amount of time taken, as it decreases the amount of points
-considered for each centroid allocation.
+grid shown in Figure \ref{fig:grid3}. This will tailor the available
+grid points to those most likely to be used. It also helps reduce the
+amount of time taken, as it decreases the amount of points considered
+for each centroid allocation.
 
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=10cm]{figs/3grid.png}
-\caption{\label{fig:filter-grid}The remaining hexagon locations from all the possible points in the initial grid after the buffer is applied.
-The blue dots show the grid points left to choose from after the buffer step.}
+\begin{Schunk}
+\begin{figure}
+\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/grid3-1} \caption[The remaining hexagon locations from all the possible points in the initial grid after the buffer is applied]{The remaining hexagon locations from all the possible points in the initial grid after the buffer is applied.
+The blue dots show the grid points left to choose from after the buffer step.}\label{fig:grid3}
 \end{figure}
+\end{Schunk}
 
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=16cm]{figs/4grid.png}
-\caption{\label{fig:buffers}The remaining available hexagon locations after filtering for the grid points within a square distance, then circular around the centroid.}
+\begin{Schunk}
+\begin{figure}
+\includegraphics[width=1\linewidth]{kobakian-cook_files/figure-latex/buffers-1} \caption[Filter for grid points within a square, then circular, distance for those closest to the centroid]{Filter for grid points within a square, then circular, distance for those closest to the centroid.}\label{fig:buffers}
 \end{figure}
+\end{Schunk}
 
@@
 from the closest capital city, to the current centroid as seen in Figure
-\ref{fig:angles} . This allows the spatial relationship to be preserved,
-even when it is allocated to a hexagon that is further from the focal
-point then the original centroid location.
+\ref{fig:buffers2} . This allows the spatial relationship to be
+preserved, even when it is allocated to a hexagon that is further from
+the focal point then the original centroid location.
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=16cm]{figs/5allocate.png}
-\caption{\label{fig:angles}The remaining available hexagon locations after filtering for grid points within the angle from the focal point to the centroid.}
+\begin{Schunk}
+\begin{figure}
+\includegraphics[width=1\linewidth]{kobakian-cook_files/figure-latex/buffers2-1} \caption[Filter for grid points within a square, then circular, distance for those closest to the centroid]{Filter for grid points within a square, then circular, distance for those closest to the centroid.}\label{fig:buffers2}
 \end{figure}
+\end{Schunk}
 
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=16cm]{figs/6allocate.png}
-\caption{\label{fig:buffs}A complete hexagon tile map of Tasmania.}
-\end{figure}
-
 A complete hexagon tile map of Tasmania is created by applying the
-algorithm steps to each centroid. The hexagon tile map visualisation is
-used below to visualise the Australian Cancer Atlas data \citep{TACA}.
-Two views of the same data are produced by filling according to the
-thyroid Cancer Standardised Incidence Rates (SIRs) downloaded from the
-Australian Cancer Atlas site. This small example in Figure \ref{fig:sir}
+algorithm steps to each centroid. The hexagon tile map is used to
+visualise the Australian Cancer Atlas data \citep{TACA}. Two views of
+the same data are produced by filling according to the thyroid Cancer
+Standardised Incidence Rates (SIRs) downloaded from the Australian
+Cancer Atlas site. This small example in Figure \ref{fig:centroids_plot}
 shows the group of blue areas in the Hobart CBD more prominently in the
@@
 space with the information regarding the rural areas.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=14cm]{figs/7SIR.png}
-\caption{\label{fig:sir}The Australian Cancer Atlas data displayed on a choropleth and hexagon tile map.
-The colour of each Statistical Area of Australian at Level 2 coloured by SIR.
-A choropleth map (a) of SIR is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented.}
-\end{figure}
-
-\hypertarget{neighbour-relationships}{%
-\paragraph{Neighbour relationships}\label{neighbour-relationships}}
-
-It is possible to consider the neighbouring areas for each SA2, for
-stronger preservation of the spatial distribution.
-
-An additional step can be included to allow the neighbours that have
-already been allocated to influence the placement of the current
-centroid. This requires specifying the \texttt{sf} object as the
-argument for the \texttt{use\_neighbours} parameter. This calculates
-neighbours using intersections of their polygons. This occurs for all
-areas before any allocations begin.
-
-During the allocation of each centroid, the list of neighbours is
-consulted. If any neighbour was already allocated, the hexagons
-surrounding the neighbours on the grid are prioritised. For multiple
-neighbours, the neighbouring hexagon grid points are aggregated and
-considered in order of distance from the original centroid.
 
@@
 in Sydney, Melbourne and Hobart. This display also highlights the
-disparity in the burden of Melanoma cancer for males in the communities
+disparity in the burden of thyroid cancer for males in the communities
 of these three cities. There are several collections of red hexagons in
@@
 connected to those around them. As seen in the Dorling cartogram in
-figure \ref{fig:nsw_grid}c), the tessellation that allows boundary
+figure \ref{fig:tas_displays}c), the tessellation that allows boundary
 connections was not imposed for rural communities, where centroid of the
@@
 The choropleth map that uses the geographic shapes of areas can be seen
-in figure \ref{fig:melanoma-geo}. Figure \ref{fig:melanoma-hex} displays
-the Australian areas with equally sized hexagons. This display allows
-the small and densely populated inner city areas to be easily contrasted
+in figure \ref{fig:choro}. Figure \ref{fig:hexmap} displays the
+Australian areas with equally sized hexagons. This display allows the
+small and densely populated inner city areas to be easily contrasted
 with their neighbouring areas.

### 2020-10-12 kobakian-cook.R

@@ -1,20 +1,14 @@
-## ----setup, echo=FALSE, message=FALSE, warning=FALSE, comment = FALSE---------
-library(knitcitations)
-library(kableExtra)
-library(RefManageR)
-library(sp)
-library(sf)
-library(sugarbag)
+# Young statisticians conference presentation plots
+
 library(absmapsdata)
 library(tidyverse)
 library(cartogram)
 library(ggthemes)
 library(cowplot)
+library(sf)
+library(sp)
 
-knitr::opts_chunk$set(warning = FALSE, message = FALSE, eval = FALSE)
-options("citation_format" = "pandoc")
-BibOptions(check.entries = FALSE, style = "markdown")
-
+### Theme set up
 
 invthm <- theme_map() + 
   theme(
@@ -26,237 +20,612 @@ invthm <- theme_map() +
     axis.text = element_text(colour = "white")
   )
 
+## States of Australia
+
+states <- absmapsdata::state2011 %>% 
+  filter(state_name_2011 != "Other Territories")
+
+###############################################################################
+###########################        ABS AREAS        ###########################
+## sa2
+sa2 <- absmapsdata::sa22011 %>% 
+  filter(state_name_2011 != "Other Territories") %>% st_transform(., crs = 3112)
+
+sa2_map <- ggplot(sa2) + 
+  geom_sf(aes(fill = albers_sqkm)) +
+  scale_fill_distiller(type = "seq", palette = "BuGn",  direction = 1, na.value = "light grey") + 
+  theme_void() +
+  coord_sf(crs = 3112) +
+   theme(legend.position ="left", legend.title = element_text("Area (sqkm)"))
+
+ggsave(filename = "figures/aus_sa2.png", plot = sa2_map,
+  device = "png", bg = "transparent", dpi = 300,  width = 10, height = 8)
+
+
+###############################################################################
+###########################     CARTOGRAMS
+# 
+# ERP <- read_csv("data/ERP.csv")
+# 
+# ERP_sa4 <- ERP %>% filter(`Geography Level` == "Statistical Area Level 4", Time == 2011) %>% arrange(`Geography Level`)
+# 
+# aus_ggcont <- ggplot(ERP_sa4) + 
[…]

### 2020-10-18 kobakian-cook.Rmd
simplified images

@@
 ```{r setup}
+library(cartogram)
+library(cowplot)
+library(gridExtra)
+library(ggthemes)
 library(knitcitations)
@@
 library(tidyverse)
-library(cartogram)
-library(ggthemes)
-library(cowplot)
 
@@
 }
-
 ```
@@
   filter(!sa2_name_2011 == "Lord Howe Island")
-
 # sa2 <- sa2 %>% rmapshaper::ms_simplify(keep = 0.05, keep_shapes = TRUE)
-
 SIR <- read_csv("data/SIR Downloadable Data.csv") %>% 
@@
   dplyr::select(Region, Value)
-
 # Alternative maps
@@
   filter(!st_is_empty(geometry))
-
 sa2thyroid_ERP <- sa2thyroid_ERP %>% 
@@
 The colours communicate the value of the estimated SIR of thyroid cancer for females, ranging from much lower than average (blue) to much higher than average (red)"}
-
 if (!file.exists("data/aus_hexmap.rda")) {
@@
   create_centroids(., "sa2_name_2011")
-
 ## Create hexagon grid
@@
                     buffer_dist = 5)
-
 ## Allocate polygon centroids to hexagon grid points
@@
 )
-
 save(aus_hexmap, file = "data/aus_hexmap.rda") }
@@
             left_join(sa2thyroid_ERP %>% select(sa2_name_2011, SIR, p50))
-
 fort_aus <- sa2thyroid_ERP %>%
   fortify_sfc()
-
 ## Make a plot
-aus_hexmap <- ggplot() +
+aus_hexmap_plot <- ggplot() +
   geom_polygon(aes(x = long,  y = lat,  group = interaction(sa2_name_2011, polygon)),
@@
   invthm + coord_equal()
-
 ```
@@
 # Contiguous Cartograms
-
 if (!file.exists("data/ncont.rda")) {
@@
   st_as_sf()
-
 save(cont, file = "data/cont.rda") }
@@
 tas_ggcont <- ggplot(cont) + 
-  geom_sf(fill = "lightgrey", colour = "black", data = sa2thyroid_ERP) +
+  geom_sf(fill = "#D3D3D3", colour = "white", data = sa2thyroid_ERP) +
   geom_sf(aes(fill = SIR), colour = NA) + 
@@
 #tas_ggcont
-
 ```
@@
 # Non - Contiguous Cartograms
-
 if (!file.exists("data/ncont.rda")) {
@@
                           st_as_sf()
-
 save(ncont, file = "data/ncont.rda")
 }
-
 ```
@@
 load("data/ncont.rda")
-
 tas_ggncont <- ggplot(ncont %>% filter(state_name_2011 == "Tasmania")) + 
-  geom_sf(fill = "lightgrey", colour = "black",  data = sa2thyroid_ERP) +
+  geom_sf(fill = "#D3D3D3", colour = "white",  data = sa2thyroid_ERP) +
   geom_sf(aes(fill = SIR), colour = NA) + 
@@
 #tas_ggncont
-
 ```
@@
 # Non - Contiguous Dorling Cartograms
-
 dorl <- sa2thyroid_ERP %>% 
@@
 tas_ggdorl <- ggplot(dorl) +
-  geom_sf(fill = "lightgrey", colour = "black",  data = sa2thyroid_ERP) + 
+  geom_sf(fill = "#D3D3D3", colour = "white",  data = sa2thyroid_ERP) + 
   geom_sf(aes(fill = SIR)) + 
@@
 The colours communicate the value of the estimated SIR of thyroid for males, they range from much lower than average (blue) to much higher than average (red)."}
-aus_hexmap
+aus_hexmap_plot
 ```
@@
 
-```{r centroids_plot, fig.cap = "The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2.
+```{r tas_centroids, fig.cap = "The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2.
 A choropleth map (a) of Standardised Incidence Rates (SIRs) is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented."}
@@
   sf_id = "sa2_name_2011")
-
 hex_size <- .2
 buffer_dist <- 2
-
 bbox <- tibble(min = c(min(centroids$longitude), min(centroids$latitude)),
   max = c(max(centroids$longitude), max(centroids$latitude)))
-
 grid <- tibble::as_tibble(expand.grid(hex_long = seq(bbox$min[1] - buffer_dist,
@@
 tas_centroids <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "lightgrey", colour = "black", size = 0.01) + 
-  geom_point(aes(x=longitude, y = latitude, colour = SIR), size = 3, shape = 19,
-             data = st_drop_geometry(sa2thyroid_ERP) %>% 
-               select(sa2_name_2011, SIR) %>%  
-               left_join(centroids)) +
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.01) + 
+  geom_point(aes(x=longitude, y = latitude), size = 2, shape = 19, colour = "white",
+             data = centroids) +
   scale_colour_identity() +
@@
 tas_hexmap <- ggplot() +
-  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "lightgrey", colour = "black", size = 0.01) + 
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.01) + 
   geom_polygon(aes(x = long, y = lat, group = hex_id, fill = SIR),
@@
   coord_equal()
-
-grid.arrange(tas_centroids, tas_hexmap, nrow=1)
 ```
@@
 
-```{r grid1}
-#grid <- create_grid(centroids = centroids, hex_size = 0.2, buffer_dist = 1.2)
-
-g1 <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "lightgrey", colour = "black", size = 0.01) + 
-  geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#374926") + theme_void() + 
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#64b1be", data = grid, size = 1.5) +
-  coord_equal() + ggtitle("a")
-```
-
 ##### Creating a tessellated grid
@@
 A unique hexagon location is created from all intersections of the longitude columns and latitude rows.
-Figure \ref{fig:grid2} shows the original grid on the left, to allow for tessellating hexagons, every second latitude row on the grid is shifted right, by half of the hexagon size.
+Figure \ref{fig:filterprocess} shows the original grid on the left, to allow for tessellating hexagons, every second latitude row on the grid is shifted right, by half of the hexagon size.
 The grid for tessellation is shown on the right.
 
-```{r grid2, fig.cap = "Complete set of grid points to create a tile map.", height = 4}
+```{r grid, fig.cap = "Complete set of grid points to create a tile map.", height = 4}
 # Find every second latitude
@@
   dplyr::filter(dplyr::row_number() %% 2 == 1) %>% unlist()
-
 # Shift the longitude of every second latitude to the right to make hex structure
@@
   dplyr::mutate(assigned=FALSE)
-
-g2 <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "lightgrey", colour = "black", size = 0.01) + 
-  geom_point(aes(x=longitude, y = latitude), data = centroids, colour = "#374926") + theme_void() + 
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#64b1be", data = grid, size = 1.5) +
-  coord_equal() + ggtitle("b")
-
-grid.arrange(g1, g2, nrow = 1)
 ```
@@
 The amount of rows in each latitude group and the amount of columns in each longitude group are used as the width of rolling windows.
-The rolling windows can be seen on the bottom and right of the grid shown in Figure \ref{fig:grid3}.
+The rolling windows can be seen on the bottom and right of the grid shown in Figure \ref{fig:filterprocess}.
 This will tailor the available grid points to those most likely to be used.
@@
 
-```{r grid3, fig.cap = "The remaining hexagon locations from all the possible points in the initial grid after the buffer is applied.
+```{r filtergrid, fig.cap = "The remaining hexagon locations from all the possible points in the initial grid after the buffer is applied.
 The blue dots show the grid points left to choose from after the buffer step."}
+g1 <- ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.01) + 
+   theme_void() + 
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = grid, size = 1) +
+  coord_equal() + ggtitle("a")
 
@@
     hex_lat_int = dense_rank(hex_lat)-1)
-
 nlong <- length(unique(grid$hex_long))
@@
   )
-
 # Amount of lats and longs in each group of rows and columns
@@
 long_size <- round(nlong / 20, 0)
-
 # Make a list of the min and max of the groups
@@
 nlong_list <- purrr::map2(seq(1:nlong), long_size + seq(1:nlong), c)
-
 # LATITUDE ROWS FILTER
@@
   max_int <- min(bounds[2], maximum)
-
   cents_in <- filter(cents, between(lat_int, bounds[1], max_int))
@@
   }
-
   cents_in <- filter(cents, between(long_int, bounds[1], max_int))
@@
 )
-
 # find the min and max longitude for each latitude
@@
   bind_cols(long_id = c(seq(1:nlong) + round(long_size / 2)), .)
-
 # APPLY A BUFFER
@@
 
-ggplot() + 
-   geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "lightgrey", colour = "black", size = 0.01) + 
-  geom_point(aes(x=longitude, y = latitude),data = centroids, colour = "#374926") + 
+g2 <- ggplot() + 
+   geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.01) +  
   theme_void() + coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#9ad5c0", data = full_grid, size = 0.5) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#64b1be", data = grid, size = 2)
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#55b56c", data = full_grid, size = 0.5) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = grid, size = 1.5) + ggtitle("b")
 
@@
 ```{r buffers, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, out.width = "100%", height = 4}
-
 centroids <- centroids %>%
@@
 
+# Choose a centroid for allocation:
 f_centroid <- centroids %>%
-        filter(rownumber == 1)
+        filter(rownumber == 7)
 
 # filter_grid_points
-
 distance <- (((f_centroid$latitude - f_centroid$focal_latitude) ^ 2) + 
          ((f_centroid$longitude - f_centroid$focal_longitude) ^ 2)) ^ (1 / 2)
-
 flong <- f_centroid$longitude
@@
 
-f1 <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "lightgrey", colour = "black", size = 0.01) +
-  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "red", size = 2) + 
-  geom_point(aes(x=longitude, y = latitude), data = f_centroid, colour = "#374926") + 
-  theme_void() + coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#9ad5c0", data = grid, size = 0.5) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#64b1be", data = f_grid, size = 2) + ggtitle("a")
-
 f_grid <- f_grid %>%
@@
   mutate(hyp = ((hex_lat_c^2) + (hex_long_c^2))^(1 / 2))
-
 f_angle <- f_centroid %>%
@@
       pull(pangle)
-
 f_grid <- f_grid %>%
@@
 
-f2 <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "lightgrey", colour = "black", size = 0.01) +
-  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "red", size = 2) + 
-  geom_point(aes(x=longitude, y = latitude), data = f_centroid, colour = "#374926") + 
+f1 <- ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.01) +
   theme_void() + coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#9ad5c0", data = grid, size = 0.5) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#64b1be", data = f_grid, size = 2) + ggtitle("b")
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#55b56c", data = grid, size = 0.5) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = f_grid, size = 1.5) + 
+  geom_point(aes(x=longitude, y = latitude), data = f_centroid, fill = "#ede187", shape = 24) + 
+#Hobart
+  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "#e9f2ed", size = 2, shape = 3) + ggtitle("c")
 
-grid.arrange(f1,f2, nrow = 1)
 ```
@@
 The width is the amount of degrees used on either side of the angle from the focal point to centroid location.
-This uses the angle from the closest capital city, to the current centroid as seen in Figure \ref{fig:buffers2} .
+This uses the angle from the closest capital city, to the current centroid as seen in Figure \ref{fig:filterprocess} .
 This allows the spatial relationship to be preserved, even when it is allocated to a hexagon that is further from the focal point then the original centroid location.
 
-```{r buffers2, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, out.width = "100%", height = 4}
-
+```{r filterprocess, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, out.width = "120%", height = 8}
 full_grid <- full_grid %>% filter(hex_long > bbox$min[1], hex_long < bbox$max[1],
                                   hex_lat > bbox$min[2], hex_lat < bbox$max[2])
+
+allocated_list <- aus_hexmap %>% 
+                  filter(points == "Hobart") %>% 
+                  slice_min(rownumber, n = 6)
+
+fort_allocated <- allocated_list %>% 
+  fortify_hexagon(., sf_id = "sa2_name_2011", hex_size = 0.2)
 
@@
 
-f3 <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "lightgrey", colour = "black", size = 0.01) +
-  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "red", size = 2) + 
-  geom_point(aes(x=longitude, y = latitude), data = f_centroid, colour = "#374926") + 
-  theme_void() + coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#9ad5c0", data = grid, size = 0.5) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#64b1be", data = f_grid, size = 2) + ggtitle("a")
-
 hex <- f_grid %>%
@@
 
-f4 <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "lightgrey", colour = "black", size = 0.01) +
-  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "red", size = 2) + 
-  geom_point(aes(x=longitude, y = latitude), data = f_centroid, colour = "#374926") + 
+f2 <- ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.01) +
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011)), data = fort_allocated, fill = "#353b38", colour = "black", size = 0.01) +
+  #Hobart
+  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "#e9f2ed", size = 2, shape = 3) + 
+  geom_point(aes(x=longitude, y = latitude), data = f_centroid, fill = "#ede187", shape = 24) + 
   theme_void() + coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#9ad5c0", data = grid, size = 0.5) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#64b1be", data = f_grid, size = 2) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "orange", data = hex, size = 2.5) + ggtitle("b")
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = f_grid, size = 1) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#e374b9", data = hex, size = 1.5) + ggtitle("d")
 
-grid.arrange(f3, f4, nrow = 1)
-
+grid.arrange(g1, g2,
+             f1, f2, ncol = 2)
 ```
@@
 Two views of the same data are produced by filling according to the thyroid Cancer Standardised Incidence Rates (SIRs) downloaded from the Australian Cancer Atlas site.
-This small example in Figure \ref{fig:centroids_plot} shows the group of blue areas in the Hobart CBD more prominently in the hexagon tile map (b).
+This small example in Figure \ref{fig:filterprocess} shows the group of blue areas in the Hobart CBD more prominently in the hexagon tile map (b).
 The small red areas visible in the choropleth map (a) along the north coast are much larger in the hexagon tile maps.

### 2020-10-18 kobakian-cook.tex
simplified images

@@
 
-\begin{Schunk}
-\begin{figure}
-\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/centroids_plot-1} \caption[The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2]{The Australian Cancer Atlas data has determined the colour of each Statistical Area of Australian at Level 2.
-A choropleth map (a) of Standardised Incidence Rates (SIRs) is paired with a hexagon tile map (b) to contrast the colours that are made obvious when every SA2 is equally represented.}\label{fig:centroids_plot}
-\end{figure}
-\end{Schunk}
-
 \hypertarget{step-2-create-the-hexagon-grid-points}{%
@@
 hexagon location is created from all intersections of the longitude
-columns and latitude rows. Figure \ref{fig:grid2} shows the original
-grid on the left, to allow for tessellating hexagons, every second
-latitude row on the grid is shifted right, by half of the hexagon size.
-The grid for tessellation is shown on the right.
-
-\begin{Schunk}
-\begin{figure}
-\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/grid2-1} \caption[Complete set of grid points to create a tile map]{Complete set of grid points to create a tile map.}\label{fig:grid2}
-\end{figure}
-\end{Schunk}
+columns and latitude rows. Figure \ref{fig:filterprocess} shows the
+original grid on the left, to allow for tessellating hexagons, every
+second latitude row on the grid is shifted right, by half of the hexagon
+size. The grid for tessellation is shown on the right.
 
@@
 windows. The rolling windows can be seen on the bottom and right of the
-grid shown in Figure \ref{fig:grid3}. This will tailor the available
-grid points to those most likely to be used. It also helps reduce the
-amount of time taken, as it decreases the amount of points considered
-for each centroid allocation.
+grid shown in Figure \ref{fig:filterprocess}. This will tailor the
+available grid points to those most likely to be used. It also helps
+reduce the amount of time taken, as it decreases the amount of points
+considered for each centroid allocation.
 
@@
 Hobart.
-
-\begin{Schunk}
-\begin{figure}
-\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/grid3-1} \caption[The remaining hexagon locations from all the possible points in the initial grid after the buffer is applied]{The remaining hexagon locations from all the possible points in the initial grid after the buffer is applied.
-The blue dots show the grid points left to choose from after the buffer step.}\label{fig:grid3}
-\end{figure}
-\end{Schunk}
 
@@
 
-\begin{Schunk}
-\begin{figure}
-\includegraphics[width=1\linewidth]{kobakian-cook_files/figure-latex/buffers-1} \caption[Filter for grid points within a square, then circular, distance for those closest to the centroid]{Filter for grid points within a square, then circular, distance for those closest to the centroid.}\label{fig:buffers}
-\end{figure}
-\end{Schunk}
-
 The \texttt{width} parameter is used to take a slice of the remaining
@@
 from the closest capital city, to the current centroid as seen in Figure
-\ref{fig:buffers2} . This allows the spatial relationship to be
+\ref{fig:filterprocess} . This allows the spatial relationship to be
 preserved, even when it is allocated to a hexagon that is further from
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{kobakian-cook_files/figure-latex/buffers2-1} \caption[Filter for grid points within a square, then circular, distance for those closest to the centroid]{Filter for grid points within a square, then circular, distance for those closest to the centroid.}\label{fig:buffers2}
+\includegraphics[width=1.2\linewidth]{kobakian-cook_files/figure-latex/filterprocess-1} \caption[Filter for grid points within a square, then circular, distance for those closest to the centroid]{Filter for grid points within a square, then circular, distance for those closest to the centroid.}\label{fig:filterprocess}
 \end{figure}
@@
 Standardised Incidence Rates (SIRs) downloaded from the Australian
-Cancer Atlas site. This small example in Figure \ref{fig:centroids_plot}
+Cancer Atlas site. This small example in Figure \ref{fig:filterprocess}
 shows the group of blue areas in the Hobart CBD more prominently in the

### 2020-10-19 kobakian-cook.Rmd
Up to implementation

@@
 
-In many countries, residents are increasingly gathering to live in urban areas around major cities [@ACTUC].
-The creation of approximately equal population areas results in dramatically different square meterage of the administrative geographic units, such as states or electorates.
-The units are filled with colour to represent the value of the statistic for each unit [@EI].
-This can lead to unequal emphasis on the statistical value of each of the geographic units.
+Over time the density of living in major cities has increased as residents have gathered to live near urban areas [@ACTUC].
+The division of these resident into approximately equal population areas results in dramatically different square meterage of administrative geographic units, such as states or electorates.
+In a choropleth map display the geographic units are filled with colour to represent the value of the statistic for each unit [@EI].
+This can allow unequal emphasis on the statistical value of each of the geographic units.
 This allows choropleth map displays to misrepresent the spatial distributions of human related statistics due to area-size bias [@BCM].
-Figure \ref{fig:choro} is a choropleth map that uses colour to display the estimated Standardised Incidence Ratios (SIRs) of thyroid cancer for males for each of the Statistical Areas at Level 2 (SA2) used by the @abs2011.
+Figure \ref{fig:choro} is a choropleth map that uses colour to display the estimated Standardised Incidence Ratios (SIRs) of thyroid cancer for females, in each of the Statistical Areas at Level 2 (SA2) used by the @abs2011.
 The Australian choropleth map display draws attention to the expanse of dark and light blue areas across the rural communities in all states.
-The SA2s around Brisbane stand out as more orange and red.
+The SA2s around Brisbane and in northern New South Wales stand out as more orange and red.
+However, this display neglects the vast amount of Australia residents living in the densely populated capital cities.
 
@@
 
-There are several established alternative visualisation methods.
-Tile maps, Rectangular cartograms [@ORC] and Dorling cartograms [@ACTUC] all use one simple shape to represent each geographic unit.
-They all minimise the emphasis on the size or shape of the geographic areas.
-These alternative map displays focus on the relationship between neighbours, attempting to preserve connections, and disregard the unique shapes of the administrative boundaries.
-Figure \ref{fig:tas_displays} shows a collection of alternative map displays, this includes a) a contiguous cartogram, b) a non-contiguous cartogram, and c) a Dorling cartogram.
-
 <!-- choropleth -->
-
 The familiar choropleth map display is often used to allow the user to orient themselves.
@@
 In figure \ref{fig:tas_displays} the choropleth map can be seen underneath each alternative map display to allow for comparisons to be made.
+
+There are several established alternative visualisation methods.
+Tile maps, Rectangular cartograms [@ORC] and Dorling cartograms [@ACTUC] all use one simple shape to represent each geographic unit.
+They all minimise the emphasis on the size or shape of the geographic areas.
+These alternative map displays focus on the relationship between neighbours, attempting to preserve connections, and disregard the unique shapes of the administrative boundaries.
+Figure \ref{fig:tas_displays} shows a collection of alternative map displays, this includes a) a contiguous cartogram, b) a non-contiguous cartogram, and c) a Dorling cartogram.
 
@@
 
-```{r alternatives}
+```{r contcart}
 # Projected data 
@@
   geom_sf(fill = "#D3D3D3", colour = "white", data = sa2thyroid_ERP) +
-  geom_sf(aes(fill = SIR), colour = NA) + 
+  geom_sf(aes(fill = SIR), colour = "grey", size = 0.01) + 
   scale_fill_identity() + guides(fill=FALSE) +
@@
 
-```{r contcart}
+```{r ncontcart}
 # Non - Contiguous Cartograms
@@
                           st_as_sf()
-save(ncont, file = "data/ncont.rda")
-}
-```
+save(ncont, file = "data/ncont.rda")}
 
-```{r plotcontcart}
 load("data/ncont.rda")
+
 tas_ggncont <- ggplot(ncont %>% filter(state_name_2011 == "Tasmania")) + 
@@
   geom_sf(fill = "#D3D3D3", colour = "white",  data = sa2thyroid_ERP) + 
-  geom_sf(aes(fill = SIR)) + 
+  geom_sf(aes(fill = SIR), colour = "grey", size = 0.01) + 
   scale_fill_identity() +
@@
 The impact of a disease over connected communities can be seen by allowing the boundaries to maintain connection in the transformed display.
-The contiguous cartogram displayed in figure \ref{fig:tas_displays}b) draws attention to smaller geographic units when they are rescaled according to the population [@DMAHP].
+The contiguous cartogram displayed in figure \ref{fig:tas_displays}a) draws attention to smaller geographic units when they are rescaled according to the population [@DMAHP].
 These new shapes can now be coloured to represent a second variable.
+The algorithm uses the geographic shape of the areas and iterates toward sizing the areas to represent the population.
 This display can create twisted and unfamiliar shapes from the geographic units as the algorithms must satisfy the topology conditions, especially when there are communities located geographically far from their neighbours [@TVSSS].
-This shown in the northern SA2s of Tasmania with an average (yellow) estimated SIR of thyroid for males.
 
@@
 
-The non-contiguous cartogram in figure \ref{fig:tas_displays}c) also uses the population to rescale the geographic units.
+The non-contiguous cartogram in figure \ref{fig:tas_displays}b) also uses the population to rescale the geographic units.
 Unlike the contiguous cartogram, the SA2 areas maintain their geographic shape, but they may not retain the connection with their neighbours.
 The population of the SA2 areas is used to scale the geographic units in the non-contiguous cartogram [@NAC].
-The amount of white space can be meaningful in non-contiguous cartograms [@ECGC], in this example the disparity between large rural areas and small urban areas means that the city of Hobart, shown in the inset map looks reasonable, but these units are not visible in the context of the Tasmania state map.
+The amount of white space can be meaningful in non-contiguous cartograms [@ECGC], in this example the disparity between large rural areas and small urban areas means that the city of Hobart may look reasonable but these units are not visible in the context of the Tasmania state map.
 Depending on the difference between the population and geographic land size, the amount of white space can also prevent meaningful understanding of the distribution [@TVSSS].
@@
 This map draws attention to the collection of coastal cities in Tasmania that were not apparent in figure \ref{fig:tas_displays} a), or b).
+This display also highlights that the approximation of equal population is not easy to fulfil, as there is some disparity in the sizes of the circles.
 
@@
 
-The purpose of this algorithm is to create a map display that highlights the spatial distributions for populations.
+The purpose of this algorithm is to create an alternative map display that highlights the spatial distributions for populations.
 There has been an increasing need for displays that recognise the large number of people that live in dense urban environments.
-The algorithm intends to maintain the spatial relationships of a group of geographic units in two ways: between each unit and its neighbours; and between each unit and the closest focal point.
+The algorithm intends to maintain the spatial relationships of a group of geographic units using the relationship between each unit and the closest focal point.
 The algorithm allocates geographic units to a representative hexagon, in order of their proximity to the closest focal point.
@@
 Native to northern and eastern Australia this stingless species builds flat layers of hexagonal brood cells, spiralling out from a central point [@PH].
-This hive design inspired the use of multiple focal points in the algorithm, individual spirals are constructed outward from various points on the geographic map base.
+This hive design inspired the use of multiple focal points in the algorithm, individual spirals are constructed by building out from various points on the geographic map base.
 
 The result of the algorithm is a display that emphasises the densely populated geographic regions surrounding the capital cities in Australia.
-Each capital city forms it's own layer of connected hexagons.
+Each capital city forms it's own collection of connected hexagons.
 Figure \ref{fig:hexmap} allows the distributions in the capital cities to be viewed at a deeper scale.
-Sydney is now notable for the considerable amount of red areas, not just for the surrounding orange areas around the New South Wales capital visible in the choropleth display in Figure \ref{fig:choro}.
-Brisbane and Perth also draw attention for the many orange areas.
-Interestingly there is no clear divide between rural and urban SA2 areas as Melbourne, Darwin, Adelaide and Hobart have low rates of thyroid cancer diagnosis.
+Sydney is now notable for the considerable amount of red hexagons, not just for the surrounding orange areas around the New South Wales capital visible in the choropleth display in Figure \ref{fig:choro}.
+Brisbane and Perth also draw attention for the many orange hexagons.
+Interestingly there is no clear divide between rural and urban SA2 areas as many rural areas, and the cities of Melbourne, Darwin, Adelaide and Hobart have low rates of thyroid cancer diagnosis for females.
 
 ```{r hexmap, fig.cap = "A hexagon tile map of the Statistical Areas of Australia at Level 2.
-The colours communicate the value of the estimated SIR of thyroid for males, they range from much lower than average (blue) to much higher than average (red)."}
+The colours communicate the value of the estimated SIR of thyroid for females, they range from much lower than average (blue) to much higher than average (red)."}
 aus_hexmap_plot
@@
 First, derive the set of centroids from the polygons provided, then create the grid of hexagons locations.
-These two steps are defined in the blue left column of the flow chart in Figure \ref{fig:sugarbag_flow}.
+These two processes are defined in the blue left column of the flow chart in Figure \ref{fig:sugarbag_flow}.
 Each centroid can then be allocated to an available hexagon location.
 The steps for the allocation process are detailed in the right column of Figure \ref{fig:sugarbag_flow}.
-To make tessellated plots, the point locations are converted to hexagon shapes, with the hexagon size used in the grid.
+There are several filter steps to speed the process of selecting an appropriate hexagon to represent each geographic area.
+To make tessellated plots with the hexagon allocations, the point locations are converted to hexagon shapes, with the hexagon size used in the grid.
 
@@
 
-Only two inputs are necessary to begin using the algorithm, the shape file, and the id variable. The id variable should uniquely identify each geographic unit in the shape file.
+Only two inputs are necessary to begin using the algorithm in the `sugarbag` package; the shape file, and the id variable.
+The id variable should uniquely identify each geographic unit in the shape file.
 
-The centroids can be derived from the shape file.
-The amount of centroids is used to determine a hexagon size.
-The derived centroids are a necessary input for an appropriate grid to be constructed, in which each grid point is located a hexagon size distance from the next closest point in all six directions.
+The centroids are derived from the shape file.
+The amount of centroids within the geographic area is used to determine a hexagon size if one is not provided.
+The derived centroids are a necessary input for an appropriate grid to be constructed, each grid point is located a hexagon size distance from the next closest point in all six directions.
 The grid will initially cover the entire map space, encompassing all the centroid locations and will extend in all directions to the extent of the buffer distance.
 This buffer distance can be helpful to account for densely populated coastal areas, allowing the use of the sea for hexagon locations.
-The hexagon size will likely need adjustments depending on the density of the population.
 
-The centroids derived from the shape file are necessary inputs when creating a grid.
-The creation of the grid and filtering out the points unlikely to be used in the hexagon map results in the hexagon tile map grid.
-At this point, the centroid set and the grid become the necessary inputs to the allocation process.
+The centroid set derived from the shape file is necessary when creating a grid.
+The hexagon tile map grid requires the creation of the full grid followed by disregarding the points unlikely to be used in the hexagon map.
 
-A set of reference locations can be provided as focal points, such as capital cities of states or countries.
-Using focal points, the algorithm will create the order of allocation in order of the closest centroid locations to the focal points.
+The centroid set and hexagon tile map grid are necessary for the allocation process.
+Additionally, a set of reference locations can be provided as focal points, such as the capital cities of states or countries.
+The algorithm will use the focal points to create the order of allocation, prioritising the closest centroid locations to the focal points.
 Alternatively, a user can specify the variable that should be used to determine the order for the allocation.
-When allocating representative hexagons, the width parameter can be used to determine the flexibility of positioning using the relationship with the nearest reference location.
-A larger width parameter will increase the amount of available hexagon locations nearer to the centroid of the geographic location.
-A smaller width will maintain the orientation from the focal point to the centroid when selecting the hexagon location, however this could mean it is placed further from the centre of the cluster.
+
+When allocating representative hexagons, the width parameter can be used to determine the flexibility of positioning.
+Using the relationship with the nearest reference location, a larger width parameter will increase the amount of available hexagon locations nearer to the centroid of the geographic location.
+A smaller width will maintain the orientation from the focal point to the centroid when selecting the hexagon location.
+However, this could mean it is placed further from the geographic centroid location.
 
@@
 Hexagon tile maps can be useful to understand a distribution across a collection of geographic areas.
-However, these maps are not easily drawn, especially as the number of areas increases.
+However, these maps are not easy to create manually, especially as the number of areas increases.
 This algorithm was created to automate this process, and reduce the manual load involved in creating and implementing alternative displays.
-This allows map makers and data communicators to allocate their time to choosing the most effective display, rather than manually creating them.
+This allows map makers and data communicators to spend their time to choosing the most effective display.
 
@@
 A user can tweak the parameters of the hexagon map using the additional arguments to the `create_hexmap` function, these options may affect the speed of the creation. 
+The hexagon size may need adjustments depending on the density of the population, users can provide an appropriate hexagon size and re-run the algorithm.
+The buffer distance may need to be increased if the coastal cities need to extend beyond the geographic land mass.
 
@@
 
-## Hexagon tile map of Australia
+### Hexagon tile map of Australia
 
@@
 This display highlights the density of Australian capital cities, as it draws attention to the many communities in Sydney, Melbourne and Hobart.
-This display also highlights the disparity in the burden of thyroid cancer for males in the communities of these three cities.
+This display also highlights the disparity in the burden of thyroid cancer for females in the communities of these three cities.
 There are several collections of red hexagons in Hobart that draw attention and they represent the communities with much higher rates of diagnosis than the Australian average.

### 2020-10-19 kobakian-cook.tex
Up to implementation

@@
 
-In many countries, residents are increasingly gathering to live in urban
-areas around major cities \citep{ACTUC}. The creation of approximately
-equal population areas results in dramatically different square meterage
-of the administrative geographic units, such as states or electorates.
-The units are filled with colour to represent the value of the statistic
-for each unit \citep{EI}. This can lead to unequal emphasis on the
-statistical value of each of the geographic units. This allows
-choropleth map displays to misrepresent the spatial distributions of
-human related statistics due to area-size bias \citep{BCM}. Figure
+Over time the density of living in major cities has increased as
+residents have gathered to live near urban areas \citep{ACTUC}. The
+division of these resident into approximately equal population areas
+results in dramatically different square meterage of administrative
+geographic units, such as states or electorates. In a choropleth map
+display the geographic units are filled with colour to represent the
+value of the statistic for each unit \citep{EI}. This can allow unequal
+emphasis on the statistical value of each of the geographic units. This
+allows choropleth map displays to misrepresent the spatial distributions
+of human related statistics due to area-size bias \citep{BCM}. Figure
 \ref{fig:choro} is a choropleth map that uses colour to display the
 estimated Standardised Incidence Ratios (SIRs) of thyroid cancer for
-males for each of the Statistical Areas at Level 2 (SA2) used by the
+females, in each of the Statistical Areas at Level 2 (SA2) used by the
 \citet{abs2011}. The Australian choropleth map display draws attention
 to the expanse of dark and light blue areas across the rural communities
-in all states. The SA2s around Brisbane stand out as more orange and
-red.
+in all states. The SA2s around Brisbane and in northern New South Wales
+stand out as more orange and red. However, this display neglects the
+vast amount of Australia residents living in the densely populated
+capital cities.
 
@@
 
-There are several established alternative visualisation methods. Tile
-maps, Rectangular cartograms \citep{ORC} and Dorling cartograms
-\citep{ACTUC} all use one simple shape to represent each geographic
-unit. They all minimise the emphasis on the size or shape of the
-geographic areas. These alternative map displays focus on the
-relationship between neighbours, attempting to preserve connections, and
-disregard the unique shapes of the administrative boundaries. Figure
-\ref{fig:tas_displays} shows a collection of alternative map displays,
-this includes a) a contiguous cartogram, b) a non-contiguous cartogram,
-and c) a Dorling cartogram.
-
 The familiar choropleth map display is often used to allow the user to
@@
 
+There are several established alternative visualisation methods. Tile
+maps, Rectangular cartograms \citep{ORC} and Dorling cartograms
+\citep{ACTUC} all use one simple shape to represent each geographic
+unit. They all minimise the emphasis on the size or shape of the
+geographic areas. These alternative map displays focus on the
+relationship between neighbours, attempting to preserve connections, and
+disregard the unique shapes of the administrative boundaries. Figure
+\ref{fig:tas_displays} shows a collection of alternative map displays,
+this includes a) a contiguous cartogram, b) a non-contiguous cartogram,
+and c) a Dorling cartogram.
+
 \begin{Schunk}
@@
 connection in the transformed display. The contiguous cartogram
-displayed in figure \ref{fig:tas_displays}b) draws attention to smaller
+displayed in figure \ref{fig:tas_displays}a) draws attention to smaller
 geographic units when they are rescaled according to the population
 \citep{DMAHP}. These new shapes can now be coloured to represent a
-second variable. This display can create twisted and unfamiliar shapes
-from the geographic units as the algorithms must satisfy the topology
-conditions, especially when there are communities located geographically
-far from their neighbours \citep{TVSSS}. This shown in the northern SA2s
-of Tasmania with an average (yellow) estimated SIR of thyroid for males.
+second variable. The algorithm uses the geographic shape of the areas
+and iterates toward sizing the areas to represent the population. This
+display can create twisted and unfamiliar shapes from the geographic
+units as the algorithms must satisfy the topology conditions, especially
+when there are communities located geographically far from their
+neighbours \citep{TVSSS}.
 
-The non-contiguous cartogram in figure \ref{fig:tas_displays}c) also
+The non-contiguous cartogram in figure \ref{fig:tas_displays}b) also
 uses the population to rescale the geographic units. Unlike the
@@
 the disparity between large rural areas and small urban areas means that
-the city of Hobart, shown in the inset map looks reasonable, but these
-units are not visible in the context of the Tasmania state map.
-Depending on the difference between the population and geographic land
-size, the amount of white space can also prevent meaningful
-understanding of the distribution \citep{TVSSS}.
+the city of Hobart may look reasonable but these units are not visible
+in the context of the Tasmania state map. Depending on the difference
+between the population and geographic land size, the amount of white
+space can also prevent meaningful understanding of the distribution
+\citep{TVSSS}.
 
@@
 of coastal cities in Tasmania that were not apparent in figure
-\ref{fig:tas_displays} a), or b).
+\ref{fig:tas_displays} a), or b). This display also highlights that the
+approximation of equal population is not easy to fulfil, as there is
+some disparity in the sizes of the circles.
 
@@
 
-The purpose of this algorithm is to create a map display that highlights
-the spatial distributions for populations. There has been an increasing
-need for displays that recognise the large number of people that live in
-dense urban environments. The algorithm intends to maintain the spatial
-relationships of a group of geographic units in two ways: between each
-unit and its neighbours; and between each unit and the closest focal
-point. The algorithm allocates geographic units to a representative
-hexagon, in order of their proximity to the closest focal point.
+The purpose of this algorithm is to create an alternative map display
+that highlights the spatial distributions for populations. There has
+been an increasing need for displays that recognise the large number of
+people that live in dense urban environments. The algorithm intends to
+maintain the spatial relationships of a group of geographic units using
+the relationship between each unit and the closest focal point. The
+algorithm allocates geographic units to a representative hexagon, in
+order of their proximity to the closest focal point.
 
@@
 point \citep{PH}. This hive design inspired the use of multiple focal
-points in the algorithm, individual spirals are constructed outward from
-various points on the geographic map base.
+points in the algorithm, individual spirals are constructed by building
+out from various points on the geographic map base.
 
@@
 populated geographic regions surrounding the capital cities in
-Australia. Each capital city forms it's own layer of connected hexagons.
-Figure \ref{fig:hexmap} allows the distributions in the capital cities
-to be viewed at a deeper scale. Sydney is now notable for the
-considerable amount of red areas, not just for the surrounding orange
-areas around the New South Wales capital visible in the choropleth
-display in Figure \ref{fig:choro}. Brisbane and Perth also draw
-attention for the many orange areas. Interestingly there is no clear
-divide between rural and urban SA2 areas as Melbourne, Darwin, Adelaide
-and Hobart have low rates of thyroid cancer diagnosis.
+Australia. Each capital city forms it's own collection of connected
+hexagons. Figure \ref{fig:hexmap} allows the distributions in the
+capital cities to be viewed at a deeper scale. Sydney is now notable for
+the considerable amount of red hexagons, not just for the surrounding
+orange areas around the New South Wales capital visible in the
+choropleth display in Figure \ref{fig:choro}. Brisbane and Perth also
+draw attention for the many orange hexagons. Interestingly there is no
+clear divide between rural and urban SA2 areas as many rural areas, and
+the cities of Melbourne, Darwin, Adelaide and Hobart have low rates of
+thyroid cancer diagnosis for females.
 
@@
 \includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/hexmap-1} \caption[A hexagon tile map of the Statistical Areas of Australia at Level 2]{A hexagon tile map of the Statistical Areas of Australia at Level 2.
-The colours communicate the value of the estimated SIR of thyroid for males, they range from much lower than average (blue) to much higher than average (red).}\label{fig:hexmap}
+The colours communicate the value of the estimated SIR of thyroid for females, they range from much lower than average (blue) to much higher than average (red).}\label{fig:hexmap}
 \end{figure}
@@
 centroids from the polygons provided, then create the grid of hexagons
-locations. These two steps are defined in the blue left column of the
-flow chart in Figure \ref{fig:sugarbag_flow}. Each centroid can then be
-allocated to an available hexagon location. The steps for the allocation
-process are detailed in the right column of Figure
-\ref{fig:sugarbag_flow}. To make tessellated plots, the point locations
-are converted to hexagon shapes, with the hexagon size used in the grid.
+locations. These two processes are defined in the blue left column of
+the flow chart in Figure \ref{fig:sugarbag_flow}. Each centroid can then
+be allocated to an available hexagon location. The steps for the
+allocation process are detailed in the right column of Figure
+\ref{fig:sugarbag_flow}. There are several filter steps to speed the
+process of selecting an appropriate hexagon to represent each geographic
+area. To make tessellated plots with the hexagon allocations, the point
+locations are converted to hexagon shapes, with the hexagon size used in
+the grid.
 
@@
 
-Only two inputs are necessary to begin using the algorithm, the shape
-file, and the id variable. The id variable should uniquely identify each
-geographic unit in the shape file.
+Only two inputs are necessary to begin using the algorithm in the
+\texttt{sugarbag} package; the shape file, and the id variable. The id
+variable should uniquely identify each geographic unit in the shape
+file.
 
-The centroids can be derived from the shape file. The amount of
-centroids is used to determine a hexagon size. The derived centroids are
-a necessary input for an appropriate grid to be constructed, in which
-each grid point is located a hexagon size distance from the next closest
-point in all six directions. The grid will initially cover the entire
-map space, encompassing all the centroid locations and will extend in
-all directions to the extent of the buffer distance. This buffer
-distance can be helpful to account for densely populated coastal areas,
-allowing the use of the sea for hexagon locations. The hexagon size will
-likely need adjustments depending on the density of the population.
+The centroids are derived from the shape file. The amount of centroids
+within the geographic area is used to determine a hexagon size if one is
+not provided. The derived centroids are a necessary input for an
+appropriate grid to be constructed, each grid point is located a hexagon
+size distance from the next closest point in all six directions. The
+grid will initially cover the entire map space, encompassing all the
+centroid locations and will extend in all directions to the extent of
+the buffer distance. This buffer distance can be helpful to account for
+densely populated coastal areas, allowing the use of the sea for hexagon
+locations.
 
-The centroids derived from the shape file are necessary inputs when
-creating a grid. The creation of the grid and filtering out the points
-unlikely to be used in the hexagon map results in the hexagon tile map
-grid. At this point, the centroid set and the grid become the necessary
-inputs to the allocation process.
+The centroid set derived from the shape file is necessary when creating
+a grid. The hexagon tile map grid requires the creation of the full grid
+followed by disregarding the points unlikely to be used in the hexagon
+map.
 
-A set of reference locations can be provided as focal points, such as
-capital cities of states or countries. Using focal points, the algorithm
-will create the order of allocation in order of the closest centroid
-locations to the focal points. Alternatively, a user can specify the
-variable that should be used to determine the order for the allocation.
+The centroid set and hexagon tile map grid are necessary for the
+allocation process. Additionally, a set of reference locations can be
+provided as focal points, such as the capital cities of states or
+countries. The algorithm will use the focal points to create the order
+of allocation, prioritising the closest centroid locations to the focal
+points. Alternatively, a user can specify the variable that should be
+used to determine the order for the allocation.
+
 When allocating representative hexagons, the width parameter can be used
-to determine the flexibility of positioning using the relationship with
-the nearest reference location. A larger width parameter will increase
+to determine the flexibility of positioning. Using the relationship with
+the nearest reference location, a larger width parameter will increase
 the amount of available hexagon locations nearer to the centroid of the
 geographic location. A smaller width will maintain the orientation from
-the focal point to the centroid when selecting the hexagon location,
-however this could mean it is placed further from the centre of the
-cluster.
+the focal point to the centroid when selecting the hexagon location.
+However, this could mean it is placed further from the geographic
+centroid location.
 
@@
 \hypertarget{hexagon-tile-map-of-australia}{%
-\subsection{Hexagon tile map of
+\subsubsection{Hexagon tile map of
 Australia}\label{hexagon-tile-map-of-australia}}
@@
 in Sydney, Melbourne and Hobart. This display also highlights the
-disparity in the burden of thyroid cancer for males in the communities
+disparity in the burden of thyroid cancer for females in the communities
 of these three cities. There are several collections of red hexagons in

### 2020-10-21 kobakian-cook.Rmd
Editing to end of doc

@@
 
-#### User choices
+### User choices
 
@@
 
-#### Creating a hexagon tile map
-
 The following code creates the hexagon tile map for all the Statistical Areas at Level 2 in Tasmania.
-These steps can be executed by the main function, `create_hexmap`, or can be implemented separately for more flexibility.
+These steps can be executed by the main function, `create_hexmap`, or can be run separately for more flexibility.
 
 If a user would like to perform each of the steps of the algorithm themselves, the necessary inputs will change for each function.
+For example, the `allocate` function can be used directly when a user wishes to use a set of centroids, rather than [@sf] polygons.
 
-Users may choose to only use the `allocate` function when they wish to use a set of centroids, rather than [@sf] polygons.
-
-#### Polygon set
-
-The polygon set of Statistical Areas at Level 2 (SA2) [@abs2011] of Tasmania in 2011 is provided with the `sugarbag` package as `tas_sa2`.
+The polygon set of Statistical Areas at Level 2 (SA2) [@abs2011] of Tasmania in 2011 is accessed from the `absmapsdata` package.
 A single column of the data set is used to identify the unique areas.
@@
 The longitude and latitude centre of the capital cities of Australia are used as focal points to allocate each geographic area around the closest capital city.
-Hobart will be the common focal point, as this example uses only the areas in the state of Tasmania.
+Hobart will be the focal point, as this example uses only the areas in the state of Tasmania.
 
@@
 
-#### Step 1: Derive the set of centroid points
+### Step 1: Derive the set of centroid points
 
-A set of centroids may be used directly.
-The set of polygons should be provided as an `sf` object, this is a data frame containing a `geometry` column.
-The `read_shape` function can assist in creating this object for use in `R`.
+The set of polygons should be provided as an `sf` object, this is a data frame containing a `geometry` column. The `read_shape` function can assist in creating this object for use in `R`.
 
@@
 
-#### Step 2: Create the hexagon grid points
+### Step 2: Create the hexagon grid points
 
 A grid is created to ensure tessellation between the hexagons that represent the geographic units on a hexagon tile map.
+The grid of possible hexagon locations is made using the `create_grid` function.
+It uses the centroids, the hexagon size and the buffer distance.
 
-The grid of possible hexagon locations is made using the `create_grid` function. It uses the centroids, the hexagon size and the buffer distance.
-
-##### Creating a tessellated grid
+#### Creating a tessellated grid
 
@@
 A unique hexagon location is created from all intersections of the longitude columns and latitude rows.
-Figure \ref{fig:filterprocess} shows the original grid on the left, to allow for tessellating hexagons, every second latitude row on the grid is shifted right, by half of the hexagon size.
-The grid for tessellation is shown on the right.
+Figure \ref{fig:filterprocess}a) allows for tessellating hexagons after every second latitude row on the grid is shifted right, by half of the hexagon size.
 
@@
 
-##### Rolling windows
+#### Rolling windows
 
 Not all of the grid points will be used, especially if islands result in a large grid space.
-To filter the grid for appropriate hexagon locations for allocation, the `create_buffer` function is used by `create_grid`.
+To filter the grid for appropriate hexagon locations for allocation, the `create_grid` function will call the `create_buffer` function.
 It finds the grid points needed to best capture the set of centroids on a hexagon tile map.
+It also helps reduce the amount of time taken, as it decreases the amount of points considered for each centroid allocation.
 
@@
 The amount of rows in each latitude group and the amount of columns in each longitude group are used as the width of rolling windows.
-The rolling windows can be seen on the bottom and right of the grid shown in Figure \ref{fig:filterprocess}.
-This will tailor the available grid points to those most likely to be used.
-It also helps reduce the amount of time taken, as it decreases the amount of points considered for each centroid allocation.
 
-The first rolling window function finds the minimum and maximum centroid values for the sliding window groups of longitude columns and the groups of latitude rows.
+The first rolling window step finds the minimum and maximum centroid values within each of the sliding window groups of longitude columns, and the groups of latitude rows.
 
-The second rolling window function finds the average of the rolling minimum and maximum centroid values, for the longitude columns and latitude rows.
+The second rolling window step finds the average of the rolling minimum and maximum centroid values, for the longitude columns and latitude rows.
 
-##### Filtering the grid
+#### Filtering the grid
 
-The grid points are kept only if they fall between the rolling average of the minimum and maximum centroid values after accounting for the buffer distance, for each row and column of the grid.
-The sparsely populated South-West region of National Park has much fewer points available compared to the South-East region containing the city of Hobart.
+The hexagon grid points are kept only if they fall within the rolling average of the minimum and maximum centroid values after accounting for the buffer distance, for each row and column of the grid.
+The sparsely populated South-West region of National Park has very few points available compared to the South-East region near the city of Hobart.
 
-```{r filtergrid, fig.cap = "The remaining hexagon locations from all the possible points in the initial grid after the buffer is applied.
-The blue dots show the grid points left to choose from after the buffer step."}
+```{r filtergrid, fig.cap = "Each key step in the hexagon allocation process.
+The full hexagon grid in a) is created first.
+The buffer is applied and the remaining points are shown as larger, dark green circles, the potential hexagon points that were removed are shown as smaller, light green points.
+For each centroid in the set, c) shows the points left after the closest points are selected as potential locations.
+The relationship between Hobart (the cross) and the centroid (the yellow triangle is used to filter the potential locations within a wedge."}
 g1 <- ggplot() + 
@@
 
-##### Centroid to focal point distance
+#### Centroid to focal point distance
 
-The distance between each centroid in the set, and each of the focal points provided is calculated.
-The name of the closest focal point, and the distance and angle from focal point to polygon centroid is joined to polygon data set.
-To minimise time taken for this step only one option is provided, Tasmania's capital city Hobart.
-The order for allocation is determined by the distance between the polygon centroid and it's closest focal point.
-The points are arranged from the centroid closest to the focal point(s), to the furthest.
+The distance is calculated between each centroid in the set, and each of the focal points provided.
+The distance and angle from the closest focal point to polygon centroid is used in the allocation process as the order for allocation is determined by the distance between the polygon centroid and it's closest focal point.
 
-#### Step 3: Allocate each centroid to a hexagon grid point
+### Step 3: Allocate each centroid to a hexagon grid point
 
 Allocation of all centroids takes place using the set of polygon centroids and the hexagon map grid.
+The points are arranged from the centroid closest to the focal point(s), to the furthest.
 Centroid allocation begins with the closest centroid to a focal point.
 This will preserve spatial relationships with the focal point, as the inner city areas are allocated first, they will be placed closest to the capital, and the areas that are further will then be accommodated.
-The possible hexagon grid points reduces by one after each allocation, then only those that have not yet been allocated are considered.
+The set of possible hexagon grid points reduces by one after each centroid is allocated, then only the grid points that have not yet been selected are considered.
 
@@
 
-##### Filter the grid for unassigned hexagon points
+#### Filter the grid for unassigned hexagon points
 
@@
 
-##### Filter the grid points for those closest to the centroid
+#### Filter the grid points for those closest to the centroid
 
@@
 
-The algorithm then removes the outer corners of the square, creating a circle of points, by only keeping points within a certain radial distance around the original centroid location.
+The algorithm creates a circle of points, by only keeping points within a certain radial distance around the original centroid location.
 
@@
 f_centroid <- centroids %>%
-        filter(rownumber == 7)
+        filter(rownumber == 8)
 
@@
 
-```{r filterprocess, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, out.width = "120%", height = 8}
+```{r filterprocess, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, height = 8}
 full_grid <- full_grid %>% filter(hex_long > bbox$min[1], hex_long < bbox$max[1],
@@
                   filter(points == "Hobart") %>% 
-                  slice_min(rownumber, n = 6)
+                  slice_min(rownumber, n = 7)
 
@@
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = f_grid, size = 1) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#e374b9", data = hex, size = 1.5) + ggtitle("d")
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", fill = "white", data = hex, size = 1.5, shape = 21) + ggtitle("d")
 
-grid.arrange(g1, g2,
-             f1, f2, ncol = 2)
+gridExtra::grid.arrange(g1, g2,
+                        f1, f2)
 ```
@@
 
-### Hexagon tile map of Australia
-
-This algorithm has been applied to the complete set of all Australian Statistical Areas at Level 2.
+When the algorithm is applied to the complete set of all Australian Statistical Areas at Level 2 it results in the hexagon tile map display shown in Figure \ref{fig:hexmap}.
 This display highlights the density of Australian capital cities, as it draws attention to the many communities in Sydney, Melbourne and Hobart.
-This display also highlights the disparity in the burden of thyroid cancer for females in the communities of these three cities.
-There are several collections of red hexagons in Hobart that draw attention and they represent the communities with much higher rates of diagnosis than the Australian average.
-The communities south of Hobart show a gradient of colour as the values progress from higher than average, to much lower than average for the communities closer to the Sydney CBD.
-This pattern progresses into the communities with lower than average rates in Melbourne and Tasmania.
+This display also highlights the disparity in the burden of thyroid cancer for females in the communities of these cities.
+There are several collections of red hexagons in Sydney that represent the communities with much higher rates of diagnosis than the Australian average.
+Brisbane also experiences higher than average rates of diagnosis, but has more orange than red, which represents much higher rates.
+The females in the cities of Adelaide and Perth  show much lower rates of diagnosis.
 
 Compared to the choropleth map display, the low rates in the rural Australian communities are no longer dominating the display.
-The much higher than average rates in Sydney draw more attention in the hexagon tile map display unlike the red and orange areas in the city of Hobart that draw attention in both displays.
+While the representative hexagons are still visible against the black background, the much lower than average rates in the Northern Territory are less noticeable.
 
@@
 
+Creating an animation connecting these two displays can allow users t grasp the meaning of the connected hexagons.
+It will also highlight the density of the communities using the rapid expansion of the inner-city areas, these hexagons will move the furthest and will move rapidly in the animation from their geographic locations.
+The rapid decrease in size of the large rural areas can show how large the landmass of Statistical Areas can be, and how few people occupy rural areas.
 The `gganimate` [@gganimate] package can be used to make an animation.
-It requires connecting the polygons for each area in two displays, which can be done using the `sf_id` variable, such as the SA2 name.
-The animation connecting these two displays will highlight the rapid growth of the inner-city areas that emphasises the density of the communities.
-The hexagons that move the furthest will move rapidly in the animation.
-The rapid decreases of the large rural areas also show how much greater the landmass of Statistical Areas can be.
+It connects the polygons for each area in the two displays using the `sf_id` variable, the names of the statistical areas, and creates intermediate displays as they geographic areas shrink or expand to the chosen hexagon size.
 
@@
 
-It is possible to use alternative maps to communicate spatial distributions.While a choropleth map display is the current practice spatial visualisation of geographical data.
-Current methods do not always work for Australia due to the large geographic space between the densely populated capital cities.
-The administrative boundaries may also distract from the statistics communicated using colour.
+A choropleth map display is the current practice spatial visualisation for geographical data.
+It is possible to enhance the communication of spatial distributions using alternative map displays.
+Current methods for alternative maps do not always work for Australia due to the large rural geographic space between the densely populated capital cities.
+The administrative boundaries may also distract from the statistics communicated using colour due to the small size of some areas.
 
 Alternative maps highlight the value of the statistics across the geographic units.
-Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing each administrative area.
+These methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing each administrative area.
 This acknowledges that the amount of residents can be different but recognises that each population area is equally important.
-The solution to this visualisation problem has equally sized areas, with neighbourhood boundary connections.
-This map algorithm is implemented in the `sugarbag` [@sugarbag] package written for `R`.
-The `sugarbag` package creates tessellated hexagon tile maps.
+The solution to this visualisation problem can be using equally sized areas, with neighbourhood boundary connections.
+The `sugarbag` package for `R` creates tessellated hexagon tile maps by automating an algorithm to design these displays.
 The Australian application preserves the spatial relationships, emphasising capital cities.
-The hexagon tile map is a visualisation solution that highlights spatial distributions.
 
 These hexagons equally represent each area.
-However, the tessellation does not allow the size of the hexagons to represent another variable, similar to the choropleth maps.
+However, similar to the choropleth map display the tessellation does not allow the size of the hexagons to represent another variable.
 The algorithm is heavily dependent on the focal points used, as this determines the order of allocation.
-It works on the assumption that viewers can use directional relationships to identify their neighbourhoods but this can be aided by the animation.
+It works on the assumption that viewers can identify their neighbourhoods using the relative directional relationships but this can be aided by the use of animation.
 With careful consideration of the choropleth map, the small geographic inner city areas may have been noticed by viewers, but the hexagon tile map display emphasises them.
-The communities in northern Tasmania and the Northern territory do not draw attention because of their size as in the choropleth, but their colour is still noticeably below average when contrasted with the hexagons further south.
+The communities in northern Tasmania and the Northern territory do not draw attention because of their size as in the choropleth, but their colour is still noticeably below average when contrasted with the hexagons in New South Wales.
 
@@
 
-The Dorling cartogram was the most influential in the design of the hexagon tile map.
-The use of a hexagon provides a simple shape that shifts the focus of the visualisation from the shape of SA2s to the distribution effects of a disease on communities.
-not impeded by the irregular and unusual shapes created by a contiguous cartogram and the immense white space created on the non-contiguous cartogram.
+The Dorling cartogram was the most influential alternative map display for the design of the hexagon tile map.
+The use of a hexagon shifts the focus of the visualisation from the shape of SA2s to the distribution effects of a disease on communities.
+It is not impeded by the irregular and unusual shapes created by a contiguous cartogram and the immense white space created on the non-contiguous cartogram.
 Hexagons can emphasise the relationship between neighbouring communities by allowing their sides to touch.
-The tessellation crated by adjoining hexagons for densely populated areas is helpful as it shows that most communities are not islands onto themselves, but are intrinsically connected to those around them.
-As seen in the Dorling cartogram in figure \ref{fig:tas_displays}c), the tessellation that allows boundary connections was not imposed for rural communities, where centroid of the geographic unit was located far from others, a feature that allows distant but dense populations of the coastal towns of Tasmania to be recognised.
-
-The choropleth map that uses the geographic shapes of areas can be seen in figure \ref{fig:choro}.
-Figure \ref{fig:hexmap} displays the Australian areas with equally sized hexagons.
-This display allows the small and densely populated inner city areas to be easily contrasted with their neighbouring areas.
+The tessellation created by adjoining hexagons for densely populated areas is helpful as it shows that most communities are not islands onto themselves, but are intrinsically connected to those around them.
+As seen in the Dorling cartogram in figure \ref{fig:tas_displays}c), the tessellation that allows boundary connections was not imposed for rural communities, where centroid of the geographic unit was located far from others, a feature that allows distant but dense populations of the coastal towns of southern Tasmania to be recognised.
 
@@
 
-Future work will include refining the algorithm.
-It would be possible to take a logarithmic function rather than a direct angle to help choose a closer hexagon to the original centroid location, before increasing the width of the angle used to filter the hexagons.
-
 This algorithm has only been tested using single countries, and does not consider definite borders of countries.
 While the buffer allows extension beyond the furthest centroids, there is no mechanism to protect the borders and ensure centroids are placed within the geographic borders of a country.
-
+It would be also possible to take a logarithmic function in the filter steps for selection of a hexagon grid point.
+A direct angle is currently used, but this may narrowly miss appropriate hexagons, a logarithmic function may help to choose a closer hexagon to the original centroid location, before increasing the width of the angle used to filter the hexagons.
 This algorithm is an effective start to creating hexagon tile maps for many geographic units.
 
-#### Installation
+### Installation
 
@@
 
-```{r eval=FALSE}
+```{r eval=FALSE, echo = TRUE}
 install.packages("sugarbag")
@@
 
-```{r eval=FALSE}
+```{r eval=FALSE, echo = TRUE}
 devtools::install_github("srkobakian","sugarbag")
 ```
-
-Load the library into your R session with:
-
-```{r}
-library(sugarbag)
-```

### 2020-10-21 kobakian-cook.tex
Editing to end of doc

@@
 \hypertarget{user-choices}{%
-\paragraph{User choices}\label{user-choices}}
+\subsubsection{User choices}\label{user-choices}}
 
@@
 Hexagon tile maps can be useful to understand a distribution across a
-collection of geographic areas. However, these maps are not easily
-drawn, especially as the number of areas increases. This algorithm was
-created to automate this process, and reduce the manual load involved in
-creating and implementing alternative displays. This allows map makers
-and data communicators to allocate their time to choosing the most
-effective display, rather than manually creating them.
+collection of geographic areas. However, these maps are not easy to
+create manually, especially as the number of areas increases. This
+algorithm was created to automate this process, and reduce the manual
+load involved in creating and implementing alternative displays. This
+allows map makers and data communicators to spend their time to choosing
+the most effective display.
 
@@
 arguments to the \texttt{create\_hexmap} function, these options may
-affect the speed of the creation.
-
-\hypertarget{creating-a-hexagon-tile-map}{%
-\paragraph{Creating a hexagon tile
-map}\label{creating-a-hexagon-tile-map}}
+affect the speed of the creation. The hexagon size may need adjustments
+depending on the density of the population, users can provide an
+appropriate hexagon size and re-run the algorithm. The buffer distance
+may need to be increased if the coastal cities need to extend beyond the
+geographic land mass.
 
@@
 Areas at Level 2 in Tasmania. These steps can be executed by the main
-function, \texttt{create\_hexmap}, or can be implemented separately for
-more flexibility.
+function, \texttt{create\_hexmap}, or can be run separately for more
+flexibility.
 
 If a user would like to perform each of the steps of the algorithm
-themselves, the necessary inputs will change for each function.
-
-Users may choose to only use the \texttt{allocate} function when they
-wish to use a set of centroids, rather than \citep{sf} polygons.
-
-\hypertarget{polygon-set}{%
-\paragraph{Polygon set}\label{polygon-set}}
+themselves, the necessary inputs will change for each function. For
+example, the \texttt{allocate} function can be used directly when a user
+wishes to use a set of centroids, rather than \citep{sf} polygons.
 
 The polygon set of Statistical Areas at Level 2 (SA2) \citep{abs2011} of
-Tasmania in 2011 is provided with the \texttt{sugarbag} package as
-\texttt{tas\_sa2}. A single column of the data set is used to identify
-the unique areas. In this case, the unique SA2 names for each SA2 have
-been used.
+Tasmania in 2011 is accessed from the \texttt{absmapsdata} package. A
+single column of the data set is used to identify the unique areas. In
+this case, the unique SA2 names for each SA2 have been used.
 
@@
 used as focal points to allocate each geographic area around the closest
-capital city. Hobart will be the common focal point, as this example
-uses only the areas in the state of Tasmania.
+capital city. Hobart will be the focal point, as this example uses only
+the areas in the state of Tasmania.
 
@@
 \hypertarget{step-1-derive-the-set-of-centroid-points}{%
-\paragraph{Step 1: Derive the set of centroid
+\subsubsection{Step 1: Derive the set of centroid
 points}\label{step-1-derive-the-set-of-centroid-points}}
 
-A set of centroids may be used directly. The set of polygons should be
-provided as an \texttt{sf} object, this is a data frame containing a
-\texttt{geometry} column. The \texttt{read\_shape} function can assist
-in creating this object for use in \texttt{R}.
+The set of polygons should be provided as an \texttt{sf} object, this is
+a data frame containing a \texttt{geometry} column. The
+\texttt{read\_shape} function can assist in creating this object for use
+in \texttt{R}.
 
@@
 \hypertarget{step-2-create-the-hexagon-grid-points}{%
-\paragraph{Step 2: Create the hexagon grid
+\subsubsection{Step 2: Create the hexagon grid
 points}\label{step-2-create-the-hexagon-grid-points}}
@@
 A grid is created to ensure tessellation between the hexagons that
-represent the geographic units on a hexagon tile map.
-
-The grid of possible hexagon locations is made using the
-\texttt{create\_grid} function. It uses the centroids, the hexagon size
-and the buffer distance.
+represent the geographic units on a hexagon tile map. The grid of
+possible hexagon locations is made using the \texttt{create\_grid}
+function. It uses the centroids, the hexagon size and the buffer
+distance.
 
 \hypertarget{creating-a-tessellated-grid}{%
-\subparagraph{Creating a tessellated
+\paragraph{Creating a tessellated
 grid}\label{creating-a-tessellated-grid}}
@@
 hexagon location is created from all intersections of the longitude
-columns and latitude rows. Figure \ref{fig:filterprocess} shows the
-original grid on the left, to allow for tessellating hexagons, every
-second latitude row on the grid is shifted right, by half of the hexagon
-size. The grid for tessellation is shown on the right.
+columns and latitude rows. Figure \ref{fig:filterprocess}a) allows for
+tessellating hexagons after every second latitude row on the grid is
+shifted right, by half of the hexagon size.
 
 \hypertarget{rolling-windows}{%
-\subparagraph{Rolling windows}\label{rolling-windows}}
+\paragraph{Rolling windows}\label{rolling-windows}}
 
@@
 a large grid space. To filter the grid for appropriate hexagon locations
-for allocation, the \texttt{create\_buffer} function is used by
-\texttt{create\_grid}. It finds the grid points needed to best capture
-the set of centroids on a hexagon tile map.
+for allocation, the \texttt{create\_grid} function will call the
+\texttt{create\_buffer} function. It finds the grid points needed to
+best capture the set of centroids on a hexagon tile map. It also helps
+reduce the amount of time taken, as it decreases the amount of points
+considered for each centroid allocation.
 
@@
 columns in each longitude group are used as the width of rolling
-windows. The rolling windows can be seen on the bottom and right of the
-grid shown in Figure \ref{fig:filterprocess}. This will tailor the
-available grid points to those most likely to be used. It also helps
-reduce the amount of time taken, as it decreases the amount of points
-considered for each centroid allocation.
+windows.
 
-The first rolling window function finds the minimum and maximum centroid
-values for the sliding window groups of longitude columns and the groups
-of latitude rows.
+The first rolling window step finds the minimum and maximum centroid
+values within each of the sliding window groups of longitude columns,
+and the groups of latitude rows.
 
-The second rolling window function finds the average of the rolling
-minimum and maximum centroid values, for the longitude columns and
-latitude rows.
+The second rolling window step finds the average of the rolling minimum
+and maximum centroid values, for the longitude columns and latitude
+rows.
 
 \hypertarget{filtering-the-grid}{%
-\subparagraph{Filtering the grid}\label{filtering-the-grid}}
+\paragraph{Filtering the grid}\label{filtering-the-grid}}
 
-The grid points are kept only if they fall between the rolling average
-of the minimum and maximum centroid values after accounting for the
-buffer distance, for each row and column of the grid. The sparsely
-populated South-West region of National Park has much fewer points
-available compared to the South-East region containing the city of
-Hobart.
+The hexagon grid points are kept only if they fall within the rolling
+average of the minimum and maximum centroid values after accounting for
+the buffer distance, for each row and column of the grid. The sparsely
+populated South-West region of National Park has very few points
+available compared to the South-East region near the city of Hobart.
 
 \hypertarget{centroid-to-focal-point-distance}{%
-\subparagraph{Centroid to focal point
+\paragraph{Centroid to focal point
 distance}\label{centroid-to-focal-point-distance}}
 
-The distance between each centroid in the set, and each of the focal
-points provided is calculated. The name of the closest focal point, and
-the distance and angle from focal point to polygon centroid is joined to
-polygon data set. To minimise time taken for this step only one option
-is provided, Tasmania's capital city Hobart. The order for allocation is
-determined by the distance between the polygon centroid and it's closest
-focal point. The points are arranged from the centroid closest to the
-focal point(s), to the furthest.
+The distance is calculated between each centroid in the set, and each of
+the focal points provided. The distance and angle from the closest focal
+point to polygon centroid is used in the allocation process as the order
+for allocation is determined by the distance between the polygon
+centroid and it's closest focal point.
 
 \hypertarget{step-3-allocate-each-centroid-to-a-hexagon-grid-point}{%
-\paragraph{Step 3: Allocate each centroid to a hexagon grid
+\subsubsection{Step 3: Allocate each centroid to a hexagon grid
 point}\label{step-3-allocate-each-centroid-to-a-hexagon-grid-point}}
@@
 Allocation of all centroids takes place using the set of polygon
-centroids and the hexagon map grid. Centroid allocation begins with the
-closest centroid to a focal point. This will preserve spatial
-relationships with the focal point, as the inner city areas are
-allocated first, they will be placed closest to the capital, and the
-areas that are further will then be accommodated. The possible hexagon
-grid points reduces by one after each allocation, then only those that
-have not yet been allocated are considered.
+centroids and the hexagon map grid. The points are arranged from the
+centroid closest to the focal point(s), to the furthest. Centroid
+allocation begins with the closest centroid to a focal point. This will
+preserve spatial relationships with the focal point, as the inner city
+areas are allocated first, they will be placed closest to the capital,
+and the areas that are further will then be accommodated. The set of
+possible hexagon grid points reduces by one after each centroid is
+allocated, then only the grid points that have not yet been selected are
+considered.
 
@@
 \hypertarget{filter-the-grid-for-unassigned-hexagon-points}{%
-\subparagraph{Filter the grid for unassigned hexagon
+\paragraph{Filter the grid for unassigned hexagon
 points}\label{filter-the-grid-for-unassigned-hexagon-points}}
@@
 \hypertarget{filter-the-grid-points-for-those-closest-to-the-centroid}{%
-\subparagraph{Filter the grid points for those closest to the
+\paragraph{Filter the grid points for those closest to the
 centroid}\label{filter-the-grid-points-for-those-closest-to-the-centroid}}
@@
 
-The algorithm then removes the outer corners of the square, creating a
-circle of points, by only keeping points within a certain radial
-distance around the original centroid location.
+The algorithm creates a circle of points, by only keeping points within
+a certain radial distance around the original centroid location.
 
@@
 \begin{figure}
-\includegraphics[width=1.2\linewidth]{kobakian-cook_files/figure-latex/filterprocess-1} \caption[Filter for grid points within a square, then circular, distance for those closest to the centroid]{Filter for grid points within a square, then circular, distance for those closest to the centroid.}\label{fig:filterprocess}
+\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/filterprocess-1} \caption[Filter for grid points within a square, then circular, distance for those closest to the centroid]{Filter for grid points within a square, then circular, distance for those closest to the centroid.}\label{fig:filterprocess}
 \end{figure}
@@
 
-\hypertarget{hexagon-tile-map-of-australia}{%
-\subsubsection{Hexagon tile map of
-Australia}\label{hexagon-tile-map-of-australia}}
-
-This algorithm has been applied to the complete set of all Australian
-Statistical Areas at Level 2. This display highlights the density of
+When the algorithm is applied to the complete set of all Australian
+Statistical Areas at Level 2 it results in the hexagon tile map display
+shown in Figure \ref{fig:hexmap}. This display highlights the density of
 Australian capital cities, as it draws attention to the many communities
@@
 disparity in the burden of thyroid cancer for females in the communities
-of these three cities. There are several collections of red hexagons in
-Hobart that draw attention and they represent the communities with much
-higher rates of diagnosis than the Australian average. The communities
-south of Hobart show a gradient of colour as the values progress from
-higher than average, to much lower than average for the communities
-closer to the Sydney CBD. This pattern progresses into the communities
-with lower than average rates in Melbourne and Tasmania.
+of these cities. There are several collections of red hexagons in Sydney
+that represent the communities with much higher rates of diagnosis than
+the Australian average. Brisbane also experiences higher than average
+rates of diagnosis, but has more orange than red, which represents much
+higher rates. The females in the cities of Adelaide and Perth show much
+lower rates of diagnosis.
 
 Compared to the choropleth map display, the low rates in the rural
-Australian communities are no longer dominating the display. The much
-higher than average rates in Sydney draw more attention in the hexagon
-tile map display unlike the red and orange areas in the city of Hobart
-that draw attention in both displays.
+Australian communities are no longer dominating the display. While the
+representative hexagons are still visible against the black background,
+the much lower than average rates in the Northern Territory are less
+noticeable.
 
@@
 
-The \texttt{gganimate} \citep{gganimate} package can be used to make an
-animation. It requires connecting the polygons for each area in two
-displays, which can be done using the \texttt{sf\_id} variable, such as
-the SA2 name. The animation connecting these two displays will highlight
-the rapid growth of the inner-city areas that emphasises the density of
-the communities. The hexagons that move the furthest will move rapidly
-in the animation. The rapid decreases of the large rural areas also show
-how much greater the landmass of Statistical Areas can be.
+Creating an animation connecting these two displays can allow users t
+grasp the meaning of the connected hexagons. It will also highlight the
+density of the communities using the rapid expansion of the inner-city
+areas, these hexagons will move the furthest and will move rapidly in
+the animation from their geographic locations. The rapid decrease in
+size of the large rural areas can show how large the landmass of
+Statistical Areas can be, and how few people occupy rural areas. The
+\texttt{gganimate} \citep{gganimate} package can be used to make an
+animation. It connects the polygons for each area in the two displays
+using the \texttt{sf\_id} variable, the names of the statistical areas,
+and creates intermediate displays as they geographic areas shrink or
+expand to the chosen hexagon size.
 
@@
 
-It is possible to use alternative maps to communicate spatial
-distributions.While a choropleth map display is the current practice
-spatial visualisation of geographical data. Current methods do not
-always work for Australia due to the large geographic space between the
-densely populated capital cities. The administrative boundaries may also
-distract from the statistics communicated using colour.
+A choropleth map display is the current practice spatial visualisation
+for geographical data. It is possible to enhance the communication of
+spatial distributions using alternative map displays. Current methods
+for alternative maps do not always work for Australia due to the large
+rural geographic space between the densely populated capital cities. The
+administrative boundaries may also distract from the statistics
+communicated using colour due to the small size of some areas.
 
 Alternative maps highlight the value of the statistics across the
-geographic units. Alternative mapping methods allow increased
-understanding of the spatial distribution of a variable across the
-population, by fairly representing each administrative area. This
-acknowledges that the amount of residents can be different but
-recognises that each population area is equally important. The solution
-to this visualisation problem has equally sized areas, with
-neighbourhood boundary connections. This map algorithm is implemented in
-the \texttt{sugarbag} \citep{sugarbag} package written for \texttt{R}.
-The \texttt{sugarbag} package creates tessellated hexagon tile maps. The
+geographic units. These methods allow increased understanding of the
+spatial distribution of a variable across the population, by fairly
+representing each administrative area. This acknowledges that the amount
+of residents can be different but recognises that each population area
+is equally important. The solution to this visualisation problem can be
+using equally sized areas, with neighbourhood boundary connections. The
+\texttt{sugarbag} package for \texttt{R} creates tessellated hexagon
+tile maps by automating an algorithm to design these displays. The
 Australian application preserves the spatial relationships, emphasising
-capital cities. The hexagon tile map is a visualisation solution that
-highlights spatial distributions.
+capital cities.
 
-These hexagons equally represent each area. However, the tessellation
-does not allow the size of the hexagons to represent another variable,
-similar to the choropleth maps. The algorithm is heavily dependent on
-the focal points used, as this determines the order of allocation. It
-works on the assumption that viewers can use directional relationships
-to identify their neighbourhoods but this can be aided by the animation.
-With careful consideration of the choropleth map, the small geographic
-inner city areas may have been noticed by viewers, but the hexagon tile
-map display emphasises them. The communities in northern Tasmania and
-the Northern territory do not draw attention because of their size as in
-the choropleth, but their colour is still noticeably below average when
-contrasted with the hexagons further south.
+These hexagons equally represent each area. However, similar to the
+choropleth map display the tessellation does not allow the size of the
+hexagons to represent another variable. The algorithm is heavily
+dependent on the focal points used, as this determines the order of
+allocation. It works on the assumption that viewers can identify their
+neighbourhoods using the relative directional relationships but this can
+be aided by the use of animation. With careful consideration of the
+choropleth map, the small geographic inner city areas may have been
+noticed by viewers, but the hexagon tile map display emphasises them.
+The communities in northern Tasmania and the Northern territory do not
+draw attention because of their size as in the choropleth, but their
+colour is still noticeably below average when contrasted with the
+hexagons in New South Wales.
 
-The Dorling cartogram was the most influential in the design of the
-hexagon tile map. The use of a hexagon provides a simple shape that
-shifts the focus of the visualisation from the shape of SA2s to the
-distribution effects of a disease on communities. not impeded by the
-irregular and unusual shapes created by a contiguous cartogram and the
-immense white space created on the non-contiguous cartogram. Hexagons
-can emphasise the relationship between neighbouring communities by
-allowing their sides to touch. The tessellation crated by adjoining
-hexagons for densely populated areas is helpful as it shows that most
-communities are not islands onto themselves, but are intrinsically
-connected to those around them. As seen in the Dorling cartogram in
-figure \ref{fig:tas_displays}c), the tessellation that allows boundary
+The Dorling cartogram was the most influential alternative map display
+for the design of the hexagon tile map. The use of a hexagon shifts the
+focus of the visualisation from the shape of SA2s to the distribution
+effects of a disease on communities. It is not impeded by the irregular
+and unusual shapes created by a contiguous cartogram and the immense
+white space created on the non-contiguous cartogram. Hexagons can
+emphasise the relationship between neighbouring communities by allowing
+their sides to touch. The tessellation created by adjoining hexagons for
+densely populated areas is helpful as it shows that most communities are
+not islands onto themselves, but are intrinsically connected to those
+around them. As seen in the Dorling cartogram in figure
+\ref{fig:tas_displays}c), the tessellation that allows boundary
 connections was not imposed for rural communities, where centroid of the
 geographic unit was located far from others, a feature that allows
-distant but dense populations of the coastal towns of Tasmania to be
-recognised.
-
-The choropleth map that uses the geographic shapes of areas can be seen
-in figure \ref{fig:choro}. Figure \ref{fig:hexmap} displays the
-Australian areas with equally sized hexagons. This display allows the
-small and densely populated inner city areas to be easily contrasted
-with their neighbouring areas.
-
-Future work will include refining the algorithm. It would be possible to
-take a logarithmic function rather than a direct angle to help choose a
-closer hexagon to the original centroid location, before increasing the
-width of the angle used to filter the hexagons.
+distant but dense populations of the coastal towns of southern Tasmania
+to be recognised.
 
@@
 protect the borders and ensure centroids are placed within the
-geographic borders of a country.
-
-This algorithm is an effective start to creating hexagon tile maps for
-many geographic units.
+geographic borders of a country. It would be also possible to take a
+logarithmic function in the filter steps for selection of a hexagon grid
+point. A direct angle is currently used, but this may narrowly miss
+appropriate hexagons, a logarithmic function may help to choose a closer
+hexagon to the original centroid location, before increasing the width
+of the angle used to filter the hexagons. This algorithm is an effective
+start to creating hexagon tile maps for many geographic units.
 
 \hypertarget{installation}{%
-\paragraph{Installation}\label{installation}}
+\subsubsection{Installation}\label{installation}}
 
@@
 
+\begin{Schunk}
+\begin{Sinput}
+install.packages("sugarbag")
+\end{Sinput}
+\end{Schunk}
+
 and the development version can be install from the GitHub repository:
 
-Load the library into your R session with:
+\begin{Schunk}
+\begin{Sinput}
+devtools::install_github("srkobakian","sugarbag")
+\end{Sinput}
+\end{Schunk}
 

### 2020-10-21 kobakian-cook.Rmd
Zoom in on Figure 5 d

@@
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = grid, size = 1) +
-  coord_equal() + ggtitle("a")
+  coord_equal()
 
@@
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#55b56c", data = full_grid, size = 0.5) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = grid, size = 1.5) + ggtitle("b")
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = grid, size = 1)
 
@@
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#55b56c", data = grid, size = 0.5) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = f_grid, size = 1.5) + 
-  geom_point(aes(x=longitude, y = latitude), data = f_centroid, fill = "#ede187", shape = 24) + 
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = f_grid, size = 1) + 
+  geom_point(aes(x=longitude, y = latitude), data = f_centroid, fill = "#ede187", shape = 25) + 
 #Hobart
-  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "#e9f2ed", size = 2, shape = 3) + ggtitle("c")
+  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "#e9f2ed", size = 2, shape = 4)
 
@@
 
-```{r filterprocess, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, height = 8}
+```{r filterprocess, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, height = 12}
 full_grid <- full_grid %>% filter(hex_long > bbox$min[1], hex_long < bbox$max[1],
@@
 f2 <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.01) +
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas %>% filter(lat < -40.3), fill = "#D3D3D3", colour = "white", size = 0.01) +
   geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011)), data = fort_allocated, fill = "#353b38", colour = "black", size = 0.01) +
   #Hobart
-  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "#e9f2ed", size = 2, shape = 3) + 
-  geom_point(aes(x=longitude, y = latitude), data = f_centroid, fill = "#ede187", shape = 24) + 
+  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "#e9f2ed", size = 3, shape = 4) + 
+  geom_point(aes(x=longitude, y = latitude), data = f_centroid, fill = "#ede187", shape = 25, size = 2) + 
   theme_void() + coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = f_grid, size = 1) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", fill = "white", data = hex, size = 1.5, shape = 21) + ggtitle("d")
+  # possible choices to select
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = f_grid, size = 1.5) +
+  # selected hexagon
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", fill = "#ede187", data = hex, size = 2.5, shape = 21)
 
-gridExtra::grid.arrange(g1, g2,
-                        f1, f2)
+# gridExtra::grid.arrange(g1, g2,
+#                         f1, f2)
+
+cowplot::plot_grid(g1, g2,
+                   f1, f2, labels = c("a", "b", "c", "d"))
 ```

### 2020-10-27 sa1 Greater Melb.R
Remove UK example

@@ -1,52 +1,0 @@
-
-# create a hexagon map
-library(sugarbag)
-library(sf)
-library(absmapsdata)
-library(ggplot2)
-
-## sa1
-## areas from absmapsdata package
-sa1 <- absmapsdata::sa12011 %>% 
-  filter(state_name_2011 != "Other Territories") %>% 
-  filter(gcc_name_2011 == "Greater Melbourne") %>% 
-  st_transform(., crs = "+proj=longlat +datum=WGS84")
-
-# Create centroids set
-centroids <- create_centroids(sa1, "sa1_7dig_2011")
-
-# choropleth map display
-ggplot(sa1) + 
-  geom_sf(aes(fill = albers_sqkm)) +
-  geom_point(aes(x = longitude, y = latitude), 
-             colour = "grey", size = 0.5, data = centroids) +
-  scale_fill_distiller(type = "seq", palette = "BuGn",
-                       direction = 1, na.value = "light grey") + 
-  theme_void() +
-  coord_sf(crs = "+proj=longlat +datum=WGS84") +
-  theme(legend.position ="left", legend.title = element_text("Area (sqkm)"))
-
-
-# Create hexagon location grid
-grid <- create_grid(centroids = centroids, hex_size = 0.02, buffer_dist = 1)
-
-# Allocate polygon centroids to hexagon grid points
-sa1_melb <- allocate(centroids = centroids,
-                          hex_grid = grid,
-                          sf_id = "sa1_7dig_2011",
-                          hex_size = 0.02, # same size used in create_grid
-                          hex_filter = 10,
-                          focal_points = capital_cities,
-                          width = 30, verbose = TRUE) # same column used in create_centroids
-
-save(hex_allocated, file = "hex_allocated.rda")
-load("hex_allocated.rda")
-
-
-
-
-
-
-ggsave(filename = "figures/aus_sa1.png", plot = sa1_map,
-       device = "png", bg = "transparent", dpi = 300,  width = 10, height = 8)
-

### 2020-10-28 kobakian-cook.Rmd
Changes with Di

@@
 
-The algorithm is named for the *Trigona carbonaria* bee species.
+The algorithm is implemented in the `sugarbag` package for R, this is the common name for the *Trigona carbonaria* bee species.
 Native to northern and eastern Australia this stingless species builds flat layers of hexagonal brood cells, spiralling out from a central point [@PH].
@@
 
-The result of the algorithm is a display that emphasises the densely populated geographic regions surrounding the capital cities in Australia.
-Each capital city forms it's own collection of connected hexagons.
-Figure \ref{fig:hexmap} allows the distributions in the capital cities to be viewed at a deeper scale.
-Sydney is now notable for the considerable amount of red hexagons, not just for the surrounding orange areas around the New South Wales capital visible in the choropleth display in Figure \ref{fig:choro}.
-Brisbane and Perth also draw attention for the many orange hexagons.
+The result of the algorithm on rates of thyroid cancer for females in each of the SA2 areas of Australia is shown in Figure \ref{fig:hexmap}.
+The difference to the choropleth map in Figure \ref{fig:choro} are clear.
+Now the thyroid cancer incidence in the densely populated areas in Sydney, Brisbane and Perth are visible.
 Interestingly there is no clear divide between rural and urban SA2 areas as many rural areas, and the cities of Melbourne, Darwin, Adelaide and Hobart have low rates of thyroid cancer diagnosis for females.
+The hexagon tile map display provides a more accurate representation of the spatial distribution of thyroid cancer incidence across Australia.
 
@@
 
-There are three key steps performed to create the tessellated hexagon tile map shown in Figure \ref{fig:hexmap}.
-First, derive the set of centroids from the polygons provided, then create the grid of hexagons locations.
+There are several key steps needed to create the hexagon tile map as described in the flow chart in Figure \ref{fig:sugarbag_flow}.
+First, derive the set of centroids from the polygons provided, then create the grid of hexagon locations.
 These two processes are defined in the blue left column of the flow chart in Figure \ref{fig:sugarbag_flow}.
@@
 The steps for the allocation process are detailed in the right column of Figure \ref{fig:sugarbag_flow}.
-There are several filter steps to speed the process of selecting an appropriate hexagon to represent each geographic area.
-To make tessellated plots with the hexagon allocations, the point locations are converted to hexagon shapes, with the hexagon size used in the grid.
+There are several filter steps to speed the process of selecting an appropriate hexagon to represent each geographic unit.
+To make tessellated plots with the hexagon allocations, the point locations are converted into hexagon shapes.
 
@@
 
-Only two inputs are necessary to begin using the algorithm in the `sugarbag` package; the shape file, and the id variable.
-The id variable should uniquely identify each geographic unit in the shape file.
+Only two inputs are necessary to begin the algorithm; the shape file, and the id variable. The id variable should uniquely identify each geographic unit in the shape file.
 
 The centroids are derived from the shape file.
-The amount of centroids within the geographic area is used to determine a hexagon size if one is not provided.
-The derived centroids are a necessary input for an appropriate grid to be constructed, each grid point is located a hexagon size distance from the next closest point in all six directions.
+The amount of centroids within the geographic map is used to determine an appropriate hexagon size if one is not provided.
+The derived centroids are a necessary input for an appropriate grid to be constructed.
+Each grid point is located a hexagon size distance from the next closest point in all six directions.
 The grid will initially cover the entire map space, encompassing all the centroid locations and will extend in all directions to the extent of the buffer distance.
 This buffer distance can be helpful to account for densely populated coastal areas, allowing the use of the sea for hexagon locations.
-
-The centroid set derived from the shape file is necessary when creating a grid.
-The hexagon tile map grid requires the creation of the full grid followed by disregarding the points unlikely to be used in the hexagon map.
 
@@
 When allocating representative hexagons, the width parameter can be used to determine the flexibility of positioning.
-Using the relationship with the nearest reference location, a larger width parameter will increase the amount of available hexagon locations nearer to the centroid of the geographic location.
+Using the relationship with the nearest focal point, a larger width parameter will increase the amount of available hexagons nearer to the original centroid of the geographic unit.
 A smaller width will maintain the orientation from the focal point to the centroid when selecting the hexagon location.
-However, this could mean it is placed further from the geographic centroid location.
+However, this could mean it is placed further away.
 
@@
 
-The following code creates the hexagon tile map for all the Statistical Areas at Level 2 in Tasmania.
+## Algorithm steps
+
+The package can be installed from CRAN:
+
+```{r eval=FALSE, echo = TRUE}
+install.packages("sugarbag")
+```
+
+and the development version can be install from the GitHub repository:
+
+```{r eval=FALSE, echo = TRUE}
+devtools::install_github("srkobakian","sugarbag")
+```
+
+The following steps create the hexagon tile map for all the Statistical Areas at Level 2 in Tasmania.
 These steps can be executed by the main function, `create_hexmap`, or can be run separately for more flexibility.
@@
 If a user would like to perform each of the steps of the algorithm themselves, the necessary inputs will change for each function.
-For example, the `allocate` function can be used directly when a user wishes to use a set of centroids, rather than [@sf] polygons.
+For example, the `allocate` function can be used directly when a user wishes to use a set of centroids, rather than polygons.
 
-The polygon set of Statistical Areas at Level 2 (SA2) [@abs2011] of Tasmania in 2011 is accessed from the `absmapsdata` package.
+The polygon set of Tasmania in 2011 is accessed from the `absmapsdata` package.
 A single column of the data set is used to identify the unique areas.
@@
 
-The longitude and latitude centre of the capital cities of Australia are used as focal points to allocate each geographic area around the closest capital city.
-Hobart will be the focal point, as this example uses only the areas in the state of Tasmania.
+The Australian capital cities are used as focal points to allocate each geographic area around the closest capital city.
+Hobart will be the focal point for this example because only the state of Tasmania is being processed.
 
@@
 
-The buffer distance, hexagon size, hexagon amount to filter and width of angle are parameters that will be determined within `create_hexmap` if they are not provided.
+The buffer distance, hexagon size, hexagon amount to filter and width of angle are parameters that will be determined within `create_hexmap()`, if they are not provided.
 They are created as they are needed throughout the following example.
+
+The results from various steps in the process are illustrated in Figure 5.
 
@@
 
-The set of polygons should be provided as an `sf` object, this is a data frame containing a `geometry` column. The `read_shape` function can assist in creating this object for use in `R`.
+The set of polygons should be provided as an `sf` object, this is a data frame containing a `geometry` column. The `read_shape()` function can assist in creating this object for use in `R`.
 
-The centroids can be derived from the set of polygons using the `create_centroids` function:
+The centroids can be derived from an `sf` object using the `create_centroids()` function:
 
@@
 A grid is created to ensure tessellation between the hexagons that represent the geographic units on a hexagon tile map.
-The grid of possible hexagon locations is made using the `create_grid` function.
+The grid of possible hexagon locations is made using the `create_grid()` function.
 It uses the centroids, the hexagon size and the buffer distance.
@@
 A unique hexagon location is created from all intersections of the longitude columns and latitude rows.
-Figure \ref{fig:filterprocess}a) allows for tessellating hexagons after every second latitude row on the grid is shifted right, by half of the hexagon size.
+Figure \ref{fig:filterprocess}a) shows the hexagon grid after every second latitude row on the grid is shifted right, by half of the hexagon size.
 
@@
 
-#### Rolling windows
+#### Filtering the grid
 
@@
 The amount of rows in each latitude group and the amount of columns in each longitude group are used as the width of rolling windows.
-
 The first rolling window step finds the minimum and maximum centroid values within each of the sliding window groups of longitude columns, and the groups of latitude rows.
-
 The second rolling window step finds the average of the rolling minimum and maximum centroid values, for the longitude columns and latitude rows.
 
-#### Filtering the grid
-
 The hexagon grid points are kept only if they fall within the rolling average of the minimum and maximum centroid values after accounting for the buffer distance, for each row and column of the grid.
+Figure 5b displays remaining hexagon grid points after applying the buffer step.
 The sparsely populated South-West region of National Park has very few points available compared to the South-East region near the city of Hobart.
@@
 The distance and angle from the closest focal point to polygon centroid is used in the allocation process as the order for allocation is determined by the distance between the polygon centroid and it's closest focal point.
+For this example, this distance is only calculated for the capital city of Hobart.
 
@@
   geom_point(aes(x=longitude, y = latitude), data = f_centroid, fill = "#ede187", shape = 25, size = 2) + 
-  theme_void() + coord_equal() +
+ # theme_void() + coord_equal() +
   # possible choices to select
@@
 
-A choropleth map display is the current practice spatial visualisation for geographical data.
-It is possible to enhance the communication of spatial distributions using alternative map displays.
-Current methods for alternative maps do not always work for Australia due to the large rural geographic space between the densely populated capital cities.
+<!-- Summarise paper, usability -->
+A choropleth map display is the current common practice for spatial data visualisation.
+As the choropleth map display relies on the geographic shapes, it does not effectively present the density of the population in small geographic areas.
+The common solution to enhance the communication of spatial distributions is to incorporate the population values as a cartogram or another alternative map display.
+Many alternative map displays do not work well for Australia due to the large rural geographic space between the densely populated capital cities.
 The administrative boundaries may also distract from the statistics communicated using colour due to the small size of some areas.
+This paper provides an algorithm for Australia called the hexagon tile map.
 
+<!-- implementation -->
 Alternative maps highlight the value of the statistics across the geographic units.
@@
 
+This algorithm should  be general enough to apply to other countries and problems
+
 <!-- why hexagon tile map addresses deficiencies -->
 
-The Dorling cartogram was the most influential alternative map display for the design of the hexagon tile map.
+<!-- The Dorling cartogram was the most influential alternative map display for the design of the hexagon tile map.
 The use of a hexagon shifts the focus of the visualisation from the shape of SA2s to the distribution effects of a disease on communities.
@@
 As seen in the Dorling cartogram in figure \ref{fig:tas_displays}c), the tessellation that allows boundary connections was not imposed for rural communities, where centroid of the geographic unit was located far from others, a feature that allows distant but dense populations of the coastal towns of southern Tasmania to be recognised.
+-->
 
-<!-- future -->
+<!-- , limitiations, where it might not work -->
 
@@
 While the buffer allows extension beyond the furthest centroids, there is no mechanism to protect the borders and ensure centroids are placed within the geographic borders of a country.
+
+<!-- future -->
 It would be also possible to take a logarithmic function in the filter steps for selection of a hexagon grid point.
@@
 This algorithm is an effective start to creating hexagon tile maps for many geographic units.
-
-### Installation
-
-The package can be installed from CRAN:
-
-```{r eval=FALSE, echo = TRUE}
-install.packages("sugarbag")
-```
-
-and the development version can be install from the GitHub repository:
-
-```{r eval=FALSE, echo = TRUE}
-devtools::install_github("srkobakian","sugarbag")
-```

### 2020-10-28 kobakian-cook.tex
Changes with Di

@@
 
-The algorithm is named for the \emph{Trigona carbonaria} bee species.
+The algorithm is implemented in the \texttt{sugarbag} package for R,
+this is the common name for the \emph{Trigona carbonaria} bee species.
 Native to northern and eastern Australia this stingless species builds
@@
 
-The result of the algorithm is a display that emphasises the densely
-populated geographic regions surrounding the capital cities in
-Australia. Each capital city forms it's own collection of connected
-hexagons. Figure \ref{fig:hexmap} allows the distributions in the
-capital cities to be viewed at a deeper scale. Sydney is now notable for
-the considerable amount of red hexagons, not just for the surrounding
-orange areas around the New South Wales capital visible in the
-choropleth display in Figure \ref{fig:choro}. Brisbane and Perth also
-draw attention for the many orange hexagons. Interestingly there is no
+The result of the algorithm on rates of thyroid cancer for females in
+each of the SA2 areas of Australia is shown in Figure \ref{fig:hexmap}.
+The difference to the choropleth map in Figure \ref{fig:choro} are
+clear. Now the thyroid cancer incidence in the densely populated areas
+in Sydney, Brisbane and Perth are visible. Interestingly there is no
 clear divide between rural and urban SA2 areas as many rural areas, and
 the cities of Melbourne, Darwin, Adelaide and Hobart have low rates of
-thyroid cancer diagnosis for females.
+thyroid cancer diagnosis for females. The hexagon tile map display
+provides a more accurate representation of the spatial distribution of
+thyroid cancer incidence across Australia.
 
@@
 
-There are three key steps performed to create the tessellated hexagon
-tile map shown in Figure \ref{fig:hexmap}. First, derive the set of
-centroids from the polygons provided, then create the grid of hexagons
-locations. These two processes are defined in the blue left column of
-the flow chart in Figure \ref{fig:sugarbag_flow}. Each centroid can then
-be allocated to an available hexagon location. The steps for the
-allocation process are detailed in the right column of Figure
-\ref{fig:sugarbag_flow}. There are several filter steps to speed the
-process of selecting an appropriate hexagon to represent each geographic
-area. To make tessellated plots with the hexagon allocations, the point
-locations are converted to hexagon shapes, with the hexagon size used in
-the grid.
+There are several key steps needed to create the hexagon tile map as
+described in the flow chart in Figure \ref{fig:sugarbag_flow}. First,
+derive the set of centroids from the polygons provided, then create the
+grid of hexagon locations. These two processes are defined in the blue
+left column of the flow chart in Figure \ref{fig:sugarbag_flow}. Each
+centroid can then be allocated to an available hexagon location. The
+steps for the allocation process are detailed in the right column of
+Figure \ref{fig:sugarbag_flow}. There are several filter steps to speed
+the process of selecting an appropriate hexagon to represent each
+geographic unit. To make tessellated plots with the hexagon allocations,
+the point locations are converted into hexagon shapes.
 
@@
 
-Only two inputs are necessary to begin using the algorithm in the
-\texttt{sugarbag} package; the shape file, and the id variable. The id
-variable should uniquely identify each geographic unit in the shape
-file.
+Only two inputs are necessary to begin the algorithm; the shape file,
+and the id variable. The id variable should uniquely identify each
+geographic unit in the shape file.
 
 The centroids are derived from the shape file. The amount of centroids
-within the geographic area is used to determine a hexagon size if one is
-not provided. The derived centroids are a necessary input for an
-appropriate grid to be constructed, each grid point is located a hexagon
-size distance from the next closest point in all six directions. The
-grid will initially cover the entire map space, encompassing all the
+within the geographic map is used to determine an appropriate hexagon
+size if one is not provided. The derived centroids are a necessary input
+for an appropriate grid to be constructed. Each grid point is located a
+hexagon size distance from the next closest point in all six directions.
+The grid will initially cover the entire map space, encompassing all the
 centroid locations and will extend in all directions to the extent of
@@
 locations.
-
-The centroid set derived from the shape file is necessary when creating
-a grid. The hexagon tile map grid requires the creation of the full grid
-followed by disregarding the points unlikely to be used in the hexagon
-map.
 
@@
 to determine the flexibility of positioning. Using the relationship with
-the nearest reference location, a larger width parameter will increase
-the amount of available hexagon locations nearer to the centroid of the
-geographic location. A smaller width will maintain the orientation from
-the focal point to the centroid when selecting the hexagon location.
-However, this could mean it is placed further from the geographic
-centroid location.
+the nearest focal point, a larger width parameter will increase the
+amount of available hexagons nearer to the original centroid of the
+geographic unit. A smaller width will maintain the orientation from the
+focal point to the centroid when selecting the hexagon location.
+However, this could mean it is placed further away.
 
@@
 
-The following code creates the hexagon tile map for all the Statistical
+\hypertarget{algorithm-steps}{%
+\subsection{Algorithm steps}\label{algorithm-steps}}
+
+The package can be installed from CRAN:
+
+\begin{Schunk}
+\begin{Sinput}
+install.packages("sugarbag")
+\end{Sinput}
+\end{Schunk}
+
+and the development version can be install from the GitHub repository:
+
+\begin{Schunk}
+\begin{Sinput}
+devtools::install_github("srkobakian","sugarbag")
+\end{Sinput}
+\end{Schunk}
+
+The following steps create the hexagon tile map for all the Statistical
 Areas at Level 2 in Tasmania. These steps can be executed by the main
@@
 example, the \texttt{allocate} function can be used directly when a user
-wishes to use a set of centroids, rather than \citep{sf} polygons.
+wishes to use a set of centroids, rather than polygons.
 
-The polygon set of Statistical Areas at Level 2 (SA2) \citep{abs2011} of
-Tasmania in 2011 is accessed from the \texttt{absmapsdata} package. A
-single column of the data set is used to identify the unique areas. In
-this case, the unique SA2 names for each SA2 have been used.
+The polygon set of Tasmania in 2011 is accessed from the
+\texttt{absmapsdata} package. A single column of the data set is used to
+identify the unique areas. In this case, the unique SA2 names for each
+SA2 have been used.
 
-The longitude and latitude centre of the capital cities of Australia are
-used as focal points to allocate each geographic area around the closest
-capital city. Hobart will be the focal point, as this example uses only
-the areas in the state of Tasmania.
+The Australian capital cities are used as focal points to allocate each
+geographic area around the closest capital city. Hobart will be the
+focal point for this example because only the state of Tasmania is being
+processed.
 
@@
 angle are parameters that will be determined within
-\texttt{create\_hexmap} if they are not provided. They are created as
+\texttt{create\_hexmap()}, if they are not provided. They are created as
 they are needed throughout the following example.
+
+The results from various steps in the process are illustrated in Figure
+5.
 
@@
 a data frame containing a \texttt{geometry} column. The
-\texttt{read\_shape} function can assist in creating this object for use
-in \texttt{R}.
+\texttt{read\_shape()} function can assist in creating this object for
+use in \texttt{R}.
 
-The centroids can be derived from the set of polygons using the
-\texttt{create\_centroids} function:
+The centroids can be derived from an \texttt{sf} object using the
+\texttt{create\_centroids()} function:
 
@@
 represent the geographic units on a hexagon tile map. The grid of
-possible hexagon locations is made using the \texttt{create\_grid}
+possible hexagon locations is made using the \texttt{create\_grid()}
 function. It uses the centroids, the hexagon size and the buffer
@@
 hexagon location is created from all intersections of the longitude
-columns and latitude rows. Figure \ref{fig:filterprocess}a) allows for
-tessellating hexagons after every second latitude row on the grid is
-shifted right, by half of the hexagon size.
+columns and latitude rows. Figure \ref{fig:filterprocess}a) shows the
+hexagon grid after every second latitude row on the grid is shifted
+right, by half of the hexagon size.
 
-\hypertarget{rolling-windows}{%
-\paragraph{Rolling windows}\label{rolling-windows}}
+\hypertarget{filtering-the-grid}{%
+\paragraph{Filtering the grid}\label{filtering-the-grid}}
 
@@
 columns in each longitude group are used as the width of rolling
-windows.
-
-The first rolling window step finds the minimum and maximum centroid
-values within each of the sliding window groups of longitude columns,
-and the groups of latitude rows.
-
-The second rolling window step finds the average of the rolling minimum
-and maximum centroid values, for the longitude columns and latitude
-rows.
-
-\hypertarget{filtering-the-grid}{%
-\paragraph{Filtering the grid}\label{filtering-the-grid}}
+windows. The first rolling window step finds the minimum and maximum
+centroid values within each of the sliding window groups of longitude
+columns, and the groups of latitude rows. The second rolling window step
+finds the average of the rolling minimum and maximum centroid values,
+for the longitude columns and latitude rows.
 
@@
 average of the minimum and maximum centroid values after accounting for
-the buffer distance, for each row and column of the grid. The sparsely
-populated South-West region of National Park has very few points
-available compared to the South-East region near the city of Hobart.
+the buffer distance, for each row and column of the grid. Figure 5b
+displays remaining hexagon grid points after applying the buffer step.
+The sparsely populated South-West region of National Park has very few
+points available compared to the South-East region near the city of
+Hobart.
 
@@
 for allocation is determined by the distance between the polygon
-centroid and it's closest focal point.
+centroid and it's closest focal point. For this example, this distance
+is only calculated for the capital city of Hobart.
 
@@
 
-A choropleth map display is the current practice spatial visualisation
-for geographical data. It is possible to enhance the communication of
-spatial distributions using alternative map displays. Current methods
-for alternative maps do not always work for Australia due to the large
-rural geographic space between the densely populated capital cities. The
+A choropleth map display is the current common practice for spatial data
+visualisation. As the choropleth map display relies on the geographic
+shapes, it does not effectively present the density of the population in
+small geographic areas. The common solution to enhance the communication
+of spatial distributions is to incorporate the population values as a
+cartogram or another alternative map display. Many alternative map
+displays do not work well for Australia due to the large rural
+geographic space between the densely populated capital cities. The
 administrative boundaries may also distract from the statistics
-communicated using colour due to the small size of some areas.
+communicated using colour due to the small size of some areas. This
+paper provides an algorithm for Australia called the hexagon tile map.
 
@@
 
-The Dorling cartogram was the most influential alternative map display
-for the design of the hexagon tile map. The use of a hexagon shifts the
-focus of the visualisation from the shape of SA2s to the distribution
-effects of a disease on communities. It is not impeded by the irregular
-and unusual shapes created by a contiguous cartogram and the immense
-white space created on the non-contiguous cartogram. Hexagons can
-emphasise the relationship between neighbouring communities by allowing
-their sides to touch. The tessellation created by adjoining hexagons for
-densely populated areas is helpful as it shows that most communities are
-not islands onto themselves, but are intrinsically connected to those
-around them. As seen in the Dorling cartogram in figure
-\ref{fig:tas_displays}c), the tessellation that allows boundary
-connections was not imposed for rural communities, where centroid of the
-geographic unit was located far from others, a feature that allows
-distant but dense populations of the coastal towns of southern Tasmania
-to be recognised.
+This algorithm should be general enough to apply to other countries and
+problems
 
@@
 protect the borders and ensure centroids are placed within the
-geographic borders of a country. It would be also possible to take a
-logarithmic function in the filter steps for selection of a hexagon grid
-point. A direct angle is currently used, but this may narrowly miss
-appropriate hexagons, a logarithmic function may help to choose a closer
-hexagon to the original centroid location, before increasing the width
-of the angle used to filter the hexagons. This algorithm is an effective
-start to creating hexagon tile maps for many geographic units.
+geographic borders of a country.
 
-\hypertarget{installation}{%
-\subsubsection{Installation}\label{installation}}
-
-The package can be installed from CRAN:
-
-\begin{Schunk}
-\begin{Sinput}
-install.packages("sugarbag")
-\end{Sinput}
-\end{Schunk}
-
-and the development version can be install from the GitHub repository:
-
-\begin{Schunk}
-\begin{Sinput}
-devtools::install_github("srkobakian","sugarbag")
-\end{Sinput}
-\end{Schunk}
+It would be also possible to take a logarithmic function in the filter
+steps for selection of a hexagon grid point. A direct angle is currently
+used, but this may narrowly miss appropriate hexagons, a logarithmic
+function may help to choose a closer hexagon to the original centroid
+location, before increasing the width of the angle used to filter the
+hexagons. This algorithm is an effective start to creating hexagon tile
+maps for many geographic units.
 

### 2020-11-03 kobakian-cook.tex
Colours of centroid location

@@
 \title{A Hexagon Tile Map Algorithm for Displaying Spatial Data}
-\author{by Stephanie Kobakian and Dianne Cook}
+\author{by Stephanie Kobakian, Dianne Cook, and Earl Duncan}
 
@@
 
+When the algorithm is applied to the complete set of all Australian
+Statistical Areas at Level 2 it results in the hexagon tile map display
+shown in Figure \ref{fig:hexmap}. This display highlights the density of
+Australian capital cities, as it draws attention to the many communities
+in Sydney, Melbourne and Hobart. This display also highlights the
+disparity in the burden of thyroid cancer for females in the communities
+of these cities. There are several collections of red hexagons in Sydney
+that represent the communities with much higher rates of diagnosis than
+the Australian average. Brisbane also experiences higher than average
+rates of diagnosis, but has more orange than red. The females in the
+cities of Adelaide and Perth show much lower rates of diagnosis.
+
+Compared to the choropleth map display, the low rates in the rural
+Australian communities are no longer dominating the display. While the
+representative hexagons are still visible against the black background,
+the much lower than average rates in the Northern Territory are less
+noticeable.
+
 \begin{Schunk}
@@
 
-A grid is created to ensure tessellation between the hexagons that
-represent the geographic units on a hexagon tile map. The grid of
-possible hexagon locations is made using the \texttt{create\_grid()}
-function. It uses the centroids, the hexagon size and the buffer
-distance.
+A grid is created to allow tessellation of the hexagons that represent
+the geographic units. For a hexagon tile map, the grid of possible
+hexagon locations is made using the \texttt{create\_grid()} function. It
+uses the centroids, the hexagon size and the buffer distance. Figure
+\ref{fig:filterprocess}a) shows the initial locations of grid points
+created for Tasmania.
 
@@
 hexagon location is created from all intersections of the longitude
-columns and latitude rows. Figure \ref{fig:filterprocess}a) shows the
+columns and latitude rows. Figure \ref{fig:filterprocess}a shows the
 hexagon grid after every second latitude row on the grid is shifted
@@
 \texttt{create\_buffer} function. It finds the grid points needed to
-best capture the set of centroids on a hexagon tile map. It also helps
-reduce the amount of time taken, as it decreases the amount of points
-considered for each centroid allocation.
+best capture the set of centroids on a hexagon tile map. Reducing the
+buffer can help to decrease the amount of time taken, as there will be
+less points in the water to consider for each centroid allocation.
 
@@
 average of the minimum and maximum centroid values after accounting for
-the buffer distance, for each row and column of the grid. Figure 5b
-displays remaining hexagon grid points after applying the buffer step.
-The sparsely populated South-West region of National Park has very few
-points available compared to the South-East region near the city of
-Hobart.
+the buffer distance, for each row and column of the grid. Figure
+\ref{fig:filterprocess}b displays remaining hexagon grid points after
+applying the buffer filter. The sparsely populated South-West region of
+National Park has fewer points available in the water compared to the
+South-East region near the city of Hobart.
 
@@
 The distance is calculated between each centroid in the set, and each of
-the focal points provided. The distance and angle from the closest focal
-point to polygon centroid is used in the allocation process as the order
-for allocation is determined by the distance between the polygon
-centroid and it's closest focal point. For this example, this distance
-is only calculated for the capital city of Hobart.
+the focal points provided. The order for allocation is determined by the
+distance between the polygon centroid and it's closest focal point. For
+this example, this distance is only calculated for the capital city of
+Hobart, represented in Figure \ref{fig:filterprocess}c and d as a white
+cross.
 
@@
 
-Allocation of all centroids takes place using the set of polygon
-centroids and the hexagon map grid. The points are arranged from the
-centroid closest to the focal point(s), to the furthest. Centroid
-allocation begins with the closest centroid to a focal point. This will
+Allocation of all centroids requires the set of polygon centroids and
+the hexagon map grid. The polygon centroids are ordered from the
+centroid closest to the focal point(s), to the furthest. This will
 preserve spatial relationships with the focal point, as the inner city
-areas are allocated first, they will be placed closest to the capital,
-and the areas that are further will then be accommodated. The set of
-possible hexagon grid points reduces by one after each centroid is
-allocated, then only the grid points that have not yet been selected are
-considered.
-
-The possible hexagon locations to consider for a centroid are determined
-by the \texttt{hex\_filter}. This is the maximum amount of hexagons
-between the centroid and the furthest considered hexagon. It is used to
-subset possible grid points to only those surrounding the polygon
-centroid within an appropriate range. A smaller distance will increase
-speed, but can decrease accuracy when width of the angle increases.
-
-The following example considers the first of the Statistical Areas at
-Level 2. Within the algorithm, these steps are repeated for each
-polygon.
+areas are allocated first and placed closest to the capital, the areas
+that are further will then be accommodated. The following example
+considers the first of the Statistical Areas at Level 2. Within the
+algorithm, these steps are repeated for each polygon.
 
@@
 
-Keeping only the available hexagon points prevents multiple geographic
-units from being allocated to the same hexagon.
+The set of possible hexagon grid points reduces by one after each
+centroid is allocated, then only the grid points that have not yet been
+selected are considered. Keeping only the available hexagon points
+prevents multiple geographic units from being allocated to the same
+hexagon. This is demonstrated in Figure \ref{fig:filterprocess}c and d
+by the black hexagons that represent the seven closest polygons to the
+capital city of Hobart. As the allocation process begins for the eighth
+closest centroid there are seven unavailable hexagon locations.
 
@@
 
-A box of possible hexagon locations around the centroid allows only the
-closest points that are not yet assigned to be considered. The corners
-of the box may not appear square if the buffer step has already removed
-unnecessary points from over the ocean.
+A selection of possible hexagon locations around the centroid allows
+only the closest points that are not yet assigned to be considered. The
+number of possible hexagon locations to consider for a centroid is
+determined by the \texttt{hex\_filter}. This is the maximum amount of
+hexagons between the centroid and the furthest considered hexagon. It is
+used to subset possible grid points to only those surrounding the
+polygon centroid within an appropriate range. A smaller distance will
+increase speed, but can decrease accuracy when width of the angle
+increases.
 
@@
 from the closest capital city, to the current centroid as seen in Figure
-\ref{fig:filterprocess} . This allows the spatial relationship to be
+\ref{fig:filterprocess}c.~This allows the spatial relationship to be
 preserved, even when it is allocated to a hexagon that is further from
@@
 distance is reached will the angle expand to accommodate more possible
-grid points.\\
-By default the angle filter to hexagon grid points that fall within the
-bounds of the angle from the focal point to the geographic centroid,
-plus and minus 30 degrees. This will increase if no points can be found
-within the \texttt{hex\_filter} distance. The default angle of 30 was
-chosen to allow the algorithm to choose hexagons that best maintained
+grid points. By default the angle filter for the hexagon grid points
+create plus and minus 30 degrees bounds of the angle from the focal
+point to the geographic centroid. This will increase if no points can be
+found within the \texttt{hex\_filter} distance. The default angle of 30
+was chosen to allow the algorithm to find hexagons that best maintained
 the spatial relationship between the focal point and geographic
 centroid.
-
-A complete hexagon tile map of Tasmania is created by applying the
-algorithm steps to each centroid. The hexagon tile map is used to
-visualise the Australian Cancer Atlas data \citep{TACA}. Two views of
-the same data are produced by filling according to the thyroid Cancer
-Standardised Incidence Rates (SIRs) downloaded from the Australian
-Cancer Atlas site. This small example in Figure \ref{fig:filterprocess}
-shows the group of blue areas in the Hobart CBD more prominently in the
-hexagon tile map (b). The small red areas visible in the choropleth map
-(a) along the north coast are much larger in the hexagon tile maps. The
-hexagon tile map shows less yellow, this no longer overwhelms the map
-space with the information regarding the rural areas.
-
-When the algorithm is applied to the complete set of all Australian
-Statistical Areas at Level 2 it results in the hexagon tile map display
-shown in Figure \ref{fig:hexmap}. This display highlights the density of
-Australian capital cities, as it draws attention to the many communities
-in Sydney, Melbourne and Hobart. This display also highlights the
-disparity in the burden of thyroid cancer for females in the communities
-of these cities. There are several collections of red hexagons in Sydney
-that represent the communities with much higher rates of diagnosis than
-the Australian average. Brisbane also experiences higher than average
-rates of diagnosis, but has more orange than red, which represents much
-higher rates. The females in the cities of Adelaide and Perth show much
-lower rates of diagnosis.
-
-Compared to the choropleth map display, the low rates in the rural
-Australian communities are no longer dominating the display. While the
-representative hexagons are still visible against the black background,
-the much lower than average rates in the Northern Territory are less
-noticeable.
 
@@
 }
+
+\address{%
+Earl Duncan\\
+Queensland University of Technology\\%
+School of Mathematical Sciences\\
+%
+%
+%
+\\\href{mailto:earl.duncan@qut.edu.au}{\nolinkurl{earl.duncan@qut.edu.au}}
+}

### 2020-11-03 kobakian-cook.Rmd
Colours of centroid location

@@
     email:  dicook@monash.edu 
+  - name: Earl Duncan
+    affiliation: Queensland University of Technology
+    address:
+    - School of Mathematical Sciences
+    email:  earl.duncan@qut.edu.au
 abstract: >
@@
 # Projected data 
-sa2thyroid_ERP <- st_transform(sa2thyroid_ERP, 3112) %>% filter(state_name_2011 == "Tasmania")
+sa2thyroid_ERP <- st_transform(sa2thyroid_ERP, 3112) %>% 
+  filter(state_name_2011 == "Tasmania")
 sa2thyroid_ERP <- sa2thyroid_ERP %>% 
@@
 The hexagon tile map display provides a more accurate representation of the spatial distribution of thyroid cancer incidence across Australia.
+
+When the algorithm is applied to the complete set of all Australian Statistical Areas at Level 2 it results in the hexagon tile map display shown in Figure \ref{fig:hexmap}.
+This display highlights the density of Australian capital cities, as it draws attention to the many communities in Sydney, Melbourne and Hobart.
+This display also highlights the disparity in the burden of thyroid cancer for females in the communities of these cities.
+There are several collections of red hexagons in Sydney that represent the communities with much higher rates of diagnosis than the Australian average.
+Brisbane also experiences higher than average rates of diagnosis, but has more orange than red.
+The females in the cities of Adelaide and Perth  show much lower rates of diagnosis.
+
+Compared to the choropleth map display, the low rates in the rural Australian communities are no longer dominating the display.
+While the representative hexagons are still visible against the black background, the much lower than average rates in the Northern Territory are less noticeable.
 
@@
 tas_centroids <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.01) + 
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.1) + 
   geom_point(aes(x=longitude, y = latitude), size = 2, shape = 19, colour = "white",
@@
 tas_hexmap <- ggplot() +
-  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.01) + 
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.1) + 
   geom_polygon(aes(x = long, y = lat, group = hex_id, fill = SIR),
@@
 
-A grid is created to ensure tessellation between the hexagons that represent the geographic units on a hexagon tile map.
-The grid of possible hexagon locations is made using the `create_grid()` function.
+A grid is created to allow tessellation of the hexagons that represent the geographic units.
+For a hexagon tile map, the grid of possible hexagon locations is made using the `create_grid()` function.
 It uses the centroids, the hexagon size and the buffer distance.
+Figure \ref{fig:filterprocess}a) shows the initial locations of grid points created for Tasmania.
 
@@
 A unique hexagon location is created from all intersections of the longitude columns and latitude rows.
-Figure \ref{fig:filterprocess}a) shows the hexagon grid after every second latitude row on the grid is shifted right, by half of the hexagon size.
+Figure \ref{fig:filterprocess}a shows the hexagon grid after every second latitude row on the grid is shifted right, by half of the hexagon size.
 
@@
 It finds the grid points needed to best capture the set of centroids on a hexagon tile map.
-It also helps reduce the amount of time taken, as it decreases the amount of points considered for each centroid allocation.
+Reducing the buffer can help to decrease the amount of time taken, as there will be less points in the water to consider for each centroid allocation.
 
@@
 The hexagon grid points are kept only if they fall within the rolling average of the minimum and maximum centroid values after accounting for the buffer distance, for each row and column of the grid.
-Figure 5b displays remaining hexagon grid points after applying the buffer step.
-The sparsely populated South-West region of National Park has very few points available compared to the South-East region near the city of Hobart.
+Figure \ref{fig:filterprocess}b displays remaining hexagon grid points after applying the buffer filter.
+The sparsely populated South-West region of National Park has fewer points available in the water compared to the South-East region near the city of Hobart.
 
@@
 g1 <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.01) + 
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.1) + 
    theme_void() + 
@@
 g2 <- ggplot() + 
-   geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.01) +  
+   geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.1) +  
   theme_void() + coord_equal() +
@@
 The distance is calculated between each centroid in the set, and each of the focal points provided.
-The distance and angle from the closest focal point to polygon centroid is used in the allocation process as the order for allocation is determined by the distance between the polygon centroid and it's closest focal point.
-For this example, this distance is only calculated for the capital city of Hobart.
+The order for allocation is determined by the distance between the polygon centroid and it's closest focal point.
+For this example, this distance is only calculated for the capital city of Hobart, represented in Figure \ref{fig:filterprocess}c and d as a white cross.
 
@@
 
-Allocation of all centroids takes place using the set of polygon centroids and the hexagon map grid.
-The points are arranged from the centroid closest to the focal point(s), to the furthest.
-Centroid allocation begins with the closest centroid to a focal point.
-This will preserve spatial relationships with the focal point, as the inner city areas are allocated first, they will be placed closest to the capital, and the areas that are further will then be accommodated.
-The set of possible hexagon grid points reduces by one after each centroid is allocated, then only the grid points that have not yet been selected are considered.
-
-The possible hexagon locations to consider for a centroid are determined by the `hex_filter`.
-This is the maximum amount of hexagons between the centroid and the furthest considered hexagon.
-It is used to subset possible grid points to only those surrounding the polygon centroid within an appropriate range.
-A smaller distance will increase speed, but can decrease accuracy when width of the angle increases.
+Allocation of all centroids requires the set of polygon centroids and the hexagon map grid.
+The polygon centroids are ordered from the centroid closest to the focal point(s), to the furthest.
+This will preserve spatial relationships with the focal point, as the inner city areas are allocated first and placed closest to the capital, the areas that are further will then be accommodated.
+The following example considers the first of the Statistical Areas at Level 2.
+Within the algorithm, these steps are repeated for each polygon.
 
@@
 
-The following example considers the first of the Statistical Areas at Level 2. Within the algorithm, these steps are repeated for each polygon.
-
 #### Filter the grid for unassigned hexagon points
 
+The set of possible hexagon grid points reduces by one after each centroid is allocated, then only the grid points that have not yet been selected are considered.
 Keeping only the available hexagon points prevents multiple geographic units from being allocated to the same hexagon.
+This is demonstrated in Figure \ref{fig:filterprocess}c and d by the black hexagons that represent the seven closest polygons to the capital city of Hobart.
+As the allocation process begins for the eighth closest centroid there are seven unavailable hexagon locations.
 
@@
 
-A box of possible hexagon locations around the centroid allows only the closest points that are not yet assigned to be considered.
-The corners of the box may not appear square if the buffer step has already removed unnecessary points from over the ocean.
+A selection of possible hexagon locations around the centroid allows only the closest points that are not yet assigned to be considered.
+The number of possible hexagon locations to consider for a centroid is determined by the `hex_filter`.
+This is the maximum amount of hexagons between the centroid and the furthest considered hexagon.
+It is used to subset possible grid points to only those surrounding the polygon centroid within an appropriate range.
+A smaller distance will increase speed, but can decrease accuracy when width of the angle increases.
 
@@
       pull(pangle)
+
 f_grid <- f_grid %>%
@@
 
-f1 <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.01) +
-  theme_void() + coord_equal() +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#55b56c", data = grid, size = 0.5) +
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = f_grid, size = 1) + 
-  geom_point(aes(x=longitude, y = latitude), data = f_centroid, fill = "#ede187", shape = 25) + 
-#Hobart
-  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "#e9f2ed", size = 2, shape = 4)
+allocated_list <- aus_hexmap %>% 
+                  filter(points == "Hobart") %>% 
+                  slice_min(rownumber, n = 7)
 
-```
+fort_allocated <- allocated_list %>% 
+  fortify_hexagon(., sf_id = "sa2_name_2011", hex_size = 0.2)
 
-The `width` parameter is used to take a slice of the remaining points.
-The width is the amount of degrees used on either side of the angle from the focal point to centroid location.
-This uses the angle from the closest capital city, to the current centroid as seen in Figure \ref{fig:filterprocess} .
-This allows the spatial relationship to be preserved, even when it is allocated to a hexagon that is further from the focal point then the original centroid location.
-
-```{r filterprocess, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", echo = FALSE, height = 12}
 full_grid <- full_grid %>% filter(hex_long > bbox$min[1], hex_long < bbox$max[1],
@@
 
+f1 <- ggplot() + 
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.1) +
+  theme_void() + coord_equal(ylim = c(-44, -40.1), xlim = c(144.5, 149)) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#55b56c", data = grid, size = 0.5) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = f_grid, size = 1) +
+  # allocated areas
+    geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011)), data = fort_allocated, fill = "#353b38", colour = "black", size = 0.01, alpha = 0.7) +
+  #Hobart
+  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "#e9f2ed", size = 4, shape = 3) + 
+  geom_point(aes(x=longitude, y = latitude), data = f_centroid, fill = "#beaed4", shape = 25)
+
+```
+
+The `width` parameter is used to take a slice of the remaining points.
+The width is the amount of degrees used on either side of the angle from the focal point to centroid location.
+This uses the angle from the closest capital city, to the current centroid as seen in Figure \ref{fig:filterprocess}c.
+This allows the spatial relationship to be preserved, even when it is allocated to a hexagon that is further from the focal point then the original centroid location.
+
+```{r filterprocess, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", dpi = 600, echo = FALSE, height = 12}
+
 hex <- f_grid %>%
@@
 f2 <- ggplot() + 
-  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas %>% filter(lat < -40.3), fill = "#D3D3D3", colour = "white", size = 0.01) +
-  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011)), data = fort_allocated, fill = "#353b38", colour = "black", size = 0.01) +
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas %>% filter(lat < -40.3), fill = "#D3D3D3", colour = "white", size = 0.1) +
+  geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011)), data = fort_allocated, fill = "#353b38", colour = "black", size = 0.01, alpha = 0.7) +
   #Hobart
-  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "#e9f2ed", size = 3, shape = 4) + 
-  geom_point(aes(x=longitude, y = latitude), data = f_centroid, fill = "#ede187", shape = 25, size = 2) + 
- # theme_void() + coord_equal() +
+  geom_point(aes(x = focal_longitude, y = focal_latitude), data = f_centroid, colour = "#e9f2ed", size = 4, shape = 3) + 
+  geom_point(aes(x=longitude, y = latitude), data = f_centroid, fill = "#beaed4", shape = 25, size = 2) + 
+  theme_void() + coord_equal(xlim = c(146.9, 147.8), ylim = c(-43.35, -42.5)) +
   # possible choices to select
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = f_grid, size = 1.5) +
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", data = f_grid, size = 2.5) +
   # selected hexagon
-  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", fill = "#ede187", data = hex, size = 2.5, shape = 21)
+  geom_point(aes(x = hex_long, y = hex_lat), colour = "#09661f", fill = "#beaed4", data = hex, size = 3.5, shape = 21)
 
@@
 
-If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded, only when a maximum distance is reached will the angle expand to accommodate more possible grid points.\
-By default the angle filter to hexagon grid points that fall within the bounds of the angle from the focal point to the geographic centroid, plus and minus 30 degrees.
+If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded, only when a maximum distance is reached will the angle expand to accommodate more possible grid points.
+By default the angle filter for the hexagon grid points create plus and minus 30 degrees bounds of the angle from the focal point to the geographic centroid.
 This will increase if no points can be found within the `hex_filter` distance.
-The default angle of 30 was chosen to allow the algorithm to choose hexagons that best maintained the spatial relationship between the focal point and geographic centroid.
+The default angle of 30 was chosen to allow the algorithm to find hexagons that best maintained the spatial relationship between the focal point and geographic centroid.
 
-A complete hexagon tile map of Tasmania is created by applying the algorithm steps to each centroid.
+<!-- Tasmania example has been removed -->
+<!-- A complete hexagon tile map of Australia is created by applying the algorithm steps to each centroid.
 The hexagon tile map is used to visualise the Australian Cancer Atlas data [@TACA].
 Two views of the same data are produced by filling according to the thyroid Cancer Standardised Incidence Rates (SIRs) downloaded from the Australian Cancer Atlas site.
-This small example in Figure \ref{fig:filterprocess} shows the group of blue areas in the Hobart CBD more prominently in the hexagon tile map (b).
+This small example in Figure \ref{fig:hexmap} shows the group of blue areas in the Hobart CBD more prominently in the hexagon tile map.
 The small red areas visible in the choropleth map (a) along the north coast are much larger in the hexagon tile maps.
 The hexagon tile map shows less yellow, this no longer overwhelms the map space with the information regarding the rural areas.
-
-When the algorithm is applied to the complete set of all Australian Statistical Areas at Level 2 it results in the hexagon tile map display shown in Figure \ref{fig:hexmap}.
-This display highlights the density of Australian capital cities, as it draws attention to the many communities in Sydney, Melbourne and Hobart.
-This display also highlights the disparity in the burden of thyroid cancer for females in the communities of these cities.
-There are several collections of red hexagons in Sydney that represent the communities with much higher rates of diagnosis than the Australian average.
-Brisbane also experiences higher than average rates of diagnosis, but has more orange than red, which represents much higher rates.
-The females in the cities of Adelaide and Perth  show much lower rates of diagnosis.
-
-Compared to the choropleth map display, the low rates in the rural Australian communities are no longer dominating the display.
-While the representative hexagons are still visible against the black background, the much lower than average rates in the Northern Territory are less noticeable.
+-->
 

### 2020-11-13 kobakian-cook.Rmd
small changes to conclusion

@@
 
-<!-- Summarise paper, usability -->
+This paper has described a new algorithm for creating an alternative display. 
+This paper provides an algorithm for Australia called the hexagon tile map.
+
+<!-- Summarise paper, usability, sound like a summary, not introduction -->
 A choropleth map display is the current common practice for spatial data visualisation.
@@
 The administrative boundaries may also distract from the statistics communicated using colour due to the small size of some areas.
-This paper provides an algorithm for Australia called the hexagon tile map.
 
@@
 
-This algorithm should  be general enough to apply to other countries and problems
-
 <!-- why hexagon tile map addresses deficiencies -->
@@
 
-<!-- , limitiations, where it might not work -->
+<!-- limitiations, where it might not work -->
 
+This algorithm should  be general enough to apply to other countries and problems.
+XXX 
 This algorithm has only been tested using single countries, and does not consider definite borders of countries.

### 2020-11-13 kobakian-cook.Rmd
capitalisation of Figure

--- 2020-11-03 kobakian-cook.Rmd
@@
 This presents an opportunity for explicit map transformations to improve communication of distributions [@CBATCC].
-In figure \ref{fig:tas_displays} the choropleth map can be seen underneath each alternative map display to allow for comparisons to be made.
+In Figure \ref{fig:tas_displays} the choropleth map can be seen underneath each alternative map display to allow for comparisons to be made.
 
@@
 The impact of a disease over connected communities can be seen by allowing the boundaries to maintain connection in the transformed display.
-The contiguous cartogram displayed in figure \ref{fig:tas_displays}a) draws attention to smaller geographic units when they are rescaled according to the population [@DMAHP].
+The contiguous cartogram displayed in Figure \ref{fig:tas_displays}a) draws attention to smaller geographic units when they are rescaled according to the population [@DMAHP].
 These new shapes can now be coloured to represent a second variable.
@@
 
-The non-contiguous cartogram in figure \ref{fig:tas_displays}b) also uses the population to rescale the geographic units.
+The non-contiguous cartogram in Figure \ref{fig:tas_displays}b) also uses the population to rescale the geographic units.
 Unlike the contiguous cartogram, the SA2 areas maintain their geographic shape, but they may not retain the connection with their neighbours.
@@
 Figure \ref{fig:tas_displays}c) shows the Tasmania SA2 areas as an individual circle located as close as possible to the geographic centroid location.
-This map draws attention to the collection of coastal cities in Tasmania that were not apparent in figure \ref{fig:tas_displays} a), or b).
+This map draws attention to the collection of coastal cities in Tasmania that were not apparent in Figure \ref{fig:tas_displays} a), or b).
 This display also highlights that the approximation of equal population is not easy to fulfil, as there is some disparity in the sizes of the circles.

### 2020-11-13 kobakian-cook.tex
capitalisation of Figure

@@
 for explicit map transformations to improve communication of
-distributions \citep{CBATCC}. In figure \ref{fig:tas_displays} the
+distributions \citep{CBATCC}. In Figure \ref{fig:tas_displays} the
 choropleth map can be seen underneath each alternative map display to
@@
 connection in the transformed display. The contiguous cartogram
-displayed in figure \ref{fig:tas_displays}a) draws attention to smaller
+displayed in Figure \ref{fig:tas_displays}a) draws attention to smaller
 geographic units when they are rescaled according to the population
@@
 
-The non-contiguous cartogram in figure \ref{fig:tas_displays}b) also
+The non-contiguous cartogram in Figure \ref{fig:tas_displays}b) also
 uses the population to rescale the geographic units. Unlike the
@@
 geographic centroid location. This map draws attention to the collection
-of coastal cities in Tasmania that were not apparent in figure
+of coastal cities in Tasmania that were not apparent in Figure
 \ref{fig:tas_displays} a), or b). This display also highlights that the

### 2020-11-13 kobakian-cook.Rmd
figure captions

@@
 
-```{r choro, fig.cap = "A choropleth map of the Statistical Areas of Australia at Level 2.
-The colours communicate the value of the estimated SIR of Thyroid cancer for females, ranging from much lower than average (blue) to much higher than average (red)"}
+```{r choro, fig.cap = "A choropleth map of thyroid incidence among females across the Statistical Areas of Australia at Level 2.
+Blue indicates lower than average and red indicates higher than average incidence.
+A cluster of high incidence is visible on the east coast."}
 aus_ggchoro <- ggplot(sa2thyroid_ERP) + 
@@
 
-```{r fullhexmap, fig.cap = "A hexagon tile map of the Statistical Areas of Australia at Level 2.
+```{r fullhexmap, fig.cap = "A hexagon tile map of Australia at SA2 level.
 The colours communicate the value of the estimated SIR of thyroid cancer for females, ranging from much lower than average (blue) to much higher than average (red)"}
@@
 
-```{r tas_displays, width = 10, height = 3, fig.cap = "The three displays show alternative maps of the Statistical Areas at Level 2 in the Australian state of Tasmania.
-These alternatives show the (a) contiguous cartogram, (b) non-contiguous cartogram and (c) Dorling cartogram of Tasmania."}
+```{r tas_displays, width = 10, height = 3, fig.cap = "The three displays show alternative maps of the Australian state of Tasmania at SA2 level: (a) contiguous cartogram, (b) non-contiguous cartogram and (c) Dorling cartogram of Tasmania.
+The contiguous cartogram looks like the state has an hourglass figure, while the non-contiguous cartogram shrinks areas into invisibility.
+The Dorling expands the metropolitan regions."}
 library(gridExtra)
@@
 
-```{r hexmap, fig.cap = "A hexagon tile map of the Statistical Areas of Australia at Level 2.
-The colours communicate the value of the estimated SIR of thyroid for females, they range from much lower than average (blue) to much higher than average (red)."}
+```{r hexmap, fig.cap = "A hexagon tile map of female tyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1.
+The high incidence in several of the metropolitan regions (Brisbane, Sydney and Perth) can now be seen, along with numerous isolated spots."}
 aus_hexmap_plot
@@
 \includegraphics[width=14cm]{figs/sugarbag flow.png}
-\caption{\label{fig:sugarbag_flow}A flow diagram detailing the necessary steps to create a hexagon tile map.}
+\caption{\label{fig:sugarbag_flow}A flow diagram detailing the steps taken to create a hexagon tile map.
+There are two basic processes, one to make the grid, and the other to allocate centroids to grid points.}
 \end{figure}
@@
 
-```{r filterprocess, fig.cap = "Filter for grid points within a square, then circular, distance for those closest to the centroid.", dpi = 600, echo = FALSE, height = 12}
+```{r filterprocess, fig.cap = "Illustration of several steps of the algorithm: (a) ... (b) ... (c) ... (d). ", dpi = 600, echo = FALSE, height = 12}
 

### 2020-11-13 kobakian-cook.tex
figure captions

@@
 \begin{figure}
-\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/choro-1} \caption[A choropleth map of the Statistical Areas of Australia at Level 2]{A choropleth map of the Statistical Areas of Australia at Level 2.
-The colours communicate the value of the estimated SIR of Thyroid cancer for females, ranging from much lower than average (blue) to much higher than average (red)}\label{fig:choro}
+\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/choro-1} \caption[A choropleth map of thyroid incidence among females across the Statistical Areas of Australia at Level 2]{A choropleth map of thyroid incidence among females across the Statistical Areas of Australia at Level 2.
+Blue indicates lower than average and red indicates higher than average incidence.
+A cluster of high incidence is visible on the east coast.}\label{fig:choro}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/tas_displays-1} \caption[The three displays show alternative maps of the Statistical Areas at Level 2 in the Australian state of Tasmania]{The three displays show alternative maps of the Statistical Areas at Level 2 in the Australian state of Tasmania.
-These alternatives show the (a) contiguous cartogram, (b) non-contiguous cartogram and (c) Dorling cartogram of Tasmania.}\label{fig:tas_displays}
+\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/tas_displays-1} \caption[The three displays show alternative maps of the Australian state of Tasmania at SA2 level]{The three displays show alternative maps of the Australian state of Tasmania at SA2 level: (a) contiguous cartogram, (b) non-contiguous cartogram and (c) Dorling cartogram of Tasmania.
+The contiguous cartogram looks like the state has an hourglass figure, while the non-contiguous cartogram shrinks areas into invisibility.
+The Dorling expands the metropolitan regions.}\label{fig:tas_displays}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/hexmap-1} \caption[A hexagon tile map of the Statistical Areas of Australia at Level 2]{A hexagon tile map of the Statistical Areas of Australia at Level 2.
-The colours communicate the value of the estimated SIR of thyroid for females, they range from much lower than average (blue) to much higher than average (red).}\label{fig:hexmap}
+\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/hexmap-1} \caption[A hexagon tile map of female tyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1]{A hexagon tile map of female tyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1.
+The high incidence in several of the metropolitan regions (Brisbane, Sydney and Perth) can now be seen, along with numerous isolated spots.}\label{fig:hexmap}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/filterprocess-1} \caption[Filter for grid points within a square, then circular, distance for those closest to the centroid]{Filter for grid points within a square, then circular, distance for those closest to the centroid.}\label{fig:filterprocess}
+\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/filterprocess-1} \caption[Illustration of several steps of the algorithm]{Illustration of several steps of the algorithm: (a) ...
+(b) ...
+(c) ...
+(d).
+}\label{fig:filterprocess}
 \end{figure}
@@
 
+This paper has described a new algorithm for creating an alternative
+display. This paper provides an algorithm for Australia called the
+hexagon tile map.
+
 A choropleth map display is the current common practice for spatial data
@@
 administrative boundaries may also distract from the statistics
-communicated using colour due to the small size of some areas. This
-paper provides an algorithm for Australia called the hexagon tile map.
+communicated using colour due to the small size of some areas.
 
@@
 This algorithm should be general enough to apply to other countries and
-problems
-
-This algorithm has only been tested using single countries, and does not
-consider definite borders of countries. While the buffer allows
-extension beyond the furthest centroids, there is no mechanism to
-protect the borders and ensure centroids are placed within the
-geographic borders of a country.
+problems. XXX This algorithm has only been tested using single
+countries, and does not consider definite borders of countries. While
+the buffer allows extension beyond the furthest centroids, there is no
+mechanism to protect the borders and ensure centroids are placed within
+the geographic borders of a country.
 

### 2020-11-18 kobakian-cook.Rmd
Earl's comments up to Algorithm section

--- 2020-11-13 kobakian-cook.Rmd
@@
 abstract: >
+  Spatial distributions have been presented on alternative representations of geography for many years.
+In modern times, interactivity and animation have allowed alternative displays to play a larger role.
+Alternative representations have been popularised by online news sites, and digital atlases with a focus on public consumption.
+Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
 The algorithm presented creates a display that uses tessellated hexagons to represent a set of spatial polygons.
@@
 The display showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps.
-Spatial distributions have been presented on alternative representations of geography for many years.
-In modern times, interactivity and animation have allowed alternative displays to play a larger role.
-Alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption.
-Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
 preamble: |
@@
 
-Over time the density of living in major cities has increased as residents have gathered to live near urban areas [@ACTUC].
-The division of these resident into approximately equal population areas results in dramatically different square meterage of administrative geographic units, such as states or electorates.
-In a choropleth map display the geographic units are filled with colour to represent the value of the statistic for each unit [@EI].
-This can allow unequal emphasis on the statistical value of each of the geographic units.
-This allows choropleth map displays to misrepresent the spatial distributions of human related statistics due to area-size bias [@BCM].
-Figure \ref{fig:choro} is a choropleth map that uses colour to display the estimated Standardised Incidence Ratios (SIRs) of thyroid cancer for females, in each of the Statistical Areas at Level 2 (SA2) used by the @abs2011.
+Over time, the density of living in major cities has increased as residents have gathered to live near urban areas [@ACTUC].
+The division of these residents into approximately equal population areas results in dramatically different square meterage of administrative geographic units, such as states or electorates.
+In a choropleth map display, the geographic units are coloured to represent the value of the statistic for each unit [@EI].
+This can cause some values to be emphasised over others, and allows choropleth map displays to misrepresent the spatial distributions of human related statistics due to area-size bias [@BCM].
+Figure \ref{fig:choro} is a choropleth map that uses colour to display the estimated standardised incidence ratios (SIRs) of thyroid cancer for females, in each of the Statistical Areas at Level 2 (SA2) used by the @abs2011.
 The Australian choropleth map display draws attention to the expanse of dark and light blue areas across the rural communities in all states.
-The SA2s around Brisbane and in northern New South Wales stand out as more orange and red.
+The SA2s on the east coast around Brisbane and in northern New South Wales stand out as more orange and red.
 However, this display neglects the vast amount of Australia residents living in the densely populated capital cities.
@@
 The solutions to this visualisation problem begin with the geography.
-Alternative maps shift the focus from land area and shape, to the value of the statistics in a collection of areas [@ACCAC].
+Alternative maps can be created to shift the focus from land area and shape to the value of the statistics [@ACCAC].
 Each style of cartogram applies a different transformation to the geographic areas, to highlight the values of the statistic of interest.
-These displays result in a distortion of the map space to represent features of the distribution across the areas [@ACCAC] as the statistic of interest is used to determine the cartogram layout.
+Alternative maps can result in a distortion of the map space to represent features of the distribution across the areas [@ACCAC] as the statistic of interest is used to determine the cartogram layout.
 
 Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing the population in each administrative area [@TAAM].
-This acknowledges that the number of residents can be different but recognises that each area, or person within it is equally important.
+This acknowledges that the number of residents can be different and also recognises that each area, or person within it is equally important.
 
-This paper contains a discussion of Existing Mapping Practices in Section 2.
-This is followed by details of the Algorithm in Section 3.
-Section 4 describes the implementation of the algorithm in the `sugarbag` package.
-Section 5 outlines the use and benefits of animation.
+This paper contains a discussion of Existing Mapping Practices.
+This is followed by details of the Algorithm.
+The implementation section discusses the algorithm in the `sugarbag` package.
+Finally, the use and benefits of animation are presented.
 
@@
 The unique shapes of boundaries can be helpful for orienting users but may not contribute to their understanding of the spatial disease distribution as many of the communities are not visible in a choropleth display [@TVSSS].
-Each Statistical Area at Level 2 (SA2) [@abs2011] was designed to represent a community.
-These administrative areas are often used to aggregate census data and used to understand demographics within communities of the Australian population.
-This presents an opportunity for explicit map transformations to improve communication of distributions [@CBATCC].
-In Figure \ref{fig:tas_displays} the choropleth map can be seen underneath each alternative map display to allow for comparisons to be made.
+
+Administrative areas are often used to aggregate census data and used to understand demographics within communities of the Australian population.
+Each SA2 [@abs2011] was designed to represent a community.
+This collection of communities presents an opportunity for explicit map transformations to improve communication of spatial distributions [@CBATCC].
+In figure \ref{fig:tas_displays} the choropleth map can be seen underneath each alternative map display to allow for comparisons to be made.
 
 There are several established alternative visualisation methods.
-Tile maps, Rectangular cartograms [@ORC] and Dorling cartograms [@ACTUC] all use one simple shape to represent each geographic unit.
+Tile maps, rectangular cartograms [@ORC] and Dorling cartograms [@ACTUC] all use one simple shape to represent each geographic unit.
 They all minimise the emphasis on the size or shape of the geographic areas.
@@
 
-```{r tas_displays, width = 10, height = 3, fig.cap = "The three displays show alternative maps of the Statistical Areas at Level 2 in the Australian state of Tasmania.
+```{r tas_displays, width = 10, height = 3, fig.cap = "The three displays show alternative maps of the Australian state of Tasmania.
 These alternatives show the (a) contiguous cartogram, (b) non-contiguous cartogram and (c) Dorling cartogram of Tasmania."}
@@
 When communicating information that is relevant to the population, each member of the population can be given equal representation by transforming the map [@TVSSS].
-The impact of a disease over connected communities can be seen by allowing the boundaries to maintain connection in the transformed display.
-The contiguous cartogram displayed in Figure \ref{fig:tas_displays}a) draws attention to smaller geographic units when they are rescaled according to the population [@DMAHP].
+The connected communities can be recognised by allowing the boundaries to maintain connection in the transformed display.
+The contiguous cartogram displayed in figure \ref{fig:tas_displays}a) draws attention to smaller geographic units when they are rescaled according to the population [@DMAHP].
 These new shapes can now be coloured to represent a second variable.
@@
 
-The non-contiguous cartogram in Figure \ref{fig:tas_displays}b) also uses the population to rescale the geographic units.
+The non-contiguous cartogram in figure \ref{fig:tas_displays}b) also uses the population to rescale the geographic units.
 Unlike the contiguous cartogram, the SA2 areas maintain their geographic shape, but they may not retain the connection with their neighbours.
 The population of the SA2 areas is used to scale the geographic units in the non-contiguous cartogram [@NAC].
-The amount of white space can be meaningful in non-contiguous cartograms [@ECGC], in this example the disparity between large rural areas and small urban areas means that the city of Hobart may look reasonable but these units are not visible in the context of the Tasmania state map.
+The amount of background space can be meaningful in non-contiguous cartograms [@ECGC].
+The size disparity between rural areas and urban areas result in reasonable display within the south eastern city of Hobart, but these units are not visible in the context of the Tasmania state map.
 Depending on the difference between the population and geographic land size, the amount of white space can also prevent meaningful understanding of the distribution [@TVSSS].
@@
 Figure \ref{fig:tas_displays}c) shows the Tasmania SA2 areas as an individual circle located as close as possible to the geographic centroid location.
-This map draws attention to the collection of coastal cities in Tasmania that were not apparent in Figure \ref{fig:tas_displays} a), or b).
+This map draws attention to the collection of coastal cities in Tasmania that were not apparent in figure \ref{fig:tas_displays} a), or b).
 This display also highlights that the approximation of equal population is not easy to fulfil, as there is some disparity in the sizes of the circles.
@@
 
-The result of the algorithm on rates of thyroid cancer for females in each of the SA2 areas of Australia is shown in Figure \ref{fig:hexmap}.
-The difference to the choropleth map in Figure \ref{fig:choro} are clear.
+The result of the algorithm on rates of thyroid cancer for females in each of the SA2 areas of Australia is shown in figure \ref{fig:hexmap}.
+The difference to the choropleth map in figure \ref{fig:choro} are clear.
 Now the thyroid cancer incidence in the densely populated areas in Sydney, Brisbane and Perth are visible.
@@
 
-When the algorithm is applied to the complete set of all Australian Statistical Areas at Level 2 it results in the hexagon tile map display shown in Figure \ref{fig:hexmap}.
+When the algorithm is applied to the complete set of all Australian Statistical Areas at Level 2 it results in the hexagon tile map display shown in figure \ref{fig:hexmap}.
 This display highlights the density of Australian capital cities, as it draws attention to the many communities in Sydney, Melbourne and Hobart.
@@
 
-There are several key steps needed to create the hexagon tile map as described in the flow chart in Figure \ref{fig:sugarbag_flow}.
+There are several key steps needed to create the hexagon tile map as described in the flow chart in figure \ref{fig:sugarbag_flow}.
 First, derive the set of centroids from the polygons provided, then create the grid of hexagon locations.
-These two processes are defined in the blue left column of the flow chart in Figure \ref{fig:sugarbag_flow}.
+These two processes are defined in the blue left column of the flow chart in figure \ref{fig:sugarbag_flow}.
 Each centroid can then be allocated to an available hexagon location.
-The steps for the allocation process are detailed in the right column of Figure \ref{fig:sugarbag_flow}.
+The steps for the allocation process are detailed in the right column of figure \ref{fig:sugarbag_flow}.
 There are several filter steps to speed the process of selecting an appropriate hexagon to represent each geographic unit.
@@
 The order for allocation is determined by the distance between the polygon centroid and it's closest focal point.
-For this example, this distance is only calculated for the capital city of Hobart, represented in Figure \ref{fig:filterprocess}c and d as a white cross.
+For this example, this distance is only calculated for the capital city of Hobart, represented in figure \ref{fig:filterprocess}c and d as a white cross.
 
@@
 Keeping only the available hexagon points prevents multiple geographic units from being allocated to the same hexagon.
-This is demonstrated in Figure \ref{fig:filterprocess}c and d by the black hexagons that represent the seven closest polygons to the capital city of Hobart.
+This is demonstrated in figure \ref{fig:filterprocess}c and d by the black hexagons that represent the seven closest polygons to the capital city of Hobart.
 As the allocation process begins for the eighth closest centroid there are seven unavailable hexagon locations.
@@
 The width is the amount of degrees used on either side of the angle from the focal point to centroid location.
-This uses the angle from the closest capital city, to the current centroid as seen in Figure \ref{fig:filterprocess}c.
+This uses the angle from the closest capital city, to the current centroid as seen in figure \ref{fig:filterprocess}c.
 This allows the spatial relationship to be preserved, even when it is allocated to a hexagon that is further from the focal point then the original centroid location.
@@
 Two views of the same data are produced by filling according to the thyroid Cancer Standardised Incidence Rates (SIRs) downloaded from the Australian Cancer Atlas site.
-This small example in Figure \ref{fig:hexmap} shows the group of blue areas in the Hobart CBD more prominently in the hexagon tile map.
+This small example in figure \ref{fig:hexmap} shows the group of blue areas in the Hobart CBD more prominently in the hexagon tile map.
 The small red areas visible in the choropleth map (a) along the north coast are much larger in the hexagon tile maps.
@@
 
-<!-- Summarise paper, usability -->
-A choropleth map display is the current common practice for spatial data visualisation.
-As the choropleth map display relies on the geographic shapes, it does not effectively present the density of the population in small geographic areas.
-The common solution to enhance the communication of spatial distributions is to incorporate the population values as a cartogram or another alternative map display.
-Many alternative map displays do not work well for Australia due to the large rural geographic space between the densely populated capital cities.
-The administrative boundaries may also distract from the statistics communicated using colour due to the small size of some areas.
 This paper provides an algorithm for Australia called the hexagon tile map.
+It also describes how this algorithm addresses the potential issues found with contiguous, non-contiguous and Dorling cartograms when applied to Australia.
+It achieves a display that effectively presents the density of the population in small geographic areas and de emphasises the large rural geographic space between the densely populated capital cities.
 
 <!-- implementation -->
-Alternative maps highlight the value of the statistics across the geographic units.
-These methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing each administrative area.
-This acknowledges that the amount of residents can be different but recognises that each population area is equally important.
-The solution to this visualisation problem can be using equally sized areas, with neighbourhood boundary connections.
-The `sugarbag` package for `R` creates tessellated hexagon tile maps by automating an algorithm to design these displays.
-The Australian application preserves the spatial relationships, emphasising capital cities.
-
-These hexagons equally represent each area.
+The hexagon tile map display acknowledges that the amount of residents can differ but each administrative area is equally important.
+This solution uses equally sized areas, and maintain neighbourhood boundary connections.
+The `sugarbag` package for `R` automates the creation of tessellated hexagon tile maps by providing an algorithm to design these displays.
+The Australian application preserves spatial relationships, and emphasises capital cities.
 However, similar to the choropleth map display the tessellation does not allow the size of the hexagons to represent another variable.
 The algorithm is heavily dependent on the focal points used, as this determines the order of allocation.
-It works on the assumption that viewers can identify their neighbourhoods using the relative directional relationships but this can be aided by the use of animation.
 With careful consideration of the choropleth map, the small geographic inner city areas may have been noticed by viewers, but the hexagon tile map display emphasises them.
@@
 
-This algorithm should  be general enough to apply to other countries and problems
+<!-- limitiations, where it might not work -->
 
-<!-- why hexagon tile map addresses deficiencies -->
-
-<!-- The Dorling cartogram was the most influential alternative map display for the design of the hexagon tile map.
-The use of a hexagon shifts the focus of the visualisation from the shape of SA2s to the distribution effects of a disease on communities.
-It is not impeded by the irregular and unusual shapes created by a contiguous cartogram and the immense white space created on the non-contiguous cartogram.
-Hexagons can emphasise the relationship between neighbouring communities by allowing their sides to touch.
-The tessellation created by adjoining hexagons for densely populated areas is helpful as it shows that most communities are not islands onto themselves, but are intrinsically connected to those around them.
-As seen in the Dorling cartogram in figure \ref{fig:tas_displays}c), the tessellation that allows boundary connections was not imposed for rural communities, where centroid of the geographic unit was located far from others, a feature that allows distant but dense populations of the coastal towns of southern Tasmania to be recognised.
--->
-
-<!-- , limitiations, where it might not work -->
-
-This algorithm has only been tested using single countries, and does not consider definite borders of countries.
-While the buffer allows extension beyond the furthest centroids, there is no mechanism to protect the borders and ensure centroids are placed within the geographic borders of a country.
-
-<!-- future -->
-It would be also possible to take a logarithmic function in the filter steps for selection of a hexagon grid point.
-A direct angle is currently used, but this may narrowly miss appropriate hexagons, a logarithmic function may help to choose a closer hexagon to the original centroid location, before increasing the width of the angle used to filter the hexagons.
+This algorithm should be general enough to apply to other countries and related problems.
+The algorithm has only been tested using single countries.
+While the buffer allows extension beyond the furthest centroids, there is no mechanism implemented to protect the borders and ensure centroids are placed within the geographic borders of a country.
+The algorithm is also currently limited to representing each geographic area with only one hexagon.
+Future developments may address these limitations, and refine the filter steps for final selection of a hexagon grid point for each centroid.
+A direct angle is currently implemented, but may narrowly miss appropriate hexagons, a logarithmic function may help to choose a closer hexagon to the original centroid location.
 This algorithm is an effective start to creating hexagon tile maps for many geographic units.
+This contributes to an extensive body of work that encourages the use of alternative map displays for statistical displays of spatial data.

### 2020-11-18 kobakian-cook.tex
Earl's comments up to Algorithm section

--- 2020-11-03 kobakian-cook.tex
@@
 \abstract{%
-The algorithm presented creates a display that uses tessellated hexagons
-to represent a set of spatial polygons. It allocates these hexagon in a
-manner that preserves the spatial relationship of the geographic units,
-in light of their positions to points of interest. The display showcases
-spatial distributions, by emphasising the small geographical regions
-that are often difficult to locate on geographic maps. Spatial
-distributions have been presented on alternative representations of
-geography for many years. In modern times, interactivity and animation
-have allowed alternative displays to play a larger role. Alternative
-representations have been popularised by online news sites, and atlas
-websites with a focus on public consumption. Applications are
+Spatial distributions have been presented on alternative representations
+of geography for many years. In modern times, interactivity and
+animation have allowed alternative displays to play a larger role.
+Alternative representations have been popularised by online news sites,
+and digital atlases with a focus on public consumption. Applications are
 increasingly widespread, especially in the areas of disease mapping, and
-election results.
+election results. The algorithm presented creates a display that uses
+tessellated hexagons to represent a set of spatial polygons. It
+allocates these hexagon in a manner that preserves the spatial
+relationship of the geographic units, in light of their positions to
+points of interest. The display showcases spatial distributions, by
+emphasising the small geographical regions that are often difficult to
+locate on geographic maps.
 }
@@
 
-Over time the density of living in major cities has increased as
+Over time, the density of living in major cities has increased as
 residents have gathered to live near urban areas \citep{ACTUC}. The
-division of these resident into approximately equal population areas
+division of these residents into approximately equal population areas
 results in dramatically different square meterage of administrative
 geographic units, such as states or electorates. In a choropleth map
-display the geographic units are filled with colour to represent the
-value of the statistic for each unit \citep{EI}. This can allow unequal
-emphasis on the statistical value of each of the geographic units. This
-allows choropleth map displays to misrepresent the spatial distributions
-of human related statistics due to area-size bias \citep{BCM}. Figure
-\ref{fig:choro} is a choropleth map that uses colour to display the
-estimated Standardised Incidence Ratios (SIRs) of thyroid cancer for
-females, in each of the Statistical Areas at Level 2 (SA2) used by the
-\citet{abs2011}. The Australian choropleth map display draws attention
-to the expanse of dark and light blue areas across the rural communities
-in all states. The SA2s around Brisbane and in northern New South Wales
-stand out as more orange and red. However, this display neglects the
-vast amount of Australia residents living in the densely populated
-capital cities.
+display, the geographic units are coloured to represent the value of the
+statistic for each unit \citep{EI}. This can cause some values to be
+emphasised over others, and allows choropleth map displays to
+misrepresent the spatial distributions of human related statistics due
+to area-size bias \citep{BCM}. Figure \ref{fig:choro} is a choropleth
+map that uses colour to display the estimated standardised incidence
+ratios (SIRs) of thyroid cancer for females, in each of the Statistical
+Areas at Level 2 (SA2) used by the \citet{abs2011}. The Australian
+choropleth map display draws attention to the expanse of dark and light
+blue areas across the rural communities in all states. The SA2s on the
+east coast around Brisbane and in northern New South Wales stand out as
+more orange and red. However, this display neglects the vast amount of
+Australia residents living in the densely populated capital cities.
 
@@
 The solutions to this visualisation problem begin with the geography.
-Alternative maps shift the focus from land area and shape, to the value
-of the statistics in a collection of areas \citep{ACCAC}. Each style of
+Alternative maps can be created to shift the focus from land area and
+shape to the value of the statistics \citep{ACCAC}. Each style of
 cartogram applies a different transformation to the geographic areas, to
-highlight the values of the statistic of interest. These displays result
-in a distortion of the map space to represent features of the
+highlight the values of the statistic of interest. Alternative maps can
+result in a distortion of the map space to represent features of the
 distribution across the areas \citep{ACCAC} as the statistic of interest
@@
 the population in each administrative area \citep{TAAM}. This
-acknowledges that the number of residents can be different but
+acknowledges that the number of residents can be different and also
 recognises that each area, or person within it is equally important.
 
-This paper contains a discussion of Existing Mapping Practices in
-Section 2. This is followed by details of the Algorithm in Section 3.
-Section 4 describes the implementation of the algorithm in the
-\texttt{sugarbag} package. Section 5 outlines the use and benefits of
-animation.
+This paper contains a discussion of Existing Mapping Practices. This is
+followed by details of the Algorithm. The implementation section
+discusses the algorithm in the \texttt{sugarbag} package. Finally, the
+use and benefits of animation are presented.
 
@@
 
-A choropleth map display is the current common practice for spatial data
-visualisation. As the choropleth map display relies on the geographic
-shapes, it does not effectively present the density of the population in
-small geographic areas. The common solution to enhance the communication
-of spatial distributions is to incorporate the population values as a
-cartogram or another alternative map display. Many alternative map
-displays do not work well for Australia due to the large rural
-geographic space between the densely populated capital cities. The
-administrative boundaries may also distract from the statistics
-communicated using colour due to the small size of some areas. This
-paper provides an algorithm for Australia called the hexagon tile map.
+This paper provides an algorithm for Australia called the hexagon tile
+map. It also describes how this algorithm addresses the potential issues
+found with contiguous, non-contiguous and Dorling cartograms when
+applied to Australia. It achieves a display that effectively presents
+the density of the population in small geographic areas and de
+emphasises the large rural geographic space between the densely
+populated capital cities.
 
-Alternative maps highlight the value of the statistics across the
-geographic units. These methods allow increased understanding of the
-spatial distribution of a variable across the population, by fairly
-representing each administrative area. This acknowledges that the amount
-of residents can be different but recognises that each population area
-is equally important. The solution to this visualisation problem can be
-using equally sized areas, with neighbourhood boundary connections. The
-\texttt{sugarbag} package for \texttt{R} creates tessellated hexagon
-tile maps by automating an algorithm to design these displays. The
-Australian application preserves the spatial relationships, emphasising
-capital cities.
-
-These hexagons equally represent each area. However, similar to the
+The hexagon tile map display acknowledges that the amount of residents
+can differ but each administrative area is equally important. This
+solution uses equally sized areas, and maintain neighbourhood boundary
+connections. The \texttt{sugarbag} package for \texttt{R} automates the
+creation of tessellated hexagon tile maps by providing an algorithm to
+design these displays. The Australian application preserves spatial
+relationships, and emphasises capital cities. However, similar to the
 choropleth map display the tessellation does not allow the size of the
@@
 dependent on the focal points used, as this determines the order of
-allocation. It works on the assumption that viewers can identify their
-neighbourhoods using the relative directional relationships but this can
-be aided by the use of animation. With careful consideration of the
-choropleth map, the small geographic inner city areas may have been
-noticed by viewers, but the hexagon tile map display emphasises them.
-The communities in northern Tasmania and the Northern territory do not
-draw attention because of their size as in the choropleth, but their
-colour is still noticeably below average when contrasted with the
-hexagons in New South Wales.
+allocation. With careful consideration of the choropleth map, the small
+geographic inner city areas may have been noticed by viewers, but the
+hexagon tile map display emphasises them. The communities in northern
+Tasmania and the Northern territory do not draw attention because of
+their size as in the choropleth, but their colour is still noticeably
+below average when contrasted with the hexagons in New South Wales.
 
 This algorithm should be general enough to apply to other countries and
-problems
-
-This algorithm has only been tested using single countries, and does not
-consider definite borders of countries. While the buffer allows
-extension beyond the furthest centroids, there is no mechanism to
-protect the borders and ensure centroids are placed within the
-geographic borders of a country.
-
-It would be also possible to take a logarithmic function in the filter
-steps for selection of a hexagon grid point. A direct angle is currently
-used, but this may narrowly miss appropriate hexagons, a logarithmic
+related problems. The algorithm has only been tested using single
+countries. While the buffer allows extension beyond the furthest
+centroids, there is no mechanism implemented to protect the borders and
+ensure centroids are placed within the geographic borders of a country.
+The algorithm is also currently limited to representing each geographic
+area with only one hexagon. Future developments may address these
+limitations, and refine the filter steps for final selection of a
+hexagon grid point for each centroid. A direct angle is currently
+implemented, but may narrowly miss appropriate hexagons, a logarithmic
 function may help to choose a closer hexagon to the original centroid
-location, before increasing the width of the angle used to filter the
-hexagons. This algorithm is an effective start to creating hexagon tile
-maps for many geographic units.
+location. This algorithm is an effective start to creating hexagon tile
+maps for many geographic units. This contributes to an extensive body of
+work that encourages the use of alternative map displays for statistical
+displays of spatial data.
 

### 2020-11-18 kobakian-cook.Rmd

@@
 
-```{r tas_displays, width = 10, height = 3, fig.cap = "The three displays show alternative maps of the Australian state of Tasmania.
-These alternatives show the (a) contiguous cartogram, (b) non-contiguous cartogram and (c) Dorling cartogram of Tasmania."}
+```{r tas_displays, width = 10, height = 3, fig.cap = "The three displays show alternative maps of the Australian state of Tasmania at SA2 level: (a) contiguous cartogram, (b) non-contiguous cartogram and (c) Dorling cartogram of Tasmania.
+The contiguous cartogram looks like the state has an hourglass figure, while the non-contiguous cartogram shrinks areas into invisibility.
+The Dorling expands the metropolitan regions."}
 library(gridExtra)

### 2020-11-18 kobakian-cook.tex

@@
 understanding of the spatial disease distribution as many of the
-communities are not visible in a choropleth display \citep{TVSSS}. Each
-Statistical Area at Level 2 (SA2) \citep{abs2011} was designed to
-represent a community. These administrative areas are often used to
-aggregate census data and used to understand demographics within
-communities of the Australian population. This presents an opportunity
-for explicit map transformations to improve communication of
-distributions \citep{CBATCC}. In figure \ref{fig:tas_displays} the
-choropleth map can be seen underneath each alternative map display to
-allow for comparisons to be made.
+communities are not visible in a choropleth display \citep{TVSSS}.
+
+Administrative areas are often used to aggregate census data and used to
+understand demographics within communities of the Australian population.
+Each SA2 \citep{abs2011} was designed to represent a community. This
+collection of communities presents an opportunity for explicit map
+transformations to improve communication of spatial distributions
+\citep{CBATCC}. In figure \ref{fig:tas_displays} the choropleth map can
+be seen underneath each alternative map display to allow for comparisons
+to be made.
 
 There are several established alternative visualisation methods. Tile
-maps, Rectangular cartograms \citep{ORC} and Dorling cartograms
+maps, rectangular cartograms \citep{ORC} and Dorling cartograms
 \citep{ACTUC} all use one simple shape to represent each geographic
@@
 member of the population can be given equal representation by
-transforming the map \citep{TVSSS}. The impact of a disease over
-connected communities can be seen by allowing the boundaries to maintain
-connection in the transformed display. The contiguous cartogram
-displayed in figure \ref{fig:tas_displays}a) draws attention to smaller
-geographic units when they are rescaled according to the population
-\citep{DMAHP}. These new shapes can now be coloured to represent a
-second variable. The algorithm uses the geographic shape of the areas
-and iterates toward sizing the areas to represent the population. This
-display can create twisted and unfamiliar shapes from the geographic
-units as the algorithms must satisfy the topology conditions, especially
-when there are communities located geographically far from their
-neighbours \citep{TVSSS}.
+transforming the map \citep{TVSSS}. The connected communities can be
+recognised by allowing the boundaries to maintain connection in the
+transformed display. The contiguous cartogram displayed in figure
+\ref{fig:tas_displays}a) draws attention to smaller geographic units
+when they are rescaled according to the population \citep{DMAHP}. These
+new shapes can now be coloured to represent a second variable. The
+algorithm uses the geographic shape of the areas and iterates toward
+sizing the areas to represent the population. This display can create
+twisted and unfamiliar shapes from the geographic units as the
+algorithms must satisfy the topology conditions, especially when there
+are communities located geographically far from their neighbours
+\citep{TVSSS}.
 
@@
 of the SA2 areas is used to scale the geographic units in the
-non-contiguous cartogram \citep{NAC}. The amount of white space can be
-meaningful in non-contiguous cartograms \citep{ECGC}, in this example
-the disparity between large rural areas and small urban areas means that
-the city of Hobart may look reasonable but these units are not visible
-in the context of the Tasmania state map. Depending on the difference
-between the population and geographic land size, the amount of white
-space can also prevent meaningful understanding of the distribution
-\citep{TVSSS}.
+non-contiguous cartogram \citep{NAC}. The amount of background space can
+be meaningful in non-contiguous cartograms \citep{ECGC}. The size
+disparity between rural areas and urban areas result in reasonable
+display within the south eastern city of Hobart, but these units are not
+visible in the context of the Tasmania state map. Depending on the
+difference between the population and geographic land size, the amount
+of white space can also prevent meaningful understanding of the
+distribution \citep{TVSSS}.
 
@@
 The result of the algorithm on rates of thyroid cancer for females in
-each of the SA2 areas of Australia is shown in Figure \ref{fig:hexmap}.
-The difference to the choropleth map in Figure \ref{fig:choro} are
+each of the SA2 areas of Australia is shown in figure \ref{fig:hexmap}.
+The difference to the choropleth map in figure \ref{fig:choro} are
 clear. Now the thyroid cancer incidence in the densely populated areas
@@
 Statistical Areas at Level 2 it results in the hexagon tile map display
-shown in Figure \ref{fig:hexmap}. This display highlights the density of
+shown in figure \ref{fig:hexmap}. This display highlights the density of
 Australian capital cities, as it draws attention to the many communities
@@
 There are several key steps needed to create the hexagon tile map as
-described in the flow chart in Figure \ref{fig:sugarbag_flow}. First,
+described in the flow chart in figure \ref{fig:sugarbag_flow}. First,
 derive the set of centroids from the polygons provided, then create the
 grid of hexagon locations. These two processes are defined in the blue
-left column of the flow chart in Figure \ref{fig:sugarbag_flow}. Each
+left column of the flow chart in figure \ref{fig:sugarbag_flow}. Each
 centroid can then be allocated to an available hexagon location. The
 steps for the allocation process are detailed in the right column of
-Figure \ref{fig:sugarbag_flow}. There are several filter steps to speed
+figure \ref{fig:sugarbag_flow}. There are several filter steps to speed
 the process of selecting an appropriate hexagon to represent each
@@
 this example, this distance is only calculated for the capital city of
-Hobart, represented in Figure \ref{fig:filterprocess}c and d as a white
+Hobart, represented in figure \ref{fig:filterprocess}c and d as a white
 cross.
@@
 prevents multiple geographic units from being allocated to the same
-hexagon. This is demonstrated in Figure \ref{fig:filterprocess}c and d
+hexagon. This is demonstrated in figure \ref{fig:filterprocess}c and d
 by the black hexagons that represent the seven closest polygons to the
@@
 angle from the focal point to centroid location. This uses the angle
-from the closest capital city, to the current centroid as seen in Figure
+from the closest capital city, to the current centroid as seen in figure
 \ref{fig:filterprocess}c.~This allows the spatial relationship to be

### 2020-11-18 kobakian-cook.Rmd
complete changes recommended by Earl

@@
 
-The algorithm is implemented in the `sugarbag` package for R, this is the common name for the *Trigona carbonaria* bee species.
-Native to northern and eastern Australia this stingless species builds flat layers of hexagonal brood cells, spiralling out from a central point [@PH].
-This hive design inspired the use of multiple focal points in the algorithm, individual spirals are constructed by building out from various points on the geographic map base.
+The algorithm is implemented in the `sugarbag` package for `R`, named after the common name for the *Trigona carbonaria* bee – a species which builds flat layers of hexagonal brood cells, spiralling out from a central point [@PH].
+This unusual pattern also provided the inspiration for the algorithm, where the maps are constructed by building out from multiple focal points on the geographic map base in a spiral fashion.
 
-The result of the algorithm on rates of thyroid cancer for females in each of the SA2 areas of Australia is shown in figure \ref{fig:hexmap}.
+The result of the algorithm applied to the same data represented in figure \ref{fig:choro} shows rates of thyroid cancer for females in each of the SA2 areas of Australia as hexagons in figure \ref{fig:hexmap}.
 The difference to the choropleth map in figure \ref{fig:choro} are clear.
-Now the thyroid cancer incidence in the densely populated areas in Sydney, Brisbane and Perth are visible.
-Interestingly there is no clear divide between rural and urban SA2 areas as many rural areas, and the cities of Melbourne, Darwin, Adelaide and Hobart have low rates of thyroid cancer diagnosis for females.
+Now the higher thyroid cancer incidence in the densely populated areas in Sydney, Brisbane and Perth are visible.
+Interestingly, there is no clear divide between rural and urban SA2 areas, as many rural areas and the cities of Melbourne, Darwin, Adelaide and Hobart have low rates of thyroid incidence for females.
 The hexagon tile map display provides a more accurate representation of the spatial distribution of thyroid cancer incidence across Australia.
 
-When the algorithm is applied to the complete set of all Australian Statistical Areas at Level 2 it results in the hexagon tile map display shown in figure \ref{fig:hexmap}.
-This display highlights the density of Australian capital cities, as it draws attention to the many communities in Sydney, Melbourne and Hobart.
+Figure \ref{fig:hexmap} highlights the density of Australian capital cities, as it draws attention to the many communities in Sydney, Melbourne and Hobart.
 This display also highlights the disparity in the burden of thyroid cancer for females in the communities of these cities.
@@
 
-Compared to the choropleth map display, the low rates in the rural Australian communities are no longer dominating the display.
-While the representative hexagons are still visible against the black background, the much lower than average rates in the Northern Territory are less noticeable.
+Compared to the choropleth map display in figure \ref{fig:choro}, the low rates in the rural Australian communities are no longer dominating the display.
+While the representative hexagons are still visible against the black background, the much lower than average rates in rural Australia are less noticeable.
 
@@
 
-There are several key steps needed to create the hexagon tile map as described in the flow chart in figure \ref{fig:sugarbag_flow}.
+There are several key steps in the creation of the hexagon tile map as described in the flow chart in figure \ref{fig:sugarbag_flow}.
 First, derive the set of centroids from the polygons provided, then create the grid of hexagon locations.
@@
 
-Only two inputs are necessary to begin the algorithm; the shape file, and the id variable. The id variable should uniquely identify each geographic unit in the shape file.
+Only two inputs are necessary to begin the algorithm; the shapefile, and the ID variable. The ID variable should uniquely identify each geographic unit in the shapefile.
 
-The centroids are derived from the shape file.
+The centroids are derived from the shapefile.
 The amount of centroids within the geographic map is used to determine an appropriate hexagon size if one is not provided.
@@
 The grid will initially cover the entire map space, encompassing all the centroid locations and will extend in all directions to the extent of the buffer distance.
-This buffer distance can be helpful to account for densely populated coastal areas, allowing the use of the sea for hexagon locations.
+This buffer distance can be helpful to account for densely populated coastal areas, allowing the hexagon locations to spread beyond the coastline, over the sea.
 
 The centroid set and hexagon tile map grid are necessary for the allocation process.
-Additionally, a set of reference locations can be provided as focal points, such as the capital cities of states or countries.
+Additionally, a set of reference locations can be provided as focal points, typically compact and/or densely populated areas such as major cities.
 The algorithm will use the focal points to create the order of allocation, prioritising the closest centroid locations to the focal points.
-Alternatively, a user can specify the variable that should be used to determine the order for the allocation.
+The user can also specify the variable that should be used to determine the order for the allocation.
 
@@
 This algorithm was created to automate this process, and reduce the manual load involved in creating and implementing alternative displays.
-This allows map makers and data communicators to spend their time to choosing the most effective display.
+This allows map makers and data communicators to spend their time choosing the most effective display.
 
-The `sugarbag` package has been written for R software, it contains a set of functions that help R users to create a hexagon tile map.
-The algorithm presented in the `sugarbag` package operates on a set of simple feature geometry objects [@sf], this package allows R users to create `sf` objects by importing polygons stored in various formats.
+The `sugarbag` package contains a set of functions that help R users to create a hexagon tile map.
+The algorithm presented in the `sugarbag` package operates on a set of simple feature geometry objects , known as `sf` objects[@sf].
+This package allows R users to create `sf` objects by importing polygons stored in various formats.
 Users should provide a set of polygons that define geographic units by their administrative boundaries.
-The functions arrange the geographic units in order of proximity to a set of locations provided, such as the centre of capital cities.
+The functions arrange the geographic units in order of proximity to a set of locations provided, such as the centre of major cities.
 The centroid location of each geographic unit is used to measure the proximity.
-It emphasises the capital cities as population hubs, rather than emphasizing the size of large, rural geographic units.
+It emphasises the major cities as population hubs, rather than emphasizing the size of large, rural geographic units.
 
-A user can tweak the parameters of the hexagon map using the additional arguments to the `create_hexmap` function, these options may affect the speed of the creation. 
-The hexagon size may need adjustments depending on the density of the population, users can provide an appropriate hexagon size and re-run the algorithm.
+A user can tweak the parameters of the hexagon map using the additional arguments to the `create_hexmap` function, but these options may affect the speed of the algorithm. 
+The hexagon size may need adjustments depending on the density of the population; users can provide an appropriate hexagon size and re-run the algorithm.
 The buffer distance may need to be increased if the coastal cities need to extend beyond the geographic land mass.
@@
 
-and the development version can be install from the GitHub repository:
+and the development version can be installed from the GitHub repository:
 
@@
 
-The polygon set of Tasmania in 2011 is accessed from the `absmapsdata` package.
+The set of SA2 polygons for Tasmania, using the 2011 definition of SA2s, is accessed from the `absmapsdata` package.
 A single column of the data set is used to identify the unique areas.
@@
 It finds the grid points needed to best capture the set of centroids on a hexagon tile map.
-Reducing the buffer can help to decrease the amount of time taken, as there will be less points in the water to consider for each centroid allocation.
+Reducing the buffer can help to decrease the amount of time taken, as there will be less points over the water to consider for each centroid allocation.
 
@@
 
-If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded, only when a maximum distance is reached will the angle expand to accommodate more possible grid points.
-By default the angle filter for the hexagon grid points create plus and minus 30 degrees bounds of the angle from the focal point to the geographic centroid.
+If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded and only when a maximum distance is reached will the angle expand to accommodate more possible grid points.
+By default the angle filter for the hexagon grid points create plus and minus 30 degree bounds of the angle from the focal point to the geographic centroid.
 This will increase if no points can be found within the `hex_filter` distance.
@@
 
-Creating an animation connecting these two displays can allow users t grasp the meaning of the connected hexagons.
+Creating an animation connecting these two displays can allow users to grasp the meaning of the connected hexagons.
 It will also highlight the density of the communities using the rapid expansion of the inner-city areas, these hexagons will move the furthest and will move rapidly in the animation from their geographic locations.
-The rapid decrease in size of the large rural areas can show how large the landmass of Statistical Areas can be, and how few people occupy rural areas.
+The rapid decrease in size of the large rural areas can show the large size of their collective landmass.
 The `gganimate` [@gganimate] package can be used to make an animation.
@@
 
-## Conclusion {#conclusion-03}
+## Discussion and Conclusion {#conclusion-03}
 
@@
 The algorithm is heavily dependent on the focal points used, as this determines the order of allocation.
-With careful consideration of the choropleth map, the small geographic inner city areas may have been noticed by viewers, but the hexagon tile map display emphasises them.
+With careful consideration of the choropleth map, the small geographic inner city areas may not have been noticed by viewers, but the hexagon tile map display emphasises them.
 The communities in northern Tasmania and the Northern territory do not draw attention because of their size as in the choropleth, but their colour is still noticeably below average when contrasted with the hexagons in New South Wales.
@@
 
-This algorithm should be general enough to apply to other countries and related problems.
+This algorithm should be general enough to apply to other study regions and contexts.
 The algorithm has only been tested using single countries.

### 2020-11-18 kobakian-cook.tex
complete changes recommended by Earl

@@
 
-The algorithm is implemented in the \texttt{sugarbag} package for R,
-this is the common name for the \emph{Trigona carbonaria} bee species.
-Native to northern and eastern Australia this stingless species builds
-flat layers of hexagonal brood cells, spiralling out from a central
-point \citep{PH}. This hive design inspired the use of multiple focal
-points in the algorithm, individual spirals are constructed by building
-out from various points on the geographic map base.
+The algorithm is implemented in the \texttt{sugarbag} package for
+\texttt{R}, named after the common name for the \emph{Trigona
+carbonaria} bee -- a species which builds flat layers of hexagonal brood
+cells, spiralling out from a central point \citep{PH}. This unusual
+pattern also provided the inspiration for the algorithm, where the maps
+are constructed by building out from multiple focal points on the
+geographic map base in a spiral fashion.
 
-The result of the algorithm on rates of thyroid cancer for females in
-each of the SA2 areas of Australia is shown in figure \ref{fig:hexmap}.
+The result of the algorithm applied to the same data represented in
+figure \ref{fig:choro} shows rates of thyroid cancer for females in each
+of the SA2 areas of Australia as hexagons in figure \ref{fig:hexmap}.
 The difference to the choropleth map in figure \ref{fig:choro} are
-clear. Now the thyroid cancer incidence in the densely populated areas
-in Sydney, Brisbane and Perth are visible. Interestingly there is no
-clear divide between rural and urban SA2 areas as many rural areas, and
-the cities of Melbourne, Darwin, Adelaide and Hobart have low rates of
-thyroid cancer diagnosis for females. The hexagon tile map display
-provides a more accurate representation of the spatial distribution of
-thyroid cancer incidence across Australia.
+clear. Now the higher thyroid cancer incidence in the densely populated
+areas in Sydney, Brisbane and Perth are visible. Interestingly, there is
+no clear divide between rural and urban SA2 areas, as many rural areas
+and the cities of Melbourne, Darwin, Adelaide and Hobart have low rates
+of thyroid incidence for females. The hexagon tile map display provides
+a more accurate representation of the spatial distribution of thyroid
+cancer incidence across Australia.
 
-When the algorithm is applied to the complete set of all Australian
-Statistical Areas at Level 2 it results in the hexagon tile map display
-shown in figure \ref{fig:hexmap}. This display highlights the density of
-Australian capital cities, as it draws attention to the many communities
-in Sydney, Melbourne and Hobart. This display also highlights the
-disparity in the burden of thyroid cancer for females in the communities
-of these cities. There are several collections of red hexagons in Sydney
-that represent the communities with much higher rates of diagnosis than
-the Australian average. Brisbane also experiences higher than average
-rates of diagnosis, but has more orange than red. The females in the
-cities of Adelaide and Perth show much lower rates of diagnosis.
+Figure \ref{fig:hexmap} highlights the density of Australian capital
+cities, as it draws attention to the many communities in Sydney,
+Melbourne and Hobart. This display also highlights the disparity in the
+burden of thyroid cancer for females in the communities of these cities.
+There are several collections of red hexagons in Sydney that represent
+the communities with much higher rates of diagnosis than the Australian
+average. Brisbane also experiences higher than average rates of
+diagnosis, but has more orange than red. The females in the cities of
+Adelaide and Perth show much lower rates of diagnosis.
 
-Compared to the choropleth map display, the low rates in the rural
-Australian communities are no longer dominating the display. While the
-representative hexagons are still visible against the black background,
-the much lower than average rates in the Northern Territory are less
-noticeable.
+Compared to the choropleth map display in figure \ref{fig:choro}, the
+low rates in the rural Australian communities are no longer dominating
+the display. While the representative hexagons are still visible against
+the black background, the much lower than average rates in rural
+Australia are less noticeable.
 
@@
 
-There are several key steps needed to create the hexagon tile map as
+There are several key steps in the creation of the hexagon tile map as
 described in the flow chart in figure \ref{fig:sugarbag_flow}. First,
@@
 
-Only two inputs are necessary to begin the algorithm; the shape file,
-and the id variable. The id variable should uniquely identify each
-geographic unit in the shape file.
+Only two inputs are necessary to begin the algorithm; the shapefile, and
+the ID variable. The ID variable should uniquely identify each
+geographic unit in the shapefile.
 
-The centroids are derived from the shape file. The amount of centroids
+The centroids are derived from the shapefile. The amount of centroids
 within the geographic map is used to determine an appropriate hexagon
@@
 the buffer distance. This buffer distance can be helpful to account for
-densely populated coastal areas, allowing the use of the sea for hexagon
-locations.
+densely populated coastal areas, allowing the hexagon locations to
+spread beyond the coastline, over the sea.
 
@@
 allocation process. Additionally, a set of reference locations can be
-provided as focal points, such as the capital cities of states or
-countries. The algorithm will use the focal points to create the order
-of allocation, prioritising the closest centroid locations to the focal
-points. Alternatively, a user can specify the variable that should be
-used to determine the order for the allocation.
+provided as focal points, typically compact and/or densely populated
+areas such as major cities. The algorithm will use the focal points to
+create the order of allocation, prioritising the closest centroid
+locations to the focal points. The user can also specify the variable
+that should be used to determine the order for the allocation.
 
@@
 load involved in creating and implementing alternative displays. This
-allows map makers and data communicators to spend their time to choosing
+allows map makers and data communicators to spend their time choosing
 the most effective display.
 
-The \texttt{sugarbag} package has been written for R software, it
-contains a set of functions that help R users to create a hexagon tile
-map. The algorithm presented in the \texttt{sugarbag} package operates
-on a set of simple feature geometry objects \citep{sf}, this package
-allows R users to create \texttt{sf} objects by importing polygons
-stored in various formats. Users should provide a set of polygons that
-define geographic units by their administrative boundaries. The
-functions arrange the geographic units in order of proximity to a set of
-locations provided, such as the centre of capital cities. The centroid
-location of each geographic unit is used to measure the proximity. It
-emphasises the capital cities as population hubs, rather than
-emphasizing the size of large, rural geographic units.
+The \texttt{sugarbag} package contains a set of functions that help R
+users to create a hexagon tile map. The algorithm presented in the
+\texttt{sugarbag} package operates on a set of simple feature geometry
+objects , known as \texttt{sf} objects\citep{sf}. This package allows R
+users to create \texttt{sf} objects by importing polygons stored in
+various formats. Users should provide a set of polygons that define
+geographic units by their administrative boundaries. The functions
+arrange the geographic units in order of proximity to a set of locations
+provided, such as the centre of major cities. The centroid location of
+each geographic unit is used to measure the proximity. It emphasises the
+major cities as population hubs, rather than emphasizing the size of
+large, rural geographic units.
 
 A user can tweak the parameters of the hexagon map using the additional
-arguments to the \texttt{create\_hexmap} function, these options may
-affect the speed of the creation. The hexagon size may need adjustments
-depending on the density of the population, users can provide an
+arguments to the \texttt{create\_hexmap} function, but these options may
+affect the speed of the algorithm. The hexagon size may need adjustments
+depending on the density of the population; users can provide an
 appropriate hexagon size and re-run the algorithm. The buffer distance
@@
 
-The polygon set of Tasmania in 2011 is accessed from the
-\texttt{absmapsdata} package. A single column of the data set is used to
-identify the unique areas. In this case, the unique SA2 names for each
-SA2 have been used.
+The set of SA2 polygons for Tasmania, using the 2011 definition of SA2s,
+is accessed from the \texttt{absmapsdata} package. A single column of
+the data set is used to identify the unique areas. In this case, the
+unique SA2 names for each SA2 have been used.
 
@@
 buffer can help to decrease the amount of time taken, as there will be
-less points in the water to consider for each centroid allocation.
+less points over the water to consider for each centroid allocation.
 
@@
 If no available hexagon grid point is found within the original filter
-distance and angle, the distance is expanded, only when a maximum
+distance and angle, the distance is expanded and only when a maximum
 distance is reached will the angle expand to accommodate more possible
 grid points. By default the angle filter for the hexagon grid points
-create plus and minus 30 degrees bounds of the angle from the focal
-point to the geographic centroid. This will increase if no points can be
-found within the \texttt{hex\_filter} distance. The default angle of 30
-was chosen to allow the algorithm to find hexagons that best maintained
-the spatial relationship between the focal point and geographic
-centroid.
+create plus and minus 30 degree bounds of the angle from the focal point
+to the geographic centroid. This will increase if no points can be found
+within the \texttt{hex\_filter} distance. The default angle of 30 was
+chosen to allow the algorithm to find hexagons that best maintained the
+spatial relationship between the focal point and geographic centroid.
 
@@
 
-Creating an animation connecting these two displays can allow users t
+Creating an animation connecting these two displays can allow users to
 grasp the meaning of the connected hexagons. It will also highlight the
@@
 the animation from their geographic locations. The rapid decrease in
-size of the large rural areas can show how large the landmass of
-Statistical Areas can be, and how few people occupy rural areas. The
-\texttt{gganimate} \citep{gganimate} package can be used to make an
-animation. It connects the polygons for each area in the two displays
-using the \texttt{sf\_id} variable, the names of the statistical areas,
-and creates intermediate displays as they geographic areas shrink or
-expand to the chosen hexagon size.
+size of the large rural areas can show the large size of their
+collective landmass. The \texttt{gganimate} \citep{gganimate} package
+can be used to make an animation. It connects the polygons for each area
+in the two displays using the \texttt{sf\_id} variable, the names of the
+statistical areas, and creates intermediate displays as they geographic
+areas shrink or expand to the chosen hexagon size.
 
 \hypertarget{conclusion-03}{%
-\subsection{Conclusion}\label{conclusion-03}}
+\subsection{Discussion and Conclusion}\label{conclusion-03}}
 
@@
 allocation. With careful consideration of the choropleth map, the small
-geographic inner city areas may have been noticed by viewers, but the
-hexagon tile map display emphasises them. The communities in northern
-Tasmania and the Northern territory do not draw attention because of
-their size as in the choropleth, but their colour is still noticeably
-below average when contrasted with the hexagons in New South Wales.
+geographic inner city areas may not have been noticed by viewers, but
+the hexagon tile map display emphasises them. The communities in
+northern Tasmania and the Northern territory do not draw attention
+because of their size as in the choropleth, but their colour is still
+noticeably below average when contrasted with the hexagons in New South
+Wales.
 
-This algorithm should be general enough to apply to other countries and
-related problems. The algorithm has only been tested using single
-countries. While the buffer allows extension beyond the furthest
-centroids, there is no mechanism implemented to protect the borders and
-ensure centroids are placed within the geographic borders of a country.
-The algorithm is also currently limited to representing each geographic
-area with only one hexagon. Future developments may address these
-limitations, and refine the filter steps for final selection of a
-hexagon grid point for each centroid. A direct angle is currently
-implemented, but may narrowly miss appropriate hexagons, a logarithmic
-function may help to choose a closer hexagon to the original centroid
-location. This algorithm is an effective start to creating hexagon tile
-maps for many geographic units. This contributes to an extensive body of
-work that encourages the use of alternative map displays for statistical
-displays of spatial data.
+This algorithm should be general enough to apply to other study regions
+and contexts. The algorithm has only been tested using single countries.
+While the buffer allows extension beyond the furthest centroids, there
+is no mechanism implemented to protect the borders and ensure centroids
+are placed within the geographic borders of a country. The algorithm is
+also currently limited to representing each geographic area with only
+one hexagon. Future developments may address these limitations, and
+refine the filter steps for final selection of a hexagon grid point for
+each centroid. A direct angle is currently implemented, but may narrowly
+miss appropriate hexagons, a logarithmic function may help to choose a
+closer hexagon to the original centroid location. This algorithm is an
+effective start to creating hexagon tile maps for many geographic units.
+This contributes to an extensive body of work that encourages the use of
+alternative map displays for statistical displays of spatial data.
 

### 2020-11-25 kobakian-cook.Rmd
abstract rtweaks

@@
 abstract: >
-  Spatial distributions have been presented on alternative representations of geography for many years.
+  Spatial distributions have been presented on alternative representations of geography, such as cartograms, for many years.
 In modern times, interactivity and animation have allowed alternative displays to play a larger role.
@@
 Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
-The algorithm presented creates a display that uses tessellated hexagons to represent a set of spatial polygons.
+The algorithm presented creates a display that uses tessellated hexagons to represent a set of spatial polygons, and is implemented in the R package called sugarbag.
 It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units, in light of their positions to points of interest.

### 2020-11-25 kobakian-cook.Rmd
slight wording in the intro

@@
 
-Alternative mapping methods allow increased understanding of the spatial distribution of a variable across the population, by fairly representing the population in each administrative area [@TAAM].
+Alternative mapping methods, like cartograms, allow increased understanding of the spatial distribution of a variable across the population, by fairly representing the population in each administrative area [@TAAM].
 This acknowledges that the number of residents can be different and also recognises that each area, or person within it is equally important.
 
-This paper contains a discussion of Existing Mapping Practices.
-This is followed by details of the Algorithm.
+This paper contains a discussion of existing mapping practices.
+This is followed by details of the algorithm.
 The implementation section discusses the algorithm in the `sugarbag` package.

### 2020-11-25 kobakian-cook.tex
slight wording in the intro

@@
 Spatial distributions have been presented on alternative representations
-of geography for many years. In modern times, interactivity and
-animation have allowed alternative displays to play a larger role.
-Alternative representations have been popularised by online news sites,
-and digital atlases with a focus on public consumption. Applications are
-increasingly widespread, especially in the areas of disease mapping, and
-election results. The algorithm presented creates a display that uses
-tessellated hexagons to represent a set of spatial polygons. It
+of geography, such as cartograms, for many years. In modern times,
+interactivity and animation have allowed alternative displays to play a
+larger role. Alternative representations have been popularised by online
+news sites, and digital atlases with a focus on public consumption.
+Applications are increasingly widespread, especially in the areas of
+disease mapping, and election results. The algorithm presented creates a
+display that uses tessellated hexagons to represent a set of spatial
+polygons, and is implemented in the R package called sugarbag. It
 allocates these hexagon in a manner that preserves the spatial

### 2020-11-25 kobakian-cook.Rmd
figure changed to Figure throughout

@@
 This collection of communities presents an opportunity for explicit map transformations to improve communication of spatial distributions [@CBATCC].
-In figure \ref{fig:tas_displays} the choropleth map can be seen underneath each alternative map display to allow for comparisons to be made.
+In Figure \ref{fig:tas_displays} the choropleth map can be seen underneath each alternative map display to allow for comparisons to be made.
 
@@
 The connected communities can be recognised by allowing the boundaries to maintain connection in the transformed display.
-The contiguous cartogram displayed in figure \ref{fig:tas_displays}a) draws attention to smaller geographic units when they are rescaled according to the population [@DMAHP].
+The contiguous cartogram displayed in Figure \ref{fig:tas_displays}a) draws attention to smaller geographic units when they are rescaled according to the population [@DMAHP].
 These new shapes can now be coloured to represent a second variable.
@@
 
-The result of the algorithm applied to the same data represented in figure \ref{fig:choro} shows rates of thyroid cancer for females in each of the SA2 areas of Australia as hexagons in figure \ref{fig:hexmap}.
-The difference to the choropleth map in figure \ref{fig:choro} are clear.
+The result of the algorithm applied to the same data represented in Figure \ref{fig:choro} shows rates of thyroid cancer for females in each of the SA2 areas of Australia as hexagons in Figure \ref{fig:hexmap}.
+The difference to the choropleth map in Figure \ref{fig:choro} are clear.
 Now the higher thyroid cancer incidence in the densely populated areas in Sydney, Brisbane and Perth are visible.
@@
 
-Compared to the choropleth map display in figure \ref{fig:choro}, the low rates in the rural Australian communities are no longer dominating the display.
+Compared to the choropleth map display in Figure \ref{fig:choro}, the low rates in the rural Australian communities are no longer dominating the display.
 While the representative hexagons are still visible against the black background, the much lower than average rates in rural Australia are less noticeable.
@@
 
-There are several key steps in the creation of the hexagon tile map as described in the flow chart in figure \ref{fig:sugarbag_flow}.
+There are several key steps in the creation of the hexagon tile map as described in the flow chart in Figure \ref{fig:sugarbag_flow}.
 First, derive the set of centroids from the polygons provided, then create the grid of hexagon locations.
-These two processes are defined in the blue left column of the flow chart in figure \ref{fig:sugarbag_flow}.
+These two processes are defined in the blue left column of the flow chart in Figure \ref{fig:sugarbag_flow}.
 Each centroid can then be allocated to an available hexagon location.
-The steps for the allocation process are detailed in the right column of figure \ref{fig:sugarbag_flow}.
+The steps for the allocation process are detailed in the right column of Figure \ref{fig:sugarbag_flow}.
 There are several filter steps to speed the process of selecting an appropriate hexagon to represent each geographic unit.
@@
 The order for allocation is determined by the distance between the polygon centroid and it's closest focal point.
-For this example, this distance is only calculated for the capital city of Hobart, represented in figure \ref{fig:filterprocess}c and d as a white cross.
+For this example, this distance is only calculated for the capital city of Hobart, represented in Figure \ref{fig:filterprocess}c and d as a white cross.
 
@@
 Keeping only the available hexagon points prevents multiple geographic units from being allocated to the same hexagon.
-This is demonstrated in figure \ref{fig:filterprocess}c and d by the black hexagons that represent the seven closest polygons to the capital city of Hobart.
+This is demonstrated in Figure \ref{fig:filterprocess}c and d by the black hexagons that represent the seven closest polygons to the capital city of Hobart.
 As the allocation process begins for the eighth closest centroid there are seven unavailable hexagon locations.
@@
 The width is the amount of degrees used on either side of the angle from the focal point to centroid location.
-This uses the angle from the closest capital city, to the current centroid as seen in figure \ref{fig:filterprocess}c.
+This uses the angle from the closest capital city, to the current centroid as seen in Figure \ref{fig:filterprocess}c.
 This allows the spatial relationship to be preserved, even when it is allocated to a hexagon that is further from the focal point then the original centroid location.
@@
 Two views of the same data are produced by filling according to the thyroid Cancer Standardised Incidence Rates (SIRs) downloaded from the Australian Cancer Atlas site.
-This small example in figure \ref{fig:hexmap} shows the group of blue areas in the Hobart CBD more prominently in the hexagon tile map.
+This small example in Figure \ref{fig:hexmap} shows the group of blue areas in the Hobart CBD more prominently in the hexagon tile map.
 The small red areas visible in the choropleth map (a) along the north coast are much larger in the hexagon tile maps.

### 2020-11-25 kobakian-cook.tex
figure changed to Figure throughout

@@
 
-Alternative mapping methods allow increased understanding of the spatial
-distribution of a variable across the population, by fairly representing
-the population in each administrative area \citep{TAAM}. This
-acknowledges that the number of residents can be different and also
-recognises that each area, or person within it is equally important.
+Alternative mapping methods, like cartograms, allow increased
+understanding of the spatial distribution of a variable across the
+population, by fairly representing the population in each administrative
+area \citep{TAAM}. This acknowledges that the number of residents can be
+different and also recognises that each area, or person within it is
+equally important.
 
-This paper contains a discussion of Existing Mapping Practices. This is
-followed by details of the Algorithm. The implementation section
+This paper contains a discussion of existing mapping practices. This is
+followed by details of the algorithm. The implementation section
 discusses the algorithm in the \texttt{sugarbag} package. Finally, the

### 2020-11-25 kobakian-cook.Rmd
conclusions

@@
 
-This paper provides an algorithm for Australia called the hexagon tile map.
+This work provides an algorithm called the hexagon tile map.
 It also describes how this algorithm addresses the potential issues found with contiguous, non-contiguous and Dorling cartograms when applied to Australia.
-It achieves a display that effectively presents the density of the population in small geographic areas and de emphasises the large rural geographic space between the densely populated capital cities.
+It achieves a display that effectively presents the density of the population in small geographic areas and de-emphasises the large rural geographic space between the densely populated capital cities.
+The hexagon tile map display acknowledges that the amount of residents can differ but each administrative area is equally important.
+This solution uses equally sized areas, and maintain neighbourhood boundary connections.
 
 <!-- implementation -->
-The hexagon tile map display acknowledges that the amount of residents can differ but each administrative area is equally important.
-This solution uses equally sized areas, and maintain neighbourhood boundary connections.
  The `sugarbag` package for `R` automates the creation of tessellated hexagon tile maps by providing an algorithm to design these displays.
@@
 However, similar to the choropleth map display the tessellation does not allow the size of the hexagons to represent another variable.
-The algorithm is heavily dependent on the focal points used, as this determines the order of allocation.
-With careful consideration of the choropleth map, the small geographic inner city areas may not have been noticed by viewers, but the hexagon tile map display emphasises them.
-The communities in northern Tasmania and the Northern territory do not draw attention because of their size as in the choropleth, but their colour is still noticeably below average when contrasted with the hexagons in New South Wales.
+The algorithm uses focal points, which are the centers of capital cities for Australia, to determine the order and direction of allocation.
+After careful consideration of the choropleth map, the small geographic inner city areas with high thyroid cancer prevalence may have been missed by viewers, but the hexagon tile map display reveals them.
+The communities in northern Tasmania and the Northern Territory draw less attention because they are smaller and more isolated in the hexagon tile map, but their colour is still comparable with the hexagons in other regions.
 
-<!-- limitiations, where it might not work -->
+<!-- limitations, where it might not work -->
 
@@
 A direct angle is currently implemented, but may narrowly miss appropriate hexagons, a logarithmic function may help to choose a closer hexagon to the original centroid location.
-This algorithm is an effective start to creating hexagon tile maps for many geographic units.
+This algorithm is an effective start to automatically creating hexagon tile maps for many geographic units.
 This contributes to an extensive body of work that encourages the use of alternative map displays for statistical displays of spatial data.

### 2020-11-25 kobakian-cook.tex
conclusions

@@
 transformations to improve communication of spatial distributions
-\citep{CBATCC}. In figure \ref{fig:tas_displays} the choropleth map can
+\citep{CBATCC}. In Figure \ref{fig:tas_displays} the choropleth map can
 be seen underneath each alternative map display to allow for comparisons
@@
 recognised by allowing the boundaries to maintain connection in the
-transformed display. The contiguous cartogram displayed in figure
+transformed display. The contiguous cartogram displayed in Figure
 \ref{fig:tas_displays}a) draws attention to smaller geographic units
@@
 The result of the algorithm applied to the same data represented in
-figure \ref{fig:choro} shows rates of thyroid cancer for females in each
-of the SA2 areas of Australia as hexagons in figure \ref{fig:hexmap}.
-The difference to the choropleth map in figure \ref{fig:choro} are
+Figure \ref{fig:choro} shows rates of thyroid cancer for females in each
+of the SA2 areas of Australia as hexagons in Figure \ref{fig:hexmap}.
+The difference to the choropleth map in Figure \ref{fig:choro} are
 clear. Now the higher thyroid cancer incidence in the densely populated
@@
 
-Compared to the choropleth map display in figure \ref{fig:choro}, the
+Compared to the choropleth map display in Figure \ref{fig:choro}, the
 low rates in the rural Australian communities are no longer dominating
@@
 There are several key steps in the creation of the hexagon tile map as
-described in the flow chart in figure \ref{fig:sugarbag_flow}. First,
+described in the flow chart in Figure \ref{fig:sugarbag_flow}. First,
 derive the set of centroids from the polygons provided, then create the
 grid of hexagon locations. These two processes are defined in the blue
-left column of the flow chart in figure \ref{fig:sugarbag_flow}. Each
+left column of the flow chart in Figure \ref{fig:sugarbag_flow}. Each
 centroid can then be allocated to an available hexagon location. The
 steps for the allocation process are detailed in the right column of
-figure \ref{fig:sugarbag_flow}. There are several filter steps to speed
+Figure \ref{fig:sugarbag_flow}. There are several filter steps to speed
 the process of selecting an appropriate hexagon to represent each
@@
 this example, this distance is only calculated for the capital city of
-Hobart, represented in figure \ref{fig:filterprocess}c and d as a white
+Hobart, represented in Figure \ref{fig:filterprocess}c and d as a white
 cross.
@@
 prevents multiple geographic units from being allocated to the same
-hexagon. This is demonstrated in figure \ref{fig:filterprocess}c and d
+hexagon. This is demonstrated in Figure \ref{fig:filterprocess}c and d
 by the black hexagons that represent the seven closest polygons to the
@@
 angle from the focal point to centroid location. This uses the angle
-from the closest capital city, to the current centroid as seen in figure
+from the closest capital city, to the current centroid as seen in Figure
 \ref{fig:filterprocess}c.~This allows the spatial relationship to be
@@
 
-This paper provides an algorithm for Australia called the hexagon tile
-map. It also describes how this algorithm addresses the potential issues
-found with contiguous, non-contiguous and Dorling cartograms when
-applied to Australia. It achieves a display that effectively presents
-the density of the population in small geographic areas and de
-emphasises the large rural geographic space between the densely
-populated capital cities.
+This work provides an algorithm called the hexagon tile map. It also
+describes how this algorithm addresses the potential issues found with
+contiguous, non-contiguous and Dorling cartograms when applied to
+Australia. It achieves a display that effectively presents the density
+of the population in small geographic areas and de-emphasises the large
+rural geographic space between the densely populated capital cities. The
+hexagon tile map display acknowledges that the amount of residents can
+differ but each administrative area is equally important. This solution
+uses equally sized areas, and maintain neighbourhood boundary
+connections.
 
-The hexagon tile map display acknowledges that the amount of residents
-can differ but each administrative area is equally important. This
-solution uses equally sized areas, and maintain neighbourhood boundary
-connections. The \texttt{sugarbag} package for \texttt{R} automates the
-creation of tessellated hexagon tile maps by providing an algorithm to
-design these displays. The Australian application preserves spatial
-relationships, and emphasises capital cities. However, similar to the
-choropleth map display the tessellation does not allow the size of the
-hexagons to represent another variable. The algorithm is heavily
-dependent on the focal points used, as this determines the order of
-allocation. With careful consideration of the choropleth map, the small
-geographic inner city areas may not have been noticed by viewers, but
-the hexagon tile map display emphasises them. The communities in
-northern Tasmania and the Northern territory do not draw attention
-because of their size as in the choropleth, but their colour is still
-noticeably below average when contrasted with the hexagons in New South
-Wales.
+The \texttt{sugarbag} package for \texttt{R} automates the creation of
+tessellated hexagon tile maps by providing an algorithm to design these
+displays. The Australian application preserves spatial relationships,
+and emphasises capital cities. However, similar to the choropleth map
+display the tessellation does not allow the size of the hexagons to
+represent another variable. The algorithm uses focal points, which are
+the centers of capital cities for Australia, to determine the order and
+direction of allocation. After careful consideration of the choropleth
+map, the small geographic inner city areas with high thyroid cancer
+prevalence may have been missed by viewers, but the hexagon tile map
+display reveals them. The communities in northern Tasmania and the
+Northern Territory draw less attention because they are smaller and more
+isolated in the hexagon tile map, but their colour is still comparable
+with the hexagons in other regions.
 

### 2020-11-25 kobakian-cook.Rmd
caption for figure 5

@@
 
+It is also common to treat all geographic units as equal, so that regardless of the population or other information, to generate equal size spatial polygons.
+The Dorling algorithm can beinduced to do this, to make equallly sized circles.
+@MDAC describes a group of alternative maps called "mosaic cartograms" for tile displays.
+The geography of the USA has been transformed into a square-binned tile map manually and made available in the R package \CRANpkg{statebins} [@statebins].The algorithm described below is an automatic layout of hexagon tiles, where a continguity constraint is relaxed.
+This gives equal weight to each geographic area even if the population differs.
+
 ## Algorithm
@@
 
-The algorithm is implemented in the `sugarbag` package for `R`, named after the common name for the *Trigona carbonaria* bee – a species which builds flat layers of hexagonal brood cells, spiralling out from a central point [@PH].
+The algorithm is implemented in the \CRANpkg{sugarbag} package for `R`, named after the common name for the *Trigona carbonaria* bee – a species which builds flat layers of hexagonal brood cells, spiralling out from a central point [@PH].
 This unusual pattern also provided the inspiration for the algorithm, where the maps are constructed by building out from multiple focal points on the geographic map base in a spiral fashion.
@@
 
-The `sugarbag` package contains a set of functions that help R users to create a hexagon tile map.
-The algorithm presented in the `sugarbag` package operates on a set of simple feature geometry objects , known as `sf` objects[@sf].
-This package allows R users to create `sf` objects by importing polygons stored in various formats.
+The \pkg{sugarbag} package contains a set of functions that help R users to create a hexagon tile map.
+The algorithm presented in the \pkg{sugarbag} package operates on a set of simple feature geometry objects , known as \CRANpkg{sf} objects[@sf].
+This package allows R users to create \pkg{sf} objects by importing polygons stored in various formats.
 Users should provide a set of polygons that define geographic units by their administrative boundaries.
@@
 
-and the development version can be installed from the GitHub repository:
+\noindent and the development version can be installed from the GitHub repository:
 
@@
 
-The set of SA2 polygons for Tasmania, using the 2011 definition of SA2s, is accessed from the `absmapsdata` package.
+The set of SA2 polygons for Tasmania, using the 2011 definition of SA2s, is accessed from the \pkg{absmapsdata} package.
 A single column of the data set is used to identify the unique areas.
@@
 
-The buffer distance, hexagon size, hexagon amount to filter and width of angle are parameters that will be determined within `create_hexmap()`, if they are not provided.
+The buffer distance, hexagon size, hexagon amount to filter and width of angle are parameters that will be determined within \code{create_hexmap()}, if they are not provided.
 They are created as they are needed throughout the following example.
@@
 
-```{r filterprocess, fig.cap = "Illustration of several steps of the algorithm: (a) ... (b) ... (c) ... (d). ", dpi = 600, echo = FALSE, height = 12}
+```{r filterprocess, fig.cap = "Illustration of key steps of the algorithm: (a) full hexagon grid is created first; (b) buffer is applied, shown as dark green circles, to accommodate irregularly shaped regions; (c, d) allocation process, relative the center of Hobart, showing the 8th centroid to be allocated.
+The relationship between Hobart (the cross) and the centroid (the purple triangle) is used to filter the potential locations from the grid within a wedge.
+Hexagons already allocated are shown in black, and the purple circle indicates the hexagon to be assigned to the 8th centroid.", dpi = 600, echo = FALSE, height = 12}
 

### 2020-11-25 kobakian-cook.tex
bib fixes
caption for figure 5

@@
 some disparity in the sizes of the circles.
+
+It is also common to treat all geographic units as equal, so that
+regardless of the population or other information, to generate equal
+size spatial polygons. The Dorling algorithm can beinduced to do this,
+to make equallly sized circles. \citet{MDAC} describes a group of
+alternative maps called ``mosaic cartograms'' for tile displays. The
+geography of the USA has been transformed into a square-binned tile map
+manually and made available in the R package \CRANpkg{statebins}
+\citep{statebins}.The algorithm described below is an automatic layout
+of hexagon tiles, where a continguity constraint is relaxed. This gives
+equal weight to each geographic area even if the population differs.
 
@@
 closer hexagon to the original centroid location. This algorithm is an
-effective start to creating hexagon tile maps for many geographic units.
-This contributes to an extensive body of work that encourages the use of
-alternative map displays for statistical displays of spatial data.
+effective start to automatically creating hexagon tile maps for many
+geographic units. This contributes to an extensive body of work that
+encourages the use of alternative map displays for statistical displays
+of spatial data.
 

### 2020-11-25 kobakian-cook.Rmd
almost ready for submission

@@
 
-The buffer distance, hexagon size, hexagon amount to filter and width of angle are parameters that will be determined within \code{create_hexmap()}, if they are not provided.
+The buffer distance, hexagon size, hexagon amount to filter and width of angle are parameters that will be determined within `create_hexmap()`, if they are not provided.
 They are created as they are needed throughout the following example.

### 2020-11-25 kobakian-cook.tex
almost ready for submission

@@
 
-The algorithm is implemented in the \texttt{sugarbag} package for
+The algorithm is implemented in the \CRANpkg{sugarbag} package for
 \texttt{R}, named after the common name for the \emph{Trigona
@@
 
-The \texttt{sugarbag} package contains a set of functions that help R
-users to create a hexagon tile map. The algorithm presented in the
-\texttt{sugarbag} package operates on a set of simple feature geometry
-objects , known as \texttt{sf} objects\citep{sf}. This package allows R
-users to create \texttt{sf} objects by importing polygons stored in
-various formats. Users should provide a set of polygons that define
-geographic units by their administrative boundaries. The functions
-arrange the geographic units in order of proximity to a set of locations
-provided, such as the centre of major cities. The centroid location of
-each geographic unit is used to measure the proximity. It emphasises the
+The \pkg{sugarbag} package contains a set of functions that help R users
+to create a hexagon tile map. The algorithm presented in the
+\pkg{sugarbag} package operates on a set of simple feature geometry
+objects , known as \CRANpkg{sf} objects\citep{sf}. This package allows R
+users to create \pkg{sf} objects by importing polygons stored in various
+formats. Users should provide a set of polygons that define geographic
+units by their administrative boundaries. The functions arrange the
+geographic units in order of proximity to a set of locations provided,
+such as the centre of major cities. The centroid location of each
+geographic unit is used to measure the proximity. It emphasises the
 major cities as population hubs, rather than emphasizing the size of
@@
 
-and the development version can be installed from the GitHub repository:
+\noindent and the development version can be installed from the GitHub
+repository:
 
@@
 The set of SA2 polygons for Tasmania, using the 2011 definition of SA2s,
-is accessed from the \texttt{absmapsdata} package. A single column of
-the data set is used to identify the unique areas. In this case, the
-unique SA2 names for each SA2 have been used.
+is accessed from the \pkg{absmapsdata} package. A single column of the
+data set is used to identify the unique areas. In this case, the unique
+SA2 names for each SA2 have been used.
 
@@
 \begin{figure}
-\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/filterprocess-1} \caption[Illustration of several steps of the algorithm]{Illustration of several steps of the algorithm: (a) ...
-(b) ...
-(c) ...
-(d).
-}\label{fig:filterprocess}
+\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/filterprocess-1} \caption[Illustration of key steps of the algorithm]{Illustration of key steps of the algorithm: (a) full hexagon grid is created first; (b) buffer is applied, shown as dark green circles, to accommodate irregularly shaped regions; (c, d) allocation process, relative the center of Hobart, showing the 8th centroid to be allocated.
+The relationship between Hobart (the cross) and the centroid (the purple triangle) is used to filter the potential locations from the grid within a wedge.
+Hexagons already allocated are shown in black, and the purple circle indicates the hexagon to be assigned to the 8th centroid.}\label{fig:filterprocess}
 \end{figure}

### 2020-12-09 kobakian-cook.Rmd

@@
 While the representative hexagons are still visible against the black background, the much lower than average rates in rural Australia are less noticeable.
+
+<!-- When the algorithm is applied to the complete set of all Australian Statistical Areas at Level 2 it results in the hexagon tile map display shown in Figure \ref{fig:hexmap}.
+This display highlights the density of Australian capital cities, as it draws attention to the many communities in Sydney, Melbourne and Hobart.
+This display also highlights the disparity in the burden of thyroid cancer for females in the communities of these cities.
+There are several collections of red hexagons in Sydney that represent the communities with much higher rates of diagnosis than the Australian average.
+Brisbane also experiences higher than average rates of diagnosis, but has more orange than red.
+The females in the cities of Adelaide and Perth  show much lower rates of diagnosis.
+-->
+
+<!-- Compared to the choropleth map display, the low rates in the rural Australian communities are no longer dominating the display.
+While the representative hexagons are still visible against the black background, the much lower than average rates in the Northern Territory are less noticeable.
+-->
 

### 2020-12-09 motivating_letter/motivating_letter.Rmd

---
from: Stephanie Kobakian
fromqualifications: MSc
fromemail: srkobakian@outlook.com
fromsignature: sigfile.png
toname: Michael Kane
toaddress: R Journal Editor
opening: Dear Mike,
closing: Best wishes
spacing: 1.4
output: MonashEBSTemplates::letter
---

Please consider my article titled "A Hexagon Tile Map Algorithm for Displaying Spatial Data" for possible publication in the R Journal. The paper describes a new algorithm available in the R package sugarbag, to automatically create hexagon tile maps to display spatial data.

This work is important for making maps, especially for Australia, where displays like choropleth maps and cartograms are inadequate for examining population based statistics geographically. The algorithm has been tested on other countries also, and is generally applicable. Please find the Rmd, tex, pdf, R and data files in the submission zip file.

### 2020-12-09 kobakian-cook.Rmd
Use RJournal commands for text marking

@@
 
-This paper contains a discussion of existing mapping practices.
-This is followed by details of the algorithm.
-The implementation section discusses the algorithm in the `sugarbag` package.
+This paper contains a discussion of Existing Mapping Practices.
+This is followed by details of the Algorithm.
+The implementation section discusses the algorithm in the \pkg{sugarbag} package.
 Finally, the use and benefits of animation are presented.
@@
 First, derive the set of centroids from the polygons provided, then create the grid of hexagon locations.
-These two processes are defined in the blue left column of the flow chart in Figure \ref{fig:sugarbag_flow}.
+These two processes are defined in the blue left column of the flow chart in figure \ref{fig:sugarbag_flow}.
 Each centroid can then be allocated to an available hexagon location.
@@
 
-<!-- The`create_hexmap` function will -->
+<!-- The\code{create\_hexmap} function will -->
 
@@
 
-A user can tweak the parameters of the hexagon map using the additional arguments to the `create_hexmap` function, but these options may affect the speed of the algorithm. 
+A user can tweak the parameters of the hexagon map using the additional arguments to the \code{create\_hexmap} function, but these options may affect the speed of the algorithm. 
 The hexagon size may need adjustments depending on the density of the population; users can provide an appropriate hexagon size and re-run the algorithm.
@@
 The following steps create the hexagon tile map for all the Statistical Areas at Level 2 in Tasmania.
-These steps can be executed by the main function, `create_hexmap`, or can be run separately for more flexibility.
+These steps can be executed by the main function, \code{create\_hexmap}, or can be run separately for more flexibility.
 
 If a user would like to perform each of the steps of the algorithm themselves, the necessary inputs will change for each function.
-For example, the `allocate` function can be used directly when a user wishes to use a set of centroids, rather than polygons.
+For example, the \code{allocate} function can be used directly when a user wishes to use a set of centroids, rather than polygons.
 
@@
 
-The buffer distance, hexagon size, hexagon amount to filter and width of angle are parameters that will be determined within `create_hexmap()`, if they are not provided.
+The buffer distance, hexagon size, hexagon amount to filter and width of angle are parameters that will be determined within \code{create\_hexmap}, if they are not provided.
 They are created as they are needed throughout the following example.
@@
 
-### Step 1: Derive the set of centroid points
+### Derive the set of centroid points
 
-The set of polygons should be provided as an `sf` object, this is a data frame containing a `geometry` column. The `read_shape()` function can assist in creating this object for use in `R`.
+The set of polygons should be provided as an \pkg{sf} object, this is a data frame containing a \code{geometry} column. The \code{read\_shape} function can assist in creating this object for use in R.
 
-The centroids can be derived from an `sf` object using the `create_centroids()` function:
+The centroids can be derived from an \pkg{sf} object using the \code{create\_centroids} function:
 
@@
 
-### Step 2: Create the hexagon grid points
+### Step 1: Create the hexagon grid points
 
 A grid is created to allow tessellation of the hexagons that represent the geographic units.
-For a hexagon tile map, the grid of possible hexagon locations is made using the `create_grid()` function.
+For a hexagon tile map, the grid of possible hexagon locations is made using the \code{create\_grid} function.
 It uses the centroids, the hexagon size and the buffer distance.
-Figure \ref{fig:filterprocess}a) shows the initial locations of grid points created for Tasmania.
+Figure \ref{fig:filterprocess} 1a) shows the initial locations of grid points created for Tasmania.
 
-#### Creating a tessellated grid
+#### (a) Creating a tessellated grid
 
 A set of longitude columns, and latitude rows are created to define the locations of the hexagons.
-The distance between each row and column is the size specified by `hex_size`.
+The distance between each row and column is the size specified by \code{hex\_size}.
 Equally spaced columns are created from the minimum longitude minus the buffer distance, up to the maximum longitude plus the buffer distance.
@@
 A unique hexagon location is created from all intersections of the longitude columns and latitude rows.
-Figure \ref{fig:filterprocess}a shows the hexagon grid after every second latitude row on the grid is shifted right, by half of the hexagon size.
+Figure \ref{fig:filterprocess} 1a) shows the hexagon grid after every second latitude row on the grid is shifted right, by half of the hexagon size.
 
@@
 
-#### Filtering the grid
+#### (b) Filtering the grid
+
+Not all of the grid points will be used, especially if islands result in a large grid space.
+To filter the grid for appropriate hexagon locations for allocation, the \code{create\_grid} function will call the \code{create\_buffer} function.
+It finds the grid points needed to best capture the set of centroids on a hexagon tile map.
+Reducing the buffer can help to decrease the amount of time taken, as there will be less points over the water to consider for each centroid allocation.
 
@@
 The hexagon grid points are kept only if they fall within the rolling average of the minimum and maximum centroid values after accounting for the buffer distance, for each row and column of the grid.
-Figure \ref{fig:filterprocess}b displays remaining hexagon grid points after applying the buffer filter.
+Figure \ref{fig:filterprocess} 1b) displays remaining hexagon grid points after applying the buffer filter.
 The sparsely populated South-West region of National Park has fewer points available in the water compared to the South-East region near the city of Hobart.
@@
 The order for allocation is determined by the distance between the polygon centroid and it's closest focal point.
-For this example, this distance is only calculated for the capital city of Hobart, represented in Figure \ref{fig:filterprocess}c and d as a white cross.
+For this example, this distance is only calculated for the capital city of Hobart, represented in figure \ref{fig:filterprocess} 2a) and 2b) as a white cross.
 
-### Step 3: Allocate each centroid to a hexagon grid point
+### Step 2: Allocate each centroid to a hexagon grid point
 
@@
 
-#### Filter the grid for unassigned hexagon points
+#### (a) Filter the grid for unassigned hexagon points
 
@@
 Keeping only the available hexagon points prevents multiple geographic units from being allocated to the same hexagon.
-This is demonstrated in Figure \ref{fig:filterprocess}c and d by the black hexagons that represent the seven closest polygons to the capital city of Hobart.
+This is demonstrated in figure \ref{fig:filterprocess} 2a) and 2b) by the black hexagons that represent the seven closest polygons to the capital city of Hobart.
 As the allocation process begins for the eighth closest centroid there are seven unavailable hexagon locations.
 
-#### Filter the grid points for those closest to the centroid
+#### (b) Filter the grid points for those closest to the centroid
 
 A selection of possible hexagon locations around the centroid allows only the closest points that are not yet assigned to be considered.
-The number of possible hexagon locations to consider for a centroid is determined by the `hex_filter`.
+The number of possible hexagon locations to consider for a centroid is determined by the hexagon filter.
 This is the maximum amount of hexagons between the centroid and the furthest considered hexagon.
@@
   geom_polygon(aes(x = long, y = lat, group = interaction(sa2_name_2011, polygon)), data = fort_tas, fill = "#D3D3D3", colour = "white", size = 0.1) +
-  theme_void() + coord_equal(ylim = c(-44, -40.1), xlim = c(144.5, 149)) +
+  theme_void() + coord_equal(ylim = c(-45.1, -40.5), xlim = c(144.5, 149)) +
   geom_point(aes(x = hex_long, y = hex_lat), colour = "#55b56c", data = grid, size = 0.5) +
@@
 
-The `width` parameter is used to take a slice of the remaining points.
+The \code{width} parameter is used to take a slice of the remaining points.
 The width is the amount of degrees used on either side of the angle from the focal point to centroid location.
-This uses the angle from the closest capital city, to the current centroid as seen in Figure \ref{fig:filterprocess}c.
+This uses the angle from the closest capital city, to the current centroid as seen in figure \ref{fig:filterprocess} 2a).
 This allows the spatial relationship to be preserved, even when it is allocated to a hexagon that is further from the focal point then the original centroid location.
@@
   geom_point(aes(x=longitude, y = latitude), data = f_centroid, fill = "#beaed4", shape = 25, size = 2) + 
-  theme_void() + coord_equal(xlim = c(146.9, 147.8), ylim = c(-43.35, -42.5)) +
+  theme_void() + coord_equal(xlim = c(146.9, 148), ylim = c(-43.6, -42.5)) +
   # possible choices to select
@@
 cowplot::plot_grid(g1, g2,
-                   f1, f2, labels = c("a", "b", "c", "d"))
+                   f1, f2,
+                   labels = c("1a", "1b", "2a", "2b"))
 ```
@@
 By default the angle filter for the hexagon grid points create plus and minus 30 degree bounds of the angle from the focal point to the geographic centroid.
-This will increase if no points can be found within the `hex_filter` distance.
+This will increase if no points can be found within the \code{hex\_filter} distance.
 The default angle of 30 was chosen to allow the algorithm to find hexagons that best maintained the spatial relationship between the focal point and geographic centroid.
@@
 The rapid decrease in size of the large rural areas can show the large size of their collective landmass.
-The `gganimate` [@gganimate] package can be used to make an animation.
-It connects the polygons for each area in the two displays using the `sf_id` variable, the names of the statistical areas, and creates intermediate displays as they geographic areas shrink or expand to the chosen hexagon size.
+The \pkg{gganimate} [@gganimate] package can be used to make an animation.
+It connects the polygons for each area in the two displays using the \code{sf\_id} variable, the names of the statistical areas, and creates intermediate displays as they geographic areas shrink or expand to the chosen hexagon size.
 
@@
 <!-- implementation -->
- The `sugarbag` package for `R` automates the creation of tessellated hexagon tile maps by providing an algorithm to design these displays.
+
+The hexagon tile map display acknowledges that the amount of residents can differ but each administrative area is equally important.
+This solution uses equally sized areas, and maintain neighbourhood boundary connections.
+The \pkg{sugarbag} package for R automates the creation of tessellated hexagon tile maps by providing an algorithm to design these displays.
 The Australian application preserves spatial relationships, and emphasises capital cities.
 However, similar to the choropleth map display the tessellation does not allow the size of the hexagons to represent another variable.
-The algorithm uses focal points, which are the centers of capital cities for Australia, to determine the order and direction of allocation.
-After careful consideration of the choropleth map, the small geographic inner city areas with high thyroid cancer prevalence may have been missed by viewers, but the hexagon tile map display reveals them.
-The communities in northern Tasmania and the Northern Territory draw less attention because they are smaller and more isolated in the hexagon tile map, but their colour is still comparable with the hexagons in other regions.
+The algorithm is heavily dependent on the focal points used, as this determines the order of allocation.
+With careful consideration of the choropleth map, the small geographic inner city areas may not have been noticed by viewers, but the hexagon tile map display emphasises them.
+The communities in northern Tasmania and the Northern territory do not draw attention because of their size as in the choropleth, but their colour is still noticeably below average when contrasted with the hexagons in New South Wales.
 

### 2020-12-09 kobakian-cook.tex
Use RJournal commands for text marking

@@
 
-This paper contains a discussion of existing mapping practices. This is
-followed by details of the algorithm. The implementation section
-discusses the algorithm in the \texttt{sugarbag} package. Finally, the
-use and benefits of animation are presented.
+This paper contains a discussion of Existing Mapping Practices. This is
+followed by details of the Algorithm. The implementation section
+discusses the algorithm in the \pkg{sugarbag} package. Finally, the use
+and benefits of animation are presented.
 
@@
 grid of hexagon locations. These two processes are defined in the blue
-left column of the flow chart in Figure \ref{fig:sugarbag_flow}. Each
+left column of the flow chart in figure \ref{fig:sugarbag_flow}. Each
 centroid can then be allocated to an available hexagon location. The
@@
 A user can tweak the parameters of the hexagon map using the additional
-arguments to the \texttt{create\_hexmap} function, but these options may
+arguments to the \code{create\_hexmap} function, but these options may
 affect the speed of the algorithm. The hexagon size may need adjustments
@@
 Areas at Level 2 in Tasmania. These steps can be executed by the main
-function, \texttt{create\_hexmap}, or can be run separately for more
+function, \code{create\_hexmap}, or can be run separately for more
 flexibility.
@@
 themselves, the necessary inputs will change for each function. For
-example, the \texttt{allocate} function can be used directly when a user
+example, the \code{allocate} function can be used directly when a user
 wishes to use a set of centroids, rather than polygons.
@@
 angle are parameters that will be determined within
-\texttt{create\_hexmap()}, if they are not provided. They are created as
+\code{create\_hexmap}, if they are not provided. They are created as
 they are needed throughout the following example.
@@
 
-\hypertarget{step-1-derive-the-set-of-centroid-points}{%
-\subsubsection{Step 1: Derive the set of centroid
-points}\label{step-1-derive-the-set-of-centroid-points}}
+\hypertarget{derive-the-set-of-centroid-points}{%
+\subsubsection{Derive the set of centroid
+points}\label{derive-the-set-of-centroid-points}}
 
-The set of polygons should be provided as an \texttt{sf} object, this is
-a data frame containing a \texttt{geometry} column. The
-\texttt{read\_shape()} function can assist in creating this object for
-use in \texttt{R}.
+The set of polygons should be provided as an \pkg{sf} object, this is a
+data frame containing a \code{geometry} column. The \code{read\_shape}
+function can assist in creating this object for use in R.
 
-The centroids can be derived from an \texttt{sf} object using the
-\texttt{create\_centroids()} function:
+The centroids can be derived from an \pkg{sf} object using the
+\code{create\_centroids} function:
 
-\hypertarget{step-2-create-the-hexagon-grid-points}{%
-\subsubsection{Step 2: Create the hexagon grid
-points}\label{step-2-create-the-hexagon-grid-points}}
+\hypertarget{step-1-create-the-hexagon-grid-points}{%
+\subsubsection{Step 1: Create the hexagon grid
+points}\label{step-1-create-the-hexagon-grid-points}}
 
@@
 the geographic units. For a hexagon tile map, the grid of possible
-hexagon locations is made using the \texttt{create\_grid()} function. It
+hexagon locations is made using the \code{create\_grid} function. It
 uses the centroids, the hexagon size and the buffer distance. Figure
-\ref{fig:filterprocess}a) shows the initial locations of grid points
+\ref{fig:filterprocess} 1a) shows the initial locations of grid points
 created for Tasmania.
 
-\hypertarget{creating-a-tessellated-grid}{%
-\paragraph{Creating a tessellated
-grid}\label{creating-a-tessellated-grid}}
+\hypertarget{a-creating-a-tessellated-grid}{%
+\paragraph{(a) Creating a tessellated
+grid}\label{a-creating-a-tessellated-grid}}
 
@@
 locations of the hexagons. The distance between each row and column is
-the size specified by \texttt{hex\_size}. Equally spaced columns are
+the size specified by \code{hex\_size}. Equally spaced columns are
 created from the minimum longitude minus the buffer distance, up to the
@@
 hexagon location is created from all intersections of the longitude
-columns and latitude rows. Figure \ref{fig:filterprocess}a shows the
+columns and latitude rows. Figure \ref{fig:filterprocess} 1a) shows the
 hexagon grid after every second latitude row on the grid is shifted
@@
 
-\hypertarget{filtering-the-grid}{%
-\paragraph{Filtering the grid}\label{filtering-the-grid}}
+\hypertarget{b-filtering-the-grid}{%
+\paragraph{(b) Filtering the grid}\label{b-filtering-the-grid}}
+
+Not all of the grid points will be used, especially if islands result in
+a large grid space. To filter the grid for appropriate hexagon locations
+for allocation, the \code{create\_grid} function will call the
+\code{create\_buffer} function. It finds the grid points needed to best
+capture the set of centroids on a hexagon tile map. Reducing the buffer
+can help to decrease the amount of time taken, as there will be less
+points over the water to consider for each centroid allocation.
 
@@
 the buffer distance, for each row and column of the grid. Figure
-\ref{fig:filterprocess}b displays remaining hexagon grid points after
+\ref{fig:filterprocess} 1b) displays remaining hexagon grid points after
 applying the buffer filter. The sparsely populated South-West region of
@@
 this example, this distance is only calculated for the capital city of
-Hobart, represented in Figure \ref{fig:filterprocess}c and d as a white
-cross.
+Hobart, represented in figure \ref{fig:filterprocess} 2a) and 2b) as a
+white cross.
 
-\hypertarget{step-3-allocate-each-centroid-to-a-hexagon-grid-point}{%
-\subsubsection{Step 3: Allocate each centroid to a hexagon grid
-point}\label{step-3-allocate-each-centroid-to-a-hexagon-grid-point}}
+\hypertarget{step-2-allocate-each-centroid-to-a-hexagon-grid-point}{%
+\subsubsection{Step 2: Allocate each centroid to a hexagon grid
+point}\label{step-2-allocate-each-centroid-to-a-hexagon-grid-point}}
 
@@
 
-\hypertarget{filter-the-grid-for-unassigned-hexagon-points}{%
-\paragraph{Filter the grid for unassigned hexagon
-points}\label{filter-the-grid-for-unassigned-hexagon-points}}
+\hypertarget{a-filter-the-grid-for-unassigned-hexagon-points}{%
+\paragraph{(a) Filter the grid for unassigned hexagon
+points}\label{a-filter-the-grid-for-unassigned-hexagon-points}}
 
@@
 prevents multiple geographic units from being allocated to the same
-hexagon. This is demonstrated in Figure \ref{fig:filterprocess}c and d
-by the black hexagons that represent the seven closest polygons to the
-capital city of Hobart. As the allocation process begins for the eighth
-closest centroid there are seven unavailable hexagon locations.
+hexagon. This is demonstrated in figure \ref{fig:filterprocess} 2a) and
+2b) by the black hexagons that represent the seven closest polygons to
+the capital city of Hobart. As the allocation process begins for the
+eighth closest centroid there are seven unavailable hexagon locations.
 
-\hypertarget{filter-the-grid-points-for-those-closest-to-the-centroid}{%
-\paragraph{Filter the grid points for those closest to the
-centroid}\label{filter-the-grid-points-for-those-closest-to-the-centroid}}
+\hypertarget{b-filter-the-grid-points-for-those-closest-to-the-centroid}{%
+\paragraph{(b) Filter the grid points for those closest to the
+centroid}\label{b-filter-the-grid-points-for-those-closest-to-the-centroid}}
 
@@
 number of possible hexagon locations to consider for a centroid is
-determined by the \texttt{hex\_filter}. This is the maximum amount of
-hexagons between the centroid and the furthest considered hexagon. It is
-used to subset possible grid points to only those surrounding the
-polygon centroid within an appropriate range. A smaller distance will
-increase speed, but can decrease accuracy when width of the angle
-increases.
+determined by the hexagon filter. This is the maximum amount of hexagons
+between the centroid and the furthest considered hexagon. It is used to
+subset possible grid points to only those surrounding the polygon
+centroid within an appropriate range. A smaller distance will increase
+speed, but can decrease accuracy when width of the angle increases.
 
@@
 
-The \texttt{width} parameter is used to take a slice of the remaining
+The \code{width} parameter is used to take a slice of the remaining
 points. The width is the amount of degrees used on either side of the
 angle from the focal point to centroid location. This uses the angle
-from the closest capital city, to the current centroid as seen in Figure
-\ref{fig:filterprocess}c.~This allows the spatial relationship to be
+from the closest capital city, to the current centroid as seen in figure
+\ref{fig:filterprocess} 2a). This allows the spatial relationship to be
 preserved, even when it is allocated to a hexagon that is further from
@@
 to the geographic centroid. This will increase if no points can be found
-within the \texttt{hex\_filter} distance. The default angle of 30 was
+within the \code{hex\_filter} distance. The default angle of 30 was
 chosen to allow the algorithm to find hexagons that best maintained the
@@
 size of the large rural areas can show the large size of their
-collective landmass. The \texttt{gganimate} \citep{gganimate} package
-can be used to make an animation. It connects the polygons for each area
-in the two displays using the \texttt{sf\_id} variable, the names of the
+collective landmass. The \pkg{gganimate} \citep{gganimate} package can
+be used to make an animation. It connects the polygons for each area in
+the two displays using the \code{sf\_id} variable, the names of the
 statistical areas, and creates intermediate displays as they geographic
@@
 
-The \texttt{sugarbag} package for \texttt{R} automates the creation of
+The hexagon tile map display acknowledges that the amount of residents
+can differ but each administrative area is equally important. This
+solution uses equally sized areas, and maintain neighbourhood boundary
+connections. The \pkg{sugarbag} package for R automates the creation of
 tessellated hexagon tile maps by providing an algorithm to design these
@@
 display the tessellation does not allow the size of the hexagons to
-represent another variable. The algorithm uses focal points, which are
-the centers of capital cities for Australia, to determine the order and
-direction of allocation. After careful consideration of the choropleth
-map, the small geographic inner city areas with high thyroid cancer
-prevalence may have been missed by viewers, but the hexagon tile map
-display reveals them. The communities in northern Tasmania and the
-Northern Territory draw less attention because they are smaller and more
-isolated in the hexagon tile map, but their colour is still comparable
-with the hexagons in other regions.
+represent another variable. The algorithm is heavily dependent on the
+focal points used, as this determines the order of allocation. With
+careful consideration of the choropleth map, the small geographic inner
+city areas may not have been noticed by viewers, but the hexagon tile
+map display emphasises them. The communities in northern Tasmania and
+the Northern territory do not draw attention because of their size as in
+the choropleth, but their colour is still noticeably below average when
+contrasted with the hexagons in New South Wales.
 

### 2020-12-09 kobakian-cook.Rmd
CRANpkg ref added

@@
 This is followed by details of the Algorithm.
-The implementation section discusses the algorithm in the \pkg{sugarbag} package.
+The implementation section discusses the algorithm in the \CRANpkg{sugarbag} package.
 Finally, the use and benefits of animation are presented.
@@
 
-The algorithm is implemented in the \CRANpkg{sugarbag} package for `R`, named after the common name for the *Trigona carbonaria* bee – a species which builds flat layers of hexagonal brood cells, spiralling out from a central point [@PH].
+The algorithm is implemented in the \pkg{sugarbag} package for `R`, named after the common name for the *Trigona carbonaria* bee – a species which builds flat layers of hexagonal brood cells, spiralling out from a central point [@PH].
 This unusual pattern also provided the inspiration for the algorithm, where the maps are constructed by building out from multiple focal points on the geographic map base in a spiral fashion.
@@
 
-The results from various steps in the process are illustrated in Figure 5.
+The results from various steps in the process are illustrated in Figure \ref{fig:filterprocess}.
 

### 2020-12-09 kobakian-cook.tex
CRANpkg ref added

@@
 followed by details of the Algorithm. The implementation section
-discusses the algorithm in the \pkg{sugarbag} package. Finally, the use
-and benefits of animation are presented.
+discusses the algorithm in the \CRANpkg{sugarbag} package. Finally, the
+use and benefits of animation are presented.
 
@@
 
-The algorithm is implemented in the \CRANpkg{sugarbag} package for
+The algorithm is implemented in the \pkg{sugarbag} package for
 \texttt{R}, named after the common name for the \emph{Trigona
@@
 The results from various steps in the process are illustrated in Figure
-5.
+\ref{fig:filterprocess}.
 

### 2020-12-17 kobakian-cook.Rmd
replace figure five labels

@@
 
-```{r filterprocess, fig.cap = "Illustration of key steps of the algorithm: (a) full hexagon grid is created first; (b) buffer is applied, shown as dark green circles, to accommodate irregularly shaped regions; (c, d) allocation process, relative the center of Hobart, showing the 8th centroid to be allocated.
+```{r filterprocess, fig.cap = "Illustration of key steps of the algorithm: (1a) full hexagon grid is created first; (1b) buffer is applied, shown as dark green circles, to accommodate irregularly shaped regions; (2a, 2b) allocation process, relative the center of Hobart, showing the 8th centroid to be allocated.
 The relationship between Hobart (the cross) and the centroid (the purple triangle) is used to filter the potential locations from the grid within a wedge.
@@
 
-## Discussion and Conclusion {#conclusion-03}
+## Discussion
 

### 2020-12-17 kobakian-cook.tex
replace figure five labels

@@
 \begin{figure}
-\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/filterprocess-1} \caption[Illustration of key steps of the algorithm]{Illustration of key steps of the algorithm: (a) full hexagon grid is created first; (b) buffer is applied, shown as dark green circles, to accommodate irregularly shaped regions; (c, d) allocation process, relative the center of Hobart, showing the 8th centroid to be allocated.
+\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/filterprocess-1} \caption[Illustration of key steps of the algorithm]{Illustration of key steps of the algorithm: (1a) full hexagon grid is created first; (1b) buffer is applied, shown as dark green circles, to accommodate irregularly shaped regions; (2a, 2b) allocation process, relative the center of Hobart, showing the 8th centroid to be allocated.
 The relationship between Hobart (the cross) and the centroid (the purple triangle) is used to filter the potential locations from the grid within a wedge.
@@
 
-\hypertarget{conclusion-03}{%
-\subsection{Discussion and Conclusion}\label{conclusion-03}}
+\hypertarget{discussion}{%
+\subsection{Discussion}\label{discussion}}
 

### 2020-12-18 motivating_letter/motivating_letter.Rmd
clean for submission

@@
 from: Stephanie Kobakian
-fromqualifications: MSc
+fromqualifications: MPhil
+fromtitle: Research Assistant
 fromemail: srkobakian@outlook.com
@@
 toaddress: R Journal Editor
-opening: Dear Mike,
-closing: Best wishes
+opening: Dear Michael,
+closing: Warm regards
 spacing: 1.4

### 2022-05-16 review/response.Rmd
reviews and start on response

---
title: "Response to review"
author: "Stephanie Kobakian and Dianne Cook"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Thank you for the review of our article. These are the changes that we have made in response. The review comment is indented italic, and our response follows in regular text.

First, we have reformatted the paper to use the `rjtools` package.

We have made a simpler code example that will run from start to end of the algorithm, but also kept the full Australia example created from data provided with the source files of the article.

> *The article is clearly written and does a good job of discussing previous mapping approaches as well as their limitations. The figures were useful in this regard, as they make the textual discussion in the background sections easily understandable even for users less experienced in geography. The flowchart summarizing the algorithm was also useful. I would suggest some minor substantive revisions to improve the substance of the background as well as the clarity of the package’s functionality. First, the discussion of the pros and cons of choropleth maps and various forms of cartograms was good, but I would like more information about the value of hexagons over other shapes. Why not circles or squares or triangles? Hexagons do have advantages, but adding a few more sentences about this would be useful, especially for non-specialist users. Second, other R packages for mapping can be cited, including cartogram (Jeworutzki et al 2020) and tilemaps (McNeill and Hale 2017). Third, I might recommend putting the “implementation” section above the “user choices” section. Fourth, and this is probably a personal preference, the implementation section could be improved by adding a simple table listing the main functions in the package and a brief summary of what they do. This makes the information more easily accessible to the reader. Fifth, the implementation section provides a running example, but please include some sample code directly in the article. This makes the package more accessible to users. It is not necessary to include all code of course, but some of the more important functions that produce a core visualization should be provided directly in the text.*

> *There were also a few minor typos that should be fixed (e.g., “tyroid” in the caption of Figure 3 and the comma beginning the third line of the second paragraph of the “implementation” section). The last two sentences of the first paragraph of the discussion section are also identical to the next two sentences. Overall, these revisions to the article are relatively minor and manageable.*

> *The package itself seems to be reasonably well-organized, the code is clean, and there is sufficient built-in documentation. The progress bars are also useful. I don’t have any major suggestions for improving the functionality of the package itself, other than the fact that I couldn’t reproduce the example maps in the implementation section because the data were not self-contained. The article says that the example is reproducible using data from the absmapsdata package, but in the provided RMD file the object “fort_aus” can be traced back to the “SIR Downloadable Data.csv” dataset, which is from an external source (and also not available on the github repo). Forgive me if I am missing something here (and it is possible that I am). If not, these SIR data should be embedded or example code fixed to not be dependent on the SIR data so that the illustrative maps are reproducible.*

### 2022-05-16 kobakian-cook.Rmd
gganimate as CRAN pkg
reviews and start on response

@@
 grid <- create_grid(centroids = centroids,
-                    hex_size = 0.2,
+                    hex_size = 0.1,
                     buffer_dist = 5)
@@
 )
-save(aus_hexmap, file = "data/aus_hexmap.rda") }
+save(aus_hexmap, file = "data/aus_hexmap.rda") 
+}
 
@@
 sa2thyroid_ERP <- sa2thyroid_ERP %>% 
-  mutate(sva = sqrt(as.numeric(Population)/as.numeric(albers_sqkm)))
+  #mutate(sva = sqrt(as.numeric(Population)/as.numeric(albers_sqkm)))
+  mutate(sva = sqrt(as.numeric(Population)/as.numeric(areasqkm_2011)))
 
@@
     st_as_sf()
-save(cont, file = "data/cont.rda") }
+  save(cont, file = "data/cont.rda") 
+}
 
@@
   geom_sf(aes(fill = SIR), colour = "grey", size = 0.01) + 
-  scale_fill_identity() + guides(fill=FALSE) +
+  scale_fill_identity() + guides(fill = "none") +
   theme_map() + ggtitle("a")
@@
                           st_as_sf()
-save(ncont, file = "data/ncont.rda")}
+  save(ncont, file = "data/ncont.rda")
+}
 
@@
   scale_fill_identity() + 
-  guides(fill=FALSE) +
+  guides(fill = "none") +
   theme_map() + ggtitle("b")
@@
   scale_fill_identity() +
-  guides(fill = FALSE) +
+  guides(fill = "none") +
   theme_map() + ggtitle("c")
@@
 The rapid decrease in size of the large rural areas can show the large size of their collective landmass.
-The \pkg{gganimate} [@gganimate] package can be used to make an animation.
+The \CRANpkg{gganimate} [@gganimate] package can be used to make an animation.
 It connects the polygons for each area in the two displays using the \code{sf\_id} variable, the names of the statistical areas, and creates intermediate displays as they geographic areas shrink or expand to the chosen hexagon size.

### 2022-05-16 kobakian-cook.tex
gganimate as CRAN pkg
reviews and start on response

@@
 size of the large rural areas can show the large size of their
-collective landmass. The \pkg{gganimate} \citep{gganimate} package can
-be used to make an animation. It connects the polygons for each area in
-the two displays using the \code{sf\_id} variable, the names of the
+collective landmass. The \CRANpkg{gganimate} \citep{gganimate} package
+can be used to make an animation. It connects the polygons for each area
+in the two displays using the \code{sf\_id} variable, the names of the
 statistical areas, and creates intermediate displays as they geographic
@@
 %
-\\\href{mailto:stephanie.kobakian@monash.edu}{\nolinkurl{stephanie.kobakian@monash.edu}}
+\href{mailto:stephanie.kobakian@monash.edu}{\nolinkurl{stephanie.kobakian@monash.edu}}%
 }
@@
 %
-\\\href{mailto:dicook@monash.edu}{\nolinkurl{dicook@monash.edu}}
+\href{mailto:dicook@monash.edu}{\nolinkurl{dicook@monash.edu}}%
 }
@@
 %
-\\\href{mailto:earl.duncan@qut.edu.au}{\nolinkurl{earl.duncan@qut.edu.au}}
+\href{mailto:earl.duncan@qut.edu.au}{\nolinkurl{earl.duncan@qut.edu.au}}%
 }

### 2022-05-17 version1/kobakian-cook.R
conversion to rjtools format

@@ -1,0 +1,631 @@
+# Young statisticians conference presentation plots
+
+library(absmapsdata)
+library(tidyverse)
+library(cartogram)
+library(ggthemes)
+library(cowplot)
+library(sf)
+library(sp)
+
+### Theme set up
+
+invthm <- theme_map() + 
+  theme(
+    panel.background = element_rect(fill = "transparent", colour = NA), 
+    plot.background = element_rect(fill = "transparent", colour = NA),
+    legend.background = element_rect(fill = "transparent", colour = NA),
+    legend.key = element_rect(fill = "transparent", colour = NA),
+    text = element_text(colour = "white"),
+    axis.text = element_text(colour = "white")
+  )
+
+## States of Australia
+
+states <- absmapsdata::state2011 %>% 
+  filter(state_name_2011 != "Other Territories")
+
+###############################################################################
+###########################        ABS AREAS        ###########################
+## sa2
+sa2 <- absmapsdata::sa22011 %>% 
+  filter(state_name_2011 != "Other Territories") %>% st_transform(., crs = 3112)
+
+sa2_map <- ggplot(sa2) + 
+  geom_sf(aes(fill = albers_sqkm)) +
+  scale_fill_distiller(type = "seq", palette = "BuGn",  direction = 1, na.value = "light grey") + 
+  theme_void() +
+  coord_sf(crs = 3112) +
+   theme(legend.position ="left", legend.title = element_text("Area (sqkm)"))
+
+ggsave(filename = "figures/aus_sa2.png", plot = sa2_map,
+  device = "png", bg = "transparent", dpi = 300,  width = 10, height = 8)
+
+
+###############################################################################
+###########################     CARTOGRAMS
+# 
+# ERP <- read_csv("data/ERP.csv")
+# 
+# ERP_sa4 <- ERP %>% filter(`Geography Level` == "Statistical Area Level 4", Time == 2011) %>% arrange(`Geography Level`)
+# 
+# aus_ggcont <- ggplot(ERP_sa4) + 
+#   geom_sf(aes(fill = `Age-standardised rate (per 100,000)`)) + 
[…]

### 2022-05-21 kobakian-cook.Rmd
Begin content changes suggested in review
First draft of edits

@@
 bibliography: kobakian-cook.bib
-output: rticles::rjournal_article
+output: rjtools::rjournal_web_article
 editor_options: 
@@
 
-Alternative mapping methods, like cartograms, allow increased understanding of the spatial distribution of a variable across the population, by fairly representing the population in each administrative area [@TAAM].
+Alternative mapping methods, like cartograms implemented in \CRANpkg{cartogram}, allow increased understanding of the spatial distribution of a variable across the population, by fairly representing the population in each administrative area [@TAAM].
 This acknowledges that the number of residents can be different and also recognises that each area, or person within it is equally important.
@@
 There are several established alternative visualisation methods.
-Tile maps, rectangular cartograms [@ORC] and Dorling cartograms [@ACTUC] all use one simple shape to represent each geographic unit.
+Rectangular cartograms [@ORC] and Dorling cartograms [@ACTUC] implemented in \pkg{cartogram} and tile maps implemented in \CRANpkg{tilemaps}, all use one simple shape to represent each geographic unit.
 They all minimise the emphasis on the size or shape of the geographic areas.
@@
 It is also common to treat all geographic units as equal, so that regardless of the population or other information, to generate equal size spatial polygons.
-The Dorling algorithm can beinduced to do this, to make equallly sized circles.
+The Dorling algorithm can be induced to do this, to make equallly sized circles.
 @MDAC describes a group of alternative maps called "mosaic cartograms" for tile displays.
@@
 This gives equal weight to each geographic area even if the population differs.
+
+The nature of Australian population boundaries means that there are many connecting neighbours of population areas.
+This solution was designed to visualise Australian population analysis, inspired by tile maps three sided triangles and four sided squares were considered, but this would not have allowed sufficient neighbours to connect.
+Hexagon tile maps utilise the tessellating features of hexagons to maximise the data ink and allow connectivity between six potential neighbours.
+Hexagons allow the alignment of geographic borders, this aides in comparison of colour values.
 
@@
 
-```{r hexmap, fig.cap = "A hexagon tile map of female tyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1.
+```{r hexmap, fig.cap = "A hexagon tile map of female thyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1.
 The high incidence in several of the metropolitan regions (Brisbane, Sydney and Perth) can now be seen, along with numerous isolated spots."}
@@
 
+```
+centroids <- create_centroids(
+  shp_sf = sa2 %>% filter(state_name_2011 == "Tasmania"), 
+  sf_id = "sa2_name_2011")
+```
 #### (a) Creating a tessellated grid
@@
 Figure \ref{fig:filterprocess} 1a) shows the hexagon grid after every second latitude row on the grid is shifted right, by half of the hexagon size.
+
+```
+grid <- create_grid(centroids = centroids, hex_size = 0.2, buffer_dist = 2)
+```
 
@@
 
+```
+hex_allocated <- allocate(centroids = centroids,
+                          sf_id = "SA2_NAME16",
+                          hex_grid = grid,
+                          hex_size = 0.2, # same size used in create_grid
+                          hex_filter = 10,
+                          use_neighbours = tas_sa2,
+                          focal_points = capital_cities,
+                          # same column used in create_centroids
+                          width = 30, verbose = TRUE)
+```
+
 ```{r centroids, eval = FALSE}

### 2022-05-21 review/response.Rmd
Draft response to reviewers

@@
 Second, other R packages for mapping can be cited, including cartogram (Jeworutzki et al 2020) and tilemaps (McNeill and Hale 2017).
-Third, I might recommend putting the “implementation” section above the “user choices” section.
+*
+
+Thank you for the affirmation of the use of written and visual descriptions.
+A small paragraph has been included at the end of Existing Mapping Practices to clearly describe the benefits of the connectivity of hexagons as per your suggestion.
+References to the R package implementations of other Mapping Practice have now been made explicit.
+
+> *Third, I might recommend putting the “implementation” section above the “user choices” section.
 Fourth, and this is probably a personal preference, the implementation section could be improved by adding a simple table listing the main functions in the package and a brief summary of what they do.
@@
 If not, these SIR data should be embedded or example code fixed to not be dependent on the SIR data so that the illustrative maps are reproducible.*
+
+The implementation section now focusses only on Tasmania, for the sake of speed.
+We have now included the R data file for a completed Australian thyroid hexagon map.
+There are two sets of data required to make the Australian thyroid map, the shape file and SIR data.
+The SIR Downloadable Data csv file can be found in the data folder.

### 2022-06-02 review/response.Rmd
links now working and more tweakig of paper

@@
 
+Done.
+
 > *There were also a few minor typos that should be fixed (e.g., “tyroid” in the caption of Figure 3 and the comma beginning the third line of the second paragraph of the “implementation” section).
@@
 Overall, these revisions to the article are relatively minor and manageable.*
+
+Fixed, and paper has been carefully proofread again.
 
@@
 
-The implementation section now focusses only on Tasmania, for the sake of speed.
-We have now included the R data file for a completed Australian thyroid hexagon map.
-There are two sets of data required to make the Australian thyroid map, the shape file and SIR data.
-The SIR Downloadable Data csv file can be found in the data folder.
+For improving the speed to knit the paper the implementation section uses only the small data set corresponding to Tasmania.
+
+The data files for the full Australia thyroid choropleth and hexagon map are provided so that the Figures 1 and 2 can be produced quickly.
+The code to produce these data sets is provided, so that the interested reader can follow the entire hexagon map generating process.
+There are two sets of data required to make the Australian thyroid map, the shape file and thyroid SIR data.
+The `SIR Downloadable Data.csv` file is located in the data folder.
+The shape file is the `sa22011` data from the `absmapsdata` package, which would need to be installed with `remotes::install_github("wfmackey/absmapsdata")`.

### 2022-06-02 kobakian-cook.Rmd
links now working and more tweakig of paper

@@
 This can cause some values to be emphasised over others, and allows choropleth map displays to misrepresent the spatial distributions of human related statistics due to area-size bias [@BCM].
-Figure \ref{fig:choro} is a choropleth map that uses colour to display the estimated standardised incidence ratios (SIRs) of thyroid cancer for females, in each of the Statistical Areas at Level 2 (SA2) used by the @abs2011.
+Figure \@ref(fig:choro) is a choropleth map that uses colour to display the estimated standardised incidence ratios (SIRs) of thyroid cancer for females, in each of the Statistical Areas at Level 2 (SA2) used by the @abs2011.
 The Australian choropleth map display draws attention to the expanse of dark and light blue areas across the rural communities in all states.
@@
 
-This paper contains a discussion of Existing Mapping Practices.
-This is followed by details of the Algorithm.
-The implementation section discusses the algorithm in the \CRANpkg{sugarbag} package.
-Finally, the use and benefits of animation are presented.
+This paper contains a discussion of existing mapping practices, followed by details of the algorithm.
+The implementation section explains the algorithm available in the \CRANpkg{sugarbag} package.
+How to utilise animation with the hexagon map is described.
+The paper finishes with a summary and possible new directions for the algorithm.
 
-## Existing Mapping Practices
+## Existing mapping practices
 
@@
 This collection of communities presents an opportunity for explicit map transformations to improve communication of spatial distributions [@CBATCC].
-In Figure \ref{fig:tas_displays} the choropleth map can be seen underneath each alternative map display to allow for comparisons to be made.
+In Figure \@ref(fig:tasdisplays) the choropleth map can be seen underneath each alternative map display to allow for comparisons to be made.
 
@@
 These alternative map displays focus on the relationship between neighbours, attempting to preserve connections, and disregard the unique shapes of the administrative boundaries.
-Figure \ref{fig:tas_displays} shows a collection of alternative map displays, this includes a) a contiguous cartogram, b) a non-contiguous cartogram, and c) a Dorling cartogram.
+Figure \@ref(fig:tasdisplays) shows a collection of alternative map displays, this includes a) a contiguous cartogram, b) a non-contiguous cartogram, and c) a Dorling cartogram.
 
@@
   scale_fill_identity() + guides(fill = "none") +
-  theme_map() + ggtitle("a")
+  theme_map() #+ ggtitle("a")
 #tas_ggcont
@@
   guides(fill = "none") +
-  theme_map() + ggtitle("b")
+  theme_map() #+ ggtitle("b")
 #tas_ggncont
@@
   guides(fill = "none") +
-  theme_map() + ggtitle("c")
+  theme_map() #+ ggtitle("c")
 #tas_ggdorl
@@
 
-```{r tas_displays, width = 10, height = 3, fig.cap = "The three displays show alternative maps of the Australian state of Tasmania at SA2 level: (a) contiguous cartogram, (b) non-contiguous cartogram and (c) Dorling cartogram of Tasmania.
+```{r tasdisplays, out.width="100%", fig.width = 8, fig.height = 3, layout = "l-body", fig.cap = "The three displays show alternative maps of the Australian state of Tasmania at SA2 level: (a) contiguous cartogram, (b) non-contiguous cartogram and (c) Dorling cartogram of Tasmania.
 The contiguous cartogram looks like the state has an hourglass figure, while the non-contiguous cartogram shrinks areas into invisibility.
 The Dorling expands the metropolitan regions."}
-library(gridExtra)
-grid.arrange(tas_ggcont, tas_ggncont, tas_ggdorl, ncol=3)
+#library(gridExtra)
+#grid.arrange(tas_ggcont, tas_ggncont, tas_ggdorl, ncol=3)
+cowplot::plot_grid(tas_ggcont, 
+                   tas_ggncont, 
+                   tas_ggdorl, ncol=3,
+                   labels = c("a", "b", "c"))
+
 ```
@@
 The connected communities can be recognised by allowing the boundaries to maintain connection in the transformed display.
-The contiguous cartogram displayed in Figure \ref{fig:tas_displays}a) draws attention to smaller geographic units when they are rescaled according to the population [@DMAHP].
+The contiguous cartogram displayed in Figure \@ref(fig:tasdisplays)a draws attention to smaller geographic units when they are rescaled according to the population [@DMAHP].
 These new shapes can now be coloured to represent a second variable.
@@
 
-The non-contiguous cartogram in Figure \ref{fig:tas_displays}b) also uses the population to rescale the geographic units.
+The non-contiguous cartogram in Figure \@ref(fig:tasdisplays)b also uses the population to rescale the geographic units.
 Unlike the contiguous cartogram, the SA2 areas maintain their geographic shape, but they may not retain the connection with their neighbours.
@@
 The Dorling cartogram presents each geographic unit as a circle, the size of the circle is scaled according to the population value of each area [@ACTUC].
-Figure \ref{fig:tas_displays}c) shows the Tasmania SA2 areas as an individual circle located as close as possible to the geographic centroid location.
-This map draws attention to the collection of coastal cities in Tasmania that were not apparent in Figure \ref{fig:tas_displays} a), or b).
+Figure \@ref(fig:tasdisplays)c shows the Tasmania SA2 areas as an individual circle located as close as possible to the geographic centroid location.
+This map draws attention to the collection of coastal cities in Tasmania that were not apparent in Figure \@ref(fig:tasdisplays) a or b.
 This display also highlights that the approximation of equal population is not easy to fulfil, as there is some disparity in the sizes of the circles.
@@
 
-The result of the algorithm applied to the same data represented in Figure \ref{fig:choro} shows rates of thyroid cancer for females in each of the SA2 areas of Australia as hexagons in Figure \ref{fig:hexmap}.
-The difference to the choropleth map in Figure \ref{fig:choro} are clear.
+The result of the algorithm applied to the same data represented in Figure \@ref(fig:choro) shows rates of thyroid cancer for females in each of the SA2 areas of Australia as hexagons in Figure \@ref(fig:hexmap).
+The difference to the choropleth map in Figure \@ref(fig:choro) are clear.
 Now the higher thyroid cancer incidence in the densely populated areas in Sydney, Brisbane and Perth are visible.
@@
 
-Figure \ref{fig:hexmap} highlights the density of Australian capital cities, as it draws attention to the many communities in Sydney, Melbourne and Hobart.
+Figure \@ref(fig:hexmap) highlights the density of Australian capital cities, as it draws attention to the many communities in Sydney, Melbourne and Hobart.
 This display also highlights the disparity in the burden of thyroid cancer for females in the communities of these cities.
@@
 
-Compared to the choropleth map display in Figure \ref{fig:choro}, the low rates in the rural Australian communities are no longer dominating the display.
+Compared to the choropleth map display in Figure \@ref(fig:choro), the low rates in the rural Australian communities are no longer dominating the display.
 While the representative hexagons are still visible against the black background, the much lower than average rates in rural Australia are less noticeable.
@@
 
-There are several key steps in the creation of the hexagon tile map as described in the flow chart in Figure \ref{fig:sugarbag_flow}.
+There are several key steps in the creation of the hexagon tile map as described in the flow chart in Figure \@ref(fig:sugarbagflow).
 First, derive the set of centroids from the polygons provided, then create the grid of hexagon locations.
-These two processes are defined in the blue left column of the flow chart in figure \ref{fig:sugarbag_flow}.
+These two processes are defined in the blue left column of the flow chart in figure \@ref(fig:sugarbagflow).
 Each centroid can then be allocated to an available hexagon location.
-The steps for the allocation process are detailed in the right column of Figure \ref{fig:sugarbag_flow}.
+The steps for the allocation process are detailed in the right column of Figure \@ref(fig:sugarbagflow).
 There are several filter steps to speed the process of selecting an appropriate hexagon to represent each geographic unit.
@@
 
-\begin{figure}
-\includegraphics[width=14cm]{figs/sugarbag flow.png}
-\caption{\label{fig:sugarbag_flow}A flow diagram detailing the steps taken to create a hexagon tile map.
-There are two basic processes, one to make the grid, and the other to allocate centroids to grid points.}
-\end{figure}
-
-### User choices
-
-<!-- The\code{create\_hexmap} function will -->
-
-<!-- Derive the centroids of the geographic units to calculate a grid of possible hexagon locations, and allocate each geographic unit to a single hexagon. -->
-
-Only two inputs are necessary to begin the algorithm; the shapefile, and the ID variable. The ID variable should uniquely identify each geographic unit in the shapefile.
-
-The centroids are derived from the shapefile.
-The amount of centroids within the geographic map is used to determine an appropriate hexagon size if one is not provided.
-The derived centroids are a necessary input for an appropriate grid to be constructed.
-Each grid point is located a hexagon size distance from the next closest point in all six directions.
-The grid will initially cover the entire map space, encompassing all the centroid locations and will extend in all directions to the extent of the buffer distance.
-This buffer distance can be helpful to account for densely populated coastal areas, allowing the hexagon locations to spread beyond the coastline, over the sea.
-
-The centroid set and hexagon tile map grid are necessary for the allocation process.
-Additionally, a set of reference locations can be provided as focal points, typically compact and/or densely populated areas such as major cities.
-The algorithm will use the focal points to create the order of allocation, prioritising the closest centroid locations to the focal points.
-The user can also specify the variable that should be used to determine the order for the allocation.
-
-When allocating representative hexagons, the width parameter can be used to determine the flexibility of positioning.
-Using the relationship with the nearest focal point, a larger width parameter will increase the amount of available hexagons nearer to the original centroid of the geographic unit.
-A smaller width will maintain the orientation from the focal point to the centroid when selecting the hexagon location.
-However, this could mean it is placed further away.
+```{r sugarbagflow, out.width = "100%", layout = "l-body-outset", fig.cap = "A flow diagram detailing the steps taken to create a hexagon tile map.
+There are two basic processes, one to make the grid, and the other to allocate centroids to grid points.", fig.alt="The steps of the algorithm to creating a hexagon grid with buffer, and the allocation of spatial polygon centroids to hexagon.
+This is the same information as provided in the text of the paper."}
+knitr::include_graphics("figs/sugarbag_flow.png")
+```
 
@@
 
-The results from various steps in the process are illustrated in Figure \ref{fig:filterprocess}.
+The results from various steps in the process are illustrated in Figure \@ref(fig:filterprocess).
 
@@
 It uses the centroids, the hexagon size and the buffer distance.
-Figure \ref{fig:filterprocess} 1a) shows the initial locations of grid points created for Tasmania.
+Figure \@ref(fig:filterprocess) 1a shows the initial locations of grid points created for Tasmania.
 
@@
 A unique hexagon location is created from all intersections of the longitude columns and latitude rows.
-Figure \ref{fig:filterprocess} 1a) shows the hexagon grid after every second latitude row on the grid is shifted right, by half of the hexagon size.
+Figure \@ref(fig:filterprocess) 1a shows the hexagon grid after every second latitude row on the grid is shifted right, by half of the hexagon size.
 
@@
 The hexagon grid points are kept only if they fall within the rolling average of the minimum and maximum centroid values after accounting for the buffer distance, for each row and column of the grid.
-Figure \ref{fig:filterprocess} 1b) displays remaining hexagon grid points after applying the buffer filter.
+Figure \@ref(fig:filterprocess) 1b displays remaining hexagon grid points after applying the buffer filter.
 The sparsely populated South-West region of National Park has fewer points available in the water compared to the South-East region near the city of Hobart.
@@
 The order for allocation is determined by the distance between the polygon centroid and it's closest focal point.
-For this example, this distance is only calculated for the capital city of Hobart, represented in figure \ref{fig:filterprocess} 2a) and 2b) as a white cross.
+For this example, this distance is only calculated for the capital city of Hobart, represented in Figure \@ref(fig:filterprocess) 2a and 2b as a white cross.
 
@@
 Keeping only the available hexagon points prevents multiple geographic units from being allocated to the same hexagon.
-This is demonstrated in figure \ref{fig:filterprocess} 2a) and 2b) by the black hexagons that represent the seven closest polygons to the capital city of Hobart.
+This is demonstrated in Figure \@ref(fig:filterprocess) 2a and 2b by the black hexagons that represent the seven closest polygons to the capital city of Hobart.
 As the allocation process begins for the eighth closest centroid there are seven unavailable hexagon locations.
@@
 The width is the amount of degrees used on either side of the angle from the focal point to centroid location.
-This uses the angle from the closest capital city, to the current centroid as seen in figure \ref{fig:filterprocess} 2a).
+This uses the angle from the closest capital city, to the current centroid as seen in Figure \@ref(fig:filterprocess) 2a.
 This allows the spatial relationship to be preserved, even when it is allocated to a hexagon that is further from the focal point then the original centroid location.
@@
 
+### User choices
+
+<!-- The\code{create\_hexmap} function will -->
+
+<!-- Derive the centroids of the geographic units to calculate a grid of possible hexagon locations, and allocate each geographic unit to a single hexagon. -->
+
+Only two inputs are necessary to begin the algorithm; the shapefile, and the ID variable. The ID variable should uniquely identify each geographic unit in the shapefile.
+
+The centroids are derived from the shapefile.
+The amount of centroids within the geographic map is used to determine an appropriate hexagon size if one is not provided.
+The derived centroids are a necessary input for an appropriate grid to be constructed.
+Each grid point is located a hexagon size distance from the next closest point in all six directions.
+The grid will initially cover the entire map space, encompassing all the centroid locations and will extend in all directions to the extent of the buffer distance.
+This buffer distance can be helpful to account for densely populated coastal areas, allowing the hexagon locations to spread beyond the coastline, over the sea.
+
+The centroid set and hexagon tile map grid are necessary for the allocation process.
+Additionally, a set of reference locations can be provided as focal points, typically compact and/or densely populated areas such as major cities.
+The algorithm will use the focal points to create the order of allocation, prioritising the closest centroid locations to the focal points.
+The user can also specify the variable that should be used to determine the order for the allocation.
+
+When allocating representative hexagons, the width parameter can be used to determine the flexibility of positioning.
+Using the relationship with the nearest focal point, a larger width parameter will increase the amount of available hexagons nearer to the original centroid of the geographic unit.
+A smaller width will maintain the orientation from the focal point to the centroid when selecting the hexagon location.
+However, this could mean it is placed further away.
+
 ## Animation
@@
 
-This algorithm should be general enough to apply to other study regions and contexts.
-The algorithm has only been tested using single countries.
-While the buffer allows extension beyond the furthest centroids, there is no mechanism implemented to protect the borders and ensure centroids are placed within the geographic borders of a country.
+Australia is used as an example, because it represents an extreme sparse geography and small dense population areas which produces unsatisfactory results with all existing cartogram-type algorithms.
+However, the algorithm is sufficiently general to apply to other geographic regions, and indeed has been applied to make hexagon maps of the UK, USA and France.
+
+There are many possible extensions to the algorithm that might be valuable future work.
+The buffer allows extension beyond the furthest centroids, but there is no mechanism to protect borders to force centroids are placed within the geographic borders of a region (e.g.
+country or state).
 The algorithm is also currently limited to representing each geographic area with only one hexagon.
-Future developments may address these limitations, and refine the filter steps for final selection of a hexagon grid point for each centroid.
-A direct angle is currently implemented, but may narrowly miss appropriate hexagons, a logarithmic function may help to choose a closer hexagon to the original centroid location.
-This algorithm is an effective start to automatically creating hexagon tile maps for many geographic units.
-This contributes to an extensive body of work that encourages the use of alternative map displays for statistical displays of spatial data.
+In the filter step for final selection of a hexagon grid point for each centroid, a direct angle constraint is currently implemented, but it may narrowly miss potentially better hexagon allocation.
+Some other constraints, such as a logarithmic function may help to choose refine the final allocation to hexagons closer to the original centroid location.
+In a country like Australia, the vast centre produces a hexagon map with small isolated hexagons, even when the city centres are hugely expanded.
+It could be useful to allow variable sized hexagons, primarily to increase the size of the isolated hexagons to improve their visibility.
+
+This new algorithm provides an effective start point for automatically creating hexagon tile maps for any spatial polygon data, and contributes to an extensive body of work that encourages the use of alternative map displays for statistical displays of spatial data.

### 2022-06-02 kobakian-cook.tex
links now working and more tweakig of paper

@@
 
-Alternative mapping methods, like cartograms, allow increased
-understanding of the spatial distribution of a variable across the
-population, by fairly representing the population in each administrative
-area \citep{TAAM}. This acknowledges that the number of residents can be
-different and also recognises that each area, or person within it is
-equally important.
+Alternative mapping methods, like cartograms implemented in
+\CRANpkg{cartogram}, allow increased understanding of the spatial
+distribution of a variable across the population, by fairly representing
+the population in each administrative area \citep{TAAM}. This
+acknowledges that the number of residents can be different and also
+recognises that each area, or person within it is equally important.
 
-This paper contains a discussion of Existing Mapping Practices. This is
-followed by details of the Algorithm. The implementation section
-discusses the algorithm in the \CRANpkg{sugarbag} package. Finally, the
-use and benefits of animation are presented.
+This paper contains a discussion of existing mapping practices, followed
+by details of the algorithm. The implementation section explains the
+algorithm available in the \CRANpkg{sugarbag} package. How to utilise
+animation with the hexagon map is described. The paper finishes with a
+summary and possible new directions for the algorithm.
 
 \hypertarget{existing-mapping-practices}{%
-\subsection{Existing Mapping
-Practices}\label{existing-mapping-practices}}
+\subsection{Existing mapping
+practices}\label{existing-mapping-practices}}
 
@@
 transformations to improve communication of spatial distributions
-\citep{CBATCC}. In Figure \ref{fig:tas_displays} the choropleth map can
+\citep{CBATCC}. In Figure \ref{fig:tasdisplays} the choropleth map can
 be seen underneath each alternative map display to allow for comparisons
@@
 
-There are several established alternative visualisation methods. Tile
-maps, rectangular cartograms \citep{ORC} and Dorling cartograms
-\citep{ACTUC} all use one simple shape to represent each geographic
-unit. They all minimise the emphasis on the size or shape of the
-geographic areas. These alternative map displays focus on the
+There are several established alternative visualisation methods.
+Rectangular cartograms \citep{ORC} and Dorling cartograms \citep{ACTUC}
+implemented in \pkg{cartogram} and tile maps implemented in
+\CRANpkg{tilemaps}, all use one simple shape to represent each
+geographic unit. They all minimise the emphasis on the size or shape of
+the geographic areas. These alternative map displays focus on the
 relationship between neighbours, attempting to preserve connections, and
 disregard the unique shapes of the administrative boundaries. Figure
-\ref{fig:tas_displays} shows a collection of alternative map displays,
+\ref{fig:tasdisplays} shows a collection of alternative map displays,
 this includes a) a contiguous cartogram, b) a non-contiguous cartogram,
@@
 \begin{figure}
-\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/tas_displays-1} \caption[The three displays show alternative maps of the Australian state of Tasmania at SA2 level]{The three displays show alternative maps of the Australian state of Tasmania at SA2 level: (a) contiguous cartogram, (b) non-contiguous cartogram and (c) Dorling cartogram of Tasmania.
+\includegraphics[width=1\linewidth]{kobakian-cook_files/figure-latex/tasdisplays-1} \caption[The three displays show alternative maps of the Australian state of Tasmania at SA2 level]{The three displays show alternative maps of the Australian state of Tasmania at SA2 level: (a) contiguous cartogram, (b) non-contiguous cartogram and (c) Dorling cartogram of Tasmania.
 The contiguous cartogram looks like the state has an hourglass figure, while the non-contiguous cartogram shrinks areas into invisibility.
-The Dorling expands the metropolitan regions.}\label{fig:tas_displays}
+The Dorling expands the metropolitan regions.}\label{fig:tasdisplays}
 \end{figure}
@@
 transformed display. The contiguous cartogram displayed in Figure
-\ref{fig:tas_displays}a) draws attention to smaller geographic units
-when they are rescaled according to the population \citep{DMAHP}. These
-new shapes can now be coloured to represent a second variable. The
-algorithm uses the geographic shape of the areas and iterates toward
-sizing the areas to represent the population. This display can create
-twisted and unfamiliar shapes from the geographic units as the
-algorithms must satisfy the topology conditions, especially when there
-are communities located geographically far from their neighbours
-\citep{TVSSS}.
+\ref{fig:tasdisplays}a draws attention to smaller geographic units when
+they are rescaled according to the population \citep{DMAHP}. These new
+shapes can now be coloured to represent a second variable. The algorithm
+uses the geographic shape of the areas and iterates toward sizing the
+areas to represent the population. This display can create twisted and
+unfamiliar shapes from the geographic units as the algorithms must
+satisfy the topology conditions, especially when there are communities
+located geographically far from their neighbours \citep{TVSSS}.
 
-The non-contiguous cartogram in Figure \ref{fig:tas_displays}b) also
-uses the population to rescale the geographic units. Unlike the
-contiguous cartogram, the SA2 areas maintain their geographic shape, but
-they may not retain the connection with their neighbours. The population
-of the SA2 areas is used to scale the geographic units in the
-non-contiguous cartogram \citep{NAC}. The amount of background space can
-be meaningful in non-contiguous cartograms \citep{ECGC}. The size
-disparity between rural areas and urban areas result in reasonable
-display within the south eastern city of Hobart, but these units are not
-visible in the context of the Tasmania state map. Depending on the
-difference between the population and geographic land size, the amount
-of white space can also prevent meaningful understanding of the
-distribution \citep{TVSSS}.
+The non-contiguous cartogram in Figure \ref{fig:tasdisplays}b also uses
+the population to rescale the geographic units. Unlike the contiguous
+cartogram, the SA2 areas maintain their geographic shape, but they may
+not retain the connection with their neighbours. The population of the
+SA2 areas is used to scale the geographic units in the non-contiguous
+cartogram \citep{NAC}. The amount of background space can be meaningful
+in non-contiguous cartograms \citep{ECGC}. The size disparity between
+rural areas and urban areas result in reasonable display within the
+south eastern city of Hobart, but these units are not visible in the
+context of the Tasmania state map. Depending on the difference between
+the population and geographic land size, the amount of white space can
+also prevent meaningful understanding of the distribution \citep{TVSSS}.
 
@@
 size of the circle is scaled according to the population value of each
-area \citep{ACTUC}. Figure \ref{fig:tas_displays}c) shows the Tasmania
-SA2 areas as an individual circle located as close as possible to the
+area \citep{ACTUC}. Figure \ref{fig:tasdisplays}c shows the Tasmania SA2
+areas as an individual circle located as close as possible to the
 geographic centroid location. This map draws attention to the collection
 of coastal cities in Tasmania that were not apparent in Figure
-\ref{fig:tas_displays} a), or b). This display also highlights that the
+\ref{fig:tasdisplays} a or b. This display also highlights that the
 approximation of equal population is not easy to fulfil, as there is
@@
 regardless of the population or other information, to generate equal
-size spatial polygons. The Dorling algorithm can beinduced to do this,
+size spatial polygons. The Dorling algorithm can be induced to do this,
 to make equallly sized circles. \citet{MDAC} describes a group of
@@
 equal weight to each geographic area even if the population differs.
+
+The nature of Australian population boundaries means that there are many
+connecting neighbours of population areas. This solution was designed to
+visualise Australian population analysis, inspired by tile maps three
+sided triangles and four sided squares were considered, but this would
+not have allowed sufficient neighbours to connect. Hexagon tile maps
+utilise the tessellating features of hexagons to maximise the data ink
+and allow connectivity between six potential neighbours. Hexagons allow
+the alignment of geographic borders, this aides in comparison of colour
+values.
 
@@
 \begin{figure}
-\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/hexmap-1} \caption[A hexagon tile map of female tyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1]{A hexagon tile map of female tyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1.
+\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/hexmap-1} \caption[A hexagon tile map of female thyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1]{A hexagon tile map of female thyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1.
 The high incidence in several of the metropolitan regions (Brisbane, Sydney and Perth) can now be seen, along with numerous isolated spots.}\label{fig:hexmap}
@@
 There are several key steps in the creation of the hexagon tile map as
-described in the flow chart in Figure \ref{fig:sugarbag_flow}. First,
+described in the flow chart in Figure \ref{fig:sugarbagflow}. First,
 derive the set of centroids from the polygons provided, then create the
 grid of hexagon locations. These two processes are defined in the blue
-left column of the flow chart in figure \ref{fig:sugarbag_flow}. Each
+left column of the flow chart in figure \ref{fig:sugarbagflow}. Each
 centroid can then be allocated to an available hexagon location. The
 steps for the allocation process are detailed in the right column of
-Figure \ref{fig:sugarbag_flow}. There are several filter steps to speed
+Figure \ref{fig:sugarbagflow}. There are several filter steps to speed
 the process of selecting an appropriate hexagon to represent each
@@
 
+\begin{Schunk}
 \begin{figure}
-\includegraphics[width=14cm]{figs/sugarbag flow.png}
-\caption{\label{fig:sugarbag_flow}A flow diagram detailing the steps taken to create a hexagon tile map.
-There are two basic processes, one to make the grid, and the other to allocate centroids to grid points.}
+\includegraphics[width=1\linewidth]{figs/sugarbag_flow} \caption[A flow diagram detailing the steps taken to create a hexagon tile map]{A flow diagram detailing the steps taken to create a hexagon tile map.
+There are two basic processes, one to make the grid, and the other to allocate centroids to grid points.}\label{fig:sugarbagflow}
 \end{figure}
-
-\hypertarget{user-choices}{%
-\subsubsection{User choices}\label{user-choices}}
-
-Only two inputs are necessary to begin the algorithm; the shapefile, and
-the ID variable. The ID variable should uniquely identify each
-geographic unit in the shapefile.
-
-The centroids are derived from the shapefile. The amount of centroids
-within the geographic map is used to determine an appropriate hexagon
-size if one is not provided. The derived centroids are a necessary input
-for an appropriate grid to be constructed. Each grid point is located a
-hexagon size distance from the next closest point in all six directions.
-The grid will initially cover the entire map space, encompassing all the
-centroid locations and will extend in all directions to the extent of
-the buffer distance. This buffer distance can be helpful to account for
-densely populated coastal areas, allowing the hexagon locations to
-spread beyond the coastline, over the sea.
-
-The centroid set and hexagon tile map grid are necessary for the
-allocation process. Additionally, a set of reference locations can be
-provided as focal points, typically compact and/or densely populated
-areas such as major cities. The algorithm will use the focal points to
-create the order of allocation, prioritising the closest centroid
-locations to the focal points. The user can also specify the variable
-that should be used to determine the order for the allocation.
-
-When allocating representative hexagons, the width parameter can be used
-to determine the flexibility of positioning. Using the relationship with
-the nearest focal point, a larger width parameter will increase the
-amount of available hexagons nearer to the original centroid of the
-geographic unit. A smaller width will maintain the orientation from the
-focal point to the centroid when selecting the hexagon location.
-However, this could mean it is placed further away.
+\end{Schunk}
 
@@
 uses the centroids, the hexagon size and the buffer distance. Figure
-\ref{fig:filterprocess} 1a) shows the initial locations of grid points
+\ref{fig:filterprocess} 1a shows the initial locations of grid points
 created for Tasmania.
+
+\begin{verbatim}
+centroids <- create_centroids(
+  shp_sf = sa2 %>% filter(state_name_2011 == "Tasmania"), 
+  sf_id = "sa2_name_2011")
+\end{verbatim}
 
@@
 hexagon location is created from all intersections of the longitude
-columns and latitude rows. Figure \ref{fig:filterprocess} 1a) shows the
+columns and latitude rows. Figure \ref{fig:filterprocess} 1a shows the
 hexagon grid after every second latitude row on the grid is shifted
 right, by half of the hexagon size.
+
+\begin{verbatim}
+grid <- create_grid(centroids = centroids, hex_size = 0.2, buffer_dist = 2)
+\end{verbatim}
 
@@
 the buffer distance, for each row and column of the grid. Figure
-\ref{fig:filterprocess} 1b) displays remaining hexagon grid points after
+\ref{fig:filterprocess} 1b displays remaining hexagon grid points after
 applying the buffer filter. The sparsely populated South-West region of
@@
 this example, this distance is only calculated for the capital city of
-Hobart, represented in figure \ref{fig:filterprocess} 2a) and 2b) as a
+Hobart, represented in Figure \ref{fig:filterprocess} 2a and 2b as a
 white cross.
@@
 
+\begin{verbatim}
+hex_allocated <- allocate(centroids = centroids,
+                          sf_id = "SA2_NAME16",
+                          hex_grid = grid,
+                          hex_size = 0.2, # same size used in create_grid
+                          hex_filter = 10,
+                          use_neighbours = tas_sa2,
+                          focal_points = capital_cities,
+                          # same column used in create_centroids
+                          width = 30, verbose = TRUE)
+\end{verbatim}
+
 \hypertarget{a-filter-the-grid-for-unassigned-hexagon-points}{%
@@
 prevents multiple geographic units from being allocated to the same
-hexagon. This is demonstrated in figure \ref{fig:filterprocess} 2a) and
-2b) by the black hexagons that represent the seven closest polygons to
+hexagon. This is demonstrated in Figure \ref{fig:filterprocess} 2a and
+2b by the black hexagons that represent the seven closest polygons to
 the capital city of Hobart. As the allocation process begins for the
@@
 angle from the focal point to centroid location. This uses the angle
-from the closest capital city, to the current centroid as seen in figure
-\ref{fig:filterprocess} 2a). This allows the spatial relationship to be
+from the closest capital city, to the current centroid as seen in Figure
+\ref{fig:filterprocess} 2a. This allows the spatial relationship to be
 preserved, even when it is allocated to a hexagon that is further from
@@
 spatial relationship between the focal point and geographic centroid.
+
+\hypertarget{user-choices}{%
+\subsubsection{User choices}\label{user-choices}}
+
+Only two inputs are necessary to begin the algorithm; the shapefile, and
+the ID variable. The ID variable should uniquely identify each
+geographic unit in the shapefile.
+
+The centroids are derived from the shapefile. The amount of centroids
+within the geographic map is used to determine an appropriate hexagon
+size if one is not provided. The derived centroids are a necessary input
+for an appropriate grid to be constructed. Each grid point is located a
+hexagon size distance from the next closest point in all six directions.
+The grid will initially cover the entire map space, encompassing all the
+centroid locations and will extend in all directions to the extent of
+the buffer distance. This buffer distance can be helpful to account for
+densely populated coastal areas, allowing the hexagon locations to
+spread beyond the coastline, over the sea.
+
+The centroid set and hexagon tile map grid are necessary for the
+allocation process. Additionally, a set of reference locations can be
+provided as focal points, typically compact and/or densely populated
+areas such as major cities. The algorithm will use the focal points to
+create the order of allocation, prioritising the closest centroid
+locations to the focal points. The user can also specify the variable
+that should be used to determine the order for the allocation.
+
+When allocating representative hexagons, the width parameter can be used
+to determine the flexibility of positioning. Using the relationship with
+the nearest focal point, a larger width parameter will increase the
+amount of available hexagons nearer to the original centroid of the
+geographic unit. A smaller width will maintain the orientation from the
+focal point to the centroid when selecting the hexagon location.
+However, this could mean it is placed further away.
 
@@
 
-This algorithm should be general enough to apply to other study regions
-and contexts. The algorithm has only been tested using single countries.
-While the buffer allows extension beyond the furthest centroids, there
-is no mechanism implemented to protect the borders and ensure centroids
-are placed within the geographic borders of a country. The algorithm is
-also currently limited to representing each geographic area with only
-one hexagon. Future developments may address these limitations, and
-refine the filter steps for final selection of a hexagon grid point for
-each centroid. A direct angle is currently implemented, but may narrowly
-miss appropriate hexagons, a logarithmic function may help to choose a
-closer hexagon to the original centroid location. This algorithm is an
-effective start to automatically creating hexagon tile maps for many
-geographic units. This contributes to an extensive body of work that
-encourages the use of alternative map displays for statistical displays
-of spatial data.
+Australia is used as an example, because it represents an extreme sparse
+geography and small dense population areas which produces unsatisfactory
+results with all existing cartogram-type algorithms. However, the
+algorithm is sufficiently general to apply to other geographic regions,
+and indeed has been applied to make hexagon maps of the UK, USA and
+France.
+
+There are many possible extensions to the algorithm that might be
+valuable future work. The buffer allows extension beyond the furthest
+centroids, but there is no mechanism to protect borders to force
+centroids are placed within the geographic borders of a region
+(e.g.~country or state). The algorithm is also currently limited to
+representing each geographic area with only one hexagon. In the filter
+step for final selection of a hexagon grid point for each centroid, a
+direct angle constraint is currently implemented, but it may narrowly
+miss potentially better hexagon allocation. Some other constraints, such
+as a logarithmic function may help to choose refine the final allocation
+to hexagons closer to the original centroid location. In a country like
+Australia, the vast centre produces a hexagon map with small isolated
+hexagons, even when the city centres are hugely expanded. It could be
+useful to allow variable sized hexagons, primarily to increase the size
+of the isolated hexagons to improve their visibility.
+
+This new algorithm provides an effective start point for automatically
+creating hexagon tile maps for any spatial polygon data, and contributes
+to an extensive body of work that encourages the use of alternative map
+displays for statistical displays of spatial data.
 

### 2022-06-11 kobakian-cook.Rmd
Update kobakian-cook.Rmd

@@
   - name: Stephanie Kobakian
-    affiliation: Monash University
+    affiliation:  
     address:
-    - Department of Econometrics and Business Statistics
-    email:  stephanie.kobakian@monash.edu 
+    - Sydney, Australia
+    email:  stephanie.kobakian@gmail.com 
   - name: Dianne Cook

### 2022-06-11 kobakian-cook.Rmd
Update kobakian-cook.Rmd

@@
 This can cause some values to be emphasised over others, and allows choropleth map displays to misrepresent the spatial distributions of human related statistics due to area-size bias [@BCM].
-Figure \@ref(fig:choro) is a choropleth map that uses colour to display the estimated standardised incidence ratios (SIRs) of thyroid cancer for females, in each of the Statistical Areas at Level 2 (SA2) used by the @abs2011.
+
+The Australian Cancer Atlas is an online, interactive display of Australian cancer statistics in each of the Statistical Areas at Level 2 (SA2s), used by the @abs2011.
+The estimated standardised incidence ratios (SIRs) of thyroid cancer
+for females was downloaded from the Australian Cancer Atlas and presented in Figure \@ref(fig:choro), a choropleth map that uses colour to display the distribution.
 The Australian choropleth map display draws attention to the expanse of dark and light blue areas across the rural communities in all states.

### 2022-06-11 kobakian-cook.Rmd
Update kobakian-cook.Rmd

@@
 The estimated standardised incidence ratios (SIRs) of thyroid cancer
-for females was downloaded from the Australian Cancer Atlas and presented in Figure \@ref(fig:choro), a choropleth map that uses colour to display the distribution.
+for females was downloaded from the publicly accessible Australian Cancer Atlas website and presented in Figure \@ref(fig:choro), a choropleth map that uses colour to display the distribution.
 The Australian choropleth map display draws attention to the expanse of dark and light blue areas across the rural communities in all states.

### 2022-10-12 kobakian-cook.Rmd
Remove dependency of absmapsdata

@@
 
-# remotes::install_github("wfmackey/absmapsdata")
-library(absmapsdata)
+# Rda files sourced from: https://github.com/wfmackey/absmapsdata
+load("data/sa22011.Rda")
+load("data/state2011.Rda")
 
@@
 ```{r thyroiddata}
-sa2 <- absmapsdata::sa22011 %>% 
+sa2 <- sa22011 %>% 
   filter(!st_is_empty(geometry)) %>% 

### 2022-10-12 kobakian-cook.R
Remove dependency on abs maps data

@@ -1,4 +1,6 @@
-# Young statisticians conference presentation plots
+# Plots
+
+## Libraries 
 
 library(absmapsdata)
 library(tidyverse)
@@ -7,6 +9,11 @@ library(ggthemes)
 library(cowplot)
 library(sf)
 library(sp)
+
+## Data 
+# Rda files sourced from: https://github.com/wfmackey/absmapsdata
+load("data/sa22011.Rda")
+load("data/state2011.Rda")
 
 ### Theme set up
 

### 2022-10-17 kobakian-cook.tex
paper compiles nicely

@@
 \abstract{%
-Spatial distributions have been presented on alternative representations
-of geography, such as cartograms, for many years. In modern times,
-interactivity and animation have allowed alternative displays to play a
-larger role. Alternative representations have been popularised by online
-news sites, and digital atlases with a focus on public consumption.
-Applications are increasingly widespread, especially in the areas of
-disease mapping, and election results. The algorithm presented creates a
-display that uses tessellated hexagons to represent a set of spatial
-polygons, and is implemented in the R package called sugarbag. It
-allocates these hexagon in a manner that preserves the spatial
-relationship of the geographic units, in light of their positions to
-points of interest. The display showcases spatial distributions, by
-emphasising the small geographical regions that are often difficult to
-locate on geographic maps.
+Spatial distributions have been presented on alternative representations of geography, such as cartograms, for many years.
+In modern times, interactivity and animation have allowed alternative displays to play a larger role.
+Alternative representations have been popularised by online news sites, and digital atlases with a focus on public consumption.
+Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
+The algorithm presented creates a display that uses tessellated hexagons to represent a set of spatial polygons, and is implemented in the R package called sugarbag.
+It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units, in light of their positions to points of interest.
+The display showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps.
 }
@@
 
-Many cancer atlases present geospatial cancer data on a choropleth map
-display. The Australian Cancer Atlas \citep{TACA} is a recent addition
-to the many cancer atlas maps worldwide. The ground-breaking atlas for
-Australia presents a central map that shows the landmass overlaid with
-administrative boundaries. This choropleth display can highlight the
-geographic patterns in geospatially related cancer statistics
-\citep{SAMGIS}.
+Many cancer atlases present geospatial cancer data on a choropleth map display.
+The Australian Cancer Atlas (Cancer Council Queensland, Queensland University of Technology, and Cooperative Research Centre for Spatial Information 2018) is a recent addition to the many cancer atlas maps worldwide.
+The ground-breaking atlas for Australia presents a central map that shows the landmass overlaid with administrative boundaries.
+This choropleth display can highlight the geographic patterns in geospatially related cancer statistics (Moore and Carpenter 1999).
 
-Over time, the density of living in major cities has increased as
-residents have gathered to live near urban areas \citep{ACTUC}. The
-division of these residents into approximately equal population areas
-results in dramatically different square meterage of administrative
-geographic units, such as states or electorates. In a choropleth map
-display, the geographic units are coloured to represent the value of the
-statistic for each unit \citep{EI}. This can cause some values to be
-emphasised over others, and allows choropleth map displays to
-misrepresent the spatial distributions of human related statistics due
-to area-size bias \citep{BCM}. Figure \ref{fig:choro} is a choropleth
-map that uses colour to display the estimated standardised incidence
-ratios (SIRs) of thyroid cancer for females, in each of the Statistical
-Areas at Level 2 (SA2) used by the \citet{abs2011}. The Australian
-choropleth map display draws attention to the expanse of dark and light
-blue areas across the rural communities in all states. The SA2s on the
-east coast around Brisbane and in northern New South Wales stand out as
-more orange and red. However, this display neglects the vast amount of
-Australia residents living in the densely populated capital cities.
+Over time, the density of living in major cities has increased as residents have gathered to live near urban areas (Dorling 2011).
+The division of these residents into approximately equal population areas results in dramatically different square meterage of administrative geographic units, such as states or electorates.
+In a choropleth map display, the geographic units are coloured to represent the value of the statistic for each unit (Tufte 1990).
+This can cause some values to be emphasised over others, and allows choropleth map displays to misrepresent the spatial distributions of human related statistics due to area-size bias (Skowronnek 2016).
 
-\begin{Schunk}
+The Australian Cancer Atlas is an online, interactive display of Australian cancer statistics in each of the Statistical Areas at Level 2 (SA2s), used by the Australian Bureau of Statistics (2011).
+The estimated standardised incidence ratios (SIRs) of thyroid cancer
+for females was downloaded from the publicly accessible Australian Cancer Atlas website and presented in Figure \ref{fig:choro}, a choropleth map that uses colour to display the distribution.
+The Australian choropleth map display draws attention to the expanse of dark and light blue areas across the rural communities in all states.
+The SA2s on the east coast around Brisbane and in northern New South Wales stand out as more orange and red.
+However, this display neglects the vast amount of Australia residents living in the densely populated capital cities.
+
 \begin{figure}
-\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/choro-1} \caption[A choropleth map of thyroid incidence among females across the Statistical Areas of Australia at Level 2]{A choropleth map of thyroid incidence among females across the Statistical Areas of Australia at Level 2.
+\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/choro-1} \caption{A choropleth map of thyroid incidence among females across the Statistical Areas of Australia at Level 2.
 Blue indicates lower than average and red indicates higher than average incidence.
@@
 \end{figure}
-\end{Schunk}
 
 The solutions to this visualisation problem begin with the geography.
-Alternative maps can be created to shift the focus from land area and
-shape to the value of the statistics \citep{ACCAC}. Each style of
-cartogram applies a different transformation to the geographic areas, to
-highlight the values of the statistic of interest. Alternative maps can
-result in a distortion of the map space to represent features of the
-distribution across the areas \citep{ACCAC} as the statistic of interest
-is used to determine the cartogram layout.
+Alternative maps can be created to shift the focus from land area and shape to the value of the statistics (Dougenik, Chrisman, and Niemeyer 1985).
+Each style of cartogram applies a different transformation to the geographic areas, to highlight the values of the statistic of interest.
+Alternative maps can result in a distortion of the map space to represent features of the distribution across the areas (Dougenik, Chrisman, and Niemeyer 1985) as the statistic of interest is used to determine the cartogram layout.
 
-Alternative mapping methods, like cartograms implemented in
-\CRANpkg{cartogram}, allow increased understanding of the spatial
-distribution of a variable across the population, by fairly representing
-the population in each administrative area \citep{TAAM}. This
-acknowledges that the number of residents can be different and also
-recognises that each area, or person within it is equally important.
+Alternative mapping methods, like cartograms implemented in \CRANpkg{cartogram}, allow increased understanding of the spatial distribution of a variable across the population, by fairly representing the population in each administrative area (Levison and Haddon Jr 1965).
+This acknowledges that the number of residents can be different and also recognises that each area, or person within it is equally important.
 
-This paper contains a discussion of existing mapping practices, followed
-by details of the algorithm. The implementation section explains the
-algorithm available in the \CRANpkg{sugarbag} package. How to utilise
-animation with the hexagon map is described. The paper finishes with a
-summary and possible new directions for the algorithm.
+This paper contains a discussion of existing mapping practices, followed by details of the algorithm.
+The implementation section explains the algorithm available in the \CRANpkg{sugarbag} package.
+How to utilise animation with the hexagon map is described.
+The paper finishes with a summary and possible new directions for the algorithm.
 
 \hypertarget{existing-mapping-practices}{%
-\subsection{Existing mapping
-practices}\label{existing-mapping-practices}}
+\subsection{Existing mapping practices}\label{existing-mapping-practices}}
 
-The familiar choropleth map display is often used to allow the user to
-orient themselves. However, the emphasis on the land mass diminishes the
-features of the distribution in densely populated communities due to the
-small size on the display \citep{ACTUC}. The unique shapes of boundaries
-can be helpful for orienting users but may not contribute to their
-understanding of the spatial disease distribution as many of the
-communities are not visible in a choropleth display \citep{TVSSS}.
+The familiar choropleth map display is often used to allow the user to orient themselves.
+However, the emphasis on the land mass diminishes the features of the distribution in densely populated communities due to the small size on the display (Dorling 2011).
+The unique shapes of boundaries can be helpful for orienting users but may not contribute to their understanding of the spatial disease distribution as many of the communities are not visible in a choropleth display (Dorling 2012).
 
-Administrative areas are often used to aggregate census data and used to
-understand demographics within communities of the Australian population.
-Each SA2 \citep{abs2011} was designed to represent a community. This
-collection of communities presents an opportunity for explicit map
-transformations to improve communication of spatial distributions
-\citep{CBATCC}. In Figure \ref{fig:tasdisplays} the choropleth map can
-be seen underneath each alternative map display to allow for comparisons
-to be made.
+Administrative areas are often used to aggregate census data and used to understand demographics within communities of the Australian population.
+Each SA2 (Australian Bureau of Statistics 2011) was designed to represent a community.
+This collection of communities presents an opportunity for explicit map transformations to improve communication of spatial distributions (Kocmoud and House 1998).
+In Figure \ref{fig:tasdisplays} the choropleth map can be seen underneath each alternative map display to allow for comparisons to be made.
 
 There are several established alternative visualisation methods.
-Rectangular cartograms \citep{ORC} and Dorling cartograms \citep{ACTUC}
-implemented in \pkg{cartogram} and tile maps implemented in
-\CRANpkg{tilemaps}, all use one simple shape to represent each
-geographic unit. They all minimise the emphasis on the size or shape of
-the geographic areas. These alternative map displays focus on the
-relationship between neighbours, attempting to preserve connections, and
-disregard the unique shapes of the administrative boundaries. Figure
-\ref{fig:tasdisplays} shows a collection of alternative map displays,
-this includes a) a contiguous cartogram, b) a non-contiguous cartogram,
-and c) a Dorling cartogram.
+Rectangular cartograms (Kreveld and Speckmann 2007) and Dorling cartograms (Dorling 2011) implemented in \pkg{cartogram} and tile maps implemented in \CRANpkg{tilemaps}, all use one simple shape to represent each geographic unit.
+They all minimise the emphasis on the size or shape of the geographic areas.
+These alternative map displays focus on the relationship between neighbours, attempting to preserve connections, and disregard the unique shapes of the administrative boundaries.
+Figure \ref{fig:tasdisplays} shows a collection of alternative map displays, this includes a) a contiguous cartogram, b) a non-contiguous cartogram, and c) a Dorling cartogram.
 
-\begin{Schunk}
 \begin{figure}
-\includegraphics[width=1\linewidth]{kobakian-cook_files/figure-latex/tasdisplays-1} \caption[The three displays show alternative maps of the Australian state of Tasmania at SA2 level]{The three displays show alternative maps of the Australian state of Tasmania at SA2 level: (a) contiguous cartogram, (b) non-contiguous cartogram and (c) Dorling cartogram of Tasmania.
+\includegraphics[width=1\linewidth]{kobakian-cook_files/figure-latex/tasdisplays-1} \caption{The three displays show alternative maps of the Australian state of Tasmania at SA2 level: (a) contiguous cartogram, (b) non-contiguous cartogram and (c) Dorling cartogram of Tasmania.
 The contiguous cartogram looks like the state has an hourglass figure, while the non-contiguous cartogram shrinks areas into invisibility.
@@
 \end{figure}
-\end{Schunk}
 
-When communicating information that is relevant to the population, each
-member of the population can be given equal representation by
-transforming the map \citep{TVSSS}. The connected communities can be
-recognised by allowing the boundaries to maintain connection in the
-transformed display. The contiguous cartogram displayed in Figure
-\ref{fig:tasdisplays}a draws attention to smaller geographic units when
-they are rescaled according to the population \citep{DMAHP}. These new
-shapes can now be coloured to represent a second variable. The algorithm
-uses the geographic shape of the areas and iterates toward sizing the
-areas to represent the population. This display can create twisted and
-unfamiliar shapes from the geographic units as the algorithms must
-satisfy the topology conditions, especially when there are communities
-located geographically far from their neighbours \citep{TVSSS}.
+When communicating information that is relevant to the population, each member of the population can be given equal representation by transforming the map (Dorling 2012).
+The connected communities can be recognised by allowing the boundaries to maintain connection in the transformed display.
+The contiguous cartogram displayed in Figure \ref{fig:tasdisplays}a draws attention to smaller geographic units when they are rescaled according to the population (Walter 2001).
+These new shapes can now be coloured to represent a second variable.
+The algorithm uses the geographic shape of the areas and iterates toward sizing the areas to represent the population.
+This display can create twisted and unfamiliar shapes from the geographic units as the algorithms must satisfy the topology conditions, especially when there are communities located geographically far from their neighbours (Dorling 2012).
 
-The non-contiguous cartogram in Figure \ref{fig:tasdisplays}b also uses
-the population to rescale the geographic units. Unlike the contiguous
-cartogram, the SA2 areas maintain their geographic shape, but they may
-not retain the connection with their neighbours. The population of the
-SA2 areas is used to scale the geographic units in the non-contiguous
-cartogram \citep{NAC}. The amount of background space can be meaningful
-in non-contiguous cartograms \citep{ECGC}. The size disparity between
-rural areas and urban areas result in reasonable display within the
-south eastern city of Hobart, but these units are not visible in the
-context of the Tasmania state map. Depending on the difference between
-the population and geographic land size, the amount of white space can
-also prevent meaningful understanding of the distribution \citep{TVSSS}.
+The non-contiguous cartogram in Figure \ref{fig:tasdisplays}b also uses the population to rescale the geographic units.
+Unlike the contiguous cartogram, the SA2 areas maintain their geographic shape, but they may not retain the connection with their neighbours.
+The population of the SA2 areas is used to scale the geographic units in the non-contiguous cartogram (Olson 1976).
+The amount of background space can be meaningful in non-contiguous cartograms (Keim et al.
+2002).
+The size disparity between rural areas and urban areas result in reasonable display within the south eastern city of Hobart, but these units are not visible in the context of the Tasmania state map.
+Depending on the difference between the population and geographic land size, the amount of white space can also prevent meaningful understanding of the distribution (Dorling 2012).
 
-The Dorling cartogram presents each geographic unit as a circle, the
-size of the circle is scaled according to the population value of each
-area \citep{ACTUC}. Figure \ref{fig:tasdisplays}c shows the Tasmania SA2
-areas as an individual circle located as close as possible to the
-geographic centroid location. This map draws attention to the collection
-of coastal cities in Tasmania that were not apparent in Figure
-\ref{fig:tasdisplays} a or b. This display also highlights that the
-approximation of equal population is not easy to fulfil, as there is
-some disparity in the sizes of the circles.
+The Dorling cartogram presents each geographic unit as a circle, the size of the circle is scaled according to the population value of each area (Dorling 2011).
+Figure \ref{fig:tasdisplays}c shows the Tasmania SA2 areas as an individual circle located as close as possible to the geographic centroid location.
+This map draws attention to the collection of coastal cities in Tasmania that were not apparent in Figure \ref{fig:tasdisplays} a or b.
+This display also highlights that the approximation of equal population is not easy to fulfil, as there is some disparity in the sizes of the circles.
 
-It is also common to treat all geographic units as equal, so that
-regardless of the population or other information, to generate equal
-size spatial polygons. The Dorling algorithm can be induced to do this,
-to make equallly sized circles. \citet{MDAC} describes a group of
-alternative maps called ``mosaic cartograms'' for tile displays. The
-geography of the USA has been transformed into a square-binned tile map
-manually and made available in the R package \CRANpkg{statebins}
-\citep{statebins}.The algorithm described below is an automatic layout
-of hexagon tiles, where a continguity constraint is relaxed. This gives
-equal weight to each geographic area even if the population differs.
+It is also common to treat all geographic units as equal, so that regardless of the population or other information, to generate equal size spatial polygons.
+The Dorling algorithm can be induced to do this, to make equallly sized circles.
+Cano et al.
+(2015) describes a group of alternative maps called ``mosaic cartograms'' for tile displays.
+The geography of the USA has been transformed into a square-binned tile map manually and made available in the R package \CRANpkg{statebins} (Rudis 2020).The algorithm described below is an automatic layout of hexagon tiles, where a continguity constraint is relaxed.
+This gives equal weight to each geographic area even if the population differs.
 
-The nature of Australian population boundaries means that there are many
-connecting neighbours of population areas. This solution was designed to
-visualise Australian population analysis, inspired by tile maps three
-sided triangles and four sided squares were considered, but this would
-not have allowed sufficient neighbours to connect. Hexagon tile maps
-utilise the tessellating features of hexagons to maximise the data ink
-and allow connectivity between six potential neighbours. Hexagons allow
-the alignment of geographic borders, this aides in comparison of colour
-values.
+The nature of Australian population boundaries means that there are many connecting neighbours of population areas.
+This solution was designed to visualise Australian population analysis, inspired by tile maps three sided triangles and four sided squares were considered, but this would not have allowed sufficient neighbours to connect.
+Hexagon tile maps utilise the tessellating features of hexagons to maximise the data ink and allow connectivity between six potential neighbours.
+Hexagons allow the alignment of geographic borders, this aides in comparison of colour values.
 
@@
 
-The purpose of this algorithm is to create an alternative map display
-that highlights the spatial distributions for populations. There has
-been an increasing need for displays that recognise the large number of
-people that live in dense urban environments. The algorithm intends to
-maintain the spatial relationships of a group of geographic units using
-the relationship between each unit and the closest focal point. The
-algorithm allocates geographic units to a representative hexagon, in
-order of their proximity to the closest focal point.
+The purpose of this algorithm is to create an alternative map display that highlights the spatial distributions for populations.
+There has been an increasing need for displays that recognise the large number of people that live in dense urban environments.
+The algorithm intends to maintain the spatial relationships of a group of geographic units using the relationship between each unit and the closest focal point.
+The algorithm allocates geographic units to a representative hexagon, in order of their proximity to the closest focal point.
 
-The algorithm is implemented in the \pkg{sugarbag} package for
-\texttt{R}, named after the common name for the \emph{Trigona
-carbonaria} bee -- a species which builds flat layers of hexagonal brood
-cells, spiralling out from a central point \citep{PH}. This unusual
-pattern also provided the inspiration for the algorithm, where the maps
-are constructed by building out from multiple focal points on the
-geographic map base in a spiral fashion.
+The algorithm is implemented in the \pkg{sugarbag} package for \texttt{R}, named after the common name for the \emph{Trigona carbonaria} bee -- a species which builds flat layers of hexagonal brood cells, spiralling out from a central point (Vit, Pedro, and Roubik 2013).
+This unusual pattern also provided the inspiration for the algorithm, where the maps are constructed by building out from multiple focal points on the geographic map base in a spiral fashion.
 
-The result of the algorithm applied to the same data represented in
-Figure \ref{fig:choro} shows rates of thyroid cancer for females in each
-of the SA2 areas of Australia as hexagons in Figure \ref{fig:hexmap}.
-The difference to the choropleth map in Figure \ref{fig:choro} are
-clear. Now the higher thyroid cancer incidence in the densely populated
-areas in Sydney, Brisbane and Perth are visible. Interestingly, there is
-no clear divide between rural and urban SA2 areas, as many rural areas
-and the cities of Melbourne, Darwin, Adelaide and Hobart have low rates
-of thyroid incidence for females. The hexagon tile map display provides
-a more accurate representation of the spatial distribution of thyroid
-cancer incidence across Australia.
+The result of the algorithm applied to the same data represented in Figure \ref{fig:choro} shows rates of thyroid cancer for females in each of the SA2 areas of Australia as hexagons in Figure \ref{fig:hexmap}.
+The difference to the choropleth map in Figure \ref{fig:choro} are clear.
+Now the higher thyroid cancer incidence in the densely populated areas in Sydney, Brisbane and Perth are visible.
+Interestingly, there is no clear divide between rural and urban SA2 areas, as many rural areas and the cities of Melbourne, Darwin, Adelaide and Hobart have low rates of thyroid incidence for females.
+The hexagon tile map display provides a more accurate representation of the spatial distribution of thyroid cancer incidence across Australia.
 
-Figure \ref{fig:hexmap} highlights the density of Australian capital
-cities, as it draws attention to the many communities in Sydney,
-Melbourne and Hobart. This display also highlights the disparity in the
-burden of thyroid cancer for females in the communities of these cities.
-There are several collections of red hexagons in Sydney that represent
-the communities with much higher rates of diagnosis than the Australian
-average. Brisbane also experiences higher than average rates of
-diagnosis, but has more orange than red. The females in the cities of
-Adelaide and Perth show much lower rates of diagnosis.
+Figure \ref{fig:hexmap} highlights the density of Australian capital cities, as it draws attention to the many communities in Sydney, Melbourne and Hobart.
+This display also highlights the disparity in the burden of thyroid cancer for females in the communities of these cities.
+There are several collections of red hexagons in Sydney that represent the communities with much higher rates of diagnosis than the Australian average.
+Brisbane also experiences higher than average rates of diagnosis, but has more orange than red.
+The females in the cities of Adelaide and Perth show much lower rates of diagnosis.
 
-Compared to the choropleth map display in Figure \ref{fig:choro}, the
-low rates in the rural Australian communities are no longer dominating
-the display. While the representative hexagons are still visible against
-the black background, the much lower than average rates in rural
-Australia are less noticeable.
+Compared to the choropleth map display in Figure \ref{fig:choro}, the low rates in the rural Australian communities are no longer dominating the display.
+While the representative hexagons are still visible against the black background, the much lower than average rates in rural Australia are less noticeable.
 
-\begin{Schunk}
 \begin{figure}
-\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/hexmap-1} \caption[A hexagon tile map of female thyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1]{A hexagon tile map of female thyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1.
+\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/hexmap-1} \caption{A hexagon tile map of female thyroid cancer incidence in Australia, the same data as shown in the choropleth map in Figure 1.
 The high incidence in several of the metropolitan regions (Brisbane, Sydney and Perth) can now be seen, along with numerous isolated spots.}\label{fig:hexmap}
 \end{figure}
-\end{Schunk}
 
-There are several key steps in the creation of the hexagon tile map as
-described in the flow chart in Figure \ref{fig:sugarbagflow}. First,
-derive the set of centroids from the polygons provided, then create the
-grid of hexagon locations. These two processes are defined in the blue
-left column of the flow chart in figure \ref{fig:sugarbagflow}. Each
-centroid can then be allocated to an available hexagon location. The
-steps for the allocation process are detailed in the right column of
-Figure \ref{fig:sugarbagflow}. There are several filter steps to speed
-the process of selecting an appropriate hexagon to represent each
-geographic unit. To make tessellated plots with the hexagon allocations,
-the point locations are converted into hexagon shapes.
+There are several key steps in the creation of the hexagon tile map as described in the flow chart in Figure \ref{fig:sugarbagflow}.
+First, derive the set of centroids from the polygons provided, then create the grid of hexagon locations.
+These two processes are defined in the blue left column of the flow chart in figure \ref{fig:sugarbagflow}.
+Each centroid can then be allocated to an available hexagon location.
+The steps for the allocation process are detailed in the right column of Figure \ref{fig:sugarbagflow}.
+There are several filter steps to speed the process of selecting an appropriate hexagon to represent each geographic unit.
+To make tessellated plots with the hexagon allocations, the point locations are converted into hexagon shapes.
 
-\begin{Schunk}
 \begin{figure}
-\includegraphics[width=1\linewidth]{figs/sugarbag_flow} \caption[A flow diagram detailing the steps taken to create a hexagon tile map]{A flow diagram detailing the steps taken to create a hexagon tile map.
+\includegraphics[width=1\linewidth]{figs/sugarbag_flow} \caption{A flow diagram detailing the steps taken to create a hexagon tile map.
 There are two basic processes, one to make the grid, and the other to allocate centroids to grid points.}\label{fig:sugarbagflow}
 \end{figure}
-\end{Schunk}
 
@@
 
-Hexagon tile maps can be useful to understand a distribution across a
-collection of geographic areas. However, these maps are not easy to
-create manually, especially as the number of areas increases. This
-algorithm was created to automate this process, and reduce the manual
-load involved in creating and implementing alternative displays. This
-allows map makers and data communicators to spend their time choosing
-the most effective display.
+Hexagon tile maps can be useful to understand a distribution across a collection of geographic areas.
+However, these maps are not easy to create manually, especially as the number of areas increases.
+This algorithm was created to automate this process, and reduce the manual load involved in creating and implementing alternative displays.
+This allows map makers and data communicators to spend their time choosing the most effective display.
 
-The \pkg{sugarbag} package contains a set of functions that help R users
-to create a hexagon tile map. The algorithm presented in the
-\pkg{sugarbag} package operates on a set of simple feature geometry
-objects , known as \CRANpkg{sf} objects\citep{sf}. This package allows R
-users to create \pkg{sf} objects by importing polygons stored in various
-formats. Users should provide a set of polygons that define geographic
-units by their administrative boundaries. The functions arrange the
-geographic units in order of proximity to a set of locations provided,
-such as the centre of major cities. The centroid location of each
-geographic unit is used to measure the proximity. It emphasises the
-major cities as population hubs, rather than emphasizing the size of
-large, rural geographic units.
+The \pkg{sugarbag} package contains a set of functions that help R users to create a hexagon tile map.
+The algorithm presented in the \pkg{sugarbag} package operates on a set of simple feature geometry objects , known as \CRANpkg{sf} objects(Pebesma 2018).
+This package allows R users to create \pkg{sf} objects by importing polygons stored in various formats.
+Users should provide a set of polygons that define geographic units by their administrative boundaries.
+The functions arrange the geographic units in order of proximity to a set of locations provided, such as the centre of major cities.
+The centroid location of each geographic unit is used to measure the proximity.
+It emphasises the major cities as population hubs, rather than emphasizing the size of large, rural geographic units.
 
-A user can tweak the parameters of the hexagon map using the additional
-arguments to the \code{create\_hexmap} function, but these options may
-affect the speed of the algorithm. The hexagon size may need adjustments
-depending on the density of the population; users can provide an
-appropriate hexagon size and re-run the algorithm. The buffer distance
-may need to be increased if the coastal cities need to extend beyond the
-geographic land mass.
+A user can tweak the parameters of the hexagon map using the additional arguments to the \code{create\_hexmap} function, but these options may affect the speed of the algorithm.
+The hexagon size may need adjustments depending on the density of the population; users can provide an appropriate hexagon size and re-run the algorithm.
+The buffer distance may need to be increased if the coastal cities need to extend beyond the geographic land mass.
 
@@
 
-\begin{Schunk}
-\begin{Sinput}
+\begin{verbatim}
 install.packages("sugarbag")
-\end{Sinput}
-\end{Schunk}
+\end{verbatim}
 
-\noindent and the development version can be installed from the GitHub
-repository:
+\noindent and the development version can be installed from the GitHub repository:
 
-\begin{Schunk}
-\begin{Sinput}
+\begin{verbatim}
 devtools::install_github("srkobakian","sugarbag")
-\end{Sinput}
-\end{Schunk}
+\end{verbatim}
 
-The following steps create the hexagon tile map for all the Statistical
-Areas at Level 2 in Tasmania. These steps can be executed by the main
-function, \code{create\_hexmap}, or can be run separately for more
-flexibility.
+The following steps create the hexagon tile map for all the Statistical Areas at Level 2 in Tasmania.
+These steps can be executed by the main function, \code{create\_hexmap}, or can be run separately for more flexibility.
 
-If a user would like to perform each of the steps of the algorithm
-themselves, the necessary inputs will change for each function. For
-example, the \code{allocate} function can be used directly when a user
-wishes to use a set of centroids, rather than polygons.
+If a user would like to perform each of the steps of the algorithm themselves, the necessary inputs will change for each function.
+For example, the \code{allocate} function can be used directly when a user wishes to use a set of centroids, rather than polygons.
 
-The set of SA2 polygons for Tasmania, using the 2011 definition of SA2s,
-is accessed from the \pkg{absmapsdata} package. A single column of the
-data set is used to identify the unique areas. In this case, the unique
-SA2 names for each SA2 have been used.
+The set of SA2 polygons for Tasmania, using the 2011 definition of SA2s, is accessed from the \pkg{absmapsdata} package.
+A single column of the data set is used to identify the unique areas.
+In this case, the unique SA2 names for each SA2 have been used.
 
-The Australian capital cities are used as focal points to allocate each
-geographic area around the closest capital city. Hobart will be the
-focal point for this example because only the state of Tasmania is being
-processed.
+The Australian capital cities are used as focal points to allocate each geographic area around the closest capital city.
+Hobart will be the focal point for this example because only the state of Tasmania is being processed.
 
-The buffer distance, hexagon size, hexagon amount to filter and width of
-angle are parameters that will be determined within
-\code{create\_hexmap}, if they are not provided. They are created as
-they are needed throughout the following example.
+The buffer distance, hexagon size, hexagon amount to filter and width of angle are parameters that will be determined within \code{create\_hexmap}, if they are not provided.
+They are created as they are needed throughout the following example.
 
-The results from various steps in the process are illustrated in Figure
-\ref{fig:filterprocess}.
+The results from various steps in the process are illustrated in Figure \ref{fig:filterprocess}.
 
 \hypertarget{derive-the-set-of-centroid-points}{%
-\subsubsection{Derive the set of centroid
-points}\label{derive-the-set-of-centroid-points}}
+\subsubsection{Derive the set of centroid points}\label{derive-the-set-of-centroid-points}}
 
-The set of polygons should be provided as an \pkg{sf} object, this is a
-data frame containing a \code{geometry} column. The \code{read\_shape}
-function can assist in creating this object for use in R.
+The set of polygons should be provided as an \pkg{sf} object, this is a data frame containing a \code{geometry} column. The \code{read\_shape} function can assist in creating this object for use in R.
 
-The centroids can be derived from an \pkg{sf} object using the
-\code{create\_centroids} function:
+The centroids can be derived from an \pkg{sf} object using the \code{create\_centroids} function:
 
 \hypertarget{step-1-create-the-hexagon-grid-points}{%
-\subsubsection{Step 1: Create the hexagon grid
-points}\label{step-1-create-the-hexagon-grid-points}}
+\subsubsection{Step 1: Create the hexagon grid points}\label{step-1-create-the-hexagon-grid-points}}
 
-A grid is created to allow tessellation of the hexagons that represent
-the geographic units. For a hexagon tile map, the grid of possible
-hexagon locations is made using the \code{create\_grid} function. It
-uses the centroids, the hexagon size and the buffer distance. Figure
-\ref{fig:filterprocess} 1a shows the initial locations of grid points
-created for Tasmania.
+A grid is created to allow tessellation of the hexagons that represent the geographic units.
+For a hexagon tile map, the grid of possible hexagon locations is made using the \code{create\_grid} function.
+It uses the centroids, the hexagon size and the buffer distance.
+Figure \ref{fig:filterprocess} 1a shows the initial locations of grid points created for Tasmania.
 
@@
 \hypertarget{a-creating-a-tessellated-grid}{%
-\paragraph{(a) Creating a tessellated
-grid}\label{a-creating-a-tessellated-grid}}
+\paragraph{(a) Creating a tessellated grid}\label{a-creating-a-tessellated-grid}}
 
-A set of longitude columns, and latitude rows are created to define the
-locations of the hexagons. The distance between each row and column is
-the size specified by \code{hex\_size}. Equally spaced columns are
-created from the minimum longitude minus the buffer distance, up to the
-maximum longitude plus the buffer distance. Similarly, the rows are
-created from the latitude values and the buffer distance. A unique
-hexagon location is created from all intersections of the longitude
-columns and latitude rows. Figure \ref{fig:filterprocess} 1a shows the
-hexagon grid after every second latitude row on the grid is shifted
-right, by half of the hexagon size.
+A set of longitude columns, and latitude rows are created to define the locations of the hexagons.
+The distance between each row and column is the size specified by \code{hex\_size}.
+Equally spaced columns are created from the minimum longitude minus the buffer distance, up to the maximum longitude plus the buffer distance.
+Similarly, the rows are created from the latitude values and the buffer distance.
+A unique hexagon location is created from all intersections of the longitude columns and latitude rows.
+Figure \ref{fig:filterprocess} 1a shows the hexagon grid after every second latitude row on the grid is shifted right, by half of the hexagon size.
 
@@
 
-Not all of the grid points will be used, especially if islands result in
-a large grid space. To filter the grid for appropriate hexagon locations
-for allocation, the \code{create\_grid} function will call the
-\code{create\_buffer} function. It finds the grid points needed to best
-capture the set of centroids on a hexagon tile map. Reducing the buffer
-can help to decrease the amount of time taken, as there will be less
-points over the water to consider for each centroid allocation.
+Not all of the grid points will be used, especially if islands result in a large grid space.
+To filter the grid for appropriate hexagon locations for allocation, the \code{create\_grid} function will call the \code{create\_buffer} function.
+It finds the grid points needed to best capture the set of centroids on a hexagon tile map.
+Reducing the buffer can help to decrease the amount of time taken, as there will be less points over the water to consider for each centroid allocation.
 
-Not all of the grid points will be used, especially if islands result in
-a large grid space. To filter the grid for appropriate hexagon locations
-for allocation, the \texttt{create\_grid} function will call the
-\texttt{create\_buffer} function. It finds the grid points needed to
-best capture the set of centroids on a hexagon tile map. Reducing the
-buffer can help to decrease the amount of time taken, as there will be
-less points over the water to consider for each centroid allocation.
+Not all of the grid points will be used, especially if islands result in a large grid space.
+To filter the grid for appropriate hexagon locations for allocation, the \texttt{create\_grid} function will call the \texttt{create\_buffer} function.
+It finds the grid points needed to best capture the set of centroids on a hexagon tile map.
+Reducing the buffer can help to decrease the amount of time taken, as there will be less points over the water to consider for each centroid allocation.
 
-The closest latitude row and longitude column are found for each
-centroid location. Then rows and columns of centroids are divided into
-20 groups. The amount of rows in each latitude group and the amount of
-columns in each longitude group are used as the width of rolling
-windows. The first rolling window step finds the minimum and maximum
-centroid values within each of the sliding window groups of longitude
-columns, and the groups of latitude rows. The second rolling window step
-finds the average of the rolling minimum and maximum centroid values,
-for the longitude columns and latitude rows.
+The closest latitude row and longitude column are found for each centroid location.
+Then rows and columns of centroids are divided into 20 groups.
+The amount of rows in each latitude group and the amount of columns in each longitude group are used as the width of rolling windows.
+The first rolling window step finds the minimum and maximum centroid values within each of the sliding window groups of longitude columns, and the groups of latitude rows.
+The second rolling window step finds the average of the rolling minimum and maximum centroid values, for the longitude columns and latitude rows.
 
-The hexagon grid points are kept only if they fall within the rolling
-average of the minimum and maximum centroid values after accounting for
-the buffer distance, for each row and column of the grid. Figure
-\ref{fig:filterprocess} 1b displays remaining hexagon grid points after
-applying the buffer filter. The sparsely populated South-West region of
-National Park has fewer points available in the water compared to the
-South-East region near the city of Hobart.
+The hexagon grid points are kept only if they fall within the rolling average of the minimum and maximum centroid values after accounting for the buffer distance, for each row and column of the grid.
+Figure \ref{fig:filterprocess} 1b displays remaining hexagon grid points after applying the buffer filter.
+The sparsely populated South-West region of National Park has fewer points available in the water compared to the South-East region near the city of Hobart.
 
 \hypertarget{centroid-to-focal-point-distance}{%
-\paragraph{Centroid to focal point
-distance}\label{centroid-to-focal-point-distance}}
+\paragraph{Centroid to focal point distance}\label{centroid-to-focal-point-distance}}
 
-The distance is calculated between each centroid in the set, and each of
-the focal points provided. The order for allocation is determined by the
-distance between the polygon centroid and it's closest focal point. For
-this example, this distance is only calculated for the capital city of
-Hobart, represented in Figure \ref{fig:filterprocess} 2a and 2b as a
-white cross.
+The distance is calculated between each centroid in the set, and each of the focal points provided.
+The order for allocation is determined by the distance between the polygon centroid and it's closest focal point.
+For this example, this distance is only calculated for the capital city of Hobart, represented in Figure \ref{fig:filterprocess} 2a and 2b as a white cross.
 
 \hypertarget{step-2-allocate-each-centroid-to-a-hexagon-grid-point}{%
-\subsubsection{Step 2: Allocate each centroid to a hexagon grid
-point}\label{step-2-allocate-each-centroid-to-a-hexagon-grid-point}}
+\subsubsection{Step 2: Allocate each centroid to a hexagon grid point}\label{step-2-allocate-each-centroid-to-a-hexagon-grid-point}}
 
-Allocation of all centroids requires the set of polygon centroids and
-the hexagon map grid. The polygon centroids are ordered from the
-centroid closest to the focal point(s), to the furthest. This will
-preserve spatial relationships with the focal point, as the inner city
-areas are allocated first and placed closest to the capital, the areas
-that are further will then be accommodated. The following example
-considers the first of the Statistical Areas at Level 2. Within the
-algorithm, these steps are repeated for each polygon.
+Allocation of all centroids requires the set of polygon centroids and the hexagon map grid.
+The polygon centroids are ordered from the centroid closest to the focal point(s), to the furthest.
+This will preserve spatial relationships with the focal point, as the inner city areas are allocated first and placed closest to the capital, the areas that are further will then be accommodated.
+The following example considers the first of the Statistical Areas at Level 2.
+Within the algorithm, these steps are repeated for each polygon.
 
@@
 \hypertarget{a-filter-the-grid-for-unassigned-hexagon-points}{%
-\paragraph{(a) Filter the grid for unassigned hexagon
-points}\label{a-filter-the-grid-for-unassigned-hexagon-points}}
+\paragraph{(a) Filter the grid for unassigned hexagon points}\label{a-filter-the-grid-for-unassigned-hexagon-points}}
 
-The set of possible hexagon grid points reduces by one after each
-centroid is allocated, then only the grid points that have not yet been
-selected are considered. Keeping only the available hexagon points
-prevents multiple geographic units from being allocated to the same
-hexagon. This is demonstrated in Figure \ref{fig:filterprocess} 2a and
-2b by the black hexagons that represent the seven closest polygons to
-the capital city of Hobart. As the allocation process begins for the
-eighth closest centroid there are seven unavailable hexagon locations.
+The set of possible hexagon grid points reduces by one after each centroid is allocated, then only the grid points that have not yet been selected are considered.
+Keeping only the available hexagon points prevents multiple geographic units from being allocated to the same hexagon.
+This is demonstrated in Figure \ref{fig:filterprocess} 2a and 2b by the black hexagons that represent the seven closest polygons to the capital city of Hobart.
+As the allocation process begins for the eighth closest centroid there are seven unavailable hexagon locations.
 
 \hypertarget{b-filter-the-grid-points-for-those-closest-to-the-centroid}{%
-\paragraph{(b) Filter the grid points for those closest to the
-centroid}\label{b-filter-the-grid-points-for-those-closest-to-the-centroid}}
+\paragraph{(b) Filter the grid points for those closest to the centroid}\label{b-filter-the-grid-points-for-those-closest-to-the-centroid}}
 
-A selection of possible hexagon locations around the centroid allows
-only the closest points that are not yet assigned to be considered. The
-number of possible hexagon locations to consider for a centroid is
-determined by the hexagon filter. This is the maximum amount of hexagons
-between the centroid and the furthest considered hexagon. It is used to
-subset possible grid points to only those surrounding the polygon
-centroid within an appropriate range. A smaller distance will increase
-speed, but can decrease accuracy when width of the angle increases.
+A selection of possible hexagon locations around the centroid allows only the closest points that are not yet assigned to be considered.
+The number of possible hexagon locations to consider for a centroid is determined by the hexagon filter.
+This is the maximum amount of hexagons between the centroid and the furthest considered hexagon.
+It is used to subset possible grid points to only those surrounding the polygon centroid within an appropriate range.
+A smaller distance will increase speed, but can decrease accuracy when width of the angle increases.
 
-The algorithm creates a circle of points, by only keeping points within
-a certain radial distance around the original centroid location.
+The algorithm creates a circle of points, by only keeping points within a certain radial distance around the original centroid location.
 
-The \code{width} parameter is used to take a slice of the remaining
-points. The width is the amount of degrees used on either side of the
-angle from the focal point to centroid location. This uses the angle
-from the closest capital city, to the current centroid as seen in Figure
-\ref{fig:filterprocess} 2a. This allows the spatial relationship to be
-preserved, even when it is allocated to a hexagon that is further from
-the focal point then the original centroid location.
+The \code{width} parameter is used to take a slice of the remaining points.
+The width is the amount of degrees used on either side of the angle from the focal point to centroid location.
+This uses the angle from the closest capital city, to the current centroid as seen in Figure \ref{fig:filterprocess} 2a.
+This allows the spatial relationship to be preserved, even when it is allocated to a hexagon that is further from the focal point then the original centroid location.
 
-\begin{Schunk}
 \begin{figure}
-\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/filterprocess-1} \caption[Illustration of key steps of the algorithm]{Illustration of key steps of the algorithm: (1a) full hexagon grid is created first; (1b) buffer is applied, shown as dark green circles, to accommodate irregularly shaped regions; (2a, 2b) allocation process, relative the center of Hobart, showing the 8th centroid to be allocated.
+\includegraphics[width=0.95\linewidth]{kobakian-cook_files/figure-latex/filterprocess-1} \caption{Illustration of key steps of the algorithm: (1a) full hexagon grid is created first; (1b) buffer is applied, shown as dark green circles, to accommodate irregularly shaped regions; (2a, 2b) allocation process, relative the center of Hobart, showing the 8th centroid to be allocated.
 The relationship between Hobart (the cross) and the centroid (the purple triangle) is used to filter the potential locations from the grid within a wedge.
@@
 \end{figure}
-\end{Schunk}
 
-If no available hexagon grid point is found within the original filter
-distance and angle, the distance is expanded and only when a maximum
-distance is reached will the angle expand to accommodate more possible
-grid points. By default the angle filter for the hexagon grid points
-create plus and minus 30 degree bounds of the angle from the focal point
-to the geographic centroid. This will increase if no points can be found
-within the \code{hex\_filter} distance. The default angle of 30 was
-chosen to allow the algorithm to find hexagons that best maintained the
-spatial relationship between the focal point and geographic centroid.
+If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded and only when a maximum distance is reached will the angle expand to accommodate more possible grid points.
+By default the angle filter for the hexagon grid points create plus and minus 30 degree bounds of the angle from the focal point to the geographic centroid.
+This will increase if no points can be found within the \code{hex\_filter} distance.
+The default angle of 30 was chosen to allow the algorithm to find hexagons that best maintained the spatial relationship between the focal point and geographic centroid.
 
@@
 
-Only two inputs are necessary to begin the algorithm; the shapefile, and
-the ID variable. The ID variable should uniquely identify each
-geographic unit in the shapefile.
+Only two inputs are necessary to begin the algorithm; the shapefile, and the ID variable. The ID variable should uniquely identify each geographic unit in the shapefile.
 
-The centroids are derived from the shapefile. The amount of centroids
-within the geographic map is used to determine an appropriate hexagon
-size if one is not provided. The derived centroids are a necessary input
-for an appropriate grid to be constructed. Each grid point is located a
-hexagon size distance from the next closest point in all six directions.
-The grid will initially cover the entire map space, encompassing all the
-centroid locations and will extend in all directions to the extent of
-the buffer distance. This buffer distance can be helpful to account for
-densely populated coastal areas, allowing the hexagon locations to
-spread beyond the coastline, over the sea.
+The centroids are derived from the shapefile.
+The amount of centroids within the geographic map is used to determine an appropriate hexagon size if one is not provided.
+The derived centroids are a necessary input for an appropriate grid to be constructed.
+Each grid point is located a hexagon size distance from the next closest point in all six directions.
+The grid will initially cover the entire map space, encompassing all the centroid locations and will extend in all directions to the extent of the buffer distance.
+This buffer distance can be helpful to account for densely populated coastal areas, allowing the hexagon locations to spread beyond the coastline, over the sea.
 
-The centroid set and hexagon tile map grid are necessary for the
-allocation process. Additionally, a set of reference locations can be
-provided as focal points, typically compact and/or densely populated
-areas such as major cities. The algorithm will use the focal points to
-create the order of allocation, prioritising the closest centroid
-locations to the focal points. The user can also specify the variable
-that should be used to determine the order for the allocation.
+The centroid set and hexagon tile map grid are necessary for the allocation process.
+Additionally, a set of reference locations can be provided as focal points, typically compact and/or densely populated areas such as major cities.
+The algorithm will use the focal points to create the order of allocation, prioritising the closest centroid locations to the focal points.
+The user can also specify the variable that should be used to determine the order for the allocation.
 
-When allocating representative hexagons, the width parameter can be used
-to determine the flexibility of positioning. Using the relationship with
-the nearest focal point, a larger width parameter will increase the
-amount of available hexagons nearer to the original centroid of the
-geographic unit. A smaller width will maintain the orientation from the
-focal point to the centroid when selecting the hexagon location.
+When allocating representative hexagons, the width parameter can be used to determine the flexibility of positioning.
+Using the relationship with the nearest focal point, a larger width parameter will increase the amount of available hexagons nearer to the original centroid of the geographic unit.
+A smaller width will maintain the orientation from the focal point to the centroid when selecting the hexagon location.
 However, this could mean it is placed further away.
@@
 
-Creating an animation connecting these two displays can allow users to
-grasp the meaning of the connected hexagons. It will also highlight the
-density of the communities using the rapid expansion of the inner-city
-areas, these hexagons will move the furthest and will move rapidly in
-the animation from their geographic locations. The rapid decrease in
-size of the large rural areas can show the large size of their
-collective landmass. The \CRANpkg{gganimate} \citep{gganimate} package
-can be used to make an animation. It connects the polygons for each area
-in the two displays using the \code{sf\_id} variable, the names of the
-statistical areas, and creates intermediate displays as they geographic
-areas shrink or expand to the chosen hexagon size.
+Creating an animation connecting these two displays can allow users to grasp the meaning of the connected hexagons.
+It will also highlight the density of the communities using the rapid expansion of the inner-city areas, these hexagons will move the furthest and will move rapidly in the animation from their geographic locations.
+The rapid decrease in size of the large rural areas can show the large size of their collective landmass.
+The \CRANpkg{gganimate} (Pedersen and Robinson 2019) package can be used to make an animation.
+It connects the polygons for each area in the two displays using the \code{sf\_id} variable, the names of the statistical areas, and creates intermediate displays as they geographic areas shrink or expand to the chosen hexagon size.
 
@@
 
-This work provides an algorithm called the hexagon tile map. It also
-describes how this algorithm addresses the potential issues found with
-contiguous, non-contiguous and Dorling cartograms when applied to
-Australia. It achieves a display that effectively presents the density
-of the population in small geographic areas and de-emphasises the large
-rural geographic space between the densely populated capital cities. The
-hexagon tile map display acknowledges that the amount of residents can
-differ but each administrative area is equally important. This solution
-uses equally sized areas, and maintain neighbourhood boundary
-connections.
+This work provides an algorithm called the hexagon tile map.
+It also describes how this algorithm addresses the potential issues found with contiguous, non-contiguous and Dorling cartograms when applied to Australia.
+It achieves a display that effectively presents the density of the population in small geographic areas and de-emphasises the large rural geographic space between the densely populated capital cities.
+The hexagon tile map display acknowledges that the amount of residents can differ but each administrative area is equally important.
+This solution uses equally sized areas, and maintain neighbourhood boundary connections.
 
-The hexagon tile map display acknowledges that the amount of residents
-can differ but each administrative area is equally important. This
-solution uses equally sized areas, and maintain neighbourhood boundary
-connections. The \pkg{sugarbag} package for R automates the creation of
-tessellated hexagon tile maps by providing an algorithm to design these
-displays. The Australian application preserves spatial relationships,
-and emphasises capital cities. However, similar to the choropleth map
-display the tessellation does not allow the size of the hexagons to
-represent another variable. The algorithm is heavily dependent on the
-focal points used, as this determines the order of allocation. With
-careful consideration of the choropleth map, the small geographic inner
-city areas may not have been noticed by viewers, but the hexagon tile
-map display emphasises them. The communities in northern Tasmania and
-the Northern territory do not draw attention because of their size as in
-the choropleth, but their colour is still noticeably below average when
-contrasted with the hexagons in New South Wales.
+The hexagon tile map display acknowledges that the amount of residents can differ but each administrative area is equally important.
+This solution uses equally sized areas, and maintain neighbourhood boundary connections.
+The \pkg{sugarbag} package for R automates the creation of tessellated hexagon tile maps by providing an algorithm to design these displays.
+The Australian application preserves spatial relationships, and emphasises capital cities.
+However, similar to the choropleth map display the tessellation does not allow the size of the hexagons to represent another variable.
+The algorithm is heavily dependent on the focal points used, as this determines the order of allocation.
+With careful consideration of the choropleth map, the small geographic inner city areas may not have been noticed by viewers, but the hexagon tile map display emphasises them.
+The communities in northern Tasmania and the Northern territory do not draw attention because of their size as in the choropleth, but their colour is still noticeably below average when contrasted with the hexagons in New South Wales.
 
-Australia is used as an example, because it represents an extreme sparse
-geography and small dense population areas which produces unsatisfactory
-results with all existing cartogram-type algorithms. However, the
-algorithm is sufficiently general to apply to other geographic regions,
-and indeed has been applied to make hexagon maps of the UK, USA and
-France.
+Australia is used as an example, because it represents an extreme sparse geography and small dense population areas which produces unsatisfactory results with all existing cartogram-type algorithms.
+However, the algorithm is sufficiently general to apply to other geographic regions, and indeed has been applied to make hexagon maps of the UK, USA and France.
 
-There are many possible extensions to the algorithm that might be
-valuable future work. The buffer allows extension beyond the furthest
-centroids, but there is no mechanism to protect borders to force
-centroids are placed within the geographic borders of a region
-(e.g.~country or state). The algorithm is also currently limited to
-representing each geographic area with only one hexagon. In the filter
-step for final selection of a hexagon grid point for each centroid, a
-direct angle constraint is currently implemented, but it may narrowly
-miss potentially better hexagon allocation. Some other constraints, such
-as a logarithmic function may help to choose refine the final allocation
-to hexagons closer to the original centroid location. In a country like
-Australia, the vast centre produces a hexagon map with small isolated
-hexagons, even when the city centres are hugely expanded. It could be
-useful to allow variable sized hexagons, primarily to increase the size
-of the isolated hexagons to improve their visibility.
+There are many possible extensions to the algorithm that might be valuable future work.
+The buffer allows extension beyond the furthest centroids, but there is no mechanism to protect borders to force centroids are placed within the geographic borders of a region (e.g.~country or state).
+The algorithm is also currently limited to representing each geographic area with only one hexagon.
+In the filter step for final selection of a hexagon grid point for each centroid, a direct angle constraint is currently implemented, but it may narrowly miss potentially better hexagon allocation.
+Some other constraints, such as a logarithmic function may help to choose refine the final allocation to hexagons closer to the original centroid location.
+In a country like Australia, the vast centre produces a hexagon map with small isolated hexagons, even when the city centres are hugely expanded.
+It could be useful to allow variable sized hexagons, primarily to increase the size of the isolated hexagons to improve their visibility.
 
-This new algorithm provides an effective start point for automatically
-creating hexagon tile maps for any spatial polygon data, and contributes
-to an extensive body of work that encourages the use of alternative map
-displays for statistical displays of spatial data.
+This new algorithm provides an effective start point for automatically creating hexagon tile maps for any spatial polygon data, and contributes to an extensive body of work that encourages the use of alternative map displays for statistical displays of spatial data.
+
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-abs2011}{}}%
+Australian Bureau of Statistics. 2011. {``{Statistical Area Level 2 (SA2) ASGS Ed 2011 Digital Boundaries in ESRI Shapefile Format}.''} data cube: ESRI Shapefile, cat. no. 1270.0.55.001. 2011.
+
+\leavevmode\vadjust pre{\hypertarget{ref-TACA}{}}%
+Cancer Council Queensland, Queensland University of Technology, and Cooperative Research Centre for Spatial Information. 2018. {``{Australian Cancer Atlas}.''} \url{https://atlas.cancer.org.au}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-MDAC}{}}%
+Cano, R. G., K. Buchin, T. Castermans, A. Pieterse, W. Sonke, and B. Speckmann. 2015. {``{Mosaic Drawings and Cartograms}.''} In \emph{Computer Graphics Forum}, 34:361--70. 3. Wiley Online Library.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ACTUC}{}}%
+Dorling, Daniel. 2011. {``Area Cartograms: Their Use and Creation.''} In \emph{Concepts and Techniques in Modern Geography (CATMOG)}, 59:252--60. \url{https://doi.org/10.1002/9780470979587.ch33}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-TVSSS}{}}%
+---------. 2012. \emph{{The Visualisation of Spatial Social Structure}}. John Wiley; Sons Ltd.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ACCAC}{}}%
+Dougenik, James A., Nicholas R.
+Chrisman, and Duane R.
+Niemeyer.
+1985.
+{``{An Algorithm to Construct Continuous Area Cartograms}.''} \emph{The Professional Geographer} 37 (1): 75--81.
+\url{https://doi.org/10.1111/j.0033-0124.1985.00075.x}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ECGC}{}}%
+Keim, D.
+A, S.
+C North, C Panse, and J Schneidewind.
+2002.
+{``{Efficient Cartogram Generation: A Comparison}.''} In \emph{{IEEE Symposium on Information Visualization, 2002.
+INFOVIS 2002}}, 2002:33--36.
+IEEE.
+
+\leavevmode\vadjust pre{\hypertarget{ref-CBATCC}{}}%
+Kocmoud, C, and D House. 1998. {``{A Constraint-based Approach to Constructing Continuous Cartograms}.''} In \emph{Proc. Symp. Spatial Data Handling}, 236--46.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ORC}{}}%
+Kreveld, Marc van, and Bettina Speckmann. 2007. {``On {R}ectangular {C}artograms.''} \emph{{Computational Geometry}} 37 (3): 175--87. \url{https://doi.org/10.1016/j.comgeo.2006.06.002}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-TAAM}{}}%
+Levison, M. E., and W. Haddon Jr. 1965. {``{The Area Adjusted Map. An Epidemiologic Device}.''} Journal Article. \emph{Public Health Reports} 80: 55--59.
+
+\leavevmode\vadjust pre{\hypertarget{ref-SAMGIS}{}}%
+Moore, Dale A., and Tim E.
+Carpenter.
+1999.
+{``{Spatial Analytical Methods and Geographic Information Systems: Use in Health Research and Epidemiology}.''} \emph{Epidemiologic Reviews} 21 (2): 143--61.
+\url{https://doi.org/10.1093/oxfordjournals.epirev.a017993}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-NAC}{}}%
+Olson, Judy M. 1976. {``{Noncontiguous Area Cartograms}.''} \emph{The Professional Geographer} 28 (4): 371--80. \url{https://doi.org/10.1111/j.0033-0124.1976.00371.x}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sf}{}}%
+Pebesma, Edzer. 2018. {``{Simple Features for R: Standardized Support for Spatial Vector Data}.''} \emph{{The R Journal}} 10 (1): 439--46. \url{https://doi.org/10.32614/RJ-2018-009}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gganimate}{}}%
+Pedersen, Thomas Lin, and David Robinson. 2019. \emph{{gganimate: A Grammar of Animated Graphics}}. \url{https://CRAN.R-project.org/package=gganimate}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-statebins}{}}%
+Rudis, Bob. 2020. \emph{Statebins: Create United States Uniform Cartogram Heatmaps}. \url{https://CRAN.R-project.org/package=statebins}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-BCM}{}}%
+Skowronnek, Alsino.
+2016.
+{``{Beyond Choropleth Maps -- A Review of Techniques to Visualize Quantitative Areal Geodata}.''} {Infovis Reading Group WS 2015/16}.
+2016.
+\url{https://alsino.io/static/papers/BeyondChoropleths_AlsinoSkowronnek.pdf}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-EI}{}}%
+Tufte, Edward R. 1990. \emph{Envisioning Information}. Graphics Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-PH}{}}%
+Vit, Patricia, Silvia R. M. Pedro, and David Roubik. 2013. \emph{{Pot-Honey: A legacy of stingless bees}}. Springer-Verlag New York. \url{http://dx.doi.org/10.1007/978-1-4614-4960-7}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-DMAHP}{}}%
+Walter, S. D. 2001. \emph{{Disease Mapping: A Historical Perspective}}. Oxford University Press. https://doi.org/\url{https://dx.doi.org/10.1093/acprof:oso/9780198515326.003.0012}.
+
+\end{CSLReferences}
 
@@
 Stephanie Kobakian\\
-Monash University\\%
-Department of Econometrics and Business Statistics\\
+\\%
+Sydney, Australia\\
 %
@@
 %
-\href{mailto:stephanie.kobakian@monash.edu}{\nolinkurl{stephanie.kobakian@monash.edu}}%
+\href{mailto:stephanie.kobakian@gmail.com}{\nolinkurl{stephanie.kobakian@gmail.com}}%
 }

### 2023-01-09 kobakian-cook.Rmd
Change to align R code file to code of the Rmd

@@
 author:
-  # see ?rjournal_article for more information
   - name: Stephanie Kobakian
@@
   theme(
-    panel.background = element_rect(fill = "black", colour = NA), 
-    plot.background = element_rect(fill = "black", colour = NA),
+    panel.background = element_rect(fill = "transparent", colour = NA), 
+    plot.background = element_rect(fill = "transparent", colour = NA),
     legend.background = element_rect(fill = "transparent", colour = NA),
@@
     text = element_text(colour = "white"),
-    axis.text = element_blank()
+    axis.text = element_text(colour = "white")
   )
@@
   filter(!sa2_name_2011 == "Lord Howe Island")
-# sa2 <- sa2 %>% rmapshaper::ms_simplify(keep = 0.05, keep_shapes = TRUE)
+
 SIR <- read_csv("data/SIR Downloadable Data.csv") %>% 
@@
 
+## Check the projection uses long and lat
 ## Create centroids set
-centroids <- sa2 %>% 
+sa2centroids <- sa2 %>% 
   create_centroids(., "sa2_name_2011")
 ## Create hexagon grid
-grid <- create_grid(centroids = centroids,
+# For speed, consider if the buffer distance beyond the centroids is necessary
+grid <- create_grid(centroids = sa2centroids,
                     hex_size = 0.1,
-                    buffer_dist = 5)
+                    buffer_dist = 4, verbose = TRUE)
 ## Allocate polygon centroids to hexagon grid points
+# This is a time consuming process for a large data set
 aus_hexmap <- allocate(
-  centroids = centroids,
+  centroids = sa2centroids,
   hex_grid = grid,
@@
   ## same column used in create_centroids
-  hex_size = 0.2,
-  ## same size used in create_grid
-  hex_filter = 10,
+  hex_size = 0.1,
+  hex_filter = 8,
   focal_points = capital_cities,
-  width = 35,
-  verbose = FALSE
-)
+  width = 25,
+  verbose = TRUE)
 save(aus_hexmap, file = "data/aus_hexmap.rda") 
@@
 # Projected data 
-sa2thyroid_ERP <- st_transform(sa2thyroid_ERP, 3112) %>% 
+sa2thyroid_ERP <- st_transform(sa2thyroid_ERP, crs = 3112) %>% 
   filter(state_name_2011 == "Tasmania")
 sa2thyroid_ERP <- sa2thyroid_ERP %>% 
-  #mutate(sva = sqrt(as.numeric(Population)/as.numeric(albers_sqkm)))
   mutate(sva = sqrt(as.numeric(Population)/as.numeric(areasqkm_2011)))
@@
   scale_fill_identity() + guides(fill = "none") +
-  theme_map() #+ ggtitle("a")
+  theme_map()
 #tas_ggcont
@@
   guides(fill = "none") +
-  theme_map() #+ ggtitle("b")
-#tas_ggncont
+  theme_map() 
 ```
@@
 #library(gridExtra)
-#grid.arrange(tas_ggcont, tas_ggncont, tas_ggdorl, ncol=3)
 cowplot::plot_grid(tas_ggcont, 
@@
                    labels = c("a", "b", "c"))
-
 ```

### 2023-01-09 kobakian-cook.tex
Change to align R code file to code of the Rmd

--- 2022-06-02 kobakian-cook.tex
@@
 misrepresent the spatial distributions of human related statistics due
-to area-size bias \citep{BCM}. Figure \ref{fig:choro} is a choropleth
-map that uses colour to display the estimated standardised incidence
-ratios (SIRs) of thyroid cancer for females, in each of the Statistical
-Areas at Level 2 (SA2) used by the \citet{abs2011}. The Australian
-choropleth map display draws attention to the expanse of dark and light
-blue areas across the rural communities in all states. The SA2s on the
-east coast around Brisbane and in northern New South Wales stand out as
-more orange and red. However, this display neglects the vast amount of
-Australia residents living in the densely populated capital cities.
+to area-size bias \citep{BCM}.
+
+The Australian Cancer Atlas is an online, interactive display of
+Australian cancer statistics in each of the Statistical Areas at Level 2
+(SA2s), used by the \citet{abs2011}. The estimated standardised
+incidence ratios (SIRs) of thyroid cancer for females was downloaded
+from the publicly accessible Australian Cancer Atlas website and
+presented in Figure \ref{fig:choro}, a choropleth map that uses colour
+to display the distribution. The Australian choropleth map display draws
+attention to the expanse of dark and light blue areas across the rural
+communities in all states. The SA2s on the east coast around Brisbane
+and in northern New South Wales stand out as more orange and red.
+However, this display neglects the vast amount of Australia residents
+living in the densely populated capital cities.
 

### 2023-01-09 kobakian-cook.R

@@ -1,21 +1,21 @@
-# Plots
+## R Code for the paper "A Hexagon Tile Map Algorithm for Displaying Spatial Data"
 
-## Libraries 
-
-library(absmapsdata)
-library(tidyverse)
+## ----setup----------------------------------------------------------------------------------------
 library(cartogram)
-library(ggthemes)
 library(cowplot)
-library(sf)
+library(gridExtra)
+library(ggthemes)
+library(knitcitations)
+library(kableExtra)
 library(sp)
+library(sf)
+library(sugarbag)
+library(tidyverse)
 
-## Data 
 # Rda files sourced from: https://github.com/wfmackey/absmapsdata
 load("data/sa22011.Rda")
 load("data/state2011.Rda")
 
-### Theme set up
 
 invthm <- theme_map() + 
   theme(
@@ -27,157 +27,190 @@ invthm <- theme_map() +
     axis.text = element_text(colour = "white")
   )
 
-## States of Australia
-
-states <- absmapsdata::state2011 %>% 
-  filter(state_name_2011 != "Other Territories")
-
-###############################################################################
-###########################        ABS AREAS        ###########################
-## sa2
-sa2 <- absmapsdata::sa22011 %>% 
-  filter(state_name_2011 != "Other Territories") %>% st_transform(., crs = 3112)
-
-sa2_map <- ggplot(sa2) + 
-  geom_sf(aes(fill = albers_sqkm)) +
-  scale_fill_distiller(type = "seq", palette = "BuGn",  direction = 1, na.value = "light grey") + 
-  theme_void() +
-  coord_sf(crs = 3112) +
-   theme(legend.position ="left", legend.title = element_text("Area (sqkm)"))
-
-ggsave(filename = "figures/aus_sa2.png", plot = sa2_map,
-  device = "png", bg = "transparent", dpi = 300,  width = 10, height = 8)
-
-
-###############################################################################
-###########################     CARTOGRAMS
-# 
-# ERP <- read_csv("data/ERP.csv")
-# 
-# ERP_sa4 <- ERP %>% filter(`Geography Level` == "Statistical Area Level 4", Time == 2011) %>% arrange(`Geography Level`)
-# 
[…]

### 2023-01-09 version1/kobakian-cook.R

@@ -1,12 +1,20 @@
-# Young statisticians conference presentation plots
+# Plots
 
-library(absmapsdata)
+## Libraries 
 library(tidyverse)
 library(cartogram)
-library(ggthemes)
 library(cowplot)
+library(gganimate)
+library(ggthemes)
+library(gridExtra)
 library(sf)
 library(sp)
+library(sugarbag)
+
+## Data 
+# Rda files sourced from: https://github.com/wfmackey/absmapsdata
+load("data/sa22011.Rda")
+load("data/state2011.Rda")
 
 ### Theme set up
 
@@ -22,18 +30,22 @@ invthm <- theme_map() +
 
 ## States of Australia
 
-states <- absmapsdata::state2011 %>% 
+states <- state2011 %>% 
   filter(state_name_2011 != "Other Territories")
 
 ###############################################################################
 ###########################        ABS AREAS        ###########################
 ## sa2
-sa2 <- absmapsdata::sa22011 %>% 
-  filter(state_name_2011 != "Other Territories") %>% st_transform(., crs = 3112)
+sa2 <- sa22011 %>% 
+  filter(!st_is_empty(geometry)) %>% 
+  filter(!state_name_2011 == "Other Territories") %>% 
+  filter(!sa2_name_2011 == "Lord Howe Island") %>% 
+  st_transform(., crs = 3112)
 
 sa2_map <- ggplot(sa2) + 
-  geom_sf(aes(fill = albers_sqkm)) +
-  scale_fill_distiller(type = "seq", palette = "BuGn",  direction = 1, na.value = "light grey") + 
+  geom_sf(aes(fill = areasqkm_2011)) +
+  scale_fill_distiller(type = "seq", palette = "BuGn", 
+                       direction = 1, na.value = "light grey") + 
   theme_void() +
   coord_sf(crs = 3112) +
    theme(legend.position ="left", legend.title = element_text("Area (sqkm)"))
@@ -64,15 +76,14 @@ SIR <- read_csv("data/SIR Downloadable Data.csv")
 
 sa2 <- sa2 %>% 
   filter((sa2_name_2011 %in% SIR$SA2_name)) 
-save(sa2, file = "")
-# 
+
 # SIR_persons <- SIR %>% 
 #   filter(Year=="2010-2014") %>% 
 #   filter(Sex_name =="Persons") %>% 
[…]

### 2023-01-09 kobakian-cook.Rmd
small changes to code

@@
   geom_polygon(aes(x = long,  y = lat,  group = interaction(sa2_name_2011, polygon)),
-               fill = "black",  colour = "darkgrey",  size = 0.1, data = fort_aus) +
+               fill = "black",  colour = "darkgrey",  linewidth = 0.1, data = fort_aus) +
   geom_polygon(aes(x = long, y = lat, group = hex_id, fill = SIR), data = fort_hex) +
@@
 # Non - Contiguous Dorling Cartograms
+if (!file.exists("data/dorl.rda")) {
   dorl <- sa2thyroid_ERP %>% 
     filter(!is.na(Population)) %>% 
-  #mutate(pop = (Population/max(Population))*10) %>% # helpful for all of Australia
+  # mutate(pop = (Population/max(Population))*10) %>% # helpful for all of Australia
     cartogram_dorling(., weight = "Population", k = 0.2, m_weight = 1) %>% st_as_sf()
+  save(dorl, file = "data/dorl.rda")
+}
+
+load("data/dorl.rda")
 d <- st_bbox(dorl)
@@
   theme_map() #+ ggtitle("c")
-#tas_ggdorl
 ```
@@
 The Dorling expands the metropolitan regions."}
-#library(gridExtra)
 cowplot::plot_grid(tas_ggcont, 

### 2023-01-09 kobakian-cook.R

@@ -1,6 +1,16 @@
-## R Code for the paper "A Hexagon Tile Map Algorithm for Displaying Spatial Data"
+## ----defaults, echo=FALSE, message=FALSE, warning=FALSE, comment = FALSE----
+knitr::opts_chunk$set(warning = FALSE, 
+                      message = FALSE, 
+                      comment = FALSE,
+                      echo = FALSE,
+                      eval = TRUE,
+                      out.width = "95%",
+                      retina = 3,
+                      dev = "png",
+                      dpi = 300)
 
-## ----setup----------------------------------------------------------------------------------------
+
+## ----setup----------------------------------------------------
 library(cartogram)
 library(cowplot)
 library(gridExtra)
@@ -15,6 +25,10 @@ library(tidyverse)
 # Rda files sourced from: https://github.com/wfmackey/absmapsdata
 load("data/sa22011.Rda")
 load("data/state2011.Rda")
+
+library(RefManageR)
+options("citation_format" = "pandoc")
+BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')
 
 
 invthm <- theme_map() + 
@@ -40,7 +54,7 @@ aus_colours <- function(sir_p50){
 }
 
 
-## ----thyroiddata----------------------------------------------------------------------------------
+## ----thyroiddata----------------------------------------------
 sa2 <- sa22011 %>% 
   filter(!st_is_empty(geometry)) %>% 
   filter(!state_name_2011 == "Other Territories") %>% 
@@ -114,13 +128,13 @@ fort_aus <- sa2thyroid_ERP %>%
 ## Make a plot
 aus_hexmap_plot <- ggplot() +
   geom_polygon(aes(x = long,  y = lat,  group = interaction(sa2_name_2011, polygon)),
-               fill = "black",  colour = "darkgrey",  size = 0.1, data = fort_aus) +
+               fill = "black",  colour = "darkgrey",  linewidth = 0.1, data = fort_aus) +
   geom_polygon(aes(x = long, y = lat, group = hex_id, fill = SIR), data = fort_hex) +
   scale_fill_identity() +
   invthm + coord_equal()
 
 
-## ----contcart-------------------------------------------------------------------------------------
[…]

### 2023-01-09 kobakian-cook.Rmd
small changes to code

@@
   theme_map()
-#tas_ggcont
 ```

### 2023-01-09 kobakian-cook.R

@@ -157,8 +157,6 @@ tas_ggcont <- ggplot(cont) +
   geom_sf(aes(fill = SIR), colour = "grey", size = 0.01) + 
   scale_fill_identity() + guides(fill = "none") +
   theme_map()
-#tas_ggcont
-
 
 ## ----ncontcart------------------------------------------------
 # Non - Contiguous Cartograms

### 2023-07-12 kobakian-cook.Rmd
Review comments addressed

@@
 Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
-The algorithm presented creates a display that uses tessellated hexagons to represent a set of spatial polygons, and is implemented in the R package called sugarbag.
-It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units, in light of their positions to points of interest.
+The algorithm presented here creates a display that uses tessellated hexagons to represent a set of spatial polygons, and is implemented in the R package called sugarbag.
+It allocates these hexagons in a manner that preserves the spatial relationship of the geographic units, in light of their positions to points of interest.
 The display showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps.
@@
 
-Over time, the density of living in major cities has increased as residents have gathered to live near urban areas [@ACTUC].
-The division of these residents into approximately equal population areas results in dramatically different square meterage of administrative geographic units, such as states or electorates.
+Over time, the population density in major cities has increased as residents have gathered to live near urban areas [@ACTUC].
+Populations tend to be distributed unevenly across geographic regions.
+When comparing sets of administrative geographic units such as states or electorates, area size is seldom proportional to the population size.
 In a choropleth map display, the geographic units are coloured to represent the value of the statistic for each unit [@EI].
@@
 The Australian Cancer Atlas is an online, interactive display of Australian cancer statistics in each of the Statistical Areas at Level 2 (SA2s), used by the @abs2011.
-The estimated standardised incidence ratios (SIRs) of thyroid cancer
-for females was downloaded from the publicly accessible Australian Cancer Atlas website and presented in Figure \@ref(fig:choro), a choropleth map that uses colour to display the distribution.
+The dataset of estimated standardised incidence ratios (SIRs) of thyroid cancer for females was downloaded from the publicly accessible Australian Cancer Atlas website and presented in Figure \@ref(fig:choro), a choropleth map that uses colour to display the distribution.
 The Australian choropleth map display draws attention to the expanse of dark and light blue areas across the rural communities in all states.
 The SA2s on the east coast around Brisbane and in northern New South Wales stand out as more orange and red.
-However, this display neglects the vast amount of Australia residents living in the densely populated capital cities.
+However, this display neglects the vast amount of Australian residents living in the densely populated capital cities.
 
@@
 The solutions to this visualisation problem begin with the geography.
-Alternative maps can be created to shift the focus from land area and shape to the value of the statistics [@ACCAC].
-Each style of cartogram applies a different transformation to the geographic areas, to highlight the values of the statistic of interest.
+Alternative maps can be created to shift the focus from land area and shape to the value of the statistics [@ACCAC] in a cartogram display.
+Cartogram methods apply different transformations to the geographic areas, to highlight the values of the statistic of interest.
 Alternative maps can result in a distortion of the map space to represent features of the distribution across the areas [@ACCAC] as the statistic of interest is used to determine the cartogram layout.
 
-Alternative mapping methods, like cartograms implemented in \CRANpkg{cartogram}, allow increased understanding of the spatial distribution of a variable across the population, by fairly representing the population in each administrative area [@TAAM].
+Alternative mapping methods, like cartograms implemented in \CRANpkg{cartogram} [@cartogram] for R [@R], promote better understanding of the spatial distribution of a variable across the population, by representing the population in each administrative area fairly [@TAAM].
 This acknowledges that the number of residents can be different and also recognises that each area, or person within it is equally important.
@@
 <!-- choropleth -->
-The familiar choropleth map display is often used to allow the user to orient themselves.
-However, the emphasis on the land mass diminishes the features of the distribution in densely populated communities due to the small size on the display [@ACTUC].
+Typically, chloropleth maps are used to orient the users within the geographic context.
+However, the strong salience of the land mass can hide or downplay the features of the distribution in densely populated communities due to the small size on the display [@ACTUC].
 The unique shapes of boundaries can be helpful for orienting users but may not contribute to their understanding of the spatial disease distribution as many of the communities are not visible in a choropleth display [@TVSSS].
@@
 There are several established alternative visualisation methods.
-Rectangular cartograms [@ORC] and Dorling cartograms [@ACTUC] implemented in \pkg{cartogram} and tile maps implemented in \CRANpkg{tilemaps}, all use one simple shape to represent each geographic unit.
-They all minimise the emphasis on the size or shape of the geographic areas.
-These alternative map displays focus on the relationship between neighbours, attempting to preserve connections, and disregard the unique shapes of the administrative boundaries.
+Rectangular cartograms [@ORC] and Dorling cartograms [@ACTUC] implemented in \pkg{cartogram} and tile maps implemented in \CRANpkg{tilemaps} [@tilemaps], all use one simple shape to represent each geographic unit.
+They all minimise the salience of the size or shape of geographic areas.
+These alternative map displays highlight the relationship between neighbours, preserve connections, and discard the unique shapes of the administrative boundaries.
 Figure \@ref(fig:tasdisplays) shows a collection of alternative map displays, this includes a) a contiguous cartogram, b) a non-contiguous cartogram, and c) a Dorling cartogram.
 
-```{r fullhexmap, fig.cap = "A hexagon tile map of Australia at SA2 level.
+```{r fullhexmap, fig.cap = "A hexagon tile map of Australia at SA2 level showing the reference undistorted maps (grey) and carotgrams (blue).
 The colours communicate the value of the estimated SIR of thyroid cancer for females, ranging from much lower than average (blue) to much higher than average (red)"}
@@
 When communicating information that is relevant to the population, each member of the population can be given equal representation by transforming the map [@TVSSS].
-The connected communities can be recognised by allowing the boundaries to maintain connection in the transformed display.
+The connectedness of the units can be preserved by using transformations that maintain the connection between boundaries.
 The contiguous cartogram displayed in Figure \@ref(fig:tasdisplays)a draws attention to smaller geographic units when they are rescaled according to the population [@DMAHP].
@@
 The amount of background space can be meaningful in non-contiguous cartograms [@ECGC].
+However, the relative size of units in comparison to the reference unit can lead to scaling issues.
 The size disparity between rural areas and urban areas result in reasonable display within the south eastern city of Hobart, but these units are not visible in the context of the Tasmania state map.
@@
 This map draws attention to the collection of coastal cities in Tasmania that were not apparent in Figure \@ref(fig:tasdisplays) a or b.
-This display also highlights that the approximation of equal population is not easy to fulfil, as there is some disparity in the sizes of the circles.
+This display also highlights the difference in the population of each unit, as there is some disparity in the sizes of the circles.
 
-It is also common to treat all geographic units as equal, so that regardless of the population or other information, to generate equal size spatial polygons.
+Another common practice is to use equal-sized polygons and treat all geographic units as equal.
 The Dorling algorithm can be induced to do this, to make equallly sized circles.
 @MDAC describes a group of alternative maps called "mosaic cartograms" for tile displays.
-The geography of the USA has been transformed into a square-binned tile map manually and made available in the R package \CRANpkg{statebins} [@statebins].The algorithm described below is an automatic layout of hexagon tiles, where a continguity constraint is relaxed.
+Similarly, the geography of USA has been transformed into a square-binned tile map manually and made available in the R package \CRANpkg{statebins} [@statebins].The algorithm described below generates an automatic layout of hexagon tiles, where a continguity constraint is relaxed.
 This gives equal weight to each geographic area even if the population differs.
@@
 
-The purpose of this algorithm is to create an alternative map display that highlights the spatial distributions for populations.
+The purpose of this algorithm is to create an alternative map display that highlights distributional features across wide ranges of geographical area size and population density.
 There has been an increasing need for displays that recognise the large number of people that live in dense urban environments.
@@
 
-Compared to the choropleth map display in Figure \@ref(fig:choro), the low rates in the rural Australian communities are no longer dominating the display.
-While the representative hexagons are still visible against the black background, the much lower than average rates in rural Australia are less noticeable.
+Compared to the choropleth map display in Figure \@ref(fig:choro), the low rates in the rural Australian communities no longer dominate the display.
+While the corresponding hexagons are still visible against the black background, the lower rates in rural Australia are less prominent.
 
@@
 First, derive the set of centroids from the polygons provided, then create the grid of hexagon locations.
-These two processes are defined in the blue left column of the flow chart in figure \@ref(fig:sugarbagflow).
+These two processes are described in the blue left column of the flow chart in figure \@ref(fig:sugarbagflow).
 Each centroid can then be allocated to an available hexagon location.
 The steps for the allocation process are detailed in the right column of Figure \@ref(fig:sugarbagflow).
-There are several filter steps to speed the process of selecting an appropriate hexagon to represent each geographic unit.
+There are several filter steps to speed up the process of selecting an appropriate hexagon to represent each geographic unit.
 To make tessellated plots with the hexagon allocations, the point locations are converted into hexagon shapes.
@@
 
-Hexagon tile maps can be useful to understand a distribution across a collection of geographic areas.
+Hexagon tile maps can be useful for visualising distributions across a collection of geographic areas.
 However, these maps are not easy to create manually, especially as the number of areas increases.
-This algorithm was created to automate this process, and reduce the manual load involved in creating and implementing alternative displays.
+This algorithm was developed to automate the process, and reduce the workload involved in creating and implementing alternative displays.
 This allows map makers and data communicators to spend their time choosing the most effective display.
@@
 The \pkg{sugarbag} package contains a set of functions that help R users to create a hexagon tile map.
-The algorithm presented in the \pkg{sugarbag} package operates on a set of simple feature geometry objects , known as \CRANpkg{sf} objects[@sf].
+The algorithm presented in the \pkg{sugarbag} package operates on a set of simple feature geometry objects , known as \CRANpkg{sf} objects [@sf].
 This package allows R users to create \pkg{sf} objects by importing polygons stored in various formats.
@@
 
-A user can tweak the parameters of the hexagon map using the additional arguments to the \code{create\_hexmap} function, but these options may affect the speed of the algorithm. 
+The user can tweak the parameters of the hexagon map using additional arguments to the \code{create\_hexmap} function, but these options may affect the speed of the algorithm. 
 The hexagon size may need adjustments depending on the density of the population; users can provide an appropriate hexagon size and re-run the algorithm.
@@
 
-If a user would like to perform each of the steps of the algorithm themselves, the necessary inputs will change for each function.
-For example, the \code{allocate} function can be used directly when a user wishes to use a set of centroids, rather than polygons.
+If a user would like to perform steps of the algorithm themselves, additional user input will be needed for the functions that perform each step.
+For example, if the user wishes to use a set of centroids, rather than polygons, the \code{allocate} function can be used directly.
 
-The set of SA2 polygons for Tasmania, using the 2011 definition of SA2s, is accessed from the \pkg{absmapsdata} package.
+The set of SA2 polygons for Tasmania, using the 2011 definition of SA2s, was accessed from the \pkg{absmapsdata} package [@absmapsdata].
 A single column of the data set is used to identify the unique areas.
@@
 It finds the grid points needed to best capture the set of centroids on a hexagon tile map.
-Reducing the buffer can help to decrease the amount of time taken, as there will be less points over the water to consider for each centroid allocation.
+Reducing the buffer size will decrease the amount of time that the algorithm needs to run for, as there will be less points over the water to consider for each centroid allocation.
 
-Not all of the grid points will be used, especially if islands result in a large grid space.
-To filter the grid for appropriate hexagon locations for allocation, the `create_grid` function will call the `create_buffer` function.
-It finds the grid points needed to best capture the set of centroids on a hexagon tile map.
-Reducing the buffer can help to decrease the amount of time taken, as there will be less points over the water to consider for each centroid allocation.
-
-The closest latitude row and longitude column are found for each centroid location.
+For each centroid location, the closest latitude row and longitude column are found.
 Then rows and columns of centroids are divided into 20 groups.
-The amount of rows in each latitude group and the amount of columns in each longitude group are used as the width of rolling windows.
+The number of rows in each latitude group and the number of columns in each longitude group are used as the width of rolling windows.
 The first rolling window step finds the minimum and maximum centroid values within each of the sliding window groups of longitude columns, and the groups of latitude rows.
@@
 
-Allocation of all centroids requires the set of polygon centroids and the hexagon map grid.
+To allocate all centroids the set of polygon centroids and the hexagon map grid are required.
 The polygon centroids are ordered from the centroid closest to the focal point(s), to the furthest.
-This will preserve spatial relationships with the focal point, as the inner city areas are allocated first and placed closest to the capital, the areas that are further will then be accommodated.
+This preserves spatial relationships with the focal point, as the inner city areas are allocated first and placed closest to the capital, the areas that are further will then be accommodated.
 The following example considers the first of the Statistical Areas at Level 2.
@@
 
-The set of possible hexagon grid points reduces by one after each centroid is allocated, then only the grid points that have not yet been selected are considered.
+After each centroid is located, it is removed from the set of grid points, and is no longer considered in the next step.
 Keeping only the available hexagon points prevents multiple geographic units from being allocated to the same hexagon.
@@
 
-A selection of possible hexagon locations around the centroid allows only the closest points that are not yet assigned to be considered.
+The algorithm creates a circle of points, by only keeping points within a certain radial distance around the original centroid location.
+Only the hexagons which are close to the centroid and have not been assigned are considered.
 The number of possible hexagon locations to consider for a centroid is determined by the hexagon filter.
-This is the maximum amount of hexagons between the centroid and the furthest considered hexagon.
+This is the maximum number of hexagons between the centroid and the furthest considered hexagon.
 It is used to subset possible grid points to only those surrounding the polygon centroid within an appropriate range.
 A smaller distance will increase speed, but can decrease accuracy when width of the angle increases.
-
-The algorithm creates a circle of points, by only keeping points within a certain radial distance around the original centroid location.
 
@@
 The \code{width} parameter is used to take a slice of the remaining points.
-The width is the amount of degrees used on either side of the angle from the focal point to centroid location.
+The slice centres on the angle from the focal point to centroid location.
 This uses the angle from the closest capital city, to the current centroid as seen in Figure \@ref(fig:filterprocess) 2a.
@@
 The centroids are derived from the shapefile.
-The amount of centroids within the geographic map is used to determine an appropriate hexagon size if one is not provided.
-The derived centroids are a necessary input for an appropriate grid to be constructed.
-Each grid point is located a hexagon size distance from the next closest point in all six directions.
-The grid will initially cover the entire map space, encompassing all the centroid locations and will extend in all directions to the extent of the buffer distance.
-This buffer distance can be helpful to account for densely populated coastal areas, allowing the hexagon locations to spread beyond the coastline, over the sea.
+The number of centroids within the geographic map is used to determine an appropriate hexagon size if one is not provided.
+The centroids are used to construct a grid.
+The grid initially covers the entire map, encompassing all the centroid locations and extending in all directions up to the buffer distance.
+This buffer distance can help to account for densely populated coastal areas, allowing the hexagon locations to spread beyond the coastline.
 
@@
 
-This work provides an algorithm called the hexagon tile map.
-It also describes how this algorithm addresses the potential issues found with contiguous, non-contiguous and Dorling cartograms when applied to Australia.
+The present work describes an algorithm called the hexagon tile map.
+It also shows how this algorithm addresses the potential issues found with contiguous, non-contiguous and Dorling cartograms when applied to the geography of Australia.
 It achieves a display that effectively presents the density of the population in small geographic areas and de-emphasises the large rural geographic space between the densely populated capital cities.
@@
 The Australian application preserves spatial relationships, and emphasises capital cities.
-However, similar to the choropleth map display the tessellation does not allow the size of the hexagons to represent another variable.
-The algorithm is heavily dependent on the focal points used, as this determines the order of allocation.
+However, similar to the choropleth map display, the tessellation does not allow the size of the hexagons to represent another variable.
+The algorithm is heavily dependent on the location and number of focal points used, as this determines the order of allocation.
 With careful consideration of the choropleth map, the small geographic inner city areas may not have been noticed by viewers, but the hexagon tile map display emphasises them.
@@
 
-Australia is used as an example, because it represents an extreme sparse geography and small dense population areas which produces unsatisfactory results with all existing cartogram-type algorithms.
+Australia serves as a good use case for the algorithm as it represents an extremely sparse geography and small dense population areas which cannot be satisfactorily represented by existing cartogram-like algorithms.
 However, the algorithm is sufficiently general to apply to other geographic regions, and indeed has been applied to make hexagon maps of the UK, USA and France.
 
-There are many possible extensions to the algorithm that might be valuable future work.
-The buffer allows extension beyond the furthest centroids, but there is no mechanism to protect borders to force centroids are placed within the geographic borders of a region (e.g.
+There are many possible extensions to the algorithm that might prove valuable in the future.
+The buffer allows extension beyond the furthest centroids, but there is no mechanism to protect borders by forcing centroids to be located within the geographic borders of a set of regions (e.g.
 country or state).
-The algorithm is also currently limited to representing each geographic area with only one hexagon.
+The algorithm is also currently limited to representing each geographic area with one hexagon only.
 In the filter step for final selection of a hexagon grid point for each centroid, a direct angle constraint is currently implemented, but it may narrowly miss potentially better hexagon allocation.
-Some other constraints, such as a logarithmic function may help to choose refine the final allocation to hexagons closer to the original centroid location.
-In a country like Australia, the vast centre produces a hexagon map with small isolated hexagons, even when the city centres are hugely expanded.
+Some other constraints, such as a logarithmic function may help to refine the final allocation to hexagons closer to the original centroid location.
+In a country like Australia, the vast empty interior produces a hexagon map with many small isolated hexagons, even when the city centres are hugely expanded.
 It could be useful to allow variable sized hexagons, primarily to increase the size of the isolated hexagons to improve their visibility.

### 2023-07-12 kobakian-cook.tex
Review comments addressed

@@
 Applications are increasingly widespread, especially in the areas of
-disease mapping, and election results. The algorithm presented creates a
-display that uses tessellated hexagons to represent a set of spatial
-polygons, and is implemented in the R package called sugarbag. It
-allocates these hexagon in a manner that preserves the spatial
+disease mapping, and election results. The algorithm presented here
+creates a display that uses tessellated hexagons to represent a set of
+spatial polygons, and is implemented in the R package called sugarbag.
+It allocates these hexagons in a manner that preserves the spatial
 relationship of the geographic units, in light of their positions to
@@
 
-Over time, the density of living in major cities has increased as
-residents have gathered to live near urban areas \citep{ACTUC}. The
-division of these residents into approximately equal population areas
-results in dramatically different square meterage of administrative
-geographic units, such as states or electorates. In a choropleth map
-display, the geographic units are coloured to represent the value of the
-statistic for each unit \citep{EI}. This can cause some values to be
-emphasised over others, and allows choropleth map displays to
-misrepresent the spatial distributions of human related statistics due
-to area-size bias \citep{BCM}.
+Over time, the population density in major cities has increased as
+residents have gathered to live near urban areas \citep{ACTUC}.
+Populations tend to be distributed unevenly across geographic regions.
+When comparing sets of administrative geographic units such as states or
+electorates, area size is seldom proportional to the population size. In
+a choropleth map display, the geographic units are coloured to represent
+the value of the statistic for each unit \citep{EI}. This can cause some
+values to be emphasised over others, and allows choropleth map displays
+to misrepresent the spatial distributions of human related statistics
+due to area-size bias \citep{BCM}.
 
@@
 Australian cancer statistics in each of the Statistical Areas at Level 2
-(SA2s), used by the \citet{abs2011}. The estimated standardised
-incidence ratios (SIRs) of thyroid cancer for females was downloaded
-from the publicly accessible Australian Cancer Atlas website and
-presented in Figure \ref{fig:choro}, a choropleth map that uses colour
-to display the distribution. The Australian choropleth map display draws
-attention to the expanse of dark and light blue areas across the rural
-communities in all states. The SA2s on the east coast around Brisbane
-and in northern New South Wales stand out as more orange and red.
-However, this display neglects the vast amount of Australia residents
-living in the densely populated capital cities.
+(SA2s), used by the \citet{abs2011}. The dataset of estimated
+standardised incidence ratios (SIRs) of thyroid cancer for females was
+downloaded from the publicly accessible Australian Cancer Atlas website
+and presented in Figure \ref{fig:choro}, a choropleth map that uses
+colour to display the distribution. The Australian choropleth map
+display draws attention to the expanse of dark and light blue areas
+across the rural communities in all states. The SA2s on the east coast
+around Brisbane and in northern New South Wales stand out as more orange
+and red. However, this display neglects the vast amount of Australian
+residents living in the densely populated capital cities.
 
@@
 Alternative maps can be created to shift the focus from land area and
-shape to the value of the statistics \citep{ACCAC}. Each style of
-cartogram applies a different transformation to the geographic areas, to
-highlight the values of the statistic of interest. Alternative maps can
-result in a distortion of the map space to represent features of the
-distribution across the areas \citep{ACCAC} as the statistic of interest
-is used to determine the cartogram layout.
+shape to the value of the statistics \citep{ACCAC} in a cartogram
+display. Cartogram methods apply different transformations to the
+geographic areas, to highlight the values of the statistic of interest.
+Alternative maps can result in a distortion of the map space to
+represent features of the distribution across the areas \citep{ACCAC} as
+the statistic of interest is used to determine the cartogram layout.
 
 Alternative mapping methods, like cartograms implemented in
-\CRANpkg{cartogram}, allow increased understanding of the spatial
-distribution of a variable across the population, by fairly representing
-the population in each administrative area \citep{TAAM}. This
-acknowledges that the number of residents can be different and also
-recognises that each area, or person within it is equally important.
+\CRANpkg{cartogram} \citep{cartogram} for R \citep{R}, promote better
+understanding of the spatial distribution of a variable across the
+population, by representing the population in each administrative area
+fairly \citep{TAAM}. This acknowledges that the number of residents can
+be different and also recognises that each area, or person within it is
+equally important.
 
@@
 
-The familiar choropleth map display is often used to allow the user to
-orient themselves. However, the emphasis on the land mass diminishes the
-features of the distribution in densely populated communities due to the
-small size on the display \citep{ACTUC}. The unique shapes of boundaries
-can be helpful for orienting users but may not contribute to their
-understanding of the spatial disease distribution as many of the
-communities are not visible in a choropleth display \citep{TVSSS}.
+Typically, chloropleth maps are used to orient the users within the
+geographic context. However, the strong salience of the land mass can
+hide or downplay the features of the distribution in densely populated
+communities due to the small size on the display \citep{ACTUC}. The
+unique shapes of boundaries can be helpful for orienting users but may
+not contribute to their understanding of the spatial disease
+distribution as many of the communities are not visible in a choropleth
+display \citep{TVSSS}.
 
@@
 implemented in \pkg{cartogram} and tile maps implemented in
-\CRANpkg{tilemaps}, all use one simple shape to represent each
-geographic unit. They all minimise the emphasis on the size or shape of
-the geographic areas. These alternative map displays focus on the
-relationship between neighbours, attempting to preserve connections, and
-disregard the unique shapes of the administrative boundaries. Figure
+\CRANpkg{tilemaps} \citep{tilemaps}, all use one simple shape to
+represent each geographic unit. They all minimise the salience of the
+size or shape of geographic areas. These alternative map displays
+highlight the relationship between neighbours, preserve connections, and
+discard the unique shapes of the administrative boundaries. Figure
 \ref{fig:tasdisplays} shows a collection of alternative map displays,
@@
 member of the population can be given equal representation by
-transforming the map \citep{TVSSS}. The connected communities can be
-recognised by allowing the boundaries to maintain connection in the
-transformed display. The contiguous cartogram displayed in Figure
+transforming the map \citep{TVSSS}. The connectedness of the units can
+be preserved by using transformations that maintain the connection
+between boundaries. The contiguous cartogram displayed in Figure
 \ref{fig:tasdisplays}a draws attention to smaller geographic units when
@@
 cartogram \citep{NAC}. The amount of background space can be meaningful
-in non-contiguous cartograms \citep{ECGC}. The size disparity between
-rural areas and urban areas result in reasonable display within the
-south eastern city of Hobart, but these units are not visible in the
-context of the Tasmania state map. Depending on the difference between
-the population and geographic land size, the amount of white space can
-also prevent meaningful understanding of the distribution \citep{TVSSS}.
+in non-contiguous cartograms \citep{ECGC}. However, the relative size of
+units in comparison to the reference unit can lead to scaling issues.
+The size disparity between rural areas and urban areas result in
+reasonable display within the south eastern city of Hobart, but these
+units are not visible in the context of the Tasmania state map.
+Depending on the difference between the population and geographic land
+size, the amount of white space can also prevent meaningful
+understanding of the distribution \citep{TVSSS}.
 
@@
 of coastal cities in Tasmania that were not apparent in Figure
-\ref{fig:tasdisplays} a or b. This display also highlights that the
-approximation of equal population is not easy to fulfil, as there is
-some disparity in the sizes of the circles.
+\ref{fig:tasdisplays} a or b. This display also highlights the
+difference in the population of each unit, as there is some disparity in
+the sizes of the circles.
 
-It is also common to treat all geographic units as equal, so that
-regardless of the population or other information, to generate equal
-size spatial polygons. The Dorling algorithm can be induced to do this,
-to make equallly sized circles. \citet{MDAC} describes a group of
-alternative maps called ``mosaic cartograms'' for tile displays. The
-geography of the USA has been transformed into a square-binned tile map
-manually and made available in the R package \CRANpkg{statebins}
-\citep{statebins}.The algorithm described below is an automatic layout
-of hexagon tiles, where a continguity constraint is relaxed. This gives
-equal weight to each geographic area even if the population differs.
+Another common practice is to use equal-sized polygons and treat all
+geographic units as equal. The Dorling algorithm can be induced to do
+this, to make equallly sized circles. \citet{MDAC} describes a group of
+alternative maps called ``mosaic cartograms'' for tile displays.
+Similarly, the geography of USA has been transformed into a
+square-binned tile map manually and made available in the R package
+\CRANpkg{statebins} \citep{statebins}.The algorithm described below
+generates an automatic layout of hexagon tiles, where a continguity
+constraint is relaxed. This gives equal weight to each geographic area
+even if the population differs.
 
@@
 The purpose of this algorithm is to create an alternative map display
-that highlights the spatial distributions for populations. There has
-been an increasing need for displays that recognise the large number of
-people that live in dense urban environments. The algorithm intends to
-maintain the spatial relationships of a group of geographic units using
-the relationship between each unit and the closest focal point. The
+that highlights distributional features across wide ranges of
+geographical area size and population density. There has been an
+increasing need for displays that recognise the large number of people
+that live in dense urban environments. The algorithm intends to maintain
+the spatial relationships of a group of geographic units using the
+relationship between each unit and the closest focal point. The
 algorithm allocates geographic units to a representative hexagon, in
@@
 Compared to the choropleth map display in Figure \ref{fig:choro}, the
-low rates in the rural Australian communities are no longer dominating
-the display. While the representative hexagons are still visible against
-the black background, the much lower than average rates in rural
-Australia are less noticeable.
+low rates in the rural Australian communities no longer dominate the
+display. While the corresponding hexagons are still visible against the
+black background, the lower rates in rural Australia are less prominent.
 
@@
 derive the set of centroids from the polygons provided, then create the
-grid of hexagon locations. These two processes are defined in the blue
+grid of hexagon locations. These two processes are described in the blue
 left column of the flow chart in figure \ref{fig:sugarbagflow}. Each
@@
 Figure \ref{fig:sugarbagflow}. There are several filter steps to speed
-the process of selecting an appropriate hexagon to represent each
+up the process of selecting an appropriate hexagon to represent each
 geographic unit. To make tessellated plots with the hexagon allocations,
@@
 
-Hexagon tile maps can be useful to understand a distribution across a
+Hexagon tile maps can be useful for visualising distributions across a
 collection of geographic areas. However, these maps are not easy to
 create manually, especially as the number of areas increases. This
-algorithm was created to automate this process, and reduce the manual
-load involved in creating and implementing alternative displays. This
-allows map makers and data communicators to spend their time choosing
-the most effective display.
+algorithm was developed to automate the process, and reduce the workload
+involved in creating and implementing alternative displays. This allows
+map makers and data communicators to spend their time choosing the most
+effective display.
 
@@
 \pkg{sugarbag} package operates on a set of simple feature geometry
-objects , known as \CRANpkg{sf} objects\citep{sf}. This package allows R
-users to create \pkg{sf} objects by importing polygons stored in various
-formats. Users should provide a set of polygons that define geographic
-units by their administrative boundaries. The functions arrange the
-geographic units in order of proximity to a set of locations provided,
-such as the centre of major cities. The centroid location of each
-geographic unit is used to measure the proximity. It emphasises the
+objects , known as \CRANpkg{sf} objects \citep{sf}. This package allows
+R users to create \pkg{sf} objects by importing polygons stored in
+various formats. Users should provide a set of polygons that define
+geographic units by their administrative boundaries. The functions
+arrange the geographic units in order of proximity to a set of locations
+provided, such as the centre of major cities. The centroid location of
+each geographic unit is used to measure the proximity. It emphasises the
 major cities as population hubs, rather than emphasizing the size of
@@
 
-A user can tweak the parameters of the hexagon map using the additional
+The user can tweak the parameters of the hexagon map using additional
 arguments to the \code{create\_hexmap} function, but these options may
@@
 
-If a user would like to perform each of the steps of the algorithm
-themselves, the necessary inputs will change for each function. For
-example, the \code{allocate} function can be used directly when a user
-wishes to use a set of centroids, rather than polygons.
+If a user would like to perform steps of the algorithm themselves,
+additional user input will be needed for the functions that perform each
+step. For example, if the user wishes to use a set of centroids, rather
+than polygons, the \code{allocate} function can be used directly.
 
 The set of SA2 polygons for Tasmania, using the 2011 definition of SA2s,
-is accessed from the \pkg{absmapsdata} package. A single column of the
-data set is used to identify the unique areas. In this case, the unique
-SA2 names for each SA2 have been used.
+was accessed from the \pkg{absmapsdata} package \citep{absmapsdata}. A
+single column of the data set is used to identify the unique areas. In
+this case, the unique SA2 names for each SA2 have been used.
 
@@
 capture the set of centroids on a hexagon tile map. Reducing the buffer
-can help to decrease the amount of time taken, as there will be less
-points over the water to consider for each centroid allocation.
+size will decrease the amount of time that the algorithm needs to run
+for, as there will be less points over the water to consider for each
+centroid allocation.
 
-Not all of the grid points will be used, especially if islands result in
-a large grid space. To filter the grid for appropriate hexagon locations
-for allocation, the \texttt{create\_grid} function will call the
-\texttt{create\_buffer} function. It finds the grid points needed to
-best capture the set of centroids on a hexagon tile map. Reducing the
-buffer can help to decrease the amount of time taken, as there will be
-less points over the water to consider for each centroid allocation.
-
-The closest latitude row and longitude column are found for each
-centroid location. Then rows and columns of centroids are divided into
-20 groups. The amount of rows in each latitude group and the amount of
+For each centroid location, the closest latitude row and longitude
+column are found. Then rows and columns of centroids are divided into 20
+groups. The number of rows in each latitude group and the number of
 columns in each longitude group are used as the width of rolling
@@
 
-Allocation of all centroids requires the set of polygon centroids and
-the hexagon map grid. The polygon centroids are ordered from the
-centroid closest to the focal point(s), to the furthest. This will
-preserve spatial relationships with the focal point, as the inner city
-areas are allocated first and placed closest to the capital, the areas
-that are further will then be accommodated. The following example
-considers the first of the Statistical Areas at Level 2. Within the
-algorithm, these steps are repeated for each polygon.
+To allocate all centroids the set of polygon centroids and the hexagon
+map grid are required. The polygon centroids are ordered from the
+centroid closest to the focal point(s), to the furthest. This preserves
+spatial relationships with the focal point, as the inner city areas are
+allocated first and placed closest to the capital, the areas that are
+further will then be accommodated. The following example considers the
+first of the Statistical Areas at Level 2. Within the algorithm, these
+steps are repeated for each polygon.
 
@@
 
-The set of possible hexagon grid points reduces by one after each
-centroid is allocated, then only the grid points that have not yet been
-selected are considered. Keeping only the available hexagon points
-prevents multiple geographic units from being allocated to the same
-hexagon. This is demonstrated in Figure \ref{fig:filterprocess} 2a and
-2b by the black hexagons that represent the seven closest polygons to
-the capital city of Hobart. As the allocation process begins for the
-eighth closest centroid there are seven unavailable hexagon locations.
+After each centroid is located, it is removed from the set of grid
+points, and is no longer considered in the next step. Keeping only the
+available hexagon points prevents multiple geographic units from being
+allocated to the same hexagon. This is demonstrated in Figure
+\ref{fig:filterprocess} 2a and 2b by the black hexagons that represent
+the seven closest polygons to the capital city of Hobart. As the
+allocation process begins for the eighth closest centroid there are
+seven unavailable hexagon locations.
 
@@
 
-A selection of possible hexagon locations around the centroid allows
-only the closest points that are not yet assigned to be considered. The
-number of possible hexagon locations to consider for a centroid is
-determined by the hexagon filter. This is the maximum amount of hexagons
-between the centroid and the furthest considered hexagon. It is used to
-subset possible grid points to only those surrounding the polygon
-centroid within an appropriate range. A smaller distance will increase
-speed, but can decrease accuracy when width of the angle increases.
-
 The algorithm creates a circle of points, by only keeping points within
-a certain radial distance around the original centroid location.
+a certain radial distance around the original centroid location. Only
+the hexagons which are close to the centroid and have not been assigned
+are considered. The number of possible hexagon locations to consider for
+a centroid is determined by the hexagon filter. This is the maximum
+number of hexagons between the centroid and the furthest considered
+hexagon. It is used to subset possible grid points to only those
+surrounding the polygon centroid within an appropriate range. A smaller
+distance will increase speed, but can decrease accuracy when width of
+the angle increases.
 
 The \code{width} parameter is used to take a slice of the remaining
-points. The width is the amount of degrees used on either side of the
-angle from the focal point to centroid location. This uses the angle
-from the closest capital city, to the current centroid as seen in Figure
-\ref{fig:filterprocess} 2a. This allows the spatial relationship to be
-preserved, even when it is allocated to a hexagon that is further from
-the focal point then the original centroid location.
+points. The slice centres on the angle from the focal point to centroid
+location. This uses the angle from the closest capital city, to the
+current centroid as seen in Figure \ref{fig:filterprocess} 2a. This
+allows the spatial relationship to be preserved, even when it is
+allocated to a hexagon that is further from the focal point then the
+original centroid location.
 
@@
 
-The centroids are derived from the shapefile. The amount of centroids
+The centroids are derived from the shapefile. The number of centroids
 within the geographic map is used to determine an appropriate hexagon
-size if one is not provided. The derived centroids are a necessary input
-for an appropriate grid to be constructed. Each grid point is located a
-hexagon size distance from the next closest point in all six directions.
-The grid will initially cover the entire map space, encompassing all the
-centroid locations and will extend in all directions to the extent of
-the buffer distance. This buffer distance can be helpful to account for
-densely populated coastal areas, allowing the hexagon locations to
-spread beyond the coastline, over the sea.
+size if one is not provided. The centroids are used to construct a grid.
+The grid initially covers the entire map, encompassing all the centroid
+locations and extending in all directions up to the buffer distance.
+This buffer distance can help to account for densely populated coastal
+areas, allowing the hexagon locations to spread beyond the coastline.
 
@@
 
-This work provides an algorithm called the hexagon tile map. It also
-describes how this algorithm addresses the potential issues found with
-contiguous, non-contiguous and Dorling cartograms when applied to
-Australia. It achieves a display that effectively presents the density
-of the population in small geographic areas and de-emphasises the large
-rural geographic space between the densely populated capital cities. The
-hexagon tile map display acknowledges that the amount of residents can
-differ but each administrative area is equally important. This solution
-uses equally sized areas, and maintain neighbourhood boundary
-connections.
+The present work describes an algorithm called the hexagon tile map. It
+also shows how this algorithm addresses the potential issues found with
+contiguous, non-contiguous and Dorling cartograms when applied to the
+geography of Australia. It achieves a display that effectively presents
+the density of the population in small geographic areas and
+de-emphasises the large rural geographic space between the densely
+populated capital cities. The hexagon tile map display acknowledges that
+the amount of residents can differ but each administrative area is
+equally important. This solution uses equally sized areas, and maintain
+neighbourhood boundary connections.
 
@@
 and emphasises capital cities. However, similar to the choropleth map
-display the tessellation does not allow the size of the hexagons to
+display, the tessellation does not allow the size of the hexagons to
 represent another variable. The algorithm is heavily dependent on the
-focal points used, as this determines the order of allocation. With
-careful consideration of the choropleth map, the small geographic inner
-city areas may not have been noticed by viewers, but the hexagon tile
-map display emphasises them. The communities in northern Tasmania and
-the Northern territory do not draw attention because of their size as in
-the choropleth, but their colour is still noticeably below average when
-contrasted with the hexagons in New South Wales.
+location and number of focal points used, as this determines the order
+of allocation. With careful consideration of the choropleth map, the
+small geographic inner city areas may not have been noticed by viewers,
+but the hexagon tile map display emphasises them. The communities in
+northern Tasmania and the Northern territory do not draw attention
+because of their size as in the choropleth, but their colour is still
+noticeably below average when contrasted with the hexagons in New South
+Wales.
 
-Australia is used as an example, because it represents an extreme sparse
-geography and small dense population areas which produces unsatisfactory
-results with all existing cartogram-type algorithms. However, the
-algorithm is sufficiently general to apply to other geographic regions,
-and indeed has been applied to make hexagon maps of the UK, USA and
-France.
+Australia serves as a good use case for the algorithm as it represents
+an extremely sparse geography and small dense population areas which
+cannot be satisfactorily represented by existing cartogram-like
+algorithms. However, the algorithm is sufficiently general to apply to
+other geographic regions, and indeed has been applied to make hexagon
+maps of the UK, USA and France.
 
-There are many possible extensions to the algorithm that might be
-valuable future work. The buffer allows extension beyond the furthest
-centroids, but there is no mechanism to protect borders to force
-centroids are placed within the geographic borders of a region
-(e.g.~country or state). The algorithm is also currently limited to
-representing each geographic area with only one hexagon. In the filter
-step for final selection of a hexagon grid point for each centroid, a
-direct angle constraint is currently implemented, but it may narrowly
-miss potentially better hexagon allocation. Some other constraints, such
-as a logarithmic function may help to choose refine the final allocation
-to hexagons closer to the original centroid location. In a country like
-Australia, the vast centre produces a hexagon map with small isolated
-hexagons, even when the city centres are hugely expanded. It could be
-useful to allow variable sized hexagons, primarily to increase the size
-of the isolated hexagons to improve their visibility.
+There are many possible extensions to the algorithm that might prove
+valuable in the future. The buffer allows extension beyond the furthest
+centroids, but there is no mechanism to protect borders by forcing
+centroids to be located within the geographic borders of a set of
+regions (e.g.~country or state). The algorithm is also currently limited
+to representing each geographic area with one hexagon only. In the
+filter step for final selection of a hexagon grid point for each
+centroid, a direct angle constraint is currently implemented, but it may
+narrowly miss potentially better hexagon allocation. Some other
+constraints, such as a logarithmic function may help to refine the final
+allocation to hexagons closer to the original centroid location. In a
+country like Australia, the vast empty interior produces a hexagon map
+with many small isolated hexagons, even when the city centres are hugely
+expanded. It could be useful to allow variable sized hexagons, primarily
+to increase the size of the isolated hexagons to improve their
+visibility.
 

### 2023-07-12 version1/kobakian-cookOLD.R

@@ -1,0 +1,539 @@
+## R code
+
+#Libraries
+library(cartogram)
+library(cowplot)
+library(gridExtra)
+library(ggthemes)
+library(sp)
+library(sf)
+library(sugarbag)
+library(tidyverse)
+
+# Rda files sourced from: https://github.com/wfmackey/absmapsdata
+load("data/sa22011.Rda")
+load("data/state2011.Rda")
+
+invthm <- theme_map() + 
+  theme(
+    panel.background = element_rect(fill = "transparent", colour = NA), 
+    plot.background = element_rect(fill = "transparent", colour = NA),
+    legend.background = element_rect(fill = "transparent", colour = NA),
+    legend.key = element_rect(fill = "transparent", colour = NA),
+    text = element_text(colour = "white"),
+    axis.text = element_text(colour = "white")
+  )
+
+# function to allocate colours to regions
+aus_colours <- function(sir_p50){
+  value <- case_when(
+    sir_p50 <  0.74 ~ "#33809d",
+    sir_p50 >= 0.74 & sir_p50 < 0.98 ~ "#aec6c7",
+    sir_p50 >= 0.98 & sir_p50 < 1.05 ~ "#fff4bc",
+    sir_p50 >= 1.05 & sir_p50 < 1.45 ~ "#ff9a64",
+    sir_p50 >= 1.45 ~ "#ff3500",
+    TRUE ~ "#FFFFFF")
+  return(value)
+}
+
+
+## ----thyroiddata------------------------------------------------------------------
+sa2 <- sa22011 %>% 
+  filter(!st_is_empty(geometry)) %>% 
+  filter(!state_name_2011 == "Other Territories") %>% 
+  filter(!sa2_name_2011 == "Lord Howe Island") %>% 
+  st_transform(., crs = 3112)
+
+SIR <- read_csv("data/SIR Downloadable Data.csv") %>% 
+  filter(SA2_name %in% sa2$sa2_name_2011) %>% 
+  dplyr::select(Cancer_name, SA2_name, Sex_name, p50) %>% 
+  filter(Cancer_name == "Thyroid", Sex_name == "Females")
+ERP <- read_csv("data/ERP.csv") %>%
+  filter(REGIONTYPE == "SA2", Time == 2011, Region %in% SIR$SA2_name) %>% 
+  dplyr::select(Region, Value)
+
+# Alternative maps
+# Join with sa2 sf object
[…]

### 2023-07-12 kobakian-cook.Rmd
added orcids

@@
     email:  stephanie.kobakian@gmail.com 
+    orcid: 0000-0002-4616-0048 
   - name: Dianne Cook
@@
     email:  dicook@monash.edu
+    orcid: 0000-0002-3813-7155 
   - name: Earl Duncan
@@
     email:  earl.duncan@qut.edu.au
+    orcid: 0000-0002-5146-7810 
 abstract: >

### 2023-07-13 kobakian-cook.tex

--- 2022-10-17 kobakian-cook.tex
@@
 \title{A Hexagon Tile Map Algorithm for Displaying Spatial Data}
+
 \author{by Stephanie Kobakian, Dianne Cook, and Earl Duncan}
@@
 
-Over time, the density of living in major cities has increased as residents have gathered to live near urban areas (Dorling 2011).
-The division of these residents into approximately equal population areas results in dramatically different square meterage of administrative geographic units, such as states or electorates.
+Over time, the population density in major cities has increased as residents have gathered to live near urban areas (Dorling 2011).
+Populations tend to be distributed unevenly across geographic regions.
+When comparing sets of administrative geographic units such as states or electorates, area size is seldom proportional to the population size.
 In a choropleth map display, the geographic units are coloured to represent the value of the statistic for each unit (Tufte 1990).
@@
 The Australian Cancer Atlas is an online, interactive display of Australian cancer statistics in each of the Statistical Areas at Level 2 (SA2s), used by the Australian Bureau of Statistics (2011).
-The estimated standardised incidence ratios (SIRs) of thyroid cancer
-for females was downloaded from the publicly accessible Australian Cancer Atlas website and presented in Figure \ref{fig:choro}, a choropleth map that uses colour to display the distribution.
+The dataset of estimated standardised incidence ratios (SIRs) of thyroid cancer for females was downloaded from the publicly accessible Australian Cancer Atlas website and presented in Figure \ref{fig:choro}, a choropleth map that uses colour to display the distribution.
 The Australian choropleth map display draws attention to the expanse of dark and light blue areas across the rural communities in all states.
 The SA2s on the east coast around Brisbane and in northern New South Wales stand out as more orange and red.
-However, this display neglects the vast amount of Australia residents living in the densely populated capital cities.
+However, this display neglects the vast amount of Australian residents living in the densely populated capital cities.
 
@@
 The solutions to this visualisation problem begin with the geography.
-Alternative maps can be created to shift the focus from land area and shape to the value of the statistics (Dougenik, Chrisman, and Niemeyer 1985).
-Each style of cartogram applies a different transformation to the geographic areas, to highlight the values of the statistic of interest.
+Alternative maps can be created to shift the focus from land area and shape to the value of the statistics (Dougenik, Chrisman, and Niemeyer 1985) in a cartogram display.
+Cartogram methods apply different transformations to the geographic areas, to highlight the values of the statistic of interest.
 Alternative maps can result in a distortion of the map space to represent features of the distribution across the areas (Dougenik, Chrisman, and Niemeyer 1985) as the statistic of interest is used to determine the cartogram layout.
 
-Alternative mapping methods, like cartograms implemented in \CRANpkg{cartogram}, allow increased understanding of the spatial distribution of a variable across the population, by fairly representing the population in each administrative area (Levison and Haddon Jr 1965).
+Alternative mapping methods, like cartograms implemented in \CRANpkg{cartogram} (Jeworutzki 2020) for R (R Core Team 2012), promote better understanding of the spatial distribution of a variable across the population, by representing the population in each administrative area fairly (Levison and Haddon Jr 1965).
 This acknowledges that the number of residents can be different and also recognises that each area, or person within it is equally important.
@@
 
-The familiar choropleth map display is often used to allow the user to orient themselves.
-However, the emphasis on the land mass diminishes the features of the distribution in densely populated communities due to the small size on the display (Dorling 2011).
+Typically, chloropleth maps are used to orient the users within the geographic context.
+However, the strong salience of the land mass can hide or downplay the features of the distribution in densely populated communities due to the small size on the display (Dorling 2011).
 The unique shapes of boundaries can be helpful for orienting users but may not contribute to their understanding of the spatial disease distribution as many of the communities are not visible in a choropleth display (Dorling 2012).
@@
 There are several established alternative visualisation methods.
-Rectangular cartograms (Kreveld and Speckmann 2007) and Dorling cartograms (Dorling 2011) implemented in \pkg{cartogram} and tile maps implemented in \CRANpkg{tilemaps}, all use one simple shape to represent each geographic unit.
-They all minimise the emphasis on the size or shape of the geographic areas.
-These alternative map displays focus on the relationship between neighbours, attempting to preserve connections, and disregard the unique shapes of the administrative boundaries.
+Rectangular cartograms (Kreveld and Speckmann 2007) and Dorling cartograms (Dorling 2011) implemented in \pkg{cartogram} and tile maps implemented in \CRANpkg{tilemaps} (Rosenberg 2020), all use one simple shape to represent each geographic unit.
+They all minimise the salience of the size or shape of geographic areas.
+These alternative map displays highlight the relationship between neighbours, preserve connections, and discard the unique shapes of the administrative boundaries.
 Figure \ref{fig:tasdisplays} shows a collection of alternative map displays, this includes a) a contiguous cartogram, b) a non-contiguous cartogram, and c) a Dorling cartogram.
@@
 When communicating information that is relevant to the population, each member of the population can be given equal representation by transforming the map (Dorling 2012).
-The connected communities can be recognised by allowing the boundaries to maintain connection in the transformed display.
+The connectedness of the units can be preserved by using transformations that maintain the connection between boundaries.
 The contiguous cartogram displayed in Figure \ref{fig:tasdisplays}a draws attention to smaller geographic units when they are rescaled according to the population (Walter 2001).
@@
 2002).
+However, the relative size of units in comparison to the reference unit can lead to scaling issues.
 The size disparity between rural areas and urban areas result in reasonable display within the south eastern city of Hobart, but these units are not visible in the context of the Tasmania state map.
@@
 This map draws attention to the collection of coastal cities in Tasmania that were not apparent in Figure \ref{fig:tasdisplays} a or b.
-This display also highlights that the approximation of equal population is not easy to fulfil, as there is some disparity in the sizes of the circles.
+This display also highlights the difference in the population of each unit, as there is some disparity in the sizes of the circles.
 
-It is also common to treat all geographic units as equal, so that regardless of the population or other information, to generate equal size spatial polygons.
+Another common practice is to use equal-sized polygons and treat all geographic units as equal.
 The Dorling algorithm can be induced to do this, to make equallly sized circles.
@@
 (2015) describes a group of alternative maps called ``mosaic cartograms'' for tile displays.
-The geography of the USA has been transformed into a square-binned tile map manually and made available in the R package \CRANpkg{statebins} (Rudis 2020).The algorithm described below is an automatic layout of hexagon tiles, where a continguity constraint is relaxed.
+Similarly, the geography of USA has been transformed into a square-binned tile map manually and made available in the R package \CRANpkg{statebins} (Rudis 2020).The algorithm described below generates an automatic layout of hexagon tiles, where a continguity constraint is relaxed.
 This gives equal weight to each geographic area even if the population differs.
@@
 
-Compared to the choropleth map display in Figure \ref{fig:choro}, the low rates in the rural Australian communities are no longer dominating the display.
-While the representative hexagons are still visible against the black background, the much lower than average rates in rural Australia are less noticeable.
+Compared to the choropleth map display in Figure \ref{fig:choro}, the low rates in the rural Australian communities no longer dominate the display.
+While the corresponding hexagons are still visible against the black background, the lower rates in rural Australia are less prominent.
 
@@
 First, derive the set of centroids from the polygons provided, then create the grid of hexagon locations.
-These two processes are defined in the blue left column of the flow chart in figure \ref{fig:sugarbagflow}.
+These two processes are described in the blue left column of the flow chart in figure \ref{fig:sugarbagflow}.
 Each centroid can then be allocated to an available hexagon location.
 The steps for the allocation process are detailed in the right column of Figure \ref{fig:sugarbagflow}.
-There are several filter steps to speed the process of selecting an appropriate hexagon to represent each geographic unit.
+There are several filter steps to speed up the process of selecting an appropriate hexagon to represent each geographic unit.
 To make tessellated plots with the hexagon allocations, the point locations are converted into hexagon shapes.
@@
 The \pkg{sugarbag} package contains a set of functions that help R users to create a hexagon tile map.
-The algorithm presented in the \pkg{sugarbag} package operates on a set of simple feature geometry objects , known as \CRANpkg{sf} objects(Pebesma 2018).
+The algorithm presented in the \pkg{sugarbag} package operates on a set of simple feature geometry objects , known as \CRANpkg{sf} objects (Pebesma 2018).
 This package allows R users to create \pkg{sf} objects by importing polygons stored in various formats.
@@
 
-A user can tweak the parameters of the hexagon map using the additional arguments to the \code{create\_hexmap} function, but these options may affect the speed of the algorithm.
+The user can tweak the parameters of the hexagon map using additional arguments to the \code{create\_hexmap} function, but these options may affect the speed of the algorithm.
 The hexagon size may need adjustments depending on the density of the population; users can provide an appropriate hexagon size and re-run the algorithm.
@@
 
-If a user would like to perform each of the steps of the algorithm themselves, the necessary inputs will change for each function.
-For example, the \code{allocate} function can be used directly when a user wishes to use a set of centroids, rather than polygons.
+If a user would like to perform steps of the algorithm themselves, additional user input will be needed for the functions that perform each step.
+For example, if the user wishes to use a set of centroids, rather than polygons, the \code{allocate} function can be used directly.
 
-The set of SA2 polygons for Tasmania, using the 2011 definition of SA2s, is accessed from the \pkg{absmapsdata} package.
+The set of SA2 polygons for Tasmania, using the 2011 definition of SA2s, was accessed from the \pkg{absmapsdata} package (Mackey 2022).
 A single column of the data set is used to identify the unique areas.
@@
 It finds the grid points needed to best capture the set of centroids on a hexagon tile map.
-Reducing the buffer can help to decrease the amount of time taken, as there will be less points over the water to consider for each centroid allocation.
+Reducing the buffer size will decrease the amount of time that the algorithm needs to run for, as there will be less points over the water to consider for each centroid allocation.
 
-Not all of the grid points will be used, especially if islands result in a large grid space.
-To filter the grid for appropriate hexagon locations for allocation, the \texttt{create\_grid} function will call the \texttt{create\_buffer} function.
-It finds the grid points needed to best capture the set of centroids on a hexagon tile map.
-Reducing the buffer can help to decrease the amount of time taken, as there will be less points over the water to consider for each centroid allocation.
-
-The closest latitude row and longitude column are found for each centroid location.
+For each centroid location, the closest latitude row and longitude column are found.
 Then rows and columns of centroids are divided into 20 groups.
-The amount of rows in each latitude group and the amount of columns in each longitude group are used as the width of rolling windows.
+The number of rows in each latitude group and the number of columns in each longitude group are used as the width of rolling windows.
 The first rolling window step finds the minimum and maximum centroid values within each of the sliding window groups of longitude columns, and the groups of latitude rows.
@@
 
-A selection of possible hexagon locations around the centroid allows only the closest points that are not yet assigned to be considered.
+The algorithm creates a circle of points, by only keeping points within a certain radial distance around the original centroid location.
+Only the hexagons which are close to the centroid and have not been assigned are considered.
 The number of possible hexagon locations to consider for a centroid is determined by the hexagon filter.
-This is the maximum amount of hexagons between the centroid and the furthest considered hexagon.
+This is the maximum number of hexagons between the centroid and the furthest considered hexagon.
 It is used to subset possible grid points to only those surrounding the polygon centroid within an appropriate range.
@@
 
-The algorithm creates a circle of points, by only keeping points within a certain radial distance around the original centroid location.
-
 The \code{width} parameter is used to take a slice of the remaining points.
-The width is the amount of degrees used on either side of the angle from the focal point to centroid location.
+The slice centres on the angle from the focal point to centroid location.
 This uses the angle from the closest capital city, to the current centroid as seen in Figure \ref{fig:filterprocess} 2a.
@@
 
-Australia is used as an example, because it represents an extreme sparse geography and small dense population areas which produces unsatisfactory results with all existing cartogram-type algorithms.
+Australia serves as a good use case for the algorithm as it represents an extremely sparse geography and small dense population areas which cannot be satisfactorily represented by existing cartogram-like algorithms.
 However, the algorithm is sufficiently general to apply to other geographic regions, and indeed has been applied to make hexagon maps of the UK, USA and France.
 
-There are many possible extensions to the algorithm that might be valuable future work.
-The buffer allows extension beyond the furthest centroids, but there is no mechanism to protect borders to force centroids are placed within the geographic borders of a region (e.g.~country or state).
-The algorithm is also currently limited to representing each geographic area with only one hexagon.
+There are many possible extensions to the algorithm that might prove valuable in the future.
+The buffer allows extension beyond the furthest centroids, but there is no mechanism to protect borders by forcing centroids to be located within the geographic borders of a set of regions (e.g.~country or state).
+The algorithm is also currently limited to representing each geographic area with one hexagon only.
 In the filter step for final selection of a hexagon grid point for each centroid, a direct angle constraint is currently implemented, but it may narrowly miss potentially better hexagon allocation.
-Some other constraints, such as a logarithmic function may help to choose refine the final allocation to hexagons closer to the original centroid location.
-In a country like Australia, the vast centre produces a hexagon map with small isolated hexagons, even when the city centres are hugely expanded.
+Some other constraints, such as a logarithmic function may help to refine the final allocation to hexagons closer to the original centroid location.
+In a country like Australia, the vast empty interior produces a hexagon map with many small isolated hexagons, even when the city centres are hugely expanded.
 It could be useful to allow variable sized hexagons, primarily to increase the size of the isolated hexagons to improve their visibility.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-cartogram}{}}%
+Jeworutzki, Sebastian. 2020. \emph{Cartogram: Create Cartograms with r}. \url{https://CRAN.R-project.org/package=cartogram}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-ECGC}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-absmapsdata}{}}%
+Mackey, Will. 2022. \emph{Absmapsdata: A Catalogue of Ready-to-Use ASGS (and Other) Sf Objects}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-SAMGIS}{}}%
@@
 Pedersen, Thomas Lin, and David Robinson. 2019. \emph{{gganimate: A Grammar of Animated Graphics}}. \url{https://CRAN.R-project.org/package=gganimate}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R}{}}%
+R Core Team. 2012. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing. \url{http://www.R-project.org/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tilemaps}{}}%
+Rosenberg, Kaelyn. 2020. \emph{Tilemaps: Generate Tile Maps}. \url{https://CRAN.R-project.org/package=cartogram}.
 
@@
 %
-%
+\textit{ORCiD: \href{https://orcid.org/0000-0002-4616-0048}{0000-0002-4616-0048}}\\%
 \href{mailto:stephanie.kobakian@gmail.com}{\nolinkurl{stephanie.kobakian@gmail.com}}%
@@
 %
-%
+\textit{ORCiD: \href{https://orcid.org/0000-0002-3813-7155}{0000-0002-3813-7155}}\\%
 \href{mailto:dicook@monash.edu}{\nolinkurl{dicook@monash.edu}}%
@@
 %
-%
+\textit{ORCiD: \href{https://orcid.org/0000-0002-5146-7810}{0000-0002-5146-7810}}\\%
 \href{mailto:earl.duncan@qut.edu.au}{\nolinkurl{earl.duncan@qut.edu.au}}%

### 2023-07-13 kobakian-cook.Rmd
fixed github location
Amended development version github reference

@@
 
-The package can be installed from CRAN:
-
-```{r eval=FALSE, echo = TRUE}
-install.packages("sugarbag")
-```
-
-\noindent and the development version can be installed from the GitHub repository:
-
-```{r eval=FALSE, echo = TRUE}
-devtools::install_github("srkobakian","sugarbag")
-```
+The package can be installed from CRAN and the development version can be installed from the GitHub repository: https://github.com/srkobakian/sugarbag.
 

### 2023-07-13 kobakian-cook.tex
fixed github location
Amended development version github reference

@@
 \title{A Hexagon Tile Map Algorithm for Displaying Spatial Data}
-
 \author{by Stephanie Kobakian, Dianne Cook, and Earl Duncan}
@@
 
-The package can be installed from CRAN:
-
-\begin{verbatim}
-install.packages("sugarbag")
-\end{verbatim}
-
-\noindent and the development version can be installed from the GitHub repository:
-
-\begin{verbatim}
-devtools::install_github("srkobakian","sugarbag")
-\end{verbatim}
+The package can be installed from CRAN and the development version can be installed from the GitHub repository: \url{https://github.com/srkobakian/sugarbag}.
 

### 2023-07-13 kobakian-cook.Rmd
Load data

@@
 # Contiguous Cartograms
-if (!file.exists("data/ncont.rda")) {
+if (!file.exists("data/cont.rda")) {
   cont <- sa2thyroid_ERP %>% 
